\section{\texorpdfstring{$N=1$}{N=1} Compatibility with Vol. III Homotopy Descent}
\label{sec:vol3-homotopy-positive-cone-dictionary}

If a Vol.~III chambered Hall-descent datum satisfies the five comparison
conditions of Theorem~\ref{prop:compact-igusa-realization-criterion},
then its \(N=1\) decategorified boundary must match the Igusa datum
listed below.  This section proves no Hall-descent construction.  It
records only the standard effective chamber
\[
\begin{aligned}
\Gamma_{\mathrm{eff}}
= {}&
\{(n,l,m)\in\Z^3\mid m>0,\ n\ge0,\ l\in\Z\}\\
&{}\cup\{(n,l,0)\in\Z^3\mid n>0,\ l\in\Z\}\\
&{}\cup\{(0,l,0)\in\Z^3\mid l<0\}
\subset \Z^3 .
\end{aligned}
\]

The compatibility dictionary is:
$$
\begin{array}{c|c}
\mathrm{Vol.\ III\ Hall\ descent} & \mathrm{Igusa\ boundary}\\ \hline
\mathrm{Gram\ index\ lattice} & \Gamma_{\mathrm{ind}}=\Z^3\\
\mathrm{sector\ completion} & \Gamma_{\mathrm{eff}}\\
\mathrm{active\ denominator\ support} &
\Gamma_{\mathrm{act}}=\{\gamma\in\Gamma_{\mathrm{eff}}\mid f(nm,l)\ne0\}\\
\mathrm{Lorentzian\ degree} &
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}\\
\mathrm{orientation\ character} & \epsilon_o=\nu_{\Delta_5}\\
\mathrm{automorphic\ boundary} &
\operatorname{Borch}(\phi_{0,1})=\Delta_5\\
\mathrm{BKM\ denominator} &
\operatorname{den}(\autcor)=64^{-1}\Delta_5(2Z)\\
\mathrm{denominator\ algebra} &
\mathcal A_{\mathrm{den}}=\mathfrak g_{\Delta_5}\\
\mathrm{formal\ current\ envelope} &
\mathsf{Den}_{\Delta_5,E}
=U_E^{\mathrm{ch}}(\mathfrak g_{\Delta_5}\otimes\mathcal O_E)\\
\mathrm{scalar\ square} &
Z^X_{\mathrm{OP}}=Z^X_{\mathrm{DT}}=-4096\Delta_5^{-2}\quad(\mathrm{proved}).
\end{array}
$$

The degree map satisfies
$$
(\alpha(\gamma),\alpha(\eta))
=-2\langle\gamma,\eta\rangle_{\mathrm{ind}},
\qquad
(\alpha(n,l,m),\alpha(n,l,m))=-2(4nm-l^2).
$$
The real walls
$$
\delta_1=2f_2-f_3,\qquad
\delta_2=2f_{-2}-f_3,\qquad
\delta_3=f_3
$$
and the Weyl vector
$$
\rho=f_2-\frac12 f_3+f_{-2},\qquad
(\rho,\delta_i)=-1,
$$
are therefore the denominator polarisation of the same Gram-index
lattice whose cusp polarisation gives the Fock determinant.  The cone is
generated by the active support; triples in \(\Gamma_{\mathrm{eff}}\)
with zero Jacobi coefficient fix ordering and do not contribute visible
product factors.  The product alone does not exclude invisible
zero-superdimension root spaces.

This section adds no new denominator theorem and no row map
$$\Phi^{\mathrm{V3}}_j\longleftrightarrow F_i.$$
It records only the $N=1$ normalisation shared with Vol.~III:
$$
\operatorname{Borch}(\phi_{0,1})=\Delta_5,\qquad
\operatorname{den}(\autcor)=64^{-1}\Delta_5(2Z),\qquad
\kappa_{\mathrm{BKM}}(\autcor)=\mathrm{wt}(\Delta_5)=5.
$$
The full protected scalar is the square
$$
Z^X_{\square}=C_{\square}\Delta_5^{-2};
$$
the Oberdieck--Pixton and reduced Hilbert-scheme DT branches have
constant \(-4096\) in the quotient-by-\(E\) normalization of
Theorem~\ref{thm:op-square}.  The chiral/denominator half is
\(\Delta_5\).
Vol.~III's compact Hall--Drinfeld double is the microscopic descent
source in which a protected bracket could be realised from the actual
compactification, but only after the five comparison data of
Theorem~\ref{prop:compact-igusa-realization-criterion} are supplied:
finite-first oriented Hall descent, protected integration, charge
additive Hall primitives, Borcherds relations inside the Hall
super-commutator, and the completed Hopf pairing with orientation
character \(\nu_{\Delta_5}\).  It is not obtained by commuting a
Drinfeld double through a homotopy colimit.  A proved homotopy descent
would have to produce the positive half and its completion data.  The
Igusa boundary identifies only the denominator algebra
\(\mathfrak g_{\Delta_5}\) and its protected decategorified
multiplicities until those comparison data are proved.

For the Clery--Gritsenko rows $F_5,F_6,F_7,F_8$ this dictionary supplies
no nonabelian chamber, no simple real roots, no reflection character,
and no Weyl-sum side.  Rows $F_5,F_6,F_7,F_8$ are handled, when a
nonabelian bracket is needed, by the separate Govindarajan CHL/WKB
denominator theorem in Theorem~\ref{thm:govindarajan-denominator-rows}.
For $F_7$ this is a theorem on the $\mu_4$-multiplier cover determined
by the Clery--Gritsenko order-four multiplier.  None of these imported
denominator rows supplies a Vol.~III row map or a CY/DT/chiral boundary
host.
