\section{BPS bracket structure constants: denominator theorem and Hall obstruction}
\label{sec:bps-bracket-structure-constants}

\providecommand{\Z}{\mathbb Z}
\providecommand{\C}{\mathbb C}
\providecommand{\La}{\Lambda}
\providecommand{\autcor}{\mathfrak g_{\Delta_5}}
\providecommand{\smult}{\operatorname{smult}}
\providecommand{\rootmult}{\operatorname{mult}}
\providecommand{\Prim}{\operatorname{Prim}}

\subsection{Claim attacked}

The denominator algebra
$$
\mathcal A_{\mathrm{den}}=\autcor
$$
has a genuine Borcherds--Kac--Moody Lie superbracket.  The present
manuscript proves this algebraic bracket and its denominator identity.
The stronger physical claim is different:
$$
\Prim_{\mathrm{prot}}\mathcal P^{\mathrm{Hall}}_{K3\times E,\sigma,o}
\stackrel{?}{\cong}
\mathcal A_{\mathrm{den}}
$$
as charge-graded Lie superalgebras, with the bracket coming from compact
Hall/CoHA/Drinfeld correspondences.  This stronger statement is not
proved by the denominator product, by the scalar square, or by equality
of protected Euler characteristics.

\subsection{The constants fixed by the denominator presentation}

Let
$$
\gamma_1=(1,1,0),\qquad
\gamma_2=(0,1,1),\qquad
\gamma_3=(0,-1,0).
$$
Then
$$
\delta_1=\alpha(\gamma_1)=2f_2-f_3,\qquad
\delta_2=\alpha(\gamma_2)=2f_{-2}-f_3,\qquad
\delta_3=\alpha(\gamma_3)=f_3.
$$
The BPS pairing on these three charges is
$$
\bigl(\langle\gamma_i,\gamma_j\rangle_{\mathrm{BPS}}\bigr)_{i,j}
=
\begin{pmatrix}
-1&1&1\\
1&-1&1\\
1&1&-1
\end{pmatrix},
$$
and the Lorentzian anti-isometry gives
$$
A=(\delta_i,\delta_j)_{i,j}
=-2\bigl(\langle\gamma_i,\gamma_j\rangle_{\mathrm{BPS}}\bigr)_{i,j}
=
\begin{pmatrix}
2&-2&-2\\
-2&2&-2\\
-2&-2&2
\end{pmatrix}.
$$
Since \(f(0,1)=f(0,-1)=1\), the three real simple root spaces are
one-dimensional and even.  Choose Chevalley generators
$$
e_i\in\mathfrak g_{\delta_i},\qquad
f_i\in\mathfrak g_{-\delta_i},\qquad
h_i=[e_i,f_i]\qquad(1\leq i\leq3).
$$
The derivable structure constants are exactly
$$
[h_i,h_j]=0,\qquad
[h_i,e_j]=A_{ij}e_j,\qquad
[h_i,f_j]=-A_{ij}f_j,\qquad
[e_i,f_j]=\delta_{ij}h_i.
$$
Equivalently,
$$
[h_i,e_i]=2e_i,\qquad
[h_i,e_j]=-2e_j\quad(i\neq j),
$$
and the same formula with the opposite sign holds on \(f_j\).
The real Serre constants are
$$
(\operatorname{ad}e_i)^3e_j=0,\qquad
(\operatorname{ad}f_i)^3f_j=0
\qquad(i\neq j),
$$
because \(1-A_{ij}=3\).

For a positive imaginary simple root \(a\in
\La^{2,1}_{II}\cap\mathbb R_{>0}\mathcal P_{II}\), let
\(u=1,\ldots,\mu_{\bar p}(a)\) index the simple generators of parity
\(\bar p\):
$$
e_{a,u}\in\mathfrak g_a,\qquad
f_{a,u}\in\mathfrak g_{-a},\qquad
h_{a,u}=[e_{a,u},f_{a,u}].
$$
The denominator construction fixes
$$
[h_i,e_{a,u}]=(\delta_i,a)e_{a,u},\qquad
[h_i,f_{a,u}]=-(\delta_i,a)f_{a,u},
$$
and, for every real \(i\),
$$
(\operatorname{ad}e_i)^{1-(\delta_i,a)}e_{a,u}=0,\qquad
(\operatorname{ad}f_i)^{1-(\delta_i,a)}f_{a,u}=0.
$$
If two simple roots in the Borcherds generating set are orthogonal, then
$$
(\alpha_i,\alpha_j)=0
\quad\Longrightarrow\quad
[e_i,e_j]=[f_i,f_j]=0.
$$
These are presentation constants.  They are not compact Hall
correspondence counts.

\subsection{A low-root test}

The three pairwise sums of real simple roots are the primitive isotropic
rays:
$$
\delta_1+\delta_2=\alpha(1,2,1),\qquad
\delta_1+\delta_3=\alpha(1,0,0),\qquad
\delta_2+\delta_3=\alpha(0,0,1).
$$
Their signed root multiplicities are
$$
f(1,2)=10,\qquad f(0,0)=10,\qquad f(0,0)=10.
$$
The real-real commutators
$$
[e_1,e_2],\qquad [e_1,e_3],\qquad [e_2,e_3]
$$
give one named vector on each corresponding isotropic ray.  The
Gritsenko--Nikulin correction supplies the remaining simple imaginary
directions: on every primitive isotropic ray \(a\),
$$
\tau(ta)=9\qquad(t\geq1).
$$
Thus, for \(a=\delta_i+\delta_j\), the first isotropic root space has
one direction forced by the real-root commutator and nine imaginary
simple directions from the correction character.  This explains the
numerical equality
$$
1+9=10=f(0,0)\quad\hbox{or}\quad f(1,2),
$$
but it does not determine a Hall multiplication table.  It determines a
Borcherds presentation.

\subsection{Jacobi and Serre checks}

The Cartan--root Jacobi identity is forced by additivity of the degree:
for homogeneous \(x_\beta\in\mathfrak g_\beta\) and
\(x_\eta\in\mathfrak g_\eta\),
$$
[h_i,[x_\beta,x_\eta]]
=[ [h_i,x_\beta],x_\eta]+[x_\beta,[h_i,x_\eta]]
=((\delta_i,\beta)+(\delta_i,\eta))[x_\beta,x_\eta].
$$
Hence
$$
[x_\beta,x_\eta]\in\mathfrak g_{\beta+\eta}.
$$
For the real roots, the rank-two Serre check is
$$
(\operatorname{ad}e_i)^3e_j=0,\qquad
(\operatorname{ad}e_i)^2e_j\ \hbox{not forced to vanish}
\qquad(i\neq j),
$$
and similarly for the \(f_i\).  This is exactly the rank-three
symmetric generalized Cartan matrix with off-diagonal entries \(-2\).
The Jacobi identity for all higher constants is then a theorem of the
universal Borcherds--Kac--Moody presentation modulo the displayed
relations \cite{KAC:1,GN}.

\subsection{Why the naive protected Euler bracket fails}

The symmetric BPS form
$$
\langle\gamma,\eta\rangle_{\mathrm{BPS}}
=2(nm'+n'm)-ll'
$$
is the discriminant polarization and, through \(\alpha\), the Cartan
form.  It cannot by itself be the Hall supercommutator coefficient.

Indeed, the tempting rule
$$
[x_\gamma,x_\eta]_{\mathrm{naive}}
=\langle\gamma,\eta\rangle_{\mathrm{BPS}}\,x_{\gamma+\eta}
$$
already fails on the real simple roots.  Since \(e_i\) is even,
super-skew symmetry requires
$$
[e_i,e_i]=0.
$$
But
$$
\langle\gamma_i,\gamma_i\rangle_{\mathrm{BPS}}=-1,
$$
so the naive rule gives a nonzero multiple of \(x_{2\gamma_i}\).  For
\(i\neq j\) the same rule gives equal constants in both orders, while
an even Lie bracket requires
$$
[e_i,e_j]=-[e_j,e_i].
$$
Thus an honest Hall/CoHA realization must contain an orientation sign,
a skew Euler form, or an equivalent antisymmetrizing Drinfeld-double
datum.  The symmetric BPS pairing may grade the Cartan matrix; it is not
the commutator kernel.

\subsection{The Hall constants that would be needed}

A compact Hall realization would have to construct, for every active
charge \(\gamma\), an oriented critical moduli object
\(\mathfrak M_\gamma^\sigma\) and extension correspondences
$$
\mathfrak M_\gamma^\sigma\times\mathfrak M_\eta^\sigma
\xleftarrow{\ p_{\gamma,\eta}\ }
\mathfrak E_{\gamma,\eta}^\sigma
\xrightarrow{\ q_{\gamma,\eta}\ }
\mathfrak M_{\gamma+\eta}^\sigma.
$$
After vanishing cycles and the orientation line are fixed, the Hall
product has the form
$$
m_{\gamma,\eta}
=q_{\gamma,\eta!}\,p_{\gamma,\eta}^{\,*}
:
H^{\mathrm{crit}}(\mathfrak M_\gamma^\sigma)
\otimes
H^{\mathrm{crit}}(\mathfrak M_\eta^\sigma)
\longrightarrow
H^{\mathrm{crit}}(\mathfrak M_{\gamma+\eta}^\sigma),
$$
with the usual cohomological Hall modifications of
Kontsevich--Soibelman and Davison--Meinhardt \cite{KSCoHA,DavisonMeinhardtCoHA}.
The protected primitive bracket would then be
$$
[u,v]_{\mathrm{Hall}}
=m_{\gamma,\eta}(u,v)
-(-1)^{|u||v|}\,\varepsilon(\gamma,\eta)\,
m_{\eta,\gamma}(v,u),
$$
where \(\varepsilon(\gamma,\eta)\) is the orientation/Drinfeld sign
compatible with the completed Hopf pairing.

Choose protected primitive bases
$$
u_{\gamma,a}\in
\left(\Prim_{\mathrm{prot}}
\mathcal P^{\mathrm{Hall}}_{K3\times E,\sigma,o}\right)_\gamma .
$$
The required structure constants are the integers
$$
[u_{\gamma,a},u_{\eta,b}]_{\mathrm{Hall}}
=
\sum_c
C^{\,c}_{(\gamma,a),(\eta,b)}
u_{\gamma+\eta,c}.
$$
The comparison with the denominator algebra requires bases
\(v_{\alpha(\gamma),a}\in\mathfrak g_{\alpha(\gamma)}\) such that
$$
C^{\,c}_{(\gamma,a),(\eta,b)}
=
N^{\,c}_{(\alpha(\gamma),a),(\alpha(\eta),b)}
$$
for the Borcherds structure constants
$$
[v_{\alpha(\gamma),a},v_{\alpha(\eta),b}]
=
\sum_c
N^{\,c}_{(\alpha(\gamma),a),(\alpha(\eta),b)}
v_{\alpha(\gamma+\eta),c}.
$$
The denominator product determines only
$$
\sum_a(-1)^{|a|}
=\smult(\alpha(\gamma))=f(nm,l).
$$
It does not determine either side of the displayed equality of
structure constants.

\subsection{Exact obstruction}

There is no unconditional derivation in the present manuscript of an
honest Hall/CoHA/Drinfeld bracket realizing
\(\mathcal A_{\mathrm{den}}\).  The missing compact correspondence is
the following single package.

\begin{enumerate}
\item Compact finite-first moduli objects
\(\mathfrak M_\gamma^\sigma\) for the \(K3\times E\) BPS sector, with
the \(E\)-translation quotient and reduced/critical obstruction theory
fixed.
\item Oriented vanishing-cycle complexes on these moduli objects, with
orientation character descending to \(\nu_{\Delta_5}\).
\item Proper extension correspondences
\(\mathfrak E_{\gamma,\eta}^\sigma\) whose pull-push product is defined
before completing in charge.
\item A protected integration functor sending compact critical
cohomology to finite-dimensional super vector spaces and preserving the
Hall supercommutator on primitives.
\item A primitive/Hopf-pairing theorem identifying the Drinfeld double
with the denominator polarization, not merely with the scalar Fock
determinant.
\item A support theorem:
$$
f((n+n')(m+m'),l+l')=0
\quad\Longrightarrow\quad
[u_\gamma,u_{\gamma'}]_{\mathrm{Hall}}=0
$$
after projection to protected primitives.
\item The real and imaginary Borcherds relations inside the Hall
supercommutator:
$$
(\operatorname{ad}u_i)^3u_j=0\quad(i\neq j),
$$
the orthogonality relations for simple imaginary roots, and the
isotropic-ray multiplicity split \(1+9=10\) in the first root spaces.
\end{enumerate}

Supplying these seven items would prove the bracket comparison.  Without
them the strongest correct statement is conditional:
$$
\begin{gathered}
\Prim_{\mathrm{prot}}\mathcal P^{\mathrm{Hall}}_{K3\times E,\sigma,o}
\cong
\mathcal A_{\mathrm{den}},\\
\text{only if the compact Hall correspondence above exists}\\
\text{and satisfies the Borcherds relations.}
\end{gathered}
$$

\subsection{Check table}

\begin{center}
\begingroup
\small
\begin{tabular}{p{0.18\textwidth}|p{0.30\textwidth}|p{0.14\textwidth}|p{0.18\textwidth}}
\textbf{Datum} & \textbf{Formula} & \textbf{Status} & \textbf{Source}\\
\hline
real charges &
\(\gamma_1=(1,1,0),\ \gamma_2=(0,1,1),\ \gamma_3=(0,-1,0)\) &
proved &
active-support cone\\
Cartan matrix &
\((\delta_i,\delta_j)=
\left(\begin{smallmatrix}2&-2&-2\\-2&2&-2\\-2&-2&2\end{smallmatrix}\right)\) &
proved &
\(\alpha\) anti-isometry\\
Chevalley constants &
\([h_i,e_j]=A_{ij}e_j,\ [e_i,f_j]=\delta_{ij}h_i\) &
proved &
BKM presentation\\
real Serre &
\((\operatorname{ad}e_i)^3e_j=0\ (i\neq j)\) &
proved &
\(A_{ij}=-2\)\\
first isotropic roots &
\(\delta_i+\delta_j,\quad \smult=10=1+9\) &
proved in denominator algebra &
\(\phi_{0,1},\eta^9\)\\
naive Euler bracket &
\([x_\gamma,x_\eta]=
\langle\gamma,\eta\rangle_{\mathrm{BPS}}x_{\gamma+\eta}\) &
false &
super-skew test\\
compact Hall constants &
\(C^{\,c}_{(\gamma,a),(\eta,b)}\) &
open &
missing compact correspondence
\end{tabular}
\endgroup
\end{center}
