\section{Second attack on the chiral Koszul realization}
\label{sec:chiral-koszul-second-attack}

\providecommand{\Z}{\mathbb Z}
\providecommand{\C}{\mathbb C}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\Cur}{\operatorname{Cur}}
\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\Obs}{\operatorname{Obs}}
\providecommand{\BKM}{\mathrm{BKM}}
\providecommand{\Hall}{\mathrm{Hall}}
\providecommand{\hCS}{\mathrm{hCS}}
\providecommand{\barB}{\bar B}
\providecommand{\Omegach}{\Omega^{\mathrm{ch}}}
\providecommand{\SCchtop}{\mathsf{SC}^{\mathrm{ch,top}}}
\providecommand{\Den}{\mathsf{Den}}
\providecommand{\smult}{\operatorname{smult}}
\providecommand{\sdim}{\operatorname{sdim}}

The attacked claim is the following implication:
$$
\begin{gathered}
\Den_{\Delta_5,E}
=U_E^{\mathrm{ch}}\!
\left(\mathcal A_{\mathrm{den}}\otimes\mathcal O_E\right)\\
\Longrightarrow\quad
\text{compact}\ K3\times E\ \text{chiral Koszul realization.}
\end{gathered}
$$
This implication is false as a theorem from the data now in the paper.
The current envelope is constructed.  The compact chiral Koszul source is
not constructed.

\begin{definition}[Data actually constructed]
\label{def:second-attack-constructed-data}
The constructed Igusa data are
$$
\mathcal D_{\mathrm{cur}}=
\left(
E,\mathcal A_{\mathrm{den}},\alpha,
\Den_{\Delta_5,E},
\operatorname{den}(\mathcal A_{\mathrm{den}})
\right),
$$
where
$$
\mathcal A_{\mathrm{den}}=\mathfrak g_{\Delta_5},\qquad
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2},
$$
and
$$
\Den_{\Delta_5,E}
:=U_E^{\mathrm{ch}}\!
\left(\Cur_E(\mathcal A_{\mathrm{den}})\right),
\qquad
\Cur_E(\mathcal A_{\mathrm{den}})
=\mathcal A_{\mathrm{den}}\otimes\mathcal O_E.
$$
The denominator identity is
$$
\operatorname{den}(\mathcal A_{\mathrm{den}})
=64^{-1}\Delta_5(2Z),
$$
and the signed charge multiplicities are
$$
\sdim\mathcal A_{\mathrm{den},(n,l,m)}=f(nm,l).
$$
\end{definition}

\begin{definition}[Strong compact chiral Koszul realization]
\label{def:strong-compact-koszul-realization}
A strong compact chiral Koszul realization of
\(\Den_{\Delta_5,E}\) is a tuple
$$
\mathfrak R=
\left(
\mathcal F_{K3\times E,\sigma,o},
C_{K3\times E},
\tau,
\Theta_{\mathrm{Kos}},
\Theta_{\hCS\to\Hall}^{\mathrm{or}},
\mathcal D_\hbar,
\Psi^+_{\Hall\to\BKM}
\right)
$$
with the following properties.
\begin{enumerate}
\item \(\mathcal F_{K3\times E,\sigma,o}\) is a finite-first,
charge-completed Costello--Gwilliam factorization algebra on
\(\Ran(E)\), constructed from the compact \(K3\times E\) theory in
stability chamber \(\sigma\) and orientation \(o\).
\item \(C_{K3\times E}\) is a coaugmented conilpotent chiral coalgebra in
the completed category in which the Vol.~I--II bar-cobar formalism is
valid, and
$$
C_{K3\times E}\simeq
\barB^{\mathrm{ch}}_E
\left(\mathcal F_{K3\times E,\sigma,o}\right).
$$
\item The twisting morphism
$$
\tau:C_{K3\times E}\longrightarrow
\Den_{\Delta_5,E}
$$
has chiral cobar adjoint
$$
\Theta_{\mathrm{Kos}}:
\Omegach_E C_{K3\times E}
\longrightarrow
\Den_{\Delta_5,E}.
$$
\item \(\Theta_{\mathrm{Kos}}\) is a quasi-isomorphism in the completed
finite-first category.
\item The protected primitive comparison is a charge-preserving
isomorphism of Lie superalgebras:
$$
H^0\Prim_{\mathrm{prot}}
\left(\mathcal F_{K3\times E,\sigma,o}\right)_\gamma
\cong
\mathcal A_{\mathrm{den},\gamma}
=\mathfrak g_{\Delta_5,\alpha(\gamma)}.
$$
\item The maps
$$
\Theta_{\hCS\to\Hall}^{\mathrm{or}},\qquad
\mathcal D_\hbar,\qquad
\Psi^+_{\Hall\to\BKM}
$$
construct the oriented compact Hall source, the completed
Hall--Drinfeld double, and the comparison with the Borcherds
denominator algebra.
\end{enumerate}
\end{definition}

\begin{theorem}[No promotion from the current data]
\label{thm:no-promotion-from-current-data}
The data \(\mathcal D_{\mathrm{cur}}\) of
Definition~\ref{def:second-attack-constructed-data} do not determine a
strong compact chiral Koszul realization in the sense of
Definition~\ref{def:strong-compact-koszul-realization}.
\end{theorem}

\begin{proof}
Beilinson--Drinfeld supplies the functor
$$
\hbox{Lie-* algebras on }E
\longrightarrow
\hbox{chiral algebras on }E,
\qquad
\mathcal L\longmapsto U_E^{\mathrm{ch}}(\mathcal L).
$$
Applying it to
\(\mathcal L=\mathcal A_{\mathrm{den}}\otimes\mathcal O_E\) constructs
\(\Den_{\Delta_5,E}\).  This is a target chiral algebra.

Chiral Koszul realization asks for different input.  One needs a
coaugmented conilpotent chiral coalgebra
\[
C_{K3\times E}
\]
or a factorization algebra whose bar construction produces it, and a
quasi-isomorphism
$$
\Omegach_E C_{K3\times E}
\xrightarrow{\ \simeq\ }
\Den_{\Delta_5,E}.
$$
No such \(C_{K3\times E}\) is part of \(\mathcal D_{\mathrm{cur}}\).
The formal bar coalgebra
\(\barB_E^{\mathrm{ch}}(\Den_{\Delta_5,E})\), if the current envelope is
placed in a valid Vol.~I completed category, is the bar coalgebra of the
already constructed target.  It is not a compact \(K3\times E\) BPS
source.

The Costello--Gwilliam input has the same logical shape.  Once a BV
theory satisfying the quantum master equation and the required locality,
descent, and anomaly conditions is constructed, it produces a
factorization algebra of observables.  The compact
\(K3\times E\) BV/Hall object with protected primitive bracket
\(\mathfrak g_{\Delta_5}\) is not constructed by the BD current envelope.

The decategorified identities do not repair this gap.  The equations
$$
\smult(\alpha(n,l,m))=f(nm,l),
\qquad
Z^X_{\square}=C_{\square}\Delta_5^{-2}
$$
are Euler-characteristic data.  For any fixed integer \(c\), the same
Euler characteristic is realized by infinitely many super vector spaces:
$$
c=(c+r)-r\quad(c\geq0),\qquad
c=r-(r-c)\quad(c<0),\qquad r\geq0.
$$
Adding acyclic pairs also changes a chain model without changing its
Euler characteristic.  Therefore the determinant and denominator data do
not determine a differential, a factorization product, a bar coalgebra, a
Koszul twisting morphism, or Hall structure constants.

Finally, the Vol.~III compatibility note records the same boundary as an
open frontier:
$$
\begin{gathered}
\text{compact}\ K3\times E\ \text{Hall cosheaf},\\
\Theta_{\hCS\to\Hall}^{\mathrm{or}},\qquad
\mathcal D_\hbar,\qquad
\Psi^+_{\Hall\to\BKM}.
\end{gathered}
$$
Thus the attempted promotion fails at the source-construction step, not
at the BD current-envelope step.
\end{proof}

\begin{proposition}[The only tautological Koszul theorem available]
\label{prop:tautological-bar-cobar-current}
Assume, as an extra hypothesis, that \(\Den_{\Delta_5,E}\) belongs to a
completed chiral category where the Vol.~I bar-cobar adjunction applies,
and that \(\Den_{\Delta_5,E}\) lies in the corresponding Koszul locus.
Then the counit
$$
\Omegach_E\barB_E^{\mathrm{ch}}
\left(\Den_{\Delta_5,E}\right)
\longrightarrow
\Den_{\Delta_5,E}
$$
is a quasi-isomorphism.  This reconstructs the current envelope from its
own bar coalgebra.  It does not construct a compact \(K3\times E\)
factorization algebra and it does not identify physical BPS states with
Borcherds root spaces.
\end{proposition}

\begin{proof}
This is exactly the bar-cobar inversion theorem on the Koszul locus,
applied with
\[
\mathcal A=\Den_{\Delta_5,E}.
\]
The conclusion is internal to the current envelope.  No compact source,
Hall correspondence, BV quantization, or primitive-state comparison is
introduced by this application.
\end{proof}

\begin{theorem}[Sharp conditional realization theorem]
\label{thm:sharp-conditional-koszul-realization}
If a tuple \(\mathfrak R\) satisfying
Definition~\ref{def:strong-compact-koszul-realization} is constructed,
then \(\Den_{\Delta_5,E}\) is the compact \(K3\times E\) chiral Koszul
realization of the Igusa denominator algebra:
$$
\Omegach_E C_{K3\times E}
\xrightarrow{\ \simeq\ }
\Den_{\Delta_5,E},
$$
and the protected primitive bracket of
\(\mathcal F_{K3\times E,\sigma,o}\) is
$$
H^0\Prim_{\mathrm{prot}}
\left(\mathcal F_{K3\times E,\sigma,o}\right)
\cong
\mathcal A_{\mathrm{den}}
=\mathfrak g_{\Delta_5}.
$$
Consequently its denominator is
$$
\operatorname{den}
H^0\Prim_{\mathrm{prot}}
\left(\mathcal F_{K3\times E,\sigma,o}\right)
=64^{-1}\Delta_5(2Z).
$$
\end{theorem}

\begin{proof}
The quasi-isomorphism is part of the realization datum:
\[
\Theta_{\mathrm{Kos}}:
\Omegach_E C_{K3\times E}\xrightarrow{\simeq}\Den_{\Delta_5,E}.
\]
The primitive comparison in
Definition~\ref{def:strong-compact-koszul-realization} identifies the
protected primitive Lie superalgebra with
\(\mathcal A_{\mathrm{den}}\).  The denominator identity then follows
from Theorem~\ref{thm:denominator-algebra-identity}.  Nothing in this proof
is automatic from the scalar square; all chain-level and Hall--Drinfeld
maps are hypotheses.
\end{proof}

\begin{center}
\begingroup
\small
\begin{tabular}{p{0.32\textwidth}|p{0.22\textwidth}|p{0.34\textwidth}}
\textbf{Input} & \textbf{Status} & \textbf{Effect}\\ \hline
\(\mathcal A_{\mathrm{den}}=\mathfrak g_{\Delta_5}\) &
proved &
Borcherds denominator bracket.\\
\(\Den_{\Delta_5,E}=U_E^{\mathrm{ch}}(\mathcal A_{\mathrm{den}}\otimes
\mathcal O_E)\) &
proved &
BD current envelope on \(E\).\\
\(\barB_E^{\mathrm{ch}}(\Den_{\Delta_5,E})\) &
formal or conditional &
Bar of the target only; no compact source.\\
\(\mathcal F_{K3\times E,\sigma,o}\) &
missing &
Would be the compact Costello--Gwilliam/Hall factorization source.\\
\(\Theta_{\mathrm{Kos}}\) &
missing &
Would prove \(\Omegach C\simeq\Den_{\Delta_5,E}\).\\
Primitive bracket comparison &
missing &
Would turn Euler data into a state-space Lie superalgebra theorem.
\end{tabular}
\endgroup
\end{center}

\begin{remark}[Finite construction checklist]
\label{rem:finite-koszul-checklist}
The missing constructions are finite.
\begin{enumerate}
\item Construct the compact \(K3\times E\) Costello--Gwilliam observable
factorization algebra on \(\Ran(E)\), including finite-first completion.
\item Construct the oriented compact Hall cosheaf.
\item Construct the comparison \(\Theta_{\hCS\to\Hall}^{\mathrm{or}}\).
\item Prove protected integration and orientation character
\(\epsilon_o=\nu_{\Delta_5}\) in the same normalization as the Igusa
denominator.
\item Promote the Hall object from an abstract \(E_1\)-algebra in graded
vector spaces to an \(E_1\)-chiral or BD factorization object on the
geometric Ran space.
\item Construct the coaugmented conilpotent chiral coalgebra
\(C_{K3\times E}\) and prove the bar differential squares to zero, or
place the curved object in the correct completed/coderived category.
\item Prove the Koszul quasi-isomorphism
\(\Omegach_E C_{K3\times E}\simeq\Den_{\Delta_5,E}\).
\item Prove the protected primitive bracket comparison with all
Borcherds relations, not only
\(\sdim=f(nm,l)\).
\item Construct the completed Hall--Drinfeld double \(\mathcal D_\hbar\).
\item Construct the comparison \(\Psi^+_{\Hall\to\BKM}\) compatible with
the Hopf pairing.
\end{enumerate}
Until these ten constructions exist, the theorem status is:
BD current envelope proved; compact chiral Koszul realization
conditional; automatic realization false.
\end{remark}
