\subsection{\texorpdfstring{Boundary physical hosts for \(F_5\)--\(F_8\)}
{Boundary physical hosts for F5-F8}}

\begin{definition}[Physical-host certificate]
A physical host for a Clery--Gritsenko boundary row
\[
F_j,\qquad j\in\{5,6,7,8\},
\]
is the following certificate:
\[
\mathfrak H_j=
\left(
X_j,\Gamma_j^{\mathrm{BPS}},\mathscr D_j,
\widetilde{\Gamma}_j,\mathcal H_{j,\kappa}^{1\mathrm p},
Z_j^{\mathrm{red}},\mathsf C_j
\right).
\]
Here \(X_j\) is a compact Calabi--Yau threefold, an orbifold
Calabi--Yau threefold, or a CHL background with an oriented reduced
obstruction theory.  The lattice \(\Gamma_j^{\mathrm{BPS}}\) is the
physical charge lattice.  The group \(\mathscr D_j\) is the physical
duality group acting on \(\Gamma_j^{\mathrm{BPS}}\).  The group
\(\widetilde{\Gamma}_j\) is the automorphic group or cover on which the
denominator form is a scalar with its chosen character.

The one-particle protected object is a cusp-labelled Ramond-sector
index
\[
\mathcal H_{j,\kappa}^{1\mathrm p}(n,l)
\]
with
\[
\sdim\mathcal H_{j,\kappa}^{1\mathrm p}(n,l)
=\widetilde c_{j,\kappa}(n,l).
\]
The reduced scalar partition function is required to satisfy
\[
Z_j^{\mathrm{red}}(Z)=C_jF_j(Z)^{-2}
\]
in the same Fourier chamber and cover as the denominator.  The chiral
object \(\mathsf C_j\) is a Hall, Drinfeld, or factorization object whose
protected primitive bracket maps to the Govindarajan denominator algebra
and whose decategorified primitive Euler characteristics give the same
cusp-labelled exponents.
\end{definition}

\begin{remark}[Certificate versus shadow]
The product-degree lattice \(L_j^{\mathrm{prod}}\), the Weyl chamber of
Theorem~\ref{thm:govindarajan-denominator-rows}, and the virtual
product current envelope of Proposition~\ref{prop:eight-formal-current-rows}
are shadows of such a certificate.  They are not the certificate.  They
do not contain \(X_j\), \(\Gamma_j^{\mathrm{BPS}}\), the physical duality
action, the reduced obstruction theory, or a Hall/chiral source.
\end{remark}

\begin{theorem}[Current no-go]
From the data currently present in the manuscript and the cited
Govindarajan CHL/WKB denominator theorem, no complete certificate
\(\mathfrak H_j\) is constructed for any \(j=5,6,7,8\).
\end{theorem}

\begin{proof}
The Clery--Gritsenko theorem \cite{GC} gives the automorphic product,
character, divisor, and congruence group.  Proposition~\ref{prop:gc-row-data}
and Proposition~\ref{prop:congruence-product-degree-lattices} record the
cusp-labelled product exponents and the monomial degree maps.  These data
determine only signed exponents in an Euler product.

Theorem~\ref{thm:govindarajan-denominator-rows}, using
\cite{CD09BKM,GK09CHL,GK10Composite,Gov11BKM}, gives the
Weyl--Kac--Borcherds denominator data:
\[
L_j,\quad P_j,\quad \mathcal M_j,\quad W_j,\quad
\epsilon_j,\quad \rho_j,\quad N_j(a).
\]
This proves a denominator algebra.  It does not construct a compact or
orbifold Calabi--Yau host, a reduced DT/PT/OP partition function, a
Ramond-sector one-particle Hilbert space, a physical charge lattice with
duality action, or a Hall/chiral current source.

The formal super vector space used in Proposition~\ref{prop:eight-formal-current-rows}
is deliberately non-unique: any two graded virtual super vector spaces
with the same signed dimensions have the same determinant.  Therefore
the determinant cannot reconstruct the physical Hilbert space, parity,
orientation data, or bracket.  This proves the stated no-go from current
data.  It does not prove that such hosts cannot exist.
\end{proof}

\begin{definition}[Known lattice and index shadows]
For rows \(5,6,7\) the denominator lattice shadow is
\[
L_5=L_6=L_7=M_1=U(4)\oplus\langle2\rangle,
\]
with
\[
e^{\alpha_1(n,l,m)}=q^nr^ls^m.
\]
For row \(8\) it is
\[
L_8=M_2=U(8)\oplus\langle2\rangle,
\qquad
e^{\alpha_2(n,l,m)}=q^nr^ls^{2m}.
\]
The cusp-labelled index shadows are:
\[
\begin{array}{c|c|c}
j&\mathcal K_j&\sdim\mathcal H_{j,\kappa}^{\mathrm{virt}}\\ \hline
5&\{\infty,S\}&c_5,\ c_{5,S}\\
6&\{\infty,S\}&c_6,\ c_{6,S}\\
7&\{\infty,M,S\}&c_7,\ \frac12c_{7,M},\ c_{7,S}\\
8&\{\infty,S\}&c_8,\ c_{8,S}.
\end{array}
\]
These are virtual one-particle index shadows.  They are not
Ramond-sector Hilbert spaces unless a physical construction supplies the
state space and proves the displayed supertrace.
\end{definition}

\begin{theorem}[Row-by-row certificate status]
The physical-host certificate status of the four boundary rows is:
\[
\begin{array}{c|c|c|c}
j&\mathrm{known\ theorem}&\mathrm{candidate\ physical\ reading}
&\mathrm{certificate\ status}\\ \hline
5&F_5=\nabla_3=\operatorname{den}\mathcal G_1(2)
&N=1,\ M=2\ \mathrm{twisted\ CHL\ sector}
&\mathrm{not\ constructed}\\
6&F_6=\nabla_2=\operatorname{den}\mathcal G_1(3)
&N=1,\ M=3\ \mathrm{twisted\ CHL\ sector}
&\mathrm{not\ constructed}\\
7&F_7=\nabla_{3/2}=\operatorname{den}\mathcal G_1(4)
&N=1,\ M=4\ \mathrm{twisted\ CHL\ sector}
&\mathrm{not\ constructed\ on\ the\ }\mu_4\mathrm{\ cover}\\
8&F_8=Q_1=\operatorname{den}\mathcal G_2(4)
&N=2,\ M=4\ \mathrm{twisted\ CHL\ sector}
&\mathrm{not\ constructed}.
\end{array}
\]
The word ``candidate'' in the third column means only compatibility with
the Govindarajan denominator label \(\mathcal G_N(M)\).  It does not mean
that a compact CY/DT/chiral host has been produced.
\end{theorem}

\begin{proof}
The theorem column is exactly Theorem~\ref{thm:govindarajan-denominator-rows}
and its proof.  Govindarajan's table identifies the four square-root
forms with \(\mathcal G_1(2)\), \(\mathcal G_1(3)\),
\(\mathcal G_1(4)\), and \(\mathcal G_2(4)\).  For fixed CHL level \(N\)
the real roots and Weyl chamber are fixed; the twist \(M\) changes the
imaginary simple-root data.  This justifies the candidate labels.

The certificate data missing from the theorem are precisely \(X_j\),
\(\Gamma_j^{\mathrm{BPS}}\), \(\mathscr D_j\), the reduced obstruction
theory, \(Z_j^{\mathrm{red}}\), and \(\mathsf C_j\).  The proof of
Theorem~\ref{thm:govindarajan-denominator-rows} explicitly stops at
the denominator theorem and supplies no Vol.~III boundary partition
identity or CY/DT/chiral host.
\end{proof}

\begin{proposition}[Row \(F_5=\nabla_3\)]
The theorem-level data for \(F_5\) are:
\[
L_5=M_1,\qquad
P_5=\{(0,-1,0),(1,1,0),(0,1,1)\},
\qquad
\rho_5=\alpha_1(\tfrac12,\tfrac12,\tfrac12),
\]
\[
W_5=\langle s_\delta\mid \delta\in P_5\rangle,\qquad
\epsilon_5=\det,
\]
\[
\widetilde{\Gamma}_5=\Gamma_0^{(2)}(2)\ \hbox{with character}\
\chi_2^{(2)}\times v_H,
\]
and
\[
\alpha_5^{\mathrm{prod}}(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_5^{\mathrm{prod}}(n,l,m;S)=\alpha_1(2n,2l,2m).
\]
The one-particle index is only the virtual cusp-labelled class with
signed dimensions \(c_5\) and \(c_{5,S}\).  The scalar identity
\[
\nabla_3^2=\Phi_6
\]
is a CHL scalar-square identity; it is not a reduced DT/PT/OP theorem of
the form \(Z_5^{\mathrm{red}}=C_5\nabla_3^{-2}\).  The chiral object
constructed from the product is the abelian
\[
\mathsf{Prod}_{5,E}=U_E^{\mathrm{ch}}
(\mathcal V_5^{\mathrm{prod}}\otimes\mathcal O_E),
\]
while the nonabelian object is the imported denominator algebra
\(\mathcal G_1(2)\).  No Hall/chiral source identifies them with
protected primitives of a physical host.
\end{proposition}

\begin{proposition}[Row \(F_6=\nabla_2\)]
The theorem-level data for \(F_6\) are:
\[
L_6=M_1,\qquad P_6=P_5,\qquad
\rho_6=\alpha_1(\tfrac12,\tfrac12,\tfrac12),\qquad
\epsilon_6=\det,
\]
\[
\widetilde{\Gamma}_6=\Gamma_0^{(2)}(3)\ \hbox{with character}\
\chi_2^{(3)}\times v_H,
\]
and
\[
\alpha_6^{\mathrm{prod}}(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_6^{\mathrm{prod}}(n,l,m;S)=\alpha_1(3n,3l,3m).
\]
The one-particle index is only the virtual cusp-labelled class with
signed dimensions \(c_6\) and \(c_{6,S}\).  The scalar identity
\[
\nabla_2^2=\Phi_4
\]
does not prove \(Z_6^{\mathrm{red}}=C_6\nabla_2^{-2}\).  The current
object constructed in the manuscript is the abelian formal product
current envelope; the nonabelian denominator algebra is
\(\mathcal G_1(3)\).  The physical CY/DT/chiral host is not constructed.
\end{proposition}

\begin{proposition}[Row \(F_7=\nabla_{3/2}\)]
The theorem-level data for \(F_7\) are:
\[
L_7=M_1,\qquad P_7=P_5,\qquad
\rho_7=\alpha_1(\tfrac12,\tfrac12,\tfrac12),\qquad
\epsilon_7=\det,
\]
with automorphic group
\[
\Gamma_0^{(2)}(4)
\]
and an order-four multiplier.  The denominator theorem is a statement on
the associated \(\mu_4\)-multiplier cover:
\[
\widetilde{\Gamma}_7\longrightarrow\Gamma_0^{(2)}(4).
\]
The degree maps are
\[
\alpha_7^{\mathrm{prod}}(n,l,m;\infty)=\alpha_1(n,l,m),
\]
\[
\alpha_7^{\mathrm{prod}}(n,l,m;M)=\alpha_1(2n,2l,2m),\qquad
\alpha_7^{\mathrm{prod}}(n,l,m;S)=\alpha_1(4n,4l,4m).
\]
The one-particle index shadow has signed dimensions
\[
c_7,\qquad \frac12c_{7,M},\qquad c_{7,S}.
\]
The half coefficient is integral on the multiplier-cover support, but it
is not a physical half-Hilbert-space construction.  The scalar square
\[
F_7^2=\Phi_3
\]
forgets the cover, reflection sign, and parity.  Thus no ordinary scalar
denominator on \(\Gamma_0^{(2)}(4)\), no reduced partition identity
\[
Z_7^{\mathrm{red}}=C_7\nabla_{3/2}^{-2},
\]
and no chiral/Hall host follow from current data.
\end{proposition}

\begin{proposition}[Row \(F_8=Q_1\)]
The theorem-level data for \(F_8\) are:
\[
L_8=M_2,\qquad
P_8=\{(0,-1,0),(1,1,0),(1,3,1),(0,1,1)\},
\]
\[
\rho_8=\alpha_2(\tfrac14,\tfrac12,\tfrac14),\qquad
\epsilon_8=\det,
\]
\[
\widetilde{\Gamma}_8=\Gamma_2(2)\ \hbox{with character}\
\chi_4^{(2)}\times v_H,
\]
and
\[
\alpha_8^{\mathrm{prod}}(n,l,m;\infty)=\alpha_2(n,l,m),\qquad
\alpha_8^{\mathrm{prod}}(n,l,m;S)=\alpha_2(2n,2l,2m).
\]
The one-particle index is only the virtual cusp-labelled class with
signed dimensions \(c_8\) and \(c_{8,S}\).  Govindarajan identifies the
denominator algebra as \(\mathcal G_2(4)\), but no compact
level-\(2\), twist-\(4\) CY/DT/chiral host is constructed in this
manuscript.  No theorem gives
\[
Z_8^{\mathrm{red}}=C_8Q_1^{-2}.
\]
\end{proposition}

\begin{assumption}[What would make the candidate hosts physical]
The candidate symbols
\[
\mathcal X_{1,2}^{\mathrm{CHL}},\quad
\mathcal X_{1,3}^{\mathrm{CHL}},\quad
\mathcal X_{1,4}^{\mathrm{CHL}},\quad
\mathcal X_{2,4}^{\mathrm{CHL}}
\]
may be promoted to physical hosts only if the following data are supplied
row by row:
\[
\begin{gathered}
X_j,\quad \Gamma_j^{\mathrm{BPS}},\quad \mathscr D_j,\quad
\Gamma_j^{\mathrm{BPS}}\to L_j,\\
\mathcal H_{j,\kappa}^{1\mathrm p},\quad
Z_j^{\mathrm{red}}=C_jF_j^{-2},\quad
\mathsf C_j\to U_E^{\mathrm{ch}}(\mathcal G_N(M)\otimes\mathcal O_E),
\end{gathered}
\]
with the multiplier cover included in the row \(F_7\).  The
Oberdieck--Pixton theorem \cite{OB,OPand} proves the \(N=1\) Igusa
scalar branch.  Bryan's Hilbert-scheme computation \cite{BRYAN} and the
Borcea--Voisin or higher-dimensional routes \cite{BORCEA,VOISIN,CKOT,BOPY}
do not supply these four certificates unless an explicit comparison
theorem is added.
\end{assumption}

\begin{theorem}[Late-extension replacement text]
The following replacement text is theorem-level and may be inserted
where a late extension identifies the boundary rows with physical hosts:

\begin{quote}
Rows \(F_5,F_6,F_7,F_8\) have Clery--Gritsenko automorphic products and
Govindarajan CHL/WKB Weyl--Kac--Borcherds denominator identities.  This
is theorem-level denominator data.  It does not construct a CY/DT
partition function, a Ramond-sector one-particle Hilbert space, or a
chiral Hall source.  The row \(F_7\) is a theorem only after pullback to
the \(\mu_4\)-multiplier cover.  Any identity
\[
Z_j^{\mathrm{red}}=C_jF_j^{-2}
\]
for \(j=5,6,7,8\) is a separate physical-host theorem or an explicit
assumption, not a consequence of the product or denominator formula.
\end{quote}

The row-by-row replacement is:
\[
\begin{array}{c|c}
j&\mathrm{replacement}\\ \hline
5&\nabla_3\ \mathrm{has\ denominator\ algebra}\ \mathcal G_1(2);
\ \mathrm{host\ open}\\
6&\nabla_2\ \mathrm{has\ denominator\ algebra}\ \mathcal G_1(3);
\ \mathrm{host\ open}\\
7&\nabla_{3/2}\ \mathrm{has\ denominator\ algebra}\ \mathcal G_1(4)
\ \mathrm{on\ the}\ \mu_4\mathrm{\ cover};\ \mathrm{host\ open}\\
8&Q_1\ \mathrm{has\ denominator\ algebra}\ \mathcal G_2(4);
\ \mathrm{host\ open}.
\end{array}
\]
\end{theorem}

\begin{proof}
This is a restatement of the preceding propositions.  It preserves the
proved automorphic and denominator claims and deletes only the unproved
physical-host inference.
\end{proof}

\begin{remark}[Source anchors]
The local manuscript anchors are
Proposition~\ref{prop:gc-row-data},
Proposition~\ref{prop:congruence-product-degree-lattices},
Proposition~\ref{prop:eight-formal-current-rows},
Theorem~\ref{thm:govindarajan-denominator-rows},
Remark~\ref{rem:f7-mu4-cover}, and
Proposition~\ref{prop:boundary-scope}.  The auxiliary attack notes
numbered \(07\) and \(08\) in \texttt{agent\_material} are compatible
with this certificate obstruction.  The bibliographic
anchors are \cite{GC,CD09BKM,GK09CHL,GK10Composite,Gov11BKM} for the
automorphic and CHL denominator data, \cite{DMVV,DVV,HM} for the BPS
index background, \cite{OB,OPand,BRYAN} for the proved or conjectural
\(K3\times E\) scalar-square literature, and
\cite{KSCoHA,DavisonMeinhardtCoHA} for the Hall-algebra language.
\end{remark}
