\subsection{\texorpdfstring{Rows \(F_5\)--\(F_8\): CHL denominator hosts versus physical row maps}
{Rows F5-F8: CHL denominator hosts versus physical row maps}}

\subsubsection*{Claim attacked}

The claim under attack is:
\[
\mathrm{Clery\mbox{--}Gritsenko\ product}
\quad+\quad
\mathrm{Govindarajan\ CHL/WKB\ denominator}
\quad\Longrightarrow\quad
\mathrm{compact\ physical\ host}.
\]
The implication is false at the present level of data.  The left hand
side is theorem-level automorphic and denominator information.  The
right hand side requires a charge lattice, a protected one-particle
index, an orientation character, a reduced scalar integration theorem
when a scalar square is claimed, and a primitive Hall/chiral comparison.
None of those physical-row-map data is constructed in the audited
sources for \(F_5,F_6,F_7,F_8\).

\begin{definition}[Boundary-row status labels]
Use the following labels for \(j=5,6,7,8\).
\begin{description}
\item[\(\mathrm{CG}\)] the Clery--Gritsenko diagonal-divisor product and
divisor theorem.
\item[\(\mathrm{CHL/WKB}\)] the Weyl--Kac--Borcherds denominator theorem
for the corresponding Govindarajan twisted CHL row.
\item[\(\mathrm{scalar\ square}\)] a dyon-counting identity
\(F_j^2=\Phi\) for a scalar Siegel modular form.
\item[\(\mathrm{physical\ host}\)] a compact Calabi--Yau, orbifold
Calabi--Yau, CHL, Hall, or chiral construction with an oriented
protected theory whose one-particle index and primitives are the same
row.
\end{description}
A scalar square is not a denominator theorem.  A denominator theorem is
not a compact physical host.
\end{definition}

\begin{theorem}[Pinned automorphic and denominator ledger]
\label{thm:agent12-f5-f8-ledger}
The source-compatible ledger for the four boundary rows is:
\[
\begin{array}{c|c|c|c|c|c}
j&F_j&\Gamma_j,\nu_j&\mathrm{wt}&\mathrm{CHL/WKB\ denominator}
&\mathrm{physical\ host}\\ \hline
5&\nabla_3&
\Gamma_0^{(2)}(2),\ \chi_2^{(2)}\times v_H
&3&\mathcal G_1(2)&\mathrm{not\ constructed}\\
6&\nabla_2&
\Gamma_0^{(2)}(3),\ \chi_2^{(3)}\times v_H
&2&\mathcal G_1(3)&\mathrm{not\ constructed}\\
7&\nabla_{3/2}&
\Gamma_0^{(2)}(4),\ \chi_4^{(4)}\times v_H
&\frac32&\mathcal G_1(4)\ \mathrm{on\ the\ }\mu_4\mathrm{\ cover}
&\mathrm{not\ constructed}\\
8&Q_1&
\Gamma_2(2),\ \chi_4^{(2)}\times v_H
&1&\mathcal G_2(4)&\mathrm{not\ constructed}
\end{array}
\]
The product-degree lattices are
\[
L^{\mathrm{prod}}_5=L^{\mathrm{prod}}_6=L^{\mathrm{prod}}_7=M_1
=U(4)\oplus\langle2\rangle,\qquad
L^{\mathrm{prod}}_8=M_2=U(8)\oplus\langle2\rangle,
\]
with
\[
e^{\alpha_1(n,l,m)}=q^nr^ls^m,\qquad
e^{\alpha_2(n,l,m)}=q^nr^ls^{2m}.
\]
The product prefactors are
\[
\rho_5=\rho_6=\rho_7=\alpha_1(\tfrac12,\tfrac12,\tfrac12),
\qquad
\rho_8=\alpha_2(\tfrac14,\tfrac12,\tfrac14).
\]
The cusp-labelled degree maps are
\[
\alpha_5(n,l,m;\infty)=\alpha_1(n,l,m),\quad
\alpha_5(n,l,m;S)=\alpha_1(2n,2l,2m),
\]
\[
\alpha_6(n,l,m;\infty)=\alpha_1(n,l,m),\quad
\alpha_6(n,l,m;S)=\alpha_1(3n,3l,3m),
\]
\[
\alpha_7(n,l,m;\infty)=\alpha_1(n,l,m),\quad
\alpha_7(n,l,m;M)=\alpha_1(2n,2l,2m),\quad
\alpha_7(n,l,m;S)=\alpha_1(4n,4l,4m),
\]
\[
\alpha_8(n,l,m;\infty)=\alpha_2(n,l,m),\quad
\alpha_8(n,l,m;S)=\alpha_2(2n,2l,2m).
\]
Thus the signed product exponents are the cusp sums
\[
\widetilde c_{5,\infty}=c_5,\quad
\widetilde c_{5,S}=c_{5,S},\qquad
\widetilde c_{6,\infty}=c_6,\quad
\widetilde c_{6,S}=c_{6,S},
\]
\[
\widetilde c_{7,\infty}=c_7,\quad
\widetilde c_{7,M}=\frac12c_{7,M},\quad
\widetilde c_{7,S}=c_{7,S},\qquad
\widetilde c_{8,\infty}=c_8,\quad
\widetilde c_{8,S}=c_{8,S}.
\]
For \(F_7\) the half exponent belongs to the sourced
\(\mu_4\)-multiplier-cover product datum.  It is not a physical
half-Hilbert-space statement.
\end{theorem}

\begin{proof}
The group, weight, character, diagonal divisor, and product displays are
the Clery--Gritsenko diagonal-divisor classification and Borcherds
product theorem \cite{GC}.  The product-degree maps are forced by the
monomials in the four displayed products in
Proposition~\(\ref{prop:gc-row-data}\) and
Proposition~\(\ref{prop:congruence-product-degree-lattices}\).
Govindarajan's twisted CHL table identifies
\[
\nabla_3\leftrightarrow\mathcal G_1(2),\qquad
\nabla_2\leftrightarrow\mathcal G_1(3),\qquad
\nabla_{3/2}\leftrightarrow\mathcal G_1(4),\qquad
Q_1\leftrightarrow\mathcal G_2(4),
\]
and proves the WKB denominator identity for these rows
\cite{Gov11BKM}, with the Cheng--Dabholkar and
Govindarajan--Gopala Krishna CHL denominator analyses as input
\cite{CD09BKM,GK09CHL,GK10Composite}.  This proves the denominator
column and no more.
\end{proof}

\begin{theorem}[CHL/WKB denominator data]
\label{thm:agent12-chl-wkb-denominator-data}
The nonabelian data imported from the CHL/WKB theorem are:
\[
P^{(1)}=\{(0,-1,0),(1,1,0),(0,1,1)\}\subset M_1,
\]
\[
P^{(2)}=\{(0,-1,0),(1,1,0),(1,3,1),(0,1,1)\}\subset M_2.
\]
Rows \(F_5,F_6,F_7\) use \(P^{(1)}\), and \(F_8\) uses \(P^{(2)}\).
The Weyl chambers and Weyl groups are
\[
\mathcal M_j=\{x\in L_j\otimes\R\mid (x,\delta)\le0
\ \mathrm{for\ all}\ \delta\in P_j\},\qquad
W_j=\langle s_\delta\mid\delta\in P_j\rangle,
\]
and the reflection character is
\[
\epsilon_j(w)=\det(w).
\]
The Cartan matrices are
\[
A^{(1)}=
\begin{pmatrix}
2&-2&-2\\
-2&2&-2\\
-2&-2&2
\end{pmatrix},
\qquad
A^{(2)}=
\begin{pmatrix}
2&-2&-6&-2\\
-2&2&-2&-6\\
-6&-2&2&-2\\
-2&-6&-2&2
\end{pmatrix}.
\]
There are integral imaginary simple-root coefficients \(N_j(a)\) such
that
\[
\begin{aligned}
F_j(Z)
&=\sum_{w\in W_j}\det(w)
\left(e^{w(\rho_j)}
+\sum_{a\in L_j\cap\R_{>0}\mathcal M_j}
N_j(a)e^{w(\rho_j+a)}\right)\\
&=e^{\rho_j}
\prod_{\lambda\in\alpha_j(\mathcal D_j)}
(1-e^\lambda)^{\mu_j(\lambda)}.
\end{aligned}
\]
This is a denominator theorem.  It is not a compact enumerative theorem.
\end{theorem}

\begin{proof}
In the pairing
\[
((n,l,m),(n',l',m'))_t=2ll'-4t(nm'+n'm),
\]
each displayed simple real root has square \(2\), and the displayed
Weyl vectors satisfy
\[
(\alpha_1(\tfrac12,\tfrac12,\tfrac12),\delta)=-1
\quad(\delta\in P^{(1)}),
\]
\[
(\alpha_2(\tfrac14,\tfrac12,\tfrac14),\delta)=-1
\quad(\delta\in P^{(2)}).
\]
Hence the Weyl-vector equations are
\((\rho,\delta)=-(\delta,\delta)/2\).  The root systems and the
Weyl-denominator interpretation are the CHL/WKB data of
\cite{CD09BKM,GK09CHL,GK10Composite,Gov11BKM}, translated into the
product-degree notation of the manuscript.  For \(F_7\), the statement
is made only after pullback to the order-four multiplier cover.
\end{proof}

\begin{remark}[Scalar-square audit]
The scalar square identities have only scalar status:
\[
\nabla_3^2=\Phi_6,\qquad
\nabla_2^2=\Phi_4,\qquad
\nabla_{3/2}^2=\Phi_3,\qquad
Q_1^2=\Phi_2^{(2,4)}
\]
in the CHL/twisted-dyon normalisations recorded in the manuscript.
They do not remember the denominator sign, the Weyl chamber, the parity
of simple real roots, the additive Weyl sum, or the physical
orientation data.  They therefore cannot be used as row maps.
\end{remark}

\begin{theorem}[Physical-host obstruction from the audited sources]
\label{thm:agent12-physical-host-obstruction}
The audited sources do not construct a physical host for any of
\(F_5,F_6,F_7,F_8\).  More precisely, none of the audited sources
constructs a datum
\[
\mathfrak H_j=
\left(
X_j,\Gamma_j^{\mathrm{BPS}},\mathscr D_j,
\alpha_j^{\mathrm{phys}},
\widetilde\Gamma_j,
\mathcal H^{1\mathrm p}_{j,\kappa},
Z_j^{\mathrm{red}},
\mathsf C_j
\right)
\]
such that
\[
\alpha_j^{\mathrm{phys}}:\Gamma_j^{\mathrm{BPS}}\longrightarrow L_j
\]
matches the cusp-labelled degree maps of
Theorem~\ref{thm:agent12-f5-f8-ledger},
\[
\sdim\mathcal H^{1\mathrm p}_{j,\kappa}(n,l)
=\widetilde c_{j,\kappa}(n,l),
\]
\[
Z_j^{\mathrm{red}}(Z)=C_jF_j(Z)^{-2}
\]
in the same chamber and cover, and
\[
\Prim_{\mathrm{prot}}(\mathsf C_j)\cong \mathcal G_N(M)
\]
for the corresponding Govindarajan denominator algebra.
\end{theorem}

\begin{proof}
The Clery--Gritsenko source proves the automorphic product, character,
and diagonal divisor.  It does not define
\(X_j,\Gamma_j^{\mathrm{BPS}},\mathscr D_j\), a protected
one-particle Hilbert space, or a reduced obstruction theory.

The CHL sources prove denominator identities for twisted dyon
generating functions.  They supply the Weyl chamber, simple real roots,
reflection sign, additive Weyl side, and integral imaginary
simple-root coefficients.  They do not prove a compact
Calabi--Yau/DT/PT/OP identity \(Z_j^{\mathrm{red}}=C_jF_j^{-2}\), and
they do not construct a Hall or factorization algebra whose protected
primitives are the same BKM algebra.

The formal product current envelope in the manuscript is deliberately
abelian and non-unique: any virtual super vector space with the same
signed dimensions has the same determinant.  It cannot reconstruct a
physical Hilbert space, orientation, Behrend sign, or nonabelian
primitive bracket.
\end{proof}

\begin{proposition}[Candidate-host attack table]
\label{prop:agent12-candidate-host-attack}
The following candidate interpretations fail unless additional row-map
data are supplied:
\begin{center}
\small
\begin{tabular}{p{0.23\textwidth}|p{0.35\textwidth}|p{0.32\textwidth}}
route&available theorem&obstruction\\ \hline
CHL/Govindarajan&
twisted helicity trace forms, scalar squares, and WKB denominator
identities for \(\mathcal G_1(2),\mathcal G_1(3),\mathcal G_1(4),
\mathcal G_2(4)\)&
no compact reduced CY/DT theorem, no Hall/chiral primitive comparison,
no row map from a physical charge lattice to the cusp-labelled CG degree
maps\\
Borcea--Voisin&
K3-involution constructions of Calabi--Yau threefolds and mirror pairs
\cite{BORCEA,VOISIN}&
no formula identifying the protected index with
\(c_5,c_{5,S},c_6,c_{6,S},c_7,\frac12c_{7,M},c_{7,S},c_8,c_{8,S}\);
no denominator algebra comparison\\
\(K3\times E\) reduced counting&
Oberdieck--Pandharipande/Oberdieck--Pixton and reduced DT/PT theory give
the \(N=1\) Igusa scalar branch \cite{OPand,OB,OberdieckReducedPT}&
the theorem is \(\Delta_5^{-2}\), not
\(\nabla_3^{-2},\nabla_2^{-2},\nabla_{3/2}^{-2},Q_1^{-2}\)\\
BOPY&
curve-counting on abelian surfaces and threefolds, with Jacobi and
quasimodular generating series \cite{BOPY}&
no exact CG row map, no CHL WKB denominator comparison, no
cusp-labelled one-particle index equality\\
Oh--Thomas&
Calabi--Yau fourfold sheaf-counting and algebraic virtual cycles
\cite{OhThomasI,OhThomasII}&
different dimension and obstruction theory; no genus-two
diagonal-divisor row and no BKM denominator identity\\
Vol.~III comparison tuple&
the theorem file records the triple-indexed GC catalogue and the
\(\kappa_{\mathrm{BKM}}\) weight identity&
any tuple with weights \((5,2,1,1,\frac12,1,\frac14,0)\) is a separate
comparison system; direct identifications with \(F_5,F_7,F_8\) are false
by weight
\end{tabular}
\end{center}
\end{proposition}

\begin{proof}
Each route lacks at least one load-bearing piece of the physical-row-map
certificate in Theorem~\ref{thm:agent12-physical-host-obstruction}.
Borcea--Voisin supplies geometry but not the row exponents.  Reduced
\(K3\times E\) curve-counting supplies the Igusa square and no boundary
row square.  BOPY and Oh--Thomas supply enumerative technology in
different geometries or dimensions but no equality with the four
Clery--Gritsenko/Govindarajan products.  Vol.~III's theorem-level
triple-indexed catalogue agrees with the weights
\[
(5,2,3,1,2,\tfrac12,\tfrac32,1)
\]
in the GC order; the older comparison tuple is not a row map.
\end{proof}

\begin{definition}[Minimal physical row-map theorem]
\label{def:agent12-minimal-row-map}
A physical row-map theorem for \(F_j\), \(j=5,6,7,8\), is a theorem
constructing the following data.
\begin{enumerate}
\item A physical charge lattice and duality group
\[
\Gamma_j^{\mathrm{BPS}},\qquad \mathscr D_j\curvearrowright
\Gamma_j^{\mathrm{BPS}},
\]
together with a degree map
\[
\alpha_j^{\mathrm{phys}}:\Gamma_j^{\mathrm{BPS}}\to L_j
\]
which equals the cusp-labelled maps
\(\alpha_j(n,l,m;\kappa)\) on the charges counted by the product.
\item A protected one-particle index satisfying
\[
\sdim\mathcal H^{1\mathrm p}_{j,\kappa}(n,l)
=\widetilde c_{j,\kappa}(n,l)
\]
for every cusp label \(\kappa\).  For \(F_7\), this equality is on the
\(\mu_4\)-multiplier cover and includes
\(\widetilde c_{7,M}=c_{7,M}/2\).
\item An orientation character
\[
\operatorname{or}_j:\mathscr D_j\to\C^\times
\]
whose automorphic pullback is \(\nu_j\) and whose restriction to the
Weyl subgroup is \(\det\).
\item If a scalar square is claimed, an oriented reduced integration
theorem
\[
Z_j^{\mathrm{red}}(Z)=C_jF_j(Z)^{-2}
\]
in the same chamber, Fourier variables, branch, and multiplier cover.
\item A primitive algebra comparison
\[
\Prim_{\mathrm{prot}}(\mathsf C_j)
\cong\mathcal G_1(2),\mathcal G_1(3),\mathcal G_1(4),
\mathcal G_2(4)
\]
row by row, preserving \(P_j,\mathcal M_j,W_j,\epsilon_j,\rho_j\), the
product multiplicity \(\mu_j\), and the imaginary simple-root
coefficients \(N_j(a)\).
\end{enumerate}
\end{definition}

\begin{theorem}[Minimal row-map status]
No row \(F_5,F_6,F_7,F_8\) currently satisfies
Definition~\ref{def:agent12-minimal-row-map} in the manuscript or in
the audited primary-source chain.  Therefore every physical-host claim
for these rows must be written as conjectural or as an explicit future
construction problem.
\end{theorem}

\begin{proof}
The first three items require physical charge, duality, protected state,
and orientation data.  The audited automorphic and CHL denominator
sources do not contain such a compact row-map construction.  The fourth
item is known in this manuscript only for the \(N=1\) Igusa branch
\(\Delta_5^{-2}\).  The fifth item is stronger than the imported
denominator theorem: it asks that the denominator algebra arise as
protected primitives of the same physical object.  No audited source
proves that comparison for rows \(5\)--\(8\).
\end{proof}

\begin{proposition}[Paper-safe replacement language]
\label{prop:agent12-paper-safe-language}
The following language preserves all theorem-level physics and removes
the overclaim.

\begin{quote}
Rows \(F_5,F_6,F_7,F_8\) carry Clery--Gritsenko diagonal-divisor
automorphic products.  In the CHL/twisted-dyon normalization of
Cheng--Dabholkar, Govindarajan--Gopala Krishna, and Govindarajan, they
also carry Weyl--Kac--Borcherds denominator identities:
\[
F_5=\nabla_3=\operatorname{den}\mathcal G_1(2),\quad
F_6=\nabla_2=\operatorname{den}\mathcal G_1(3),
\]
\[
F_7=\nabla_{3/2}=\operatorname{den}\mathcal G_1(4)
\ \hbox{on the }\mu_4\hbox{-multiplier cover},\quad
F_8=Q_1=\operatorname{den}\mathcal G_2(4).
\]
These are theorem-level automorphic and denominator statements.  They
do not construct compact CY/DT partition functions, Ramond-sector
one-particle Hilbert spaces, or chiral Hall hosts.  Any identity
\[
Z_j^{\mathrm{red}}=C_jF_j^{-2}
\]
for \(j=5,6,7,8\) is a separate physical-host theorem or a stated
conjecture.
\end{quote}

For \(Q_1\), add:
\begin{quote}
The row \(F_8=Q_1\) is the \((t,N)=(2,2)\) Clery--Gritsenko row and the
\(\mathcal G_2(4)\) Govindarajan denominator row.  It is not an
\(N=1\) boundary row in disguise.
\end{quote}

For Vol.~III comparison language, add:
\begin{quote}
The Clery--Gritsenko boundary weights are
\[
\mathrm{wt}(F_5,F_6,F_7,F_8)=(3,2,\tfrac32,1).
\]
Any physical or chiral tuple with different weights is a separate row
system.  A comparison with \(F_5,\ldots,F_8\) requires an explicit row
map preserving group or cover, multiplier, cusp-labelled product
degrees, protected one-particle index, orientation character, and
primitive algebra.
\end{quote}
\end{proposition}

\begin{remark}[Local and primary-source anchors]
The local manuscript anchors audited here are
\(\texttt{main.tex:2519--2720}\),
\(\texttt{main.tex:2869--3492}\),
\(\texttt{main.tex:3520--4058}\), and
\(\texttt{main.tex:4071--4273}\), together with
\(\texttt{agent\_material/07\_nonabelian\_promotion\_f5\_f8.tex}\),
\(\texttt{agent\_material/08\_physical\_row\_map\_boundary\_extensions.tex}\),
\(\texttt{agent\_material/10\_boundary\_row\_physical\_hosts.tex}\), and
\(\texttt{agent\_material/11\_chl\_boundary\_primary\_source\_audit.tex}\).
The Vol.~III theorem anchors are
\(\texttt{~/calabi-yau-quantum-groups/FRONTIER.md}\) and
\(\texttt{chapters/examples/cy\_d\_kappa\_stratification.tex}\),
especially the triple-indexed Gritsenko--Clery catalogue and the
\(\kappa_{\mathrm{BKM}}\)-weight corollary.  The audited
\(\texttt{~/calabi-yau-quantum-groups/CLAUDE.md}\) still contains an
older comparison tuple with weights \((5,2,1,1,\frac12,1,\frac14,0)\);
that tuple must not be imported as the Clery--Gritsenko catalogue.

The primary-source anchors are Clery--Gritsenko Theorems \(1.4\) and
\(3.1\) \cite{GC}; Cheng--Dabholkar Sections \(4\)--\(5\)
\cite{CD09BKM}; Govindarajan--Gopala Krishna Sections \(4.3\)--\(4.4\)
\cite{GK09CHL}; Govindarajan--Gopala Krishna composite \(N=4\)
\cite{GK10Composite}; Govindarajan Sections \(4.2\)--\(4.3\), Table
\(3\), and Appendices C--D \cite{Gov11BKM}; and the enumerative
comparison sources \cite{OPand,OB,OberdieckReducedPT,BOPY,OhThomasI,
OhThomasII,BORCEA,VOISIN}.
\end{remark}

\begin{remark}[Files, checks, and remaining obligations]
Files changed:
\[
\texttt{agent\_material/12\_eight\_rows\_hosts\_F5\_F8\_attack\_heal.tex}.
\]
Checks run for this audit: local rule and source reads by \(\texttt{sed}\)
and \(\texttt{rg}\); cross-repo reads of the Vol.~III anchors; primary
arXiv/source-title checks for \cite{GC,Gov11BKM,GK09CHL,GK10Composite,
CD09BKM,OPand,BOPY,OhThomasI,OhThomasII}; \(\texttt{git diff --check}\)
on this file; weak-phrasing and non-ASCII scans.  A full
\(\texttt{make}\) build is not required for this standalone
agent-material file.

The open obligations are exact:
\[
\begin{array}{c|l}
F_5&\mathrm{construct\ a\ compact\ row\ map\ for\ }
\mathcal G_1(2)\ \mathrm{and}\ \nabla_3\\
F_6&\mathrm{construct\ a\ compact\ row\ map\ for\ }
\mathcal G_1(3)\ \mathrm{and}\ \nabla_2\\
F_7&\mathrm{construct\ the\ same\ datum\ on\ the\ }\mu_4
\mathrm{\ cover\ for\ }\mathcal G_1(4)\ \mathrm{and}\ \nabla_{3/2}\\
F_8&\mathrm{construct\ the\ level\ }2,\ \mathrm{twist\ }4
\mathrm{\ row\ map\ for\ }\mathcal G_2(4)\ \mathrm{and}\ Q_1
\end{array}
\]
Each obligation must prove the five conditions of
Definition~\ref{def:agent12-minimal-row-map}.  Until then, the correct
paper status is: automorphic product proved, CHL/WKB denominator proved,
scalar square recorded where sourced, compact physical host open.
\end{remark}
