\section{Synthesis architecture and theorem-strength attack-heal}
\label{sec:synthesis-architecture-attack-heal}

\subsection{Scope and source packet}

This dossier owns only
\[
\texttt{agent\_material/12\_synthesis\_architecture\_attack\_heal.tex}.
\]
It proposes integration policy for \(\texttt{main.tex}\); it does not
edit \(\texttt{main.tex}\).

The required local controls were read:
\[
\texttt{CLAUDE.md},\quad
\texttt{AGENTS.md},\quad
\texttt{/Users/raeez/ecosystem/INVARIANTS.md},\quad
\texttt{main.tex},\quad
\texttt{proj.bib}.
\]
The harness self-reflection section of
\(\texttt{/Users/raeez/ecosystem/AGENTS-HARNESS.md}\) was also read.
At the start of this pass no other
\(\texttt{agent\_material/12\_*}\) file was present.  During
verification two parallel \(12\)-packets appeared; both were read and
their row-host constraints are incorporated here:
\[
\texttt{12\_eight\_rows\_hosts\_F1\_F4\_attack\_heal.tex},\qquad
\texttt{12\_eight\_rows\_hosts\_F5\_F8\_attack\_heal.tex}.
\]

The synthesis incorporates the successful repairs recorded in the local
packets on compact Hall truncations, protected integration and
orientation, primitive bracket constants, OP/DT comparison, and boundary
row hosts:
\[
\begin{gathered}
\texttt{08\_compact\_hall\_factorization\_object.tex},\quad
\texttt{10\_compact\_hall\_atlas\_attack\_heal.tex},\quad
\texttt{11\_compact\_hall\_finite\_heart\_and\_hn.tex},\\
\texttt{05\_normalization\_chain.tex},\quad
\texttt{10\_bps\_bracket\_constants\_attack\_heal.tex},\quad
\texttt{11\_denominator\_low\_degree\_computation\_table.tex},\\
\texttt{10\_reduced\_dt\_pt\_op\_comparison\_theorem.tex},\quad
\texttt{11\_op\_dt\_theorem\_integration\_patch.tex},\\
\texttt{10\_boundary\_row\_physical\_hosts.tex},\quad
\texttt{11\_chl\_boundary\_primary\_source\_audit.tex},\quad
\texttt{11\_factorization\_koszul\_minimal\_data.tex},\\
\texttt{12\_eight\_rows\_hosts\_F1\_F4\_attack\_heal.tex},\quad
\texttt{12\_eight\_rows\_hosts\_F5\_F8\_attack\_heal.tex}.
\end{gathered}
\]

\subsection{North-star architecture}

The paper should read in the order forced by the physics, not in the
order in which the automorphic technology is easiest to state:
\[
\hbox{protected locality}
\longrightarrow
\hbox{factorization}
\longrightarrow
\hbox{primitives}
\longrightarrow
\hbox{denominator}
\longrightarrow
\hbox{scalar square}
\longrightarrow
\hbox{eight-row boundary physics}.
\]

\paragraph{Protected locality.}
The only physical object used at theorem level is the protected index.
Right-moving localization of the K3 Ramond sector gives the signed
Euler characteristic \(Z_{\mathrm{K3}}=2\phi_{0,1}\).  The compact
local theory on \(K3\times E\) is not constructed.  Its required first
datum is a holomorphic \(E_3\)-factorization algebra
\[
\mathcal A^{E_3}_X
\]
with descent, quantum master equation, anomaly cancellation, charge
completion, and finite-first control.  Until this datum is built,
locality is an open realization requirement, not a theorem.

\paragraph{Factorization.}
If the \(E_3\)-source exists, a chain-level \(K3\)-to-\(E\)
specialization must produce the curve-level chiral shadow
\[
\mathcal F_X\simeq
\mathrm{Sp}^{\mathrm{ch}}_{K3,E}(\mathcal A^{E_3}_X)
\in \mathrm{Fact}(\operatorname{Ran}(E)).
\]
This is the first place where collision maps can live.  The scalar
series and the Borcherds product do not supply these maps.  Pushforward
along \(p_E\), restriction to sectors, and chiral Koszul duality are
operations on a supplied \(\mathcal A^{E_3}_X\) or \(\mathcal F_X\);
they do not reconstruct the source.

\paragraph{Primitives.}
The theorem-level object is the virtual class
\[
\mathbb U_{n,l}\in K_0(\mathrm{sVect}_{\mathrm{fd}}),\qquad
\sdim\mathbb U_{n,l}=f(n,l),
\]
and the virtual one-particle determinant
\[
\mathcal V_{(n,l,m)}=\mathbb U_{nm,l}.
\]
This is a \(K_0\)-model.  It does not construct a canonical half of the
K3 Hilbert space, a one-particle Hilbert space on \(K3\times E\), or a
primitive bracket.

\paragraph{Denominator.}
The Gritsenko--Nikulin theorem constructs the denominator Lie
superalgebra
\[
\mathcal A_{\mathrm{den}}=\mathfrak g_{\Delta_5}
\]
with real simple roots \(\delta_1,\delta_2,\delta_3\), Weyl vector
\(\rho\), degree map
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2},
\]
visible signed root supermultiplicities \(f(nm,l)\) on
\(\Gamma_{\mathrm{act}}\), and denominator
\[
\operatorname{den}(\mathcal A_{\mathrm{den}})
=64^{-1}\Delta_5(2Z).
\]
This is a theorem about the denominator algebra.  It is not a theorem
about compact Hall constants.

\paragraph{Scalar square.}
The enumerative scalar branch is now theorem-level:
\[
Z^X_{\mathrm{DT}}(T,Q,P)
=Z^X_{\mathrm{OP}}(P,Q,T)
=-4096\,\Delta_5(Z)^{-2}.
\]
It uses Oberdieck's reduced DT/PT comparison, the primitive
Oberdieck--Pandharipande GW/PT comparison, and Oberdieck--Pixton.  The
physical D-brane protected-index dictionary remains conjectural:
\[
\Omega_X(h,d,n)\stackrel{\mathrm{phys}}{=}
\mathbf{DT}^X_{n,(\beta_h,d)}.
\]

\paragraph{Eight-row boundary physics.}
The Clery--Gritsenko catalogue supplies eight diagonal-divisor
automorphic products.  Rows \(1\)--\(4\) have Gritsenko--Nikulin
denominator theorems.  Row \(1\) also has the theorem-level
Oberdieck--Oberdieck--Pandharipande--Oberdieck--Pixton scalar host for
the Igusa square, but still no compact Hall/chiral host.  Rows
\(2\)--\(4\) should be treated as denominator rows only until a row-map
certificate is constructed.  Rows \(5\)--\(8\) have Govindarajan
CHL/WKB denominator theorems in the CHL normalization, with \(F_7\)
only on the \(\mu_4\)-multiplier cover.  No row \(5\)--\(8\) physical
host, reduced CY/DT scalar theorem, or compact chiral/Hall source is
constructed in the current manuscript.

\subsection{Theorem-strength ledger}

\begin{center}
\small
\begin{tabular}{p{0.23\textwidth}p{0.19\textwidth}p{0.46\textwidth}}
\hline
Claim & Status & Integration rule \\
\hline
\(Z_{\mathrm{K3}}=2\phi_{0,1}\) and right-moving localization &
proved under the unitary K3 sigma-model input &
Use as protected Euler characteristic.  Do not call
\(\phi_{0,1}\) an honest half-Hilbert-space character. \\
\(\mathbb U_{n,l}\) and \(\mathcal V_{(n,l,m)}=\mathbb U_{nm,l}\) &
constructed in \(K_0\) &
Promote only to virtual one-particle determinant.  Refuse Hilbert-space
or operator-product language. \\
\([q^{1/2}r^{1/2}s^{1/2}]\Delta_5=64\) &
proved normalization &
Explain from the theta-constant product before using \(D_5=64^{-1}\Delta_5\). \\
\(\mathcal D_X=\Delta_5\) &
theorem, by Borcherds--Gritsenko--Nikulin product &
State as normalized virtual Fock determinant.  It is not an analytic
branch and not a microscopic BPS space. \\
\(Z^X_{\mathrm{DT}}=Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2}\) &
theorem in the quotient-by-\(E\), Behrend-weighted primitive setting &
Promote fully as enumerative scalar theorem.  Keep the protected
D-brane dictionary conjectural. \\
\(\alpha(\Gamma_{\mathrm{act}})\) gives the type-II cone &
proved lattice/Jacobi-support computation &
Use to enter the Weyl chamber.  Do not infer absence of zero
superdimension roots or absence of microscopic states. \\
\(\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z)\) &
theorem, Gritsenko--Nikulin &
Promote as denominator algebra.  It determines signed root
superdimensions, not compact Hall constants. \\
Low-degree Chevalley--Serre constants &
denominator-algebra constants &
May be displayed as algebra constants after choosing Chevalley
generators.  Must be labelled not Hall constants. \\
\(\mathsf{Den}_{\Delta_5,E}\) &
formal BD current envelope &
Promote as formal current algebra on \(E\).  Refuse compact source or
Koszul realization without the five-object datum. \\
Sectorial Hall completion &
conditional proposition &
Use only after a stability sector, HN property, support property,
finite type, and oriented critical correspondences are supplied. \\
\(\mathfrak K_X\) compact realization datum &
criterion/open problem &
Consequences may be stated conditionally.  No existence language. \\
Rows \(F_2,F_3,F_4\) &
GN denominator theorems &
Use in the \(e_t^{(n,l,m)}=q^nr^ls^{tm}\) normalization.  Do not import
the doubled \(N=1\) normalization.  Physical hosts and row maps are
open. \\
Rows \(F_5,F_6,F_7,F_8\) &
CG products plus Govindarajan CHL/WKB denominator theorems &
Use as denominator rows only.  \(F_7\) always carries the
\(\mu_4\)-cover qualification.  Physical hosts remain open. \\
\hline
\end{tabular}
\end{center}

\subsection{Constants \(64\) and \(-4096\)}

The constants must be explained before they are used.

\paragraph{\(64\).}
\(\Delta_5\) is the product of the ten even genus-two theta constants.
With
\[
q=e^{2\pi iz_1},\qquad r=e^{2\pi iz_2},\qquad s=e^{2\pi iz_3},
\]
the leading theta-constant calculation gives
\[
\Delta_5(Z)=64q^{1/2}s^{1/2}(r^{1/2}-r^{-1/2})+\cdots,
\]
and in the Fourier convention used in the manuscript
\[
c_\Delta(1,1,1)=64,\qquad c_\Delta(1,-1,1)=-64.
\]
Therefore the monic Borcherds product is
\[
D_5=64^{-1}\Delta_5
=q^{1/2}r^{1/2}s^{1/2}
\prod_{\Gamma_{\mathrm{eff}}}(1-q^nr^ls^m)^{f(nm,l)}.
\]
Here ``monic'' refers to the vacuum monomial before expanding the
boundary factor \((1-r^{-1})\).

\paragraph{\(-4096\).}
Oberdieck--Pixton use the K3 elliptic genus as product input:
\[
Z_{\mathrm{K3}}=2\phi_{0,1}.
\]
Hence their monic product is the square of \(D_5\):
\[
\chi_{10}^{\mathrm{OP}}=D_5^2
=(64^{-1}\Delta_5)^2
=4096^{-1}\Delta_5^2.
\]
Their theorem gives
\[
Z^X_{\mathrm{OP}}=-\left(\chi_{10}^{\mathrm{OP}}\right)^{-1},
\]
so in the theta-constant normalization
\[
Z^X_{\mathrm{OP}}=-4096\,\Delta_5^{-2}.
\]
Oberdieck's reduced DT/PT theorem and the primitive OP/GW/PT comparison
give the same constant for the reduced Hilbert-scheme DT branch.  The
factor \(4096=64^2\) is only a normalization conversion.  The sign is
the sign in the OP theorem.

\subsection{Exact main-text integration instructions}

The current \(\texttt{main.tex}\) has already absorbed most successful
repairs.  The main thread should avoid a wholesale rewrite and apply
only local theorem-strength polish unless new reports from Agents
\(1\)--\(5\) add contradictions.

\paragraph{A. Introduction, lines 55--118 and 123--229.}
Keep the current abstract and claim-strength table.  They already state
OP/DT as theorem-level, the determinant as virtual, the denominator
algebra as known, and the compact realization as open.

Recommended local addition after the table at current lines
\(187\)--\(222\):
\[
\begin{minipage}{0.92\textwidth}
\small
\emph{Literature versus synthesis.}
Oberdieck--Pixton and Oberdieck supply the scalar OP/DT theorem.
Borcherds--Gritsenko--Nikulin supply the product and denominator
algebra.  Beilinson--Drinfeld supplies only the formal current envelope.
The synthesis in this paper is the normalization comparison and the
realization criterion; it is not a new construction of the compact
local theory.
\end{minipage}
\]

\paragraph{B. Honest one-particle lift, lines 524--543.}
Replace the phrase
\[
\hbox{``the same charge grading and the same signed multiplicities''}
\]
at current lines \(539\)--\(540\) by
\[
\hbox{``the same Gram-index grading and the same signed
supermultiplicities''}.
\]
Patch block:
\begin{verbatim}
The determinant construction uses only the virtual classes
\(\mathbb U_{n,l}\) and their signed dimensions.  The algebraic object
constructed from the same Gram-index grading and the same signed
supermultiplicities is the Borcherds denominator algebra.
\end{verbatim}

\paragraph{C. Normalization chain, lines 545--714 and 762--887.}
Keep the current structure.  It explains \(64\), \(D_5=64^{-1}\Delta_5\),
the substitution \(Z\mapsto2Z\), and \(-4096\).  Do not move the
normalization proof into an appendix; it is load-bearing.

If space is tightened, do not delete:
\[
[q^{1/2}r^{1/2}s^{1/2}]\Delta_5=64,\qquad
\chi_{10}^{\mathrm{OP}}=(64^{-1}\Delta_5)^2,\qquad
Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2}.
\]

\paragraph{D. Duality and Gram-index section, lines 975--1074.}
Keep the current ``Gram-index notation'' and ``Gram matrix convention''
language.  It correctly says the physical charge grading is supplied
input.  Before inscription, scan for any reintroduced
\(\Gamma_{\mathrm{BPS}}=\Z^3\) claim.  None should survive outside a
conditional physical-realization hypothesis.

\paragraph{E. Denominator and current section, lines 1566--1767.}
Keep the current theorem title ``Denominator algebra identity''.  The
theorem is correctly denominator-level.  Preserve the sentence:
\[
\hbox{``A microscopic BPS Hilbert space and its operator product require
separate construction.''}
\]
It is a guardrail, not exposition padding.

\paragraph{F. Compact realization, lines 1834--2096.}
Keep the finite-first HN replacement.  The key repaired claim is:
\[
\hbox{finite object}=
\varprojlim_R
\left(\mathcal H_{\sigma,S}^{or}/\mathcal H_{\sigma,S}^{>R}\right),
\]
not a finite active-support heart.  Do not remove the obstruction that
\(\Gamma_{\mathrm{act}}\) is not additive.

The criterion at lines \(1981\)--\(2003\) may be promoted only as:
\[
\hbox{if }\mathfrak K_X\hbox{ exists, then the primitive comparison
holds.}
\]
It must never read as an existence theorem.

\paragraph{G. Main synthesis theorem, lines 2382--2516.}
Keep this theorem as the local summit.  If the title is changed, use:
\[
\hbox{Virtual Igusa determinant and reduced OP/DT scalar square}.
\]
Do not use ``BPS theorem'' in the title.  Its last paragraph must keep
the compact \(E_3\)/Hall/chiral comparison as an open problem.

\paragraph{H. Eight-row part, lines 2521--4275.}
Separate the first row from the rest.  For \(F_1=\Delta_5\), the
scalar square is theorem-level by the reduced \(K3\times E\) OP/DT
comparison, and the denominator algebra is theorem-level by
Gritsenko--Nikulin.  The compact Hall/chiral host remains open.

For \(F_2,F_3,F_4\), the manuscript may use the Gritsenko--Nikulin
denominator algebras in their stated normalization.  It may not claim a
CHL identification, CY/DT scalar host, or compact physical realization
without a row-map certificate.  The same-weight collision
\(\Delta_2\) versus \(\nabla_2\) is not such a certificate.

Keep rows \(5\)--\(8\) as:
\[
\hbox{CG product}+\hbox{Govindarajan CHL/WKB denominator}
\not\Rightarrow
\hbox{physical host}.
\]
For \(F_7=\nabla_{3/2}\), every denominator statement must carry the
\(\mu_4\)-cover qualification.  Any row-map claim must name the group or
cover, character, divisor, Jacobi seed at every cusp, product-degree
lattice, Weyl vector, real roots, reflection character, CY/DT/chiral
host, and reduced scalar identity.

The minimal theorem-level row-map certificate for any boundary row is:
physical charge lattice, one-particle protected index, orientation
character, scalar theorem if a scalar square is claimed, and primitive
algebra comparison.  Without all five pieces the row remains a
denominator row plus an open physical-host problem.

\subsection{Claim-status recommendations}

\begin{enumerate}
\item Promote the reduced Hilbert-scheme DT branch to theorem-level,
with the hypotheses explicit: primitive non-zero \(\beta_h\), \(d\ge0\),
quotient-by-\(E\), Behrend-weighted invariants, and no MacMahon factor
because \(\chi(K3\times E)=0\).
\item Promote the determinant \(\mathcal D_X=\Delta_5\) only as a
virtual \(K_0\) determinant.  The word ``BPS'' may appear only as
``virtual BPS'' or inside the realization problem.
\item Promote the denominator algebra and its low-degree constants as
Gritsenko--Nikulin/Borcherds algebra facts.  Label every such constant
``not a compact Hall constant'' until a Hall correspondence computes it.
\item Promote \(\mathsf{Den}_{\Delta_5,E}\) as a formal current
envelope.  Refuse ``compact chiral Koszul theorem'' unless
\((\mathcal F_X,\mathcal H_X,C_X,\Theta_{\mathrm{Kos}},\Pi_{\mathrm{prim}})\)
are constructed.
\item Keep the compact Hall atlas as conditional.  The missing maps are:
HN descent, Thom--Sebastiani orientation transport, equivariant or
reduced \(E\)-descent retaining relative position, protected
integration, and orientation character comparison
\(\epsilon_o=\nu_{\Delta_5}\).
\item Keep physical row maps for \(F_5,\ldots,F_8\) open.  The
Govindarajan theorem proves denominator data, not a CY/DT scalar theorem
or compact host.
\item Keep physical row maps for \(F_2,F_3,F_4\) open as well.  Their
Gritsenko--Nikulin denominator theorems do not provide CY/DT scalar
hosts or compact Hall/chiral sources.
\item Keep external scalar-square branches separate:
\[
Z^X_{\square,\mathrm{ext}}=C_{\square,\mathrm{ext}}\Delta_5^{-2}.
\]
Do not call such a branch \(Z^X_{\mathrm{DT}}\) or assign it
\(-4096\) without an enumerative theorem.
\end{enumerate}

\subsection{Adversarial checklist before inscription}

Before the main thread writes any theorem-level sentence into
\(\texttt{main.tex}\), check:
\begin{enumerate}
\item Does every use of ``charge lattice'' distinguish the microscopic
compactification lattice from \(\Gamma_{\mathrm{gram}}=\Z^3\)?
\item Does every use of ``BPS'' have status: protected index,
conjectural D-brane dictionary, virtual \(K_0\) determinant, or open
realization?
\item Are \(64\) and \(-4096\) both explained before use?
\item Is \(D_5=64^{-1}\Delta_5\) kept distinct from
\(\Delta_5\), and is \(D_5(2Z)\) kept distinct from \(D_5(Z)\)?
\item Does every denominator identity specify its normalization:
\(64^{-1}\Delta_5(2Z)\) for the \(N=1\) doubled convention, and
\(a_j=1\) in the Gritsenko--Nikulin/Govindarajan product convention for
rows \(2\)--\(8\)?
\item Does any finite Hall object rely on a finite active-support heart?
If yes, delete and replace by HN height quotients.
\item Does any Hall bracket constant appear without a compact extension
correspondence, orientation cocycle, protected integration, basis, and
parity split?  If yes, downgrade to denominator constant.
\item Does any chiral Koszul assertion construct only
\(\Omega_E^{\mathrm{ch}}\bar B_E^{\mathrm{ch}}(\mathsf{Den})\to
\mathsf{Den}\)?  If yes, call it target-internal inversion, not compact
realization.
\item Does any boundary-row scalar square imply a denominator theorem?
If yes, require Weyl chamber, simple real roots, reflection character,
parity, and Weyl alternating sum.
\item Does any row \(F_7\) statement omit the \(\mu_4\)-cover?  If yes,
the statement is false as written.
\item Does any comparison tuple with weights
\((5,2,1,1,\tfrac12,1,\tfrac14,0)\) get identified with the
Clery--Gritsenko row system?  If yes, stop: it is a different indexing
system until a row map is built.
\item Does any row \(F_2,F_3,F_4\) statement claim a physical host from
the Gritsenko--Nikulin denominator theorem alone?  If yes, downgrade to
denominator-row status.
\item Are primary-source attributions present for all load-bearing
claims: Oberdieck--Pixton, Oberdieck, Oberdieck--Pandharipande,
Borcherds, Gritsenko--Nikulin, Clery--Gritsenko, Govindarajan,
Beilinson--Drinfeld?
\end{enumerate}

\subsection{Residual open obligations}

The remaining mathematical obligations are exact:
\begin{enumerate}
\item Construct the compact holomorphic \(E_3\)-factorization algebra on
\(K3\times E\), with QME, descent, anomaly cancellation, and
finite-first charge completion.
\item Construct the chain-level \(K3\)-to-\(E\) specialization and the
compact chiral shadow on \(\operatorname{Ran}(E)\).
\item Construct the oriented critical Hall atlas: extension-closed
heart, stability sector, HN property, support property, finite-type
semistable stacks, vanishing-cycle coefficients, and strong orientation.
\item Prove reduced or equivariant \(E\)-descent for Hall convolution,
retaining the relative \(E\)-position lost by the scalar quotient.
\item Prove \(\epsilon_o=\nu_{\Delta_5}\) on the reflection action for
the constructed orientation domain.
\item Prove protected primitive integration:
\[
\sdim\Prim_{\mathrm{prot},(n,l,m)}=f(nm,l).
\]
\item Prove the primitive Hall/factorization bracket satisfies the
Gritsenko--Nikulin/Borcherds relations, including real Serre,
imaginary-root parity, orthogonality, Hopf pairing, and radical
quotient.
\item Construct \(C_X\), prove conilpotence in the completed chiral bar
category, and construct
\[
\Theta_{\mathrm{Kos}}:\Omega_E^{\mathrm{ch}}C_X
\xrightarrow{\simeq}
\mathsf{Den}_{\Delta_5,E}.
\]
\item For rows \(2\)--\(8\), construct a physical-host certificate
\[
(X_j,\Gamma_j^{\mathrm{BPS}},\widetilde\Gamma_j,\theta_j,
Z_j^{\mathrm{red}},\mathcal H^{1p}_{j,\kappa},\mathsf C_j)
\]
before writing \(Z_j^{\mathrm{red}}=C_jF_j^{-2}\) as theorem.  For row
\(1\), the scalar host is known, but the analogous compact Hall/chiral
certificate is still open.
\end{enumerate}

\subsection{Files changed}

Only this file was created:
\[
\texttt{agent\_material/12\_synthesis\_architecture\_attack\_heal.tex}.
\]

\subsection{Checks run}

\begin{itemize}
\item \(\texttt{sed -n}\) reads of \(\texttt{CLAUDE.md}\),
\(\texttt{AGENTS.md}\), \(\texttt{/Users/raeez/ecosystem/INVARIANTS.md}\),
\(\texttt{/Users/raeez/ecosystem/AGENTS-HARNESS.md}\),
\(\texttt{main.tex}\), and \(\texttt{proj.bib}\).
\item \(\texttt{rg --files agent\_material}\) and
\(\texttt{find agent\_material -maxdepth 1 -name '12\_*' -print}\).
\item \(\texttt{sed -n}\) reads of the late-arriving
\(\texttt{12\_eight\_rows\_hosts\_F1\_F4\_attack\_heal.tex}\) and
\(\texttt{12\_eight\_rows\_hosts\_F5\_F8\_attack\_heal.tex}\) packets.
\item Targeted \(\texttt{rg}\) scans of \(\texttt{main.tex}\) for
\(\texttt{4096}\), \(\texttt{64}\), \(\texttt{Borcherds}\),
\(\texttt{Oberdieck}\), \(\texttt{Gritsenko}\), \(\texttt{Govindarajan}\),
\(\texttt{compact}\), \(\texttt{Hall}\), \(\texttt{realization}\),
\(\texttt{conject}\), and \(\texttt{open}\).
\item Targeted \(\texttt{nl -ba main.tex}\) reads around the abstract,
denominator/current section, synthesis theorem, and eight-row section.
\item Post-write \(\texttt{sed -n}\) reads of this dossier and targeted
\(\texttt{rg}\) scans for stale source-ledger language and forbidden
attribution strings.
\item \(\texttt{git status --short}\) before writing.
\end{itemize}

No manuscript build was run.  This file is an internal synthesis dossier
and is not included by \(\texttt{main.tex}\).
