\subsection{\texorpdfstring{Eight-row physical-host certificate repair}
{Eight-row physical-host certificate repair}}

\subsubsection*{Claim attacked}

The attacked claim is that the eight Clery--Gritsenko rows form a
physical-host catalogue once their products and denominator identities
are listed:
\[
\mathrm{CG\ product}
\quad+\quad
\mathrm{denominator\ row}
\quad\Longrightarrow\quad
\mathrm{physical\ host}.
\]
This implication is false.  A product row, a denominator row, a
CHL/dyon square, a reduced CY/DT scalar host, and a compact Hall/chiral
host are separate structures.

\subsubsection*{Repair inserted in the manuscript}

The repair introduces Definition~\ref{def:physical-host-certificate}
before the row tables in Section~\ref{sec:eight-dd-rows-status}.  A row
certificate has five independent levels:
\[
(\mathscr A_j,\mathscr D_j,\mathscr S_j,\mathscr Z_j,\mathscr H_j),
\]
where \(\mathscr A_j\) is the automorphic product,
\(\mathscr D_j\) is the Weyl--Kac--Borcherds denominator theorem,
\(\mathscr S_j\) is a CHL/dyon scalar-square certificate,
\(\mathscr Z_j\) is a reduced CY/DT scalar-host theorem, and
\(\mathscr H_j\) is a compact Hall/chiral primitive-bracket
certificate.

The row ledger in `main.tex` was rewritten with exactly these columns.
It now records:
\[
\begin{array}{c|c|c|c|c|c}
j&F_j&\mathscr A_j&\mathscr D_j&\mathscr Z_j&\mathscr H_j\\ \hline
1&\Delta_5&\mathrm{proved}&\mathrm{GN\ proved}&
\mathrm{OP/DT\ scalar\ host\ proved}&\mathrm{open}\\
2&\Delta_2&\mathrm{proved}&\mathrm{GN\ proved}&
\mathrm{no\ audited\ host}&\mathrm{no\ audited\ host}\\
3&\Delta_1&\mathrm{proved}&\mathrm{GN\ proved}&
\mathrm{no\ audited\ host}&\mathrm{no\ audited\ host}\\
4&\Delta_{1/2}&\mathrm{proved\ on\ cover}&
\mathrm{GN\ proved\ on\ cover}&
\mathrm{no\ audited\ host}&\mathrm{no\ audited\ host}\\
5&\nabla_3&\mathrm{proved}&
\mathrm{Govindarajan\ }\mathcal G_1(2)&
\mathrm{no\ CY/DT\ certificate}&\mathrm{no\ compact\ certificate}\\
6&\nabla_2&\mathrm{proved}&
\mathrm{Govindarajan\ }\mathcal G_1(3)&
\mathrm{no\ CY/DT\ certificate}&\mathrm{no\ compact\ certificate}\\
7&\nabla_{3/2}&\mathrm{proved\ on\ }\mu_4\mathrm{\ cover}&
\mathrm{Govindarajan\ }\mathcal G_1(4)\ \mathrm{on\ }\mu_4&
\mathrm{no\ CY/DT\ certificate}&\mathrm{no\ compact\ certificate}\\
8&Q_1&\mathrm{proved}&
\mathrm{Govindarajan\ }\mathcal G_2(4)&
\mathrm{no\ CY/DT\ certificate}&\mathrm{no\ compact\ certificate}.
\end{array}
\]
The \(\mathscr S_j\) column is nonempty for rows \(5\)--\(8\) only as a
sourced dyon-square statement:
\[
\nabla_3^2=\Phi_6,\qquad
\nabla_2^2=\Phi_4,\qquad
\nabla_{3/2}^2=\Phi_3,\qquad
Q_1^2=\Phi_2^{(2,4)}.
\]
These identities do not imply \(\mathscr Z_j\) or \(\mathscr H_j\).

\subsubsection*{Attack--heal checks}

\begin{enumerate}
\item \(F_1\).  The repaired statement is sharp: the reduced
\(K3\times E\) OP/DT scalar host is proved,
\[
Z^X_{\mathrm{DT}}=Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2},
\]
while the compact Hall/chiral host remains open.  The virtual determinant
is not promoted to a compact source.
\item \(F_2,F_3,F_4\).  The Gritsenko--Nikulin denominator rows remain
theorem-level.  No audited source supplies a CHL row map, reduced
curve-counting theorem, Hall object, or factorization host for these rows.
\item \(F_5,F_6,F_7,F_8\).  The Govindarajan CHL/WKB denominator
theorem is retained.  The scalar dyon squares are recorded only in the
\(\mathscr S_j\) level.  No physical host is asserted without a
certificate.
\item \(F_7\).  Every denominator and square-root statement carries the
\(\mu_4\)-multiplier-cover qualification forced by the order-four
Clery--Gritsenko multiplier.
\item \(Q_1\).  The row is treated as the special
\((t,N)=(2,2)\), \(\mathcal G_2(4)\) Govindarajan row.  It is not
identified with an \(N=1\) boundary row or a weight-zero comparison slot.
\item Comparison symbols.  The tuple
\[
(5,2,1,1,\tfrac12,1,\tfrac14,0)
\]
is kept separate from the Clery--Gritsenko weights.  A comparison with
the \(F_i\) rows now requires the relevant entries of the physical-host
certificate.
\end{enumerate}

\subsubsection*{Files changed}

\[
\begin{array}{l}
\texttt{main.tex},\\
\texttt{agent\_material/13\_eight\_row\_certificate\_attack\_repair.tex}.
\end{array}
\]

\subsubsection*{Checks run}

\[
\begin{array}{l}
\texttt{sed}\ \mathrm{reads\ of\ CLAUDE.md,\ AGENTS.md,\ }
\texttt{/Users/raeez/ecosystem/INVARIANTS.md},\\
\texttt{sed}\ \mathrm{reads\ of\ main.tex\ row\ sections,\ }
\texttt{agent\_material/12\_eight\_rows\_hosts\_F1\_F4\_attack\_heal.tex},\\
\texttt{sed}\ \mathrm{reads\ of\ }
\texttt{agent\_material/12\_eight\_rows\_hosts\_F5\_F8\_attack\_heal.tex},\\
\texttt{sed}\ \mathrm{reads\ of\ }
\texttt{agent\_material/11\_chl\_boundary\_primary\_source\_audit.tex},\\
\texttt{rg}\ \mathrm{for\ physical\ host,\ CHL,\ Govindarajan,\ }
\mathrm{and\ certificate\ language},\\
\texttt{git\ diff\ --check\ --\ main.tex\ }
\texttt{agent\_material/13\_eight\_row\_certificate\_attack\_repair.tex},\\
\texttt{pdflatex\ -interaction=nonstopmode\ -file-line-error\ }
\texttt{-output-directory=/tmp/igusa-cusp-form-build\ main.tex}.
\end{array}
\]
The TeX pass was intentionally run into \(\texttt{/tmp}\), not
\(\texttt{out/}\), because \(\texttt{out/main.pdf}\) was already modified
by another worker.  The pass completed successfully.  Undefined
references and citations remain the expected one-pass/no-bibtex warnings.

\subsubsection*{Residual open obligations}

\[
\begin{array}{c|p{0.72\textwidth}}
F_1&
Construct the compact protected Hilbert space, orientation comparison,
Hall/factorization source, and primitive bracket comparison with
\(\mathfrak g_{\Delta_5}\).\\
F_2,F_3,F_4&
Find or construct reduced scalar identities
\(Z_j^{\mathrm{red}}=C_jF_j^{-2}\), physical charge lattices, and
Hall/chiral hosts matching the Gritsenko--Nikulin denominator rows.\\
F_5,F_6,F_7&
Construct compact row maps for
\(\mathcal G_1(2),\mathcal G_1(3),\mathcal G_1(4)\), including the
\(\mu_4\)-cover for \(F_7\).\\
F_8&
Construct the level-two, twist-four row map for
\(\mathcal G_2(4)\) and \(Q_1\).\\
Comparison rows&
For every fractional or external comparison symbol, construct the
modular-root certificate, exact row map, reduced scalar theorem if
claimed, and compact Hall/chiral primitive comparison.
\end{array}
\]
