\section{Abstract and introduction rewrite attack-repair}
\label{sec:intro-rewrite-attack-repair}

\subsection{Claim attacked}

The attacked weakness was scalar-first exposition.  Beginning with
\[
Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2}
\]
makes the paper read as a normalization recovery problem.  The correct
logical order is physical:
\[
\hbox{protected locality}
\longrightarrow
\hbox{compact/hybrid factorization}
\longrightarrow
\hbox{primitive recognition}
\longrightarrow
\hbox{Borcherds denominator}
\longrightarrow
\hbox{OP scalar square}
\longrightarrow
\hbox{eight-row host certificates}.
\]

\subsection{Findings}

\begin{enumerate}
\item The abstract now starts from protected K3 localization and the
virtual one-particle determinant.  It states that no microscopic Hilbert
space or compact local algebra is constructed.
\item The five structural levels are explicit in the introduction:
virtual determinant, scalar Behrend square, BKM denominator, compact
Hall/factorization realization, and eight-row host certificates.
\item The \(\operatorname{Ran}(E)\) obstruction is visible before the
first part: positive elliptic degree is global over \(E\), so ordinary
support-local factorization sees only projection-finite sectors.
\item The primitive recognition statement is labelled conditional.  If
\(\mathfrak K_X\) exists with the oriented Hall object, protected
integration, chiral comparison, and primitive Lie comparison, then the
primitive algebra is recognized as \(\mathfrak g_{\Delta_5}\).  This is
not an existence theorem.
\item The constants are explained once at the introductory level:
\[
[q^{1/2}r^{1/2}s^{1/2}]\Delta_5=64,\qquad
D_5=64^{-1}\Delta_5,\qquad
\chi_{10}^{\mathrm{OP}}=D_5^2,
\]
hence
\[
Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1}
=-4096\Delta_5^{-2}.
\]
\item The orientation monodromy problem is separated from scalar
normalization:
\[
\epsilon_o=\nu_{\Delta_5}
\]
remains open.
\item The eight-row boundary discussion now requires a row certificate
before a Clery--Gritsenko row becomes a physical host.
\end{enumerate}

\subsection{Files changed}

\begin{itemize}
\item \texttt{main.tex}: owned range only, from
\verb|\begin{abstract}| through the end of the introduction and
claim-strength block before the first \verb|\part|.
\item \texttt{agent\_material/13\_intro\_rewrite\_attack\_repair.tex}.
\item \texttt{out/main.pdf}: regenerated by the forced paper build.
\end{itemize}

Concurrent work was observed in \(\texttt{main.tex}\) outside the owned
introductory range,
\(\texttt{appendices/boundary\_compatibility\_conditions.tex}\),
\(\texttt{agent\_material/13\_integration\_orientation\_attack\_repair.tex}\),
\(\texttt{agent\_material/13\_primitive\_recognition\_attack\_repair.tex}\),
\(\texttt{agent\_material/13\_ranE\_obstruction\_attack\_repair.tex}\),
and
\(\texttt{agent\_material/13\_synthesis\_coherence\_attack\_repair.tex}\).
Those non-owned text ranges and files were not edited here.

\subsection{Checks run}

\begin{itemize}
\item Read \texttt{CLAUDE.md}, \texttt{AGENTS.md},
\texttt{/Users/raeez/ecosystem/INVARIANTS.md},
\texttt{/Users/raeez/ecosystem/AGENTS-HARNESS.md} self-reflection
section, \texttt{main.tex}, and
\texttt{agent\_material/12\_synthesis\_architecture\_attack\_heal.tex}.
\item Targeted \(\texttt{rg}\) scans of \(\texttt{main.tex}\) for
\(\operatorname{Ran}(E)\), orientation, monodromy, primitive
recognition, row certificate, \(64\), \(-4096\), Behrend, Hall,
factorization, and eight-row anchors.
\item Focused read-back of \(\texttt{main.tex}\) lines containing the
abstract and introduction after the patch.
\item Forced paper build:
\[
\texttt{make -B out/main.pdf}
\]
completed successfully.
\end{itemize}

\subsection{Remaining issues}

\begin{enumerate}
\item The compact holomorphic \(E_3\)-factorization algebra on
\(K3\times E\) remains unconstructed.
\item The \(\operatorname{Ran}(E)\) obstruction still requires a chosen
repair route: projection-finite locality plus global Hecke/Fock modes,
or a hybrid local/global wrapped factorization theory.
\item The geometric orientation character \(\epsilon_o\) and its
comparison with \(\nu_{\Delta_5}\) remain open.
\item The primitive comparison remains conditional on the full compact
Igusa datum, including protected integration and presentation-level
Borcherds relations.
\item Rows \(2\)--\(8\) have no physical-host certificate in this
manuscript.  Row \(1\) has the scalar OP/DT host and the denominator
algebra, but its compact Hall/chiral host is still open.
\end{enumerate}
