\section{Primitive recognition theorem: attack--repair}
\label{sec:primitive-recognition-attack-repair}

\providecommand{\Z}{\mathbb Z}
\providecommand{\C}{\mathbb C}
\providecommand{\La}{\Lambda}
\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\sdim}{\operatorname{sdim}}
\providecommand{\smult}{\operatorname{smult}}
\providecommand{\autcor}{\mathfrak g_{\Delta_5}}

\subsection{Claim attacked}

The false implication is
\[
\mathcal D_X=\Delta_5,\qquad
\sdim H^0\Prim_{\mathrm{prot}}(\mathcal F_X)_{(n,l,m)}=f(nm,l)
\quad\Longrightarrow\quad
H^0\Prim_{\mathrm{prot}}(\mathcal F_X)\cong\autcor .
\]
It is false.  The determinant and the signed superdimension equality are
Grothendieck shadows.  They do not contain compact Hall products,
primitive projections, bracket constants, parity dimensions, simple-root
representatives, or a Hopf-pairing radical quotient.

\subsection{Repair inserted in the manuscript}

The primitive comparison is now a recognition theorem.  Let
\(\mathscr B_{\Delta_5}\) be the Gritsenko--Nikulin Borcherds--Cartan
superdatum: Cartan \(\La^{2,1}_{II}\otimes\C\), real simple roots
\(\delta_1,\delta_2,\delta_3\), imaginary simple-root fibres with the
Gritsenko--Nikulin parity split, and bilinear form
\((\alpha_i,\alpha_j)\).  The corresponding Borcherds--Kac Lie
superalgebra modulo the standard radical is
\[
G(\mathscr B_{\Delta_5})=\mathcal A_{\mathrm{den}}=\autcor .
\]

A compact primitive object
\[
P_X=H^0\Prim_{\mathrm{prot}}(\mathcal F_X)
\]
is recognized as \(\autcor\) only after the following data have been
supplied.
\begin{enumerate}
\item A charge-graded Lie superalgebra structure on \(P_X\), with finite
homogeneous parity pieces and Cartan
\[
P_{X,0}\simeq\La^{2,1}_{II}\otimes\C .
\]
\item The charge-to-root map
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}
\]
identifying the protected charge grading with the
Gritsenko--Nikulin root grading.
\item Primitive representatives \(e_i^X,f_i^X,h_i^X\) for every real and
imaginary simple-root index of \(\mathscr B_{\Delta_5}\), preserving
multiplicity fibres and parity.
\item Verification in the protected Hall/factorization bracket of the
Borcherds--Kac defining relations: Cartan, Chevalley, real Serre,
imaginary-root orthogonality, and super signs.
\item A completed Hopf pairing whose radical quotient is the same as the
Gritsenko--Nikulin/Kac quotient.
\item Generation by the Cartan and simple primitive representatives.
\item Agreement of full root-space parity dimensions, not only signed
Euler characteristics.
\end{enumerate}
Under these hypotheses the universal presentation gives a surjection
\[
G(\mathscr B_{\Delta_5})\longrightarrow P_X .
\]
Generation gives surjectivity, and the radical quotient plus full parity
dimensions gives injectivity.  Hence
\[
P_X\cong\autcor
\]
as a charge-graded Lie superalgebra.  This is a presentation-level
recognition theorem.  It is not a determinant theorem.

\subsection{What is not proved}

The manuscript still does not construct:
\begin{enumerate}
\item the compact Hall/factorization object;
\item the compact Hall bracket constants;
\item the full compact primitive parity dimensions;
\item primitive representatives of all real and imaginary simple roots;
\item the Borcherds--Kac defining relations inside the compact bracket;
\item the completed Hopf pairing and its radical quotient;
\item the chiral Koszul quasi-isomorphism from the compact bar--cobar
object to \(\mathsf{Den}_{\Delta_5,E}\).
\end{enumerate}
The signed equality
\[
\sdim P_{X,(n,l,m)}=f(nm,l)
\]
is necessary for recognition.  It is insufficient.

\subsection{Determinant-forgets attack}

Let
\[
B=\bigoplus_{\gamma\in\Gamma_{\mathrm{eff}}}B_\gamma,\qquad
\sdim B_{(n,l,m)}=f(nm,l).
\]
Then
\[
64q^{1/2}r^{1/2}s^{1/2}
\prod_{\gamma\in\Gamma_{\mathrm{eff}}}(1-x^\gamma)^{\sdim B_\gamma}
=\Delta_5(Z).
\]
Putting the zero bracket on \(B\) gives the same determinant but not
\(\autcor\), since \([e_i,e_j]\ne0\) in the denominator algebra for
\(i\ne j\).

Even after fixing \(\autcor\), adding a root-graded pair
\[
M\oplus \Pi M
\]
of opposite parity has zero signed character.  A semidirect extension by
such a pair can preserve the signed determinant while changing the
algebra.  The recognition theorem excludes this only by requiring full
parity dimensions and the completed radical quotient.

\subsection{Claim status}

The repaired manuscript may assert:
\[
\hbox{recognition hypotheses}
\quad\Longrightarrow\quad
H^0\Prim_{\mathrm{prot}}(\mathcal F_X)\cong\autcor .
\]
It may not assert:
\[
\mathcal D_X=\Delta_5
\quad\Longrightarrow\quad
H^0\Prim_{\mathrm{prot}}(\mathcal F_X)\cong\autcor .
\]

\subsection{Files changed, checks, remaining obligations}

Files changed by this agent:
\[
\texttt{main.tex},\qquad
\texttt{agent\_material/13\_primitive\_recognition\_attack\_repair.tex},\qquad
\texttt{out/main.pdf}\ \hbox{(rebuilt)}.
\]

Checks run:
\[
\begin{array}{l}
\texttt{sed -n '1,240p' CLAUDE.md},\\
\texttt{sed -n '1,260p' AGENTS.md},\\
\texttt{sed -n '1,220p' /Users/raeez/ecosystem/INVARIANTS.md},\\
\texttt{sed -n '1,220p' /Users/raeez/ecosystem/AGENTS-HARNESS.md},\\
\texttt{nl -ba main.tex | sed -n '1724,1905p'},\\
\texttt{nl -ba main.tex | sed -n '2148,2448p'},\\
\texttt{nl -ba main.tex | sed -n '2628,2736p'},\\
\texttt{sed -n '1,520p' agent\_material/12\_primitive\_comparison\_attack\_heal.tex},\\
\texttt{sed -n '1,260p' agent\_material/04\_bkm\_state\_algebra.tex},\\
\texttt{rg -n -F -e "Pi\_\{\textbackslash\textbackslashmathrm\{prim\}" -e "primitive Lie comparison" main.tex},\\
\texttt{rg -n -F -e "thm:primitive-recognition" -e "What is not proved" main.tex agent\_material/13\_primitive\_recognition\_attack\_repair.tex},\\
\texttt{git diff --check -- main.tex agent\_material/13\_primitive\_recognition\_attack\_repair.tex},\\
\texttt{git status --short -- main.tex agent\_material/13\_primitive\_recognition\_attack\_repair.tex out/main.pdf},\\
\texttt{make},\\
\texttt{make -B}.
\end{array}
\]

Remaining obligations:
\begin{enumerate}
\item Construct the compact Hall/factorization object.
\item Compute the protected primitive bracket constants.
\item Prove full compact parity dimensions.
\item Produce simple primitive representatives for all real and imaginary
simple roots.
\item Verify the Borcherds--Kac relations in the compact bracket.
\item Construct the completed Hopf pairing and identify its radical
quotient with the Gritsenko--Nikulin/Kac quotient.
\item Prove the chiral Koszul comparison.
\end{enumerate}
