\section{Synthesis coherence attack-repair}
\label{sec:synthesis-coherence-attack-repair}

\subsection{Scope}

Writable scope was the section
\[
\texttt{main.tex}
\quad
\hbox{from }
\texttt{\string\section\{Coefficient dictionary and main synthesis\}}
\hbox{ to before }
\texttt{\string\part\{Diagonal-divisor rows and CHL boundary physics\}},
\]
and this report.

The source packet read before inscription was:
\[
\texttt{CLAUDE.md},\quad
\texttt{AGENTS.md},\quad
\texttt{\string~/ecosystem/INVARIANTS.md},\quad
\texttt{main.tex},\quad
\texttt{agent\_material/12\_synthesis\_architecture\_attack\_heal.tex},
\]
together with all local \(\texttt{agent\_material/12\_*}\) reports.

\subsection{Claim attacked}

The attacked failure mode was synthesis drift: the coefficient
dictionary could read as a repair ledger instead of as the forced spine
of the paper.  The repaired spine is now stated in mathematical prose:
\[
\hbox{virtual determinant}
\longrightarrow
\hbox{denominator algebra}
\longrightarrow
\hbox{reduced scalar square}
\longrightarrow
\hbox{compact realization problem}
\longrightarrow
\hbox{eight-row certificate extension}.
\]
The arrows are explicitly declared to be comparison order, not automatic
implications from product formulae to physical hosts.

\subsection{Main repair}

The synthesis theorem was rewritten as a status-exact ledger:
\begin{enumerate}
\item the \(K_0\)-virtual determinant is proved:
\[
\mathcal D_X=\Delta_5;
\]
\item the Gritsenko--Nikulin denominator theorem is imported:
\[
\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z);
\]
\item the Oberdieck--Pixton/Oberdieck/Oberdieck--Pandharipande scalar
branch is imported:
\[
Z^X_{\mathrm{DT}}=Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2};
\]
\item the compact \(E_3\)/Hall/chiral comparison is kept open unless
Definition~\ref{def:compact-igusa-realization-datum} is constructed;
\item the eight-row extension is stated as a row-certificate problem.
\end{enumerate}

\subsection{Constants}

The constants are placed at theorem level.
\[
[q^{1/2}r^{1/2}s^{1/2}]\Delta_5=64,\qquad
D_5=64^{-1}\Delta_5.
\]
The scalar normalization is recorded as
\[
\chi_{10}^{\mathrm{OP}}=D_5^2
=(64^{-1}\Delta_5)^2
=4096^{-1}\Delta_5^2,
\qquad
Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1}.
\]
Thus
\[
Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2}.
\]
The report and the manuscript both state that \(64\), \(4096\), and the
OP minus sign are not compact Hall orientation data.

\subsection{Three consequences inserted}

The Ran(\(E\)) obstruction is now a consequence of any claimed compact
realization: positive elliptic degree projects onto all of \(E\), so a
naive support-local Ran(\(E\)) object sees only projection-finite
sectors unless a global Fock/Hecke mode or hybrid wrapped factorization
theory is supplied.

The orientation monodromy problem is now a consequence of the scalar
square forgetting \(\nu_{\Delta_5}\): a compact realization must
construct a strong orientation character \(\epsilon_o\) and prove
\[
\epsilon_o|_{W^{(2)}(\Lambda^{2,1}_{II})}
=\nu_{\Delta_5}|_{W^{(2)}(\Lambda^{2,1}_{II})}.
\]

The primitive recognition theorem is now stated as presentation-level:
signed dimensions are insufficient; one needs simple primitive
representatives, parities, defining Borcherds--Kac relations,
generation, completed Hopf pairing, and the same radical quotient.

\subsection{Files changed}

\[
\texttt{main.tex},\qquad
\texttt{agent\_material/13\_synthesis\_coherence\_attack\_repair.tex}.
\]

\subsection{Checks run}

Before this report was written:
\begin{enumerate}
\item \(\texttt{git status --short --branch}\) verified the active
branch and clean starting state.
\item \(\texttt{sed -n}\) reads loaded the required control files,
the synthesis section, adjacent manuscript sections, and all
\(\texttt{agent\_material/12\_*}\) reports.
\item \(\texttt{rg}\) scanned \(\texttt{main.tex}\) for
\(\texttt{Coefficient dictionary}\), \(\texttt{64}\),
\(\texttt{-4096}\), \(\texttt{Ran(E)}\), orientation, primitive
recognition, and row-certificate anchors.
\item Post-edit \(\texttt{sed -n '2568,2825p' main.tex}\) reread the
owned section.
\end{enumerate}

After the edit:
\begin{enumerate}
\item \(\texttt{git diff --check -- main.tex agent\_material/13\_synthesis\_coherence\_attack\_repair.tex}\)
reported no whitespace errors.
\item \(\texttt{rg}\) verified the synthesis anchors for
\(-4096=-(64)^2\), Ran(\(E\)), orientation monodromy, primitive
recognition, and row certificates.
\item A full \(\texttt{make}\) build was not run.  The shared checkout
already contained concurrent modifications outside this agent's scope,
including \(\texttt{appendices/boundary\_compatibility\_conditions.tex}\),
\(\texttt{out/main.pdf}\), and other Agent 13 reports.  Building would
mutate the shared generated PDF and auxiliary files.
\end{enumerate}

\subsection{Residual issues}

No contradiction with the Agent 12 reports was found in the owned
section.  Residual mathematical issues are the paper's stated open
obligations: compact \(E_3\)/Hall/chiral realization, Ran(\(E\))
global-wrapping or projection-finite repair, strong orientation
monodromy, primitive presentation recognition, and row-by-row physical
host certificates.
