\subsection{\texorpdfstring{Boundary rows and physical hosts from the
surrounding volumes: attack--heal audit}{Boundary rows and physical
hosts from the surrounding volumes: attack-heal audit}}

\subsubsection*{Claim attacked}

The attacked claim is that the surrounding research volumes already
contain physical-host or row-map technology for the eight
Clery--Gritsenko diagonal-divisor rows, especially for rows \(F_2\)--
\(F_8\).  In its strongest false form the claim is
\[
\mathrm{Vol.\ III\ } \kappa\hbox{-}\mathrm{technology}
\quad+\quad
\mathrm{CHL/DT/chiral\ language}
\quad\Longrightarrow\quad
\mathrm{physical\ host\ for\ every\ }F_j .
\]
This implication fails.  The surrounding volumes contain useful
automorphic constants, conditional Hall/chiral architecture for the
\(\Delta_5\) row, and conjectural routes, but they do not construct
compact CY/CHL/DT/chiral row-map certificates for \(F_2,\ldots,F_8\).

\subsubsection*{Audit standard}

A physical-host assertion for a row \(F_j\) is accepted here only if it
supplies the five independent certificates
\[
(\mathscr A_j,\mathscr D_j,\mathscr S_j,\mathscr Z_j,\mathscr H_j).
\]
Here \(\mathscr A_j\) is the automorphic product, group or cover,
character, diagonal divisor, chamber, Jacobi input at every cusp, and
product-degree map.  The certificate \(\mathscr D_j\) is the
Weyl--Kac--Borcherds denominator algebra: root lattice, Weyl vector,
simple real roots, Weyl group, reflection character, imaginary
coefficients, product side, and Weyl alternating side.  The certificate
\(\mathscr S_j\) is a CHL/dyon scalar-square certificate mapping to the
same row and cover.  The certificate \(\mathscr Z_j\) is a compact or
orbifold reduced CY/DT scalar-host theorem
\[
  Z^{\mathrm{red}}_j=C_jF_j^{-2}
\]
with variables and chamber fixed.  The certificate
\(\mathscr H_j\) is a compact Hall/chiral primitive-bracket theorem
whose one-particle index, orientation character, and primitive
relations match \(\mathscr D_j\).

Equivalently, a row-map theorem must name at least
\[
(X_j,\widetilde\Gamma_j,\Gamma^{\mathrm{BPS}}_j,\Gamma^{\mathrm{eff}}_j,
\alpha^{\mathrm{phys}}_j,J_j,o_j,Z_j,\mathcal H_j)
\]
where \(X_j\) is the host, \(\widetilde\Gamma_j\) is the exact modular
group or multiplier cover, \(\Gamma^{\mathrm{BPS}}_j\) and
\(\Gamma^{\mathrm{eff}}_j\) are the charge lattice and chamber,
\(\alpha^{\mathrm{phys}}_j\) is the Lorentzian degree map to the same
product lattice used by the row, \(J_j\) is the one-particle Jacobi
index, \(o_j\) is the orientation character, \(Z_j\) is the scalar
partition function if one is claimed, and \(\mathcal H_j\) is the
primitive Hall/chiral object.  Matching a weight, a square, or a
formal Borcherds product is not enough.

\subsubsection*{What the surrounding volumes actually supply}

The current Igusa manuscript supplies the full eight-row automorphic
ledger.  It proves the \(F_1\) virtual determinant and scalar
OP/DT identity, records the Gritsenko--Nikulin denominator rows
\(F_1\)--\(F_4\), and records the Govindarajan/CHL WKB denominator rows
\(F_5\)--\(F_8\).  It does not claim compact Hall/chiral hosts for any
row, and it treats \(F_2,\ldots,F_8\) as open physical-host rows.

The Vol.~III files in
\(\texttt{/Users/raeez/calabi-yau-quantum-groups}\) supply a
cover-sensitive automorphic weight and constant technology for the
Gritsenko--Clery census.  In the triple order
\[
(1,1),\ (2,1),\ (1,2),\ (3,1),\ (1,3),\ (4,1),\ (1,4),\ (2,2)
\]
the recorded weights are
\[
5,\ 2,\ 3,\ 1,\ 2,\ \tfrac12,\ \tfrac32,\ 1
\]
and the corresponding zero-coefficients are
\[
10,\ 4,\ 6,\ 2,\ 4,\ 1,\ 3,\ 2,
\qquad
\kappa_{\mathrm{BKM}}=\frac{c(0)}2.
\]
This is useful row-map-adjacent automorphic data.  It is not a compact
physical row map: no \(X_j\), reduced obstruction theory, protected
partition equality, or primitive Hall bracket is constructed for
\(F_2,\ldots,F_8\).  Vol.~III also contains a conjectural
twisted-twined K3-orbifold ladder and a conditional
Hall--Borcherds bridge for \(K3\times E\).  Those are programme routes,
not completed row certificates.

The Vol.~I and Vol.~II chiral bar--cobar files supply chiral/Hall/HT
language around the \(K3\times E\) and \(\Delta_5\) row: a
Hall--Drinfeld double target, a Borcherds output rather than input, and
conditional \(H_{\Delta_5}\) technology.  They do not supply row maps
for \(F_2,\ldots,F_8\).  Vol.~II also contains the older spread
\[
5,\ 2,\ 1,\ 1,\ \tfrac12,\ 1,\ \tfrac14,\ 0
\]
with zero-coefficients
\[
10,\ 4,\ 2,\ 2,\ 1,\ 2,\ \tfrac12,\ 0.
\]
That spread is not the Clery--Gritsenko eight-row catalogue in the
present Igusa ordering and must not be used as a physical atlas for
the rows below.

The topological-strings volume supplies BCOV/MNOP and \(K3\times E\)
framing, including compatibility with the \(K3\times E\) scalar
Igusa-square story.  Targeted searches for
\(\nabla_3,\nabla_2,\nabla_{3/2},Q_1\), Clery--Gritsenko row maps, or
the eight-row host package give no row certificate there.

\subsubsection*{Exact row-map certificate data}

The present Igusa ordering is
\[
\begin{array}{c|c|c|c|c|c}
j&F_j&(t,N)&\mathrm{weight}&c(0)&\mathrm{cover/character}\\ \hline
1&\Delta_5&(1,1)&5&10&v_\eta^{12}\times v_H\\
2&\Delta_2&(2,1)&2&4&v_\eta^{6}\times v_H\;(\chi_4)\\
3&\Delta_1&(3,1)&1&2&v_\eta^{4}\times v_H\;(\chi_6)\\
4&\Delta_{1/2}&(4,1)&\tfrac12&1&
v_\eta^{3}\times v_H\;(v_8)\\
5&\nabla_3&(1,2)&3&6&\chi_2^{(2)}\times v_H\\
6&\nabla_2&(1,3)&2&4&\chi_2^{(3)}\times v_H\\
7&\nabla_{3/2}&(1,4)&\tfrac32&3&
\chi_4^{(4)}\times v_H\ \hbox{on the }\mu_4\hbox{-cover}\\
8&Q_1&(2,2)&1&2&\chi_4^{(2)}\times v_H .
\end{array}
\]
The permutation from Vol.~III triple order to this \(F\)-order is
\[
(1,2,5,3,6,4,7,8).
\]

For \(F_1\), the product-degree map is the \(N=1\) Igusa map
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2},
\qquad
q^nr^ls^m=\exp(-\pi i(\alpha(n,l,m),z)).
\]
The denominator normalization is
\[
\operatorname{den}(\mathfrak g_{\Delta_5})
=64^{-1}\Delta_5(2Z),
\]
whereas the scalar OP/DT normalization is
\[
Z^{\mathrm{OP}}_{K3\times E}=-4096\,\Delta_5^{-2}.
\]
The constants \(64\) and \(4096=64^2\) are leading-coefficient and
square normalizations, not an orientation theorem.

For \(F_2,F_3,F_4\), Gritsenko--Nikulin use
\[
M_t=U(4t)\oplus\langle 2\rangle,\qquad
\alpha_t(n,l,m)=nf_2+l\widehat f_3+mf_{-2},
\qquad
e_t^{(n,l,m)}=q^nr^ls^{tm},
\]
with
\[
\rho_t=\left(\frac1{2t},\frac12,\frac1{2t}\right),
\qquad (j,t)=(2,2),(3,3),(4,4).
\]
The denominator identities are exactly
\[
\operatorname{den}(\mathfrak g^{\mathrm{GN}}_2)=\Delta_2,\qquad
\operatorname{den}(\mathfrak g^{\mathrm{GN}}_3)=\Delta_1,\qquad
\operatorname{den}(\mathfrak g^{\mathrm{GN}}_4)=\Delta_{1/2}
\]
in the \(e_t\)-normalization; hence \(C'_j=1\) and \(a_j=1\) for
\(j=2,3,4\) in that normalization.  The simple real roots are
\[
P_2=\{(0,-1,0),(1,1,0),(1,3,1),(0,1,1)\},
\]
\[
P_3=\{(0,-1,0),(1,1,0),(2,5,1),
(2,7,2),(1,5,2),(0,1,1)\},
\]
and
\[
P_4=\{\delta\in M_4\mid(\delta,\delta)=2,\;(\delta,\rho_4)=-1\}.
\]
Every simple real root is even and the reflection character is
\(\det\).

For \(F_5,F_6,F_7,F_8\), the Clery--Gritsenko product-degree lattices
are \(L_j^{\mathrm{prod}}=M_{t_j}\) with
\[
(t_5,N_5)=(1,2),\quad (t_6,N_6)=(1,3),\quad
(t_7,N_7)=(1,4),\quad (t_8,N_8)=(2,2).
\]
The cusp-labelled maps are
\[
\alpha_5(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_5(n,l,m;S)=\alpha_1(2n,2l,2m),
\]
\[
\alpha_6(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_6(n,l,m;S)=\alpha_1(3n,3l,3m),
\]
\[
\alpha_7(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_7(n,l,m;M)=\alpha_1(2n,2l,2m),\qquad
\alpha_7(n,l,m;S)=\alpha_1(4n,4l,4m),
\]
and
\[
\alpha_8(n,l,m;\infty)=\alpha_2(n,l,m),\qquad
\alpha_8(n,l,m;S)=\alpha_2(2n,2l,2m).
\]
The prefactors are
\[
\rho_5=\rho_6=\rho_7=\alpha_1(\tfrac12,\tfrac12,\tfrac12),
\qquad
\rho_8=\alpha_2(\tfrac14,\tfrac12,\tfrac14).
\]
The multiplicity function is the sum of labelled cusp coefficients at
the same product degree:
\[
\mu_j(\lambda)=
\sum_{\alpha_j(n,l,m;\kappa)=\lambda}
\widetilde c_{j,\kappa}(nm,l),
\]
with
\[
\widetilde c_{7,M}=\tfrac12 c_{7,M}.
\]
This half-exponent is a sourced \(\mu_4\)-cover datum for
\(\nabla_{3/2}\), not a scalar-character exponent on the original
congruence group.

Govindarajan's denominator rows give
\[
F_5\leftrightarrow \mathcal G_1(2),\qquad
F_6\leftrightarrow \mathcal G_1(3),\qquad
F_7\leftrightarrow \mathcal G_1(4),\qquad
F_8\leftrightarrow \mathcal G_2(4).
\]
For \(F_5,F_6,F_7\) the root lattice is \(M_1\), the Weyl vector is
\(\alpha_1(1/2,1/2,1/2)\), and
\[
P^{(1)}=\{(0,-1,0),(1,1,0),(0,1,1)\}.
\]
For \(F_8\) the root lattice is \(M_2\), the Weyl vector is
\(\alpha_2(1/4,1/2,1/4)\), and
\[
P^{(2)}=\{(0,-1,0),(1,1,0),(1,3,1),(0,1,1)\}.
\]
In all four rows the reflection character is \(\det\).  This is
\(\mathscr D_j\) data, not \(\mathscr Z_j\) or \(\mathscr H_j\) data.

\subsubsection*{Row-by-row status}

\begin{center}
\small
\begin{tabular}{c|p{0.26\linewidth}|p{0.27\linewidth}|p{0.29\linewidth}}
\(j\)&automorphic/denominator status&
constructed cross-volume host&
programme route\\ \hline
1&
\(\Delta_5\) product and
\(\mathfrak g_{\Delta_5}\) denominator proved; OP/DT scalar
\(-4096\Delta_5^{-2}\) proved.&
\(K3\times E\) gives the scalar host.  Vol.~I/II/III give conditional
Hall/chiral architecture for the same row, but the compact primitive
Hall/chiral theorem is still open.&
Complete the oriented compact Hall/factorization object, prove the
one-particle index \(f(nm,l)\), the orientation character
\(\nu_{\Delta_5}\), and the primitive bracket/PBW comparison.\\ \hline
2&
\(\Delta_2\) automorphic product and
\(\mathfrak g^{\mathrm{GN}}_2\) denominator proved on \(M_2\);
weight \(2\), character \(\chi_4\).&
No audited CY/CHL/DT/chiral host in the surrounding volumes.  Vol.~III
records the weight and \(c(0)=4\), not a host.&
Find a physical source whose charge lattice maps to \(M_2\), whose
Jacobi seed is \(\phi_{0,2}\), whose orientation realizes \(\chi_4\),
and whose scalar theorem is \(C\Delta_2^{-2}\) if scalar physics is
claimed.\\ \hline
3&
\(\Delta_1\) product and \(\mathfrak g^{\mathrm{GN}}_3\) denominator
proved on \(M_3\); weight \(1\), character \(\chi_6\).&
No audited host.  Same-weight collisions in other volumes do not give
a row map to \(M_3\) or to \(\phi_{0,3}\).&
Construct the \(M_3\)-valued BPS charge map, one-particle index
\(\phi_{0,3}\), \(\chi_6\)-orientation, scalar theorem if any, and
primitive comparison with \(\mathfrak g^{\mathrm{GN}}_3\).\\ \hline
4&
\(\Delta_{1/2}\) product and \(\mathfrak g^{\mathrm{GN}}_4\)
denominator proved on the degree-\(8\) multiplier cover; weight
\(\tfrac12\).&
No audited host.  The surrounding \(N=5,7,8\) or quarter-weight
language is a different boundary shorthand, not this row.&
Any host must live on the \(v_8\) cover, realize \(M_4\), match
\(\phi_{0,4}\), and prove the parabolic \(P_4\) denominator chamber.\\
\hline
5&
\(\nabla_3\) product proved; Govindarajan denominator
\(\mathcal G_1(2)\); scalar square \(\nabla_3^2=\Phi_6\) is sourced.&
No compact reduced CY/DT or Hall/chiral host.  CHL dyon data supply a
scalar square and WKB denominator, not a compact row map to the
Clery--Gritsenko cusp-labelled product.&
Use the \(\mathcal G_1(2)\) denominator as target; construct a compact
host whose charge map equals the two-cusp maps
\(\alpha_1(n,l,m)\), \(\alpha_1(2n,2l,2m)\) and whose scalar theorem is
\(C\nabla_3^{-2}\) if claimed.\\ \hline
6&
\(\nabla_2\) product proved; Govindarajan denominator
\(\mathcal G_1(3)\); scalar square \(\nabla_2^2=\Phi_4\) is sourced.&
No compact host in Vol.~I/II/III or topological strings.  Weight \(2\)
does not identify it with \(\Delta_2\).&
Construct the threefold/CHL/DT object, map charges to
\(\alpha_1(n,l,m)\) and \(\alpha_1(3n,3l,3m)\), and prove primitive
comparison with \(\mathcal G_1(3)\).\\ \hline
7&
\(\nabla_{3/2}\) product proved only in the sourced
\(\mu_4\)-cover normalization; Govindarajan denominator
\(\mathcal G_1(4)\); scalar square gives the CHL \(\Phi_3\) row.&
No compact host.  The \(\mu_4\) cover is not a quarter-weight row and
does not supply a CY/DT or Hall orientation theorem.&
Any programme must keep the middle cusp exponent
\(c_{7,M}/2\), the three labelled cusp maps, and the \(\mu_4\) cover
visible, then prove a compact orientation and primitive bracket.\\
\hline
8&
\(Q_1\) product proved; Govindarajan denominator
\(\mathcal G_2(4)\); scalar square \(Q_1^2=\Phi_2^{(2,4)}\) is
sourced.&
No compact host.  It is a \((2,2)\) row on \(M_2\), not an \(N=1\)
boundary, not a weight-zero endpoint, and not \(\Delta_1\).&
Construct a host with \(M_2\) charge lattice, four real roots
\(P^{(2)}\), degree map \(q^nr^ls^{2m}\), and scalar theorem
\(CQ_1^{-2}\) if physics is claimed.
\end{tabular}
\end{center}

\subsubsection*{Falsified identifications}

\begin{enumerate}
\item The tuple
\[
5,\ 2,\ 1,\ 1,\ \tfrac12,\ 1,\ \tfrac14,\ 0
\]
is not the present Clery--Gritsenko eight-row catalogue.  The catalogue
has weights
\[
5,\ 2,\ 1,\ \tfrac12,\ 3,\ 2,\ \tfrac32,\ 1
\]
in \(F\)-order, or
\[
5,\ 2,\ 3,\ 1,\ 2,\ \tfrac12,\ \tfrac32,\ 1
\]
in triple order.  There is no Clery--Gritsenko row of weight
\(\tfrac14\) or \(0\).

\item The identifications
\[
\Delta_2=\nabla_2,\qquad
\Delta_1=Q_1,\qquad
\Delta_{1/2}=\nabla_{3/2}^{\,1/3}
\]
are false.  They fail by group, multiplier, Jacobi seed, product
lattice, and product-degree map.  Equal or related weights do not give
row maps.

\item The CHL/Jatkar--Sen tower with weights
\[
10,\ 6,\ 4,\ 2,\ 1,\ 0
\]
or its square-root language is not the Clery--Gritsenko eight-row
catalogue.  At \(N=1\), \(\Phi_{10}=\Delta_5^2\).  Away from that
entry the towers have different selection rules and normalizations.

\item The Vol.~III order-indexed \(N=5,7,8\) boundary discussion is not
the \(F_5,F_7,F_8\) row system.  In the order-indexed lane the constants
are
\[
(c_N(0),\kappa_{\mathrm{BKM}})=(4,2),(2,1),(2,1),
\]
whereas the present Clery--Gritsenko \(F\)-rows \(F_5,F_7,F_8\) have
\[
(c(0),\kappa_{\mathrm{BKM}})=(6,3),(3,\tfrac32),(2,1).
\]
The surrounding notes correctly mark the \(N=5,7,8\) compact CY
hosts as open or conjectural.

\item The scalar-square statements
\[
\nabla_3^2=\Phi_6,\qquad
\nabla_2^2=\Phi_4,\qquad
\nabla_{3/2}^2=\Phi_3,\qquad
Q_1^2=\Phi_2^{(2,4)}
\]
do not imply reduced CY/DT scalar-host theorems and do not imply
primitive Hall/chiral denominator algebras.  They are \(\mathscr S_j\)
or denominator-adjacent data only.

\item The \(F_7\) \(\mu_4\)-cover is not a quarter-weight
\(\widetilde{\mathrm{Mp}}_4\) certificate.  The \(F_8\) row is not a
weight-zero degenerate endpoint.  The \(F_4\) degree-\(8\) cover is not
provided by any \(K3\times E\) CHL quotient in the audited material.
\end{enumerate}

\subsubsection*{Recommended programme route}

For \(F_1\), keep the OP/DT scalar theorem and the
Gritsenko--Nikulin denominator theorem separate.  The remaining
programme is the compact Hall/chiral theorem: construct the oriented
compact object before elliptic reduction, repair the \(E\)-direction
locality obstruction by a global Fock or hybrid wrapped
factorization model, prove the orientation character
\(\nu_{\Delta_5}\), and prove the primitive bracket/PBW comparison
with \(\mathfrak g_{\Delta_5}\).

For \(F_2,F_3,F_4\), begin from the Gritsenko--Nikulin denominators,
not from CHL square roots.  A theorem must produce a host, an exact
cover \(\chi_4,\chi_6,v_8\), a BPS charge lattice mapping to \(M_t\),
the one-particle indices \(\phi_{0,2},\phi_{0,3},\phi_{0,4}\), and a
reduced scalar identity only if that scalar physics is actually proved.

For \(F_5,F_6,F_7,F_8\), begin from the Govindarajan denominator rows
\(\mathcal G_1(2),\mathcal G_1(3),\mathcal G_1(4),\mathcal G_2(4)\)
and from the exact Clery--Gritsenko cusp-labelled product maps.  The
first missing theorem is a compact row map from physical charges to
those labelled maps.  The second missing theorem is a reduced scalar
identity \(C_jF_j^{-2}\).  The third is a compact Hall/chiral primitive
comparison with the WKB denominator algebra.  For \(F_7\) the \(\mu_4\)
cover and the half middle-cusp exponent must remain part of the
statement.

Cross-volume material should be propagated only with its proved
strength.  Vol.~III \(\kappa_{\mathrm{BKM}}=c(0)/2\) is an
automorphic weight certificate.  Vol.~I/II chiral technology is
conditional \(F_1\) architecture unless a row-specific certificate is
supplied.  The topological-strings volume is scalar/BCOV context, not
an eight-row host atlas.  Therefore the current correct status is:
\[
\begin{array}{c|c|c|c}
\mathrm{rows}&\mathscr A&\mathscr D&
\mathscr Z,\mathscr H\ \mathrm{from\ surrounding\ volumes}\\ \hline
F_1&\mathrm{proved}&\mathrm{proved}&
\mathscr Z\ \mathrm{proved\ only\ as\ scalar;\ }\mathscr H\ \mathrm{open}\\
F_2,F_3,F_4&\mathrm{proved}&\mathrm{proved}&\mathrm{open}\\
F_5,F_6,F_7,F_8&\mathrm{proved}&\mathrm{proved}&\mathrm{open}.
\end{array}
\]
