\section{Agent 14-E: chiral bar--cobar/Koszul realization attack--heal}
\label{sec:agent14-chiral-bar-cobar-koszul-realization}

\providecommand{\C}{\mathbb C}
\providecommand{\Z}{\mathbb Z}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\Fact}{\mathsf{Fact}}
\providecommand{\Coalg}{\mathsf{Coalg}}
\providecommand{\ChAlg}{\mathsf{ChAlg}}
\providecommand{\Cur}{\operatorname{Cur}}
\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\sdim}{\operatorname{sdim}}
\providecommand{\Den}{\mathsf{Den}}
\providecommand{\Aut}{\operatorname{Aut}}
\providecommand{\Bch}{B^{\mathrm{ch}}}
\providecommand{\Och}{\Omega^{\mathrm{ch}}}
\providecommand{\Spch}{\mathrm{Sp}^{\mathrm{ch}}}
\providecommand{\Aden}{\mathcal A_{\mathrm{den}}}
\providecommand{\gDelta}{\mathfrak g_{\Delta_5}}
\providecommand{\DDelta}{\Den_{\Delta_5,E}}
\providecommand{\Hall}{\mathcal H}

\subsection{Question attacked}

The claim under attack is
\[
        \Och_E C_X \simeq \DDelta ,
\]
where \(X=K3\times E\), \(C_X\) is supposed to be the compact chiral
bar coalgebra produced by the \(K3\times E\) geometry, and
\(\DDelta\) is the denominator current algebra attached to the
Borcherds--Kac--Moody superalgebra whose denominator is the Igusa square
root \(\Delta_5\).

The attack conclusion is negative in its unconditional form.  The
available chiral bar--cobar theorem proves an inversion statement once a
valid chiral algebra or conilpotent chiral coalgebra on the curve has
already been constructed.  It does not construct the compact object
\(C_X\), it does not identify compact BPS primitives with
\(\gDelta\), and it does not turn the scalar Borcherds product into a
Hall factorization algebra.  The correct manuscript statement is a
conditional theorem, with explicit compact construction lemmas still
missing.

\subsection{The chiral bar--cobar theorem that exists}

The theorem available from the chiral bar--cobar papers is the following
curve-level statement.  Let \(E\) be a smooth complex curve.  In the
appropriate finite-type, completed, or coderived category of
\(\mathcal D\)-modules on \(\Ran(E)\) there is an adjunction
\[
        \Och_E :
        \Coalg^{\mathrm{conil}}_{\mathrm{ch}}(E)
        \rightleftarrows
        \ChAlg^{\mathrm{aug}}_{\mathrm{ch}}(E) :
        \Bch_E .
\]
For an augmented chiral algebra \(A\) there is a counit
\[
        \epsilon_A:\Och_E\Bch_E(A)\longrightarrow A ,
\]
and for a coaugmented conilpotent chiral coalgebra \(C\) there is a unit
\[
        \eta_C:C\longrightarrow \Bch_E\Och_E(C).
\]
On the strict Koszul locus, or after passing to the prescribed
conilpotent-complete/coderived setting, these maps are quasi-isomorphisms
in the relevant homotopy category.

This is an inversion theorem.  It is not the statement that the Koszul
dual algebra of \(A\) is \(\Och_E\Bch_E(A)\).  In the Vol. I language,
\(\Och_E\Bch_E(A)\to A\) reconstructs the original chiral algebra.  The
Koszul-dual or Verdier-dual object is obtained by the Ran Verdier-dual
bar construction, not by confusing the cobar inverse with a new compact
algebra.  Vol. II keeps this distinction explicit:
\[
        A,\qquad \Bch_E(A),\qquad
        A^!=\bigl(H^\ast\Bch_E(A)\bigr)^\vee,\qquad
        Z^{\mathrm{der}}_{\mathrm{ch}}(A)
\]
are different objects.  The equality
\(\Och_E\Bch_E(A)\simeq A\) is not a construction of \(A^!\) and is not
a compact \(K3\times E\) realization.

For the present paper this theorem can be used in exactly two ways.
First, if a compact coalgebra \(C_X\) is already constructed and lies in
the conilpotent-complete domain, then \(\Och_E C_X\) is a well-defined
chiral algebra.  Second, if \(\DDelta\) is put in the augmented completed
domain, then
\[
        \Och_E\Bch_E(\DDelta)\longrightarrow \DDelta
\]
is a target-internal bar--cobar resolution.  This second statement is
tautological for the target and does not exhibit any compact source.

\subsection{Inputs needed on a curve}

A genuine curve-level input for \(\Och_E C_X\) consists of the following
data.

\begin{enumerate}
\item A smooth curve \(E\) and a precise category, usually a category of
constructible or holonomic \(\mathcal D\)-modules on \(\Ran(E)\), with
the required completed or coderived enhancement.

\item A coaugmented chiral coalgebra \(C_X\) on \(\Ran(E)\), or an
augmented chiral algebra \(F_X\) together with a bar equivalence
\[
        C_X \simeq \Bch_E(F_X).
\]
The coalgebra structure must include the collision coproducts, signs,
differential, and factorization descent.

\item A square-zero total differential in the ordinary DG case.  In the
curved case one must instead work in the CDG/coderived category and
state the curvature and coacyclic equivalences.  Genus-one input is not
automatically ordinary-DG; the prime-form/curvature terms in the
bar--cobar formalism have to be killed by a total differential or kept
in the coderived category.

\item Conilpotence.  With \(\bar C_X=\ker(C_X\to{\bf 1})\), every local
section must be killed by a sufficiently high iterated reduced
coproduct.  Equivalently, the coaugmentation filtration must be
exhaustive at finite level, or pro-exhaustive after completion.

\item Finite-first control.  Each finite charge, conformal-weight, or
Harder--Narasimhan truncation must have finite-dimensional graded
pieces and a well-defined bar/cobar complex.  The completed object must
be an inverse limit of such finite stages with Mittag--Leffler control
on the transition maps and on the cones of the finite-stage
quasi-isomorphisms.

\item For a compact \(K3\times E\) source, a chain-level specialization
\[
        \Spch_{K3,E}: A_X^{E_3}\longmapsto F_X\in \Fact(\Ran(E))
\]
from the compact \(E_3\)-factorization algebra on \(X\) to a chiral
factorization algebra on \(E\).  This is extra geometry.  It is not a
formal consequence of the Borcherds product.

\item A Hall-theoretic or BPS construction of \(F_X\): stability
condition, extension stacks, orientations, vanishing cycles, protected
integration, and product compatibility.  The Oprea--Pandharipande scalar
spaces used in the manuscript are not by themselves an extension-stack
Hall object.
\end{enumerate}

The prior Agent 12 and 13 reports correctly isolate the main obstruction
for the compact \(K3\times E\) problem.  A sector of positive elliptic
degree does not stay in a small open interval of \(E\); its projection
wraps all of \(E\).  Therefore a local Ran algebra on \(E\) cannot be
obtained merely by cutting compact curve classes into small elliptic
arcs.  One needs either a global Fock/Hecke factorization object, a
hybrid local/global wrapped sector theory, or a different compact
specialization mechanism.

\subsection{How \(\DDelta\) fits}

The manuscript already contains a formal target object.  Let
\(\Aden=\gDelta\) be the Gritsenko--Nikulin denominator Lie superalgebra
attached to the automorphic correction whose denominator is
\[
        64^{-1}\Delta_5(2Z).
\]
On the elliptic curve \(E\) form the level-zero BD current algebra
\[
        \Cur_E(\Aden)=\Aden\otimes \mathcal O_E
\]
with the current bracket induced by the bracket of \(\Aden\).  Then
\[
        \DDelta
        :=
        U_E^{\mathrm{ch}}\bigl(\Cur_E(\Aden)\bigr)
\]
is the BD chiral enveloping algebra of the current algebra.

This construction is legitimate as a formal completed ind-object.  Its
constant-current primitives recover \(\Aden=\gDelta\), and its
denominator identity is the Borcherds denominator identity already
recorded in the manuscript.  Thus \(\DDelta\) is the right target for a
chiral realization of the Igusa denominator algebra.

It is not a compact source.  The current-envelope construction supplies
neither the compact \(E_3\)-factorization algebra \(A_X^{E_3}\), nor the
specialization to \(\Ran(E)\), nor the Hall extension product, nor the
compact coalgebra \(C_X\).  Applying bar--cobar to \(\DDelta\) gives
\(\Och_E\Bch_E(\DDelta)\to\DDelta\), which is the bar--cobar theorem
applied to the target itself.  It cannot be cited as the desired
compact \(K3\times E\) realization.

\subsection{Conilpotence and completion requirements}

The object \(C_X\) must be more than a symbolic coalgebra.  It must be a
coaugmented conilpotent chiral coalgebra or a completed pro-object built
from conilpotent finite stages.  A usable completion has the form
\[
        C_X=\varprojlim_R C_{X,\leq R},
\]
where \(R\) may be a charge bound, a Harder--Narasimhan bound, a
conformal-weight bound, or a combined sectorial bound.  Each
\(C_{X,\leq R}\) must be conilpotent, and all chiral coproducts must be
continuous for the inverse-limit topology.

The cobar algebra is then defined continuously:
\[
        \widehat{\Och}_E(C_X)
        :=
        \varprojlim_R \Och_E(C_{X,\leq R}),
\]
provided the finite-stage cobar complexes are compatible under the
transition maps.  The finite-stage quasi-isomorphisms must pass to the
limit.  A sufficient condition is the Mittag--Leffler condition for
cohomology and for the mapping cones of the comparison maps.  Without
this control an infinite product of acyclic finite-stage cones may
acquire derived inverse-limit cohomology.

Curvature is a separate issue.  If the chiral bar differential contains
a curvature term, then ordinary quasi-isomorphism is not the correct
notion.  One must work in the Positselski coderived category of CDG
coalgebras/algebras and prove coacyclicity of the cone.  Only when the
total differential is square-zero after adding all geometric
corrections may the comparison be read as an ordinary chain-level
quasi-isomorphism.

The same warning applies to \(\DDelta\).  It has infinitely many root
spaces, though finite multiplicity in each root predicted by the Jacobi
coefficients.  To compare it with a compact source one must choose a
charge completion on the current envelope compatible with the completion
used for \(C_X\).  Otherwise the expression
\(\Och_E C_X\simeq\DDelta\) has no fixed category in which it can be
true.

\subsection{Whether a compact \(C_X\) is constructed anywhere}

No compact \(C_X\) is constructed in the material read.

In the present Igusa manuscript, the compact realization datum is stated
as a target problem.  The manuscript defines the formal denominator
current envelope and then asks for a compact chiral Koszul realization.
It also records the elliptic-degree locality obstruction and the need
for a primitive-comparison theorem.  These are open obligations, not
completed constructions.

In \texttt{/Users/raeez/chiral-bar-cobar}, the general bar--cobar
adjunction and the chiral Positselski/Koszul inversion theorem are
developed.  These results say what happens after a curve-level algebra
or conilpotent coalgebra is supplied.  They do not supply the compact
\(K3\times E\) Hall object.

In \texttt{/Users/raeez/chiral-bar-cobar-vol2}, the two-stage
CY-to-chiral architecture is explained: first a compact or Calabi--Yau
factorization object, then a specialization to a curve.  The text
emphasizes that the chiral shadow is a CY-to-chiral construction and is
not the same thing as bar--cobar inversion.  No chain-level
\(K3\times E\) coalgebra \(C_X\) with
\(\Och_E C_X\simeq\DDelta\) is constructed there.

In \texttt{/Users/raeez/calabi-yau-quantum-groups}, the
\(K3\times E\) and \(\Delta_5\) bridge is part of the frontier
architecture.  It supplies the organizing frame and the expected
compatibility with the \(\kappa\)-stratification, but it also treats the
non-abelian compact-to-BKM comparison as a frontier target.  It is not a
proof of the compact realization required here.

\subsection{Exact conditional theorem}

\begin{theorem}[conditional compact chiral Koszul realization]
\label{thm:agent14-conditional-compact-chiral-koszul}
Let \(X=K3\times E\).  Assume the following compact Igusa realization
datum exists.
\begin{enumerate}
\item A finite-first compact \(E_3\)-factorization algebra
\(A_X^{E_3}\) of protected compact BPS states on \(X\), with a
square-zero differential or a specified CDG/coderived curvature theory.

\item A chain-level curve specialization
\[
        \Spch_{K3,E}(A_X^{E_3})=F_X\in\Fact(\Ran(E))
\]
with factorization descent, collision products, and compatibility with
the compact orientation data.

\item A Hall model for \(F_X\): an extension-closed compact heart or
stability theory, finite-type Harder--Narasimhan truncations, extension
stacks, vanishing-cycle sheaves, a strong orientation, and a protected
integration map compatible with Hall multiplication.

\item A coaugmented conilpotent completed chiral coalgebra \(C_X\) on
\(\Ran(E)\), with finite stages \(C_{X,\le R}\), continuous coproducts,
and a bar comparison
\[
        b_X:C_X\xrightarrow{\sim}\Bch_E(F_X)
\]
in the completed or coderived chiral coalgebra category.

\item A chiral twisting cochain or Koszul comparison map
\[
        \Theta_{\mathrm{Kos}}:\Och_E C_X\longrightarrow \DDelta
\]
which is a quasi-isomorphism in the same completed or coderived chiral
algebra category.

\item A primitive-recognition certificate identifying the protected
primitive Lie superalgebra of \(F_X\) with \(\gDelta\), including the
real simple roots, imaginary simple roots with multiplicities and
parities prescribed by the coefficients of \(\phi_{0,1}\), the
Borcherds--Kac relations, generation, and quotient by the radical of
the Hopf pairing.

\item A compatible charge completion on \(\DDelta\) and on
\(\Och_E C_X\), so that \(\Theta_{\mathrm{Kos}}\) is a morphism in a
single fixed category.
\end{enumerate}
Then
\[
        \Och_E C_X\simeq \DDelta
\]
in the completed/coderived category of chiral algebras on \(E\).  The
constant-current primitive Lie superalgebra is \(\gDelta\), and its
denominator is \(64^{-1}\Delta_5(2Z)\).
\end{theorem}

\begin{proof}
By hypothesis \(C_X\) is an object of the domain of the chiral cobar
functor, so \(\Och_E C_X\) is defined in the chosen completed or
coderived category.  The map \(\Theta_{\mathrm{Kos}}\) is, by
hypothesis, a quasi-isomorphism from this cobar algebra to the BD
current envelope \(\DDelta\).  The formal target calculation identifies
\(\DDelta\) with
\[
        U_E^{\mathrm{ch}}\bigl(\Cur_E(\gDelta)\bigr).
\]
The primitive-recognition certificate identifies the compact primitive
Lie superalgebra with \(\gDelta\).  The Borcherds--Gritsenko--Nikulin
denominator identity for \(\gDelta\) gives the denominator
\(64^{-1}\Delta_5(2Z)\).  No additional inference from the scalar
determinant is used.
\end{proof}

The theorem is intentionally conditional.  Hypothesis (5) is not a
cosmetic assumption: it is the missing Koszul comparison.  Without it,
the bar--cobar adjunction gives only
\[
        \Och_E\Bch_E(F_X)\simeq F_X
\]
once \(F_X\) has already been built and lies in the Koszul domain.  It
does not identify \(F_X\), or \(\Och_E C_X\), with the Igusa current
envelope.

\subsection{Missing construction lemmas}

The compact realization requires the following construction lemmas.
They are not present in the material read.

\begin{enumerate}
\item \textbf{Compact curve-specialization lemma.}
Construct the functor
\(\Spch_{K3,E}:A_X^{E_3}\to\Fact(\Ran(E))\) at chain level, with
factorization descent, collision maps, anomaly cancellation, and
finite-first completion.

\item \textbf{Wrapped elliptic-sector lemma.}
Repair the positive elliptic-degree obstruction.  Either build a global
Fock/Hecke factorization object over \(E\), or build a hybrid
local/global wrapped sector whose convolution remains associative over
flags of collisions.

\item \textbf{Compact Hall heart and HN lemma.}
Produce an extension-closed compact heart or stability condition on the
relevant compact category, prove the support property, and construct
finite-type semistable/HN stacks with a charge map compatible with the
\(\Lambda^{3,2}\) root variables.

\item \textbf{Critical atlas and orientation lemma.}
Construct derived critical charts, vanishing-cycle sheaves, and a
strong orientation for the compact extension stacks.  The orientation
character must match the denominator parity character used for
\(\Delta_5\).

\item \textbf{Protected integration lemma.}
Build a Hall character from compact vanishing-cycle cohomology to the
completed chiral algebra on \(E\), compatible with Hall convolution and
with any reduced \(E\)-translation quotient.  Scalar generating
functions alone do not give this map.

\item \textbf{Relative-position descent lemma.}
If one quotients by translation along \(E\), retain enough relative
position data to define chiral collision products.  A fully reduced
scalar theory has forgotten the geometry needed by a BD current
envelope.

\item \textbf{Chiral bar coalgebra lemma.}
Construct \(C_X\), prove coaugmentation, conilpotence of finite stages,
continuity of coproducts, and the comparison
\[
        C_X\simeq \Bch_E(F_X)
\]
in the completed or coderived category.

\item \textbf{Koszul comparison lemma.}
Construct the twisting cochain
\[
        C_X\longrightarrow \DDelta
\]
whose induced cobar map is \(\Theta_{\mathrm{Kos}}\), verify its
Maurer--Cartan equation including signs and curvature terms, prove
finite-stage quasi-isomorphism, and pass to the completed limit.

\item \textbf{Primitive generators lemma.}
Construct compact primitive classes for the real and imaginary simple
roots, with multiplicities and parities matching the Fourier
coefficients of \(\phi_{0,1}\).

\item \textbf{Primitive relations lemma.}
Prove the Borcherds--Kac relations, generation, and quotient by the
radical of the Hopf pairing.  The determinant alone does not determine
these Hall constants.

\item \textbf{Current-envelope augmentation/completion lemma.}
Choose an augmentation and charge completion for \(\DDelta\) compatible
with the compact charge completion of \(C_X\), so that bar--cobar
comparison lives in a single fixed category.

\item \textbf{Cross-volume compatibility lemma.}
Check that the compact construction agrees with the Vol. III
\(\kappa\)-stratification row containing the \(\Delta_5\) Borcherds
product, without importing Vol. III frontier expectations as proof.
\end{enumerate}

\subsection{Claim-status recommendation}

The manuscript should not state
\[
        \Och_E C_X \simeq \DDelta
\]
as a proved compact theorem.  The strongest correct status is:

\begin{quote}
The BD current envelope \(\DDelta\) is a formal chiral target whose
constant primitives are the Gritsenko--Nikulin denominator algebra
\(\gDelta\).  If a compact \(K3\times E\) Hall/factorization object
produces a conilpotent completed chiral coalgebra \(C_X\) and a Koszul
comparison \(\Och_E C_X\to\DDelta\) satisfying the primitive-recognition
and completion hypotheses above, then the compact chiral Koszul
realization follows.  The construction of such \(C_X\) and of the
comparison map remains open.
\end{quote}

This is the precise attack-healed form.  It preserves the useful
target, prevents false transfer from the scalar Borcherds product to a
compact Hall algebra, and isolates the construction lemmas needed for a
future proof.

\subsection{Local anchors checked}

The conclusion above uses the following local anchors.

\begin{itemize}
\item \texttt{main.tex:1780--1906}: denominator Lie superalgebra,
denominator identity, formal current envelope, and quantum upgrade
problem.
\item \texttt{main.tex:1908--1999}, \texttt{main.tex:2001--2087},
\texttt{main.tex:2179--2353}, and \texttt{main.tex:2437--2453}:
elliptic-degree locality obstruction, projection-finite repair
language, sectorial Hall truncations, compact Igusa realization datum,
primitive-recognition theorem, and open chiral-Koszul realization
problem.
\item
\texttt{agent\_material/12\_compact\_hall\_ranE\_attack\_heal.tex:165--235}
and
\texttt{agent\_material/12\_compact\_hall\_ranE\_attack\_heal.tex:266--451}:
scalar spaces versus Hall stacks, conditional Ran construction, and
global-wrapping obstruction.
\item
\texttt{agent\_material/13\_ranE\_obstruction\_attack\_repair.tex:16--87}:
positive elliptic-degree wrapping obstruction and conditional Ran
factorization repairs.
\item
\texttt{agent\_material/12\_primitive\_comparison\_attack\_heal.tex:1--240}
and
\texttt{agent\_material/13\_primitive\_recognition\_attack\_repair.tex:1--210}:
determinant-to-primitive insufficiency and primitive-recognition
hypotheses.
\item
\texttt{/Users/raeez/chiral-bar-cobar/chapters/theory/bar\_construction.tex:1--220},
\texttt{/Users/raeez/chiral-bar-cobar/chapters/theory/cobar\_construction.tex:1--220},
\texttt{/Users/raeez/chiral-bar-cobar/chapters/theory/bar\_cobar\_adjunction\_curved.tex:1--220},
and
\texttt{/Users/raeez/chiral-bar-cobar/chapters/theory/coderived\_models.tex}:
bar--cobar adjunction, conilpotence, completion, and coderived caveats.
\item
\texttt{/Users/raeez/chiral-bar-cobar-vol2/CLAUDE.md:250--390} and
\texttt{/Users/raeez/chiral-bar-cobar-vol2/chapters/connections/bar-cobar-review.tex:4518--4536}:
separation of
bar--cobar inversion, Verdier/Koszul duality, and CY-to-chiral
specialization.
\item
\texttt{/Users/raeez/calabi-yau-quantum-groups/FRONTIER.md},
\texttt{/Users/raeez/calabi-yau-quantum-groups/chapters/connections/bar\_cobar\_bridge.tex},
and
\texttt{/Users/raeez/calabi-yau-quantum-groups/chapters/theory/cy\_to\_chiral.tex}:
Vol. III architecture and
the status of the \(K3\times E\) comparison as a frontier target rather
than a completed compact construction.
\end{itemize}
