\section{Primitive Borcherds recognition from the volumes: attack--heal}
\label{sec:primitive-borcherds-recognition-from-volumes-attack-heal}

\providecommand{\Deltafive}{\Delta_{5}}
\providecommand{\gDelta}{\mathfrak g_{\Delta_{5}}}
\providecommand{\HDelta}{H_{\Delta_{5}}}
\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\Primprot}{\operatorname{Prim}_{\mathrm{prot}}}
\providecommand{\Rad}{\operatorname{Rad}}
\providecommand{\sdim}{\operatorname{sdim}}
\providecommand{\smult}{\operatorname{smult}}
\providecommand{\CoHA}{\operatorname{CoHA}}
\providecommand{\Hall}{\operatorname{Hall}}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\Bch}{B^{\operatorname{ch}}}
\providecommand{\OmegaCh}{\Omega^{\operatorname{ch}}}

\subsection{Question attacked}

The proposed shortcut is:
\[
   H^0\Primprot(F_X)\stackrel{?}{\simeq}\gDelta ,
\]
with the hope that the Hall--Drinfeld, chiral bar--cobar, and Koszul
machinery spread across the surrounding volumes already supplies a
presentation-level recognition theorem for the compact object attached to
\(K3\times E\).

The attack succeeds against the unconditional form of the claim.  The
cross-volume machinery supplies recognition criteria and target-internal
bar--cobar inversions for a supplied object \(\HDelta\), but it does not
construct the compact protected primitive Lie superalgebra with all
Borcherds--Kac defining relations, parity dimensions, Hopf pairing, and
radical quotient.  The healed statement is a conditional recognition theorem:
if the compact Hall/factorization package produces the listed presentation
data, then the primitive algebra is canonically \(\gDelta\).  Without those
data the comparison remains open.

\subsection{Source anchors used}

Local anchors in this repository:
\[
\begin{gathered}
\texttt{CLAUDE.md},\quad \texttt{AGENTS.md},\quad
\texttt{main.tex},\quad \texttt{proj.bib},\\
\texttt{agent\_material/12\_primitive\_comparison\_attack\_heal.tex},\quad
\texttt{agent\_material/13\_primitive\_recognition\_attack\_repair.tex},\\
\texttt{agent\_material/12\_compact\_hall\_ranE\_attack\_heal.tex},\quad
\texttt{agent\_material/13\_ranE\_obstruction\_attack\_repair.tex},\\
\texttt{agent\_material/12\_protected\_integration\_orientation\_attack\_heal.tex},\quad
\texttt{agent\_material/13\_integration\_orientation\_attack\_repair.tex},\\
\texttt{agent\_material/12\_synthesis\_architecture\_attack\_heal.tex},\quad
\texttt{agent\_material/13\_synthesis\_coherence\_attack\_repair.tex}.
\end{gathered}
\]
Cross-volume anchors:
\[
\begin{gathered}
\texttt{calabi-yau-quantum-groups/FRONTIER.md},\\
\texttt{calabi-yau-quantum-groups/chapters/examples/k3e\_bkm\_chapter.tex},\\
\texttt{calabi-yau-quantum-groups/chapters/examples/k3\_chiral\_bialgebra\_platonic.tex},\\
\texttt{calabi-yau-quantum-groups/chapters/theory/cy\_to\_chiral.tex},\\
\texttt{calabi-yau-quantum-groups/chapters/theory/e1\_chiral\_algebras.tex},\\
\texttt{calabi-yau-quantum-groups/chapters/theory/gluing/sec\_8\_k3xe\_master.tex},\\
\texttt{calabi-yau-quantum-groups/chapters/theory/gluing/sec\_10\_unifying.tex},\\
\texttt{chiral-bar-cobar/worldview\_synthesis\_2026\_04\_17.tex},\\
\texttt{chiral-bar-cobar/chapters/theory/theorem\_B\_scope\_platonic.tex},\\
\texttt{chiral-bar-cobar-vol2/FRONTIER.md},\\
\texttt{chiral-bar-cobar-vol2/appendices/cfg\_side\_by\_side.tex},\\
\texttt{chiral-bar-cobar-vol2/chapters/theory/axioms.tex},\\
\texttt{topological-strings/CLAUDE.md}.
\end{gathered}
\]
Primary literature frame, via \(\texttt{proj.bib}\): Borcherds on automorphic
forms with singularities and generalized Kac--Moody algebras,
Gritsenko--Nikulin on automorphic corrections and Lorentzian Kac--Moody
algebras, Kac on the presentation and radical quotient formalism,
Beilinson--Drinfeld on chiral envelopes, and the
Kontsevich--Soibelman/Davison--Meinhardt critical CoHA technology.  These
sources support the target-side and formal-recognition machinery; they do not
remove the compact \(K3\times E\) Hall-data obligations listed below.

\subsection{Primitive functor}

The notation \(H^0\Primprot(F_X)\) is meaningful only after supplying more
than the scalar Igusa determinant.  One needs a charge-completed
factorization/Hall object \(F_X\) over the elliptic direction, an augmentation
and coproduct, and a protected integration functor compatible with the
critical structure.  The primitive functor must be the equalizer
\[
   \Prim(F_X)_\gamma
   =
   \ker\left(
      \Delta_\gamma -
      1\otimes(-)-(-)\otimes1:
      (F_X)_\gamma\to
      \bigoplus_{\gamma_1+\gamma_2=\gamma}(F_X)_{\gamma_1}\otimes(F_X)_{\gamma_2}
   \right)
\]
inside the protected, parity-graded, completed category.  The superscript
\(H^0\) must then select the cohomological degree-zero protected primitive
part after the chosen integration and after the prescribed radical quotient.

Thus the compact datum must include:
\[
   (F_X,\Delta,\epsilon,\Primprot,\Gamma\text{-grading},\deg:\Gamma\to
   \Lambda^{2,1}_{II},H_X,C_X,\Theta_{\operatorname{Kos}}).
\]
Here \(C_X\) is the chiral coalgebra expected to be
\(\Bch_E(F_X)\), and \(\Theta_{\operatorname{Kos}}\) is the bar--cobar
comparison.  The present paper has the virtual determinant and the
Borcherds--Gritsenko--Nikulin target algebra.  It does not yet contain the
compact protected primitive functor as a constructed object.

\subsection{Bracket source}

The bracket on \(H^0\Primprot(F_X)\) must come from the compact Hall or
factorization product, not from the target denominator algebra.  Concretely,
the missing source is an oriented critical Hall package:
\[
   \mathcal M_{\gamma_1}\times \mathcal M_{\gamma_2}
   \xleftarrow{\ p\ }
   \mathcal E_{\gamma_1,\gamma_2}
   \xrightarrow{\ q\ }
   \mathcal M_{\gamma_1+\gamma_2},
\]
with vanishing cycles, Thom--Sebastiani compatibility, stability/HN
completion, and equivariant or reduced descent along \(E\).  The product
\(q_!p^*(-\boxtimes-)\), with its orientation signs, gives a
supercommutator.  The primitive projection then gives the candidate Lie
superbracket.  In a chiral model the same bracket should appear as the
binary collision residue of the factorization product.

The Beilinson--Drinfeld current envelope of \(\gDelta\) verifies what the
target bracket is once \(\gDelta\) is already supplied.  It does not verify
that the compact Hall bracket has the same structure constants.  The Hall
extension correspondences, the orientation character, and the primitive
projection are therefore load-bearing.

\subsection{Chevalley, Serre, and orthogonality checks}

The target algebra \(\gDelta\) is the Borcherds--Kac--Moody superalgebra
with real and imaginary simple roots determined by the
Borcherds--Gritsenko--Nikulin denominator.  A presentation-level recognition
of \(H^0\Primprot(F_X)\) must exhibit compact primitive classes
\[
   e_i^X,\quad f_i^X,\quad h_i^X
\]
and prove the defining relations in the compact bracket.

The required checks are:
\begin{enumerate}
\item Cartan action and Chevalley relation:
\[
   [h,e_i^X]=(\alpha_i,h)e_i^X,\qquad
   [h,f_i^X]=-(\alpha_i,h)f_i^X,\qquad
   [e_i^X,f_j^X]=\delta_{ij}h_i^X .
\]
\item Real-root Serre relations for every even real simple root:
\[
   (\operatorname{ad}e_i^X)^{1-a_{ij}}e_j^X=0,\qquad
   (\operatorname{ad}f_i^X)^{1-a_{ij}}f_j^X=0
\]
for \(i\neq j\), with \(a_{ij}=2(\alpha_i,\alpha_j)/(\alpha_i,\alpha_i)\).
In the \(\Deltafive\) rank-three real subsystem the distinct real simple
roots have square \(2\) and mutual pairing \(-2\), so the visible real
Serre exponent is \(3\).
\item Borcherds orthogonality:
\[
   [e_i^X,e_j^X]=0,\qquad [f_i^X,f_j^X]=0
\]
whenever \(\alpha_i\) and \(\alpha_j\) are imaginary simple roots, or one is
imaginary and one is real, with \((\alpha_i,\alpha_j)=0\), subject to the
usual super sign convention.
\item Generation: these simple primitive classes generate the full compact
primitive Lie superalgebra after radical quotient.
\item No extra relations: the kernel of the map from the abstract
Borcherds--Kac presentation to \(H^0\Primprot(F_X)/\Rad\) is exactly the
Borcherds--Serre ideal.
\end{enumerate}

None of these checks follows from equality of the determinant.  They are
bracket-level facts.  The existing local reports already isolate this as the
central obstruction, and the cross-volume Hall--Drinfeld criteria repeat the
same requirement rather than eliminating it.

\subsection{Imaginary simple root parity and multiplicity}

The compact primitive theorem must match not only the signed root
multiplicities but the full parity dimensions
\[
   \bigl(\dim P_{\alpha,\bar 0},\dim P_{\alpha,\bar 1}\bigr)
\]
for every simple imaginary root and, by generation and PBW, for every root
space.  The denominator determines the superdimension
\[
   \sdim P_\alpha=
   \dim P_{\alpha,\bar0}-\dim P_{\alpha,\bar1},
\]
not the two dimensions separately.

For this paper the canonical parity convention is the
Gritsenko--Nikulin split used in \(\texttt{main.tex}\).  If \(m(a)\) denotes
the signed multiplicity attached to a negative-norm imaginary simple root,
then \(m(a)>0\) contributes even multiplicity \(m(a)\), and \(m(a)<0\)
contributes odd multiplicity \(-m(a)\).  For isotropic simple roots the
\(\tau(a)\)-term supplies the even isotropic multiplicity in the stated
normalization.  Real simple roots are even.

This convention is not replaceable by a cross-volume slogan such as
``negative norm is fermionic''.  Some surrounding files use different
coordinates or a target-side shorthand.  Those statements are not directly
portable into this paper without a basis and parity-normalization audit.
The compact theorem therefore needs an explicit parity map
\[
   P^X_\alpha\longrightarrow
   \mathbb C^{\mu_0(\alpha)}\oplus \Pi\mathbb C^{\mu_1(\alpha)}
\]
for every imaginary simple \(\alpha\), including the isotropic ray.

\subsection{Hopf pairing and radical quotient}

Recognition of the double is stronger than recognition of a positive signed
character.  The compact package must supply a negative half, Cartan part, and
continuous Hopf pairing
\[
   \langle -,-\rangle:
   H_X^+\widehat\otimes H_X^-\longrightarrow \mathbb C
\]
compatible with coproduct, super signs, grading, and completion.  The radical
must be exactly the radical used in the Borcherds--Kac quotient:
\[
   P_X^{\operatorname{red}}
   =
   H^0\Primprot(F_X)/\Rad\langle-,-\rangle .
\]
The quotient must introduce no extra central primitives and kill no target
root space.  Finite-height truncations are the right test objects: the pairing
has to be non-degenerate after quotient at each height, and the inverse limit
must be complete for the Hall product, coproduct, and Lie bracket.

The Vol III Hall--Drinfeld equivalence criterion requires precisely these
data: positive half, Serre-dual negative half, Cartan completion, continuous
Hopf pairing, radical quotient, centre control, PBW flatness, and
compatibility with the chosen completion.  It is a criterion, not a
construction of the compact \(K3\times E\) object.

\subsection{Healed conditional theorem}

\begin{theorem}[conditional primitive recognition]
Assume the compact \(K3\times E\) package supplies the following data.
\begin{enumerate}
\item A protected charge-completed Hall/factorization object \(F_X\) with
coproduct, augmentation, primitive functor, and degree map to the
\(\Deltafive\) root lattice.
\item An oriented critical Hall bracket on \(H^0\Primprot(F_X)\), compatible
with the protected integration and super parity.
\item A Cartan subalgebra identified with
\(\Lambda^{2,1}_{II}\otimes\mathbb C\) and compact primitive representatives
\(e_i^X,f_i^X,h_i^X\) for every real and imaginary simple root in the
Gritsenko--Nikulin \(\Deltafive\) simple system.
\item The Cartan, Chevalley, real Serre, Borcherds orthogonality, and super
sign relations hold for these classes.
\item The full parity dimensions of the compact root spaces agree with the
Gritsenko--Nikulin parity split, including all imaginary simple root
multiplicities and the isotropic \(\tau\)-multiplicities.
\item The compact primitives are generated by the simple classes, and the
kernel of the map from the abstract Borcherds--Kac presentation is exactly
the Borcherds--Serre ideal.
\item The Hall double has a continuous Hopf pairing, Cartan completion, and
radical quotient matching the denominator-algebra quotient, with no extra
central or stability-wall primitives.
\end{enumerate}
Then there is a canonical isomorphism of graded Lie superalgebras
\[
   H^0\Primprot(F_X)/\Rad \;\cong\; \gDelta .
\]
Consequently the denominator of the compact primitive algebra is the
normalized Borcherds product
\[
   \operatorname{den}\bigl(H^0\Primprot(F_X)/\Rad\bigr)
   =
   64^{-1}\Deltafive(2Z).
\]
If, in addition, the chiral Koszul comparison
\(\Theta_{\operatorname{Kos}}:C_X\simeq \Bch_E(F_X)\) is supplied and
\(\OmegaCh_EC_X\) is complete on the same charge topology, then
\[
   \OmegaCh_E C_X\simeq \operatorname{Den}_{\Delta_5,E}
\]
as the current/chiral enveloping object attached to \(\gDelta\).
\end{theorem}

\begin{proof}[Proof sketch]
The assumptions define a surjective homomorphism from the abstract
Borcherds--Kac--Moody superalgebra with the Gritsenko--Nikulin simple root
datum to the compact primitive quotient.  The Chevalley, Serre, orthogonality,
and parity hypotheses put the Borcherds--Serre ideal in the kernel.  The
``no extra relations'' and Hopf radical hypotheses identify the kernel with
that ideal and identify the Cartan quotient.  The parity-dimension hypothesis
rules out invisible zero-superdimension changes.  Hence the compact primitive
quotient is \(\gDelta\).  The denominator follows from the already verified
Borcherds--Gritsenko--Nikulin product normalization in the paper.  The last
assertion is the standard chiral bar--cobar inversion, applied only after the
compact object and its completion have been supplied.
\end{proof}

\subsection{Impossible shortcuts}

The following implications are false or presently unsupported.
\begin{enumerate}
\item The equality of scalar determinants does not determine the primitive
Lie superalgebra.  A zero bracket on the same signed graded vector space has
the same signed character and the wrong algebra.
\item The Oberdieck--Pandharipande scalar square does not construct the Hall
bracket, coproduct, primitive projection, or Hopf pairing.
\item The Gritsenko--Nikulin denominator identifies the target
\(\gDelta\).  It does not prove that compact protected primitives realize
that target.
\item The formal current envelope of \(\gDelta\) is target-internal.  It
cannot replace the compact Hall extension correspondences.
\item Chiral bar--cobar inversion recovers an algebra from its supplied
Koszul coalgebra.  It does not identify an unknown compact \(F_X\) with
\(\HDelta\).
\item The Vol III Hall--Drinfeld/Super-Yangian theorem is a recognition
criterion with hypotheses.  It is not an unconditional compact
\(K3\times E\) primitive theorem.
\item A homotopy colimit of the twenty-four curve-stalk positive halves does
not by itself supply the negative half, Cartan completion, Hopf pairing,
Serre ideal, centre control, or compact bracket comparison.
\item The eight-row diagonal-divisor catalogue gives the correct product row
and normalization frame.  It does not give compact primitive generators and
relations.
\item A claim that \(H^0\Primprot(F_X)\) has the right superdimension cannot
separate an honest even generator from an even-plus-odd cancelling pair.
\item Quotienting by the elliptic translation direction before constructing
projection-finite and globally wrapped sectors can erase the relative-position
data needed for Hall products.
\end{enumerate}

\subsection{Compact data still missing}

The smallest remaining data packet needed for an actual proof is:
\begin{enumerate}
\item An extension-closed compact heart or stability condition for the
relevant \(K3\times E\) objects, with HN completion and charge grading.
\item A projection-finite/global-wrapping repair of the naive \(\Ran(E)\)
model, so positive elliptic degree sectors are not lost.
\item A critical atlas, vanishing-cycle sheaves, Thom--Sebastiani
isomorphisms, and a strong orientation character compatible with the
\(\Deltafive\) signs.
\item A protected integration functor whose scalar shadow is the established
Igusa product and whose categorified output still carries Hall product,
coproduct, and parity.
\item The primitive functor and primitive projection on the completed
protected Hall object.
\item Compact representatives for all real and imaginary simple roots, with
the full parity dimensions \((\mu_0,\mu_1)\), not merely signed
multiplicities.
\item Direct Hall-bracket computations proving Cartan, Chevalley, real Serre,
Borcherds orthogonality, and generation.
\item A negative half, Cartan completion, continuous Hopf pairing, radical
quotient, PBW theorem, finite-height completion, and centre-control theorem.
\item The chiral coalgebra \(C_X\), conilpotence/completion checks, and the
Koszul comparison \(\Theta_{\operatorname{Kos}}\).
\end{enumerate}

\subsection{Normalization warnings}

The denominator normalization in this repository is
\[
   \operatorname{den}(\gDelta)=64^{-1}\Deltafive(2Z).
\]
The scalar Oberdieck--Pandharipande form is the square in the monic
normalization, so statements phrased in terms of the Igusa form
\(\Phi_{10}\) must be translated before being imported into this paper.
Likewise, surrounding files that call \(\HDelta\) a completed
Hall--Drinfeld double generally work after imposing a criterion or after
supplying the target object.  They should not be cited as constructing
\(H^0\Primprot(F_X)\) unless the compact data listed above have been
provided.

\subsection{Status}

The primitive comparison
\[
   H^0\Primprot(F_X)\stackrel{?}{=}\gDelta
\]
is not presently a theorem of the cross-volume machinery.  The correct
statement is conditional presentation-level recognition.  The missing compact
data are small in description but large in proof: the protected Hall bracket,
the imaginary simple parity and multiplicity lift, the Chevalley--Serre--
orthogonality verification, and the Hopf pairing/radical quotient.  These are
exactly the data that determinant, row-catalogue, and bar--cobar shortcuts
forget.

\subsection{Claim status recommendation}

The line \(H^0\Primprot(F_X)=\gDelta\) should remain
\emph{conditional}.  A theorem may be stated only in the presentation-level
form above, with all primitive, bracket, parity, relation, pairing, radical,
and completion hypotheses visible.  It should not be cited as an established
compact realization theorem until the missing data packet has been supplied.

\subsection{Files changed and checks}

Files changed by this report:
\[
   \texttt{agent\_material/14\_primitive\_borcherds\_recognition\_from\_volumes\_attack\_heal.tex}.
\]
No manuscript source or generated PDF was edited.  The working tree already
contained unrelated modifications outside this file; they were not touched.
Checks run: \(\texttt{git diff --check}\) on this file, targeted readback with
\(\texttt{sed}\), and keyword audit with \(\texttt{rg}\).  No global build was
run, since this is a standalone agent report and is not included in
\(\texttt{main.tex}\).
