\section{Ran(\(E\)) locality, global modes, and hybrid wrapping}
\label{sec:agent-14-ranE-hybrid-wrapping}

\providecommand{\Z}{\mathbb Z}
\providecommand{\C}{\mathbb C}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\Supp}{\operatorname{Supp}}
\providecommand{\Ext}{\operatorname{Ext}}
\providecommand{\RHom}{\operatorname{RHom}}
\providecommand{\Fact}{\mathsf{Fact}}
\providecommand{\Perf}{\operatorname{Perf}}
\providecommand{\Coh}{\operatorname{Coh}}
\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\sdim}{\operatorname{sdim}}
\providecommand{\Spch}{\mathrm{Sp}^{\mathrm{ch}}}
\providecommand{\Hall}{\mathcal H}
\providecommand{\Mloc}{\mathcal M^{\mathrm{loc}}}
\providecommand{\Mwr}{\mathcal M^{\mathrm{wr}}}
\providecommand{\Eloc}{\mathfrak E^{\mathrm{loc}}}
\providecommand{\Ewr}{\mathfrak E^{\mathrm{wr}}}
\providecommand{\Ehyb}{\mathfrak E^{\mathrm{hyb}}}

\subsection{Claim attacked}

The attacked implication is:
\[
\begin{gathered}
\hbox{there is a compact Hall/chiral object on }\Ran(E)\\
\Longrightarrow
\hbox{ordinary support-local factorization on }\Ran(E)
\hbox{ carries the full Igusa }(q,r,s)\hbox{-product}.
\end{gathered}
\]
This implication is false.  Ordinary Ran locality over \(E\) is a
finite-support statement.  The positive elliptic-degree sector of
\(K3\times E\) is not finite over \(E\).  Hence the \(s\)-direction of
the Igusa product cannot be recovered from the usual disjoint-open
factorization calculus unless one adds extra global data.

The checked local anchors are \verb|main.tex|,
\verb|lem:elliptic-degree-locality-obstruction|,
\verb|cor:ranE-locality-misses-elliptic-degree|,
\verb|rem:Repair alternatives|,
\verb|def:compact-igusa-realization-datum|, and
\verb|thm:primitive-recognition|.  The preceding local reports used
here are
\verb|agent_material/12_compact_hall_ranE_attack_heal.tex|,
\verb|agent_material/13_ranE_obstruction_attack_repair.tex|,
\verb|agent_material/12_protected_integration_orientation_attack_heal.tex|,
\verb|agent_material/13_integration_orientation_attack_repair.tex|,
\verb|agent_material/12_primitive_comparison_attack_heal.tex|, and
\verb|agent_material/13_primitive_recognition_attack_repair.tex|.

\subsection{Exact obstruction}

Let \(X=K3\times E\), and let \(p_E:X\to E\) be projection.  If
\[
(p_E)_*[C]=b[E],\qquad b>0,
\]
for a one-dimensional subscheme \(C\subset X\), then \(p_E(C)=E\).
Indeed, if \(p_E(C)\) were zero-dimensional, the pushforward of the
one-cycle \([C]\) would be zero.  Since \(E\) is irreducible, any
one-dimensional closed image is all of \(E\).  Thus positive elliptic
degree is a wrapped or global condition over \(E\), not a finite-support
condition.

Consequences:
\begin{enumerate}
\item A projection-finite object, with \(p_E(\Supp A)\subset F\) for
finite \(F\subset E\), can be assigned to a point of \(\Ran(E)\).
\item A positive elliptic-degree object has support dominating \(E\);
it cannot be assigned to any finite subset of \(E\).
\item The reduced OP/DT quotient by translation on \(E\) is a scalar
operation.  If one quotients before forming Hall extension
correspondences, the relative \(E\)-position needed for convolution has
already been forgotten.
\item Therefore a naive compact Hall object on \(\Ran(E)\) can see the
projection-finite part, but misses the full \(s\)-direction of
\[
\Delta_5
=64\,q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)>0}(1-q^n r^l s^m)^{f(nm,l)}.
\]
\end{enumerate}

This is not a failure of the Borcherds product or of the OP scalar
square.  It is a locality failure for the proposed compact
Hall/factorization source.

\subsection{What the other volumes already provide}

\paragraph{Vol. I: \texttt{chiral-bar-cobar}.}
The first volume provides curve-level bar-cobar technology and a
Heisenberg determinant-line/Fock mechanism in a controlled setting.  Its
working notes explicitly separate scalar Fock amplitudes from a full
dg-categorical modular cooperad.  They also record the finite-Fock
obstruction: no finite dg-category with finite-dimensional total
Hochschild trace can recover the full infinite product.  The honest lift
there is pro-nuclear or completed Fock data, built as an inverse limit of
finite-energy truncations.

Vol. I therefore supplies a useful template for a global Fock leg, but
not an Igusa \(K3\times E\) wrapped elliptic-degree construction.  It
also refuses the automatic Hecke conclusion: a Hecke decomposition is
available only when an actual Hecke-compatible decomposition has been
constructed.  A weight-defective or scalar sewing identity does not by
itself create Hecke modes.

\paragraph{Vol. II: \texttt{chiral-bar-cobar-vol2}.}
The second volume retracts the naive statement that an \(E_2\)- or
ordinary Ran-factorization object on a genus-one curve already sees
global modular structure.  Its higher-genus integration notes say the
local chiral algebra lives on small disks, while modular information
lives in factorization/chiral homology or in extra global structure.

For the Igusa/BKM problem Vol. II points to a bi-based architecture:
smooth Ran data on a discriminant curve, nearby-cycle data at singular
points, and parameter-side factorization on \(\overline{\mathcal A}_2\).
It also states that the BKM-side object is a Hall--Drinfeld double, not
a plain Yangian, and retracts direct nodal BD chirality.  This is an
architectural model for a hybrid base, not a constructed
\(K3\times E\) local/global extension stack.

\paragraph{Vol. III: \texttt{calabi-yau-quantum-groups}.}
The third volume distinguishes the native \(E_d\)-factorization algebra
of a Calabi--Yau category from the Stage-2 curve specialization
\(\Spch_{\Sigma,C}\).  For \(K3\times E\), the chain-level object
\[
\Spch_{K3,E}(\Phi^{FA}_3(K3\times E))\simeq H_{\Delta_5}
\]
is a target or conjectural bridge, not a theorem.  The same volume says
that comparison with a global Hall--Borcherds/Drinfeld object is an
additional bridge requiring a positive half, Hopf pairing, completion,
descent, and bracket comparison.

Thus Vol. III supplies the correct status discipline: the
Gritsenko--Nikulin denominator is the theorem-grade value shadow, while
the compact Hall--Drinfeld or chiral-Borcherds source remains
conditional.  It does not construct the missing wrapped elliptic-degree
locality.

\paragraph{\texttt{topological-strings}.}
The topological-strings volume separates local topological or
holomorphic factorization on small disks from global BPS/GV
resummations.  Its local Fukaya model near a compact interval explicitly
does not include wrapped generators at infinity.  Its MNOP/BCOV framing
records a global trans-series/BPS completion, but that is a scalar
global summation, not a local collision factorization operation.

This is the same structural warning: local factorization and global
wrapped sectors are different data.

\subsection{First repair: projection-finite local factorization plus global modes}

The first proposed repair is:
\[
\mathcal F^{\mathrm{loc}}\in\Fact(\Ran(E))
\quad\hbox{for projection-finite sectors}
\]
together with a separate completed Fock/Hecke object
\(\mathcal G^{\mathrm{glob}}\) carrying positive elliptic degree.

\paragraph{Attack.}
This repair is not automatic from any existing volume.  Vol. I has
Heisenberg Fock technology and a pro-nuclear completion template, but
not the Igusa \(K3\times E\) elliptic-degree modes.  Vol. II and Vol.
III treat the relevant BKM object as Hall--Drinfeld or
chiral-Borcherds data still requiring completion and bracket comparison.
The OP/DT scalar series proves a coefficient shadow, not a Hall action.

Moreover, if \(\mathcal G^{\mathrm{glob}}\) is simply appended as an
external Fock factor, then one may recover a product formula while still
failing the primitive-recognition theorem.  A decoupled product has no
reason to carry the mixed brackets between vertical projection-finite
charges and positive elliptic-degree charges.  It can have the correct
signed dimensions and the wrong Lie superalgebra.

\paragraph{Healed conditional form.}
This repair becomes mathematically usable only after supplying the
following data:
\begin{enumerate}
\item a projection-finite oriented critical Hall/chiral object
\(\mathcal F^{\mathrm{loc}}\) on \(\Ran(E)\);
\item a completed global object \(\mathcal G^{\mathrm{glob}}\) graded by
positive elliptic degree \(b>0\) and by the remaining Igusa charges;
\item actual Hecke or Fock operators \(T_m\) whose trace identity gives
the exponents \(f(nm,l)\), not merely a scalar equality after the fact;
\item an action or module structure of the local Hall object on the
global object, retaining relative \(E\)-position before reduction;
\item orientation and protected integration compatible with both the
local product and the global-mode action;
\item primitive recognition:
\[
\sdim \Prim_{\mathrm{prot},(n,l,m)}=f(nm,l),
\]
with the Gritsenko--Nikulin/Borcherds bracket and radical quotient
identified, not only the determinant.
\end{enumerate}

Under only items (1)--(3), this is at best a determinant-level repair.
For the manuscript's compact realization problem, items (4)--(6) are
load-bearing.

\subsection{Second repair: hybrid local/global wrapped factorization}

The second proposed repair is a two-sorted or coloured factorization
object.  Local colours are projection-finite and live over
\(\Ran(E)\).  Wrapped colours dominate \(E\) and live globally.  The
operation spaces are not ordinary disjoint-open products alone; they are
extension stacks with local and global legs.

\paragraph{Attack.}
No surveyed volume already constructs this hybrid object for
\(K3\times E\).  Vol. II gives a bi-based Ran/nearby-cycle/parameter
architecture, and Vol. III gives the Hall--Drinfeld target.  These are
models for the shape of the answer, not the answer.  In particular, no
existing text supplies the mixed extension correspondences, their
Thom--Sebastiani orientation transport, their associativity over
two-step flags, or their compatibility with reduced OP integration.

\paragraph{Healed conditional form.}
The hybrid construction should be formulated through the following
stacks and correspondences.

For a finite subset or disjoint opens \(U_1,\ldots,U_r\subset E\), let
\(\Mloc_{\alpha_i}(U_i)\) classify projection-finite objects of charge
\(\alpha_i\) supported over \(U_i\).  Let \(\Mwr_{\eta}\) classify
wrapped objects of charge \(\eta\), with positive elliptic-degree
component \(b(\eta)>0\), so that their support dominates \(E\).

The local-only correspondence is the usual projection-finite Hall
correspondence
\[
\prod_{i=1}^r \Mloc_{\alpha_i}(U_i)
\longleftarrow
\Eloc_{\alpha_1,\ldots,\alpha_r}(U_1,\ldots,U_r)
\longrightarrow
\Mloc_{\alpha_1+\cdots+\alpha_r}(U_1\cup\cdots\cup U_r).
\]

The mixed correspondence must be a stack
\[
\prod_{i=1}^r \Mloc_{\alpha_i}(U_i)\times \Mwr_{\eta}
\longleftarrow
\Ehyb_{\alpha_1,\ldots,\alpha_r;\eta}(U_1,\ldots,U_r)
\longrightarrow
\Mwr_{\eta+\alpha_1+\cdots+\alpha_r},
\]
whose points are exact sequences or exact triangles with local
subquotients of charges \(\alpha_i\) and one wrapped leg of charge
\(\eta\).  The output is wrapped as soon as one input is wrapped.

The wrapped-wrapped correspondence is
\[
\Mwr_{\eta_1}\times\Mwr_{\eta_2}
\longleftarrow
\Ewr_{\eta_1,\eta_2}
\longrightarrow
\Mwr_{\eta_1+\eta_2}.
\]

For associativity, one also needs flag stacks
\[
\mathfrak{Flag}^{\mathrm{hyb}}_{\alpha_1,\ldots,\alpha_r;\eta}
\]
classifying two-step filtrations whose associated graded pieces are the
specified local and wrapped legs.  The two push-pull composites attached
to different parenthesizations must agree after the chosen orientation
and completion.

The reduced \(E\)-quotient must not be taken before these
correspondences are formed.  The stacks must first remember relative
\(E\)-position, carry the determinant-line orientation, and only then
descend or integrate to the reduced protected theory.

\subsection{Required orientation, completion, and integration data}

Both repairs need the same missing structural layers:
\begin{enumerate}
\item an extension-closed heart or stable \(\infty\)-categorical sector
for the compact \(K3\times E\) objects used in the Hall construction;
\item a critical or shifted-symplectic atlas on local, wrapped, and
mixed extension stacks;
\item a strong orientation: compatible square roots of determinant
lines for local-local, local-wrapped, and wrapped-wrapped
correspondences;
\item a Harder--Narasimhan or energy completion making all infinite
charge sums continuous and coefficientwise finite;
\item equivariant construction before translation reduction by \(E\);
\item a protected integration map whose scalar shadow is the OP/DT
series and whose primitive shadow is the Borcherds denominator algebra;
\item a primitive recognition certificate proving the root
multiplicities, parity, bracket, Serre/Borcherds relations, and radical
quotient for \(\mathfrak g_{\Delta_5}\).
\end{enumerate}

\subsection{Tests}

The following tests are required before either repair can be promoted to
a manuscript theorem.

\begin{enumerate}
\item \textbf{Projection test.}  Verify that the local sector has
elliptic degree \(b=0\) or otherwise finite projection to \(E\), while
each positive \(b\) sector is classified as wrapped.
\item \textbf{Support locality test.}  For local objects supported over
disjoint opens of \(E\), prove the required vanishing or splitting of
cross-\(\Ext\) terms used by the factorization product.  Identify the
collision stack when the opens meet.
\item \textbf{Wrapped obstruction test.}  For every proposed operation
placing a positive elliptic-degree object at a finite Ran point, check it
against \(p_E(C)=E\).  Such an operation is invalid unless it is part of
the global or hybrid leg.
\item \textbf{Quotient-order test.}  Construct Hall correspondences
\(E\)-equivariantly before reduced quotienting.  A quotient-first
construction fails if it cannot recover relative \(E\)-position in a
mixed extension.
\item \textbf{Mixed associativity test.}  Compare the two push-pull
maps through
\(\mathfrak{Flag}^{\mathrm{hyb}}_{\alpha,\beta;\eta}\):
first combine \(\alpha\) with \(\beta\), then act on \(\eta\), versus
first act by \(\beta\), then by \(\alpha\).  The same test is required
for two wrapped legs.
\item \textbf{Orientation test.}  Check determinant-line square roots
and Thom--Sebastiani signs on local-local, local-wrapped, and
wrapped-wrapped extension stacks.  This is where the open
orientation-monodromy character must be decided.
\item \textbf{Determinant shadow test.}  After protected integration,
the Euler-characteristic shadow must recover the normalized denominator
\[
\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z)
\]
and the scalar OP/DT square
\[
Z^{K3\times E}_{DT}=Z^{K3\times E}_{OP}=-4096\,\Delta_5^{-2}.
\]
\item \textbf{Primitive test.}  In a finite charge box, for example
\(0\le n,m\le 2\) and \(|l|\le 4\), compute the protected primitives and
verify
\[
\sdim \Prim_{\mathrm{prot},(n,l,m)}=f(nm,l).
\]
Then check the bracket relations, not only the dimensions.
\end{enumerate}

\subsection{Recommendation for the manuscript}

The manuscript should keep the current compact realization statement
conditional and obstruction-aware.  The theorem-grade facts are the
Borcherds product, the denominator identification imported from
Gritsenko--Nikulin/Borcherds, and the OP/DT scalar square.  They do not
construct the compact Hall/factorization source.

The cleanest manuscript language is:
\[
\begin{gathered}
\hbox{projection-finite sectors may form a local object on }\Ran(E),\\
\hbox{positive elliptic-degree sectors require either global Fock/Hecke
modes}\\
\hbox{with mixed Hall action, or a hybrid local/global wrapped
factorization theory.}
\end{gathered}
\]
The first repair is acceptable as a determinant-level architecture only
after actual completed global modes are supplied.  It becomes a compact
realization architecture only after mixed local/global action and
primitive recognition are proved.

The second repair is the geometrically better target, because it keeps
the extension problem visible: local vertical legs and wrapped
elliptic-degree legs must interact through explicit mixed extension
stacks.  No other volume presently constructs those stacks for
\(K3\times E\).  The manuscript should therefore state hybrid wrapping
as required future data, not as an available theorem.

\subsection{Claim-status conclusion}

\[
\boxed{
\begin{array}{l}
\text{Ordinary }\Ran(E)\text{ locality for the full Igusa product:
false.}\\
\text{Projection-finite local factorization: conditional and plausible.}\\
\text{Separate global Fock/Hecke repair: not yet constructed for
}K3\times E.\\
\text{Hybrid local/global wrapped repair: correct target shape, open.}\\
\text{Compact Hall realization of }\mathfrak g_{\Delta_5}\text{: open.}
\end{array}}
\]

Files changed by this report: only
\verb|agent_material/14_ranE_hybrid_wrapping_from_volumes_attack_heal.tex|.
