\providecommand{\AEX}{\mathcal A^{E_3}_X}
\providecommand{\AX}{\mathcal A_X}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\Fact}{\mathsf{Fact}}
\providecommand{\Perf}{\operatorname{Perf}}
\providecommand{\CoHA}{\operatorname{CoHA}}
\providecommand{\Hall}{\operatorname{Hall}}
\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\Primprot}{\Prim_{\operatorname{prot}}}
\providecommand{\Spch}{\operatorname{Sp}^{\operatorname{ch}}}
\providecommand{\PhiFA}{\Phi^{\operatorname{FA}}}
\providecommand{\hCS}{\operatorname{hCS}}
\providecommand{\gDelta}{\mathfrak g_{\Delta_5}}
\providecommand{\DDelta}{\mathsf{Den}_{\Delta_5,E}}
\providecommand{\epsor}{\epsilon_o}
\providecommand{\nuDelta}{\nu_{\Delta_5}}
\providecommand{\sdim}{\operatorname{sdim}}

\section{Agent 15-A: compact finite-first \(E_3\) source}

\subsection{Claim attacked}

The attacked statement is the strongest compact realization shortcut:
\[
\begin{gathered}
\hbox{Vol. I/II/III bar--cobar, hCS, CoHA, and BKM technology}\\
\Longrightarrow
\hbox{a compact finite-first holomorphic \(E_3\)-factorization algebra }
\AEX\\
\hbox{on }X=K3\times E
\hbox{ whose Ran specialization, Hall atlas, orientation, integration,}\\
\hbox{orientation character, and primitive quotient already realize }
\gDelta .
\end{gathered}
\]

This implication is false.  The surrounding volumes supply a coherent
conditional architecture, several local or formal witnesses, and target-side
denominator data.  They do not construct the compact finite-first source
\(\AEX\), nor the downstream wrapped Ran object, compact Hall atlas,
protected integration, character comparison, or primitive presentation.  The
correct repair is not a weaker slogan.  It is a theorem-grade conditional
construction packet whose first gate is the compact finite-first
holomorphic \(E_3\) source.

\subsection{First-principles formulation of gate 1}

Let \(X=S\times E\), with \(S\) a projective \(K3\) surface and \(E\) an
elliptic curve.  A compact finite-first holomorphic \(E_3\) source for the
Igusa realization is not a scalar invariant.  It is the following object.

\begin{definition}[compact finite-first \(E_3\) source]
A compact finite-first holomorphic \(E_3\)-factorization source on
\(X=K3\times E\) is a charge-completed object
\[
        \AEX\in E_3\text{-}\operatorname{HolFA}_\Gamma(X)^\wedge
\]
with these data.
\begin{enumerate}
\item A numerical charge lattice \(\Gamma\) with a fixed degree map to the
Igusa variables and to the Gritsenko--Nikulin root lattice, compatible
with
\[
        \alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}.
\]
\item Local holomorphic observables on polydisks of \(X\), restriction maps,
and \(E_3\)-factorization products for disjoint opens, with collision
operations before any trace is taken.
\item A compact BV/\(\hCS\) or equivalent quantum construction satisfying
descent, gauge fixing, the quantum master equation, anomaly cancellation,
and all-scale renormalization in the completed compact charge category.
\item A sectorial stability/HN tower.  For every strict sector \(S\) and
height bound \(R\), the finite quotient
\[
        \mathsf F_R\AEX
\]
is an honest finite-stage object.  The completed source is the inverse
limit of these finite stages, with transition maps continuous for all
factorization products.
\item Compatibility with compact support and \(E\)-equivariance before the
translation quotient on \(E\).  Quotienting first is not permitted: it loses
the relative \(E\)-position needed by Hall convolution and mixed wrapped
operations.
\item A fixed \(E_3\)-formality point and chain-level \(S^3\)-framing
witness.  The vanishing of a formal Atiyah-class obstruction on
\(K3\times E\) is evidence for a locus, not the completed compact quantum
object.
\end{enumerate}
\end{definition}

The word ``finite-first'' is load-bearing.  It does not mean that the
charge support is finite.  A nonzero additive heart has infinitely many
charges.  It means that all products, coproducts, obstructions, and
comparison maps are defined on finite HN/height quotients first, and only
then promoted to the completed inverse system.  The first obstruction
therefore lies before \(\Delta_5\): can one construct \(\AEX\) itself with
QME, anomaly, descent, framing, and completion witnesses?

\subsection{Attack--heal cycle across the six gates}

\paragraph{Gate 1: compact finite-first \(E_3\) source.}
Attack.  Vol. III says the two-stage architecture is
\(\Phi_d=\Spch\circ\PhiFA_d\) and records favorable \(K3\times E\)
formality input.  It also records that, at \(d=3\), the object-level theorem
is conditional on a chosen \(E_3\)-formality point, chain-level \(S^3\)
framing, anomaly-cancellation and analytic-completion witnesses, and an
admissible specialization datum.  Hence the formal \(K3\times E\) witness
does not construct the compact source.

Heal.  State gate 1 as a conditional compact-source theorem: if the
formality point, \(S^3\)-framing, QME, anomaly, descent, compact support,
and finite-first HN tower are all supplied, then \(\AEX\) is a legitimate
input for the Igusa realization problem.  No denominator or scalar trace is
used in this construction.

\paragraph{Gate 2: Ran(\(E\)) elliptic-degree obstruction.}
Attack.  Ordinary support-local factorization on \(\Ran(E)\) is a
finite-support calculus.  If \(C\subset K3\times E\) has positive elliptic
degree, then \((p_E)_*[C]=b[E]\), \(b>0\), and \(p_E(C)=E\).  Such a sector
cannot be assigned to a finite Ran point.  The full Igusa \(s\)-direction is
therefore invisible to naive Ran locality.

Heal.  Gate 2 must be a hybrid local/global theory: projection-finite
sectors give the ordinary local Ran part; positive elliptic-degree sectors
are wrapped global legs.  Mixed extension stacks must remember relative
\(E\)-position and must be associative over two-step flags before reduced
integration.

\paragraph{Gate 3: oriented compact Hall/CoHA atlas.}
Attack.  OP/DT Hilbert-scheme or stable-pair moduli produce scalar
integrals.  They are not an extension-closed compact Hall atlas with
oriented extension correspondences.  Vol. III's positive-geometry grammar
names the correct Hall package, but its compact certificates require
stability, support, HN control, critical charts, orientation, motivic
target, integration, and realization maps.

Heal.  Gate 3 is a separate construction of
\[
\mathfrak M_\gamma^\sigma\times\mathfrak M_\eta^\sigma
\xleftarrow{\ p_{\gamma,\eta}\ }
\mathfrak E_{\gamma,\eta}^\sigma
\xrightarrow{\ q_{\gamma,\eta}\ }
\mathfrak M_{\gamma+\eta}^\sigma
\]
with finite-type HN quotients, shifted-symplectic or critical charts,
vanishing cycles, and Thom--Sebastiani orientation transport.  It is not
deduced from \(Z^{X}_{\operatorname{OP}}=-4096\Delta_5^{-2}\).

\paragraph{Gate 4: protected integration and orientation character.}
Attack.  The constants \(64\), \(4096\), and the OP minus sign fix
normalizations of functions.  They do not define a Hall-side orientation
line, a protected integration map, or a Weyl action.  Generic orientability
of a CY3 moduli stack gives at most a square-root system; it does not
compute its reflection monodromy.

Heal.  Gate 4 must construct
\[
I^{\operatorname{prot}}_{\sigma,o}:
\Hall^{\operatorname{or}}_{K3\times E}
\longrightarrow
\widehat{\mathbf C[\Gamma_{\operatorname{eff}}]}
\]
compatible with Hall product, HN completion, wall crossing, primitive
projection, and the chosen determinant-line square roots.

\paragraph{Gate 5: comparison \(\epsor=\nuDelta\).}
Attack.  The expression \(\epsor\) has no domain until the oriented Hall
object and a lifted type-II Weyl action exist.  The automorphic character
\(\nuDelta\) is theorem-level on the modular side; equality with a geometric
orientation character is a comparison theorem, not a normalization.

Heal.  Construct
\[
\rho_o:W^{(2)}(\Lambda^{2,1}_{II})
\to
\operatorname{Aut}(\Hall^{\operatorname{or}}_{K3\times E})
\]
preserving product, charge map, completion, and protected integration.
Then prove
\[
        \operatorname{sgn}_o\circ\rho_o
        =
        \nuDelta\circ\iota_{\operatorname{ext}}
\]
on \(W^{(2)}(\Lambda^{2,1}_{II})\), including the simple reflection signs
and the Coxeter/Nikulin relations.

\paragraph{Gate 6: primitive recognition.}
Attack.  Signed denominator multiplicities determine only
\[
        \sdim P_{(n,l,m)}=f(nm,l).
\]
They do not determine parity dimensions, Hall brackets, simple primitive
representatives, Serre/Borcherds relations, a negative half, Hopf pairing,
or the radical quotient.

Heal.  Gate 6 is a presentation-level theorem.  After gates 1--5 have
constructed \(F_X=\Spch_{K3,E}(\AEX)\), its protected primitive quotient
must carry the Gritsenko--Nikulin simple real and imaginary roots, the full
parity split, the Borcherds--Kac relations, generation, continuous Hopf
pairing, and the same radical quotient.  Only then may one conclude
\[
        H^0\Primprot(F_X)/\operatorname{Rad}
        \cong
        \gDelta .
\]

\subsection{Healed conditional theorem}

\begin{theorem}[conditional compact Igusa realization from a supplied \(E_3\) source]
Let \(X=K3\times E\).  Assume the following data are supplied.
\begin{enumerate}
\item A compact finite-first holomorphic \(E_3\)-factorization algebra
\(\AEX\) on \(X\), with fixed \(E_3\)-formality point, \(S^3\)-framing,
descent, QME, anomaly cancellation, compact-support conventions, and HN
finite-first completion.
\item A chain-level specialization
\[
        F_X=\Spch_{K3,E}(\AEX)
\]
with Beck--Chevalley, Fubini/envelope, Tor-independence, proper-support,
compact-support, and completion witnesses.
\item A hybrid local/global wrapped factorization theory on the elliptic
direction, whose projection-finite part is local on \(\Ran(E)\) and whose
positive elliptic-degree part is carried by global wrapped legs with mixed
extension correspondences.
\item An oriented compact Hall/CoHA atlas for the same charge sectors,
defined before reduction by translations on \(E\), with vanishing cycles,
Thom--Sebastiani orientation transport, and finite HN quotients.
\item A protected integration map compatible with Hall product, wall
crossing, completion, and primitive projection.
\item A lifted Weyl action on the oriented completed Hall object and a
proof that its orientation monodromy character equals
\(\nuDelta\) after the exterior-square/lattice identification.
\item A conilpotent completed chiral coalgebra
\[
        C_X\simeq \overline B^{\operatorname{ch}}_E(F_X)
\]
and a completed/coderived chiral Koszul comparison
\[
        \Theta_{\operatorname{Kos}}:
        \Omega_E^{\operatorname{ch}}C_X
        \xrightarrow{\ \simeq\ }
        \DDelta .
\]
\item A primitive recognition certificate: full parity dimensions, simple
primitive representatives, Cartan/Chevalley/real-Serre/Borcherds
orthogonality relations, generation, continuous Hopf pairing, and the
Gritsenko--Nikulin radical quotient.
\end{enumerate}
Then
\[
        H^0\Primprot(F_X)/\operatorname{Rad}
        \cong
        \gDelta
\]
as a charge-graded Borcherds--Kac--Moody Lie superalgebra, and its
Weyl--Kac--Borcherds denominator is \(64^{-1}\Delta_5(2Z)\).  If
\(\Theta_{\operatorname{Kos}}\) is included, the elliptic chiral cobar
object is \(\DDelta\).
\end{theorem}

\begin{proof}
The first two hypotheses construct the local/factorization domain and its
curve shadow.  The hybrid hypothesis prevents loss of the positive
elliptic-degree sectors.  The Hall and orientation hypotheses give a
source for the product, super signs, protected integration, and geometric
reflection character.  The primitive certificate gives a homomorphism from
the abstract Gritsenko--Nikulin/Borcherds--Kac presentation to the compact
primitive quotient.  Generation gives surjectivity.  The relation,
parity-dimension, Hopf-pairing, and radical hypotheses rule out extra
kernel and invisible zero-superdimension root spaces.  Therefore the
compact primitive quotient is \(\gDelta\).  The denominator is then the
already fixed Borcherds--Gritsenko--Nikulin denominator.  The chiral claim
is exactly the assumed completed/coderived quasi-isomorphism
\(\Theta_{\operatorname{Kos}}\).
\end{proof}

This theorem is the strongest correct statement I can extract from the
local and cross-volume material.  It is a recognition theorem from a
supplied compact source and supplied comparison data.  It is not an
existence theorem for \(\AEX\).

\subsection{Exact missing objects, maps, obstructions, and tests}

\paragraph{Objects still missing.}
\begin{enumerate}
\item The compact source \(\AEX\in E_3\text{-}\operatorname{HolFA}_\Gamma(X)^\wedge\).
\item A chosen compact \(E_3\)-formality point and \(S^3\)-framing homotopy.
\item A compact BV/\(\hCS\) all-scale quantum package on \(K3\times E\).
\item Sectorial stability/HN data and finite quotients \(\mathsf F_R\AEX\).
\item Projection-finite local moduli \(\mathcal M^{\operatorname{loc}}\) and
wrapped elliptic moduli \(\mathcal M^{\operatorname{wr}}\).
\item Mixed local/wrapped extension stacks \(\mathfrak E^{\operatorname{hyb}}\).
\item The oriented compact Hall object \(\Hall^{\operatorname{or}}_{K3\times E}\).
\item Orientation lines \(\ell_\gamma\) with square-root and
Thom--Sebastiani coherence.
\item The protected integration map \(I^{\operatorname{prot}}_{\sigma,o}\).
\item The lifted Weyl action \(\rho_o\).
\item The completed chiral coalgebra \(C_X\) and the comparison
\(\Theta_{\operatorname{Kos}}\).
\item Primitive representatives \(e_i^X,f_i^X,h_i^X\) and parity data for
every real and imaginary simple root.
\end{enumerate}

\paragraph{Maps still missing.}
\begin{enumerate}
\item Restriction, disjoint-union product, and collision maps for \(\AEX\)
on finite HN quotients.
\item The specialization/pushforward
\[
        \Spch_{K3,E}(\AEX)\simeq (p_E)_*\AEX.
\]
\item Local-local, local-wrapped, and wrapped-wrapped Hall correspondences.
\item A protected integration map compatible with product, coproduct, and
completion.
\item The exterior-square compatible Weyl action on the oriented Hall object.
\item The bar map \(C_X\to\overline B_E^{\operatorname{ch}}(F_X)\) and
the cobar map \(\Omega_E^{\operatorname{ch}}C_X\to\DDelta\).
\item The presentation map from the abstract Borcherds--Kac algebra to the
compact primitive quotient.
\end{enumerate}

\paragraph{Obstructions to kill.}
\begin{enumerate}
\item Compact QME, anomaly, gauge-fixing, source/target descent, critical
atlas, stationary-phase, and vertex quasi-isomorphism defects.
\item Relative orientation, Thom--Sebastiani, grading/Tate, compact-support
Beck--Chevalley, Ran factorization, and completion defects.
\item The positive elliptic-degree locality obstruction \(p_E(C)=E\).
\item The non-additivity of active support and the resulting need for
finite-first HN quotients.
\item The quotient-order obstruction: reduced \(E\)-quotient before Hall
convolution forgets relative \(E\)-position.
\item The possible automorphic radical
\(\operatorname{Rad}_{\operatorname{Aut}}\) in the raw Hall algebra.
\item The \(\varprojlim^1\) obstruction in completed finite comparisons.
\item Parity invisibility: signed superdimension does not determine
\((\dim_{\bar0},\dim_{\bar1})\).
\end{enumerate}

\paragraph{Tests.}
\begin{enumerate}
\item \textbf{Stage-1 test.}  On every finite HN quotient, verify QME,
anomaly cancellation, descent, and \(E_3\)-operations before taking the
inverse limit.
\item \textbf{Formality/framing test.}  Separate the \(K3\times E\) Atiyah
class/formality witness from the compact quantum \(S^3\)-framing and
anomaly witnesses.  The former is not a substitute for the latter.
\item \textbf{Wrapped support test.}  Any operation placing positive
elliptic degree at a finite Ran point fails unless it is part of a
global or hybrid wrapped leg.
\item \textbf{Quotient-order test.}  Form Hall correspondences
\(E\)-equivariantly before reduced quotienting.
\item \textbf{Mixed associativity test.}  Compare the two push-pull
composites through two-step local/wrapped flag stacks.
\item \textbf{Orientation test.}  Compute determinant-line transport on
simple diagonal wall reflections and prove the Coxeter/Nikulin relations.
\item \textbf{Determinant shadow test.}  After integration, recover
\[
        \operatorname{den}(\gDelta)=64^{-1}\Delta_5(2Z),
        \qquad
        Z^{K3\times E}_{\operatorname{OP}}
        =-4096\,\Delta_5^{-2}.
\]
This test is necessary, not sufficient.
\item \textbf{Primitive box test.}  In small charge boxes, for example
\(0\le n,m\le 2\), \(|l|\le 4\), compute protected primitives, their
parity split, and their brackets.  Verify relations, not only
superdimensions.
\item \textbf{Chiral completion test.}  Check conilpotence, Mittag--Leffler
continuity, and coderived curvature control for \(C_X\) and \(\DDelta\).
\item \textbf{Raw Hall radical test.}  At finite height/charge cutoffs,
compute whether \(\operatorname{Rad}_{\operatorname{Aut},\le N,\le R}=0\).
The quotient theorem does not prove the raw compact Hall theorem.
\end{enumerate}

\subsection{Local anchors}

\begin{itemize}
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:108--115|:
the abstract already makes compact \(E_3\), Ran obstruction, and primitive
bracket recognition an open compact realization problem.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:126--209|:
claim-strength order: protected locality, compact/hybrid factorization,
primitive recognition, denominator, scalar square.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:906--956|:
protected Hall integration criterion and orientation monodromy open
problem.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:1962--1983|:
compact holomorphic \(E_3\) source open problem.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:2007--2048|:
Stage 2 is specialization, not inversion; target-internal bar--cobar does
not reconstruct the compact source.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:2073--2166|:
projection-finite and wrapped sectors, elliptic-degree obstruction, and
hybrid wrapped open problem.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:2182--2238|:
sectorial Hall truncation and finite charge-support Hall quotient are conditional on a
supplied oriented critical Hall object.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:2258--2341|:
compact Igusa realization datum.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:2344--2440|:
primitive recognition theorem and its ``what is not proved'' warning.
\item \verb|/Users/raeez/igusa-cusp-form/main.tex:2833--2882|:
Jacobi coefficients have three readings, none of which is an equality of
Hilbert spaces, brackets, or Hall constants.
\item \verb|/Users/raeez/igusa-cusp-form/agent_material/14_compact_E3_source_from_volumes_attack_heal.tex:16--33|:
previous compact-source attack: the volumes do not construct the compact
\(K3\times E\) source.
\item \verb|/Users/raeez/igusa-cusp-form/agent_material/14_ranE_hybrid_wrapping_from_volumes_attack_heal.tex:54--88|:
positive elliptic-degree support obstruction.
\item \verb|/Users/raeez/igusa-cusp-form/agent_material/14_ranE_hybrid_wrapping_from_volumes_attack_heal.tex:204--292|:
hybrid local/global wrapped factorization target shape.
\item \verb|/Users/raeez/igusa-cusp-form/agent_material/14_orientations_protected_integration_from_volumes_attack_heal.tex:86--148|:
type-correct orientation-character comparison.
\item \verb|/Users/raeez/igusa-cusp-form/agent_material/14_primitive_borcherds_recognition_from_volumes_attack_heal.tex:248--305|:
conditional primitive recognition theorem.
\item \verb|/Users/raeez/igusa-cusp-form/agent_material/14_chiral_bar_cobar_Koszul_realization_attack_heal.tex:157--189|:
\(\DDelta\) is the correct formal target, not the compact source.
\end{itemize}

\subsection{Cross-volume anchors}

\begin{itemize}
\item \verb|/Users/raeez/calabi-yau-quantum-groups/FRONTIER.md:27--31|:
two-stage factorization \(\Phi_d=\Sp\circ\PhiFA_d\); Stage 2 is
specialization, not inversion.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/FRONTIER.md:47--49|:
6d hCS gives an \(E_3\) witness on \(\mathbb C^3\) and records anomaly
vanishing on \(K3\times E\), but this is not the compact Hall source.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/FRONTIER.md:79--88|:
bracket-level BPS \(\cong\) BKM remains open.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/FRONTIER.md:679--690|:
CY-A\(_3\) remains conditional/witnessed; the \(K3\times E\) reduction is
a Heisenberg-to-Borcherds route on the principal locus, not a compact
hCS-to-Hall comparison.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/FRONTIER.md:730--740|:
center-hocolim obstruction and global braiding warning.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/theory/cy_to_chiral.tex:4--105|:
conditional two-stage theorem; \(K3\times E\) formal witness; Stage 2
requires Beck--Chevalley, Fubini/envelope, proper-support,
Tor-independence, compact-support, and completion.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/theory/cy_to_chiral.tex:128--165|:
CY-A\(_3\) object-level existence and rigidity require a formality point,
\(S^3\)-framing, anomaly-completion witness, and admissible specialization
datum; the theorem does not produce a global quantum group.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/theory/bps_positive_geometry_closure.tex:231--247|:
compact chamber existence certificate.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/theory/bps_positive_geometry_closure.tex:286--330|:
Igusa boundary is a quotient theorem modulo an automorphic radical; raw
Hall requires finite radical vanishing.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/theory/bps_positive_geometry_closure.tex:334--385|:
hCS--Hall descent has named obstruction classes.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/examples/k3_chiral_algebra.tex:48--67|:
\(G(K3\times E)\) and the Hall--Drinfeld/BKM object are conjectural or
conditional beyond the formal root datum and product-level evidence.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/theory/m3_b2_obstruction.tex:1--20|:
Stage-1 \(E_3\) construction requires \(S^3\)-framing of Hochschild data.
\item \verb|/Users/raeez/calabi-yau-quantum-groups/chapters/theory/m3_b2_obstruction.tex:969--990|:
\(\Delta_5\) is a one-loop-forced invariant, not a compact source object.
\item \verb|/Users/raeez/chiral-bar-cobar/CLAUDE.md:113--123|:
epistemic hierarchy: false claims must be repaired by verified smaller
theorems.
\item \verb|/Users/raeez/chiral-bar-cobar/chapters/theory/bar_cobar_adjunction_curved.tex:1040--1097|:
completed chiral bar--cobar is conditional on strong completion towers,
finite-stage acyclicity, and Mittag--Leffler control.
\item \verb|/Users/raeez/chiral-bar-cobar-vol2/CLAUDE.md:342--382|:
SC\({}^{\operatorname{ch,top}}\) and \(E_3\) are different objects; the
shadow arrow is Stage 1 to Stage 2, never back.
\item \verb|/Users/raeez/chiral-bar-cobar-vol2/FRONTIER.md:7--44|:
6d hCS \(E_3\) witness, trace identity, and retraction of native
curve-level \(E_n\)-chiral output.
\item \verb|/Users/raeez/chiral-bar-cobar-vol2/FRONTIER.md:58--68|:
Vol. II K3/BKM lane targets a Hall--Drinfeld double on a bi-based
Ran/\(\overline{\mathcal A_2}\) datum; direct Schur \(=1/\Delta_5\) and
plain K3 Yangian shortcuts are retracted.
\item \verb|/Users/raeez/topological-strings/CLAUDE.md:20--22|:
BCOV/topological-string comparison is heuristic and convention-checking
unless a local theorem proves a precise comparison.
\item \verb|/Users/raeez/topological-strings/main.tex:162--185|:
local holomorphic factorization sector; the surface model is not a
truncation of threefold BCOV.
\item \verb|/Users/raeez/topological-strings/main.tex:1223--1245|:
full factorization-center lift remains a problem even in the local model.
\item \verb|/Users/raeez/topological-strings/main.tex:2387--2398| and
\verb|/Users/raeez/topological-strings/main.tex:2467--2472|:
Costello/Costello--Li flat results do not prove the mixed or compact graph
realization needed here.
\end{itemize}

\subsection{Claim-status recommendations}

\begin{enumerate}
\item Keep the automorphic/BKM/OP scalar core as theorem-level.
\item State the compact \(E_3\) source as an open problem or as the first
hypothesis of the compact recognition theorem.
\item Use Vol. III's \(K3\times E\) formality and hCS material as
evidence for the shape of gate 1, not as construction of gate 1.
\item Make the hybrid wrapped factorization route primary.  The
projection-finite plus global Fock/Hecke route is weaker unless mixed
brackets and relative \(E\)-position are supplied.
\item Do not write \(\epsor=\nuDelta\) as a fact.  Write it as a
comparison theorem conditional on the oriented Hall object, Weyl lift, and
determinant-line monodromy computation.
\item Do not write
\[
        H^0\Primprot(F_X)=\gDelta
\]
without the full primitive presentation certificate.  Signed coefficients
are necessary shadows only.
\end{enumerate}

\subsection{Files changed}

\begin{itemize}
\item \verb|/Users/raeez/igusa-cusp-form/agent_material/15_compact_finite_first_E3_source_attack_heal.tex|
\end{itemize}

\subsection{Checks run}

\begin{itemize}
\item Verified current directory and branch with
\verb|pwd|, \verb|git branch --show-current|, and
\verb|git status --short --branch|.
\item Read local instructions:
\verb|CLAUDE.md|, \verb|AGENTS.md|,
\verb|/Users/raeez/ecosystem/INVARIANTS.md|, and
\verb|/Users/raeez/ecosystem/AGENTS-HARNESS.md|.
\item Searched and read local anchors in \verb|main.tex|, \verb|proj.bib|,
and \verb|agent_material/14_*.tex| using \verb|rg| and \verb|nl -ba|.
\item Searched and read cross-volume anchors in
\verb|/Users/raeez/calabi-yau-quantum-groups|,
\verb|/Users/raeez/chiral-bar-cobar|,
\verb|/Users/raeez/chiral-bar-cobar-vol2|, and
\verb|/Users/raeez/topological-strings|.
\end{itemize}

\subsection{Remaining open questions}

\begin{enumerate}
\item Can the compact \(K3\times E\) hCS/BV package be made all-scale and
anomaly-free on the exact finite-first HN tower needed by the Igusa charges?
\item What is the canonical stability/HN datum on the compact
\(K3\times E\) category whose finite quotients are compatible with both
the OP scalar chamber and the Borcherds chamber?
\item Is the wrapped elliptic-degree repair best implemented by a
two-colour hybrid Hall factorization theory, or by projection-finite Ran
locality plus a global Fock/Hecke module with nontrivial mixed brackets?
\item Does the automorphic radical in the raw compact Hall algebra vanish
on finite quotients, or is the quotient by
\(\operatorname{Rad}_{\operatorname{Aut}}\) the best theorem available?
\item Can the determinant-line monodromy on simple type-II reflections be
computed directly from compact extension stacks, producing
\(\epsor(s_{\delta_i})=-1\)?
\item Can one construct explicit compact primitive representatives in the
first nontrivial charge box and verify the Borcherds--Kac relations before
invoking any global denominator identity?
\end{enumerate}
