\section{Agent 15-B: Ran(\(E\)) elliptic-degree hybrid attack--heal}
\label{sec:agent15b-rane-elliptic-degree-hybrid}

\providecommand{\Z}{\mathbb Z}
\providecommand{\C}{\mathbb C}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\Supp}{\operatorname{Supp}}
\providecommand{\Ext}{\operatorname{Ext}}
\providecommand{\RHom}{\operatorname{RHom}}
\providecommand{\Fact}{\mathsf{Fact}}
\providecommand{\CoHA}{\operatorname{CoHA}}
\providecommand{\Hall}{\mathcal H}
\providecommand{\Perf}{\operatorname{Perf}}
\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\sdim}{\operatorname{sdim}}
\providecommand{\smult}{\operatorname{smult}}
\providecommand{\Spch}{\mathrm{Sp}^{\mathrm{ch}}}
\providecommand{\PhiFA}{\Phi^{\mathrm{FA}}}
\providecommand{\hCS}{\mathrm{hCS}}
\providecommand{\BV}{\mathrm{BV}}
\providecommand{\TS}{\mathrm{TS}}
\providecommand{\gDelta}{\mathfrak g_{\Delta_5}}
\providecommand{\nuDelta}{\nu_{\Delta_5}}
\providecommand{\epsor}{\epsilon_o}
\providecommand{\Mloc}{\mathcal M^{\mathrm{loc}}}
\providecommand{\Mwr}{\mathcal M^{\mathrm{wr}}}
\providecommand{\Mhyb}{\mathcal M^{\mathrm{hyb}}}
\providecommand{\Eloc}{\mathfrak E^{\mathrm{loc}}}
\providecommand{\Ewr}{\mathfrak E^{\mathrm{wr}}}
\providecommand{\Ehyb}{\mathfrak E^{\mathrm{hyb}}}
\providecommand{\Flaghyb}{\mathfrak{Flag}^{\mathrm{hyb}}}
\providecommand{\Den}{\mathsf{Den}}

\subsection{Claim attacked}

The attacked six-gate assertion is the unconditional compact construction
\[
\begin{gathered}
\mathcal A_X^{E_3}\ \hbox{on }X=K3\times E
\longrightarrow
\mathcal F_X\in\Fact(\Ran(E))
\longrightarrow
\Hall_X^{\mathrm{or}}
\\
\longrightarrow
I^{\mathrm{prot}},\ \epsor=\nuDelta,\quad
H^0\Prim_{\mathrm{prot}}(\mathcal F_X)/\operatorname{Rad}
\cong \gDelta ,
\end{gathered}
\]
with the hope that ordinary finite Ran locality on \(E\), perhaps with a
Fock product appended, supports the full Igusa product.

This assertion is false in its unconditional form.  The obstruction is
not a numerical mismatch.  It is a support-locality mismatch.  Ordinary
\(\Ran(E)\) factorization is a finite-support calculus.  Positive
elliptic degree is global over \(E\).  A compact source for the full
Igusa product must therefore use either a genuinely coupled
projection-finite/local plus global-mode theory, or a two-colour
local/global wrapped Hall factorization theory.  The second is the
stronger correct target.  It keeps the mixed extension problem visible.

The healed statement is:

\begin{quote}
If a compact \(K3\times E\) theory supplies a finite-first
holomorphic \(E_3\) source, a chain-level \(K3\)-to-\(E\)
specialization, and a hybrid Hall/factorization datum whose local,
wrapped, and mixed extension stacks are formed before the reduced
\(E\)-quotient, then its protected trace may be tested against the
Igusa determinant and its primitives may be tested against
\(\gDelta\).  No surveyed local or cross-volume source constructs this
datum.
\end{quote}

\subsection{Exact obstruction}

Let \(p_E:X=K3\times E\to E\).  Let \(C\subset X\) be a
one-dimensional subscheme with positive elliptic degree:
\[
        (p_E)_*[C]=b[E],\qquad b>0.
\]
Then \(p_E(C)=E\).  If \(p_E(C)\) were zero-dimensional, the pushforward
of the one-cycle \([C]\) would vanish.  Since \(E\) is irreducible, the
remaining possibility is the whole curve.

Consequences:
\begin{enumerate}
\item A projection-finite object can be localized over a finite subset
of \(E\), hence can live on \(\Ran(E)\).
\item A positive elliptic-degree object dominates \(E\), hence cannot
be inserted at finitely many Ran points.
\item The Borcherds \(s\)-variable records the OP elliptic-degree
direction after the variable conversion in the manuscript.  Therefore
the full \(s\)-direction is not a consequence of finite support on
\(\Ran(E)\).
\item If one reduces by the translation action of \(E\) before forming
extension correspondences, the relative \(E\)-position needed by mixed
Hall convolution has been destroyed.
\end{enumerate}

Thus ordinary disjoint-open factorization on \(\Ran(E)\) is only the
projection-finite part of the desired compact theory.  It cannot by
itself support the full product
\[
\Delta_5
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}.
\]

\subsection{Failed shortcuts}

\begin{enumerate}
\item \textbf{Finite Ran locality for the full product.}  False.
Finite Ran support cannot contain a class with positive pushforward to
\(E\).

\item \textbf{Projection-finite factorization plus a decoupled Fock
factor.}  Insufficient.  It can reproduce a product character while
leaving the mixed brackets between projection-finite charges and wrapped
elliptic-degree charges undefined or wrong.

\item \textbf{DMVV/Hecke exponents as Hall operators.}  Unsupported.
The formula \(f(nm,l)\) gives the \(K_0\)-level virtual exponent used by
the determinant.  A compact theorem needs actual Hecke or Fock functors,
their trace identity, and their compatibility with Hall convolution and
primitive projection.

\item \textbf{Reduced OP/DT quotient first, Hall algebra second.}
False as a construction principle.  The OP/DT quotient integration is
scalar.  Hall products require extension stacks before quotienting,
because mixed extensions remember relative position along \(E\).

\item \textbf{Formal current envelope as compact source.}  False.
\(\Den_{\Delta_5,E}\) is the target current envelope attached to the
known denominator algebra.  It does not construct \(K3\times E\)
moduli stacks, orientations, or collision maps.

\item \textbf{Bar--cobar inversion as source construction.}  False.
The chiral bar--cobar theorem inverts a supplied curve-level object in
the proper completed category.  It does not build the compact object
\(\mathcal F_X\) or the coalgebra \(C_X\).

\item \textbf{Borcherds product determines primitive recognition.}
False.  The product determines signed root supermultiplicities.  It
does not determine parity dimensions, simple representatives, Hall
structure constants, Serre/Borcherds relations, Hopf pairing, or the
radical quotient.

\item \textbf{Vol. III \(\PhiFA_3\) notation as an existence theorem
for this \(X\).}  False in this context.  Vol. III gives a two-stage
architecture and conditional comparison criteria.  The witnessed compact
Hall/factorization package for the Igusa realization remains open.
\end{enumerate}

\subsection{Strongest hybrid construction candidate}

Fix a compact stability/HN sector for a candidate \(K3\times E\) Hall
category \(\mathcal C_\sigma\), with charge lattice \(\Gamma\) and an
elliptic-degree map
\[
        b:\Gamma\to\Z_{\geq0}.
\]
Let \(\Gamma_{\mathrm{loc}}\) be the charges representable by
projection-finite objects over \(E\), and let
\(\Gamma_{\mathrm{wr}}\) be the charges with \(b(\eta)>0\).

\paragraph{Local stacks.}
For a small open \(U\subset E\) and
\(\alpha\in\Gamma_{\mathrm{loc}}\), define
\[
        \Mloc_\alpha(U)
        =
        \{A\in\mathcal C_\sigma\mid
        [A]=\alpha,\ \Supp A\subset p_E^{-1}(U)\}.
\]
For disjoint opens \(U_i\), the local Hall correspondence is
\[
\prod_i\Mloc_{\alpha_i}(U_i)
\xleftarrow{\ p\ }
\Eloc_{\alpha_1,\ldots,\alpha_r}(U_1,\ldots,U_r)
\xrightarrow{\ q\ }
\Mloc_{\alpha_1+\cdots+\alpha_r}(U_1\cup\cdots\cup U_r).
\]
This is the ordinary Ran/factorization sector.

\paragraph{Wrapped stacks.}
For \(\eta\in\Gamma_{\mathrm{wr}}\), define
\[
        \Mwr_\eta
        =
        \{W\in\mathcal C_\sigma\mid
        [W]=\eta,\ p_E(\Supp W)=E\},
\]
with a rigidified pre-quotient version \(\Mwr_\eta^{\mathrm{rig}}\)
whenever the \(E\)-translation action is present.  The rigidification
may be a chosen Abel--Jacobi center, determinant trivialization, or other
named device; the report does not assert that one is constructed.  It
records that some such pre-quotient memory is necessary.

The wrapped-wrapped Hall correspondence is global:
\[
\Mwr_{\eta_1}^{\mathrm{rig}}\times \Mwr_{\eta_2}^{\mathrm{rig}}
\xleftarrow{\ p\ }
\Ewr_{\eta_1,\eta_2}
\xrightarrow{\ q\ }
\Mwr_{\eta_1+\eta_2}^{\mathrm{rig}}.
\]
It is not a disjoint-open factorization operation.

\paragraph{Mixed stacks.}
For disjoint \(U_1,\ldots,U_r\subset E\), local charges
\(\alpha_i\), and one wrapped charge \(\eta\), define
\[
\prod_i\Mloc_{\alpha_i}(U_i)\times\Mwr_\eta^{\mathrm{rig}}
\xleftarrow{\ p\ }
\Ehyb_{\alpha_1,\ldots,\alpha_r;\eta}(U_1,\ldots,U_r)
\xrightarrow{\ q\ }
\Mwr_{\eta+\alpha_1+\cdots+\alpha_r}^{\mathrm{rig}}.
\]
Points of \(\Ehyb\) are exact triangles or exact sequences in
\(\mathcal C_\sigma\) with associated graded pieces the local
\(\alpha_i\)-objects and one wrapped \(\eta\)-object.  The output is
wrapped as soon as one input is wrapped.

Associativity requires flag stacks
\[
        \Flaghyb_{\alpha_1,\ldots,\alpha_r;\eta}
\]
classifying two-step and multi-step filtrations with the same associated
graded pieces.  The two pull-push composites attached to different
parenthesizations must agree after vanishing cycles, Thom--Sebastiani
transport, orientation signs, Tate shifts, and HN completion.

\paragraph{Hybrid factorization object.}
The candidate object is not an ordinary \(D\)-module on
\(\Ran(E)\).  It is a two-colour completed Hall/factorization datum
\[
\mathcal F_X^{\mathrm{hyb}}
=
\left(
\mathcal F_X^{\mathrm{loc}},
\mathcal G_X^{\mathrm{wr}},
\Eloc,\Ehyb,\Ewr,\Flaghyb,
o,\ I^{\mathrm{prot}}
\right),
\]
where \(\mathcal F_X^{\mathrm{loc}}\) is local on \(\Ran(E)\),
\(\mathcal G_X^{\mathrm{wr}}\) is global in the elliptic direction, and
\(\Ehyb\) is the mixed action/collision datum.  This is the minimal
shape that can support both the \(s\)-direction and a nontrivial
primitive Lie bracket.

\subsection{Maps, functors, and coherences needed}

The construction requires the following typed maps and functors.

\begin{enumerate}
\item A Stage-1 compact source
\[
        \mathcal A_X^{E_3}\in E_3\hbox{-}\mathrm{HolFA}(X)
\]
with QME, anomaly, descent, and charge-completion witnesses.

\item A Stage-2 specialization
\[
        \Spch_{K3,E}(\mathcal A_X^{E_3})
        \simeq (p_E)_*\mathcal A_X^{E_3}
\]
with Beck--Chevalley, Fubini/envelope, Tor-independence,
proper-support, compact-support, and completion data.

\item A support classifier
\[
        \operatorname{supp}_E:\mathcal C_\sigma
        \longrightarrow
        \{\hbox{projection-finite},\hbox{wrapped}\}
\]
compatible with exact triangles: an extension with a wrapped subquotient
is wrapped.

\item Compact extension correspondences \(\Eloc,\Ehyb,\Ewr\) and flag
correspondences \(\Flaghyb\), all finite type after sectorial HN
truncation and continuous after inverse limit.

\item Vanishing-cycle functors on all local, wrapped, and mixed critical
charts, with Thom--Sebastiani isomorphisms compatible with triple
extensions.

\item A strong orientation system \(o\), i.e. square roots of virtual
determinant lines for every local, wrapped, and mixed chart, with
coherent transport under restriction, direct sum, exact triangle, and
two-step flag composition.

\item A protected integration map
\[
        I^{\mathrm{prot}}:
        \widehat{\Hall}^{\mathrm{hyb},o}_{X,\sigma,S}
        \longrightarrow
        \widehat{\C[\Gamma_{\mathrm{eff}}]}
\]
compatible with product, coproduct, primitive projection, wall crossing,
and the reduced \(E\)-quotient.

\item If the global-mode route is used inside the hybrid datum, actual
Hecke/Fock functors \(\mathsf H_m\), not only formal exponents, with
\[
        [\mathsf H_m(\mathbb U)]_{n,l}=[\mathbb U_{nm,l}]
\]
in the relevant finite stage and with a trace whose determinant shadow is
the Igusa product.  These functors must act on, or be acted on by, the
projection-finite Hall sector through \(\Ehyb\).

\item A primitive functor
\[
        \Prim_{\mathrm{prot}}
        \left(\mathcal F_X^{\mathrm{hyb}}\right)
\]
defined after coproduct and completion, not merely after decategorified
trace.
\end{enumerate}

\subsection{Tests}

The following tests are necessary before promotion from programme to
theorem.

\begin{enumerate}
\item \textbf{Projection test.}  Prove that every local input has finite
image in \(E\), and that every positive elliptic-degree input is routed
to the wrapped colour.

\item \textbf{No illegal Ran insertion test.}  Any operation placing a
positive elliptic-degree object at finitely many Ran points is invalid
unless it factors through the wrapped colour.

\item \textbf{Quotient-order test.}  Construct \(\Eloc,\Ehyb,\Ewr\)
before quotienting by \(E\).  Then prove descent or equivariant
integration.  A quotient-first construction fails this test.

\item \textbf{Mixed \(\Ext\)-support test.}  For
\(A_i\in\Mloc_{\alpha_i}(U_i)\) and \(W\in\Mwr_\eta^{\mathrm{rig}}\),
compute the support of \(\RHom(A_i,W)\) and \(\RHom(W,A_i)\).  The
mixed correspondence must identify which local collisions are measured
and which global terms survive.

\item \textbf{Associativity test.}  Compare the two pull-push maps
through
\[
        \Flaghyb_{\alpha,\beta;\eta}.
\]
First combine \(\alpha,\beta\), then act on \(\eta\); compare with first
acting by \(\beta\), then by \(\alpha\).  Repeat for two wrapped legs.

\item \textbf{Orientation test.}  Verify square-root determinant-line
transport on local-local, local-wrapped, and wrapped-wrapped extension
stacks.  The signs must be compatible with Thom--Sebastiani
associativity.

\item \textbf{Hecke/Fock trace test.}  In finite HN boxes, compute the
trace of the proposed global modes and verify the exponent rule
\(f(nm,l)\).  A scalar equality after infinite completion is not enough.

\item \textbf{Scalar shadow test.}  The decategorified protected trace
must recover the theorem-level scalar identities:
\[
        \operatorname{den}(\gDelta)=64^{-1}\Delta_5(2Z),
        \qquad
        Z^{K3\times E}_{DT}=Z^{K3\times E}_{OP}
        =-4096\Delta_5^{-2}.
\]

\item \textbf{Primitive low-degree test.}  In the first finite charge
box, exhibit the compact primitive representatives corresponding to
\[
\delta_i,\qquad \delta_i+\delta_j,\qquad
\delta_1+\delta_2+\delta_3,
\]
and verify the signed dimensions \(1,10,-64\) in the manuscript's
normalization, then check the brackets.  Dimensions alone do not pass.

\item \textbf{Borcherds relations test.}  Verify Cartan, Chevalley, real
Serre, imaginary orthogonality, generation, Hopf pairing, and radical
quotient for the compact primitive bracket.
\end{enumerate}

\subsection{Interaction with the six gates}

\paragraph{Gate 1: compact finite-first holomorphic \(E_3\) source.}
The hybrid repair cannot begin from the determinant.  It needs the
Stage-1 object \(\mathcal A_X^{E_3}\) and its charge/HN completion.
Vol. III's two-stage formalism supplies the correct grammar, but the
Igusa paper correctly treats \(\PhiFA_3(X)\) as a placeholder unless the
chain-level object, QME, anomaly, descent, and completion witnesses are
supplied.

\paragraph{Gate 2: Ran(\(E\)) elliptic-degree obstruction.}
Ordinary Ran locality is false for the full object.  The best correct
repair is the hybrid datum above.  Projection-finite plus global
Fock/Hecke modes is acceptable only if those modes are coupled to the
local sector through mixed Hall correspondences.  A decoupled product is
only a determinant-level repair.

\paragraph{Gate 3: oriented compact Hall/CoHA atlas.}
The Hall atlas must be built before reduction by \(E\) and must include
local, wrapped, and mixed stacks.  A Hall atlas only for scalar reduced
OP/DT invariants is insufficient.  The mixed extension stacks are part
of the atlas, not an optional comparison map.

\paragraph{Gate 4: protected integration and orientation character.}
Protected integration must be a morphism out of the hybrid completed
Hall object.  It must preserve product, coproduct, primitive projection,
and wall crossing.  The orientation character is defined only after a
strong orientation and a lifted Weyl action on this oriented completed
object have been constructed.

\paragraph{Gate 5: \(\epsor=\nuDelta\).}
The equality is type-correct only after the Hall-side character
\(\epsor\) exists.  The hybrid construction contributes the relevant
normal modes: local real-root walls, wrapped elliptic-degree movement,
and mixed extension signs.  The constants \(64\) and \(-4096\) do not
compute these signs.

\paragraph{Gate 6: primitive recognition.}
The hybrid mixed brackets are essential.  Without them one may recover
the signed product exponents while producing the wrong Lie
superalgebra.  The primitive theorem needs full parity dimensions,
simple representatives, Borcherds--Kac relations, Hopf pairing, and the
same radical quotient as the Gritsenko--Nikulin algebra.

\subsection{Local anchors}

\begin{itemize}
\item \verb|main.tex:167--186|: compact/hybrid factorization is stated
as open; positive elliptic degree requires global Fock/Hecke or hybrid
wrapped data.
\item \verb|main.tex:329--364|: the physical-question section gives the
projection-finite versus wrapped obstruction.
\item \verb|main.tex:511--631|: the Fock trace and virtual determinant
are \(K_0\)-level constructions and do not supply locality or operator
products.
\item \verb|main.tex:906--933|: protected Hall integration is a
criterion requiring oriented extension correspondences, HN completion,
primitive projection, and Weyl action.
\item \verb|main.tex:960--1051|: the OP elliptic-degree variable maps to
the Borcherds \(s\)-variable and the scalar square is an OP theorem.
\item \verb|main.tex:1911--1983|: the holomorphic \(E_3\) source and
chain-level \(K3\)-to-\(E\) specialization are open data.
\item \verb|main.tex:2073--2166|: projection-finite/wrapped sectors,
elliptic-degree locality obstruction, repair alternatives, and the
hybrid wrapped factorization open problem.
\item \verb|main.tex:2182--2256|: sectorial HN truncation gives finite
quotients only after the Hall object and correspondences are supplied.
\item \verb|main.tex:2258--2342|: compact Igusa realization datum.
\item \verb|main.tex:2344--2440|: primitive recognition is conditional;
signed dimensions are necessary shadows, not sufficient data.
\item \verb|agent_material/14_ranE_hybrid_wrapping_from_volumes_attack_heal.tex|:
ordinary Ran locality for the full product is false; hybrid wrapping is
the correct target shape, open.
\item \verb|agent_material/14_compact_E3_source_from_volumes_attack_heal.tex|:
the compact \(E_3\) source is not constructed by the surrounding
volumes.
\item \verb|agent_material/14_orientations_protected_integration_from_volumes_attack_heal.tex|:
\(\epsor=\nuDelta\) is an open orientation-monodromy comparison.
\item \verb|agent_material/14_primitive_borcherds_recognition_from_volumes_attack_heal.tex|:
primitive recognition requires presentation-level data.
\item \verb|agent_material/14_chiral_bar_cobar_Koszul_realization_attack_heal.tex|:
bar--cobar technology is target-internal unless the compact source
coalgebra is supplied.
\item \verb|agent_material/14_boundary_rows_physical_hosts_from_volumes_attack_heal.tex|:
automorphic and denominator row data do not give compact physical hosts.
\end{itemize}

\subsection{Cross-volume anchors}

\begin{itemize}
\item \verb|calabi-yau-quantum-groups/chapters/theory/cy_to_chiral.tex:4--23|:
Vol. III states the two-stage assignment
\(\Phi_d=\Spch\circ\PhiFA_d\).
\item \verb|calabi-yau-quantum-groups/chapters/theory/cy_to_chiral.tex:90--104|:
Stage 2 needs Beck--Chevalley, Fubini/envelope, proper-support,
Tor-independence, compact-support, and completion witnesses.
\item \verb|calabi-yau-quantum-groups/chapters/theory/cy_to_chiral.tex:128--165|:
CY-A\(_3\) existence is conditional on witnessed formality, framing,
anomaly-completion, and specialization data.
\item \verb|calabi-yau-quantum-groups/chapters/theory/bps_positive_geometry_closure.tex:231--247|:
compact chamber existence requires stability, support, HN control,
orientation, critical atlas, motivic integration, and realization maps.
\item \verb|calabi-yau-quantum-groups/chapters/theory/bps_positive_geometry_closure.tex:286--330|:
the Igusa boundary statement is a quotient theorem by an automorphic
radical, not the raw compact Hall theorem.
\item \verb|calabi-yau-quantum-groups/chapters/theory/bps_positive_geometry_closure.tex:334--385|:
hCS--Hall descent has explicit MC, orientation, grading,
Thom--Sebastiani, Ran, compact-support, and completion obstructions.
\item \verb|calabi-yau-quantum-groups/chapters/theory/cy3_chain_level_bridge.tex:437--490|:
the Hall-valued factorization-cosheaf target is a full DWR/Ran nerve
object with orientation and TS coherences.
\item \verb|calabi-yau-quantum-groups/chapters/theory/cy3_chain_level_bridge.tex:522--700|:
the oriented hCS--Hall comparison theorem constructs no datum; it proves
sufficiency after orientation, trace, twist, completion, product, and
coherence are supplied.
\item \verb|calabi-yau-quantum-groups/chapters/examples/k3e_bkm_chapter.tex:13977--14054|:
the six \(K3\times E\) routes converge only conditionally through a
completed Hall--Drinfeld/Borcherds package.
\item \verb|calabi-yau-quantum-groups/chapters/examples/k3e_bkm_chapter.tex:14082--14106|:
the character \(-\Delta_5^{-2}\) is numerical theorem-grade; its compact
critical-CoHA interpretation is conditional.
\item \verb|chiral-bar-cobar/CLAUDE.md:56--63|:
Vol. I bar--cobar is the \(E_1\)-chiral shadow after Stage-2
specialization, not the compact \(E_3\) source.
\item \verb|chiral-bar-cobar/compute/lib/theorem_universal_chiral_genus_extension_engine.py:735--747|:
factorization-envelope methods start from a Lie conformal algebra and do
not directly produce higher-genus/global data.
\item \verb|chiral-bar-cobar-vol2/CLAUDE.md:348--385|:
Stage 2 is specialization, never inversion.
\item \verb|chiral-bar-cobar-vol2/chapters/theory/factorization_swiss_cheese.tex:35--58|:
the local operadic shadow does not determine the global Ran object,
periods, monodromy, or factorization pattern.
\item \verb|topological-strings/main.tex:625--633|:
the local exact Fukaya model explicitly contains no wrapped generators
at infinity.
\item \verb|topological-strings/main.tex:2469--2475|:
Costello--Li flat anomaly cancellation is a source theorem and model,
not an automatic compact transfer.
\end{itemize}

\subsection{Status recommendation for \texttt{main.tex}}

The current manuscript direction is correct: theorem-level content is
the virtual determinant, the Gritsenko--Nikulin/Borcherds denominator
identity, and the OP scalar square; compact realization remains a
recognition programme.

The recommended sharpening is to state the gate-2 repair as a definition
or open problem, not as an informal alternative:

\begin{quote}
A hybrid wrapped factorization datum for \(K3\times E\) consists of
projection-finite local moduli \(\Mloc\), wrapped elliptic-degree moduli
\(\Mwr\), mixed extension stacks \(\Ehyb\), wrapped-wrapped stacks
\(\Ewr\), flag stacks \(\Flaghyb\), strong orientations, and protected
integration, all formed before the reduced \(E\)-quotient and continuous
for the sectorial HN completion.  It is a compact realization input.
It is not constructed by the Igusa determinant or by the OP scalar
square.
\end{quote}

The projection-finite plus global Fock/Hecke route should be presented
as a weaker determinant-level architecture unless mixed action stacks
are included.  The hybrid route is the canonical programme for a
future primitive theorem because it can see the local-wrapped brackets.

\subsection{Claim-status conclusion}

\[
\boxed{
\begin{array}{l}
\text{Finite Ran locality for the full Igusa product: false.}\\
\text{Projection-finite local sector: plausible only after the Hall
source is supplied.}\\
\text{Decoupled global Fock/Hecke factor: determinant-level only.}\\
\text{Coupled global modes through mixed Hall action: conditional.}\\
\text{Hybrid local/global wrapped factorization: correct target shape,
open.}\\
\text{Compact primitive realization of }\gDelta\text{: open.}
\end{array}}
\]

\subsection{Open questions}

\begin{enumerate}
\item What is the correct compact category \(\mathcal C_\sigma\) whose
objects realize both projection-finite vertical sectors and wrapped
elliptic-degree sectors?
\item What rigidification of \(\Mwr_\eta\) retains enough relative
\(E\)-position before reduced quotienting?
\item Are mixed \(\Ext\)-groups between projection-finite and wrapped
objects finite type after sectorial HN truncation?
\item Does the wrapped-wrapped Hall product admit a continuous
completion compatible with the Borcherds chamber
\(0<|s|\ll |q|\ll |r|^{-1}\ll1\)?
\item Can actual Hecke/Fock functors be constructed whose \(K_0\)
trace gives \(f(nm,l)\), and do they act through the mixed extension
stacks?
\item Does the determinant-line orientation on \(\Ehyb\) produce the
Maass sign on the type-II real-root reflections?
\item In the first nontrivial wrapped box, can one compute compact
primitive brackets and see the Gritsenko--Nikulin constants rather than
only the signed dimensions?
\end{enumerate}

\subsection{Files changed}

Only this file was written:
\verb|agent_material/15_RanE_elliptic_degree_hybrid_attack_heal.tex|.

\subsection{Checks run}

Read local instructions, \verb|main.tex|, \verb|proj.bib|, all six
\verb|agent_material/14_*| reports, and the cross-volume anchors listed
above.  Ran
\begin{verbatim}
git diff --check -- agent_material/15_RanE_elliptic_degree_hybrid_attack_heal.tex
\end{verbatim}
with clean output.  Checked the assigned-file worktree status; the file
is untracked and no manuscript source or generated PDF was edited by this
agent.
