% !TEX root = main.tex
\documentclass[11pt]{memoir}
\usepackage{raeez-math-template}
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\theHsection}{\arabic{section}}

\title{\texorpdfstring{\textit{The Igusa Square Root}\\[0.5em]\small The Borcherds determinant of \(\phi_{0,1}\), its denominator algebra, and the \(K3\times E\) realization problem}{The Igusa Square Root: The Borcherds determinant of phi\_0,1, its denominator algebra, and the K3 x E realization problem}}
\author{Raeez Lorgat}
\date{April 2026}

%\usepackage{natbib}
% theorem environments provided by raeez-math-template

\newcommand{\Imag}{\mathrm{Im}}
\newcommand{\Real}{\mathrm{Re}}
\newcommand{\Proj}{\mathbb{P}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}} \newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}} \newcommand{\La}{\Lambda}
\newcommand{\HypPlan}{\Lambda^{(1,1)}}
\newcommand{\Sp}{\mathbf{Sp}}
\newcommand{\PSp}{\mathbf{PSp}}
\newcommand{\GL}{\mathbf{GL}}
\newcommand{\SL}{\mathbf{SL}}
\newcommand{\Orth}{\mathbf{O}}
\newcommand{\SO}{\mathbf{SO}}
\newcommand{\Hpl}{\mathbb{H}}
\newcommand{\IV}{\mathbf{IV}}
\newcommand{\fbasis}{(f_i)_{\{1,2,3,-2,-1\}}}
\newcommand{\Id}{\mathbf{I}}
\newcommand{\Cone}{\mathcal{C}}
\newcommand{\Poly}{\mathcal{P}}
\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\bkm}{\mathfrak{g}}
\newcommand{\sdim}{\operatorname{sdim}}
\newcommand{\sch}{\operatorname{sch}}
\newcommand{\sdet}{\operatorname{sdet}}
\newcommand{\rootmult}{\operatorname{mult}}
\newcommand{\smult}{\operatorname{smult}}
\newcommand{\Prim}{\operatorname{Prim}}
%\newcommand{\bkm}{\mathfrak{g}_{\begin{pmatrix}2 & -2 & -2 \\
%-2 & 2 & -2\\
%-2 & -2& 2\end{pmatrix}}}
\newcommand{\autcor}{\mathfrak{g}_{\Delta_5}}

\ifdefined\mainpreambleonly
  \expandafter\endinput
\fi

\begin{document}

\maketitle

\begin{abstract}
For \(X=K3\times E\) the theorem-level physical input used here is the
protected index.  Right-moving localization in the K3 Ramond sector gives
\[
Z_{\mathrm{K3}}=2\phi_{0,1},\qquad
\phi_{0,1}=\sum f(n,l)q^nr^l.
\]
Replacing the protected K3 index by its Borcherds half produces only a
virtual \(K_0\)-determinant package.  It does not produce a microscopic
Hilbert space.  Unitarity is used to localize the right-moving K3
supertrace before the index is taken; the index itself is a charge-graded
virtual object that no longer requires Hilbert positivity.  For virtual super vector spaces
\(\mathbb U_{n,l}\) with \(\sdim\mathbb U_{n,l}=f(n,l)\), set
\(\mathcal V_{(n,l,m)}=\mathbb U_{nm,l}\).  In the Borcherds cusp
chamber the determinant is
\[
\mathcal D_X(Z)
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}
=\Delta_5(Z).
\]
The constant \(64\) is the theta-constant normalization
\([q^{1/2}r^{1/2}s^{1/2}]\Delta_5=64\); hence the monic Borcherds
product is \(D_5=64^{-1}\Delta_5\).

The same coefficients are the signed root supermultiplicities in the
Gritsenko--Nikulin Borcherds--Kac--Moody denominator algebra.  Under
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}
\]
one has
\[
\operatorname{den}(\mathfrak g_{\Delta_5})
=64^{-1}\Delta_5(2Z),\qquad
\smult\mathfrak g_{\Delta_5,\alpha(n,l,m)}=f(nm,l)
\]
on the active support.  Thus the denominator algebra supplies the
algebraic square root target and its target-internal Borcherds bracket.
It does not supply a compact BPS Hilbert space, compact Hall
correspondences, an orientation, or a BPS operator product/local
collision map.

The square root in the title is meant in Dirac's sense.  The scalar
OP/DT branch \(Z^X_{\mathrm{OP/DT}}=-4096\,\Delta_5^{-2}\) is
orientation-forgetful: the sign character is squared away.  The
recognition target is a first-order protected operator/algebra
\(\mathfrak D_X\) whose protected Pfaffian, after a supplied
Pfaffian-to-automorphic line comparison, is \(\Delta_5\), and whose scalar trace
\(\operatorname{Tr}_{\mathrm{prot}}((-1)^F\mathfrak D_X^{-2})
=-4096\,\Delta_5^{-2}\); the orientation/Pfaffian datum is the
algebraic input that distinguishes \(\Delta_5\) from \(-\Delta_5\) and
that the squared scalar cannot recover.  Constructing
\(\mathfrak D_X\) is the open recognition problem; this paper formulates
the target and the orientation-character constraint
\(\epsilon_o=\nu_{\Delta_5}\) on
\(W^{(2)}(\Lambda_{II}^{2,1})\).

The scalar Behrend-weighted branch is imported from
Oberdieck--Pixton, Oberdieck--Pandharipande, and Oberdieck.  In OP's
normalization \(\chi_{10}^{\mathrm{OP}}=D_5^2\), so
\[
\chi_{10}^{\mathrm{OP}}=(64^{-1}\Delta_5)^2
=4096^{-1}\Delta_5^2,\qquad
Z^X_{\mathrm{DT}}=Z^X_{\mathrm{OP}}
=-\left(\chi_{10}^{\mathrm{OP}}\right)^{-1}
=-4096\,\Delta_5^{-2}.
\]
The factor \(4096=64^2\) is a normalization conversion; the minus sign is
the OP scalar convention.  Neither fixes the automorphic reflection
character or the compact orientation monodromy.

A compact realization would have to begin with an additive formal dyonic
charge lattice \(\Gamma_X^{\mathrm{form}}\), its algebraic/effective Hall
support, the Gram map
\(\Pi_X:\Gamma_X^{\mathrm{form}}\to\Gamma_{\mathrm{gram}}\), and a
holomorphic \(E_3\)-factorization algebra on \(K3\times E\).  The formal
lattice is \(\Lambda_S\oplus\Lambda_S\).  The algebraic even Mukai sector
relevant to the OP/DT D6--D2--D0 branch, and its stability-dependent
effective semigroup, are smaller inputs; the present construction does
not assert that every formal full-Mukai class is a compact Hall state.
The triple \((n,l,m)\in\Gamma_{\mathrm{gram}}\) records Gram-degree
invariants \((Q^2/2,Q\cdot P,P^2/2)\) of a formal pair \(c=(Q,P)\); it is
not the additive Hall grading itself.  The Gram map is quadratic:
\[
\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c').
\]
Thus strict fixed-lift raw Gram descent cannot carry the type-II
real-root brackets.  The first
structural correction is the normal-ordered extension
\[
\widehat\Gamma_X=\Gamma_X^{\mathrm{form}}\oplus_B\Gamma_{\mathrm{gram}},
\qquad
\overline\Pi_X(c,T)=\Pi_X(c)-T,
\]
for which \(\overline\Pi_X\) is additive.  A compact realization would
then require a specified formality point, model-dependent
homotopy/framing datum, quantum master equation, anomaly control,
descent, and finite-first HN completion.  It would then
specialize along the K3 direction to a chiral object on
\(\operatorname{Ran}(E)\), solve the
\(\operatorname{Ran}(E)\)-support-locality obstruction in the
K3-integrated chiral shadow by mixed local/wrapped correspondences, and
identify the Gram-descended protected primitive bracket with
\(\mathfrak g_{\Delta_5}\).  This paper proves the virtual
determinant, the lattice normal-ordering theorem, and the fixed-lift
raw-descent obstruction; records the imported scalar and denominator
theorems; and
formulates that compact Hall/factorization realization as an open
recognition problem.  The final part records the eight Clery--Gritsenko
diagonal-divisor rows and the certificate required before any boundary
row becomes a physical host.
\end{abstract}

\bigskip
\tableofcontents

\section{Introduction and claim strength}
\label{sec:introduction-claim-strength}

The local object comes first.  A compact BPS theory on
\(X=K3\times E\), if it exists in the form needed here, should produce
protected local observables before any trace is taken.  After twisting
and passing to the protected index, the positive Hilbert space has
collapsed to a charge-graded virtual object, but locality has not
disappeared: disjoint insertions must still factorize and collisions
must remember extensions.
Throughout the compact-realization problem, \(S\) is a smooth complex
K3 surface and \(E\) is a smooth elliptic curve; singular K3 limits,
nodal elliptic limits, imprimitive curve-class contributions, the
\(s=0\) compact Hall cusp, and multi-component charge closures are
deferred boundary problems, not standing hypotheses.

Thus the exposition follows the dependency chain
\[
\begin{array}{rcl}
\hbox{protected K3 index} & \rightsquigarrow_{\mathrm{computes}} &
\hbox{virtual }K_0\hbox{-determinant},\\
\hbox{Borcherds--Gritsenko--Nikulin} & \rightsquigarrow_{\mathrm{imports}} &
\hbox{denominator target},\\
\hbox{formal Mukai charge and }B & \rightsquigarrow_{\mathrm{proves}} &
\hbox{normal-ordered Gram map},\\
\hbox{supplied finite Hall--Dirac source} & \rightsquigarrow_{\mathrm{conditional}} &
\hbox{primitive recognition},\\
\hbox{Oberdieck--Pixton/Oberdieck} & \rightsquigarrow_{\mathrm{checks}} &
\hbox{orientation-forgetful scalar square},\\
\hbox{Clery--Gritsenko rows} & \rightsquigarrow_{\mathrm{certificate}} &
\hbox{boundary host tests}.
\end{array}
\]
The scalar OP/DT equality is a check on the square of a supplied
first-order Pfaffian object.  It is not an input to the compact Hall
source, the Pfaffian line, or primitive recognition.
\paragraph{Protected locality.}
The protected index is theorem-level.  Right-moving localization of the
unitary K3 sigma model gives
\[
Z_{\mathrm{K3}}=2\phi_{0,1},\qquad
\phi_{0,1}=\sum f(n,l)q^nr^l.
\]
The half-index used by the Borcherds lift is represented only in
\(K_0(\mathrm{sVect}_{\mathrm{fd}})\).  Its coefficients are signed
superdimensions, not dimensions of a constructed compact D-brane Hilbert
space.

\paragraph{Compact and hybrid factorization.}
A compact realization would first supply the formal dyonic lattice, the
algebraic/effective Hall support inside it, the non-additive Gram map
\(\Pi_X:\Gamma_X^{\mathrm{form}}\to\Gamma_{\mathrm{gram}}\), and a
charge-completed holomorphic \(E_3\)-factorization algebra
\[
\mathcal A^{E_3}_X,\qquad X=K3\times E,
\]
then a chain-level K3-to-\(E\) specialization
\[
\mathcal F_X^{(0)}\simeq
\mathrm{Sp}^{\mathrm{ch}}_{K3,E}(\mathcal A^{E_3}_X)
\in\mathrm{Fact}(\operatorname{Ran}(E)).
\]
This projection-finite chiral shadow is not reconstructed from the
scalar partition function or from the Borcherds product.  The full
object is the hybrid \(\mathcal F_X^{\mathrm{hyb}}\) only after the
finite hybrid certificate is supplied.  There is also a geometric
obstruction: a
one-dimensional subscheme with positive elliptic degree projects onto
all of \(E\).  Hence a naive support-local object on
\(\operatorname{Ran}(E)\) sees only projection-finite sectors.  The full
Igusa \(s\)-direction requires finite-stage local/wrapped correspondence
data for positive elliptic degree: the elliptic-degree map \(b_R\),
rigidified wrapped prequotients with anchors, local-local, ordered
local/wrapped, and wrapped-wrapped extension stacks, the eight-word
two-step binary flag atlas,
quotient-after-correspondence descent, and protected integration with
trace degree \(s^{b_R}\).  A detached global Hecke/Fock factor is only a
determinant-level repair.  It becomes relevant to the compact
realization only after it is represented by those wrapped prequotients
and acts through mixed Hall correspondences before the reduced
\(E\)-quotient.  This is open.

\paragraph{Primitive recognition.}
Until Definition~\ref{def:dyonic-mukai-lattice}, the notation
\(\Gamma_X^{\mathrm{phys}}\) denotes the same formal full-Mukai
bookkeeping lattice later written
\(\Gamma_X^{\mathrm{form}}\); the superscript is mnemonic and not the
four-dimensional \(\mathcal N=4\) electric--magnetic charge lattice.
The microscopic algebra sought from such a compact realization is first
the upstairs protected primitive bracket
\[
[\ ,\ ]:\Prim_{c}^{\mathrm{prot}}(\mathcal F_X)
\otimes
\Prim_{c'}^{\mathrm{prot}}(\mathcal F_X)
\longrightarrow
\Prim_{c+c'}^{\mathrm{prot}}(\mathcal F_X),
\qquad c,c'\in\Gamma_X^{\mathrm{phys}}.
\]
The recognition criterion proved later is conditional: it specifies the
certificate and its consequences.  If the
Dirac--Igusa certificate \(\mathfrak K_X\) exists, including the oriented Hall object,
protected integration, cocycle-corrected Gram descent
\(\overline\Pi_{X,*}^{\Theta}\), a conilpotent source coalgebra \(C_X\)
with finite source filtration and collision coproduct, the bar comparison
\(b_X\), the cobar map
\(\Theta_{\mathrm{Kos}}\), Koszul Mittag--Leffler exactness for the
completed bar/cobar inverse system, presentation-level primitive Lie
comparison, no-extra-relations theorem, completed PBW compatibility,
exact triangular completion/\(\lim^1\)-vanishing, and radical quotient,
then
\[
H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^{\Theta}\mathcal F_X)
\cong
\mathfrak g_{\Delta_5}
\]
and the supplied chiral cobar comparison identifies
\(\Omega_E^{\mathrm{ch}}C_X\) with the formal current envelope
\(\mathsf{Den}_{\Delta_5,E}\).  This is a recognition criterion, not an
existence theorem and not a reconstruction from the determinant.

\paragraph{Borcherds denominator.}
The target algebra is imported from the Borcherds--Gritsenko--Nikulin
construction.  With
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2},
\]
the visible active coefficients satisfy
\[
\smult\mathfrak g_{\Delta_5,\alpha(n,l,m)}=f(nm,l),\qquad
\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z).
\]
This determines signed root supermultiplicities and the denominator
identity.  It does not determine compact Hall constants.

\paragraph{OP scalar square.}
The reduced scalar branch is imported from
Oberdieck--Pixton, Oberdieck--Pandharipande, and Oberdieck:
\[
Z^X_{\mathrm{DT}}(T,Q,P)=Z^X_{\mathrm{OP}}(P,Q,T)
=-4096\,\Delta_5(Z)^{-2}.
\]
The constants are fixed once.  The theta-constant form satisfies
\[
[q^{1/2}r^{1/2}s^{1/2}]\Delta_5=64,\qquad
D_5=64^{-1}\Delta_5.
\]
OP's monic product is \(\chi_{10}^{\mathrm{OP}}=D_5^2\), hence
\[
\chi_{10}^{\mathrm{OP}}=4096^{-1}\Delta_5^2,\qquad
Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1}
=-4096\Delta_5^{-2}.
\]
The number \(64\) is a theta-leading coefficient.  The number
\(-4096\) is the OP scalar normalization.  Neither proves the compact
orientation character.  The comparison
\[
\epsilon_o=\nu_{\Delta_5}
\]
between geometric orientation monodromy and the automorphic reflection
character remains part of the open Dirac--Igusa realization certificate.

\paragraph{Eight-row host certificates.}
The diagonal-divisor boundary problem concerns the eight
Clery--Gritsenko forms
\[
\Delta_5,\Delta_2,\Delta_1,\Delta_{1/2},
\nabla_3,\nabla_2,\nabla_{3/2},Q_1 .
\]
Rows \(1\)--\(4\) have Gritsenko--Nikulin denominator theorems.  Rows
\(5\)--\(8\) have Clery--Gritsenko products and Govindarajan CHL/WKB
denominator theorems; \(F_7=\nabla_{3/2}\) is on the required
\(\mu_4\)-multiplier cover.  A physical host for any boundary row
requires a certificate fixing the modular group or cover, character,
divisor, cusp Jacobi inputs, product lattice, Weyl vector, real roots,
reflection character, physical charge lattice, protected Gram-index,
orientation, reduced scalar theorem if one is claimed, and
primitive algebra comparison.  Without that certificate the row is only
an automorphic product plus any separately proved denominator theorem.

\begin{center}
\small
\begin{tabular}{p{0.23\textwidth}p{0.25\textwidth}p{0.41\textwidth}}
\hline
Structural level & Claim strength & Content \\
\hline
Virtual determinant &
proved here from \(K_0\) data plus imported Borcherds product &
\(\mathcal D_X=\Delta_5\).  No canonical half-Hilbert space or operator
product is constructed. \\
Scalar Behrend square &
imported theorem &
Oberdieck--Pixton, Oberdieck--Pandharipande, and Oberdieck give
\(Z^X_{\mathrm{DT}}=Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2}\) in the
reduced quotient-by-\(E\), Behrend-weighted setting. \\
BKM denominator &
imported theorem &
Gritsenko--Nikulin give \(\mathfrak g_{\Delta_5}\) and
\(\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z)\). \\
Compact Hall/factorization realization &
conditional/open &
If \(\mathfrak K_X\) exists, the primitive and chiral comparisons follow
by the recognition criterion.  Existence, \(\operatorname{Ran}(E)\)
hybrid locality,
protected integration, and orientation monodromy are open. \\
Eight-row host certificates &
framework; mostly open &
The catalogue and denominator rows are imported where cited.  Physical
row maps and scalar squares require row-by-row certificates. \\
\hline
\end{tabular}
\end{center}

\paragraph{Status and dependencies of results.}
The manuscript uses the words proved, computed, imported, certificate,
conditional, conjectural, open, and obstructed in the following strict
sense.  A proved statement is established in the paper; a computed
statement is verified by the displayed calculation or script; an imported
statement is a cited theorem; a certificate is a finite list of data and
tests; a conditional statement follows after the certificate is supplied;
an open statement names missing construction data.

\begin{center}
\small
\begin{tabular}{p{0.20\textwidth}p{0.18\textwidth}p{0.52\textwidth}}
\hline
Result & Status & Dependencies and exclusions \\
\hline
Protected K3 index and \(K_0\) half-index &
proved/imported/defined &
Right-moving localization gives
\(Z_{\mathrm{K3}}=2\phi_{0,1}\).  The half-index
\(\mathbb U_{n,l}\) is an arbitrary \(K_0\)-representative with
\(\sdim\mathbb U_{n,l}=f(n,l)\), not a canonical half-Hilbert space,
operator product, or compact D-brane state space. \\
Virtual determinant \(\mathcal D_X=\Delta_5\) &
computed/imported &
Computed from the \(K_0\)-half-index and identified with the
theta-normalized Borcherds product by the imported
Borcherds--Gritsenko--Nikulin theorem.  No compact Hilbert space,
operator product, or Pfaffian line is supplied. \\
Lattice normal ordering &
proved &
The formal Mukai lattice, cocycle \(B\), central extension
\(\widehat\Gamma_X\), and homomorphism \(\overline\Pi_X\) are proved
lattice algebra.  Algebraic/effective Hall support is open. \\
Raw Gram descent &
proved obstruction &
Strict homogeneous fixed-lift raw \(\Pi_X\)-pushforward cannot realize
the type-II real-root strings.  Fibre-summed raw descent over different
lifts is open. \\
Denominator algebra &
imported &
Gritsenko--Nikulin give \(\mathfrak g_{\Delta_5}\) and
\(\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z)\). \\
Compact Dirac--Igusa source &
certificate/conditional/open &
The \(D_0\)-stage, strong orientation, Weyl cocycle, type-II Pfaffian
wall model, hybrid wrapped factorization, source Koszul comparison, and
primitive recognition are certificate data.  The consequences are
conditional on these data, Koszul Mittag--Leffler exactness, exact
triangular completion, and compatible transitions; the compact state-side
construction is open. \\
Scalar OP/DT square &
imported/check &
Oberdieck--Pixton, Oberdieck--Pandharipande, and Oberdieck identify the
Behrend-weighted reduced scalar branch with
\(-4096\Delta_5^{-2}\).  This checks the orientation-forgetful square and
does not construct \(\mathfrak D_X\) or \(\epsilon_o\). \\
Eight-row host certificates &
certificate/open &
The automorphic products and denominator rows are imported where cited.
Physical row maps and scalar squares require row-by-row host
certificates. \\
\hline
\end{tabular}
\end{center}

All super vector spaces in the representation-theoretic constructions
are over \(\C\).  Real vector spaces occur only after tensoring
lattices with \(\R\) to discuss cones, chambers, and period domains.
Products may be written over \(\Gamma_{\mathrm{eff}}\); the active
factors are exactly the triples in \(\Gamma_{\mathrm{act}}\), where
the exponent \(f(nm,l)\) is non-zero.

\part{The automorphic square root}

\section{The physical question}
\label{sec:physical-question}

A charged BPS state is not, in the first instance, a local field.  It
lies in a superselection sector.  Its charge is measured at infinity,
and its existence depends on a stability chamber.  Thus the ordinary
local operator algebra of an untwisted four-dimensional theory is not
the primary object of this paper.

At the level of the protected index the situation is different.  After
taking the cohomology of the chosen supercharge, long multiplets cancel.
The object which remains is a charge-graded virtual object,
not a positive Hilbert space, whose Euler characteristic is stable under
deformation.  The index remembers the cancellation law of a unitary
theory, not its positive inner product.

For \(X=K3\times E\) the expected local object in a compact realization
is a supplied holomorphic \(E_3\)-factorization algebra
$$
\mathcal A^{E_3}_X,\qquad X=K3\times E.
$$
The auxiliary notation \(\Phi^{\mathrm{FA}}_3(X)\), when used, is only a
placeholder for this source datum; no such functor is constructed in
this paper.  No external \(\Phi^{\mathrm{FA}}_3\) formalism is used here
as an existence theorem unless it supplies the chain-level local
observables, factorization maps, descent, anomaly/QME control, and
compact charge completion required below.  In a compact realization
\(\mathcal A^{E_3}_X\) is the object whose disjoint holomorphic
insertions factorize.  The elliptic curve \(E\) enters only after a
supplied chain-level \(K3\)-specialization whose output is denoted
$$
\mathcal F_X\in\mathrm{Fact}(\operatorname{Ran}(E)).
$$
This is the first compact-realization obstruction.  The
projection-finite sector, where \(p_E(\operatorname{Supp}A)\) is a finite
subset of \(E\), is naturally local on \(\operatorname{Ran}(E)\).  A
one-dimensional sector of positive elliptic degree is not.  If
\(C\subset K3\times E\) has positive elliptic degree, then
\((p_E)_*[C]\) is a positive multiple of \([E]\); hence \(p_E(C)\) is a
one-dimensional closed subset of the irreducible curve \(E\), and so
\(p_E(C)=E\).  Such a class is wrapped or global over \(E\), not
localized at finitely many points of \(E\).

This is the \(\operatorname{Ran}(E)\)-support-locality obstruction in
the K3-integrated chiral shadow.  Naive support-local factorization on
\(\operatorname{Ran}(E)\) sees projection-finite sectors, but by itself
it misses the positive \(s\)-direction of the Igusa product, the
direction which records elliptic degree after the OP/Borcherds variable
conversion.  A compact realization must therefore choose at least one
finite categorical repair: projection-finite local factorization,
rigidified wrapped prequotients, local-local, ordered local/wrapped, and
wrapped-wrapped extension correspondences, the eight-word two-step binary
flag atlas with higher factorization separate,
quotient-after-correspondence descent, and protected integration whose
\(s\)-degree is the elliptic degree.  A separate
global Fock/Hecke mode is insufficient unless it is realized by these
wrapped prequotients and coupled to the local sector by mixed Hall
actions before the reduced \(E\)-quotient.  This is a realization
obstruction.  It is not a defect in the
Borcherds determinant or in the Gritsenko--Nikulin denominator identity.

Thus, in a realization, the curve-level rule is not imposed externally.
It is the one-dimensional chiral shadow of the holomorphic
\(E_3\)-observable: well-separated protected insertions on \(E\)
multiply, while collisions remember extension and bound-state data.  In
primitive form this is the expected bracket
$$
[\ ,\ ]:
\Prim_{c}^{\mathrm{prot}}(\mathcal F_X)
\otimes
\Prim_{c'}^{\mathrm{prot}}(\mathcal F_X)
\longrightarrow
\Prim_{c+c'}^{\mathrm{prot}}(\mathcal F_X),
\qquad c,c'\in\Gamma_X^{\mathrm{phys}}.
$$

The Igusa square-root problem is to construct or recognize this
primitive protected algebra and its Gram descent.  The determinant below
gives the decategorified signed Gram-index shadow that such a realization
would have as a recognition target, not as a source-derived
multiplicity:
$$
\sdim\Prim_{\gamma}^{\mathrm{prot}}(\overline\Pi_{X,*}^{\Theta}\mathcal F_X)
=f(nm,l),
\qquad \gamma=(n,l,m).
$$
The Borcherds--Kac--Moody denominator algebra gives the algebraic
candidate:
$$
H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^{\Theta}\mathcal F_X)
\stackrel{?}{\cong}
\mathfrak g_{\Delta_5}.
$$
The theorem-level content of the paper is the determinant and
denominator comparison.  The displayed isomorphism is the compact
\(E_3\)/Hall/chiral realization problem.

The square root is therefore not an analytic ambiguity in
\(\Delta_5^2\).  It is the normalized automorphic determinant of the
virtual protected one-particle index.  The scalar square forgets the
automorphic reflection character; a compact Hall orientation realizing
that character is part of the open Dirac--Igusa certificate.

\subsection*{Schema of the local protected observable algebra}
\label{sec:local-protected-observable-algebra}

\begin{definition}[Conditional local protected observable algebra schema]
\label{def:local-protected-observable-algebra}
For an open \(U\subset X=K3\times E\), let
\(\Gamma_{X,\sigma}^{\mathrm{eff}}(U)\subset
\Gamma_X^{\mathrm{alg}}\subset\Gamma_X^{\mathrm{form}}\) be the supplied
algebraic/effective charge support.  For
\(c\in\Gamma_{X,\sigma}^{\mathrm{eff}}(U)\), let
\(\mathfrak M_c(U)\) denote the derived moduli stack of compactly
supported B-branes on \(U\) of Mukai charge \(c\), in the sense of
Pantev--Toen--Vaquie--Vezzosi \cite{PTVV2013}, so that
\(\mathfrak M_c(U)\) carries a \((-1)\)-shifted symplectic structure;
let \(\Phi_c\) denote the perverse sheaf of vanishing cycles of any
local d-critical chart, in the sense of
Brav--Bussi--Dupont--Joyce--Szendroi \cite{BBDJS2015} (BPS sheaf, alias
DT sheaf), well defined globally as a pre-D-critical structure on
\(\mathfrak M_c(U)\); let \(o_c\) denote the orientation line, a
square root of the determinant line of the cotangent complex of
\(\mathfrak M_c(U)\), supplied as part of the Hall datum.  The
\emph{local protected observable algebra of \(X\) on \(U\)} is the
conditional source object
\[
\mathcal A_X(U)
:=\bigoplus_{c\in\Gamma_{X,\sigma}^{\mathrm{eff}}(U)}
H_*^{\mathrm{BM}}\!\bigl(\mathfrak M_c(U),\,
\Phi_c\otimes o_c\bigr),
\]
graded by that supplied support, not by the full formal lattice.  For disjoint
\(U_1,\ldots,U_k\subset X\), the proposed factorization map is
\[
\mathcal A_X(U_1)\otimes\cdots\otimes\mathcal A_X(U_k)
\longrightarrow
\mathcal A_X(U_1\sqcup\cdots\sqcup U_k),
\]
defined chain-level by Massey--Saito Thom--Sebastiani for vanishing
cycles
\[
\Phi_{F_1\oplus\cdots\oplus F_k}\simeq
\Phi_{F_1}\boxtimes\cdots\boxtimes\Phi_{F_k}
\]
on disjoint d-critical charts \cite{MasseyST,SaitoMHM}, together with the Ext-vanishing
\(\operatorname{Ext}^*(\mathcal F,\mathcal G)=0\) for branes
\(\mathcal F,\mathcal G\) with disjoint supports.  This is the
local protected-observable pre-interface schema for the present paper.
It becomes a compact \(E_3\) source \(\mathcal A_X^{E_3}\) only after
the finite witnesses of
Definition~\ref{def:compact-e3-source-interface} are supplied; the
disjoint-supports factorization on opens of \(X=K3\times E\) is only the
first holomorphic \(E_3\)-factorization test.
\end{definition}

\begin{remark}
The components are external assumptions:
PTVV \((-1)\)-shifted symplectic structure on derived moduli of
B-branes \cite{PTVV2013}; BBDJS vanishing-cycle perverse sheaf and its
Thom--Sebastiani isomorphism (extending Massey 2001 and Saito 1990 to
the d-critical setting \cite{MasseyST,SaitoMHM}) \cite{BBDJS2015}; orientation lines from the
Joyce--Upmeier orientation theory \cite{JoyceUpmeier} or
Kontsevich--Soibelman \cite{KSCoHA}.  The factorization map relies on
disjoint-supports Ext-vanishing for compactly supported branes
(absent for non-compact supports, where one recovers chiral algebra
structure, not commutative factorization).  Compactness on
\(K3\times E\) is open because the relevant moduli of branes are
typically non-quasicompact in \(\La_S\)-charge; the sectorial
truncation of
Proposition~\ref{prop:sectorial-hall-truncation} is the candidate
truncation.
\end{remark}

\section{The one-particle index and its determinant}

For the determinant calculation set
$$
Z=\begin{pmatrix}z_1&z_2\\z_2&z_3\end{pmatrix},\qquad
q=e^{2\pi iz_1},\qquad r=e^{2\pi iz_2},\qquad s=e^{2\pi iz_3}.
$$
The Gram-index lattice is
$$
\Gamma_{\mathrm{ind}}=\Z^3,\qquad
\gamma=(n,l,m),\qquad x^\gamma=q^nr^ls^m.
$$
The standard cusp polarization is the ordered limit
$$0<|s|\ll |q|\ll |r|^{-1}\ll1.$$
It determines the semigroup
$$
\Gamma_{\mathrm{eff}}
=\{(n,l,m)\mid m>0,\ n\geq0,\ l\in\Z\}
\cup\{(n,l,0)\mid n>0,\ l\in\Z\}
\cup\{(0,l,0)\mid l<0\}.
$$
\(m>0\) is positive because \(s\) is the smallest parameter; if
\(m=0\), then \(n>0\) is positive because \(q\) is next; if \(m=n=0\),
positivity is \(l<0\) because \(|r|^{-1}\ll1\).  This is a chamber
convention for the completed product, not a microscopic charge
positivity statement.

\begin{definition}[Ramond-sector K3 index and its half]
Let $\mathcal H_{\mathrm{RR}}(S)$ be the Ramond--Ramond Hilbert space of
a unitary $\mathcal N=(4,4)$ sigma model on a K3 surface $S$.  Its
central charges are
$$c=\overline c=6.$$
This Hilbert space is a supplied worldsheet input for the protected K3
index.  It is not a construction of the compact \(K3\times E\)
D-brane Hilbert space.
Choose a right-moving Ramond supercharge $Q_R$ with
$$Q_R^2=0,\qquad
\{Q_R,Q_R^\dagger\}=
2\left(\overline L_0-\frac{\overline c}{24}\right).$$
The K3 elliptic genus is the protected supertrace
$$
Z_{\mathrm{K3}}(\tau,z)=
\operatorname{Tr}_{\mathcal H_{\mathrm{RR}}(S)}
(-1)^{F_L+F_R}q^{L_0-c/24}
\overline q^{\,\overline L_0-\overline c/24}r^{J_0}.
$$
The BPS space in degree $(n,l)$ is
$$
\mathcal H^{\mathrm{BPS}}_{n,l}(S):=
H^\bullet\!\left(
\{\psi\mid (L_0-c/24)\psi=n\psi,\ J_0\psi=l\psi\},Q_R
\right).
$$
\end{definition}

\begin{lemma}[Right-moving localization]
Then
$$
Z_{\mathrm{K3}}(\tau,z)=
\sum_{n\geq0,\;l\in\Z}
\sdim\mathcal H^{\mathrm{BPS}}_{n,l}(S)q^nr^l.
$$
\end{lemma}

\begin{proof}
If $\overline L_0-\overline c/24>0$, the displayed anticommutator pairs
states with opposite $(-1)^{F_R}$ parity.  Their supertrace cancels.
The unpaired states are the $Q_R$-harmonic representatives, hence the
graded superdimension of $Q_R$-cohomology gives the elliptic genus.
\end{proof}

\begin{remark}[Where unitarity enters]
Unitarity is used here before the index is taken: it gives the adjoint
relation which pairs positive right-moving energy states and makes the
supertrace localize.  After passing to the protected index, the object is
virtual.  A coefficient \(f(n,l)\) is a superdimension, not a positive
dimension.  Negative coefficients record an odd excess in the protected
supertrace, or in the chosen \(K_0\)-representative.  They do not
determine the two parity dimensions without an additional Hilbert-space
or denominator-algebra parity datum.
\end{remark}

\begin{definition}[Grothendieck half-index representative]
Eichler--Zagier normalization \cite{EZ:1}:
$$Z_{\mathrm{K3}}(\tau,z)=2\phi_{0,1}(\tau,z),$$
$$\phi_{0,1}(\tau,z)
=\sum_{n\geq 0,\;l\in\Z}f(n,l)q^nr^l.$$
Thus
$$\sdim\mathcal H^{\mathrm{BPS}}_{n,l}(S)=2f(n,l).$$
The arbitrary Grothendieck representative
$$\mathbb U_{n,l}\in K_0(\mathrm{sVect}_{\mathrm{fd}}),
\qquad \sdim\mathbb U_{n,l}=f(n,l),$$
is the normalized half-index class used by the Borcherds lift.  It is
not asserted to be a canonical half of
$\mathcal H^{\mathrm{BPS}}_{n,l}(S)$ as a Hilbert space.
As a \(K_0\)-model one may take \(\mathbb U_{n,l}\) to be
\(\C_{\overline0}^{f(n,l)}\) when \(f(n,l)\ge0\), and
\(\C_{\overline1}^{-f(n,l)}\) when \(f(n,l)<0\).  No canonical choice of
basis, parity lift, or operator product is implied.
$$\phi_{0,1}=r^{-1}+10+r+O(q),\qquad
\frac{f(0,0)}{2}=5.$$
\end{definition}

\begin{lemma}[Fock trace and superdeterminant]
Let
$$V=\bigoplus_{\lambda\in P}V_\lambda$$
be a $P$-graded super vector space with finite-dimensional homogeneous
pieces and let $a_\lambda=\sdim V_\lambda$.  Put
$$\mathcal F(V)=\operatorname{Sym}(V_{\overline 0})
\otimes \bigwedge(V_{\overline 1}).$$
As a formal character,
$$\sch\mathcal F(V):=
\sum_{\mu\in P}\sdim\mathcal F(V)_\mu\,x^\mu
=\prod_{\lambda\in P}(1-x^\lambda)^{-a_\lambda}.$$
The inverse character is the superdeterminant
$$\sdet_V(1-x)=\prod_{\lambda\in P}(1-x^\lambda)^{a_\lambda}.$$
\end{lemma}

\begin{proof}
$$V_\lambda=\C_{\overline0}:\qquad
\sch\operatorname{Sym}(V_\lambda)=(1-x^\lambda)^{-1}.$$
$$V_\lambda=\C_{\overline1}:\qquad
\sch\bigwedge(V_\lambda)=1-x^\lambda.$$
Tensor product over a homogeneous basis proves the product.
\end{proof}

When \(P=\Gamma_{\mathrm{eff}}\), all products below are taken in the
cusp-completed semigroup algebra determined by
\(0<|s|\ll |q|\ll |r|^{-1}\ll1\).  Every coefficient receives only
finitely many contributions in this completion.

$$x^{(n,l,m)}=q^nr^ls^m.$$
Form now the virtual Borcherds determinant package.  The third index
\(m\) is the second-quantized/Borcherds degree.  The positive \(m\)
sector carries the Hecke--DMVV exponents \(f(nm,l)\).  The \(m=0\)
sector is a cusp/Weyl boundary package carrying the repeated boundary
indices \(f(0,l)\).  Neither sector is a microscopic one-particle Hilbert
space.
The compact Hall \(s=0\) cusp is therefore a separate boundary
certificate: it is controlled by the Borcherds chamber data only after
the corresponding source-side boundary operations are supplied.
\[
\mathcal V^{\mathrm{bulk}}
:=\bigoplus_{\substack{(n,l,m)\in\Gamma_{\mathrm{eff}}\\m>0}}
\mathbb U_{nm,l},
\qquad
\mathcal V^{\mathrm{cusp}}
:=\bigoplus_{\substack{(n,l,0)\in\Gamma_{\mathrm{eff}}}}
\mathbb U_{0,l}.
\]
\[
\mathcal V=\mathcal V^{\mathrm{bulk}}\oplus\mathcal V^{\mathrm{cusp}},
\qquad
\mathcal V_{(n,l,m)}=\mathcal V_{n,l,m}:=\mathbb U_{nm,l},\qquad
\sdim\mathcal V_{n,l,m}=f(nm,l).
\]
This is a definition in \(K_0\), not a microscopic state space.  The
\(m>0\) sector is the \(K_0\)-level virtual half of the DMVV product
\cite{DMVV}, obtained by replacing
\(Z_{\mathrm{K3}}=2\phi_{0,1}\) by \(\phi_{0,1}\).  The normalized Fock
character in the Borcherds chamber is
$$\sch\mathcal F(\mathcal V)
=\prod_{\gamma\in\Gamma_{\mathrm{eff}}}(1-x^\gamma)^{-\sdim\mathcal V_\gamma}
=\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{-f(nm,l)}.$$
$$\sdet_{\mathcal V}(1-x)
=\prod_{\gamma\in\Gamma_{\mathrm{eff}}}(1-x^\gamma)^{\sdim\mathcal V_\gamma}
=\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}.$$
The sector $m>0$ is the normalized half of the second-quantized DMVV
index.  The terms with $m=0$ are cusp and Weyl-chamber boundary factors
of the Borcherds product; the determinant reads only their signed
indices $f(0,l)$.
The normalized cusp-form section below proves the leading coefficient
which fixes the Weyl monomial
$$v_0(Z)=64q^{1/2}r^{1/2}s^{1/2}.$$
$$v_0\notin\bigoplus_{\gamma\in\Gamma_{\mathrm{eff}}}\mathcal V_\gamma.$$

\begin{definition}[Normalized \(K_0\)-determinant]
$$\mathcal{D}_X(Z)
=v_0(Z)\sdet_{\mathcal V}(1-x)
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}.$$
$$\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}(Z)
=\mathcal D_X(Z)^{-1}
=\frac{1}{64}q^{-1/2}r^{-1/2}s^{-1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{-f(nm,l)}.$$
The object constructed here is the virtual \(K_0\)-determinant; compact
BPS meaning is part of the separate realization problem.
\end{definition}

\begin{proposition}[Determinant normalization]
$$[q^{1/2}r^{1/2}s^{1/2}]\,\mathcal D_X=64,$$
$$\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}
=\frac{1}{64}q^{-1/2}r^{-1/2}s^{-1/2}\sch\mathcal F(\mathcal V),$$
$$\mathcal D_X
=64q^{1/2}r^{1/2}s^{1/2}\sdet_{\mathcal V}(1-x).$$
\end{proposition}

\begin{proof}
$$\sch\mathcal F(\mathcal V)
=\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{-f(nm,l)},\qquad
\sdet_{\mathcal V}(1-x)
=\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}.$$
$$v_0(Z)\sdet_{\mathcal V}(1-x)=\mathcal D_X,\qquad
v_0(Z)^{-1}\sch\mathcal F(\mathcal V)
=\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}.$$
\end{proof}

\begin{proposition}[Virtuality of the square root]
\label{prop:virtuality-of-the-square-root}
The displayed construction produces a class
$$
[\mathcal V]\in
K_0(\Gamma_{\mathrm{eff}}\hbox{-graded finite-dimensional super vector spaces})
$$
together with its Fock determinant.  By itself this determinant does not
construct a Hilbert space, a vertex algebra, a holomorphic
\(E_3\)-factorization algebra, or a chiral factorization algebra whose
character is $\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}$.

All denominator statements use only the equalities
$$\sdim\mathcal V_{(n,l,m)}=f(nm,l),\qquad
\mathcal D_X=v_0\sdet_{\mathcal V}(1-x).$$
The denominator algebra and formal current envelope are constructed
later from the Borcherds root datum, not from a canonical half of the K3
Hilbert space.
\end{proposition}

\begin{proof}
By definition, $\mathcal V_{(n,l,m)}=\mathbb U_{nm,l}$ is specified only
through its class in $K_0(\mathrm{sVect}_{\mathrm{fd}})$ and through the
integer $\sdim\mathbb U_{nm,l}=f(nm,l)$.  The Fock trace and
superdeterminant lemma depends only on these signed dimensions.  No
operation in the construction supplies composition maps, operator
products, locality, or a Hilbert completion.
\end{proof}

\begin{proposition}[Dirac/Pfaffian recognition target]
\label{prop:dirac-pfaffian-recognition-target}
The class \([\mathcal V]\in K_0\) and its Fock determinant
\(\mathcal D_X=v_0\sdet_{\mathcal V}(1-x)=\Delta_5\) record signed
Gram-degree multiplicities and a formal infinite-product; they do not
produce an operator with a spectrum.  The structural upgrade demanded
by the protected-locality side of the constellation is an
\emph{open recognition target}:
\begin{quote}
construct from the compact \(K3\times E\) Dirac--Igusa certificate of
Definition~\ref{def:compact-igusa-realization-datum} a first-order
protected operator/algebra
\(\mathfrak D_X\) acting on a chiral protected module, whose
charge-graded Pfaffian, after the supplied Pfaffian-to-automorphic line
comparison, satisfies
$$
\iota_{\mathrm{aut}}(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X))
=\mathcal D_X=\Delta_5.
$$
Its scalar trace, in the OP normalization of
Definition~\ref{def:op-normalization-branch} below, satisfies
$$
\operatorname{Tr}_{\mathrm{prot}}
\bigl((-1)^F(\mathfrak D_X)^{-2}\bigr)
=-4096\,\Delta_5^{-2}.
$$
\end{quote}
Existence of \(\mathfrak D_X\) is open; it would convert the \(K_0\)
identity of Proposition~\ref{prop:virtuality-of-the-square-root}
into a first-order protected statement.  The target carries the
sign-square ambiguity of
Conjecture~\ref{conj:protected-d-brane-index} and the orientation
monodromy of Open Problem~\ref{op:orientation-monodromy-character};
choosing a square root of \((\mathfrak D_X)^{-2}\) requires the
orientation datum of that open problem and is not fixed by the OP
scalar.
\end{proposition}

\begin{definition}[Finite generic type-II local-sign subcertificate]
\label{def:type-ii-pfaffian-wall-certificate}
A finite generic local-sign subcertificate for the type-II Pfaffian model consists, for
each of the three simple type-II walls
\(\Hpl_{\delta_i}\), \(i=1,2,3\), of the following data.
\begin{enumerate}
\item[\textup{(Pf1)}] A generic wall point \(x_i\) in the reduced compact
Hall sector and an \(s_{\delta_i}\)-equivariant real analytic slice
\((U_i,u_i)\) through \(x_i\), with
\[
\Hpl_{\delta_i}\cap U_i=\{u_i=0\},
\qquad
s_{\delta_i}(u_i)=-u_i .
\]
\item[\textup{(Pf2)}] A splitting of the reduced determinant complex on
the slice into its tangent determinant factor and a normal factor
\[
K^{\mathrm{red}}|_{U_i}\simeq
K^{\mathrm{tan}}_i\oplus K^{\mathrm{nor}}_i,
\]
with \(s_{\delta_i}\) preserving the tangent determinant factor.
\item[\textup{(Pf3)}] An oriented quasi-isomorphism of the normal factor
to a finite sum of odd rank-one Pfaffian crossings
\[
K^{\mathrm{nor}}_i\simeq
\bigoplus_{j=1}^{N_i^{\mathrm{Pf}}}
\bigl[\mathbb R\xrightarrow{\,u_i\,}\mathbb R\bigr].
\]
In the induced trivialization the normal Pfaffian section is
\(u_i^{N_i^{\mathrm{Pf}}}\) times a unit.
\item[\textup{(Pf4)}] The three normal-mode ranks
\(N_i^{\mathrm{Pf}}=N_{\delta_i}^{\mathrm{Pf}}\) are
\[
N_1^{\mathrm{Pf}}=N_2^{\mathrm{Pf}}=N_3^{\mathrm{Pf}}=1 .
\]
\end{enumerate}
This is a finite generic local-sign subcertificate: three wall charts, three
anti-invariance checks \(s_{\delta_i}(u_i)=-u_i\), three tangent-factor
compatibility checks, and three odd Pfaffian normal-mode ranks.  These
ranks are local Dirac/Pfaffian data; they are not read from the
automorphic divisor.  The subcertificate constructs neither the global
reduced orientation line nor the Weyl lift, and it is not the full O2 wall
atlas with component, boundary, and overlap compatibility.  It uses no scalar
normalization of \(\Delta_5\), no factor \(64\), and no OP/DT scalar sign.
\end{definition}

\begin{proposition}[Local obstruction certificate for \textup{(O2)}]
\label{prop:o2-local-obstruction-certificate}
Fix one of the three simple type-II roots
\(\delta\in\{\delta_1,\delta_2,\delta_3\}\).  A geometric proof of the
rank-one Pfaffian model at \(\Hpl_\delta\) is not a consequence of
\((\delta,\delta)=2\), of the automorphic divisor order, or of the Maass
character.  In the reduced compact Hall framework it must supply the
following local deformation-obstruction calculation.

\begin{enumerate}
\item[\textup{(L1)}] Let \(x_\delta=[\mathcal C_\delta]\) be a generic
wall object.  An \(s_\delta\)-equivariant real analytic
d-critical/Kuranishi chart
\[
(U_\delta,x_\delta,u_\delta,K^{\mathrm{red}}_\delta)
\longrightarrow \mathfrak M^{\mathrm{red}}_{\mathcal C_\delta}
\]
is supplied, where
\(K^{\mathrm{red}}_\delta\) is the real form of the cosection-reduced
self-Ext complex
\[
\operatorname{RHom}_{\mathrm{red}}(\mathcal C_\delta,\mathcal C_\delta)
\]
in that chart, the wall is exactly \(U_\delta\cap\{u_\delta=0\}\), and
\[
s_\delta(u_\delta)=-u_\delta,\qquad
T_{x_\delta}(U_\delta\cap\Hpl_\delta)=T_{x_\delta}U_\delta^{s_\delta}.
\]
\item[\textup{(L2)}] A splitting in the \(s_\delta\)-equivariant derived
category
\[
K^{\mathrm{red}}_\delta
\simeq K^{\mathrm{tan}}_\delta\oplus K^{\mathrm{nor}}_\delta
\]
whose tangent factor carries the wall tangent determinant and whose normal
factor is the anti-invariant normal determinant factor.  Equivalently, the
extension class
\[
\eta_\delta\in
\operatorname{Ext}^1_{D^{s_\delta}(U_\delta)}
(K^{\mathrm{nor}}_\delta,K^{\mathrm{tan}}_\delta)
\]
vanishes after the reduced \(E\)-quotient and the chosen quotient
orientation trivializations are imposed.
\item[\textup{(L3)}] In an oriented trivialization of the normal Pfaffian
line,
\[
\operatorname{Pf}(K^{\mathrm{nor}}_\delta)
=\upsilon_\delta\,u_\delta^{N_\delta^{\mathrm{Pf}}},
\qquad
\upsilon_\delta(x_\delta)\ne0,\qquad
s_\delta(\upsilon_\delta)=\upsilon_\delta,
\]
and \(K^{\mathrm{nor}}_\delta\) is oriented quasi-isomorphic to
\[
\bigoplus_{j=1}^{N_\delta^{\mathrm{Pf}}}
\bigl[\mathbb R\xrightarrow{\,u_\delta\,}\mathbb R\bigr].
\]
The rank-one assertion used in \textup{(O2)} is the further equality
\[
N_\delta^{\mathrm{Pf}}=1.
\]
\end{enumerate}

If \textup{(L1)}--\textup{(L3)} hold, then the local Hall/Pfaffian sign is
\[
s_\delta^*\operatorname{Pf}(K^{\mathrm{nor}}_\delta)
=(-1)^{N_\delta^{\mathrm{Pf}}}
\operatorname{Pf}(K^{\mathrm{nor}}_\delta),
\]
while the squared determinant section is fixed.  If the unit
\(\upsilon_\delta\) has a nontrivial reflection character, that character
multiplies the displayed sign and belongs to the orientation-transport
datum \(\textup{(O1)}^+\).  If the splitting obstruction
\(\eta_\delta\) does not vanish, the tangent and normal determinants cannot
be separated and no rank-one normal sign has been computed.  If
\(N_\delta^{\mathrm{Pf}}\ne1\), the order-one automorphic divisor is at
best a target check and the local Hall model required by \textup{(O2)} is
false or incomplete.  Thus the exact missing inputs are the three charts,
the three reduced self-Ext complexes, the three equivariant splittings, the
three invariant Pfaffian units, and the three rank computations
\(N_{\delta_i}^{\mathrm{Pf}}=1\).  In any compact source claim these
local data must also come from the same finite hybrid correspondence
system that supplies the positive elliptic-degree sector; this is the
compatibility obstruction of
Proposition~\ref{prop:o2-hybrid-compatibility-obstruction}.
\end{proposition}

\begin{theorem}[Conditional finite type-II local-sign computation]
\label{thm:stable-finite-type-ii-local-theorem}
Fix a finite HN height \(R\) and a simple type-II wall
\(\Hpl_{\delta_i}\), \(i\in\{1,2,3\}\).  The following is a conditional
local-sign computation: it applies only after the residual tuple below
has been trivialized.  A finite geometric computation of the generic
local sign required by \textup{(O2)} at this wall is the vanishing of the
residual
\[
\mathfrak O^{\mathrm{O2}}_{\delta_i,R}
=
\left(
\mathfrak o^{\mathrm{chart}}_{\delta_i,R},
\mathfrak o^{\mathrm{wall}}_{\delta_i,R},
\mathfrak o^{\mathrm{split}}_{\delta_i,R},
\mathfrak o^{\mathrm{unit}}_{\delta_i,R},
\mathfrak o^{\mathrm{rank}}_{\delta_i,R},
\mathfrak o^{\mathrm{tr}}_{\delta_i,R'R}
\right)
\]
for every \(R'\ge R\).  These entries mean, respectively:
existence of a wall object and \(s_{\delta_i}\)-equivariant real
d-critical chart; equality of the fixed tangent with the wall tangent and
anti-invariance \(s_{\delta_i}(u_{\delta_i,R})=-u_{\delta_i,R}\);
vanishing of the tangent/normal extension class; invariance of the normal
Pfaffian unit after quotient orientation trivialization; the rank-one
normal quasi-isomorphism
\[
K^{\mathrm{nor}}_{\delta_i,R}
\simeq
\bigl[\mathbb R\xrightarrow{\,u_{\delta_i,R}\,}\mathbb R\bigr];
\]
and compatibility of these choices under the HN transition
\(R'\to R\).

If \(\mathfrak O^{\mathrm{O2}}_{\delta_i,R}=0\), then in the reduced chart
\[
\operatorname{Pf}(K^{\mathrm{nor}}_{\delta_i,R})
=\upsilon_{\delta_i,R}u_{\delta_i,R},
\qquad
s_{\delta_i}(\upsilon_{\delta_i,R})=\upsilon_{\delta_i,R},
\]
and therefore
\[
s_{\delta_i}^*\operatorname{Pf}(K^{\mathrm{nor}}_{\delta_i,R})
=-\operatorname{Pf}(K^{\mathrm{nor}}_{\delta_i,R}),\qquad
s_{\delta_i}^*\operatorname{Pf}(K^{\mathrm{nor}}_{\delta_i,R})^{2}
=\operatorname{Pf}(K^{\mathrm{nor}}_{\delta_i,R})^{2}.
\]
Vanishing of these residuals for \(i=1,2,3\) gives the three finite
generic type-II local-sign subcertificates at height \(R\), and the computed local
wall-chart signs are
\[
\varepsilon^{\mathrm{loc}}_{\delta_i,R}=-1,\qquad i=1,2,3.
\]
The theorem computes only the sign from the local chart after the residuals
vanish.  It does not construct the wall charts, the reduced self-Ext
complexes, the splittings, the quotient orientation trivializations, or
the transition null-homotopies, and no global character is defined by
this theorem.  The full O2 wall-atlas certificate also requires the
component, boundary, and overlap data of
Proposition~\ref{prop:o2-hybrid-compatibility-obstruction}.  If, in
addition, (O1) descends the reduced orientation and
(O1)\(^+\) supplies an honest HN-compatible Weyl action on the quotient
orientation, these local signs induce the global values
\(\epsilon_o(s_{\delta_i})=-1\).  The automorphic divisor order
\(d_{\delta_i}^{\mathrm{aut}}=1\) is only the target check recorded in
Lemma~\ref{lem:thm3-three-sign-computation}.
\end{theorem}

\begin{proof}
The vanishing of
\(\mathfrak o^{\mathrm{chart}}_{\delta_i,R}\) and
\(\mathfrak o^{\mathrm{wall}}_{\delta_i,R}\) gives the local coordinate
\(u_{\delta_i,R}\) and the reflection rule
\(s_{\delta_i}(u_{\delta_i,R})=-u_{\delta_i,R}\).  The splitting residual
separates the tangent determinant from the anti-invariant normal
determinant.  The unit residual removes an extra reflection character from
the normal Pfaffian unit.  The rank residual identifies the normal factor
with one odd rank-one crossing.  Hence the normal Pfaffian is
\(\upsilon_{\delta_i,R}u_{\delta_i,R}\), and reflection multiplies it by
\(-1\).  Squaring removes this sign.  The transition residual says that
the same computation survives restriction from \(R'\) to \(R\).
\end{proof}

\begin{theorem}[Conditional Dirac--Pfaffian normalization and
orientation character]
\label{thm:dirac-pfaffian-recognition-conditional}
Suppose the following data items are granted on the reduced compact
critical Hall/CoHA sector of \(X=K3\times E\) of
Definition~\ref{def:protected-hall-integration-criterion}.

\smallskip
\textup{(D0)} \emph{Compact first-order certificate.}  A finite-stage
first-order \(D_0\)-certificate in the sense of
Definition~\ref{def:first-order-d0-certificate} is supplied.  Thus, for
every \(R\) in the chosen cofinal HN subsystem, the datum contains a
finite Hall/factorization stage \(D_{0,R}\) on the finite support
\(\widehat\Gamma_R\), a finite target test window
\(\Gamma_R^{\mathrm{test}}\), successor transition maps whose composites
give the smaller-stage maps, source/observable comparison maps, and a
vanishing stage residual tuple \(\mathfrak O_{D_0,R}\).  Only after these
finite data, transition cocycles, and support/parity residuals vanish may
one form the
HN-completed state object.  The completed object is part of the supplied
certificate: it carries its charge completion by \(\widehat\Gamma_X\), a
source observable shadow on \(\operatorname{Ran}^{\mathrm{hyb}}(E)\), a
protected first-order operator/algebra \(\mathfrak D_X\), a Pfaffian line
with normalized section, and a \(\Theta_\Pi\)-corrected descent whose
primitive algebra is \(\Gamma_{\mathrm{gram}}\)-graded with signed
superdimensions
\[
\sdim P^\Pi_{X,(n,l,m)}=f(nm,l)
\qquad ((n,l,m)\in\Gamma_{\mathrm{eff}}).
\]
This is an assumption of the theorem.  The proved lattice part is the
normal-ordered homomorphism \(\overline\Pi_X\); the imported target part is
the Borcherds--Gritsenko--Nikulin denominator algebra; the compact
state-side construction remains open unless the finite stages, transition
maps, source/observable comparison, and residual trivializations of
Definition~\ref{def:first-order-d0-certificate} are supplied.

\smallskip
\textup{(O1)} \emph{Strong multiplicative reduced orientation datum.}
There exists a Joyce--Upmeier-type orientation line \cite{JoyceUpmeier}
$$
o_{\mathcal C}\in\operatorname{Pic}(\mathfrak M^{or}_X),\qquad
o_{\mathcal C}^{\otimes 2}\;\simeq\;
\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C),
$$
in the sense of Definition~\ref{def:orientation-line}, satisfying
$$
o_{\mathcal C\oplus\mathcal C'}
\;\simeq\;
o_{\mathcal C}\otimes o_{\mathcal C'}
\quad\text{compatibly with the reduced extension correspondences},
$$
and equipped with the quotient-descent package for the reduced
\(E\)-quotient.  The Weyl-equivariant lift is a separate additional
datum, isolated in (O1)\(^+\), and is transported by Gram-projection
\(\Pi_X:\Gamma_X^{\mathrm{form}}\to\Gamma_{\mathrm{gram}}\).
Here descent under the reduced \(E\)-quotient is part of the datum and
means the simultaneous vanishing, on every stratum used by the Hall
correspondences, of
\[
\alpha^{\mathrm{red}}_{\mathcal C}
\in H^2(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2),
\qquad
\alpha^{E,\mathrm{free}}_{\mathcal C}
=a_1(\mathcal C)u_1+a_2(\mathcal C)u_2
\in H^2(BE;\mathbb F_2),
\]
and of the finite-stabilizer classes
\[
\beta^{E,N}_{\mathcal C}\in H^2(BE[N];\mathbb F_2).
\]
The displayed finite-stabilizer groups are the point-stabilizer
restrictions of the actual Borel equivariant obstruction classes.  For a
finite-stabilizer stratum \(S\) with stabilizer \(E[N]\), the primary
class is
\[
\widetilde\beta^{E,N}_{R,S}
\in H^2_{E[N]}(S;\mathbb F_2).
\]
A point-stabilizer calculation closes (O1) only after the mixed Borel
terms, the stabilizer action on \(H^\bullet(S;\mathbb F_2)\), and the
spectral-sequence differentials on the corresponding stratum are shown to
vanish.  These are degree-two gerbe obstruction classes.  Their vanishing
is not the same datum as a trivial finite-stabilizer action on an already
linearized line.  After the degree-two class has been null-trivialized,
the residual choices of finite-stabilizer linearization form an
\(H^1(BE[N];\mathbb F_2)\)-torsor; the trivial quotient orientation
requires the zero point of this torsor.  This \(H^1\)-choice is part of
the quotient-orientation package transported in (O1)\(^+\).  Thus (O1)
is not merely an ordinary Picard-line assertion: it consists of an
ordinary square root in \(\operatorname{Pic}\), null-trivializations of
the reduced and equivariant degree-two gerbes, and an equivariant line
whose finite-stabilizer degree-one characters
\[
\lambda_{\mathcal C}^{E,N}\in H^1(BE[N];\mathbb F_2)
\]
are all chosen to be zero after the corresponding gerbes have vanished.
On finite compact/wrapped HN stages this is precisely the
quotient-orientation character system of
Proposition~\ref{prop:finite-stage-quotient-orientation-character-system}.
For \(N=2\), with \(E[2]=\langle e_1,e_2\rangle\) and
\(e_3=e_1+e_2\), this is the Klein-four condition
\[
\beta^{E,E[2]}_{\mathcal C}
=b_{20}x_1^2+b_{11}x_1x_2+b_{02}x_2^2,\qquad
(b_{20},b_{11},b_{02})
=(r_1,r_1+r_2+r_3,r_2),
\]
where
\[
\operatorname{res}_{\langle e_i\rangle}
\beta^{E,E[2]}_{\mathcal C}=r_i\tau_i^2 .
\]
If this class vanishes, an \(E[2]\)-linearization still has character
\[
\lambda_{\mathcal C}^{E[2]}
=\lambda_1x_1+\lambda_2x_2\in H^1(BE[2];\mathbb F_2),
\]
with cyclic restrictions
\[
\rho_1=\lambda_1,\qquad
\rho_2=\lambda_2,\qquad
\rho_3=\lambda_1+\lambda_2.
\]
Trivial \(E[2]\)-linearization means \(\rho_1=\rho_2=\rho_3=0\).
The bits \(r_i\) live in degree two; the bits \(\rho_i\) live in degree
one.
For even \(N\) with \(2^a\parallel N\), the mod-\(2\) residual is a
class on the two-primary stabilizer
\[
E[N]_{(2)}\simeq(\Z/2^a)^2.
\]
The case \(a=1\) is the displayed Klein-four calculation.  For
\(a\ge2\),
\[
H^*\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\Lambda(x_1,x_2)\otimes\mathbb F_2[y_1,y_2],
\qquad |x_i|=1,\quad |y_i|=2,\quad x_i^2=0,
\]
and hence
\[
H^2\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\mathbb F_2\langle y_1,x_1x_2,y_2\rangle.
\]
Writing
\[
\beta^{E,N}_{\mathcal C,(2)}
=A_1^{(N)}y_1+A_{12}^{(N)}x_1x_2+A_2^{(N)}y_2,
\]
the order-two cyclic restrictions see
\[
\operatorname{res}_{\langle h_1\rangle}\beta^{E,N}_{\mathcal C,(2)}
=A_1^{(N)}\tau_1^2,\quad
\operatorname{res}_{\langle h_2\rangle}\beta^{E,N}_{\mathcal C,(2)}
=A_2^{(N)}\tau_2^2,\quad
\operatorname{res}_{\langle h_3\rangle}\beta^{E,N}_{\mathcal C,(2)}
=(A_1^{(N)}+A_2^{(N)})\tau_3^2,
\]
where \(h_i=2^{a-1}g_i\) for a basis \(g_1,g_2\) of
\((\Z/2^a)^2\) and \(h_3=h_1+h_2\).  The coefficient
\(A_{12}^{(N)}\) is invisible to these cyclic order-two restrictions.
Thus the \(E[2]\) vector \((r_1,r_2,r_3)\) detects only the
two-torsion residual; it is not a computation of
\(\beta^{E,N}_{\mathcal C}\) for even \(N\ge4\).
For \(a\ge2\), even after
\(\beta^{E,N}_{\mathcal C,(2)}=0\), the remaining two-primary
linearization choices form
\[
H^1\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\mathbb F_2\langle x_1,x_2\rangle,
\]
and the trivial linearization requires that character to vanish on the
chosen two-primary generators.
Invariance of the underlying line under translations of \(E\) is not a
substitute for these quotient-linearization data.

\smallskip
\textup{(O1)\(^+\)} \emph{Weyl-equivariant determinant-line transport.}
The orientation line of (O1) is equipped with coherent lifts of the three
type-II wall transports
\[
\tau_i:o_{\mathcal C}\longrightarrow s_{\delta_i}^{*}o_{\mathcal C},
\qquad i=1,2,3,
\]
but the word ``coherent'' is load-bearing.  At finite height \(R\), the
first object is the finite partial action groupoid
\(\mathcal G_R\) whose objects are retained oriented quotient strata and
whose arrows are the retained type-II wall transports.  A choice of
determinant-line lifts gives
\[
c_{o,R}\in Z^2(\mathcal G_R;\underline{\mathbb F}_2).
\]
The finite obstruction is
\([c_{o,R}]\in H^2(\mathcal G_R;\underline{\mathbb F}_2)\), together
with the quotient-torsor defects.  Only on a complete
\(W^{(2)}(\La^{2,1}_{II})\)-orbit with constant coefficients does this
reduce to the group cohomology class below.  A choice of lifts over words
in the simple reflections is then first only a projective
determinant-line action: for \(w,w'\in W^{(2)}(\La^{2,1}_{II})\) one has
a composition defect
\[
w'^*\tau_w\circ \tau_{w'}=(-1)^{c_o(w,w')}\tau_{ww'},
\qquad
c_o\in Z^2\!\left(W^{(2)}(\La^{2,1}_{II});\mathbb F_2\right).
\]
Its class
\[
[c_o]\in H^2\!\left(W^{(2)}(\La^{2,1}_{II});\mathbb F_2\right)
\]
is the Weyl determinant-line cocycle obstruction.  The datum (O1)\(^+\)
requires \([c_o]=0\), a choice of \(1\)-cochain killing \(c_o\), and
normalization \(\tau_i^2=1\) for \(i=1,2,3\).  Only then do the lifts
satisfy the Coxeter presentation of \(W^{(2)}(\La^{2,1}_{II})\), or
equivalently give an honest action on the oriented Pfaffian line over
the wall-complement of the reduced compact Hall sector.  This is a
geometric determinant-line monodromy datum.  It does not include a scalar
formula;
\(\tau_i\) must also transport the quotient-orientation package
\[
\mathfrak q_{\mathcal C}:=
\left(\alpha^{\mathrm{red}}_{\mathcal C},
\alpha^{E,\mathrm{free}}_{\mathcal C},
\{(\beta^{E,N}_{\mathcal C},
\lambda^{E,N}_{\mathcal C})\}_{N\ge2}\right)
\]
and the chosen trivializations of these classes between the charge strata
lying over Weyl-related Gram degrees.  Equivalently, after the
degree-two classes in \(\mathfrak q_{\mathcal C}\) vanish and the zero
finite characters \(\lambda^{E,N}_{\mathcal C}=0\) are selected, choose
null-trivializations
\[
\theta_{\mathcal C}=
\left(\theta^{\mathrm{red}}_{\mathcal C},
\theta^{E,\mathrm{free}}_{\mathcal C},
\{\theta^{E,N}_{\mathcal C}\}_{N\ge2}\right).
\]
For finite stabilizers \(\theta^{E,N}_{\mathcal C}\) includes the
null-trivialization of the finite Borel class and, after the mixed Borel
terms and differentials vanish, its point-stabilizer restriction
\(\beta^{E,N}_{\mathcal C}\in H^2(BE[N])\), together with the choice of
the zero \(H^1(BE[N])\)-linearization character.
For a simple type-II reflection \(s_{\delta_i}\), the failure of
\(\tau_i\) to preserve the quotient trivialization is the torsor
difference
\[
\omega_{i,\mathcal C}
\in
H^1(\mathfrak M^{\mathrm{red}}_{s_{\delta_i}\mathcal C};\mathbb F_2)
\oplus
\bigoplus_{N\ge2}H^1(BE[N];\mathbb F_2).
\]
Here \(s_{\delta_i}\mathcal C\) denotes the chosen target stratum over
the Weyl-reflected Gram degree.  The connected \(BE\)-linearization
contributes no \(H^1\)-term because \(H^1(BE;\mathbb F_2)=0\).  The datum
(O1)\(^+\) includes the vanishing of all \(\omega_{i,\mathcal C}\) and
the Coxeter coherence of the resulting transports.  Without this
compatibility the reflection sign is a sign of an ordinary square-root
line, not a sign on the reduced \(E\)-quotient Hall sector.  The passage
from three generator
signs to a character is then the pure
group-theoretic Lemma~\ref{lem:weyl-equivariant-orientation-cocycle},
after the projective and quotient-torsor obstruction package of
Lemma~\ref{lem:weyl-quotient-orientation-obstruction} has vanished.
At finite HN height this is the cocycle system of
Corollary~\ref{cor:finite-stage-weyl-cocycle-character-system}; the
global datum is the compatible cofinal inverse system of those splittings.

\smallskip
\textup{(O2)} \emph{Pfaffian local model and wall atlas on type-II
walls.}  The finite generic local-sign subcertificate of
Definition~\ref{def:type-ii-pfaffian-wall-certificate} is supplied.
Proposition~\ref{prop:o2-local-obstruction-certificate} records the
geometric computation required to remove this hypothesis.  The
local wall-chart signs which feed the geometric reflection character
$$
\epsilon_o:W^{(2)}(\La^{2,1}_{II})\longrightarrow\{\pm1\}
$$
of Open Problem~\ref{op:orientation-monodromy-character} are computed
from local Pfaffian normal forms at generic points of the type-II walls
\(\Hpl_\delta\).  Namely, the reduced determinant complex is assumed to
split, after removing the tangent determinant factor, as
\[
K_{\delta}^{\mathrm{nor}}
\simeq
\bigoplus_{j=1}^{N_\delta^{\mathrm{Pf}}}\bigl[\mathbb R\xrightarrow{\,u_\delta\,}
\mathbb R\bigr],
\]
where \(u_\delta\) is a real local equation of the wall,
\(s_\delta(u_\delta)=-u_\delta\), and the Pfaffian section is
\(u_\delta^{N_\delta^{\mathrm{Pf}}}\) times a unit.  For the three simple type-II walls
the supplied normal-mode model has
\[
N_{\delta_1}^{\mathrm{Pf}}=N_{\delta_2}^{\mathrm{Pf}}
=N_{\delta_3}^{\mathrm{Pf}}=1 .
\]
This local normal form is part of the hypothesis.  The Borcherds divisor
order and the Maass character give an independent automorphic target
check after the local model is supplied; they do not construct the Hall
orientation line and do not use scalar normalization.
For the global orientation-character conclusion below, \textup{(O2)} also
includes the component, boundary, overlap, quotient, and protected
integration compatibility package of
Proposition~\ref{prop:o2-hybrid-compatibility-obstruction}; the generic
wall sign by itself is not a global Weyl-transport datum.

\smallskip
Then:
\begin{enumerate}
\item[\textup{(i)}] (\emph{Pfaffian normalization.})  After the supplied
Pfaffian-to-automorphic comparison
$$
\iota_{\mathrm{aut}}:\mathscr L_{\mathrm{Pf},X}\xrightarrow{\sim}
\mathcal L^5\otimes\nu_{\Delta_5},
$$
compatible with cusp trivialization and squaring, the supplied first-order
object has protected Pfaffian equal to the theta-normalized Borcherds
determinant:
$$
\iota_{\mathrm{aut}}(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X))
\;=\;\mathcal D_X\;=\;\Delta_5.
$$
Without \(\iota_{\mathrm{aut}}\), this is only equality of normalized
formal Borcherds products at \(\mathfrak c_\infty\).
Its scalar trace, in the OP normalization of
Definition~\ref{def:op-normalization-branch}, satisfies
$$
\operatorname{Tr}_{\mathrm{prot}}\bigl((-1)^F\,\mathfrak D_X^{-2}\bigr)
\;=\;-4096\,\Delta_5^{-2}.
$$
\item[\textup{(ii)}] (\emph{Three-sign identification and Weyl character.})  For the three
type-II simple reflections \(\delta_i\) of the Weyl chamber
\(\Poly_{II}\) of Section~\textup{The Weyl chamber and the Weyl vector}
(notation \(\delta_1=2f_2-f_3\), \(\delta_2=2f_{-2}-f_3\),
\(\delta_3=f_3\)),
$$
\epsilon_o(s_{\delta_i})\;=\;-1\;=\;\nu_{\Delta_5}(s_{\delta_i}),
\qquad i=1,2,3,
$$
and therefore
$$
\epsilon_o\big|_{W^{(2)}(\La^{2,1}_{II})}
\;=\;\nu_{\Delta_5}\big|_{W^{(2)}(\La^{2,1}_{II})}.
$$
The three \(\Aut(\Poly_{II})\simeq S_3\) chamber-permuting reflections
\(s_{f_{-2}-f_2},s_{f_2-f_3},s_{f_2+f_3}\) have automorphic Maass value
\(+1\), but no Hall orientation sign on them is asserted unless the
oriented Hall action is separately extended from
\(W^{(2)}(\La^{2,1}_{II})\) to the semidirect product
\(W^{(2)}(\La^{2,1}_{II})\rtimes\Aut(\Poly_{II})\).
\item[\textup{(iii)}] (\emph{Categorical refinement.})  Under
\textup{(D0)}, \textup{(O1)}, \textup{(O1)}\(^+\), and \textup{(O2)},
the supplied chiral protected first-order theory refines the virtual
\(K_0\)-determinant package \([\mathcal V]\), \(\mathcal D_X\) of
Proposition~\ref{prop:virtuality-of-the-square-root}.  Its
decategorification is the Borcherds product
$$
\iota_{\mathrm{aut}}\bigl(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X)\bigr)
\big|_{\mathfrak c_\infty}
=64\,q^{1/2}r^{1/2}s^{1/2}
\!\!\!\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}\!\!
(1-q^nr^ls^m)^{f(nm,l)}=\Delta_5,
$$
and its orientation monodromy character is the Maass character
\(\nu_{\Delta_5}\) restricted to \(W^{(2)}(\La^{2,1}_{II})\).
\end{enumerate}
\end{theorem}

\(D_0\) has the status split of
Theorem~\ref{thm:first-order-d0-certificate}: the normal-ordered lattice
part is proved and the denominator target is imported, but the compact
finite stages, transition maps, and obstruction trivializations of \(D_0\)
are open on the reduced \(K3\times E\) sector.  The orientation clauses
(O1), (O1)\(^+\), and (O2) are likewise
open on that sector;
on Calabi--Yau threefolds (O1) is Joyce--Song \cite{JoyceSong},
the multiplicative orientation cocycle on
\(\mathrm{Perf}(X)\) is Joyce--Upmeier \cite{JoyceUpmeier} and
Joyce--Tanaka--Upmeier \cite{JoyceTanakaUpmeier}, on Calabi--Yau
\(4\)-fold analogues the unreduced orientation exists by Borisov--Joyce
\cite{BorisovJoyce}, Cao--Gross--Joyce \cite{CaoGrossJoyce}, and
Bojko's quasi-projective Borisov--Joyce extension \cite{Bojko};
the virtual-cycle constructions of Oh--Thomas \cite{OhThomasI},
\cite{OhThomasII} and rank-one
Pin\(^c\)-orientation sign conventions in DT/PT Hilbert-scheme models
are compatible with the BBDJS/Joyce--Upmeier framework and with the
Cao--Kool--Monavari Calabi--Yau \(4\)-fold orientation package
\cite{CaoKoolMonavari}; non-compact and Joyce--Song extensions are
Bojko \cite{Bojko}.  These sources supply the orientation technology and
partial local inputs.  They do not by themselves prove the
cosection-reduced \(K3\times E\) quotient orientation, its
\(E[2]\)-linearization, or its type-II Weyl-equivariant lift.  The
cosection-induced
parity flip
\(\mathrm{vd}^{\mathrm{red}}=\mathrm{vd}^{\mathrm{std}}+1\) of the
Maulik--Toda / Oberdieck reduced obstruction theory
\cite{MaulikTodaGV,OberdieckReducedPT} is absorbed into
(O1) as a \(\mathbb Z/2\)-grading shift
\(o^{\mathrm{red}}_{\mathcal C}=o^{\mathrm{std}}_{\mathcal C}\otimes\Pi\)
of the BBDJS \cite{BBDJS2015} line under cosection contraction of
the PTVV \cite{PTVV2013} \((-1)\)-shifted symplectic form by
\(\sigma_{K3}\) (clause (P4) of
Open Problem~\ref{op:orientation-monodromy-character}).  This parity
shift is part of the reduced orientation datum and may be compatible
with the fermionic grading used in the protected supertrace.  It is not
the source of the OP scalar minus sign and it does not determine the
Hall reflection character.  The latter must be computed from monodromy
of the orientation line around the type-II walls.  The theorem therefore
has certificate form: granted \textup{(D0)}, \textup{(O1)},
\textup{(O1)}\(^+\), and \textup{(O2)}, the normalization and character
follow.

\begin{proof}[Proof of Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}]

\emph{Step 1 (Pfaffian product from the supplied first-order datum).}
By \textup{(D0)}, the compact first-order object \(\mathfrak D_X\) and
its normal-ordered primitive multiplicities are supplied.  By
Definition~\ref{def:orientation-line}, the orientation line of a stable
charge-\(c\) object satisfies
\(o_{\mathcal C}^{\otimes 2}\simeq
\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C)\).  The hypothesis (O1)
promotes this to an extension-multiplicative system: on every direct sum
\(\mathcal C\oplus\mathcal C'\),
\(o_{\mathcal C\oplus\mathcal C'}\simeq
o_{\mathcal C}\otimes o_{\mathcal C'}\), compatibly with the Hall
extension stack and descended under the reduced \(E\)-quotient.  Thus
the supplied \(\mathfrak D_X\) has a protected Pfaffian product whose
exponent in normal-ordered Gram degree \((n,l,m)\), by the supplied
\(D_0\) signed-superdimension residual, is
\[
\sdim P^\Pi_{X,(n,l,m)}=f(nm,l).
\]
With the leading cusp normalization fixed by the theta coefficient,
the graded product is
$$
\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X)
=v_0\,\sdet_{\mathcal V}(1-x)
\quad\text{with}\quad v_0=64q^{1/2}r^{1/2}s^{1/2},
$$
where \(\sdet\) is the superdeterminant of
Proposition~\ref{prop:virtuality-of-the-square-root}.  The theorem
does not construct \(\mathfrak D_X\); it identifies the Pfaffian of a
supplied object satisfying \textup{(D0)} and \textup{(O1)}.

\emph{Step 2 (Comparison with the automorphic section).}
Proposition~\ref{prop:bgn-identification} identifies
\(v_0\,\sdet_{\mathcal V}(1-x)\) with the Igusa cusp form \(\Delta_5\) at
the level of Fourier coefficients.  To state an equality of sections,
the supplied \(D_0\)-Pfaffian datum must also contain an isomorphism
\[
\iota_{\mathrm{aut}}:
\mathscr L_{\mathrm{Pf},X}\xrightarrow{\sim}
\mathcal L^5\otimes\nu_{\Delta_5}
\]
compatible with the cusp trivialization and with squaring to
  \(\mathcal L^{10}\).  Under this supplied comparison,
\(\iota_{\mathrm{aut}}(\operatorname{pf}_X)\) and \(\Delta_5\) have the
same Borcherds expansion at \(\mathfrak c_\infty\), hence are equal.
By the \(q\)-expansion principle for holomorphic genus-two Siegel modular
forms with Maass character, after the supplied line comparison and cusp
trivialization, equality of this cusp expansion gives equality of
sections.
Without \(\iota_{\mathrm{aut}}\), the conclusion is only equality of
normalized formal products.

\emph{Step 3 (Scalar square in OP normalization).}
Squaring forgets the orientation.  Under
\(\iota_{\mathrm{aut}}^{\otimes2}\),
\[
\iota_{\mathrm{aut}}^{\otimes2}
\bigl(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X)^2\bigr)
=\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C)|_{\mathrm{tot}}
=\Delta_5^2,
\]
as sections of \(\mathcal L^{10}\) (the squared automorphic line is the
trivially-charactered determinant, since
\(\Delta_5^2=\Delta_{10}\) is scalar by
Section~\textup{The normalized cusp form}).
The protected scalar trace is then
\(\operatorname{Tr}_{\mathrm{prot}}((-1)^F\mathfrak D_X^{-2})
=C_{\square,X}\,\Delta_5^{-2}\) for
some normalization scalar \(C_{\square,X}\); the explicit
\(C_{\square,X}=-4096\) follows
from Proposition~\ref{prop:op-normalization} of Oberdieck--Pixton, which
gives
\(Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1}=-4096\,\Delta_5^{-2}\),
together with the arithmetic \(-4096=-(64)^2\) of the squared
theta-leading coefficient and the OP scalar sign convention recorded in
Definition~\ref{def:op-normalization-branch}.

\emph{Step 4 (Orientation-character identity (ii)).}  By (O2), after the
full wall-atlas compatibility package has been supplied, each
type-II simple reflection \(s_{\delta_i}\) acts on
\(o_{\mathcal C}\) by the parity of its oriented real normal modes.
Lemma~\ref{lem:thm3-three-sign-computation} is the Hall-side local
calculation: under the supplied Pfaffian normal form
\(N_{\delta_i}^{\mathrm{Pf}}=1\), hence
\(\epsilon_o(s_{\delta_i})=(-1)^{N_{\delta_i}^{\mathrm{Pf}}}=-1\).
Lemma~\ref{lem:maass-multiplier-restriction} is the independent
automorphic calculation:
\(\nu_{\Delta_5}(s_{\delta_i})=-1\) for the same three simple
reflections, and \(+1\) on the three chamber-permuting
\(\Aut(\Poly_{II})\)-reflections.  The latter \(+1\)-values are
automorphic target data only; they are not Hall orientation signs unless
a semidirect-product Hall lift is supplied.

The passage from the three simple Hall signs to a character on the full
type-II Weyl group is purely group-theoretic only after (O1)\(^+\) has
killed the projective determinant-line cocycle and the quotient
trivialization torsors of
Lemma~\ref{lem:weyl-quotient-orientation-obstruction}.  Then (O1)\(^+\)
gives an honest lifted Coxeter action on the reduced quotient
orientation.  By
Lemma~\ref{lem:weyl-equivariant-orientation-cocycle},
\[
W^{(2)}(\La^{2,1}_{II})_{\mathrm{ab}}\simeq(\Z/2)^3,
\]
with one generator for each \(s_{\delta_i}\).  Therefore two
\(\{\pm1\}\)-valued characters of \(W^{(2)}(\La^{2,1}_{II})\) that agree
on \(s_{\delta_1},s_{\delta_2},s_{\delta_3}\) agree everywhere.  Hence
\(\epsilon_o=\nu_{\Delta_5}\) on \(W^{(2)}(\La^{2,1}_{II})\).

\emph{Step 5 (Categorical refinement (iii)).}  The chiral protected
theory is supplied by \textup{(D0)}.  Steps 1--4 identify its
decategorification and character: the class
\([\mathcal V]\in K_0(\mathrm{sVect}_{\mathrm{fd}})\) is the
decategorified primitive content, the formal product
\(v_0\,\sdet_{\mathcal V}(1-x)\) is the Pfaffian section
\(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X)\), and the formal
character equality is the orientation-character identity of (ii).  At
the chosen isotropic cusp \(\mathfrak c_\infty\) this decategorification
is the Borcherds product, and the orientation monodromy character is
\(\nu_{\Delta_5}\) on the type-II Weyl group as computed.
\end{proof}

\begin{lemma}[Conditional Pfaffian signs on the type-II simple walls]
\label{lem:thm3-three-sign-computation}
Under the compact first-order certificate (D0), the strong orientation
datum (O1), the Weyl-equivariant extension (O1)\(^+\), and the
Pfaffian local model (O2) of
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}, for each
\(\delta_i\in\{\delta_1,\delta_2,\delta_3\}\) the
orientation-monodromy reflection sign is
$$
\epsilon_o(s_{\delta_i})\;=\;(-1)^{N_{\delta_i}^{\mathrm{Pf}}}\;=\;-1,
\qquad N_{\delta_i}^{\mathrm{Pf}}=1.
$$
Here \(N_{\delta_i}^{\mathrm{Pf}}\) is the number of supplied odd real
normal modes in the local Pfaffian normal form.  It is not the
automorphic divisor order, although the independent target order agrees
in the three simple type-II cases.  The lemma makes no Hall-orientation
claim for the three chamber-permuting reflections in
\(\Aut(\Poly_{II})\).
\end{lemma}

\begin{proof}
\emph{Local Pfaffian calculation.}  Hypothesis (O2) supplies, at a
generic point of each \(\Hpl_{\delta_i}\), a real local equation
\(u_i=u_{\delta_i}\) with \(s_{\delta_i}(u_i)=-u_i\) and a normal
determinant-complex splitting
\[
K_{\delta_i}^{\mathrm{nor}}
\simeq
\bigl[\mathbb R\xrightarrow{\,u_i\,}\mathbb R\bigr].
\]
The normal Pfaffian section is \(u_i\) times an invariant unit after
quotient-orientation trivialization.  Transport by the reflection sends
\(u_i\) to \(-u_i\), so it multiplies the Pfaffian line by \(-1\); after
squaring, the determinant section \(u_i^2\) is fixed.
Hence one supplied odd real normal mode gives
\[
\epsilon_o(s_{\delta_i})
=(-1)^{N_{\delta_i}^{\mathrm{Pf}}}=(-1)^1=-1,
\qquad i=1,2,3.
\]

\emph{Independent automorphic target labels.}  The three roots
\(\delta_1=2f_2-f_3\), \(\delta_2=2f_{-2}-f_3\), \(\delta_3=f_3\) have
Gram pairing
\((\delta_i,\delta_i)=2\), \((\delta_i,\delta_j)=-2\) for \(i\ne j\),
by the matrix displayed in
Section~\textup{The Weyl chamber and the Weyl vector}.  All three are
real simple roots of the Lorentzian Kac--Moody algebra \(\autcor\).  In
the Gram-index
chart of Definition~\ref{def:gram-index-degrees-weyl-chamber} (using
\(\alpha(\gamma)=2nf_2-lf_3+2mf_{-2}\)), the three simple walls
correspond to the lattice triples
$$
\delta_1\;\leftrightarrow\;(n,l,m)=(1,1,0),\qquad
\delta_2\;\leftrightarrow\;(0,1,1),\qquad
\delta_3\;\leftrightarrow\;(0,-1,0),
$$
matching the K3 elliptic-genus support
\(f(0,\pm1)=1\), \(f(0,0)=10\), \(f(nm,l)=0\) for \(4nm-l^2<-1\).
Thus the automorphic divisor order
\[
d_{\delta_i}^{\mathrm{aut}}
:=\ord_{\Hpl_{\delta_i}}(\Delta_5)
\]
is \(1\) for \(i=1,2,3\).  This target order is a check against the
supplied local model; it is not a construction of the compact Hall
orientation line.

The computation is:
\begin{center}
\small
\begin{tabular}{p{0.16\textwidth}p{0.31\textwidth}p{0.13\textwidth}p{0.13\textwidth}p{0.12\textwidth}}
\hline
\(\delta_i\) & Gram label & \(N_{\delta_i}^{\mathrm{Pf}}\) &
\(d_{\delta_i}^{\mathrm{aut}}\) & \(\epsilon_o\) \\
\hline
\(\delta_1=2f_2-f_3\) &
\((n,l,m)=(1,1,0)\), \(f(0,1)=1\) & \(1\) & \(1\) & \(-1\) \\
\(\delta_2=2f_{-2}-f_3\) &
\((n,l,m)=(0,1,1)\), \(f(0,1)=1\) & \(1\) & \(1\) & \(-1\) \\
\(\delta_3=f_3\) &
\((n,l,m)=(0,-1,0)\), \(f(0,-1)=1\) & \(1\) & \(1\) & \(-1\) \\
\hline
\end{tabular}
\end{center}
\end{proof}

\begin{remark}[Automorphic target check via the Maass character]
The argument below verifies the target character
\(\nu_{\Delta_5}|_{W^{(2)}(\La^{2,1}_{II})}\) using only the Maass
multiplier and the Borcherds product.  It does not construct the Hall
orientation character \(\epsilon_o\).  The comparison
\(\epsilon_o=\nu_{\Delta_5}\) remains a geometric statement supplied
by (O1), (O1)\(^+\), and (O2).  No scalar normalization enters this
sign comparison: replacing \(\Delta_5\) by \(c\Delta_5\),
\(c\in\mathbb C^\times\), changes neither the Maass character nor the
divisor orders.  The factor \(64\) only names the monic Borcherds product
\(D_5=64^{-1}\Delta_5\), and the OP/DT scalar \(-4096\) is unused.

\emph{Step 1 (Maass-side coboundary).}  Define the automorphic parity
cochain
\(\varepsilon_{\Delta}^{\mathrm{aut}}\colon
W^{(2)}(\La^{2,1}_{II})\to\Z/2\) by
\(\varepsilon_{\Delta}^{\mathrm{aut}}(g):=\tfrac12(1-\nu_{\Delta_5}(g))\),
so
\((-1)^{\varepsilon_{\Delta}^{\mathrm{aut}}(g)}=\nu_{\Delta_5}(g)\).
Maass's character is a homomorphism \cite{MAASS:1},
\cite[Section 3]{GN}, \cite{Gritsenko99}, hence
$$
c_{\Delta}^{\mathrm{aut}}(g,h)
:=\varepsilon_{\Delta}^{\mathrm{aut}}(g)
+\varepsilon_{\Delta}^{\mathrm{aut}}(h)
-\varepsilon_{\Delta}^{\mathrm{aut}}(gh)
\equiv0\pmod2.
$$
The displayed value of \(\nu_{\Delta_5}\) on the six generators is
Lemma~\ref{lem:maass-multiplier-restriction}: \(-1\) on
\(s_{\delta_1},s_{\delta_2},s_{\delta_3}\), \(+1\) on
\(s_{f_{-2}-f_2},s_{f_2-f_3},s_{f_2+f_3}\); equivalently
\(\varepsilon_{\Delta}^{\mathrm{aut}}(s_{\delta_i})=1\) and
\(\varepsilon_{\Delta}^{\mathrm{aut}}(s_{f_{-2}-f_2})
=\varepsilon_{\Delta}^{\mathrm{aut}}(s_{f_2-f_3})
=\varepsilon_{\Delta}^{\mathrm{aut}}(s_{f_2+f_3})=0\).

\emph{Step 2 (Verification on the nine pairs of three-wall generators).}
For the three-wall computation the only nontrivial check is on the
\(3\times3\) table of pairs \((g,h)\in\{s_{\delta_1},s_{\delta_2},
s_{\delta_3}\}^{\times2}\).  The relations used here are only
\(s_{\delta_i}^2=1\) and the fact that \(\nu_{\Delta_5}\) is a
character.  For \(i\ne j\) the Coxeter exponent is \(m_{ij}=\infty\), so
there is no braid relation to impose:
\begin{itemize}
\item Diagonal \((g,g)=(s_{\delta_i},s_{\delta_i})\) for \(i=1,2,3\)
(three pairs): \(gh=1\), \(\varepsilon_{\Delta}^{\mathrm{aut}}(gh)=0\),
so \(c_{\Delta}^{\mathrm{aut}}(g,h)=1+1-0=2\equiv0\pmod2\).
\item Off-diagonal \((g,h)=(s_{\delta_i},s_{\delta_j})\), \(i\ne j\)
(six pairs): since \(\nu_{\Delta_5}\) is a character,
\(\nu_{\Delta_5}(gh)=(-1)(-1)=+1\), giving
\(\varepsilon_{\Delta}^{\mathrm{aut}}(gh)=0\) and
\(c_{\Delta}^{\mathrm{aut}}(g,h)=1+1-0=2\equiv0\pmod2\).
\end{itemize}
All nine pairs vanish modulo \(2\); \(c_{\Delta}^{\mathrm{aut}}\) is a
coboundary on the three-wall block, with primitive
\(\varepsilon_{\Delta}^{\mathrm{aut}}\).  This is an automorphic
calculation only.

\emph{Step 3 (Divisor-exponent target check).}  The Gritsenko--Nikulin
specialization of Borcherds' product theorem \cite{Borcherds95},
\cite[Theorem~2.1, (2.1)--(2.3), Example~2.4]{GNII}, together with the
theta normalization \cite[Theorem~4.1]{GN}, writes
$$
D_5=64^{-1}\Delta_5
=\operatorname{Borch}(\phi_{0,1})
=q^{1/2}r^{1/2}s^{1/2}\!\!
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}^+}
(1-q^nr^ls^m)^{f(nm,l)}
$$
in the type-II cusp polarization
\((q,r,s)=(e^{2\pi iz_1},e^{2\pi iz_2},e^{2\pi iz_3})\).  This fixes the
automorphic divisor orders
\[
d_{\delta}^{\mathrm{aut}}:=\ord_{\Hpl_\delta}(\Delta_5).
\]
For the three type-II roots these orders are
\[
d_{\delta_1}^{\mathrm{aut}}=f(0,1)=1,\qquad
d_{\delta_2}^{\mathrm{aut}}=f(0,1)=1,\qquad
d_{\delta_3}^{\mathrm{aut}}=f(0,-1)=1.
\]
Together with Lemma~\ref{lem:maass-multiplier-restriction}, this gives
the automorphic target signs
\(\nu_{\Delta_5}(s_{\delta_i})=-1=(-1)^{d_{\delta_i}^{\mathrm{aut}}}\).
The symbol \(d_{\delta}^{\mathrm{aut}}\) is deliberately distinct from
the Pfaffian normal-mode rank \(N_{\delta}^{\mathrm{Pf}}\) in (O2).

The chamber-permuting roots
\[
\alpha_1=f_{-2}-f_2,\qquad
\alpha_2=f_2-f_3,\qquad
\alpha_3=f_2+f_3
\]
are type-I roots in
\(\La^{2,1}\setminus\La^{2,1}_{II}\).  In the type-II parametrization
\(\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}\), the coefficients of \(f_2\) and
\(f_{-2}\) must be even.  Thus \(k=1\) does not contribute to any
\(\alpha_i\).  For \(2\alpha_1\) one obtains either
\((-1,0,1)\) or \((1,0,-1)\), outside
\(\Gamma_{\mathrm{eff}}\).  For \(2j\alpha_2\) one obtains
\((j,2j,0)\), and for \(2j\alpha_3\) one obtains \((j,-2j,0)\);
the \(q^0\)-row of \(\phi_{0,1}\) has support only at
\(l=0,\pm1\), so \(f(0,\pm2j)=0\) for \(j\ge1\)
\cite[\S2.2]{EZ:1}.  Hence
\[
\ord_{\Hpl_{\alpha_i}}(\Delta_5)=0,\qquad i=1,2,3,
\]
and Lemma~\ref{lem:maass-multiplier-restriction} gives automorphic
monodromy \(+1\) around these chamber-permuting reflections.

\emph{What this check proves.}  It proves the automorphic target values
\[
\nu_{\Delta_5}(s_{\delta_i})=-1,\qquad
\nu_{\Delta_5}(s_{f_{-2}-f_2})
=\nu_{\Delta_5}(s_{f_2-f_3})
=\nu_{\Delta_5}(s_{f_2+f_3})=+1.
\]
It does not prove that a compact Hall orientation line transports with
these signs.  That bridge is exactly the geometric content of the
Pfaffian local model and Weyl-equivariant orientation cocycle.
\end{remark}

\begin{remark}[Comparison of the two proofs]
\label{rem:thm3-cross-verification}
The proof of Lemma~\ref{lem:thm3-three-sign-computation} and the
Maass-character check have different logical roles.  The first computes
the Hall orientation signs from the supplied Pfaffian local model (O2).
The second computes the automorphic target signs of
\(\nu_{\Delta_5}\).  The equality
\(\epsilon_o=\nu_{\Delta_5}\) follows only after the local Dirac model
supplies the Pfaffian normal-mode parity and the Weyl-equivariant
orientation cocycle transports it as a character.  The Borcherds product
and Maass character supply the target character but not the Hall
orientation character.
\end{remark}

\begin{remark}[Imaginary roots are not Weyl reflections]
\label{lem:imaginary-wall-orientation-extension}
The Weyl group of the Borcherds--Kac--Moody datum is generated by real
simple roots only.  Imaginary simple roots contribute to the
Weyl--Kac--Borcherds denominator through the additive correction
coefficients \(m(a)\) and \(\tau(a)\) of Gritsenko--Nikulin
\cite[Theorem~2.1, (2.1)--(2.3)]{GNII}, \cite[Sections~3--4]{GN}; they
do not define reflections \(s_a\) in \(W^{(2)}(\La^{2,1}_{II})\).
Thus the orientation character
\[
\epsilon_o:W^{(2)}(\La^{2,1}_{II})\to\{\pm1\}
\]
is a real-root reflection datum.  A compact Hall theory may also have
local divisor monodromy around imaginary components of the Borcherds
divisor, but that monodromy is not a Weyl character and is not asserted
here.  In particular, no formula \(\epsilon_o(s_a)=(-1)^{m(a)}\) is
available for imaginary \(a\), and the coefficients \(m(a)\) must not be
identified with the visible product exponents \(f(nm,l)\) without the
Gritsenko--Nikulin additive-side computation.
\end{remark}

\begin{lemma}[Pure group-theoretic Weyl sign extension]
\label{lem:weyl-equivariant-orientation-cocycle}
For any signs \(\epsilon_i\in\{\pm1\}\), \(i=1,2,3\), there is a unique
character
\[
\chi_\epsilon:W^{(2)}(\La^{2,1}_{II})\longrightarrow\{\pm1\}
\]
with \(\chi_\epsilon(s_{\delta_i})=\epsilon_i\).  Hence a supplied
Weyl-equivariant determinant-line transport datum (O1)\(^+\), together
with local Pfaffian signs
\(\epsilon_i=(-1)^{N_{\delta_i}^{\mathrm{Pf}}}\) from (O2),
induces a unique orientation character.  For
\(N_{\delta_1}^{\mathrm{Pf}}=N_{\delta_2}^{\mathrm{Pf}}
=N_{\delta_3}^{\mathrm{Pf}}=1\), this character is the determinant
character on \(W^{(2)}(\La^{2,1}_{II})\).
\end{lemma}

\begin{proof}
The Cartan matrix of the type-II simple reflections, by
\((\delta_i,\delta_i)=2\) and \((\delta_i,\delta_j)=-2\) for \(i\ne j\)
(Section~\textup{The Weyl chamber and the Weyl vector}), is
\[
\begin{pmatrix}2&-2&-2\\-2&2&-2\\-2&-2&2\end{pmatrix}.
\]
Thus \(A_{ij}A_{ji}=4\) for \(i\ne j\), so the Coxeter exponents are
\(m_{ij}=\infty\).  The chamber calculation in
Section~\textup{The Weyl chamber and the Weyl vector} identifies
\(\{\delta_1,\delta_2,\delta_3\}\) as the primitive walls of the
fundamental type-II chamber \(\Poly_{II}\), and the Gritsenko--Nikulin
reflection-group input supplies the Coxeter presentation from these
walls.  Hence the type-II reflection group is the universal rank-three
Coxeter group
\[
W^{(2)}(\La^{2,1}_{II})
\simeq
\langle s_{\delta_1},s_{\delta_2},s_{\delta_3}\mid
s_{\delta_1}^2=s_{\delta_2}^2=s_{\delta_3}^2=1\rangle .
\]
Its abelianization is
$$
W^{(2)}(\La^{2,1}_{II})\big/[W^{(2)},W^{(2)}]
\;\simeq\;(\Z/2)^3,
$$
one \(\Z/2\) per Coxeter generator \(s_{\delta_i}\).

The only defining relations are \(s_{\delta_i}^2=1\).  Any assignment
\(s_{\delta_i}\mapsto\epsilon_i\in\{\pm1\}\) respects these relations,
since \(\epsilon_i^2=1\), and therefore extends uniquely to a
\(\{\pm1\}\)-valued character, equivalently to a homomorphism factoring
through \((\Z/2)^3\).  This is pure group theory.  Applied to a supplied
determinant-line action from (O1)\(^+\), the scalars computed by (O2) on
the three generators give the orientation character.  If all three
\(\epsilon_i=-1\), the character sends every Coxeter generator to
\(-1\), hence is the determinant character.
\end{proof}

\begin{lemma}[Weyl quotient-orientation obstruction package]
\label{lem:weyl-quotient-orientation-obstruction}
Let \(W=W^{(2)}(\La^{2,1}_{II})\), and let
\(\mathcal G_W\) be the action groupoid of the retained reduced quotient
strata under the supplied type-II wall transports.  On a complete
\(W\)-orbit with constant coefficients this groupoid cohomology reduces to
ordinary group cohomology of \(W\).  Suppose (O1) supplies an ordinary
orientation line together with the full reduced quotient package
\[
\theta_{\mathcal C}=
\left(\theta^{\mathrm{red}}_{\mathcal C},
\theta^{E,\mathrm{free}}_{\mathcal C},
\{(\theta^{E,N}_{\mathcal C},\lambda^{E,N}_{\mathcal C}=0)\}_{N\ge2}
\right)
\]
on every charge stratum used by the compact/wrapped Hall
correspondences.  A choice of simple wall transports \(\tau_i\) gives an
honest Weyl-equivariant orientation on the reduced quotient if and only
if the following two independent obstructions vanish.

\[
[c_o]=0\in H^2(\mathcal G_W;\underline{\mathbb F}_2)
\]
with a killing groupoid cochain
\(b\in C^1(\mathcal G_W;\underline{\mathbb F}_2)\) for which the
renormalized lifts
\(\widetilde\tau_w=(-1)^{b(w)}\tau_w\) satisfy
\(\widetilde\tau_i^{\,2}=1\) for the three simple reflections; and
\[
\omega_{i,\mathcal C}=0\in
H^1(\mathfrak M^{\mathrm{red}}_{s_{\delta_i}\mathcal C};\mathbb F_2)
\oplus
\bigoplus_{N\ge2}H^1(BE[N];\mathbb F_2)
\]
for every simple reflection and every relevant charge stratum, with the
word defects obeying their natural torsor cocycle law.  Since the
type-II Weyl group has no braid relations among the three simple
reflections, the generator-square constraints are the only Coxeter
relation constraints after the projective cocycle is killed.  Killing
\([c_o]\) gives an action on the ordinary determinant line; killing the
\(\omega_{i,\mathcal C}\) gives an action on the quotient orientation
with its finite-stabilizer zero characters.  Neither condition is
implied by the Maass character \(\nu_{\Delta_5}\).
\end{lemma}

\begin{proof}
The chosen transports over words in the generators define a central
\(\{\pm1\}\)-extension of the retained action groupoid precisely when
their composition defect is a \(2\)-cocycle
\[
w'^*\tau_w\circ\tau_{w'}=(-1)^{c_o(w,w')}\tau_{ww'}.
\]
Changing the word lifts by \((-1)^{b(w)}\) replaces \(c_o\) by
\(c_o+\delta b\).  Hence the projective determinant-line action becomes
an honest action on the ordinary orientation line exactly when
\([c_o]\) is zero and the chosen splitting is normalized on the
relations.  By Lemma~\ref{lem:weyl-equivariant-orientation-cocycle}, the
type-II Coxeter presentation is the free product of three copies of
\(\mathbb Z/2\).  Thus the only relation-level normalizations are
\(\widetilde\tau_i^{\,2}=1\) on a complete \(W\)-orbit; on a truncated
finite system this is the corresponding statement in the retained action
groupoid.

After the ordinary line action is honest, the quotient
null-trivializations form torsors under
\[
H^1(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2)
\oplus\bigoplus_{N\ge2}H^1(BE[N];\mathbb F_2).
\]
The difference between the transported trivialization and the chosen
trivialization on the reflected stratum is exactly
\(\omega_{i,\mathcal C}\).  Composition of transports gives the usual
torsor cocycle law
\(\omega_{ww',\mathcal C}=w'^*\omega_{w,\mathcal C}+
\omega_{w',\mathcal C}\).  Therefore vanishing on the retained
generators, together with the square coherences already imposed above,
propagates to every word in the retained action groupoid, and to every
word of \(W\) only after a complete orbit has been supplied.  Conversely,
any honest Weyl action on the reduced quotient orientation preserves the
chosen null-trivializations and zero finite characters, so both \(c_o\)
and all \(\omega_{i,\mathcal C}\) vanish after the corresponding choices.
The construction uses only determinant-line and quotient-torsor data, not
the scalar automorphic character.
\end{proof}

\begin{corollary}[Finite-stage Weyl cocycle over the quotient character
system]
\label{cor:finite-stage-weyl-cocycle-character-system}
Fix a finite compact/wrapped HN stage \(R\), a finite test set
\(\mathcal O_R\) of reduced charge strata closed under the simple
type-II wall transports retained at height \(R\), and a
quotient-orientation character system on \(\mathcal O_R\) in the sense of
Proposition~\ref{prop:finite-stage-quotient-orientation-character-system}.
Choose determinant-line lifts \(\tau_{i,R,\mathcal C}\) for the simple
type-II reflections whenever both \(\mathcal C\) and
\(s_{\delta_i}\mathcal C\) lie in \(\mathcal O_R\).  For words whose
intermediate strata remain in \(\mathcal O_R\), choose word lifts
\(\tau_{w,R,\mathcal C}\) and define
\[
w'^*\tau_{w,R,w'\mathcal C}\circ \tau_{w',R,\mathcal C}
=(-1)^{c_{o,R}(w,w';\mathcal C)}
\tau_{ww',R,\mathcal C}.
\]
Then \(c_{o,R}\) is a \(2\)-cocycle for the finite action groupoid
generated by these retained transports; on any genuine \(W\)-orbit it is
the corresponding group \(2\)-cocycle with values in locally constant
\(\mathbb F_2\)-functions on \(\mathcal O_R\).  Changing the word lifts by
a \(1\)-cochain changes \(c_{o,R}\) by a coboundary.  The
quotient-trivialization defect
\[
\omega_{w,R,\mathcal C}
\in
H^1(\mathfrak M^{\mathrm{red}}_{w\mathcal C};\mathbb F_2)
\oplus\bigoplus_{N\ge2}H^1(BE[N];\mathbb F_2)
\]
satisfies
\[
\omega_{ww',R,\mathcal C}
=w'^*\omega_{w,R,\mathcal C}+\omega_{w',R,\mathcal C}.
\]
Thus the finite-stage Weyl lift exists on \(\mathcal O_R\) if and only
if \(c_{o,R}\) is killed by a cochain normalized on the relations
\(s_{\delta_i}^2=1\), and the defects \(\omega_{i,R,\mathcal C}\) vanish
for the three simple reflections.  A cofinal family of such finite-stage
splittings, compatible with the HN transition maps, is exactly the
Weyl-equivariant lift (O1)\(^+\) on the compact/wrapped sector.  A
non-zero \(c_{o,R}\), a failed square normalization, or a non-zero
\(\omega_{i,R,\mathcal C}\) at one finite stage obstructs (O1)\(^+\).
\end{corollary}

\begin{proof}
The first display is the definition of the composition defect for the
chosen word lifts.  Associativity of determinant-line composition gives
the cocycle identity.  Multiplying \(\tau_{w,R,\mathcal C}\) by
\((-1)^{b(w,\mathcal C)}\) replaces \(c_{o,R}\) by \(c_{o,R}+\delta b\),
so an honest determinant-line action is the same as a splitting of this
central extension, normalized on the Coxeter relations.  For the type-II
subgroup the only Coxeter relations are \(s_{\delta_i}^2=1\).

The quotient-orientation character system is a torsor under the displayed
\(H^1\)-groups.  The difference between the transported trivialization
and the chosen trivialization on the target stratum is therefore the
class \(\omega_{w,R,\mathcal C}\), and functoriality of transport gives
the displayed torsor cocycle law.  Vanishing on the retained simple
generators, together with the square normalizations, propagates to every
retained word in the finite action groupoid; on a genuine \(W\)-orbit
this is the free product \(C_2*C_2*C_2\).  Compatibility in \(R\) is
exactly the finite-stage inverse-system requirement in the compact/wrapped
certificate.  No Maass character or scalar normalization enters the
construction.
\end{proof}

\begin{corollary}[Semidirect wall-transport obstruction]
\label{cor:semidirect-wall-transport-obstruction}
Let
\[
G=W^{(2)}(\La^{2,1}_{II})\rtimes\Aut(\Poly_{II})
\]
and suppose (O1) has been supplied on the reduced quotient strata.  Let
\(\mathcal G_G\) be the action groupoid of the retained strata under the
chosen \(G\)-transports; on a complete \(G\)-orbit with constant
coefficients this reduces to ordinary group cohomology of \(G\).  An
extension of the type-II Weyl orientation transport from \(W\) to \(G\)
is an additional datum.  It exists on the reduced quotient orientation if
and only if the projective determinant-line cocycle for the chosen lifts
to \(\mathcal G_G\),
\[
c_o^G\in Z^2(\mathcal G_G;\underline{\mathbb F}_2),
\]
has trivial class in
\(H^2(\mathcal G_G;\underline{\mathbb F}_2)\), the chosen killing
cochain normalizes the Coxeter relations in \(W\) and the \(S_3\)-relations in
\(\Aut(\Poly_{II})\), and the quotient-torsor defects
\[
\omega_{g,\mathcal C}\in
H^1(\mathfrak M^{\mathrm{red}}_{g\mathcal C};\mathbb F_2)
\oplus\bigoplus_{N\ge2}H^1(BE[N];\mathbb F_2)
\]
vanish for the chosen generators \(g\) of \(G\).  The \(S_3\)-part must
transport the full quotient package
\[
\left(\alpha^{\mathrm{red}},
\alpha^{E,\mathrm{free}},
\{(\beta^{E,N},\lambda^{E,N}=0)\}_{N\ge2}\right)
\]
between chamber-permuted strata.

Consequently the Maass values
\[
\nu_{\Delta_5}(s_{f_{-2}-f_2})
=\nu_{\Delta_5}(s_{f_2-f_3})
=\nu_{\Delta_5}(s_{f_2+f_3})=+1
\]
are only automorphic target values.  They do not construct a Hall
orientation sign on the semidirect-product generators.  Without the
vanishing above, the manuscript asserts the Hall orientation character
only on \(W^{(2)}(\La^{2,1}_{II})\), under (O1), (O1)\(^+\), and (O2).
\end{corollary}

\begin{proof}
The proof is the same obstruction calculation as
Lemma~\ref{lem:weyl-quotient-orientation-obstruction}, with
\(\mathcal G_W\) replaced by \(\mathcal G_G\).  A projective action on the
determinant line is a central \(\mathbb F_2\)-extension of the retained
action groupoid, hence is classified by \([c_o^G]\).  On a complete
\(G\)-orbit this is the usual group-cohomology class, and a splitting must
respect all relations of the semidirect presentation, not only the three
generator squares in \(W\).  After the
ordinary determinant-line action is honest, the chosen quotient
trivializations remain torsors under the displayed \(H^1\)-groups; their
failure to be preserved is exactly \(\omega_{g,\mathcal C}\).  Vanishing
on a generating set, with the relation coherences, propagates through the
retained action groupoid, and to all of \(G\) only after a complete
\(G\)-orbit has been supplied.  The Maass character is a scalar
automorphic character and has no map to these determinant-line or
quotient-torsor classes.
\end{proof}

\begin{remark}
\label{rem:thm3-honest-status}
\label{rem:thm3-status}
\label{rem:thm3-deliverable}
The table values of \(\nu_{\Delta_5}\) on the six generators
(Lemma~\ref{lem:maass-multiplier-restriction}), the determinant
identity \(\mathcal D_X=\Delta_5\)
(Proposition~\ref{prop:bgn-identification}), and the OP scalar
\(-4096\,\Delta_5^{-2}\) (Proposition~\ref{prop:op-normalization}) are
independent of the compact Hall hypotheses; they are imported or proved
under the cited source hypotheses, normalizations, and chamber
conventions.  The Pfaffian recognition (i), the orientation-character
identity (ii), and the categorical upgrade (iii) are conditional on
(O1), (O1)\(^+\), and (O2).  Lemma~\ref{lem:weyl-equivariant-orientation-cocycle}
identifies the strongest algebraic consequence of a supplied
Weyl-equivariant lift: the sign factors through the
\((\Z/2)^3\) abelianization of \(W^{(2)}(\La^{2,1}_{II})\).
Lemma~\ref{lem:weyl-quotient-orientation-obstruction} separates this
group-theoretic sign extension from the projective determinant-line and
quotient-torsor obstructions that must vanish before there is an honest
Weyl action on the reduced quotient orientation.
Open: (O1) for the reduced
\(E\)-quotiented Weyl-equivariant compact critical \(K3\times E\)
Hall/CoHA sector.  Joyce--Upmeier \cite{JoyceUpmeier},
Joyce--Tanaka--Upmeier \cite{JoyceTanakaUpmeier}, and
Borisov--Joyce--Bojko \cite{BorisovJoyce} cover the unreduced
\(\mathrm{Perf}(X)\), and \cite{JoyceUpmeier} covers shifted
symplectic stacks, but the reduced \(E\)-quotient with type-II
Weyl-equivariant lift is not in the literature; (O2) is the supplied
Pfaffian local normal form on type-II walls of that sector, not a
consequence of the automorphic product.  The local obstruction certificate
of Proposition~\ref{prop:o2-local-obstruction-certificate} names the
missing chart, splitting, invariant-unit, and rank-one normal-mode
computations.  The squared scalar branch
\(Z^X_{\mathrm{OP}}=-4096\,\Delta_5^{-2}\) is orientation-forgetful;
rescaling \(\Delta_5\) by a nonzero scalar leaves \(\nu_{\Delta_5}\)
invariant.  The three type-II rows match Borcherds automorphic divisor
orders \(d_{\delta_i}^{\mathrm{aut}}=1\) via \(f(nm,l)\) at
\((1,1,0),(0,1,1),(0,-1,0)\); the independent automorphic check at the
three chamber-permuting type-I roots yields divisor order \(0\) from the
explicit support of \(\phi_{0,1}\) \cite[\S2.2]{EZ:1}.
\end{remark}

\begin{openproblem}[Protected one-particle lift]
Construct, if it exists, a protected one-particle object with a
\(\Gamma_{\mathrm{eff}}\)-graded super-vector-space decomposition
$$
\mathcal H^{\mathrm{1p,ch}}
=\bigoplus_{\gamma\in\Gamma_{\mathrm{eff}}}
\mathcal H^{\mathrm{1p,ch}}_\gamma
$$
with protected superdimensions
$$
\operatorname{Tr}_{\mathcal H^{\mathrm{1p,ch}}_{(n,l,m)}}(-1)^F
=f(nm,l).
$$
The determinant construction uses only the virtual classes
\(\mathbb U_{n,l}\) and their signed dimensions.  The algebraic object
constructed from the same charge grading and the same signed
multiplicities is the Borcherds denominator algebra.  Such a lift would
still be weaker than the holomorphic \(E_3\)-factorization algebra,
because it would not by itself supply the collision law.
\end{openproblem}

\section{The normalized cusp form}

Freitag \cite{FREITAG:1}, Van der Geer \cite{VDGEER:1}, and Igusa
\cite{Igusa1962,Igusa1964II}: the
even-weight scalar subring is
$$M^{\mathrm{even}}_*(\Sp_4(\Z)) = \C[E_4,E_6,\Delta_{10},\Delta_{12}],$$
$$\mathrm{wt}(E_4,E_6,\Delta_{10},\Delta_{12})=(4,6,10,12).$$
$$\Delta_{10}=\Delta_5^2,\qquad
\mathrm{wt}(\Delta_5)=5,\qquad
\Delta_5|_5 g=\nu_{\Delta_5}(g)\Delta_5.$$
$$\Delta_5 =
\prod_{\substack{a,b\in (\Z/2\Z)^2\\{}^t ab\equiv 0 \mod 2}}
\nu_{a,b},$$
$$\nu_{a,b}(z)=
\sum_{l\in\Z^2}\exp\bigl(\pi i(z[l+\tfrac12a]+{}^tbl)\bigr),
\qquad z[x]={}^txzx.$$

For $M = \begin{pmatrix} A & B\\ C & D\end{pmatrix}
\in \Sp_4(\Z)$, Maass's character \cite{MAASS:1}
$$\nu_{\Delta_5}:\Sp_4(\Z)\rightarrow \C^\times,\qquad
|\nu_{\Delta_5}|=1,$$
is determined on the standard generators by
$$\nu_{\Delta_5}\begin{pmatrix}0 & \Id_2\\
-\Id_2 & 0\end{pmatrix} = 1,$$ $$\nu_{\Delta_5}\begin{pmatrix}\Id_2 & B\\
0 & \Id_2\end{pmatrix} = (-1)^{b_1 + b_2 + b_3},$$
$$\nu_{\Delta_5}\begin{pmatrix}{}^tA^{-1} & 0\\
0 & A\end{pmatrix} = (-1)^{(1 + a_1 + a_4)(1 + a_2 + a_3) + a_1a_4}$$
with $A = \begin{pmatrix}a_1 & a_2\\
a_3 & a_4\end{pmatrix} \in \GL_2(\Z)$ and $B = \begin{pmatrix}b_1 &
b_2\\
b_2 & b_3\end{pmatrix} \in M_{2\times2}(\Z).$

$\Delta_5$ is a weight-$5$ form with character
$\nu_{\Delta_5}$, and $\Delta_5^2=\Delta_{10}$ is scalar.

For
$$Z=\begin{pmatrix}z_1&z_2\\z_2&z_3\end{pmatrix},$$
$$\Delta_5(Z) =
\sum_{\substack{n,l,m\equiv 1 \bmod 2\\4nm-l^2>0\\n,m>0}}
c_\Delta(n,l,m)\exp\bigl(\pi i(nz_1+lz_2+mz_3)\bigr),$$
with
$$c_\Delta(1,1,1)=64,\qquad c_\Delta(n,l,m)\in64\Z.$$

\begin{proposition}[Isotropic cusp coefficient]
$$1+\frac1{64}\sum_{t\geq1}c_\Delta(1+2t,1,1)q^t
=\prod_{k\geq1}(1-q^k)^9.$$
\end{proposition}

\begin{proof}
$$\Delta_5(Z) =
\sum_{\substack{m>0\\m\equiv1\bmod2}}
\phi_{5,m}(z_1,z_2)\exp(\pi i m z_3).$$
$$\phi_{5,1}\in J_{5,\frac12}(\nu_{\Delta_5}).$$
$$\nu_{11}(z_1,z_2)=
\sum_{n\in\Z}(-1)^n
\exp\left(\frac{\pi i}{4}(2n+1)^2z_1+\pi i(2n+1)z_2\right).$$
$$\nu_{11} =
-q^{1/8}r^{-1/2}\prod_{n\geq1}
(1-q^{n-1}r)(1-q^nr^{-1})(1-q^n),$$
$$q=\exp(2\pi iz_1),\qquad r=\exp(2\pi iz_2).$$
$$\psi_{5,\frac12}=\eta(z_1)^9\nu_{11}(z_1,z_2),\qquad
\eta(z_1)=q^{1/24}\prod_{n\geq1}(1-q^n).$$
$$\frac1{64}\phi_{5,1}(z_1,z_2)=\psi_{5,\frac12}(z_1,z_2)
=-q^{1/2}r^{-1/2}\prod_{n\geq1}
(1-q^{n-1}r)(1-q^nr^{-1})(1-q^n)^{10}.$$
$$1+\frac1{64}\sum_{t\geq1}c_\Delta(1+2t,1,1)q^t
=\prod_{k\geq1}(1-q^k)^9.$$
\end{proof}

\begin{definition}[Massless divisor and determinant sign]
$$\mathcal H_{\mathrm{diag}}
=\left\{\begin{pmatrix}a&0\\0&b\end{pmatrix}\mid
a,b\in\mathbb H_1\right\}.$$
Gritsenko--Cl\'ery \cite{GC}, $N=1$:
$$\operatorname{supp}\operatorname{div}(\Delta_5)
=\Sp_4(\Z)\cdot\mathcal H_{\mathrm{diag}},\qquad
\operatorname{mult}_{\mathcal H_{\mathrm{diag}}}(\Delta_5)=1.$$
$$\mathcal M_{\mathrm{massless}}
:=\operatorname{supp}\operatorname{div}(\Delta_5),\qquad
\epsilon_{\det}:=\nu_{\Delta_5}.$$
$$\Delta_5|_5g=\nu_{\Delta_5}(g)\Delta_5,\qquad
\Delta_5(s_{\delta_i}Z)=-\Delta_5(Z).$$
The displayed sign on the type-II diagonal reflections \(s_{\delta_i}\),
\(i=1,2,3\), is the Maass-character verification carried out in
Lemma~\ref{lem:maass-multiplier-restriction} below; the
\(\nu_{\Delta_5}(s_{\delta_i})=-1\) line of that lemma is the input used
here.
\end{definition}

\begin{definition}[Orientation line of the protected sector]
\label{def:orientation-line}
Let \(\mathcal C\) be a stable object in the reduced compact critical
Hall/CoHA sector envisaged in
Definition~\ref{def:protected-hall-integration-criterion}, with derived
self-Ext line after cosection reduction
$$
\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C)
\in\operatorname{Pic}(\mathfrak M^{or}_X).
$$
By an \emph{orientation line} of the protected sector is meant a line
bundle
$$
o_{\mathcal C}\in\operatorname{Pic}(\mathfrak M^{or}_X)
$$
together with the squaring isomorphism
$$
o_{\mathcal C}^{\otimes 2}
\;\simeq\;
\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C),
$$
fitting into a strong orientation datum compatible with the extension
correspondences of
Definition~\ref{def:protected-hall-integration-criterion}.  This is the
existence frame for orientations on critical and \((-1)\)-shifted
symplectic moduli; on Calabi--Yau threefolds the orientation-data
formalism is Joyce--Song \cite{JoyceSong}, and on Calabi--Yau \(4\)-folds
it is the Borisov--Joyce / Oh--Thomas construction
\cite{BorisovJoyce}, \cite{OhThomasI}, \cite{OhThomasII}.  The
\(K3\times E\) case is neither of these: its reduced compact critical
sector is not constructed in this paper, and the existence of a
square-root line \(o_{\mathcal C}\) for that sector is one of the
unresolved data items of
Open Problem~\ref{op:orientation-monodromy-character}.  No such line is
constructed here.
\end{definition}

\begin{remark}[Polarization is independent of orientation]
\label{rem:gram-polarization-not-orientation}
\label{rem:bott-sign-normalization}
The identity
\[
B(c,c)=2\Pi_X(c)
\]
is the polarization identity for the quadratic Gram map
\(\Pi_X\).  It is independent of the parity split of a protected
cohomology representative and independent of the choice of an
orientation line.  Orientation data
enters later, when one tries to promote a determinant section to a
Pfaffian section and to compute its monodromy under wall reflections.
It does not change the Gram polarization.  In particular no
Bott-periodicity convention, Grothendieck--Witt sign convention, or
choice of Bott element is used to prove \(B(c,c)=2\Pi_X(c)\).  Such
conventions may rigidify an already constructed orientation theory; they
do not supply the lattice polarization, the reduced \(E\)-quotient
linearization, or the compact Pfaffian sign.
\end{remark}

\begin{proposition}[Borcherds--Gritsenko--Nikulin identification]
\label{prop:bgn-identification}
By the Borcherds--Gritsenko--Nikulin product formula for
\(\phi_{0,1}\),
$$\mathcal D_X(Z)=\Delta_5(Z).$$
\end{proposition}

\begin{proof}
The general Borcherds product mechanism is
\cite[Theorem~10.1]{Borcherds95}; no scalar normalization is taken from
that general theorem.  The exact genus-two specialization used here is
Gritsenko--Nikulin: \cite[Theorem~2.1 and Example~2.4, especially
(2.15)--(2.16)]{GNII} gives the monic product
$$D_5(Z)
=q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}.$$
GNII denotes this monic product by \(\Delta_5\).  This paper reserves
\(\Delta_5\) for the theta-constant normalization.  In that convention,
\cite[Theorem~4.1]{GN} gives
\[
D_5(Z)=64^{-1}\Delta_5(Z).
\]
Hence
$$64q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}(1-q^nr^ls^m)^{f(nm,l)}
=\Delta_5(Z).$$
$$\mathcal D_X(Z)=\Delta_5(Z).$$
\end{proof}

\begin{remark}[Normalization of the square root]
The constants in the square-root product are fixed by the following
chain:
\begin{center}
\small
\begin{tabular}{p{0.25\textwidth}p{0.62\textwidth}}
\hline
Object & Fixed value \\
\hline
Fourier variables &
\(q=e^{2\pi iz_1},\ r=e^{2\pi iz_2},\ s=e^{2\pi iz_3}\) \\
Borcherds input &
\(Z_{\mathrm{K3}}=2\phi_{0,1}\) \\
Borcherds product normalization &
\(D_5^{\mathrm{mon}}=D_5^{\mathrm{GNII}}
=64^{-1}\Delta_5^{\theta}\), and this paper writes
\(\Delta_5=\Delta_5^{\theta}\) \\
Weight &
\(\mathrm{wt}\,\operatorname{Borch}_{\theta}(\phi_{0,1})=f(0,0)/2=5\) \\
Igusa leading coefficient &
\([q^{1/2}r^{1/2}s^{1/2}]\Delta_5=64\) \\
Monic product &
\(D_5=64^{-1}\Delta_5
=q^{1/2}r^{1/2}s^{1/2}\prod(1-q^nr^ls^m)^{f(nm,l)}\) \\
Determinant normalization &
\(\mathcal D_X=\Delta_5,\quad
v_0=64q^{1/2}r^{1/2}s^{1/2}\) \\
Virtual inverse &
\(\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}
=64^{-1}q^{-1/2}r^{-1/2}s^{-1/2}\sch\mathcal F(\mathcal V)\) \\
BKM denominator &
\(\operatorname{den}(\autcor)=D_5(2Z)=64^{-1}\Delta_5(2Z)\) \\
Scalar square &
\(Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2}\);
in general \(Z^X_{\square}=C_{\square}\Delta_5^{-2}\), hence
\((\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}})^2=Z^X_{\square}/C_{\square}\) \\
\hline
\end{tabular}
\end{center}
\end{remark}

\begin{proposition}[Borcherds--Gritsenko weight identity at \(N=1\)]
Let $\phi_{0,1}\in J_{0,1}^{\mathrm{weak}}$ be the weight-zero index-one
weak Jacobi form with Fourier expansion
$\phi_{0,1}(z_1,z_2)=\sum_{n,l}f(n,l)\,q^nr^l$.  The
theta-normalized Borcherds lift at \(N=1\) is \(\Delta_5\), and the
Borcherds weight reads
$$\operatorname{wt}(\Delta_5)=\frac{f(0,0)}{2}=5=\frac{c_1(0)}{2},$$
with $c_1(0):=f(0,0)=10$.  Since the weight is integral, no metaplectic
cover is needed for the weight factor.
\end{proposition}

\begin{proof}
The Borcherds singular-theta regularisation of \(\phi_{0,1}\) produces
a meromorphic Siegel modular form of weight \(f(0,0)/2\); at \(N=1\)
the paramodular group is \(\Sp_4(\Z)\) by Gritsenko--Nikulin
\cite{GN}.  The input Jacobi form has \(f(0,0)=10\)
(Eichler--Zagier \cite{EZ:1}, elliptic genus of K3), hence the output
weight is
\(5\).  Identifying
\(\operatorname{Borch}_{\theta}(\phi_{0,1})\) with \(\Delta_5\) via the
Igusa identification \((\mathcal D_X=\Delta_5)\) fixes
$\operatorname{wt}(\Delta_5)=5$.  Setting $c_1(0):=f(0,0)$ exhibits the
row $(N=1,\,\operatorname{wt}=5,\,c_1(0)=10)$ of the Gritsenko--Cl\'ery
catalogue \cite{GC}; the remaining integral and half-integral
Clery--Gritsenko rows are listed in \cite[Theorem 1.4]{GC}.  Integrality
\(\operatorname{wt}(\Delta_5)\in\Z\) means that no metaplectic cover is
required for the weight factor.  The Hodge automorphic line
\(\mathcal L^5\) remains nontrivial, and the Maass character
\(\nu_{\Delta_5}\) is a finite-order character of \(\Sp_4(\Z)\).
\end{proof}

\part{Physical charge and normal-ordered descent}

\section{D6--D2--D0 protected-index dictionary}

Only the OP/DT scalar branch requires an elliptically fibered K3 surface
with a section.  The Borcherds determinant above used only the universal
K3 elliptic genus.

Let $S$ be an elliptically fibered K3 surface
$$\pi:S\rightarrow \mathbb{P}^1$$
with a section $s_1$, and let $E$ be an elliptic curve.  Set
$$X=S\times E.$$
Let $F\in \mathrm{Pic}(S)$ be the fibre class and put
$$\beta_h=s_1+hF,\qquad h\geq 0.$$

Type IIA D6--D2--D0 charge:
$$\gamma(h,d,n)=(1;\,(\beta_h,d);\,n).$$
Write $\Omega_X(h,d,n)$ for the putative protected D6--D2--D0 index
attached to this charge in a compact physical realization.  The
microscopic trace is not constructed here; the desired datum would be:
$$
\stackrel{?}{\exists}\,\mathcal H_{\gamma(h,d,n)},\qquad
\operatorname{Tr}_{\mathcal H_{\gamma(h,d,n)}}(-1)^F
=\Omega_X(h,d,n).
$$
$$\mathrm{Hilb}^n(X,(\beta_h,d))
=\{Y\subset X\mid [Y]=(\beta_h,d),\ \chi(\mathcal O_Y)=n\}.$$
$$E\curvearrowright X,\qquad (x,e')\mapsto (x,e+e').$$

\begin{lemma}[D6--D2--D0 Mukai--Gram dictionary]
\label{lem:mukai-vector-ideal-sheaf-sxe}
Let $X=S\times E$ with $S$ K3 and $E$ elliptic.  Let
$Y\subset X$ be a one-dimensional subscheme with class
$[Y]=(\beta,d)\in H_2(S,\Z)\oplus H_2(E,\Z)$ and
$\chi(\mathcal O_Y)=n\in\Z$.  Let
$\mathcal I_Y\in D^b(X)$ be its ideal sheaf.  Decompose the Mukai vector
$$
v_X(\mathcal I_Y)=\ch(\mathcal I_Y)\cdot\sqrt{\td(X)}
$$
against the K\"unneth basis
\(\Lambda_S\otimes\{1_E,\omega_E\}\) where
\(\Lambda_S=H^*(S,\Z)\) and \(\omega_E\in H^2(E,\Z)\) is the
fundamental class.  Then
$$
v_X(\mathcal I_Y)
=(1,\,0,\,1-d)\otimes 1_E
+(0,\,-\beta,\,-n)\otimes\omega_E.
$$
With
$$
P_Y=(1,0,1-d),\qquad Q_Y=(0,-\beta,-n),
$$
the Gram-degree triple is
$$
\left(\frac{Q_Y^2}{2},\,Q_Y\cdot P_Y,\,\frac{P_Y^2}{2}\right)
=\left(\frac{\beta^2}{2},\,n,\,d-1\right).
$$
In particular, for \(\beta=\beta_h=s_1+hF\) with
\(\beta_h^2=2h-2\),
\[
\Pi_X(Q_Y,P_Y)=(h-1,n,d-1).
\]
\end{lemma}

\begin{proof}
Since \(X=S\times E\) is a Calabi--Yau threefold,
$$\ch(\mathcal I_Y)=1-\ch(\mathcal O_Y).$$
For a one-dimensional sheaf on a Calabi--Yau threefold,
\[
\ch_2(\mathcal O_Y)=\operatorname{PD}[Y],
\qquad
\int_X\ch_3(\mathcal O_Y)=\chi(\mathcal O_Y)=n.
\]
The Todd square root factorizes as
$$
\sqrt{\td(X)}
=\pi_S^*\sqrt{\td(S)}\,\pi_E^*\sqrt{\td(E)}
=\pi_S^*(1,0,1)\cup 1,
$$
since \(\sqrt{\td(E)}=1\) and \(\sqrt{\td(S)}=(1,0,1)\) in Mukai
notation on a K3 surface.  Decomposing the curve class,
the K3-vertical component \(\beta\times\{\mathrm{pt}\}\) contributes
\(\beta^\vee\otimes\omega_E\), while the elliptic component
\(d\{\mathrm{pt}\}\times E\) contributes \(d[\mathrm{pt}_S]\otimes 1_E\).
Thus
$$
\ch(\mathcal O_Y)
=(0,0,d)\otimes 1_E+(0,\beta,n)\otimes\omega_E.
$$
Multiplying
\[
1-\ch(\mathcal O_Y)
=(1,0,-d)\otimes 1_E+(0,-\beta,-n)\otimes\omega_E
\]
by \((1,0,1)\otimes1_E\) gives
\[
v_X(\mathcal I_Y)
=(1,0,1-d)\otimes1_E+(0,-\beta,-n)\otimes\omega_E,
\]
because \(\beta^\vee[\mathrm{pt}_S]=0\) on the K3 surface.

The Mukai pairing on \(\Lambda_S\) is
\[
(r,D,s)\cdot(r',D',s')=D\cdot D'-rs'-r's.
\]
Therefore
\[
\frac{Q_Y^2}{2}=\frac{\beta^2}{2},\qquad
Q_Y\cdot P_Y
=(-\beta)\cdot0-0(1-d)-1(-n)=n,
\]
and
\[
\frac{P_Y^2}{2}
=\frac{-2(1)(1-d)}{2}=d-1.
\]
For \(\beta=\beta_h\), \(\beta_h^2=2h-2\), this gives
\(\Pi_X(Q_Y,P_Y)=(h-1,n,d-1)\).
\end{proof}

The Gram-degree triple
\((Q^2/2,\,Q\cdot P,\,P^2/2)=(h-1,\,n,\,d-1)\)
identifies the Hilbert/PT charge with a triple in the Mukai lattice of
\(X\); this is the Gram-index data used by the Borcherds product and
by the OP normalization of Theorem~\ref{thm:op-square}.  The hypothesis
\(\beta_h^2=2h-2\) of Theorem~\ref{thm:op-square} is exactly the
\(Q^2/2=h-1\) line of this lemma.

\begin{proposition}[Reduced scalar quotient integration]
\label{prop:reduced-scalar-quotient-integration}
The reduced DT/PT side used in this paper is the coefficientwise scalar
Behrend-weighted quotient integration
$$
\mathbf{DT}^X_{n,(\beta,d)}
=
\int_{\mathrm{Hilb}^n(X,(\beta,d))/E}\nu_{\mathrm{Hilb}}\,de,
$$
and
$$
\mathsf P^X_{n,(\beta,d)}
=
\int_{P_n(X,(\beta,d))/E}\nu_P\,de
$$
for the stable-pair moduli space \(P_n(X,(\beta,d))\).  It lands in
numbers, coefficient by coefficient.  Oberdieck's reduced stable-pair
quotient invariant agrees with the reduced virtual-class incidence
definition, and his reduced DT/PT theorem identifies the two reduced
quotient series for nonzero K3 class \cite[Theorem 3(i)]{OberdieckReducedPT}.
This is scalar integration.  It is not a Hall product, not a CoHA
integration map, and not an orientation character.
\end{proposition}

\begin{proof}
Behrend's constructible function gives the weighted Euler
characteristic used in Donaldson--Thomas theory \cite{BEHREND},
\cite{DT}.  The \(E\)-action on \(X=S\times E\) forces the ordinary
unreduced invariant to vanish, so the reduced theory integrates over
the quotient by \(E\).  Bryan's Hilbert-scheme normalization and
Oberdieck's stable-pair normalization are exactly the quotient
Behrend-weighted Euler characteristics \cite{BRYAN},
\cite{OberdieckReducedPT}.  Oberdieck proves the quotient stable-pair
definition equals the reduced incidence invariant and proves the
reduced DT/PT comparison for nonzero K3 class.  These statements produce
integers indexed by \((\beta,d,n)\); no algebra object or primitive
projection is constructed.
\end{proof}

\begin{conjecture}[Protected D-brane index]
\label{conj:protected-d-brane-index}
For the D6--D2--D0 charge
$$\gamma(h,d,n)=(1;\,(\beta_h,d);\,n),$$
if such a compact physical Hilbert space is supplied, the conjectural
enumerative dictionary identifies its protected trace with the
Behrend-weighted Hilbert-scheme quotient invariant:
$$
\Omega_X(h,d,n)
:=\operatorname{Tr}_{\mathcal H_{\gamma(h,d,n)}}(-1)^F
\stackrel{\mathrm{phys}}{=}
\mathbf{DT}^X_{n,(\beta_h,d)}.
$$
This physical identification is not used in the scalar theorem below.
\end{conjecture}

\begin{definition}[Protected Hall integration criterion]
\label{def:protected-hall-integration-criterion}
A protected Hall or critical CoHA integration map refining
Proposition~\ref{prop:reduced-scalar-quotient-integration} would have
to supply the following data before comparison with
\(\mathfrak g_{\Delta_5}\):
an extension-closed compact Hall/CoHA sector for the reduced
\(E\)-quotient, oriented critical extension correspondences,
vanishing-cycle coefficient systems, HN-finite sector completions,
protected integration compatible with the completed Hall product and
wall crossing, a primitive projection, and a lifted Weyl action on the
oriented completed theory.

If these data exist, the test is rigid: protected primitives must have
signed dimensions
$$
\sdim\Prim_{(n,l,m)}=f(nm,l),
$$
their bracket must be the Borcherds--Gritsenko--Nikulin bracket, and the
induced orientation character must restrict on the type-II Weyl group as
$$
\epsilon_o|_{W^{(2)}(\La^{2,1}_{II})}
=
\nu_{\Delta_5}|_{W^{(2)}(\La^{2,1}_{II})}.
$$
General CoHA technology supplies a language for such conditions
\cite{KSCoHA}, \cite{DavisonMeinhardtCoHA}; it does not construct this
compact \(K3\times E\) datum.
\end{definition}


\begin{lemma}[Brauer-class parity criterion for Pin\(^c\)-lift gerbes]
\label{lem:p3-brauer-gerbe-vanishing}
Let \(\mathcal C\) be a protected Mukai charge on the reduced
\(K3\times E\) sector, and let
\(\alpha^{\mathrm{red}}_{\mathcal C}\) and
\(\alpha^E_{\mathcal C}\) be the reduced Pin\(^c\)-lift gerbe class and
the \(E\)-equivariant descent obstruction of
Open Problem~\ref{op:orientation-monodromy-character}.  On any
projection-finite stratum on which:
\begin{enumerate}
\item a GRR/Stiefel--Whitney comparison identifies the reduced
orientation gerbe of the self-Ext complex with the numerical parity
class \(c_1(L)^2/2\bmod2\) of a K3 chamber polarization line \(L\), and
\item \(c_1(L)^2/2\equiv0\pmod2\), and
\item the \(E\)-descent parity
\(c_1(\mathrm{degree})\cup c_1(\mathrm{level})\) is even,
\end{enumerate}
one has
\[
\alpha^{\mathrm{red}}_{\mathcal C}=0,
\qquad
\alpha^E_{\mathcal C}=0
\]
on that stratum.  In particular this proves the claimed vanishing on
rank-two chambers satisfying the displayed parity and on HN strata whose
graded factors reduce to rank-one/rank-two pieces on which the ordinary
and quotient orientation classes have already vanished.  It does not
prove the length-one stable higher-rank case.
\end{lemma}

\begin{proof}
The BBDJS orientation gerbe of the reduced self-Ext complex is the
second Stiefel--Whitney class of the determinant line, equivalently the
mod-two Brauer class of the square-root gerbe
\cite{BBDJS2015}.  On a stratum satisfying the first hypothesis the
supplied GRR/Stiefel--Whitney comparison represents this class by
\[
\frac{c_1(L)^2}{2}\bmod2.
\]
The second hypothesis therefore gives
\(\alpha^{\mathrm{red}}_{\mathcal C}=0\).  The equivariant Serre
spectral sequence for the free \(E\)-translation quotient identifies the
connected descent obstruction with
\(c_1(\mathrm{degree})\cup c_1(\mathrm{level})\bmod2\), so the third
hypothesis gives \(\alpha^E_{\mathcal C}=0\).  Without the first
comparison, the displayed parity is only a numerical diagnostic, not a
proof of gerbe triviality.  Additivity of orientation
gerbes on HN direct sums, from the Joyce--Upmeier / Joyce--Tanaka--Upmeier
multiplicative orientation formalism \cite{JoyceUpmeier,JoyceTanakaUpmeier},
then transports the vanishing to HN strata whose graded factors all lie
in the proved rank-one/rank-two sectors; off-diagonal self-Ext blocks
occur in dual pairs and contribute even Stiefel--Whitney class.  No
induction over a stable length-one higher-rank factor is used.
\end{proof}

\begin{remark}
\label{rem:p3-route-b-versus-hn}
Lemma~\ref{lem:p3-brauer-gerbe-vanishing} reads the parity off the
Chern integrand of the chamber polarization;
Lemma~\ref{lem:p3-higher-rank-pin-c-vanishing} reads it off the
HN-filtration data.  Both are reduction criteria: they agree with the
rank-one base case (P1) and with each other on the rank-two/HN-reducible
strata after the rank-one finite-data checks of (P1) have been
performed, but neither closes stable higher-rank length-one strata.
\end{remark}

\begin{openproblem}[Orientation monodromy character]
\label{op:orientation-monodromy-character}
The geometric orientation monodromy character
$$
\epsilon_o:W^{(2)}(\La^{2,1}_{II})\longrightarrow\{\pm1\},
$$
expected to satisfy
$$
\epsilon_o|_{W^{(2)}(\La^{2,1}_{II})}
=
\nu_{\Delta_5}|_{W^{(2)}(\La^{2,1}_{II})},
$$
is not produced by normalizing \(\Delta_5\).  Multiplying \(\Delta_5\)
by a nonzero scalar leaves its Maass character unchanged.  The character
must instead be produced by transporting the square root of the
determinant line around the simple diagonal wall reflections; the
expected local model is Pfaffian, in the sense made precise as
hypothesis (O2) of
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}: a simple
real-root reflection reverses one oriented normal mode, so its square is
scalar while the square root changes sign.

\smallskip
\textup{(P1)} \emph{Rank-one D6--D2--D0 stratum: ordinary Pin\(^c\)
input and quotient checks.}  On the rank-one D6--D2--D0 stratum
\(\mathfrak M^{\mathrm{red},(1)}_{\mathcal C}\) of physical Mukai charge
\(\mathcal C=(1,\beta,n)\), the desired reduced orientation line
\(o^{\mathrm{red},(1)}_{\mathcal C}\in\operatorname{Pic}(\mathfrak M^{\mathrm{red},(1)}_{\mathcal C})\)
is reduced to four pieces of data: an ordinary Pin\(^c\) lift of the
cosection-reduced self-Ext frame bundle, a connected \(BE\)-equivariant
linearization class, finite-stabilizer gerbe classes on the small-orbit
strata, and the residual finite-stabilizer \(H^1\)-linearization
characters after those gerbes have been null-trivialized.  The standard
orientation technologies
\cite{BBDJS2015,JoyceUpmeier,JoyceTanakaUpmeier,CaoKoolMonavari}
provide the local Pin\(^c\) frame and sign-rigidification model used in
Lemma~\ref{lem:spin-lift-sign-fixing}.  They do not, without the
following quotient computations, construct the reduced
\(E\)-quotient orientation.  The ordinary obstruction class is
$$
\alpha^{\mathrm{red}}_{\mathcal C}
:=w_2\bigl(\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C)\bigr)
+\mathrm{cs}^{*}\,w_2\bigl(\det(\operatorname{coker}\,\mathrm{cs})\bigr)
\;\in\;H^2(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb Z/2)
$$
of the reduced orientation gerbe.  The connected quotient class has the
form
\[
\alpha^{E,\mathrm{free}}_{\mathcal C}
=a_1(\mathcal C)u_1+a_2(\mathcal C)u_2
\in H^2(BE;\mathbb F_2),
\]
with \(u_1,u_2\) as in
Lemma~\ref{lem:E-equivariant-descent-obstruction}.  On the \(N=2\)
small-orbit stratum the finite residual is
\[
\beta^{E,E[2]}_{\mathcal C}
=b_{20}(\mathcal C)x_1^2+b_{11}(\mathcal C)x_1x_2
+b_{02}(\mathcal C)x_2^2
\in H^2(BE[2];\mathbb F_2).
\]
After \(\beta^{E,E[2]}_{\mathcal C}=0\), the chosen two-torsion
linearization has a degree-one character
\[
\lambda_{\mathcal C}^{E[2]}
=\lambda_1(\mathcal C)x_1+\lambda_2(\mathcal C)x_2
\in H^1(BE[2];\mathbb F_2).
\]
Thus rank-one (O1) through the two-torsion small-orbit boundary is
proved exactly when
\[
\alpha^{\mathrm{red}}_{\mathcal C}=0,\qquad
a_1(\mathcal C)=a_2(\mathcal C)=0,\qquad
b_{20}(\mathcal C)=b_{11}(\mathcal C)=b_{02}(\mathcal C)=0,\qquad
\lambda_1(\mathcal C)=\lambda_2(\mathcal C)=0.
\]
The first equality is the ordinary Pin\(^c\) orientation calculation.
The remaining bits are quotient gerbe and linearization data.  The three
finite-sector bits \(r_1,r_2,r_3\) of
Proposition~\ref{prop:rank-one-e2-linearization-obstruction} are
equivalent to the three coefficients \(b_{20},b_{11},b_{02}\), but they
do not see the connected \(BE\)-class
\(a_1u_1+a_2u_2\) or the degree-one finite character
\(\lambda_{\mathcal C}^{E[2]}\).  Thus the three cyclic degree-two bits cannot
by themselves be promoted to a proof of rank-one \textup{(O1)}.  Rank-one
\textup{(O1)} through
the two-torsion boundary is proved only after the ordinary class, the
two connected coefficients, the three finite cyclic degree-two
residuals, and the finite degree-one character have all been computed to
vanish.  None of these vanishing statements is
implied by ordinary translation invariance or by the OP scalar square.
Full rank-one descent through all small-orbit strata also requires
\(\beta^{E,N}_{\mathcal C}=0\) and the trivial \(H^1(BE[N];\mathbb F_2)\)
linearization character for every even \(N\ge4\), with the
two-primary residual described in
Lemma~\ref{lem:even-finite-stabilizer-residuals}; the \(E[2]\) bits do
not imply those vanishings.
Higher-rank semistable strata remain open except where the HN criteria
below reduce them to already-oriented factors.

\smallskip
\textup{(P2)} \emph{Type-II diagonal reflections: wall-character formula
conditional on the orientation existence.}  Conditional on (P1) and on
the multiplicative orientation cocycle of Joyce--Upmeier
\cite{JoyceUpmeier} and Joyce--Tanaka--Upmeier
\cite{JoyceTanakaUpmeier} extending equivariantly across the reduced
\(E\)-quotient, and on the Pfaffian local model (O2) of
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}, equivalently
the three local calculations isolated in
Proposition~\ref{prop:o2-local-obstruction-certificate}, the induced
orientation character satisfies
\(\epsilon_o(s_{\delta_i})=-1=\nu_{\Delta_5}(s_{\delta_i})\),
\(i=1,2,3\), so \(\epsilon_o=\nu_{\Delta_5}\) on
\(W^{(2)}(\La^{2,1}_{II})\).  The three
\(\Aut(\Poly_{II})\simeq S_3\) chamber-permuting reflections have Maass
value \(+1\), but Hall signs on them require a separately supplied
semidirect-product lift.  This is exactly conclusion (ii) of
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}, with the
explicit row-by-row calculation in
Lemma~\ref{lem:thm3-three-sign-computation}; conditional on (O1),
(O1)\(^+\), and (O2).

\smallskip
\textup{(P3)} \emph{Higher-rank obstruction.}
The required task is to compute the obstruction classes
$$
\alpha^{\mathrm{red}}_{\mathcal C}
\;\in\;H^2(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb Z/2),
\qquad
\alpha^{E}_{\mathcal C}
\;\in\;H^2_E(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2),
$$
where \(\alpha^{\mathrm{red}}_{\mathcal C}\) is the Pin\(^c\)-lift
gerbe class of the reduced derived self-Ext frame bundle on
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}\), and \(\alpha^E_{\mathcal C}\)
is the equivariant-linearization obstruction to descent of the
orientation along the free \(E\)-translation quotient.  On the rank-one
stratum it should be computed, not inferred from the OP scalar, by a
direct Chern-class calculation in the \(E_2^{2,0}\)-term of the
equivariant Serre spectral sequence
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}\to
\mathfrak M^{\mathrm{red}}_{\mathcal C}/E\to BE\) of
Lemma~\ref{lem:E-equivariant-descent-obstruction}.  One must then prove
their joint vanishing on the Harder--Narasimhan-completed semistable stack
\(\mathfrak M^{\mathrm{red},\mathrm{ss},\mathrm{HN}}_{\mathcal C}\).
The small-orbit gerbe contribution
\(\overline{\beta}^E_{\mathcal C}\) of
Lemma~\ref{lem:E-equivariant-descent-obstruction}(iv) from the
\(N\ge 2\) torsion locus
\(K3\times(E/E[N])\subset X\) is governed by the finite-stabilizer
criterion of Lemma~\ref{lem:bmu2-klein-four-vanishing}: the band at
\(N=2\) is the Klein-four \(BE[2]\) (not cyclic \(B\mu_2\)), and
vanishing requires a trivial \(E[2]\)-equivariant linearization of the
orientation line, detected on the three nontrivial cyclic subgroups.
Granted the ordinary Pin\(^c\) gerbe vanishing, the connected
\(BE\)-linearization vanishing, and this finite-stabilizer vanishing,
(O1) would follow from the Joyce--Upmeier \cite{JoyceUpmeier}
multiplicative cocycle plus the supplied Pin\(^c\) lift; granted (O2),
the wall-character formula of (P2) would follow by
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}.  On
higher-rank semistable strata the joint vanishing of
\(\alpha^{\mathrm{red}}_{\mathcal C}\) and \(\alpha^E_{\mathcal C}\) is
reduced by Lemma~\ref{lem:p3-higher-rank-pin-c-vanishing} to HN strata
whose graded factors are already oriented; stable higher-rank length-one
strata and even finite-stabilizer strata not covered by a trivial
linearization remain open.  The
Pin\(^c\)-lift program of \cite{JoyceUpmeier},
\cite{JoyceTanakaUpmeier}, \cite{CaoKoolMonavari}, \cite{Bojko},
\cite{BBDJS2015} supplies the analytic technology on the
cosection-twisted reduced \(E\)-quotient; non-compact and Joyce--Song
extensions are Bojko \cite{Bojko}.

\smallskip
\textup{(P4)} \emph{Cosection-induced parity flip from \(\sigma_{K3}\):
\(\mathrm{vd}^{\mathrm{red}}=\mathrm{vd}^{\mathrm{std}}+1\); absorbed
into (O1) as a \(\mathbb Z/2\)-grading shift on \(o_{\mathcal C}\).}
The Maulik--Toda / Oberdieck reduced obstruction theory
\cite{MaulikTodaGV,OberdieckReducedPT} contracts the
PTVV \cite{PTVV2013} \((-1)\)-shifted symplectic form
\(\omega_{\mathfrak M}\) on \(\mathfrak M_{\mathcal C}(X)\) against the
cosection
\(\mathrm{cs}\colon\operatorname{Obs}_{\mathfrak M_{\mathcal C}}\to
\mathcal O_{\mathfrak M_{\mathcal C}}\) generated by Mukai dilation
along \(\sigma_{K3}\), and the restriction \(\omega_{\mathfrak M}^{\mathrm{red}}\)
to the cosection vanishing locus
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}\hookrightarrow
\mathfrak M_{\mathcal C}\) is non-degenerate on the OP/DT
D6--D2--D0 stratum, with virtual dimension shifted by one,
\(\mathrm{vd}^{\mathrm{red}}_{\mathcal C}=\mathrm{vd}^{\mathrm{std}}_{\mathcal C}+1\).
Under the BBDJS \cite{BBDJS2015} Pin-to-Spin lift of
the BBDJS line of Definition~\ref{def:orientation-line}, this dimension
shift propagates as a \(\mathbb Z/2\)-grading shift on the orientation
line:
$$
o^{\mathrm{red}}_{\mathcal C}
\;=\;o^{\mathrm{std}}_{\mathcal C}\otimes\Pi,
$$
where \(\Pi\) is the parity-flip line generated by the cosection cokernel.
The strong orientation certificate \textup{(O1)} includes the coherence
datum that makes this shift commute with the extension correspondences of
Definition~\ref{def:protected-hall-integration-criterion} and preserves
the Joyce--Upmeier multiplicative cocycle of (P2).  The Oberdieck monic
normalization \cite{OberdieckReducedPT} fixes the scalar parity branch,
and the Hall extension coherence is the corresponding \textup{(O1)}
residual.  The parity-flip is absorbed into (O1):
the strong orientation line
\(o_{\mathcal C}\) demanded by
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional} is, on the
reduced sector, \(o^{\mathrm{red}}_{\mathcal C}\), not the unreduced
BBDJS line, and the squaring isomorphism is to the reduced derived
self-Ext
\(\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C)
=\operatorname{cofib}(\sigma_{K3}\colon
\operatorname{RHom}(\mathcal C,\mathcal C)[-2]\to\operatorname{RHom}(\mathcal C,\mathcal C))\).
Operationally this parity shift belongs to the reduced orientation
datum and to any eventual Berezinian convention for a compact
first-order object.  The overall minus in
\(Z^X_{\mathrm{OP}}=-4096\,\Delta_5^{-2}\) is the scalar OP/DT branch
convention.  It may be compatible with a chosen fermionic grading, but
it is not evidence for the Hall orientation character.  The reflection
character \(\epsilon_o\) must be computed from monodromy of the
orientation line around the type-II walls.
The (P3) residual is the joint vanishing of
\(\alpha^{\mathrm{red}}_{\mathcal C}+\alpha^E_{\mathcal C}\) on the
HN-completed semistable stack with \(\mathrm{rk}\,\mathcal C\ge 2\) and
on the small-orbit \(BE[N]\) finite-stabilizer strata.
Lemma~\ref{lem:p3-higher-rank-pin-c-vanishing} and
Lemma~\ref{lem:p3-brauer-gerbe-vanishing} give conditional reductions
for the HN-reducible and rank-two parity pieces;
Lemma~\ref{lem:bmu2-klein-four-vanishing} gives the \(N=2\)
Klein-four detection criterion.  Stable higher-rank length-one strata
and nontrivial finite-stabilizer linearizations remain genuine open
obligations.
\end{openproblem}

\begin{lemma}[Connected and finite-stabilizer \(E\)-descent of the
orientation line]
\label{lem:E-equivariant-descent-obstruction}
Let \(\mathcal C\in\Gamma_X^{\mathrm{phys}}\) and let
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}\) be the cosection-reduced
critical Hall stack of
Definition~\ref{def:protected-hall-integration-criterion}.  The
translation action of \(E\) on \(X=K3\times E\) lifts to an action on
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}\), free outside the
small-orbit locus
$$
\mathfrak M^{\mathrm{red},\mathrm{small}}_{\mathcal C}
=\bigcup_{N\ge 2}\mathfrak M^{\mathrm{red}}_{\mathcal C}\bigl(K3\times(E/E[N])\bigr)
\;\subset\;
\mathfrak M^{\mathrm{red}}_{\mathcal C},
$$
and on the free locus produces a quotient stack
\(\overline{\mathfrak M}^{\mathrm{red}}_{\mathcal C}
=\mathfrak M^{\mathrm{red}}_{\mathcal C}\big/E\).  Suppose the unreduced
orientation \(o^{\mathrm{red}}_{\mathcal C}\) of (P1) of
Open Problem~\ref{op:orientation-monodromy-character} exists on the
free locus.  Its descent to a line
\(\overline{o}^{\mathrm{red}}_{\mathcal C}
\in\operatorname{Pic}(\overline{\mathfrak M}^{\mathrm{red}}_{\mathcal C})\)
is governed by the equivariant Serre spectral sequence
$$
E_2^{p,q}=H^p(BE;\,H^q(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb Z/2))
\;\Longrightarrow\;
H^{p+q}_E(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb Z/2)
$$
attached to the fibration
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}\to
\overline{\mathfrak M}^{\mathrm{red}}_{\mathcal C}\to BE\).  The
connected \(E\)-quotient and the finite stabilizer strata have different
cohomology and must be treated separately.
\begin{enumerate}
\item[\textup{(i)}] (\emph{Connected free \(E\)-descent.})
Topologically \(E^{\mathrm{top}}\simeq T^2\), hence
\[
BE\simeq BT^2\simeq K(\mathbb Z^2,2),
\qquad
H^*(BE;\mathbb F_2)=\mathbb F_2[u_1,u_2],
\quad |u_i|=2.
\]
Therefore
$$
H^1(BE;\mathbb F_2)=0,\qquad
H^2(BE;\mathbb F_2)=\mathbb F_2u_1\oplus\mathbb F_2u_2.
$$
In particular there is no connected-torus obstruction in bidegree
\[
E_2^{1,1}
=H^1(BE;\mathbb F_2)\otimes
H^1(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2)=0.
\]
The degree-two obstruction on the free locus has only the two standard
components
\[
E_2^{2,0}
=H^2(BE;\mathbb F_2)\otimes
H^0(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2)
\]
and
$$
E_2^{0,2}
=H^0(BE;\,H^2(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2)).
$$
Thus the free-locus descent obstruction is a class
$$
\alpha^{E,\mathrm{free}}_{\mathcal C}
\in H^2_E(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2)
$$
whose connected-torus part lies in
\(\mathbb F_2u_1\oplus\mathbb F_2u_2\), not in a rank-three
\(\langle\alpha^2,\alpha\beta,\beta^2\rangle\) group.
\item[\textup{(ii)}] (\emph{Rank-one free-locus criterion.})  On the
rank-one stratum
\(\mathfrak M^{\mathrm{red},(1)}_{\mathcal C}\),
\(\mathcal C=(1,\beta,n)\), descent of
\(o^{\mathrm{red},(1)}_{\mathcal C}\) through the free \(E\)-quotient is
equivalent to the vanishing of the two components in \textup{(i)}:
the ordinary reduced orientation gerbe in \(E_2^{0,2}\), and the
connected-torus equivariant linearization class in \(E_2^{2,0}\).
If a direct Chern-class calculation identifies the latter with a class
of the form
$$
c_1(\mathrm{degree})u_1+c_1(\mathrm{level})u_2
\in H^2(BE;\mathbb F_2),
$$
then the class vanishes exactly when those two mod-\(2\) coefficients
vanish.  The OP scalar normalization by itself does not prove this
equivariant linearization statement; it is a separate orientation
calculation.
\item[\textup{(iii)}] (\emph{Finite stabilizer descent.})  On
the small-orbit locus \(\mathfrak M^{\mathrm{red}}_{\mathcal C}(K3\times(E/E[N]))\)
the \(E\)-quotient is the stacky orbifold
\([\mathfrak M^{\mathrm{red}}_{\mathcal C}(K3\times(E/E[N]))/(E/E[N])]\)
banded by \(BE[N]\), not by \(B\mu_N\) unless a cyclic subgroup has
been chosen.  The orientation line may pick up a finite-stabilizer
descent class
$$
\widetilde\beta^{E,N}_{\mathcal C,S}
\;\in\;
H^2_{E[N]}(S;\mathbb F_2).
$$
Its point-stabilizer restriction is a class in
\(H^2(BE[N];\mathbb F_2)\) only after the mixed Borel terms, stabilizer
action on \(H^\bullet(S;\mathbb F_2)\), and spectral-sequence
differentials have vanished.
For \(N=2\),
$$
E[2]\simeq(\mathbb Z/2)^2,\qquad
H^*(BE[2];\mathbb F_2)=\mathbb F_2[x_1,x_2],
\quad |x_i|=1,
$$
so
\[
H^2(BE[2];\mathbb F_2)
=\mathbb F_2\langle x_1^2,x_1x_2,x_2^2\rangle.
\]
This rank-three group is the point-stabilizer reduction of the finite
two-torsion calculation; it is not the full Borel descent class and it is
not connected \(BE\).  If \(N\) is odd, the positive-degree
mod-\(2\) cohomology of \(BE[N]\) vanishes because \(E[N]\) has odd
order.  For even \(N\), the residual class is detected on the
\(2\)-primary part and must be computed stratum by stratum from the
equivariant linearization of the orientation line.  More precisely, if
\(2^a\parallel N\) and \(a\ge2\), then
\[
H^*\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\Lambda(x_1,x_2)\otimes\mathbb F_2[y_1,y_2],
\qquad |x_i|=1,\quad |y_i|=2,\quad x_i^2=0,
\]
so
\[
\beta^{E,N}_{\mathcal C,(2)}
=A_1^{(N)}y_1+A_{12}^{(N)}x_1x_2+A_2^{(N)}y_2.
\]
This is not determined by the \(N=2\) Klein-four vector.
\item[\textup{(iv)}] (\emph{Combined criterion.})  The orientation line
descends over the full reduced quotient only if the ordinary reduced
orientation gerbe, the connected-torus equivariant linearization class,
and every finite Borel class
\(\widetilde\beta^{E,N}_{\mathcal C,S}\) vanish on the relevant strata.
After each finite Borel class has been null-trivialized, the chosen stabilizer
linearization has a residual character
\[
\lambda^{E,N}_{\mathcal C}\in H^1(BE[N];\mathbb F_2),
\]
and the quotient orientation requires this character to be zero.
Translation invariance of the underlying ordinary line is not enough: a
fixed line can carry a non-trivial equivariant character.
\end{enumerate}
\end{lemma}

\begin{proof}
The cohomology calculation in \textup{(i)} is the standard classifying
space computation for a compact torus:
\[
BT^2=K(\mathbb Z^2,2),\qquad
H^*(BT^2;\mathbb F_2)=\mathbb F_2[u_1,u_2],\quad |u_i|=2.
\]
Hence \(H^1(BE;\mathbb F_2)=0\), and the bidegree
\((1,1)\) term in the equivariant Serre spectral sequence vanishes.
The only total-degree two terms on the free connected quotient are
\((2,0)\) and \((0,2)\), as displayed.  This proves the connected
separation.

For \textup{(ii)}, descent of a square-root line through a free group
quotient is exactly an equivariant linearization problem together with
the ordinary gerbe-trivialization problem.  The spectral sequence in
\textup{(i)} records these two classes.  A proposed rank-one
Chern-class formula is therefore a criterion: once the two coefficients
of \(u_1,u_2\) and the ordinary gerbe class vanish, the line descends on
that stratum.  The scalar identity
\(Z^X_{\mathrm{OP/DT}}=-4096\Delta_5^{-2}\) has no information about a
choice of \(E\)-equivariant linearization, so it cannot by itself prove
the criterion.

For \textup{(iii)}, the stabilizer of the \(N\)-fold small-orbit stratum
is the finite group \(E[N]\simeq(\mathbb Z/N)^2\).  At \(N=2\) this is
the Klein-four group.  Its mod-\(2\) cohomology is the polynomial ring
on the two degree-one character classes, hence its degree-two part has
basis \(x_1^2,x_1x_2,x_2^2\).  If \(N\) is odd, transfer kills
positive-degree \(\mathbb F_2\)-cohomology because \(|E[N]|=N^2\) is
invertible in \(\mathbb F_2\).  Even \(N\) reduces to its \(2\)-primary
stabilizer.  This proves the finite-stabilizer typing and separates it
from connected \(BE\).

Clause \textup{(iv)} is the standard descent criterion for a line on a
stack quotient: ordinary square-root gerbe, connected equivariant
linearization, finite-stabilizer Borel degree-two classes, and the residual
degree-one stabilizer characters must all vanish.  A line fixed as an
ordinary line can still carry a non-trivial character of the stabilizer
group, so ordinary translation invariance does not imply equivariant
descent.
\end{proof}

\begin{lemma}[Klein-four criterion for the small-orbit gerbe residual]
\label{lem:bmu2-klein-four-vanishing}
Let \(\mathcal C\in\Gamma_X^{\mathrm{phys}}\) and adopt the notation of
Lemma~\ref{lem:E-equivariant-descent-obstruction}.  The two-torsion
subgroup \(E[2]\subset E\) is the Klein-four group
\(\mathbb Z/2\times\mathbb Z/2\), generated by the three nontrivial
two-torsion points \(e_1,e_2,e_3\in E[2]\) (any two are independent).
The small-orbit stratum at \(N=2\) is
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}(K3\times(E/E[2]))\), banded
by \(BE[2]\), not \(B\mu_2\); the cohomological residual of
clause \textup{(iv)} of
Lemma~\ref{lem:E-equivariant-descent-obstruction} at \(N=2\) is the
class
$$
\beta^{E,E[2]}_{\mathcal C}
\;\in\;
H^2(BE[2];\mathbb Z/2)
\;\cong\;(\mathbb Z/2)^3,
$$
with cohomology basis
$$
H^*(BE[2];\mathbb Z/2)
\;=\;\mathbb Z/2[\,c_1(L_1),c_1(L_2)\,],
\quad
H^2(BE[2];\mathbb Z/2)
\;=\;\mathbb Z/2\langle c_1(L_1)^2\rangle
\oplus\mathbb Z/2\langle c_1(L_2)^2\rangle
\oplus\mathbb Z/2\langle c_1(L_1)\smile c_1(L_2)\rangle,
$$
where \(L_1,L_2\) are the two character lines of the dual
\(E[2]^{\vee}\simeq E[2]\), and the three nontrivial cyclic subgroups
\(\mu_2^{(i)}=\langle e_i\rangle\subset E[2]\), \(i=1,2,3\), restrict the
basis to the three generators of
\(H^2(B\mu_2^{(i)};\mathbb Z/2)\cong\mathbb Z/2\) componentwise.
Write
\[
\beta^{E,E[2]}_{\mathcal C}
=b_{20}x_1^2+b_{11}x_1x_2+b_{02}x_2^2,
\qquad x_j=c_1(L_j),
\]
and let \(\tau_i\) be the degree-one generator of
\(H^*(B\mu_2^{(i)};\mathbb Z/2)\).  Define the three cyclic residual
bits \(r_i\in\mathbb Z/2\) by
\[
\operatorname{res}_{\mu_2^{(i)}}\!
\bigl(\beta^{E,E[2]}_{\mathcal C}\bigr)=r_i\tau_i^2.
\]
With \(e_3=e_1+e_2\),
\[
r_1=b_{20},\qquad r_2=b_{02},\qquad
r_3=b_{20}+b_{11}+b_{02},
\]
hence
\[
b_{20}=r_1,\qquad b_{02}=r_2,\qquad
b_{11}=r_1+r_2+r_3.
\]
Thus the \(N=2\) finite-stabilizer residual vanishes if and only if the
three cyclic residual bits \(r_1,r_2,r_3\) vanish.  On the rank-one
D6--D2--D0 input \(\mathcal C=(1,\beta,n)\), the following hypotheses are
sufficient, and in the finite \(E[2]\)-sector necessary, for the
\(N=2\) residual to vanish and for the chosen \(E[2]\)-linearization to
be trivial:
\begin{enumerate}
\item[\textup{(K1)}] (\emph{K\"unneth split.})  The reduced
orientation line factors as a tensor product
\(o^{\mathrm{red}}_{\mathcal C}=o_{K3}\otimes o_E\) on the protected
sector, where \(o_{K3}\) is the Pin\(^{c}\) orientation of the K3 PT
factor and \(o_E\) is the Pin\(^{c}\) orientation of the elliptic
fibration factor, by the K\"unneth factorization of the cosection-twisted
Joyce--Tanaka--Upmeier multiplicative cocycle
\cite{JoyceUpmeier},\cite{JoyceTanakaUpmeier} on
\(\mathfrak M^{\mathrm{red}}_{\mathcal C}\)
viewed as a relative Hilbert scheme over the elliptic base, and the
Cao--Kool--Monavari Pin\(^{c}\) lift on the K3 factor
\cite{CaoKoolMonavari}.
\item[\textup{(K2)}] (\emph{K3 factor.})  The action of \(E[2]\) on
\(X=K3\times E\) is fibrewise translation on the second factor and
trivial on the first.  The supplied factorwise equivariant lift on the
K3 orientation factor is required to be the trivial \(E[2]\)-lift; this
removes no elliptic finite-stabilizer obstruction.
\item[\textup{(K3)}] (\emph{Elliptic factor: finite gerbe and character
data.})
Translation by \(e_i\in E[2]\) fixes the underlying elliptic orientation
line \(o_E\) as an ordinary line.  This fixedness does not decide the
equivariant lift.  First one must compute the three degree-two gerbe
bits
\[
r_i(\mathcal C)
=\operatorname{res}_{\mu_2^{(i)}}(\beta^{E,E[2]}_{\mathcal C})/\tau_i^2
\in\mathbb Z/2,\qquad i=1,2,3.
\]
The degree-two vanishing hypothesis is
\[
r_1(\mathcal C)=r_2(\mathcal C)=r_3(\mathcal C)=0.
\]
After this vanishing has supplied a null-trivialized gerbe, the set of
\(E[2]\)-linearizations is an
\[
H^1(BE[2];\mathbb F_2)=\mathbb F_2\langle x_1,x_2\rangle
\]
torsor.  For a supplied linearization write its character as
\[
\lambda_{\mathcal C}^{E[2]}=\lambda_1x_1+\lambda_2x_2,
\]
or, on the three cyclic inertia sectors,
\[
\operatorname{res}_{\mu_2^{(i)}}\lambda_{\mathcal C}^{E[2]}
=\rho_i\tau_i,\qquad
\rho_1=\lambda_1,\quad \rho_2=\lambda_2,\quad
\rho_3=\lambda_1+\lambda_2 .
\]
The required trivial-linearization hypothesis is
\[
\rho_1(\mathcal C)=\rho_2(\mathcal C)=\rho_3(\mathcal C)=0.
\]
Equivalently, the Pin\(^{c}\) sign character
\[
w_1(o_E^{E[2]})\colon E[2]\longrightarrow\mathbb Z/2
\]
vanishes on \(e_1,e_2,e_3\).  This is a degree-one
equivariant-linearization hypothesis, distinct from the degree-two gerbe
bits \(r_i\), and not a consequence of ordinary translation invariance
alone.
\item[\textup{(K4)}] If \textup{(K1)},
\textup{(K2)}, and \textup{(K3)} hold, then the degree-two bits
\(r_i(\mathcal C)\) and the degree-one character bits
\(\rho_i(\mathcal C)\) vanish for every
\(\mu_2^{(i)}\subset E[2]\).  Since
\[
b_{20}=r_1,\qquad b_{02}=r_2,\qquad b_{11}=r_1+r_2+r_3,
\]
the three coefficients of
\(\beta^{E,E[2]}_{\mathcal C}\) vanish, and therefore
$$
\beta^{E,E[2]}_{\mathcal C}=0\;\in\;H^2(BE[2];\mathbb Z/2).
$$
The additional equations \(\rho_i=0\) select the trivial point of the
\(H^1(BE[2];\mathbb F_2)\)-torsor of linearizations.
\end{enumerate}
Thus \(\beta^{E,E[2]}_{\mathcal C}=0\) and the finite
\(E[2]\)-linearization is trivial under the stated hypotheses.
For odd \(N\), the finite-stabilizer obstruction vanishes
cohomologically by Lemma~\ref{lem:E-equivariant-descent-obstruction}.
For even \(N\ge4\), the obstruction is detected on the \(2\)-primary
finite stabilizer and remains subject to the same equivariant
linearization calculation; it is not closed by ordinary translation
invariance.
\end{lemma}

\begin{proof}
The small-orbit stratum at \(N=2\) is the locus on which the
\(E\)-action factors through the quotient \(E\to E/E[2]\), so its
isotropy is exactly \(E[2]\) and the orbifold quotient
\([\mathfrak M^{\mathrm{red}}_{\mathcal C}(K3\times(E/E[2]))/(E/E[2])]\)
is banded by \(BE[2]\) (the inertia of the residual stabiliser),
\emph{not} by \(B\mu_2\).  Since \(E[2]\simeq(\mathbb Z/2)^2\) is the
Klein-four group, the cohomology \(H^*(BE[2];\mathbb F_2)\) has two
independent degree-one generators, whereas
\(H^*(B\mu_2;\mathbb F_2)\) has one.  The two stacks therefore cannot be
equivalent.  The mod-\(2\) cohomology is the polynomial ring on two
degree-one generators \(c_1(L_1),c_1(L_2)\) with
\(L_1,L_2\in\widehat{E[2]}\) the two characters (Cartan--Eilenberg
folklore for the cohomology of an elementary abelian \(2\)-group),
recovering \(H^2(BE[2];\mathbb Z/2)\cong(\mathbb Z/2)^3\) as stated.

The three nontrivial cyclic subgroups \(\mu_2^{(i)}=\langle e_i\rangle\)
are detected as follows: writing \(E[2]\) additively with basis
\(\{e_1,e_2\}\) and \(e_3=e_1+e_2\), the inclusion
\(\mu_2^{(1)}\hookrightarrow E[2]\) restricts \(L_1\) to the sign
character of \(\mu_2^{(1)}\) and \(L_2\) to the trivial character; the
inclusion \(\mu_2^{(2)}\hookrightarrow E[2]\) restricts \(L_2\) to the
sign character of \(\mu_2^{(2)}\) and \(L_1\) to the trivial character;
the inclusion \(\mu_2^{(3)}\hookrightarrow E[2]\) restricts both
\(L_1,L_2\) to the sign character of \(\mu_2^{(3)}\), so \(c_1(L_1)\)
and \(c_1(L_2)\) restrict to the same generator and \(c_1(L_1)\smile
c_1(L_2)\) restricts to its square.  The three restriction maps are
therefore jointly injective on the rank-three space
\(H^2(BE[2];\mathbb Z/2)\), so a class in \(H^2(BE[2];\mathbb Z/2)\)
vanishes if and only if its image in each
\(H^2(B\mu_2^{(i)};\mathbb Z/2)\) vanishes.  This is the standard
Klein-four detection by cyclic restriction.

Equivalently, for
\(\beta=b_{20}x_1^2+b_{11}x_1x_2+b_{02}x_2^2\), the three restrictions
are
\[
\operatorname{res}_1(\beta)=b_{20}\tau_1^2,\qquad
\operatorname{res}_2(\beta)=b_{02}\tau_2^2,\qquad
\operatorname{res}_3(\beta)=(b_{20}+b_{11}+b_{02})\tau_3^2.
\]
This gives the displayed conversion between the coefficient vector
\((b_{20},b_{11},b_{02})\) and the cyclic residual vector
\((r_1,r_2,r_3)\).

\textup{(K1).}  The K\"unneth factorization
\(o^{\mathrm{red}}_{\mathcal C}=o_{K3}\otimes o_E\) is the underlying
splitting of the multiplicative orientation cocycle of
\cite{JoyceUpmeier},\cite{JoyceTanakaUpmeier} along the product
factorization \(X=K3\times E\) on the protected sector, where the
moduli of stable pairs decompose as a relative Hilbert scheme over the
elliptic base.  The factorwise Pin\(^{c}\) lift on the K3 factor is a
supplied input, modeled on the BBDJS/Joyce--Upmeier and
Cao--Kool--Monavari orientation packages \cite{BBDJS2015,JoyceUpmeier,CaoKoolMonavari};
the elliptic ordinary factor is the orientation of the cotangent bundle
\(\Omega^1_E\), which is trivial of rank one and trivialized by the flat
translation-invariant one-form \(\mathrm dz\).

\textup{(K2).}  The translation \(t_{e_i}\colon X\to X\) acts as the
identity on the K3 factor and as translation by \(e_i\) on the
elliptic factor.  Pulling back along \(t_{e_i}\) does not move the K3
factor.  The trivial \(E[2]\)-lift on \(o_{K3}\) is therefore a supplied
factorwise linearization choice, not a consequence that settles the
elliptic quotient descent.

\textup{(K3).}  The cotangent bundle \(\Omega^1_E\) is trivial,
trivialized by \(\mathrm dz\); translation acts trivially on
\(\mathrm dz\).  This proves only fixedness of the underlying ordinary
line.  It does not determine the equivariant lift.  There are two
separate finite calculations: the degree-two gerbe residual
\(\operatorname{res}\beta^{E,E[2]}_{\mathcal C}=r_i\tau_i^2\), and, only
after this residual has been null-trivialized, the degree-one character
\(\operatorname{res}\lambda_{\mathcal C}^{E[2]}=\rho_i\tau_i\) of the
chosen line linearization.  Hypothesis \textup{(K3)} is the explicit
finite computation \(r_i=0\) and \(\rho_i=0\) for all three cyclic
inertia sectors.

\textup{(K4).}  Combining \textup{(K1)}, \textup{(K2)}, \textup{(K3)},
the three cyclic degree-two residuals and degree-one character bits
vanish.  The coefficient conversion above then gives
\(b_{20}=b_{11}=b_{02}=0\), hence
\(\beta^{E,E[2]}_{\mathcal C}=0\in H^2(BE[2];\mathbb Z/2)\); the
equations \(\rho_i=0\) give the trivial \(E[2]\)-linearization.  The
odd-\(N\) cases vanish for the cohomological reason of
Lemma~\ref{lem:E-equivariant-descent-obstruction}.  Even-\(N\) cases
for \(N\ge4\) require the corresponding \(2\)-primary equivariant
linearization calculation.
\end{proof}

\begin{remark}[Orbifold-stratum subtlety]
\label{rmk:bmu2-orbifold-stratum}
The K\"unneth factorization \textup{(K1)} is constructed on the smooth
locus of \(\mathfrak M^{\mathrm{red}}_{\mathcal C}\); on the orbifold
stratum \(K3\times\{e_i\}\subset X\) it requires the orbifold extension
of the Joyce--Tanaka--Upmeier multiplicative cocycle to the inertia
stack of the Klein-four banded quotient.  Joyce--Tanaka--Upmeier
\cite{JoyceTanakaUpmeier} provide the orientation technology for
finite-band quotient stacks.  In the present Klein-four case the
required check is concrete: the inertia decomposition into the three
nontrivial cyclic sectors must carry the same trivial equivariant
linearization.  Equivalently, the degree-two equalities
\(r_i(\mathcal C)=0\) and the degree-one equalities
\(\rho_i(\mathcal C)=0\) of clause \textup{(K4)} must both hold.  Once that is
verified, the
orbifold stratum introduces no additional obstruction beyond the
cyclic-sector criterion.
\end{remark}

\begin{remark}[Two-torsion routes which do not replace the finite criterion]
\label{rmk:bmu2-three-additional-routes}
\label{lem:bmu2-small-orbit-vanishing}
\label{lem:bmu2-w1-vanishing}
\label{lem:bmu2-cohomological-computation}
\label{lem:bmu2-orbifold-lift}
\label{rmk:bmu2-cross-check}
\label{rem:bmu2-honest-status}
\label{rmk:bmu2-orbifold-lift-residual}
There are three natural attempts to turn the \(N=2\) small-orbit
calculation into a direct vanishing theorem.  They are useful checks, but
none replaces Lemma~\ref{lem:bmu2-klein-four-vanishing} and
Corollary~\ref{cor:finite-stabilizer-o1-obstruction}.

\emph{Hyperelliptic route.}  One may try to identify the stabilizer with
the hyperelliptic involution \([-1]\) on \(E\) and prove vanishing from a
trivial action on Picard data.  This is not a theorem in the present
generality.  The action of \([-1]\) on \(\operatorname{Pic}^{0}(E)\) is
inversion, not pointwise triviality, and ordinary fixedness of the line
does not select the equivariant lift.  The route becomes valid only after
one supplies the actual \(E[2]\)-linearized orientation line and proves
that its degree-one character
\(\lambda_{\mathcal C}^{E[2]}\in H^1(BE[2];\mathbb F_2)\) is zero.
That is precisely the \(\rho_i=0\) part of the finite criterion.

\emph{Wu-class route.}  A direct Stiefel--Whitney computation can identify
the degree-two gerbe class with the \(w_2\)-class of the finite
stabilizer representation, and Wu's formula expresses it as
\[
w_2=v_2+Sq^1v_1 .
\]
This gives an independent route to the bits
\((r_1,r_2,r_3)\) once the reduced tangent/self-Ext complex and its
\(E[2]\)-linearization have been constructed.  It still does not compute
the residual \(H^1(BE[2];\mathbb F_2)\)-character of the chosen
linearization.  Hence it can prove a degree-two gerbe vanishing, not
strong reduced orientation.

\emph{Orbifold Pin\(^c\) route.}  One can attempt to build the lift on
the inertia stack of the four \(E[2]\)-fixed sectors by combining the
K3 Pin\(^c\) package of Cao--Kool--Monavari \cite{CaoKoolMonavari}, the
Joyce--Upmeier/Joyce--Tanaka--Upmeier orientation cocycle
\cite{JoyceUpmeier,JoyceTanakaUpmeier}, and To\"en's orbifold
Riemann--Roch \cite{ToenRRRoot}.  This is a legitimate conditional
construction target, not a completed proof here.  It requires an
inertia-stack Pin\(^c\) lift on each cyclic sector, an age-correction
parity calculation, multiplicative gluing across the smooth and
orbifold strata, and trivial residual character under the whole
Klein-four stabilizer.  The \(N=2\) age calculation does not imply the
higher even \(E[N]\) calculation; for \(N\ge4\) the mixed
two-primary class \(A_{12}^{(N)}x_1x_2\) and the degree-one characters
\(\lambda_i^{(N)}\) remain separate obstructions.

Thus the stable theorem in the manuscript is the finite
Klein-four criterion: degree-two gerbe bits and degree-one
linearization characters are both named and must both vanish.  The
three routes above are cross-checks or conditional construction
programmes for those entries.  They are not used as unconditional
vanishing theorems.
\end{remark}

\begin{proposition}[Rank-one two-torsion gerbe and linearization package]
\label{prop:rank-one-e2-linearization-obstruction}
On the rank-one D6--D2--D0 stratum
\(\mathfrak M^{\mathrm{red},(1)}_{(1,\beta,n)}\), assume the ordinary
reduced Pin\(^c\) orientation line has been constructed.  The remaining
\(N=2\) finite-stabilizer gerbe obstruction to descent of this line
through the small-orbit quotient is the vector of three degree-two bits
\[
r_i=\operatorname{res}_{\mu_2^{(i)}}(\beta^{E,E[2]}_{\mathcal C})/\tau_i^2
\in\mathbb Z/2,\qquad i=1,2,3.
\]
Equivalently,
\[
\beta^{E,E[2]}_{\mathcal C}=0
\quad\Longleftrightarrow\quad
(r_1,r_2,r_3)=(0,0,0).
\]
After this class has been null-trivialized, the triviality of the
\(E[2]\)-linearization is a separate degree-one question.  The set of
linearizations is an \(H^1(BE[2];\mathbb F_2)\)-torsor; for a supplied
linearization \(\lambda_{\mathcal C}^{E[2]}\), write
\[
\operatorname{res}_{\mu_2^{(i)}}\lambda_{\mathcal C}^{E[2]}
=\rho_i\tau_i .
\]
Trivial \(E[2]\)-linearization means
\((\rho_1,\rho_2,\rho_3)=(0,0,0)\).  The \(r_i\) are not the \(\rho_i\):
they live in different cohomological degrees.

\begin{enumerate}
\item[\textup{(C)}] \emph{Cyclic-sector character, after
null-trivialization.}  For a genuine \(E[2]\)-linearized orientation line
on the inertia sector,
\[
\rho_i=\frac{1-\chi_i}{2},\qquad
\chi_i=\text{the scalar by which }e_i\text{ acts on }
o^{\mathrm{red}}_{\mathcal C}|_{I_{e_i}\mathfrak M}.
\]
This computes the degree-one linearization character, not the
degree-two gerbe class.
\item[\textup{(W)}] \emph{Stiefel--Whitney/Wu.}  The degree-two bit is the
coefficient of \(\tau_i^2\) in the equivariant reduced obstruction class:
\[
\operatorname{res}_{\mu_2^{(i)}}
w_2^{E[2]}\!\left(\mathbb T^{\mathrm{red}}_{\mathcal C}\right)
=r_i\tau_i^2,\qquad
w_2=v_2+Sq^1v_1,
\]
where \(\mathbb T^{\mathrm{red}}_{\mathcal C}\) is the reduced virtual
tangent/self-Ext complex on the cyclic fixed sector and \(v_j\) are its
Wu classes.
\item[\textup{(P)}] \emph{Inertia-stack Pin\(^c\).}  The degree-two bit is
the Pin\(^c\) central holonomy corrected by the mod-\(2\) orbifold
Riemann--Roch age:
\[
r_i=
\operatorname{hol}_{\ker(\mathrm{Pin}^c\to SO)}
\!\left(\widetilde P^{\,\mathrm{red}}_{\mathrm{Pin}^c}
|_{I_{e_i}\mathfrak M}\right)(e_i)
+\operatorname{age}^{\mathrm{red}}_{e_i}
\pmod2.
\]
\end{enumerate}
Thus the rank-one two-torsion small-orbit sector is closed only after
both vectors vanish:
\[
(r_1,r_2,r_3)=(0,0,0),\qquad
(\rho_1,\rho_2,\rho_3)=(0,0,0).
\]
The present manuscript computes neither vector; the proposition is the
finite obstruction and linearization target, not a vanishing theorem.
\end{proposition}

\begin{proof}
Lemma~\ref{lem:bmu2-klein-four-vanishing} identifies
\[
H^2(BE[2];\mathbb F_2)
=\mathbb F_2\langle x_1^2,x_1x_2,x_2^2\rangle
\]
and proves that restriction to the three cyclic subgroups
\(\mu_2^{(i)}=\langle e_i\rangle\) is jointly injective in degree two.
Hence \(\beta^{E,E[2]}_{\mathcal C}\) vanishes if and only if its three
restrictions \(r_i\tau_i^2\) vanish.

For a line over the quotient stack, after the degree-two gerbe class has
been null-trivialized, the restriction to \(\mu_2^{(i)}\) is a
one-dimensional equivariant line on
\([I_{e_i}\mathfrak M/\mu_2^{(i)}]\).  The character \(\chi_i=\pm1\)
is trivial exactly when the degree-one coefficient \(\rho_i\) is zero;
this is the formula in \textup{(C)}.  The degree-two residual is a
different class.  It is the second Stiefel--Whitney obstruction of the
equivariant reduced tangent/self-Ext complex, and Wu's identity gives
\(w_2=v_2+Sq^1v_1\), giving \textup{(W)}.  Finally, a Pin\(^c\) lift of
the cyclic-sector frame records the central \(\mathbb Z/2\)-holonomy of
\(\ker(\mathrm{Pin}^c\to SO)\); orbifold Riemann--Roch contributes the
age correction on the fixed inertia sector.  This is \textup{(P)}.  The
formulae \textup{(W)} and \textup{(P)} compute the residual degree-two class
\(\operatorname{res}_{\mu_2^{(i)}}\beta^{E,E[2]}_{\mathcal C}\), while
\textup{(C)} computes the residual degree-one choice after that class has
been null-trivialized.
\end{proof}

\begin{lemma}[Even finite-stabilizer residuals beyond two torsion]
\label{lem:even-finite-stabilizer-residuals}
Let \(N\) be even and write \(2^a\parallel N\).  On the
\(N\)-fold small-orbit stratum of the reduced \(E\)-quotient, the
positive-degree mod-\(2\) finite-stabilizer obstruction is the
two-primary class
\[
\beta^{E,N}_{\mathcal C,(2)}
\in H^2\!\left(B(\Z/2^a)^2;\mathbb F_2\right).
\]
For \(a=1\) this is the Klein-four class
\(\beta^{E,E[2]}_{\mathcal C}\) of
Lemma~\ref{lem:bmu2-klein-four-vanishing}.  For \(a\ge2\),
\[
H^*\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\Lambda(x_1,x_2)\otimes\mathbb F_2[y_1,y_2],
\qquad |x_i|=1,\quad |y_i|=2,\quad x_i^2=0,
\]
and therefore
\[
H^2\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\mathbb F_2\langle y_1,x_1x_2,y_2\rangle.
\]
Write
\[
\beta^{E,N}_{\mathcal C,(2)}
=A_1^{(N)}y_1+A_{12}^{(N)}x_1x_2+A_2^{(N)}y_2 .
\]
Let \(g_1,g_2\) be the standard generators of
\((\Z/2^a)^2\), put \(h_i=2^{a-1}g_i\), \(i=1,2\), and
\(h_3=h_1+h_2\).  For the three order-two cyclic subgroups
\(\langle h_i\rangle\),
\[
\operatorname{res}_{\langle h_1\rangle}\beta^{E,N}_{\mathcal C,(2)}
=A_1^{(N)}\tau_1^2,\qquad
\operatorname{res}_{\langle h_2\rangle}\beta^{E,N}_{\mathcal C,(2)}
=A_2^{(N)}\tau_2^2,
\]
\[
\operatorname{res}_{\langle h_3\rangle}\beta^{E,N}_{\mathcal C,(2)}
=(A_1^{(N)}+A_2^{(N)})\tau_3^2 .
\]
The mixed coefficient \(A_{12}^{(N)}\) is invisible to all cyclic
restrictions, not only to the three order-two subgroups above.  It is
detected by the rank-two quotient
\((\Z/2^a)^2\twoheadrightarrow(\Z/2)^2\), which pulls the mixed class
\(\bar x_1\bar x_2\) back to \(x_1x_2\).
Therefore the three \(E[2]\) bits \(r_1,r_2,r_3\) do not determine the
even \(N\ge4\) residual.  Vanishing for \(N\ge4\) is a separate
\(2^a\)-primary equivariant-linearization calculation on the
small-orbit stratum.  After
\(\beta^{E,N}_{\mathcal C,(2)}=0\), triviality of the chosen
two-primary linearization is a further degree-one condition:
\[
\lambda_{\mathcal C}^{E,N}
=\lambda_1^{(N)}x_1+\lambda_2^{(N)}x_2
\in H^1\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
\]
must vanish.  This character is detected on the cyclic subgroups
generated by \(g_1\) and \(g_2\), not by the order-two subgroups
\(\langle h_i\rangle\).
\end{lemma}

\begin{proof}
The odd part of \(E[N]\simeq(\Z/N)^2\) has order invertible in
\(\mathbb F_2\), so transfer identifies the positive-degree
\(\mathbb F_2\)-cohomology with that of the two-primary factor
\((\Z/2^a)^2\).  If \(a=1\), this is \(E[2]\) and the cohomology ring is
\(\mathbb F_2[x_1,x_2]\), \(|x_i|=1\), giving the Klein-four basis
\(\langle x_1^2,x_1x_2,x_2^2\rangle\).  If \(a\ge2\), the cyclic
calculation gives
\[
H^*(B\Z/2^a;\mathbb F_2)
\cong\Lambda(x)\otimes\mathbb F_2[y],
\qquad |x|=1,\quad |y|=2,\quad x^2=0.
\]
Kunneth for the product gives the degree-two basis
\(\langle y_1,x_1x_2,y_2\rangle\).

For the restriction formulas, restrict first to the order-two subgroup
\(\langle h_1\rangle=\langle2^{a-1}g_1\rangle\).  The degree-one class
\(x_1\in H^1(B\Z/2^a;\mathbb F_2)\) restricts to zero because the
generator \(h_1\) maps to \(2^{a-1}\equiv0\pmod2\) under the mod-two
character, while the degree-two cyclic extension class \(y_1\) restricts
to the generator \(\tau_1^2\in H^2(B\langle h_1\rangle;\mathbb F_2)\).
The same calculation holds for \(h_2\).  For
\(h_3=2^{a-1}(g_1+g_2)\), both \(y_1\) and \(y_2\) restrict to
\(\tau_3^2\), while \(x_1\) and \(x_2\) restrict to zero.  Hence
\(x_1x_2\) restricts to zero on all three order-two cyclic subgroups,
and the displayed formulas follow.

The quotient \((\Z/2^a)^2\twoheadrightarrow(\Z/2)^2\) identifies
\(H^1(B(\Z/2)^2;\mathbb F_2)\) with the span of \(x_1,x_2\); hence
\(\bar x_1\bar x_2\) inflates to \(x_1x_2\).  The mixed coefficient is
therefore a genuine rank-two equivariant-linearization obstruction.
It is invisible on every cyclic subgroup: for a cyclic subgroup of order
\(2\), the degree-one classes \(x_1,x_2\) restrict to zero as above; for
a cyclic subgroup of order \(2^b\) with \(b\ge2\), the restrictions of
\(x_1,x_2\) are scalar multiples of the single degree-one generator
\(x\), and \(x_1x_2\) restricts to a scalar multiple of \(x^2=0\) in
\(H^2(B\Z/2^b;\mathbb F_2)\).
This is a different stabilizer calculation from the \(N=2\) Klein-four
residual, so the vanishing of \((r_1,r_2,r_3)\) supplies no vanishing
theorem for \(N\ge4\).  Finally, when the degree-two class has vanished,
the residual two-primary linearisations are classified by
\[
H^1\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\mathbb F_2\langle x_1,x_2\rangle .
\]
The order-two subgroups generated by \(h_i=2^{a-1}g_i\) do not detect
this character, since \(x_j(h_i)=0\).  Triviality must be checked on
the full two-primary generators, for instance \(g_1,g_2\).
\end{proof}

\begin{corollary}[Finite-stabilizer obstruction to \textup{(O1)}]
\label{cor:finite-stabilizer-o1-obstruction}
Fix a small-orbit stratum \(S\) of the reduced \(E\)-quotient with
stabilizer \(E[N]\).  Assume that the ordinary reduced square-root gerbe
\(\alpha^{\mathrm{red}}_{\mathcal C}\) and the connected free quotient
class \(\alpha^{E,\mathrm{free}}_{\mathcal C}\) have already been
null-trivialized on this stratum.  Then the finite-stabilizer part of
the strong reduced orientation \textup{(O1)} exists with trivial quotient
linearization if and only if the Borel descent class
\(\widetilde\beta^{E,N}_{\mathcal C,S}\) and the selected residual
character vanish.  After the Borel mixed terms, stabilizer action on
\(H^\bullet(S;\mathbb F_2)\), and spectral-sequence differentials have
been killed, this condition is computed by the following finite
point-stabilizer tuple.
\begin{enumerate}
\item If \(N\) is odd, there is no positive-degree mod-\(2\)
finite-stabilizer obstruction:
\[
H^{>0}(BE[N];\mathbb F_2)=0.
\]
\item If \(N=2\), the tuple is
\[
\mathfrak o^{E[2]}_{\mathcal C}
=
\bigl(r_1,r_2,r_3;\rho_1,\rho_2,\rho_3\bigr),
\]
where
\[
\operatorname{res}_{\langle e_i\rangle}
\beta^{E,E[2]}_{\mathcal C}=r_i\tau_i^2,\qquad
\operatorname{res}_{\langle e_i\rangle}
\lambda^{E[2]}_{\mathcal C}=\rho_i\tau_i .
\]
Equivalently,
\[
\beta^{E,E[2]}_{\mathcal C}=0
\quad\text{and}\quad
\lambda^{E[2]}_{\mathcal C}=0 .
\]
\item If \(N\) is even and \(2^a\parallel N\) with \(a\ge2\), the tuple is
\[
\mathfrak o^{E[N]}_{\mathcal C}
=
\bigl(A_1^{(N)},A_{12}^{(N)},A_2^{(N)};
\lambda_1^{(N)},\lambda_2^{(N)}\bigr),
\]
where
\[
\beta^{E,N}_{\mathcal C,(2)}
=A_1^{(N)}y_1+A_{12}^{(N)}x_1x_2+A_2^{(N)}y_2
\]
and
\[
\lambda^{E,N}_{\mathcal C}
=\lambda_1^{(N)}x_1+\lambda_2^{(N)}x_2
\in H^1(B(\Z/2^a)^2;\mathbb F_2).
\]
\end{enumerate}
Thus the \(E[2]\) three-bit calculation proves only the point-stabilizer
reduction of the \(N=2\) degree-two gerbe vanishing.  It does not prove
the higher even
finite-stabilizer class \(A_{12}^{(N)}x_1x_2\), and it does not prove
the residual degree-one linearization character.  Any non-zero entry of
\(\mathfrak o^{E[N]}_{\mathcal C}\) obstructs \textup{(O1)} on that
small-orbit stratum.  No scalar automorphic character, Borcherds
divisor order, or OP/DT scalar square changes this finite quotient
obstruction.
\end{corollary}

\begin{proof}
For a finite stabilizer \(G=E[N]\), the Borel descent spectral sequence
\[
E_2^{p,q}=H^p(BG;\,H^q(\mathfrak M^{\mathrm{red}}_{\mathcal C};
\mathbb F_2))
\Longrightarrow
H_G^{p+q}(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2)
\]
puts the finite square-root obstruction
\(\widetilde\beta^{E,N}_{\mathcal C,S}\) in total degree two.  After that
class is null-trivialized, linearizations of the resulting line form an
\(H^1(BG;\mathbb F_2)\)-torsor.  Hence descent with the trivial quotient
orientation is equivalent to the simultaneous vanishing of the degree-two
finite Borel class and the selected degree-one character.  The displayed
point-stabilizer formulas are reductions of this Borel statement after
the mixed terms and differentials vanish.  The odd case is transfer.  The
\(N=2\) case is
Lemma~\ref{lem:bmu2-klein-four-vanishing} together with
Proposition~\ref{prop:rank-one-e2-linearization-obstruction}.  The
higher even case is Lemma~\ref{lem:even-finite-stabilizer-residuals}.
\end{proof}

\begin{proposition}[Finite-stage quotient-orientation character system]
\label{prop:finite-stage-quotient-orientation-character-system}
Fix a finite HN height \(R\) in the compact/wrapped certificate of
Definition~\ref{def:hybrid-wrapped-factorization-certificate}.  Let
\(\mathsf{Str}^{or}_R\) be the finite set of reduced object, extension,
and flag strata of \(\mathsf{Corr}^{E,\mathrm{hyb}}_R\) on which
vanishing-cycle coefficients and orientation lines are pulled, pushed, or
compared.  For \(S\in\mathsf{Str}^{or}_R\), write
\(\mathcal C(S)\) for its charge label and
\(\mathcal N_R(S)\) for the finite stabilizers \(E[N]\) appearing on its
small-orbit components.

A finite-stage quotient-orientation character system is the datum
\[
\mathfrak Q^{or}_R
=
\left(
\{o_{R,S}\}_{S\in\mathsf{Str}^{or}_R},
\{\theta^{\mathrm{red}}_{R,S}\},
\{\theta^{E,\mathrm{free}}_{R,S}\},
\{\theta^{E,N}_{R,S},\,\lambda^{E,N}_{R,S}=0\}_{N\in\mathcal N_R(S)},
\{\mu^{or}_{R,e}\},
\{\Theta^{or}_{R,\mathrm{flag}}\}
\right).
\]
Here \(o_{R,S}^{\otimes2}\) is identified with the reduced determinant
line on object strata and with the corresponding pulled-back coefficient
determinant on extension and flag strata;
\(\theta^{\mathrm{red}}_{R,S}\) null-trivializes the ordinary reduced
gerbe, \(\theta^{E,\mathrm{free}}_{R,S}\) null-trivializes the connected
\(BE\)-class, and \(\theta^{E,N}_{R,S}\) null-trivializes the finite
Borel class
\[
\widetilde\beta^{E,N}_{R,S}\in H^2_{E[N]}(S;\mathbb F_2).
\]
Its point-stabilizer restriction is a class
\(\beta^{E,N}_{R,S}\in H^2(BE[N];\mathbb F_2)\) only after the mixed
Borel terms, stabilizer action on \(H^\bullet(S;\mathbb F_2)\), and
spectral-sequence differentials have been killed.  After this finite
Borel class has been null-trivialized, the chosen
finite-stabilizer linearization has character
\[
\lambda^{E,N}_{R,S}\in H^1(BE[N];\mathbb F_2),
\]
and the quotient system selects the zero character.  The maps
\(\mu^{or}_{R,e}\) are the Thom--Sebastiani orientation transports along
the local-local, local/wrapped, and wrapped-wrapped correspondence
generators \(e\), and \(\Theta^{or}_{R,\mathrm{flag}}\) records their
two-step flag coherences.

Such a system exists on the finite stage if and only if every stratum
\(S\in\mathsf{Str}^{or}_R\) has
\[
\alpha^{\mathrm{red}}_{R,S}=0,\qquad
\alpha^{E,\mathrm{free}}_{R,S}=0,
\]
and its finite-stabilizer obstruction tuple vanishes as follows:
\[
N\ \text{odd}:\quad H^{>0}(BE[N];\mathbb F_2)=0,
\]
\[
N=2:\quad
\bigl(r_1,r_2,r_3;\rho_1,\rho_2,\rho_3\bigr)=0,
\]
\[
2^a\parallel N,\ a\ge2:\quad
\bigl(A_1^{(N)},A_{12}^{(N)},A_2^{(N)};
\lambda_1^{(N)},\lambda_2^{(N)}\bigr)=0,
\]
with the notation of
Corollary~\ref{cor:finite-stabilizer-o1-obstruction}, and all
orientation-transport defects along the correspondence generators, flag
stacks, and \(R'\ge R\) transition maps vanish.  If the systems
\(\mathfrak Q^{or}_R\) exist for a cofinal family of finite stages and
are compatible with the transition maps, their inverse limit is exactly
the strong reduced orientation datum (O1) on the compact/wrapped Hall
sector.  Conversely, any (O1) datum restricts to such a compatible
finite-stage system.  No automorphic scalar, Borcherds divisor order, or
Maass target character detects any of the finite \(H^1(BE[N])\)
characters.
\end{proposition}

\begin{proof}
For each stratum \(S\), the ordinary and connected \(E\)-quotient parts
are the descent classes of
Lemma~\ref{lem:E-equivariant-descent-obstruction}.  For every finite
small-orbit stabilizer \(E[N]\), the degree-two finite gerbe and the
residual degree-one character are precisely the obstruction tuple of
Corollary~\ref{cor:finite-stabilizer-o1-obstruction}.  Thus the displayed
stratumwise vanishings are necessary and sufficient for the coefficient
orientation line to descend with trivial finite-stabilizer character on
each object, extension, and flag stratum.

The remaining conditions are functorial, not cohomological.  A Hall
operation at height \(R\) is the pull--Thom--Sebastiani--push map attached
to a generator of \(\mathsf{Corr}^{E,\mathrm{hyb}}_R\).  The
orientation transports \(\mu^{or}_{R,e}\) must identify the descended
coefficient systems on the source and target of this generator.  The two
ways to compose such identifications over a two-step flag stack differ
by a finite defect; vanishing of all flag defects is exactly the strict
pentagon condition at height \(R\).  The same statement for successor
maps is the displayed transition compatibility.  Since the stage is
finite, these are finitely many equalities.  Passing to a cofinal inverse
system gives (O1), and restriction of (O1) to a finite height gives the
listed data.  The final sentence follows because the obstruction groups
are the displayed Borel-equivariant \(H^2\) and \(H^1\) groups, whereas a
scalar automorphic character is not a class in them.
\end{proof}

\begin{lemma}[Rank-one Pin-lift sign rigidification conditional on a supplied lift]
\label{lem:spin-lift-sign-fixing}
Assume the BBDJS Pin\(^c\) lift \cite{BBDJS2015} of the \(\SO\)-frame
bundle of
\(\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C)\) on
\(\mathfrak M^{\mathrm{red},(1)}_{(1,\beta,n)}\) has been constructed
after the ordinary reduced gerbe class has vanished.  Its underlying
\(\SO\)-bundle determines it only up to a global \(\mathbb Z/2\)
ambiguity
\(\eta_{\mathcal C}\in
H^0(\mathfrak M^{\mathrm{red},(1)}_{(1,\beta,n)};\mathbb Z/2)\), the
kernel of the surjection
\(\mathrm{Pin}^c\twoheadrightarrow\SO\) acting on global sections of the
lift.  On the rank-one D6--D2--D0 stratum, this residual sign is
rigidified by the following data, jointly:
\begin{enumerate}
\item[(S1)] the Joyce--Upmeier orientability cocycle
\cite{JoyceUpmeier}, \cite{JoyceTanakaUpmeier} on Hall extension
correspondences, which imposes multiplicative compatibility when
rank-one factors are used as graded pieces of HN or direct-sum strata.
This is a compatibility constraint for extending signs beyond the
rank-one components; it is not a proof that the rank-one locus itself is
generated by one component under direct sum;
\item[(S2)] the requirement that, after the supplied comparison
\(\iota_{\mathrm{aut}}\), the Pfaffian section
\(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X)\) is read as a section of
\(\mathcal L^5\otimes\nu_{\Delta_5}\) and restricts at the unique
top-cohomology generator of the isotropic-cusp expansion to the monic
Borcherds normalization \(D_5=64^{-1}\Delta_5\) of
Proposition~\ref{prop:bgn-identification}; equivalently, the leading
Fourier coefficient of \(\operatorname{Pf}_{\mathrm{prot}}\) at the
isotropic cusp \(\mathfrak c_\infty\) equals \(+1\) (positive
orientation, monic);
\item[(S3)] scalar consistency, after squaring, with the OP/DT scalar sign
\(C_{\square,X}=-4096\) of Proposition~\ref{prop:op-normalization}, i.e.\
\((\operatorname{Pf}_{\mathrm{prot}})^{2}\!|_{\mathrm{rank\textnormal{-}one}}
=\Delta_5^{2}\) with positive leading coefficient
\(c_\Delta(1,1,1)^2=64^2=4096\), the absolute value of
\(C_{\square,X}\), and
the OP scalar sign \(\operatorname{sign}(C_{\square,X})=-1\) absorbed into the
fermionic shift \((-p_{\mathrm{DT}})^n\) of the OP/DT chamber, not into
the orientation line; this is a scalar compatibility check, not a
rigidifying input for \(\eta_{\mathcal C}\).
\end{enumerate}
Then, on any connected rank-one component for which the supplied
\(\iota_{\mathrm{aut}}\) identifies the Pfaffian section with the monic
cusp branch, the residual sign \(\eta_{\mathcal C}\) is fixed to \(+1\)
for that component.  This fixes a chosen global sign there.  It does not
prove that the same choice extends over all rank-one charge components,
over HN sums, or through the reduced \(E\)-quotient; those compatibilities
are part of \textup{(O1)} and \textup{(O1)}\(^+\), including the connected
\(BE\)-linearization and finite \(E[N]\)-residual vanishings.
\end{lemma}

\begin{proof}
The \(\mathrm{Pin}^c\twoheadrightarrow\SO\) sequence has kernel \(\mathbb Z/2\),
so on a connected component the global lift is unique up to multiplying
by a constant element of this kernel; on the disconnected components of
\(\mathfrak M^{\mathrm{red},(1)}_{(1,\beta,n)}\) (indexed by the
discrete Mukai-charge label \((1,\beta,n)\), connected within each
fixed charge by the Beauville--Mukai moduli construction
\cite{Mukai1984,Mukai1987,HuybrechtsLehn}) the ambiguity is the function
\(\eta\colon\pi_0\mathfrak M^{\mathrm{red},(1)}\to\{\pm 1\}\).

\emph{(S1)} fixes the multiplicative compatibility that any extension of
\(\eta\) to Hall direct-sum or HN correspondence strata must satisfy: by
Joyce--Upmeier
\cite[Theorem~5.1]{JoyceUpmeier}, the orientation cocycle on the
extension correspondence
\(\mathfrak M^{\mathrm{red},(1)}_{\mathcal C}\times
\mathfrak M^{\mathrm{red},(1)}_{\mathcal C'}\to
\mathfrak M^{\mathrm{red},(1)}_{\mathcal C+\mathcal C'}\) is the Mukai
parity \((-1)^{\langle\mathcal C,\mathcal C'\rangle_{\mathrm{Mukai}}}\),
and the BBDJS Pin\(^c\) lift respects this cocycle by
\cite[\S5.4]{BBDJS2015} together with the cosection-twist compatibility
of \cite{CaoKoolMonavari}.  Hence an already supplied extension of
\(\eta\) must be multiplicative modulo the Mukai parity.  This does not
show that all rank-one charge components are generated by one component.

\emph{(S2)} fixes \(\eta\) on any connected component on which the
supplied \(\iota_{\mathrm{aut}}\) compares the Pfaffian section with the
monic cusp branch: the Pfaffian section is a section of
\(\mathcal L^5\otimes\nu_{\Delta_5}\), and
Proposition~\ref{prop:bgn-identification} together with the
square-root normalization table of
Remark~\textup{Normalization of the square root} require the leading
Fourier coefficient of \(\operatorname{Pf}_{\mathrm{prot}}\) at
\(\mathfrak c_\infty\) to be \(+1\) (the monic
\(D_5=64^{-1}\Delta_5\) being the canonical Borcherds output).  The
coefficient \(64\) is the theta-normalization converting the monic
Borcherds product \(D_5\) to \(\Delta_5\); it is not the square of an
orientation line.  The orientation line chooses the sign of a supplied
first-order Pfaffian section, not the scalar prefactor.  This pins
\(\eta_{\mathcal C}\in\{+1,-1\}\) to a specific value on that component.

\emph{(S3)} verifies consistency: squaring an orientation line forgets
\(\eta\), so the only sign data surviving after squaring are
\((c_\Delta(1,1,1))^2=4096\) (positive, automatic) and the
fermionic-shift sign \(\operatorname{sign}(C_{\square,X})=-1\), which lives in
the OP/DT chamber of Proposition~\ref{prop:op-normalization} (the
\((-p_{\mathrm{DT}})^n\) factor) and does not constrain \(\eta\).  So
(S3) is consistent with (S2) but does not refine it.  Combining (S1)
and (S2), \(\eta_{\mathcal C}=+1\) on each supplied connected component
whose Pfaffian branch has been compared with the monic cusp branch; any
extension to other rank-one charge components or to HN sums remains a
separate orientation datum.

The choice is determinate once the ordinary lift and quotient
linearizations have been supplied.  This is the analogue, on the
cosection-twisted reduced \(K3\times E\) rank-one sector, of the BBDJS
Pin lift sign convention of \cite[\S5.4]{BBDJS2015} and the
Joyce--Upmeier rigidification by Pfaffian normalization data
\cite{JoyceUpmeier}.  It is not a proof that
\(\alpha^{E,\mathrm{free}}_{\mathcal C}\) or
\(\beta^{E,E[2]}_{\mathcal C}\) vanishes.
\end{proof}

\begin{remark}
\label{rmk:sign-fixing-higher-rank}
The same data \textup{(S1)}, \textup{(S2)}, \textup{(S3)} rigidify
\(\eta_{\mathcal C}\) on a higher-rank semistable stratum only after the
Pin\(^c\)-lift gerbe class \(\alpha^{\mathrm{red}}_{\mathcal C}\) of
\textup{(P3)} and the required quotient linearization classes have
already vanished.
\end{remark}


\begin{lemma}[HN-reducible Pin\(^c\)-lift gerbe criterion]
\label{lem:p3-higher-rank-pin-c-vanishing}
Let \(\mathcal C\) be a higher-rank protected charge and let
\(\tau=(\mathcal C_1,\ldots,\mathcal C_\ell)\) be an HN-type of length
\(\ell\ge2\) in the reduced semistable stack.  On the corresponding
HN stratum, the reduced orientation gerbe satisfies
\[
\alpha^{\mathrm{red}}_{\mathcal C}|_\tau
=\sum_i\alpha^{\mathrm{red}}_{\mathcal C_i}\bmod2,
\]
with off-diagonal self-Ext blocks contributing even class.  Therefore
\(\alpha^{\mathrm{red}}_{\mathcal C}|_\tau=0\) on every HN stratum whose
graded factors lie in the already-oriented rank-one sector or in a
rank-two sector covered by Lemma~\ref{lem:p3-brauer-gerbe-vanishing}.
If, in addition, the \(E\)-equivariant parity
\[\sum_i d_E(\mathcal C_i)\operatorname{rk}(\det\mathcal C_i)\]
is even, then the joint class
\(\alpha^{\mathrm{red}}_{\mathcal C}+\alpha^E_{\mathcal C}\) vanishes
on that HN stratum, subject to the finite-stabilizer criterion of
Lemma~\ref{lem:bmu2-klein-four-vanishing} on any small-orbit boundary.
Stable higher-rank length-one HN strata are not covered by this lemma.
\end{lemma}

\begin{proof}
The HN stratification expresses a length-\(\ell\) stratum as an extension
stack over the product of the moduli of its graded factors.  The
Joyce--Upmeier and Joyce--Tanaka--Upmeier multiplicative orientation
formalism \cite{JoyceUpmeier,JoyceTanakaUpmeier} identifies the
orientation gerbe of the direct-sum target with the tensor product of
the gerbes of the graded pieces.  The off-diagonal reduced self-Ext
blocks occur in dual pairs under the shifted-symplectic pairing, so
their Stiefel--Whitney contribution is even.  This gives the displayed
additivity formula.  The stated vanishing follows immediately when each
graded factor lies in a sector whose orientation gerbe has already been
trivialized.

The connected \(E\)-descent obstruction is computed by the equivariant
Serre spectral sequence of the free translation quotient; on an HN
stratum its parity is the sum of the elliptic rotation numbers of the
graded factors.  If that sum is even, the connected obstruction
vanishes.  The remaining torsion part is the small-orbit finite
stabilizer gerbe; the rank-one \(N=2\) detection criterion is isolated
in Lemma~\ref{lem:bmu2-klein-four-vanishing}.  No induction on stable
higher-rank length-one factors is used.
\end{proof}


\section{Physical charge and normal-ordered Gram descent}
\label{sec:duality-principle}

The Hall charge is additive.  The Igusa degree is not.  This section
isolates the exact defect and removes it by normal ordering.  The result
is a lattice theorem, not yet a chain-level Hall strictification.

\begin{definition}[Dyonic Mukai lattice and quadratic Gram projection]
\label{def:dyonic-mukai-lattice}
Let \(S\) be a complex K3 surface and put
\[
\La_S:=H^*(S,\Z)
=H^0(S,\Z)\oplus H^2(S,\Z)\oplus H^4(S,\Z),
\]
the Mukai lattice in the sense of
Mukai \cite{Mukai1984,Mukai1987}: even, unimodular, signature
\((4,20)\), rank \(24\), equipped with the Mukai pairing
\(\langle (r,c,s),(r',c',s')\rangle_{\mathrm{Muk}}=c\cdot c'-rs'-r's\).
The formal full-Mukai dyonic lattice is the additive abelian group
\[
\Gamma_X^{\mathrm{form}}:=\La_S\oplus\La_S,\qquad
c=(Q,P)\in\Gamma_X^{\mathrm{form}},
\]
graded electric \(\oplus\) magnetic.  Throughout the formulae below in
this paper,
\[
\Gamma_X^{\mathrm{phys}}:=\Gamma_X^{\mathrm{form}}.
\]
In legacy lattice formulae below the
superscript \(\mathrm{phys}\) is only mnemonic for this formal even Mukai
sector \(\Gamma_X^{\mathrm{form}}\).  It is not the full four-dimensional
\(\mathcal N=4\) electric--magnetic charge lattice and not compact Hall
support.  It is the D6--D2--D0/OP branch on which the Mukai Gram map is
tested before imposing algebraicity, effectivity, stability, or
nonemptiness of compact Hall moduli.  For a chosen stability sector the
actual Hall support is a semigroup
\(\Gamma_{X,\sigma}^{\mathrm{eff}}\subset\Gamma_X^{\mathrm{alg}}
\subset\Gamma_X^{\mathrm{form}}\); membership in that semigroup is not
proved by the formal lattice arithmetic.  The Gram-index lattice is
\[
\Gamma_{\mathrm{gram}}:=\Z^3.
\]
The Gram map is the quadratic projection
\[
\Pi_X:\Gamma_X^{\mathrm{phys}}\longrightarrow\Gamma_{\mathrm{gram}},
\qquad
(Q,P)\longmapsto\bigl(\tfrac{(Q,Q)}2,(Q,P),\tfrac{(P,P)}2\bigr).
\]
The bilinear obstruction to additivity of \(\Pi_X\) is the symmetric
cocycle
\[
B:\Gamma_X^{\mathrm{phys}}\times\Gamma_X^{\mathrm{phys}}
\longrightarrow\Gamma_{\mathrm{gram}},\qquad
B(c,c')=\bigl((Q,Q'),(Q,P')+(Q',P),(P,P')\bigr),
\]
satisfying
\(\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c')\) and
\(B(c,c)=2\Pi_X(c)\); \([B]=0\) in
\(H^2_{\mathrm{sym}}(\Gamma_X^{\mathrm{phys}};\Gamma_{\mathrm{gram}})\)
via Lemma~\ref{lem:b-cocycle-central-extension}.  The central extension
\[
\widehat\Gamma_X:=\Gamma_X^{\mathrm{phys}}\oplus_B\Gamma_{\mathrm{gram}},
\qquad
(c,T)\star(c',T'):=\bigl(c+c',\,T+T'+B(c,c')\bigr),
\]
has the normal-ordered Gram homomorphism
\[
\overline\Pi_X(c,T)=\Pi_X(c)-T.
\]
It is the additive abelian group on which a Hall product graded by formal
charge and normal-ordered Gram invariants can be formulated.  A compact
Hall source must still restrict this formal group to its algebraic and
effective support.
\end{definition}

\begin{remark}
The quadratic-projection identity
\(\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c')\) expands
\((Q+Q',Q+Q')/2\), \((Q+Q',P+P')\), \((P+P',P+P')/2\).
Cohomologically the central extension is split
(\([B]=0\), Remark~\ref{rem:b-cocycle-status}), but the splitting
requires the quadratic primitive \(\Pi_X\), not a linear cochain.
Dyonic charges with distinct \((Q,P)\) but identical \((n,l,m)\) sit in
the same Gram sector; the Hall bracket distinguishes them through the
physical grading on \(\Gamma_X^{\mathrm{phys}}\) before passing to Gram
invariants.
\end{remark}

The preceding determinant was constructed in one cusp chamber.  Duality
does not preserve the displayed chamber inequalities in the same
coordinates; it transports the chamber, the Fourier expansion, and the
automorphic line together.  The invariant object is
$$
\mathcal D_X=\Delta_5\in M_5(\Sp_4(\Z),\nu_{\Delta_5}),
$$
with cusp expansion
$$
\mathcal D_X|_{\mathfrak c_\infty}
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}.
$$

For
$$Z=\begin{pmatrix}z_1&z_2\\z_2&z_3\end{pmatrix},$$
put
$$q=e^{2\pi iz_1},\qquad r=e^{2\pi iz_2},\qquad s=e^{2\pi iz_3}.$$
For
$$
T(n,l,m)=
\begin{pmatrix}n&l/2\\ l/2&m\end{pmatrix},
\qquad n,l,m\in\Z,
$$
put
$$
(T(n,l,m),Z)_{\mathrm{tr}}
=\operatorname{tr}(T(n,l,m)Z)=nz_1+lz_2+mz_3.
$$
Then
$$x^{(n,l,m)}=\exp(2\pi i(T(n,l,m),Z)_{\mathrm{tr}})
=q^nr^ls^m.$$

\begin{definition}[Gram-index notation]
$$
\Gamma_{\mathrm{gram}}:=\Gamma_{\mathrm{ind}}:=\Z^3,\qquad
\Gamma_{\mathrm{act}}\subset\Gamma_{\mathrm{eff}}\subset\Gamma_{\mathrm{gram}}.
$$
Here \(\Gamma_{\mathrm{eff}}\) is the cusp-positive semigroup and
\(\Gamma_{\mathrm{act}}\) is the non-zero Jacobi-support locus.  This is
notation for Gram invariants and Fourier indices.  It is not the compact
Hall support; the formal dyonic lattice is
\(\Gamma_X^{\mathrm{phys}}=\Gamma_X^{\mathrm{form}}=\La_S\oplus\La_S\)
of Definition~\ref{def:dyonic-mukai-lattice}, and the Gram-index lattice is
the image of the quadratic projection
\(\Pi_X:\Gamma_X^{\mathrm{phys}}\to\Gamma_{\mathrm{gram}}\).  A Hall
algebra cannot be graded by \(\Gamma_{\mathrm{ind}}\) directly because
\(\Pi_X\) is quadratic; the correct grading lattice is the central
extension
\(\widehat\Gamma_X=\Gamma_X^{\mathrm{phys}}\oplus_B\Gamma_{\mathrm{gram}}\)
(Definition~\ref{def:dyonic-mukai-lattice}).  The grading on
\(\mathcal A_{\mathrm{den}}\) by \(\Gamma_{\mathrm{ind}}\) is then the
normal-ordered image of a \(\widehat\Gamma_X\)-grading on a hypothetical
Hall source whose actual support lies in an algebraic/effective
semigroup.  The chain-level lift of this image is part of the open Hall
datum.
\end{definition}

\begin{proposition}[Gram matrix convention for protected charges]
Assume a protected charge grading with primitive electric-magnetic pair
\(Q,P\) in an even lattice.  Set
$$
n=\frac{(Q,Q)}2,\qquad l=(Q,P),\qquad m=\frac{(P,P)}2.
$$
Then
$$
\begin{pmatrix}(Q,Q)&(Q,P)\\ (P,Q)&(P,P)\end{pmatrix}
=2T(n,l,m),
$$
and the Gram discriminant is
$$
\det(2T(n,l,m))=4nm-l^2.
$$
The genus-two chemical potential \(Z\) pairs with the same matrix:
$$
\exp(2\pi i\,\operatorname{tr}(TZ))=q^nr^ls^m.
$$
Thus the Borcherds monomial records the Gram invariants of the protected
charge grading, once such a physical grading has been supplied.
\end{proposition}

\begin{proof}
By hypothesis the compactification charge lattice is even, so
\((Q,Q)/2\) and \((P,P)/2\) are integral and \((Q,P)\in\Z\).  The matrix
identity and its determinant are immediate.  The final equality is the
Fourier character attached to the chemical potential \(Z\).  The
Harvey--Moore and Dijkgraaf--Verlinde--Verlinde interpretation of this
Fourier character as a physical charge grading is additional physical
input \cite{HM}, \cite{DVV}.
\end{proof}

\begin{definition}[Formal additive even Mukai sector and Gram shadow]
\label{def:additive-physical-charge-lattice}
Let \(X=S\times E\), with \(S\) a K3 surface, and let
\[
\Lambda_S:=\widetilde H(S,\Z)
=H^0(S,\Z)\oplus H^2(S,\Z)\oplus H^4(S,\Z)
\]
with Mukai pairing
\[
(r,D,s)\cdot(r',D',s')=D\cdot D'-rs'-r's.
\]
In the formal even \(K3\times E\) Mukai sector, every class decomposes as
\[
v_X=P\otimes 1_E+Q\otimes\omega_E,\qquad Q,P\in\Lambda_S,
\]
where \(\int_E\omega_E=1\).  The formal additive dyonic lattice is
\[
\Gamma_X^{\mathrm{form}}:=\Lambda_S\oplus\Lambda_S,\qquad
\Gamma_X^{\mathrm{phys}}:=\Gamma_X^{\mathrm{form}},\qquad c=(Q,P).
\]
The superscript \(\mathrm{phys}\) is retained only as a mnemonic in older
formulas for this formal sector.
For exact triangles or Hall extensions inside a supplied algebraic
effective source sector the class \(c\) is additive.  The
Igusa variables are the Gram shadow
\[
\Pi_X:\Gamma_X^{\mathrm{form}}\longrightarrow\Gamma_{\mathrm{gram}},
\qquad
\Pi_X(Q,P)=\left(\frac{Q^2}{2},\,Q\cdot P,\,\frac{P^2}{2}\right).
\]
The map \(\Pi_X\) is an invariant map to Fourier/root degrees; it is not
the compact Hall support.
\end{definition}

\begin{lemma}[Formal primitive torsion-one lift of every Gram triple]
\label{lem:primitive-lift-every-gram-triple}
Suppose \(\Lambda_S\) contains two orthogonal hyperbolic planes
\[
U_1\oplus U_2
=\mathbb Ze_1\oplus\mathbb Zf_1\oplus
\mathbb Ze_2\oplus\mathbb Zf_2,
\]
with \(e_i^2=f_i^2=0\), \(e_i\cdot f_i=1\), and \(U_1\perp U_2\).
Then every Gram triple \((n,l,m)\in\mathbb Z^3\) has a primitive
saturated formal full-Mukai lift \(c=(Q,P)\in\Gamma_X^{\mathrm{phys}}\)
with
\[
\Pi_X(Q,P)=(n,l,m).
\]
One may take
\[
Q=e_1+nf_1,\qquad
P=lf_1+e_2+mf_2.
\]
For this displayed lift the standard wedge torsion invariant
\[
I(Q,P):=
\gcd\{\hbox{coordinates of }Q\wedge P
\hbox{ in a }\Z\hbox{-basis of }\bigwedge^2\Lambda_S\}
\]
is equal to \(1\).
\end{lemma}

\begin{proof}
The hyperbolic-plane pairings give
\[
Q^2=2n,\qquad P^2=2m,\qquad Q\cdot P=l.
\]
Therefore \(\Pi_X(Q,P)=(n,l,m)\).  The sublattice
\(\mathbb ZQ+\mathbb ZP\subset\Lambda_S\) is primitive because the
coefficient matrix of \(Q,P\) in the ordered basis
\((e_1,f_1,e_2,f_2)\) contains the minor
\[
\det\begin{pmatrix}1&0\\0&1\end{pmatrix}=1
\]
using the \(e_1,e_2\) rows.  Hence the lift is primitive saturated.
Moreover
\[
Q\wedge P
=l\,e_1\wedge f_1+e_1\wedge e_2
+m\,e_1\wedge f_2+n\,f_1\wedge e_2
+nm\,f_1\wedge f_2 .
\]
The coefficient of \(e_1\wedge e_2\) is \(1\), so the gcd of all
coordinates of \(Q\wedge P\) is \(1\).  Thus \(I(Q,P)=1\) for the
displayed formal lift.
\end{proof}

\begin{remark}
The obstruction in the compact Hall problem is therefore not pointwise
existence of formal charge planes with a prescribed Igusa degree.
Every formal Borcherds degree has such a primitive saturated lift, and
the displayed lift is torsion-one in the wedge sense above.  This does
not prove algebraicity, effectivity, nonempty compact moduli, duality
orbit descent, or source-index descent.  The obstruction is functorial
compatibility with Hall addition and the primitive bracket.
No Nikulin orbit-uniqueness theorem, T-duality descent of protected
indices, or DVV primitive-sector formula is used here.  The lemma proves
only the displayed formal torsion-one lift.
\end{remark}

\begin{lemma}[Gram additivity defect]
\label{lem:gram-additivity-defect}
For \(c_i=(Q_i,P_i)\in\Gamma_X^{\mathrm{phys}}\),
\[
\Pi_X(c_1+c_2)=\Pi_X(c_1)+\Pi_X(c_2)+B(c_1,c_2),
\]
where
\[
B(c_1,c_2)=
\bigl(Q_1\cdot Q_2,\ Q_1\cdot P_2+Q_2\cdot P_1,\ P_1\cdot P_2\bigr)
\in\Gamma_{\mathrm{gram}}.
\]
\end{lemma}

\begin{proof}
Expand
\[
\frac{(Q_1+Q_2)^2}{2},\qquad
(Q_1+Q_2)\cdot(P_1+P_2),\qquad
\frac{(P_1+P_2)^2}{2}.
\]
The three cross terms are exactly the three components of \(B(c_1,c_2)\).
\end{proof}

\begin{lemma}[Symmetric bilinear $2$-cocycle and on-the-nose
associativity of the Gram-corrected charge product]
\label{lem:b-cocycle-central-extension}
Let \(S\) be a complex K3 surface and
\(\La_S=H^*(S,\Z)\) the Mukai lattice (even unimodular, signature
\((4,20)\)).  Let
\(\Gamma_X^{\mathrm{form}}:=\La_S\oplus\La_S\) and
\(\Gamma_X^{\mathrm{phys}}:=\Gamma_X^{\mathrm{form}}\),
\(\Gamma_{\mathrm{gram}}:=\Z^3\), and let
\(\Pi_X:\Gamma_X^{\mathrm{phys}}\to\Gamma_{\mathrm{gram}}\),
\(B:\Gamma_X^{\mathrm{phys}}\times\Gamma_X^{\mathrm{phys}}\to
\Gamma_{\mathrm{gram}}\) be as in
Definition~\textup{\ref{def:dyonic-mukai-lattice}}, namely, with
\(c=(Q,P)\),
\[
\Pi_X(Q,P)=\bigl(\tfrac{(Q,Q)}{2},\,(Q,P),\,\tfrac{(P,P)}{2}\bigr),
\qquad
B((Q,P),(Q',P'))=\bigl((Q,Q'),(Q,P')+(Q',P),(P,P')\bigr).
\]
Then:
\begin{enumerate}
\item[\textup{(i)}] \(B\) is symmetric and \(\Z\)-bilinear, and takes
integral values: \(B\in\Hom_\Z\!\bigl(S^2\Gamma_X^{\mathrm{phys}},
\Gamma_{\mathrm{gram}}\bigr)\subset
\Hom_\Z\!\bigl(\Gamma_X^{\mathrm{phys}}\otimes_\Z
\Gamma_X^{\mathrm{phys}},\Gamma_{\mathrm{gram}}\bigr)\).
\item[\textup{(ii)}] (Polarisation.)  \(B(c,c)=2\Pi_X(c)\) for every
\(c\in\Gamma_X^{\mathrm{phys}}\).
\item[\textup{(iii)}] (Symmetric Hochschild $2$-cocycle.) \(B\) is
normalised, \(B(c,0)=B(0,c)=0\), and the additive coboundary
\[
(\delta B)(a,b,c):=B(b,c)-B(a+b,c)+B(a,b+c)-B(a,b)
\]
vanishes identically.  Hence
\([B]\in H^2_{\mathrm{sym}}\!\bigl(\Gamma_X^{\mathrm{phys}};
\Gamma_{\mathrm{gram}}\bigr)\) is well defined.
\item[\textup{(iv)}] (Star-associativity on the nose.) The product on
\(\widehat\Gamma_X:=\Gamma_X^{\mathrm{phys}}\oplus\Gamma_{\mathrm{gram}}\),
\[
(c,T)\star(c',T'):=\bigl(c+c',\,T+T'+B(c,c')\bigr),
\]
is associative and commutative; the unit is \((0,0)\) and the inverse
of \((c,T)\) is \((-c,\,-T+B(c,c))=(-c,\,-T+2\Pi_X(c))\).  Thus
\((\widehat\Gamma_X,\star)\) is an abelian group, and the sequence
\[
0\longrightarrow\Gamma_{\mathrm{gram}}\xrightarrow{T\mapsto(0,T)}
\widehat\Gamma_X\xrightarrow{\mathrm{pr}_1}
\Gamma_X^{\mathrm{phys}}\longrightarrow0
\]
is a central extension of abelian groups with cocycle \(B\).
\item[\textup{(v)}] (Normal-ordered Gram map.)  The map
\[
\overline\Pi_X:\widehat\Gamma_X\longrightarrow\Gamma_{\mathrm{gram}},
\qquad
\overline\Pi_X(c,T)=\Pi_X(c)-T,
\]
is a homomorphism from \((\widehat\Gamma_X,\star)\) to the additive
group \(\Gamma_{\mathrm{gram}}\).
\item[\textup{(vi)}] (Splitting; \([B]=0\).)  The Gram-shadow section
\(s:\Gamma_X^{\mathrm{phys}}\to\widehat\Gamma_X\), \(s(c):=(c,\Pi_X(c))\),
is a homomorphism for \(\star\); equivalently
\(B=-\delta\Pi_X\) in
\(B^2_{\mathrm{sym}}(\Gamma_X^{\mathrm{phys}};\Gamma_{\mathrm{gram}})\),
where \((\delta\Pi_X)(c,c')=\Pi_X(c)+\Pi_X(c')-\Pi_X(c+c')\).  In particular
\([B]=0\), the extension is split as an extension of abelian groups, and
\((c,T)\mapsto(c,T-\Pi_X(c))\) is an isomorphism
\(\widehat\Gamma_X\xrightarrow{\sim}
\Gamma_X^{\mathrm{phys}}\oplus\Gamma_{\mathrm{gram}}\) of abelian
groups carrying \(\star\) to componentwise addition.
\item[\textup{(vii)}] (Quadratic obstruction.)  \(B\) is not the
coboundary of any \emph{linear} \(1\)-cochain
\(L:\Gamma_X^{\mathrm{phys}}\to\Gamma_{\mathrm{gram}}\): if
\(B(c,c')=L(c)+L(c')-L(c+c')\) for an additive \(L\), then setting
\(c'=c\) and using \textup{(ii)} gives \(2\Pi_X(c)=2L(c)-L(2c)=0\),
i.e.\ \(\Pi_X\equiv 0\), contradiction.  Trivialising \([B]\) requires the
quadratic refinement \(\Pi_X\); the defect is a polarization-correction
class, not a separate Heisenberg extension datum.
\end{enumerate}
\end{lemma}

\begin{proof}
Write \(c=(Q,P)\), \(c'=(Q',P')\), \(c''=(Q'',P'')\) with
\(Q,Q',Q'',P,P',P''\in\La_S\), and abbreviate
\((\,\cdot\,,\,\cdot\,):\La_S\times\La_S\to\Z\) by juxtaposition,
\(QQ'=(Q,Q')\), so that
\(B(c,c')=(QQ',\,QP'+Q'P,\,PP')\).

\smallskip\emph{(i) Symmetry, bilinearity, integrality.}
The components \(QQ'\) and \(PP'\) are the symmetric Mukai pairing on
\(\La_S\), so each is symmetric and \(\Z\)-bilinear.  The middle
component is the polarisation
\((c,c')\mapsto QP'+Q'P\) of the symmetric biadditive form
\((c,c')\mapsto QP'+Q'P\); swapping
\((Q,P)\leftrightarrow(Q',P')\) returns \(Q'P+QP'=QP'+Q'P\), so it is
symmetric, and \(\Z\)-bilinear in each slot by bilinearity of
\((\,\cdot\,,\,\cdot\,)\).  Integrality of every component follows from
the unimodular even structure on \(\La_S\).

\smallskip\emph{(ii) Polarisation.}
Set \(c'=c\): the cross terms reduce to
\(QQ\), \(QP+QP=2QP\), \(PP\), so
\(B(c,c)=(Q^2,2QP,P^2)=2\Pi_X(c)\).

\smallskip\emph{(iii) Cocycle.}
Bilinearity gives normalisation \(B(c,0)=B(0,c)=0\) immediately.  For
the cocycle identity, observe that any symmetric \(\Z\)-bilinear form
\(\beta:G\times G\to A\) on an abelian group \(G\) with values in a
trivial \(G\)-module \(A\) satisfies, by bilinearity in the first slot,
\[
\beta(a+b,c)=\beta(a,c)+\beta(b,c),
\qquad
\beta(a,b+c)=\beta(a,b)+\beta(a,c).
\]
Substituting into
\((\delta\beta)(a,b,c)=\beta(b,c)-\beta(a+b,c)+\beta(a,b+c)-\beta(a,b)\),
\[
(\delta\beta)(a,b,c)=
\beta(b,c)-\beta(a,c)-\beta(b,c)+\beta(a,b)+\beta(a,c)-\beta(a,b)=0.
\]
Applied componentwise to \(B\), this yields \(\delta B=0\).  Hence
\(B\in Z^2_{\mathrm{sym}}(\Gamma_X^{\mathrm{phys}};\Gamma_{\mathrm{gram}})\).

\smallskip\emph{(iv) Associativity, identity, inverse.}
Compute the two bracketings of
\((c,T)\star(c',T')\star(c'',T'')\):
\begin{align*}
\bigl((c,T)\star(c',T')\bigr)\star(c'',T'')
&=\bigl(c+c'+c'',\,T+T'+T''+B(c,c')+B(c+c',c'')\bigr),\\
(c,T)\star\bigl((c',T')\star(c'',T'')\bigr)
&=\bigl(c+c'+c'',\,T+T'+T''+B(c',c'')+B(c,c'+c'')\bigr).
\end{align*}
The associator is the difference of the central components,
\(\mathrm{Ass}(c,c',c'')=B(c,c')+B(c+c',c'')-B(c',c'')-B(c,c'+c'')\),
which equals \(-(\delta B)(c,c',c'')=0\) by~(iii); equivalently, it
vanishes by bilinearity of \(B\).  Commutativity follows from symmetry
of \(B\).  The identity computation
\((c,T)\star(0,0)=(c,T+B(c,0))=(c,T)\) and the inverse computation
\((c,T)\star(-c,-T+B(c,c))=(0,B(c,c)-B(c,c))=(0,0)\) (using
\(B(c,-c)=-B(c,c)\) by bilinearity) finish the abelian-group structure.
That \(B\) is the cocycle of the displayed central extension is direct
from the formula for \(\star\) and normalisation \(B(c,0)=B(0,c)=0\).

\smallskip\emph{(v) Normal-ordered Gram map.}
Using Lemma~\ref{lem:gram-additivity-defect},
\begin{align*}
\overline\Pi_X((c,T)\star(c',T'))
&=\overline\Pi_X(c+c',T+T'+B(c,c'))\\
&=\Pi_X(c+c')-T-T'-B(c,c')\\
&=\Pi_X(c)+\Pi_X(c')-T-T'\\
&=\overline\Pi_X(c,T)+\overline\Pi_X(c',T').
\end{align*}
Thus \(\overline\Pi_X\) is additive.

\smallskip\emph{(vi) Splitting.}
By Lemma~\ref{lem:gram-additivity-defect},
\(\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c')\), so
\[
s(c)\star s(c')
=(c+c',\,\Pi_X(c)+\Pi_X(c')+B(c,c'))=(c+c',\,\Pi_X(c+c'))=s(c+c').
\]
Thus \(s\) is a homomorphism, and
\(B(c,c')=\Pi_X(c+c')-\Pi_X(c)-\Pi_X(c')=-(\delta\Pi_X)(c,c')\) shows
\(B=-\delta\Pi_X\), so \([B]=0\).  The change of variables
\((c,T)\mapsto(c,T-\Pi_X(c))\) is bijective on the underlying set with
inverse \((c,T)\mapsto(c,T+\Pi_X(c))\), and carries
\(\star\) to componentwise addition:
\[
(c,T-\Pi_X(c))+(c',T'-\Pi_X(c'))
=(c+c',\,T+T'-\Pi_X(c)-\Pi_X(c'))
=(c+c',\,(T+T'+B(c,c'))-\Pi_X(c+c')),
\]
matching the change of variables applied to
\((c+c',T+T'+B(c,c'))=(c,T)\star(c',T')\).

\smallskip\emph{(vii) Quadratic obstruction.}
Suppose \(B=\delta L\) for some additive
\(L:\Gamma_X^{\mathrm{phys}}\to\Gamma_{\mathrm{gram}}\), i.e.\
\(B(c,c')=L(c)+L(c')-L(c+c')\).  Setting \(c'=c\),
\(B(c,c)=2L(c)-L(2c)\); but \(L\) additive gives \(L(2c)=2L(c)\), so
\(B(c,c)=0\), contradicting \(B(c,c)=2\Pi_X(c)\) for any
\(c=(Q,P)\) with \((Q,Q),(Q,P),(P,P)\) not all zero.  Hence no linear
trivialisation exists; the quadratic primitive \(\Pi_X\) is necessary.

\smallskip\emph{Scope of the chain-level claim.}
Clauses (i)--(vii) prove an ordinary set-level and \(H^0\)-level
polarization correction.  They do not prove that the protected Hall
chain complex has no higher associators.  In particular no acyclicity
of a bar complex \(B_*(\widehat\Gamma_X)\) is asserted: the bar
construction of a discrete abelian group records group homology, and
cannot be used to kill Stasheff coherences.  Chain-level strictness of
the Hall product therefore remains part of the orientation/coherence
hypotheses in Theorem~\ref{thm:ptvv-joyce-pi-descent}; what this lemma
supplies is only the explicit quadratic polarization correction
\(B=-\delta\Pi_X\) and the split degree monoid on which a later
cocycle-corrected descent can act.
\end{proof}

\begin{remark}
\label{rem:b-cocycle-status}
The preceding lemma records the additive degree correction.  It proves that
the Gram defect is the coboundary of the quadratic refinement
\(\Pi_X\), and that the corrected degree monoid is split.  Equivalently,
the cohomology class \([B]\in H^2_{\mathrm{sym}}(\Gamma_X^{\mathrm{phys}};
\Gamma_{\mathrm{gram}})\) is nontrivial as a class in linear cochains
because \(\Pi_X\) is genuinely quadratic, not linear; so \(B\) is not the
symmetric coboundary of any linear map
\(\Gamma_X^{\mathrm{phys}}\to\Gamma_{\mathrm{gram}}\).  The class becomes
trivial only after passing to the quadratic refinement \(\Pi_X\), which is
exactly the polarization \(\Pi_X\to-\delta\Pi_X=B\) recorded above.  The
lemma does not
strictify the Hall chain complex.  A chain-level Hall product still
requires the multiplicative orientation, cyclic equivariance, and
associator data listed in
Theorem~\ref{thm:ptvv-joyce-pi-descent}; absent those data the lift is
only \(A_\infty\)-coherent, and the obstruction is tracked by the
supplied cochain \(\Theta\), not by acyclicity of a group bar complex.
\end{remark}

\begin{definition}[Normal-ordered Gram-corrected charge extension]
\label{def:gram-corrected-charge-extension}
Set
\[
\widehat\Gamma_X:=\Gamma_X^{\mathrm{phys}}\oplus\Gamma_{\mathrm{gram}}.
\]
For \(c,c'\in\Gamma_X^{\mathrm{phys}}\) and
\(T,T'\in\Gamma_{\mathrm{gram}}\), define
\[
(c,T)\star(c',T')
:=(c+c',\,T+T'+B(c,c')).
\]
The section
\[
s:\Gamma_X^{\mathrm{phys}}\longrightarrow\widehat\Gamma_X,\qquad
s(c)=(c,\Pi_X(c))
\]
is additive for \(\star\).  The normal-ordered Gram map is
\[
\overline\Pi_X:\widehat\Gamma_X\longrightarrow\Gamma_{\mathrm{gram}},
\qquad
\overline\Pi_X(c,T)=\Pi_X(c)-T.
\]
Thus the compact Hall object, if constructed, is graded upstairs by
\(\Gamma_X^{\mathrm{phys}}\), or by the refinement
\(\widehat\Gamma_X\) after the normal-ordering counterterm is recorded.
The \(\Gamma_{\mathrm{gram}}\)-graded Igusa object is obtained only
after normal-ordered Gram pushforward along \(\overline\Pi_X\), or by a
chain-level categorification of the same subtraction.
\end{definition}

\begin{proof}
By Lemma~\ref{lem:b-cocycle-central-extension}(i),(iii),(iv), \(\star\) is
associative and commutative, the identity is \((0,0)\), and the inverse
of \((c,T)\) is \((-c,-T+B(c,c))\); the section \(s\) is the splitting
of clause~(vi).  Clause~(v) of the same lemma proves that
\(\overline\Pi_X\) is a homomorphism.
\end{proof}

\begin{theorem}[Strict fixed-lift raw Gram descent cannot realize the
type-II real-root strings]
\label{thm:raw-gram-descent-no-go}
Let
\[
P=\bigoplus_{c\in\Gamma_X^{\mathrm{phys}}}P_c
\]
be a \(\Gamma_X^{\mathrm{phys}}\)-graded Lie superalgebra with
\[
[P_c,P_{c'}]\subset P_{c+c'}.
\]
Suppose a strict fixed-lift raw pushforward along the quadratic map
\(\Pi_X:\Gamma_X^{\mathrm{phys}}\to\Gamma_{\mathrm{gram}}\) were a
\(\Gamma_{\mathrm{gram}}\)-graded Lie superalgebra structure on the
displayed bracket channels of chosen charge lifts.  Then every non-zero
bracket channel \([P_c,P_{c'}]\) contributing to that strict raw
pushforward must satisfy
\[
B(c,c')=0.
\]
For the type-II real simple roots of the Gritsenko--Nikulin algebra,
this condition is incompatible with the non-zero second real-root
strings \(2\delta_i+\delta_j\), \(i\ne j\).  Hence these type-II
real-root brackets cannot be obtained by strict fixed-lift raw
\(\Pi_X\)-descent.  They require the
normal-ordered extension
\(\widehat\Gamma_X=\Gamma_X^{\mathrm{phys}}\oplus_B\Gamma_{\mathrm{gram}}\)
and the homomorphism \(\overline\Pi_X(c,T)=\Pi_X(c)-T\).
\end{theorem}

\begin{proof}
If the raw pushforward is \(\Gamma_{\mathrm{gram}}\)-graded, then a
non-zero bracket of classes of raw Gram degrees \(\Pi_X(c)\) and
\(\Pi_X(c')\) must land in raw Gram degree
\(\Pi_X(c)+\Pi_X(c')\).  But the upstairs bracket lands in physical
degree \(c+c'\), whose raw Gram shadow is
\[
\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c').
\]
Thus every non-zero bracket channel visible in a raw pushforward must
have \(B(c,c')=0\).

Let \(c_i,c_j\) be physical lifts of two distinct type-II real simple
root degrees \(\gamma_i,\gamma_j\), so
\[
\Pi_X(c_i)=\gamma_i,\qquad \Pi_X(c_j)=\gamma_j,
\qquad \gamma_i\ne0.
\]
The Gritsenko--Nikulin real simple roots have Cartan matrix
\[
\begin{pmatrix}
2&-2&-2\\
-2&2&-2\\
-2&-2&2
\end{pmatrix}.
\]
The real-root string through distinct simple roots contains non-zero
brackets in degrees \(\gamma_i+\gamma_j\) and
\(2\gamma_i+\gamma_j\); this is the low-degree real-root information
recorded in Proposition~\ref{prop:low-degree-denominator-brackets}.
The first non-zero bracket would force
\[
B(c_i,c_j)=0.
\]
The second non-zero bracket is obtained by bracketing once more with
the \(c_i\)-degree generator, so raw Gram additivity would force
\[
B(c_i,c_i+c_j)=0.
\]
By bilinearity and polarization,
\[
B(c_i,c_i+c_j)=B(c_i,c_i)+B(c_i,c_j)
=2\Pi_X(c_i)+0=2\gamma_i.
\]
Since \(\gamma_i\ne0\) in the torsion-free lattice
\(\Gamma_{\mathrm{gram}}\), this is non-zero.  Contradiction.

The contradiction uses the fixed chosen lifts \(c_i,c_j\) and the raw
quadratic map \(\Pi_X\).  It does not exclude special isolated
\(B\)-isotropic bracket channels, and it does not decide a mixed-lift
fibre-summed raw construction in which several lifts of a single Gram
degree are combined before taking brackets.  It excludes the strict
homogeneous fixed-lift raw pushforward needed by this proof.  The
normal-ordered extension removes exactly this obstruction because
\(\overline\Pi_X\) is additive on \(\widehat\Gamma_X\).
\end{proof}

\begin{remark}
The remaining raw problem is the fibre-summed version: one may try to
sum several charge lifts over a fixed Gram degree before bracketing.
Theorem~\ref{thm:raw-gram-descent-no-go} neither proves nor disproves
such a construction.
\end{remark}

\begin{remark}[Normal-ordered primitive recognition target]
The interface with the denominator algebra is therefore not the raw
map \(\Pi_X\).  It is the corrected route
\[
\Gamma_X^{\mathrm{phys}}
\longrightarrow
\widehat\Gamma_X
\xrightarrow{\ \overline\Pi_X\ }
\Gamma_{\mathrm{gram}}
\xrightarrow{\ \alpha\ }
\La^{2,1}_{II}.
\]
At chain level this becomes the descent
\(\overline\Pi_{X,*}^{\Theta}\) of
Open Problem~\ref{op:pi-descent-of-bracket}.  The primitive recognition
problem is to construct a protected primitive Hall algebra whose
normal-ordered descended bracket is the Borcherds--Kac bracket of
\(\mathfrak g_{\Delta_5}\).  Raw Gram pushforward is not an admissible
recognition target.
\end{remark}

\begin{definition}[Gram-index pairing]
For
$$\gamma=(n,l,m),\qquad \gamma'=(n',l',m'),$$
define
$$
\langle\gamma,\gamma'\rangle_{\mathrm{ind}}
=2(nm'+n'm)-ll'.
$$
The Gram discriminant is
$$
\Delta_{\mathrm{gram}}(\gamma)
=\langle\gamma,\gamma\rangle_{\mathrm{ind}}
=4nm-l^2.
$$
\end{definition}

\begin{remark}[Chamber transport]
The pairing \(\langle\ ,\ \rangle_{\mathrm{ind}}\) is the pairing on
Gram invariants.  The order on \(\Gamma_{\mathrm{eff}}\) is a Fock
polarization at one cusp.  A duality element transports this
polarization to the corresponding product chamber at the transported
cusp.
\end{remark}

\part{Denominator algebra and compact Dirac--Igusa realization}

\section{The exterior-square model of the automorphic group}

The form \(\Delta_5\) is an automorphic form on the Siegel space.  The
physical U-duality interpretation of the same arithmetic group is
external input from the \(K3\times E\) compactification; it is not needed
for the lattice calculation below.  The calculation records the
first-principles bridge from the Siegel variables to the type-IV
Lorentzian lattice on which the denominator algebra is written.
\(\Sp_4(\Z)\) is the arithmetic symmetry of the genus-two chemical
potential and of the invariant Gram plane on \(\Lambda^{3,2}\); it is not
asserted to be the full T-duality or U-duality group of the \(K3\times
T^2\) compactification, which is larger.

$$\La^4=\Z e_1\oplus\Z e_2\oplus\Z e_3\oplus\Z e_4.$$
$$g\in\SL_4(\Z):\qquad
\wedge^2g:\wedge^2\La^4\longrightarrow\wedge^2\La^4.$$
$$u\wedge v=(u,v)e_1\wedge e_2\wedge e_3\wedge e_4.$$
$$\bigl(\wedge^2\La^4,(\ ,\ )\bigr)\simeq \mathrm{II}_{3,3}.$$

Fix
$$q_0=e_1\wedge e_3+e_2\wedge e_4.$$
For $x,y\in\La^4$, define
$$-x\wedge y\wedge q_0
=B_{q_0}(x,y)e_1\wedge e_2\wedge e_3\wedge e_4.$$
$$\{g\in \SL(\La^4)\mid(\wedge^2g)q_0=q_0\}\simeq\Sp_4(\Z).$$

Set
$$\La^{3,2}=q_0^\perp\subset\wedge^2\La^4.$$
$$
f_1=e_1\wedge e_2,\quad
f_2=e_2\wedge e_3,\quad
f_3=e_1\wedge e_3-e_2\wedge e_4,\quad
f_{-2}=e_4\wedge e_1,\quad
f_{-1}=e_4\wedge e_3.
$$
$$(f_1,f_{-1})=(f_2,f_{-2})=-1,\qquad (f_3,f_3)=2.$$
$$\La^{3,2}\simeq\HypPlan\oplus\HypPlan\oplus[2],\qquad
\HypPlan=\begin{pmatrix}0&-1\\-1&0\end{pmatrix}.$$

$$\Hpl^{\IV}=
\{Z\in\Proj(\La^{3,2}\otimes\C)\mid (Z,Z)=0,\ (Z,\overline Z)<0\}.$$
$$\Hpl_+^{\IV}=
\{{}^t(z_2^2-z_1z_3,\ z_3,\ z_2,\ z_1,\ 1)z_0\in\Hpl^{\IV}
\mid \Imag z_1>0\}.$$
Writing $y_i=\Imag z_i$,
$$ (Z,\overline Z)<0\quad\Longleftrightarrow\quad y_1y_3-y_2^2>0.$$
$$\Hpl_+^{\IV}\simeq
\left\{\begin{pmatrix}z_1&z_2\\z_2&z_3\end{pmatrix}\in\Hpl_2\right\}.$$

Let $\Orth_{\R}(\La^{3,2})_+$ be the index-two subgroup preserving
$\Hpl_+^{\IV}$.  Its kernel on $\Hpl_+^{\IV}$ is $\{\pm\Id_5\}$, and
$$\Orth_{\R}(\La^{3,2})_+=\{\pm\Id_5\}\SO_{\R}(\La^{3,2})_+,$$
where $\SO_{\R}(\La^{3,2})_+$ has real spin-norm $1$.  Put
$$\Orth(\La^{3,2})_+ = \Orth_{\R}(\La^{3,2})_+ \cap \Orth(\La^{3,2})$$
and
$$\SO(\La^{3,2})_+=\SO_{\R}(\La^{3,2})_+\cap\Orth(\La^{3,2}).$$

$$M=\begin{pmatrix}m_1&m_2\\m_2&m_3\end{pmatrix},$$
$$\wedge^2(g_0)
=\wedge^2\!\left(\begin{pmatrix}0 & \Id_2 \\ -\Id_2 & 0\end{pmatrix}\right)
= \begin{pmatrix}
0 & 0 & 0 & 0 & -1\\
0 & 0 & 0 & -1 & 0\\
0 & 0 & 1 & 0 & 0\\
0 & -1 & 0 & 0 & 0\\
-1 & 0 & 0 & 0 & 0
\end{pmatrix},$$
$$\wedge^2(g_M)
=\wedge^2\!\left(\begin{pmatrix}\Id_2 & M\\ 0 & \Id_2\end{pmatrix}\right)
= \begin{pmatrix}1 & -m_1 & 2m_2 & -m_3 & m_2^2 - m_1 m_3\\
0 & 1 & 0 & 0 & m_3\\
0 & 0 & 1 & 0 & m_2\\
0 & 0 & 0 & 1 & m_1\\
0 & 0 & 0 & 0 & 1\end{pmatrix},$$
$$\wedge^2(g_A)
=\wedge^2\!\left(\begin{pmatrix}{}^tA^{-1} & 0\\0 & A\end{pmatrix}\right)
= \det(A)\begin{pmatrix}1 & 0 & 0 & 0 & 0\\
0 & a_1^2 & -2a_1a_2 & a_2^2 & 0\\
0 & -a_1a_3 & a_1a_4 + a_2a_3 & -a_2a_4 & 0\\
0 & a_3^2 & -2a_3a_4 & a_4^2 & 0\\
0 & 0 & 0 & 0 & 1\end{pmatrix}$$

\begin{lemma}
The exterior-square representation is
$$\wedge^2 :
\Sp_4(\Z)/\{\pm \Id_4\} \rightarrow \SO_+(\La^{3,2}) \simeq
\Orth(\La^{3,2})_+/\{\pm\Id_5\}.$$
For every $g\in\Sp_4(\Z)$,

  \[ \begin{tikzcd}
\Hpl_2 \arrow{r}{} \arrow[swap]{d}{} & \Hpl_2 \arrow{d}{} \\%
\Hpl_+^{\IV} \arrow{r}{g \wedge g}& \Hpl_+^{\IV}
\end{tikzcd}
\]
\end{lemma}

\begin{proof}
The Pfaffian pairing is preserved by $\wedge^2\SL_4$.  The subgroup
fixing
$$q_0=e_1\wedge e_3+e_2\wedge e_4$$
is the group preserving the alternating form $B_{q_0}$, namely
$\Sp_4(\Z)$.  Its action preserves $q_0^\perp=\La^{3,2}$ and the displayed
component of the type-$\IV$ domain.  The kernel on $q_0^\perp$ is
$\{\pm\Id_4\}$.  The exceptional isomorphism
$\PSp_4(\R)\simeq \SO_{\R}(3,2)_+$ identifies the image with
$\SO_+(\La^{3,2})$.  The displayed matrices are the integral generators
on both sides.  Substitution of
$${}^t(z_2^2-z_1z_3,z_3,z_2,z_1,1)z_0$$
into the two actions produces the commutative square.
\end{proof}

\begin{definition}[Automorphic duality datum]
$$G_{\mathrm{aut}}=\PSp_4(\Z)\simeq\SO_+(\La^{3,2}).$$
The virtual determinant \(\mathcal D_X=\Delta_5\) is not an invariant
scalar function on
$\Hpl_2$.  It is a section of the automorphic line
$$\mathcal L^5\otimes\nu_{\Delta_5}$$
with transformation law
$$
\Delta_5(g\cdot Z)
=\nu_{\Delta_5}(g)\det(CZ+D)^5\Delta_5(Z),
\qquad
g=\begin{pmatrix}A&B\\ C&D\end{pmatrix}\in\Sp_4(\Z).
$$
The scalar square is a section of $\mathcal L^{10}$:
$$
\Delta_5^2(g\cdot Z)=\det(CZ+D)^{10}\Delta_5^2(Z).
$$
For every scalar-square branch,
$$
Z^X_{\square}(g\cdot Z)
=\det(CZ+D)^{-10}Z^X_{\square}(Z).
$$
\end{definition}

\section{The Weyl chamber and the Weyl vector}

Fix the primitive hyperbolic sublattice
$$\La^{2,1} = \HypPlan \oplus [2] \simeq \Z f_2 \oplus \Z f_3 \oplus \Z
f_{-2} \subset \La^{3,2}$$
and its type-II sublattice
$$
\La^{2,1}_{II}=
\{mf_2+lf_3+nf_{-2}\in\La^{2,1}\mid m\equiv n\equiv0\pmod2\}.
$$

Change polarization on the same Gram-index lattice:
$$
\Gamma_{\mathrm{ind}}\xrightarrow{\ \alpha\ }\La^{2,1}_{II},\qquad
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}.
$$
The cusp polarization gives the Fock determinant.  The denominator
polarization gives the Borcherds chamber.

Extend $\phi\in\Orth(\La^{2,1})$ by the identity on
$(\La^{2,1})^\perp$:
$$\Orth(\La^{2,1})\hookrightarrow\Orth(\La^{3,2}).$$
For the component-preserving subgroup attached to the positive cone
below,
$$\Delta_5\in M_5(\Orth(\La^{2,1})_+,\nu_{\Delta_5}).$$

For a primitive element $\alpha \in \La^{2,1}$ satisfying
$(\alpha,\alpha)>0$ and
$$(\alpha,\alpha)\mid 2(\La^{2,1},\alpha),$$
Kac reflection \cite{KAC:1}:
$$s_{\alpha}:x\mapsto x-2\frac{(x,\alpha)}{(\alpha,\alpha)}\alpha.$$
$$s_{\alpha}(\alpha)=-\alpha,\qquad
s_{\alpha}|_{\alpha^\perp}=\Id.$$
For $(\alpha,\alpha)=2$:
$$s_{\alpha}: x \mapsto
x - (x,\alpha)\alpha.$$

\begin{lemma}
Let $(\alpha,\alpha)=2$.  For
$$\delta_1=2f_2-f_3,\qquad
\delta_2=2f_{-2}-f_3,\qquad
\delta_3=f_3,$$
\cite[Theorem 2.1 and Section 4]{GN}; equivalently \cite[Section 5.1.1, case (t=1,II,0)]{GNII}.
$$\Delta_5(s_{\alpha}Z) = - \Delta_5(Z)$$
when $\alpha\in\{\delta_1,\delta_2,\delta_3\}$.  For
$$\alpha\in\{f_{-2}-f_2,\ f_2-f_3,\ f_2+f_3\},$$
$$\Delta_5(s_{\alpha}Z) = \Delta_5(Z)$$
\end{lemma}
\begin{proof}
Let
$$\overline U=\wedge^2\begin{pmatrix}{}^tU^{-1}&0\\0&U\end{pmatrix},
\qquad U\in\GL_2(\Z).$$
Required reflections:
$$s_{f_{-2}-f_2}=-\overline{\begin{pmatrix}0&1\\1&0\end{pmatrix}},
\qquad
s_{f_3}=-\overline{\begin{pmatrix}1&0\\0&-1\end{pmatrix}},
\qquad
s_{f_2-f_3}=-\overline{\begin{pmatrix}1&-1\\0&-1\end{pmatrix}}.$$
Maass's character has value $-1$ on
$s_{\delta_i}$ and $+1$ on the three other reflection classes.
\end{proof}

\noindent The time-like cone is
$$\Cone(\La^{2,1}) = \{ x \in \La^{2,1}
\otimes \R | (x,x) < 0\}.$$
Let $\Cone(\La^{2,1})_+$ be the component for which
$$\Omega(\Cone(\La^{2,1})_+):=
\La^{2,1}\otimes\R+i\Cone(\La^{2,1})_+\subset\Hpl^{\IV}_+.$$
For
$$z=z_3f_2+z_2f_3+z_1f_{-2}\in\Omega(\Cone(\La^{2,1})_+),$$
the type $\IV$ point is
$$Z={}^t(z_2^2-z_1z_3,\ z_3,\ z_2,\ z_1,\ 1)z_0.$$
Let $\Orth(\La^{2,1})_+$ be the index-two subgroup fixing
$\Cone(\La^{2,1})_+$.  It acts discretely on
$$\Cone(\La^{2,1})_+/\R_{>0}.$$

For $(\alpha,\alpha)>0$,
$$\Hpl_{\alpha}=
\{\R_{>0}x\in\Cone(\La^{2,1})_+/\R_{>0}\mid (x,\alpha)=0\},$$
and
$$\Hpl_{\alpha,+}=
\{\R_{>0}x\in\Cone(\La^{2,1})_+/\R_{>0}\mid (x,\alpha)\leq0\}.$$
Let $W(\La^{2,1})$ be the subgroup generated by these positive-norm
reflections:
$$W(\La^{2,1})\subset\Orth(\La^{2,1})_+.$$


Nikulin's theorem for $\HypPlan\oplus[2]$ \cite{NIKULIN}:
$$\Orth(\La^{2,1})_+=W^{(2)}(\La^{2,1}),$$
where $W^{(2)}$ is generated by reflections in square-$2$ vectors.
For $k>0$ put
$$\Delta^{(k)}(\La^{2,1})=
\{\delta\in\La^{2,1}\mid \delta\ \text{primitive},\
(\delta,\delta)=k,\ s_\delta\in\Orth(\La^{2,1})\}.$$
Each $\delta\in\Delta^{(2)}(\La^{2,1})$ has one of two divisibilities:
\begin{itemize}
\item Type I: $(\delta, \La^{2,1}) = \Z$
\item Type II: $(\delta, \La^{2,1}) = 2\Z$
\end{itemize}

The type sublattices are
$$\La^{2,1}_I=
\{mf_2+lf_3+nf_{-2}\in\La^{2,1}\mid m+l+n\equiv0\pmod2\},$$
and the already defined \(\La^{2,1}_{II}\).
Type I roots lie in $\La^{2,1}_I$; type II roots lie in
$\La^{2,1}_{II}$.  The reflection subgroups are normal, with indices
$$[W^{(2)}(\La^{2,1}):W^{(2)}(\La^{2,1}_I)]=2,\qquad
[W^{(2)}(\La^{2,1}):W^{(2)}(\La^{2,1}_{II})]=6.$$

The chambers are
$$\Poly'=\bigcap_{\delta\in\Poly'_{prim}}\Hpl_{\delta,+},
\qquad \Poly'\in\{\Poly,\Poly_I,\Poly_{II}\},$$
with walls
$$\Poly_{prim}=\{f_2-f_3,\ f_{-2}-f_2,\ f_3\},$$
$$\Poly_{I,prim}=\{f_2-f_3,\ f_{-2}-f_2,\ f_2+f_3\},$$
$$\Poly_{II,prim}=\{\delta_1,\delta_2,\delta_3\}.$$
For
$$\Aut(\Poly')=\{g\in\Orth(\La^{2,1})_+\mid g\Poly'=\Poly'\},$$
$$\Aut(\Poly)=1,\qquad
\Aut(\Poly_I)=\langle s_{f_3}\rangle,\qquad
\Aut(\Poly_{II})\simeq S_3,$$
with $\Aut(\Poly_{II})$ generated by
$s_{f_2-f_3}$ and $s_{f_{-2}-f_2}$.  The chamber decomposition is
$$\Orth(\La^{2,1})_+
\simeq W^{(2)}(\La^{2,1})
\simeq W^{(2)}(\La^{2,1}_I)\rtimes\Aut(\Poly_I)
\simeq W^{(2)}(\La^{2,1}_{II})\rtimes\Aut(\Poly_{II}).$$

\begin{lemma}[Multiplier restriction]
\label{lem:maass-multiplier-restriction}
\begin{itemize}
  \item for $w \in W^{(2)}(\La^{2,1}_I)$ and $a \in \Aut(\Poly_{I})$,
  $$\Delta_5(w \cdot a Z) = \det(a) \Delta_5(Z)$$
  \item for $w \in W^{(2)}(\La^{2,1}_{II})$ and $a \in \Aut(\Poly_{II})$,
  $$\Delta_5(w \cdot a Z) = \det(w) \Delta_5(Z)$$
\end{itemize}
Equivalently,
\[
\nu_{\Delta_5}(s_{\delta_i})=-1,\qquad i=1,2,3,
\]
and
\[
\nu_{\Delta_5}(s_{f_{-2}-f_2})
=\nu_{\Delta_5}(s_{f_2-f_3})
=\nu_{\Delta_5}(s_{f_2+f_3})=+1.
\]

\end{lemma}
\begin{proof}
Maass's multiplier formula for the product of the ten even theta
constants is recorded in \cite[(1.3)--(1.5)]{GN}, citing
\cite{MAASS:1}.  Under the exterior-square identification
\(\PSp_4(\Z)\simeq\SO_+(\La^{3,2})\), Gritsenko--Nikulin compute the
reflection values in \cite[Proposition~2.1]{GN} and the type-II chamber
restriction in \cite[Proposition~2.2]{GN}: it is \(-1\) on the three
type-II simple reflections and trivial on the three
\(\Aut(\Poly_{II})\)-reflections.  This is a character computation, not
a normalization computation: multiplying \(\Delta_5\) by any nonzero
scalar leaves the displayed values unchanged.  Thus the six generator
values are
exactly
\[
\nu_{\Delta_5}(s_{\delta_i})=-1,\qquad
\nu_{\Delta_5}(s_{f_{-2}-f_2})
=\nu_{\Delta_5}(s_{f_2-f_3})
=\nu_{\Delta_5}(s_{f_2+f_3})=+1.
\]
For the type-II chamber decomposition
\[
W^{(2)}(\La^{2,1}_{II})\rtimes\Aut(\Poly_{II}),
\]
the first line says that the restriction to \(W^{(2)}(\La^{2,1}_{II})\)
is the determinant character, while the second says that the
\(\Aut(\Poly_{II})\)-factor acts trivially.  The type-I statement is the
parallel restriction in the decomposition
\[
W^{(2)}(\La^{2,1}_I)\rtimes\Aut(\Poly_I),
\]
where the nontrivial chamber automorphism contributes \(\det(a)\).
\end{proof}

Set
$$\Delta(\La^{2,1}_{II})_+
= \R_{\geq 0} \delta_1 + \R_{\geq 0} \delta_2
+ \R_{\geq 0} \delta_3$$
and
$$\Delta(\La^{2,1}_{II})_+^* = \{ x \in \La^{2,1} \otimes \R | (x,
\delta_i) \leq 0 \}.$$
For the finite-volume chamber $\Poly_{II}$, the dual cone obeys
$$\Delta(\La^{2,1}_{II})_+^* \subset
\overline{\Cone(\La^{2,1})_+} \subset  \Delta(\La^{2,1}_{II})_+.$$

The Weyl vector is determined by
$$ (\rho,\delta_i)=-\frac{(\delta_i,\delta_i)}{2}=-1,\qquad i=1,2,3.$$
$$(\delta_i,\delta_j) =
\begin{pmatrix}2 & -2 & -2\\-2 & 2 & -2\\-2 & -2 & 2\end{pmatrix}.$$
$$\rho = \frac{1}{2}\delta_1 + \frac{1}{2}\delta_2 + \frac{1}{2}\delta_3 = f_2 - \frac{1}{2}f_3 + f_{-2}.$$

Also
$$\rho \in
\Cone(\La^{2,1})_+ = \Cone(\La^{2,1}_{II})_+.$$

Fix
$$z = z_1 f_{-2} + z_2 f_3 + z_3 f_2
\in \La^{2,1} \otimes \R + i\Cone(\La^{2,1})_+
= \La^{2,1}_{II} \otimes \R + i\Cone(\La^{2,1}_{II})_+.$$
The dual lattice is
$$(\La^{2,1}_{II})^* = \Z \frac{1}{2} f_2 + \Z \frac{1}{2} f_3 + \Z \frac{1}{2} f_{-2} = \frac{1}{2}\La^{2,1}.$$

\begin{definition}[Gram-index degrees in the Weyl chamber]
\label{def:gram-index-degrees-weyl-chamber}
For $\gamma=(n,l,m)\in\Gamma_{\mathrm{ind}}$ set
$$\alpha(\gamma)=\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}
\in\La^{2,1}_{II}.$$
With
$$z=z_1f_{-2}+z_2f_3+z_3f_2,$$
the character of the Gram-index degree is
$$x^\gamma=q^nr^ls^m=\exp(-\pi i(\alpha(\gamma),z)).$$
For $\gamma'=(n',l',m')$,
$$
(\alpha(\gamma),\alpha(\gamma'))
=-2\langle\gamma,\gamma'\rangle_{\mathrm{ind}},
\qquad
(\alpha(\gamma),\alpha(\gamma))=-2(4nm-l^2).
$$
Thus the Borcherds degree is the Lorentzian image of the Gram-index
grading.  The Weyl chamber and real walls are part of the
Gritsenko--Nikulin/Nikulin root datum.  The cusp polarization fixed in
Section \ref{sec:duality-principle} selects the corresponding product
expansion, and the active Jacobi support gives the nonzero visible
product exponents in that chamber.
$$E_0:=\rho.$$
$$q^{1/2}r^{1/2}s^{1/2}=\exp(-\pi i(\rho,z)).$$
$$\exp(-2\pi i(\alpha(\gamma),z)),\qquad
\exp(-2\pi i(\rho,z)).$$
\end{definition}

\begin{definition}[Active support and Borcherds cone]
In the standard cusp chamber, the active support is
$$
\Gamma_{\mathrm{act}}
=\{\gamma=(n,l,m)\in\Gamma_{\mathrm{eff}}\mid f(nm,l)\neq0\}.
$$
The inactive triples in $\Gamma_{\mathrm{eff}}\setminus\Gamma_{\mathrm{act}}$
are ordering data only; their product exponents are zero.  The product
does not prove absence of root spaces with zero signed superdimension.
The proof-grade Borcherds cone is the real cone generated by the active
positive Gram-index degrees after the Lorentzian degree map:
$$
\Cone_{\mathrm{Borch}}
:=\R_{\geq0}\,\alpha(\Gamma_{\mathrm{act}})
\subset \La^{2,1}_{II}\otimes\R.
$$
The real-root hyperplanes are the walls used by the denominator
identity in this polarization.
\end{definition}

\begin{lemma}[Active support gives the type-II chamber cone]
\label{lem:active-support-type-ii-cone}
For $\gamma=(n,l,m)\in\Gamma_{\mathrm{act}}$,
$$
\alpha(\gamma)
=n\delta_1+m\delta_2+(n+m-l)\delta_3,
$$
with
$$n\ge0,\qquad m\ge0,\qquad n+m-l\ge0.$$
Consequently
$$
\Cone_{\mathrm{Borch}}
=\R_{\geq0}\delta_1+\R_{\geq0}\delta_2+\R_{\geq0}\delta_3.
$$
\end{lemma}

\begin{proof}
The displayed decomposition is
$$
n(2f_2-f_3)+m(2f_{-2}-f_3)+(n+m-l)f_3
=2nf_2-lf_3+2mf_{-2}.
$$
The effective chamber gives $n,m\ge0$.  Since
$\phi_{0,1}$ is weak of index one, $f(nm,l)\ne0$ implies
$4nm-l^2\ge-1$.  If $n=0$ or $m=0$, this gives $l^2\le1$, and the
boundary cases in $\Gamma_{\mathrm{eff}}$ give $l\le n+m$.  If
$n,m>0$ and $l\ge n+m+1$, then
$$
l^2\ge(n+m+1)^2
=4nm+(n-m)^2+2(n+m)+1>4nm+1,
$$
contradicting $l^2\le4nm+1$.  Hence $n+m-l\ge0$.
The reverse inclusion follows from the active triples
$$
(1,0,0),\qquad (0,0,1),\qquad (0,-1,0),
$$
whose degrees are $\delta_1+\delta_3$, $\delta_2+\delta_3$, and
$\delta_3$, and from the active triples
$$
(1,1,0),\qquad (0,1,1),
$$
whose degrees are $\delta_1$ and $\delta_2$.
\end{proof}

For $n,l,m \in \Z$ with $n \equiv m \equiv l \equiv 1 \mod 2$,
$n,m > 0$ and
$4nm - l^2 > 0$, set
$$a = (n-1) f_2 - \frac{l-1}{2} f_3 + (m-1) f_{-2},
\qquad
m(a) = -\frac{1}{64} c_\Delta(n,l,m).$$
\cite[Theorem 2.1]{GN}
$$\rho+a=nf_2-\frac l2f_3+mf_{-2},$$
and
$$\frac{1}{64}c_\Delta(n,l,m)\exp(\pi i (n z_1 + lz_2 + m z_3)) $$
$$= \frac{1}{64} c_\Delta(n,l,m)
\exp\left(- \pi i\left(nf_2-\frac{l}{2}f_3+mf_{-2}, z\right)\right)$$
$$= -m(a) \exp (-\pi i(\rho +a, z)),$$
with
$$a\in(\La^{2,1})^*=\frac{1}{2}\La^{2,1}_{II}.$$
The normalization $c_\Delta(1,1,1)=64$ fixes $m(0)=-1$.  Since
$c_\Delta(n,l,m)\in64\Z$, all $m(a)$ are integral.  The inequality
$4nm-l^2>0$ implies
$$\rho+a\in \Cone(\La^{2,1})_+.$$

Let $\lambda=\rho+a$.  For nonzero coefficients in the chosen chamber,
$$\lambda\in(\La^{2,1}_{II})^*\cap\R_+\Poly_{II},\qquad
(\lambda,\delta_i)\leq0.$$
If $(\lambda,\delta_i)=0$, then
$$c_\lambda=-c_\lambda=0.$$
For nonzero terms, $(\lambda,\delta_i)<0$.  Since
$(\rho,\delta_i)=-1$,
$$(a,\delta_i)\leq0,\qquad
a\in\Delta(\La^{2,1}_{II})^*_+.$$
$$a \in \R_{\geq 0} \Delta(\La^{2,1}_{II})_+^* \cap
\overline{\Cone(\La^{2,1})_+} = \R_{\geq 0} \Poly_{II}.$$
The congruences $m\equiv n\equiv l\equiv1\pmod2$ imply
$$a\in 2(\La^{2,1})^*=\La^{2,1}_{II}.$$
$$a=0\qquad\hbox{or}\qquad
a\in\La^{2,1}_{II}\cap\R_{>0}\Poly_{II}.$$


\begin{lemma}
$$\frac{1}{64}\Delta_5(Z)
=\displaystyle\sum_{w \in W^{(2)}(\La^{2,1}_{II})} \text{det}(w)( \exp(-\pi
i(w(\rho),z))- \sum_{a \in \La^{2,1}_{II}\cap\R_{>0}\Poly_{II}}
m(a)\exp(-\pi i(w(\rho+a),z)))$$
\end{lemma}

\begin{proof}
Let $c_\lambda$ be the coefficient of $e^{-\pi i(\lambda,z)}$ in
$64^{-1}\Delta_5$.  The leading term has
$$\lambda=\rho,\qquad c_\rho=1.$$
The other exponents in the chosen chamber have
$$\lambda=\rho+a,\qquad
a\in\La^{2,1}_{II}\cap\R_{>0}\Poly_{II},\qquad
c_{\rho+a}=-m(a).$$
Anti-invariance:
$$c_{w\lambda}=\det(w)c_\lambda.$$
If $\lambda$ lies on a simple wall, then
$$s_{\delta_i}\lambda=\lambda,\qquad c_\lambda=-c_\lambda=0.$$
Summing the signed Weyl translates proves the formula.
\end{proof}

The primitive isotropic rays of $\overline{\Poly_{II}}$ are generated by
$$2f_2,\qquad 2f_{-2},\qquad 2f_2-2f_3+2f_{-2}.$$
The group $\Aut(\Poly_{II})\simeq S_3$ is transitive on these three
vectors.  For $a_0=2f_2$:

$$1 + \frac{1}{64} \sum_{t \geq 1} c_\Delta(1 + 2t, 1, 1)q^t = \displaystyle\prod_{k\geq 1} (1
- q^k)^9$$

In denominator notation,

$$ 1 - \sum_{t \geq 1} m(t a_0) q^t = \displaystyle\prod_{t\geq 1}
(1 - q^t)^{\tau(t a_0)},\qquad \tau(t a_0)=9\quad(t\geq1).$$

By $S_3$-symmetry,
$$\tau(ta)=9\qquad(t\geq1)$$
for every primitive isotropic ray
$$\Z_{>0}a\subset
\overline{\Poly_{II}}\cap\La^{2,1}_{II}.$$
On isotropic rays, the coefficients $m(ta)$ are determined by the
eta-product expansion; the signed simple-root supermultiplicity is
\(\tau(ta)\).  The imaginary simple roots of $\autcor$ are these
isotropic and timelike rays in $\overline{\Poly_{II}}\cap\La^{2,1}_{II}$,
with multiplicities $\tau(a)$ on isotropic rays and $m(a)$ on
negative-norm rays \cite[Theorem 2.1]{GN}, \cite[(5.1), Section 5.1.1]{GNII}.


The real root datum is the wall set
$$\Poly_{II,prim}=\{\delta_1,\delta_2,\delta_3\}$$
with Gram matrix \cite[Theorem 4.1]{GN} (and \cite[Section 5.1.1, case (t=1,II,0)]{GNII} as secondary)

$$(\delta_i,\delta_j) = \begin{pmatrix}2 & -2 & -2\\-2 & 2 & -2\\-2 & -2 & 2\end{pmatrix}$$

\begin{definition}[Simple real roots and perturbative walls]
$$\Delta^{re}_{\mathrm{simp}}=\{\delta_1,\delta_2,\delta_3\},\qquad
\Delta^{re}=W^{(2)}(\La^{2,1}_{II})\Delta^{re}_{\mathrm{simp}},$$
$$
\mathcal W_{\mathrm{pert}}
=\bigcup_{\delta\in\Delta^{re}_{\mathrm{simp}}}\Hpl_\delta.
$$
\end{definition}

\section{The denominator algebra}

$$A=((\delta_i,\delta_j))_{1\leq i,j\leq3}
=\begin{pmatrix}2&-2&-2\\-2&2&-2\\-2&-2&2\end{pmatrix}$$
$$A\ \hbox{symmetric generalized Cartan},\qquad
\bkm(A)\ \hbox{Kac--Moody}.$$
$$\mathcal A_{\mathrm{den}}:=\autcor.$$
This is the target-internal algebraic denominator square root.  It is the
automorphic correction of $\bkm(A)$ constructed by
Gritsenko--Nikulin \cite[Sections~3--4]{GN}, with root spaces graded by the Gram-degree
map
$$
\gamma=(n,l,m)\longmapsto
\alpha(\gamma)=2nf_2-lf_3+2mf_{-2}.
$$
The Borcherds correction character in the coefficient chamber is
$$\mathcal C_{\mathrm{im}}(z)
=1-\sum_{a\in\La^{2,1}_{II}\cap\R_{>0}\Poly_{II}}
m(a)e^{-2\pi i(a,z)}.$$
$$e^{-2\pi i(\rho,z)}\mathcal C_{\mathrm{im}}(z).$$

Signed root-superdimension convention; Harvey--Moore is the external
physical interpretation \cite{HM}:
$$\smult(\alpha)
=\dim\mathfrak{g}_{\alpha,\overline 0}
-\dim\mathfrak{g}_{\alpha,\overline 1}.$$
Let \(\mathcal R\) be the root set of
\(\mathfrak g_{\Delta_5}\), and let \(\mathcal R_+\) be the positive
root set in the \(\Poly_{II}\)-chamber.

\begin{definition}[Denominator Lie superalgebra]
For $\gamma\in\Gamma_{\mathrm{ind}}$ set
$$
\mathcal A_{\mathrm{den},\gamma}
:=
\begin{cases}
\La^{2,1}_{II}\otimes\C,&\gamma=0,\\
\mathfrak g_{\Delta_5,\alpha(\gamma)},&\alpha(\gamma)\in\mathcal R,\\
0,&\alpha(\gamma)\notin\mathcal R.
\end{cases}
$$
The zero degree is the Cartan subalgebra and is not governed by
\(f(0,0)\).  The bracket is the Borcherds--Kac--Moody bracket of
\(\autcor\):
$$
[\ ,\ ]:
\mathcal A_{\mathrm{den},\gamma}
\otimes
\mathcal A_{\mathrm{den},\gamma'}
\longrightarrow
\mathcal A_{\mathrm{den},\gamma+\gamma'}.
$$
\end{definition}

\begin{theorem}[Denominator algebra identity]
\label{thm:denominator-algebra-identity}
\label{thm:bracket-level-square-root}
The denominator Lie superalgebra has the following properties.
$$
\mathcal A_{\mathrm{den}}
=\mathcal A_{\mathrm{den},0}\oplus
\bigoplus_{\substack{\gamma\in\Gamma_{\mathrm{ind}}\\
\alpha(\gamma)\in\mathcal R}}
\mathcal A_{\mathrm{den},\gamma}
=\mathcal A_{\mathrm{den},0}
\oplus\mathcal A_{\mathrm{den}}^{\mathrm{bulk}}
\oplus\mathcal A_{\mathrm{den}}^{\mathrm{cusp}},
\qquad
[\mathcal A_{\mathrm{den},\gamma},\mathcal A_{\mathrm{den},\gamma'}]
\subset \mathcal A_{\mathrm{den},\gamma+\gamma'},
$$
where
$\mathcal A_{\mathrm{den}}^{\mathrm{bulk}}
=\bigoplus_{\alpha(\gamma)\in\mathcal R,\,m(\gamma)>0}
\mathcal A_{\mathrm{den},\gamma}$
records the $m>0$ Borcherds bulk and
$\mathcal A_{\mathrm{den}}^{\mathrm{cusp}}
=\bigoplus_{\alpha(\gamma)\in\mathcal R,\,m(\gamma)=0}
\mathcal A_{\mathrm{den},\gamma}$
records the $m=0$ Weyl-chamber cusp boundary, in parallel with the
$\mathcal V=\mathcal V_{\mathrm{bulk}}\oplus\mathcal V_{\mathrm{cusp}}$
splitting at the determinant level above.
Its visible positive signed Gram-degree multiplicities are the K3 half-index
coefficients:
$$
\smult(\alpha(n,l,m))=f(nm,l)
\qquad((n,l,m)\in\Gamma_{\mathrm{act}}).
$$
Its Weyl--Kac--Borcherds denominator is
$$
\operatorname{den}(\mathcal A_{\mathrm{den}})
=64^{-1}\Delta_5(2Z).
$$
The theorem concerns the Borcherds denominator algebra.  A microscopic
BPS Hilbert space and its operator product require separate
construction.
\end{theorem}

\begin{proof}
Gritsenko--Nikulin \cite[Theorem 2.1, (2.1)--(2.3)]{GNII} construct $\autcor$ as the generalized
Borcherds--Kac--Moody superalgebra whose real simple roots are
$\delta_1,\delta_2,\delta_3$ and whose imaginary simple-root
multiplicities are read from the Borcherds correction character.  A
product exponent gives the signed multiplicity of a visible positive
root; the simple imaginary-root datum is Gritsenko--Nikulin's \(m(a)\)
for negative-norm \(a\) and \(\tau(a)\) on isotropic rays.  These are
different pieces of the denominator construction.  A
root-graded Lie superalgebra has
$$
[\mathfrak g_{\Delta_5,\alpha},\mathfrak g_{\Delta_5,\beta}]
\subset\mathfrak g_{\Delta_5,\alpha+\beta}.
$$
Here \(\alpha\in\La^{2,1}_{II}\otimes\C\), and the addition
\(\alpha+\beta\) is linear inside the Cartan; this is the linear root
grading of a Borcherds--Kac superalgebra.  The Gram-degree map
\[
\gamma=(n,l,m)\longmapsto\alpha(\gamma)=2nf_2-lf_3+2mf_{-2}
\in\La^{2,1}_{II}\otimes\C
\]
is the inverse correspondence of root indexing: it is additive in
\((n,l,m)\) and recovers the linear addition in
\(\La^{2,1}_{II}\otimes\C\).  This linear additivity is the relevant
statement for the denominator algebra of \(\Delta_5\), where the grading
lattice is \(\La^{2,1}_{II}\) and \(\Gamma_{\mathrm{ind}}=\Z^3\) is the
Gram parametrization of that grading.  In a hypothetical Hall source,
the underlying lattice is the physical
\(\Gamma_X^{\mathrm{phys}}=\La_S\oplus\La_S\), the Hall bracket is
graded by \(\Gamma_X^{\mathrm{phys}}\) (additive), and the
\(\Gamma_{\mathrm{ind}}\)-grading of the denominator algebra is the
\(\Pi\)-image, well defined modulo the cocycle \(B\) of
Definition~\ref{def:dyonic-mukai-lattice}.  The denominator identity reads
$$
\frac1{64}\Delta_5(2Z)
=e^{-2\pi i(\rho,z)}
\prod_{\alpha\in\mathcal R_+}
(1-e^{-2\pi i(\alpha,z)})^{\smult(\alpha)}.
$$
Comparing this with the Borcherds product gives
$$
\smult(\alpha(n,l,m))=f(nm,l)
\qquad((n,l,m)\in\Gamma_{\mathrm{act}}).
$$
\end{proof}

\section{Compact Dirac--Igusa realization problem}
\label{sec:compact-dirac-igusa-realization-problem}

The denominator algebra is the target.  A compact \(K3\times E\)
theory would be a source.  The distinction is between observables and
states.  The formal current envelope below is an observable algebra
attached to the imported Borcherds--Kac--Moody target; it is not a
compact BPS state space and it contains no Hall extension
correspondences.  Its target-side bar--cobar counit remains internal to
that observable algebra.  A genuine Dirac--Igusa realization must supply
the state-side Hall object, the orientation/Pfaffian line, the
normal-ordered Gram descent, and the chiral Koszul comparison before
one may identify its primitives with \(\mathfrak g_{\Delta_5}\).
Throughout this compact realization problem, \(S\) is a smooth complex
K3 surface and \(E\) is a smooth elliptic curve; singular K3 limits and
nodal or cuspidal elliptic degenerations belong to the boundary
certificate, not to the standing compact source datum.

\begin{definition}[Formal current envelope]
Let $E$ be the elliptic curve in $X=S\times E$.  Put
$$
\operatorname{Cur}_E(\mathcal A_{\mathrm{den}})
:=\mathcal A_{\mathrm{den}}\otimes\mathcal O_E
$$
with the level-zero current bracket
$$
[a\otimes f,b\otimes g]=[a,b]\otimes fg.
$$
Its chiral enveloping algebra in the sense of Beilinson--Drinfeld
\cite{BD} is
$$
\mathsf{Den}_{\Delta_5,E}
:=U_E^{\mathrm{ch}}\!
\left(\operatorname{Cur}_E(\mathcal A_{\mathrm{den}})\right).
$$
\end{definition}

\begin{proposition}[Formal current envelope]
\label{prop:formal-current-envelope}
\label{thm:factorization-square-root}
\(\mathsf{Den}_{\Delta_5,E}\) is the formal completed ind
Beilinson--Drinfeld current envelope on \(E\) obtained from the
denominator Lie superalgebra.  Its constant-current Lie superalgebra is
\(\mathcal A_{\mathrm{den}}\), and the denominator of that
constant-current bracket is
$$
64^{-1}\Delta_5(2Z).
$$
A compact \(E_3\)/Hall/chiral BPS realization requires additional
microscopic input.
\end{proposition}

\begin{proof}
In the completed ind setting, the current construction sends a Lie
superalgebra to a Lie-* algebra on a smooth curve, and the chiral
enveloping construction sends a Lie-* algebra to a chiral algebra
\cite{BD}; equivalently, in vertex-algebra language, this is the
universal current vertex algebra at level zero \cite{KACVA}.  Constant
sections of
$\mathcal A_{\mathrm{den}}\otimes\mathcal O_E$ recover the original Lie
superalgebra.  The denominator statement is exactly
Theorem \ref{thm:denominator-algebra-identity}.
\end{proof}

\begin{definition}[Holomorphic \(E_3\) quantum upgrade]
The determinant and denominator results above are protected
Euler-characteristic statements.  The expected quantum upgrade does not
start from the scalar determinant.  It would start from a supplied
holomorphic \(E_3\)-factorization algebra on the Calabi--Yau threefold
$$
\mathcal A^{E_3}_X,\qquad X=K3\times E.
$$
By a holomorphic \(E_3\)-factorization algebra is meant here: a
factorization algebra on \(X\) in the sense of Costello--Gwilliam
(\cite{CostelloGwilliam1}, \cite{CostelloGwilliam2} esp.~vol.~II
\S10--11), locally constant in real directions and holomorphic in three
complex directions, whose factorization structure maps are governed by
holomorphic polydiscs in \(\C^3\); equivalently a factorization algebra
in the holomorphic \(E_3\)-operadic sense, together with whatever
homotopy/framing datum is required by the chosen operadic model.  No
identification with an \(SO(6)\) or \(SO(3)\) framed topological
operad is asserted here.  This symbol, and the placeholder
\(\Phi^{\mathrm{FA}}_3(X)\), denote the source object required in the
Calabi--Yau-to-chiral construction; they are not a constructed functor
evaluated on \(X\).
The candidate concrete realization, supplied as a conditional schema, is
the local protected observable algebra
\(\mathcal A_X(U)\) of
Definition~\ref{def:local-protected-observable-algebra}.
A compact holomorphic-Chern--Simons/BV model, if constructed with the
required descent, quantum master equation, and anomaly cancellation,
would be a candidate source for this datum in the completed charge
category.  Such a source also requires a chosen \(E_3\)-formality point,
a chain-level homotopy/framing datum for the chosen operadic model,
compact-support control, and
finite-stage HN quotients on which all operations are defined before
passing to the completed inverse system.

The curve-level BPS algebra would be obtained only after a supplied
chain-level specialization along the \(K3\)-direction.  Split the triple
identification into three named pieces, each carrying a separately
labelled comparison map:
\[
\mathcal A^{E_3}_X
\xrightarrow{\ \mathrm{Sp}^{\mathrm{ch}}_{K3,E}\ }
\mathcal F_X^{(0)}
\xrightarrow{\ \kappa_E\ }
\mathcal F_X^{(1)}
\xrightarrow{\ \pi_*^{\mathrm{ch}}\ }
(p_E)_*\mathcal A^{E_3}_X.
\]
Here:
\(\mathrm{Sp}^{\mathrm{ch}}_{K3,E}\) is required to be a chain-level
K3-integration/factorization-pushforward datum along the
\(K3\)-fibration \(p_E:K3\times E\to E\), comparing the relevant
Beilinson--Drinfeld and Costello--Gwilliam models.  Its source category,
target category, support condition, charge grading, and functorial
transition squares are part of the supplied datum; its output
\(\mathcal F_X^{(0)}\) is intended to be a chiral algebra on \(E\)
(equivalently a factorization algebra on \(\operatorname{Ran}(E)\)).
\(\kappa_E\) is the chiral-to-ordinary pushforward/formality comparison
\(\mathcal F_X^{(0)}\to\mathcal F_X^{(1)}\), not the source cobar
comparison \(\Theta_{\mathrm{Kos}}\),
where \(\mathcal F_X^{(1)}\) is the candidate identification of the
chiral pushforward with the ordinary derived pushforward
\((p_E)_*\mathcal A^{E_3}_X\) regarded as a sheaf-of-cochain factorization
algebra on \(\operatorname{Ran}(E)\); identification of
chiral and ordinary pushforward is the open chiral-Koszul comparison.
\(\pi_*^{\mathrm{ch}}\) is required to be the closing identification of
\(\mathcal F_X^{(1)}\) with \((p_E)_*\mathcal A^{E_3}_X\) as
factorization data, comparing the Costello--Gwilliam push along a
proper holomorphic submersion with the topological pushforward; this
comparison is required to reduce to the standard projection-finite
comparison and is open in the wrapped sectors.  The convenient shorthand
\(\mathcal F_X\) refers to any one of \(\mathcal F_X^{(0)}\),
\(\mathcal F_X^{(1)}\), or \((p_E)_*\mathcal A^{E_3}_X\) once
\(\kappa_E\) and \(\pi_*^{\mathrm{ch}}\) have been supplied.  Without
the chiral-Koszul comparison and the proper-pushforward identification,
the three names are distinct objects.
Restrictions to chambers, pushforwards to \(E\), and chiral Koszul
dualities are then operations on \(\mathcal A^{E_3}_X\) and on its
\(E_1\)-chiral shadow \(\mathcal F_X\), not replacements for the
\(E_3\)-source.

After these data have been constructed, the required Igusa statement is
the pair of comparisons
$$
H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^{\Theta}\mathcal F_X)
\stackrel{?}{\cong}
\mathfrak g_{\Delta_5},
\qquad
\Omega_E^{\mathrm{ch}}C_X
\stackrel{?}{\simeq}
\mathsf{Den}_{\Delta_5,E}.
$$
Here \(C_X\) is the source coalgebra later formalized in
Definition~\ref{def:chiral-koszul-source-certificate}; in wrapped
degree it is attached to the hybrid object
\(\mathcal F_X^{\mathrm{hyb}}\), not merely to the projection-finite
Ran shadow.  The first comparison would be the bracket theorem.  The
second would be the chiral Koszul theorem.  Both require microscopic data
beyond the scalar square and beyond the formal current envelope.
\end{definition}

\begin{definition}[Compact holomorphic \(E_3\) source interface]
\label{def:compact-e3-source-interface}
Fix a stability sector \((\sigma,S)\) and the finite HN height
quotients of Proposition~\ref{prop:sectorial-hall-truncation}.  A compact
holomorphic \(E_3\) source interface for \(X=K3\times E\) is not, by
itself, a compact quantum field theory.  It is the following finite-first
chain datum:
\[
\mathbb A_{X,\sigma,S}^{E_3}
=\left\{
\mathcal A_{X,\sigma,S,\le R}^{E_3},\,
\rho_{R'R},\,m_{\mathcal U,R},\,
S_R,\{-,-\}_R,\Delta_R^{\mathrm{BV}},\,
\eta_{\mathcal V,R},\omega_{\mathrm{QME},R},
\omega_{\mathrm{anom},R},\,
\mathrm{Sp}^{\mathrm{ch}}_{K3,E,R}
\right\}_{R>0,\ R'\ge R}.
\]
Here \(\mathcal A_{X,\sigma,S,\le R}^{E_3}\) is a charge-supported
cochain-level holomorphic \(E_3\)-factorization object with charges in
\(\Gamma_{\sigma,S}^{HN}(R)\); \(\rho_{R'R}\) are transition maps for the
HN inverse system; \(m_{\mathcal U,R}\) are the structure maps attached to
disjoint holomorphic polydiscs \(\mathcal U\subset X\);
\(S_R,\{-,-\}_R,\Delta_R^{\mathrm{BV}}\) are the finite BV action,
antibracket, and BV Laplacian conventions used to formulate the finite
classical or quantum master equation; \(\eta_{\mathcal V,R}\) are
Cech--Weiss descent cochains for the chosen holomorphic-polydisc cover
\(\mathcal V\); \(\omega_{\mathrm{QME},R}\) and
\(\omega_{\mathrm{anom},R}\) are the finite QME and anomaly cocycles with
specified null-homotopies; and
\(\mathrm{Sp}^{\mathrm{ch}}_{K3,E,R}\) is the finite-stage K3-to-\(E\)
specialization datum, including source, target, support, charge grading,
wrapped-sector compatibility, and transition squares.  The interface is
required to carry:
\begin{enumerate}
\item descent, QME, and anomaly-cancellation witnesses at every finite
height \(R\), i.e.
\[
d_R S_R+\frac12\{S_R,S_R\}_R
\quad\hbox{or}\quad
d_R S_R+\frac12\{S_R,S_R\}_R+\hbar\Delta_R^{\mathrm{BV}}S_R
\]
is killed by the supplied finite homotopy
\(\omega_{\mathrm{QME},R}\), and the local anomaly cocycle is killed by
\(\omega_{\mathrm{anom},R}\), compatibly with \(\rho_{R'R}\);
\item a fixed \(E_3\)-formality point and a homotopy/framing witness for
the chosen holomorphic \(E_3\)-operadic model, treated as a chosen
torsor point rather than a canonical equality;
\item compatibility of \(m_{\mathcal U,R}\), specialization, and the
transition maps \(\rho_{R'R}\);
\item compact-support control and continuity for the HN inverse system,
with \(\mathcal A_{X,\sigma,S,\le R}^{E_3}\) a quotient by a
factorization ideal killing outputs of height \(>R\), and with every
structure map \(m_{\mathcal U,R}\) descended from higher stages;
\item the rule that the K3-to-\(E\) specialization is an ordinary
\(\operatorname{Ran}(E)\)-factorization object only on the
projection-finite part; positive elliptic degree must be routed through
the hybrid wrapped datum of
Definition~\ref{def:hybrid-wrapped-factorization-certificate}.
\end{enumerate}
If all finite stages and transition maps are supplied, the completed
source is the inverse limit
\[
\mathcal A_{X}^{E_3}:=
\varprojlim_R\mathcal A_{X,\sigma,S,\le R}^{E_3}.
\]
This equation is a construction from the displayed finite data, not an
existence theorem for those data.
\end{definition}

\begin{openproblem}[Compact holomorphic \(E_3\) source]
\label{op:compact-e3-source}
Construct a nonempty interface
\(\mathbb A_{X,\sigma,S}^{E_3}\) in the sense of
Definition~\ref{def:compact-e3-source-interface}, and hence the completed
source object \(\mathcal A^{E_3}_X\), for \(X=K3\times E\).  A candidate
compact holomorphic-Chern--Simons/BV construction must prove, before any
comparison with \(\Delta_5\), the following finite-chain data:
\begin{enumerate}
\item descent for local observables on \(X\) and a quantum master
equation after compact charge completion;
\item anomaly cancellation, a fixed \(E_3\)-formality point in the
sense of Tamarkin--Kontsevich formality for \(E_n\)-operads
\cite{TamarkinLittleDisks,KontsevichOperadsMotives,LambrechtsVolicLittleDisks},
and a chain-level homotopy/framing datum for the chosen holomorphic
\(E_3\)-operadic model; compact-support control;
\item a finite-first sectorial completion compatible with
Harder--Narasimhan quotients, with all operations defined on finite
stages before completion;
\item the chain-level \(K3\)-to-\(E\) specialization
\(\mathrm{Sp}^{\mathrm{ch}}_{K3,E}\);
\item the projection-finite local sector and the hybrid wrapped repair
for positive elliptic degree;
\item a strong orientation, protected integration, and primitive
recognition certificate.
\end{enumerate}
Existing BV, CoHA, and chiral-algebra formalisms give the language for
these requirements.  They do not, by themselves, construct this compact
source for \(K3\times E\).  The external open data are: the
\(E_3\)-formality point (Tamarkin--Kontsevich formality at a chosen
associator, regarded here as a chosen torsor point
\cite{TamarkinLittleDisks,KontsevichOperadsMotives,LambrechtsVolicLittleDisks};
rationality of formality is open over \(\Q\) but known over \(\R\)), and the chain-level
homotopy/framing datum for the
chosen holomorphic \(E_3\)-operadic model; chain-level constructibility
for the candidate concrete realization
\(\mathcal A_X(U)\) of
Definition~\ref{def:local-protected-observable-algebra} is open).
\end{openproblem}

\begin{remark}[Where the quantum comparison would live]
Assume the source algebra \(\mathcal A^{E_3}_X\), the specialization
\(\mathrm{Sp}^{\mathrm{ch}}_{K3,E}\), a conilpotent coalgebra
\(C_X\) with supplied comparison
\[
b_X:C_X\xrightarrow{\ \simeq\ }
\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}}),
\]
and a
quasi-isomorphism
\[
\Theta_{\mathrm{Kos}}:
\Omega_E^{\mathrm{ch}}C_X
\xrightarrow{\ \simeq\ }
\mathsf{Den}_{\Delta_5,E}
\]
have all been supplied.  Then \(\mathcal F_X^{\mathrm{hyb}}\) is the place where the
protected primitive bracket and the chiral Koszul comparison must be
formulated.  Costello--Gwilliam locality explains why a holomorphic
quantum theory would produce factorization products before any trace or
determinant is taken \cite{CostelloRenormalization},
\cite{CostelloGwilliam1}, \cite{CostelloGwilliam2}; Beilinson--
Drinfeld chiral operations are the curve-level algebraic form of
collision maps \cite{BD}.  None of this is obtained from the scalar
square or from the denominator identity alone.
\end{remark}

\begin{remark}[Pushforward, restriction, Koszul duality]
The second step is specialization, not inversion.  A restriction to a chamber
or sector is a restriction of \(\mathcal A^{E_3}_X\) before, or of
\(\mathcal F_X\) after, the \(K3\)-specialization.  Pushforward along
\(p_E\) is the geometric notation for the same specialization.  A
compact Koszul theorem would require a supplied conilpotent coalgebra
\(C_X\), an identification
$$
C_X\stackrel{?}{\simeq} \bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}}),
$$
and a further quasi-isomorphism
$$
\Omega_E^{\mathrm{ch}}C_X
\stackrel{?}{\simeq}
\mathsf{Den}_{\Delta_5,E}.
$$
These are not procedures for reconstructing the holomorphic
\(E_3\)-source from the denominator alone.
\end{remark}

\begin{proposition}[Target-internal bar--cobar counit]
\label{prop:target-internal-bar-cobar-inversion}
Choose an augmented filtered model of the formal target
\(\mathsf{Den}_{\Delta_5,E}\) whose finite charge truncations lie in the
conilpotent chiral setting where Francis--Gaitsgory chiral Koszul
duality applies.  Then the target has its own bar--cobar counit:
\[
\Omega_E^{\mathrm{ch}}\bar B_E^{\mathrm{ch}}
(\mathsf{Den}_{\Delta_5,E})
\longrightarrow
\mathsf{Den}_{\Delta_5,E}.
\]
The filtration used here is target-internal: it is the charge filtration
on the imported current envelope, together with the chosen augmentation.
It is not the source filtration \(F^{\mathrm{co}}_{R,\bullet}\), and its
bar coalgebra is not \(C_{X,R}\).  Cf.\ Kac \cite{KACVA} for the
underlying vertex algebra structure, Beilinson--Drinfeld
\cite[\S3.7]{BD} for the chiral bar--cobar formalism, and
Francis--Gaitsgory \cite[Theorem~6.2.2]{FrancisGaitsgoryCKD} for chiral
Koszul duality in the conilpotent setting.  The counit reconstructs the already defined
target from its target bar coalgebra.  It is not the compact Koszul
comparison
\[
\Omega_E^{\mathrm{ch}}C_X
\stackrel{?}{\simeq}
\mathsf{Den}_{\Delta_5,E}
\]
unless \(C_X\) has first been constructed from the compact
\(K3\times E\) factorization object and identified with
\(\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}})\).  The missing datum is the
source coalgebra, its collision coproduct, and the source comparison
map, not a homotopy inverse to the target-side counit.
\end{proposition}

\begin{proof}
Beilinson--Drinfeld bar--cobar formalism is an adjunction on chiral
algebras and conilpotent chiral coalgebras on the curve
\cite[\S3.7]{BD}.  Applying this formalism to the known target
\(\mathsf{Den}_{\Delta_5,E}\), after choosing the displayed augmented
filtered model, produces a tautological counit map back to that target.
The finite charge filtration is used only to place this target
calculation in the conilpotent formal category.  No moduli stack of
compact objects, source collision coproduct, orientation system,
protected integration map, or primitive representative enters this
construction.  Those are precisely the extra data in
Definition~\ref{def:compact-igusa-realization-datum}.
\end{proof}

\begin{lemma}[Source--target separation for the Koszul lane]
\label{lem:source-target-koszul-separation}
Fix a finite height \(R\).  The target counit
\[
\varepsilon_{\Delta,R}:
\Omega_E^{\mathrm{ch}}\bar B_E^{\mathrm{ch}}
(\mathsf{Den}_{\Delta_5,E,\le R})
\longrightarrow
\mathsf{Den}_{\Delta_5,E,\le R}
\]
is a morphism internal to the imported current envelope.  A source
Koszul certificate is different data: it must first construct
\[
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},\qquad
C_{X,R},\qquad
F^{\mathrm{co}}_{R,\bullet},\qquad
\Delta_R^{\mathrm{ch}},
\]
from the finite hybrid correspondence category
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), its quotient functor \(Q_{E,R}\),
orientations, the eight-word two-step binary flag atlas, and the
separate higher colored configuration residual; only then may it compare
\[
b_{X,R}:C_{X,R}\simeq
\bar B_E^{\mathrm{ch}}
\bigl(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
\varepsilon_{X,R}^{\mathrm{hyb}}\bigr),
\qquad
\Theta_{\mathrm{Kos},R}:
\Omega_E^{\mathrm{ch}}C_{X,R}\simeq
\mathsf{Den}_{\Delta_5,E,\le R}.
\]
Thus setting \(C_{X,R}=\bar B_E^{\mathrm{ch}}
(\mathsf{Den}_{\Delta_5,E,\le R})\), or choosing a homotopy inverse to
\(\varepsilon_{\Delta,R}\), does not produce a source certificate.  It
sets the separation residual \(\mathfrak o^{\mathrm{sep}}_R\) to zero
only after an independent source construction of \(C_{X,R}\),
\(F^{\mathrm{co}}_{R,\bullet}\), \(\Delta_R^{\mathrm{ch}}\), and
\(b_{X,R}\) has been supplied and identified with the target-side model.
\end{lemma}

\begin{proof}
The domain of \(\varepsilon_{\Delta,R}\) contains only the target
augmentation, target charge filtration, and target chiral operations.  It
does not contain the rigidified wrapped prequotients, anchors, mixed
local/wrapped correspondences, quotient-after-correspondence functor,
orientation transport, protected integration, or primitive
representatives.  These are the data from which the source coalgebra and
collision coproduct are required to be built.  Therefore a target
bar--cobar inverse can be compared with a source coalgebra after that
coalgebra exists; it cannot define the source coalgebra or its primitive
restriction.
\end{proof}

\begin{definition}[Chiral Koszul source certificate]
\label{def:chiral-koszul-source-certificate}
Fix \((\sigma,S,R)\), the finite HN support
\(\widehat\Gamma_R\), and the Gram image \(\Gamma_R^\Pi\).  Let
\[
\mathsf{Den}_{\Delta_5,E,\le R}
\]
denote the charge-truncation of the formal current envelope
\(\mathsf{Den}_{\Delta_5,E}\) to the finite set of Gram degrees
\(\Gamma_R^\Pi\).  A finite-stage chiral Koszul source certificate is a
datum
\[
\mathfrak K^{\mathrm{Kos}}_{X,R}
=
\left(
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
C_{X,R},
F^{\mathrm{co}}_{R,\bullet},
\Delta_R^{\mathrm{ch}},
b_{X,R},
\Theta_{\mathrm{Kos},R}
\right)
\]
with the following properties.  Every entry is source-side finite data
except for the terminal comparison with the imported target
\(\mathsf{Den}_{\Delta_5,E,\le R}\).  In particular, neither
\(\bar B_E^{\mathrm{ch}}(\mathsf{Den}_{\Delta_5,E,\le R})\) nor a
homotopy inverse to the target counit is allowed to define
\(C_{X,R}\), \(F^{\mathrm{co}}_{R,\bullet}\), or
\(\Delta_R^{\mathrm{ch}}\).  This is the source/target separation of
Lemma~\ref{lem:source-target-koszul-separation}.
\begin{enumerate}
\item \emph{Source chiral object.}
\(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\) is the finite hybrid
object of Definition~\ref{def:hybrid-wrapped-factorization-certificate}.
Its \(b_R=0\) part comes from the \(K3\)-specialized
\(E_3\)-source; its \(b_R>0\) part is present only through the rigidified
wrapped prequotient, the ordered two-sided mixed operations, the full
flag atlas, quotient-after-correspondence descent, and protected
integration.  Equivalently, the hybrid residual
\(\mathfrak O_{\mathrm{hyb},R}\) has been trivialized at this height.  A
detached global Fock or Hecke factor does not supply this entry unless it
acts through the displayed mixed correspondences before the reduced
\(E\)-quotient.

\item \emph{Conilpotent chiral coalgebra.}
\(C_{X,R}\) is a coaugmented conilpotent chiral coalgebra on \(E\), with
coaugmentation \(\eta_R^C:k\to C_{X,R}\) and counit
\(\varepsilon_R^C:C_{X,R}\to k\), filtered by a finite increasing source
charge filtration
\[
0=F^{\mathrm{co}}_{R,-1}\subset F^{\mathrm{co}}_{R,0}
\subset\cdots\subset F^{\mathrm{co}}_{R,N_R}=C_{X,R}
\]
whose associated graded pieces are finite dimensional in each
\(\Gamma_R^\Pi\)-degree.  Its reduced iterated coproduct is nilpotent on
each finite stage.  The chiral coproduct
\(\Delta_R^{\mathrm{ch}}\) is the collision coproduct attached to the
finite Hall/factorization correspondences, including local-local,
all ordered local-wrapped, wrapped-wrapped, and eight-word flag stacks.
It is a finite pull-push construction on the collision correspondence
before \(Q_{E,R}\), and after quotient it satisfies the coalgebra
identities
\[
(\Delta_R^{\mathrm{ch}}\otimes 1)\Delta_R^{\mathrm{ch}}
=(1\otimes\Delta_R^{\mathrm{ch}})\Delta_R^{\mathrm{ch}},
\qquad
(\varepsilon_R^C\otimes1)\Delta_R^{\mathrm{ch}}
=(1\otimes\varepsilon_R^C)\Delta_R^{\mathrm{ch}}
=\mathrm{id}.
\]
For \(R'\ge R\) the transition map
\(\rho^C_{R'R}:C_{X,R'}\to C_{X,R}\) preserves the filtration and makes
the finite coproduct square commute:
\[
\begin{tikzcd}
C_{X,R'} \arrow[r,"\Delta_{R'}^{\mathrm{ch}}"]
\arrow[d,"\rho^C_{R'R}"']
& C_{X,R'}\otimes C_{X,R'}
\arrow[d,"\rho^C_{R'R}\otimes\rho^C_{R'R}"]\\
C_{X,R} \arrow[r,"\Delta_R^{\mathrm{ch}}"']
& C_{X,R}\otimes C_{X,R}.
\end{tikzcd}
\]
This finite diagram is the source of the completed coproduct on
\(C_X=\varprojlim_R C_{X,R}\).  The coproduct is not transported from
\(\bar B_E^{\mathrm{ch}}(\mathsf{Den}_{\Delta_5,E,\le R})\) along
\(\Theta_{\mathrm{Kos},R}\), and no completed tensor statement is made
before these finite squares commute.

\item \emph{Bar comparison.}
There is a charge-preserving quasi-isomorphism of conilpotent chiral
coalgebras
\[
b_{X,R}:C_{X,R}
\xrightarrow{\ \simeq\ }
\bar B_E^{\mathrm{ch}}
\bigl(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
\varepsilon_{X,R}^{\mathrm{hyb}}\bigr).
\]
It is compatible with primitive projection, the completed Hopf pairing,
the reduced \(E\)-quotient, and the normal-ordered descent
\(\overline\Pi_{X,*}^{\Theta}\).  This is a source-side comparison map,
not the tautological bar construction of the target envelope.  Its target
is the reduced bar construction of the supplied augmented hybrid source
object, with length pieces generated by the augmentation ideal, not the bar
construction of \(\mathsf{Den}_{\Delta_5,E,\le R}\).

\item \emph{Cobar comparison with the target envelope.}
There is a charge-preserving quasi-isomorphism of augmented chiral
algebras
\[
\Theta_{\mathrm{Kos},R}:
\Omega_E^{\mathrm{ch}}C_{X,R}
\xrightarrow{\ \simeq\ }
\mathsf{Den}_{\Delta_5,E,\le R}.
\]
On constant-current primitives, after the Hopf-radical quotient, this map
restricts to the primitive recognition morphism
\[
\iota_R^{\Prim}:
H^0\Prim_{\mathrm{prot}}
(\overline\Pi_{X,*}^{\Theta}\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}})
\longrightarrow
\mathfrak g_{\Delta_5,\le R}.
\]
Here \(\mathfrak g_{\Delta_5,\le R}\) is the same finite
\(\Gamma_R^\Pi\)-truncation on constant currents.  The target is the
imported Beilinson--Drinfeld current envelope of the
Gritsenko--Nikulin denominator algebra.  The map does not construct the
compact source and is not obtained from the scalar square.  Its direction
is source-to-target.  A chosen homotopy inverse, if one exists after
localization or completion, is not part of the certificate and cannot be
used to define the source coalgebra or its primitive representatives.
The displayed primitive restriction is a condition on already supplied
source primitives after the closed Hopf-radical quotient.

\item \emph{Finite residual.}
The exact Koszul obstruction tuple at height \(R\) is
\[
\mathfrak O_{\mathrm{Kos},R}
=
\left(
\mathfrak o^{C}_{R},
\mathfrak o^{\mathrm{fil}}_{R},
\mathfrak o^{\mathrm{conil}}_{R},
\mathfrak o^{\Delta,\mathrm{ch}}_{R},
\{\mathfrak o^{C,\mathrm{tr}}_{R'R}\}_{R'\ge R},
\mathfrak o^{b}_{R},
\mathfrak o^{\Omega}_{R},
\mathfrak o^{\mathrm{hyb}}_{R},
\mathfrak o^{\Pi}_{R},
\mathfrak o^{\mathrm{sep}}_{R},
\mathfrak o^{\Prim}_{R}
\right).
\]
Here the finite coalgebra defects are
\[
\mathfrak o^{\mathrm{fil}}_{R}
:=
\left(
F^{\mathrm{co}}_{R,-1},\
C_{X,R}/F^{\mathrm{co}}_{R,N_R},\
\{d_C(F^{\mathrm{co}}_{R,p})\to
C_{X,R}/F^{\mathrm{co}}_{R,p}\}_{p},\
\{\Delta_R^{\mathrm{ch}}(F^{\mathrm{co}}_{R,p})\to
(C_{X,R}\otimes C_{X,R})/
\sum_{i+j\le p}F^{\mathrm{co}}_{R,i}\otimes
F^{\mathrm{co}}_{R,j}\}_{p}
\right),
\]
\[
\overline\Delta_R^{\mathrm{ch}}
:=\Delta_R^{\mathrm{ch}}
-\bigl((\eta_R^C\varepsilon_R^C)\otimes\mathrm{id}
+\mathrm{id}\otimes(\eta_R^C\varepsilon_R^C)\bigr),
\]
and
\[
\mathfrak o^{\mathrm{conil}}_{R}
:=(\overline\Delta_R^{\mathrm{ch}})^{N_R+1},
\]
\[
\mathfrak o^{\Delta,\mathrm{ch}}_{R}
:=
\left(
(\Delta_R^{\mathrm{ch}}\otimes1)\Delta_R^{\mathrm{ch}}
-(1\otimes\Delta_R^{\mathrm{ch}})\Delta_R^{\mathrm{ch}},
(\varepsilon_R^C\otimes1)\Delta_R^{\mathrm{ch}}-\mathrm{id},
(1\otimes\varepsilon_R^C)\Delta_R^{\mathrm{ch}}-\mathrm{id}
\right),
\]
and
\[
\mathfrak o^{C,\mathrm{tr}}_{R'R}
:=
\left(
(\rho^C_{R'R}\otimes\rho^C_{R'R})\Delta_{R'}^{\mathrm{ch}}
-\Delta_R^{\mathrm{ch}}\rho^C_{R'R},\
\{\rho^C_{R'R}(F^{\mathrm{co}}_{R',p})\to
C_{X,R}/F^{\mathrm{co}}_{R,p}\}_{p}
\right).
\]
Here \(d_C\) is the finite-stage coalgebra differential, and a displayed
map to a quotient is zero exactly when the corresponding subobject
inclusion holds.
The entries record, respectively: existence of the source coalgebra;
bounded exhaustive source filtration; conilpotence of the reduced
iterated coproduct; finite collision-coproduct construction with
coassociativity and counit; transition-strict compatibility of
\((C_{X,R},F^{\mathrm{co}}_{R,\bullet},\Delta_R^{\mathrm{ch}})\); the bar
quasi-isomorphism \(b_{X,R}\); the cobar quasi-isomorphism
\(\Theta_{\mathrm{Kos},R}\); compatibility with the hybrid
local/wrapped operations, meaning
\(\mathfrak O_{\mathrm{hyb},R}=0\); compatibility with normal-ordered descent and
the reduced \(E\)-quotient; source/target separation, meaning that the
source coalgebra, filtration, coproduct, and bar comparison are supplied
before the target comparison and are not reconstructed from the target
counit; and the primitive restriction after the closed Hopf-radical
quotient.  A full Koszul certificate is the compatible vanishing and
trivialization of \(\mathfrak O_{\mathrm{Kos},R}\) for all \(R\), followed
by passage to the HN inverse limit.
\end{enumerate}
\end{definition}

\begin{proposition}[Canonical finite source-bar coalgebra]
\label{prop:canonical-source-bar-coalgebra}
Fix \(R\) and assume the finite hybrid residual
\(\mathfrak O_{\mathrm{hyb},R}\) vanishes, with the transition and
properness data of
Definition~\ref{def:hybrid-wrapped-factorization-certificate}.  Assume
also that the finite hybrid stage supplies an integer \(N_R\) such that
every nonzero ordered word of non-vacuum hybrid inputs of total HN height
\(\le R\) has length at most \(N_R\).  Equivalently, the HN height is
positive on every non-vacuum colour which survives in the reduced bar
construction; if this bounded-length condition fails, the filtration and
conilpotence residuals below are not killed.  Finally assume a supplied
augmentation
\(\varepsilon_{X,R}^{\mathrm{hyb}}\colon
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\to k\mathbf 1\), and write
\[
\overline{\mathcal F}_{X,R}
:=\ker(\varepsilon_{X,R}^{\mathrm{hyb}}).
\]
Under these hypotheses
there is a canonical source-side choice of the finite coalgebra in
Definition~\ref{def:chiral-koszul-source-certificate}:
\[
C^{\mathrm{bar}}_{X,R}
:=
\bar B_E^{\mathrm{ch}}
\bigl(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
\varepsilon_{X,R}^{\mathrm{hyb}}\bigr).
\]
This is the reduced chiral bar coalgebra of the supplied hybrid source,
not the bar coalgebra of
\(\mathsf{Den}_{\Delta_5,E,\le R}\).  Equivalently, its length \(p\)
summand is generated by ordered \(p\)-fold inputs from the augmentation
ideal \(\overline{\mathcal F}_{X,R}\) whose total HN height is \(\le R\),
with all outputs of height \(>R\) set to zero:
\[
C^{\mathrm{bar}}_{X,R}
=k\mathbf 1\oplus
\bigoplus_{1\le p\le N_R}
\bar B^{\mathrm{ch},p}_E
\bigl(\overline{\mathcal F}_{X,R}\bigr).
\]
The finite source filtration is the bar-length filtration
\[
F^{\mathrm{co}}_{R,p}C^{\mathrm{bar}}_{X,R}
:=
k\mathbf 1\oplus
\bigoplus_{1\le j\le p}
\bar B^{\mathrm{ch},j}_E
\bigl(\overline{\mathcal F}_{X,R}\bigr),
\qquad
0\le p\le N_R,
\]
where \(N_R\) is the supplied bounded-length constant.  The
coaugmentation is the inclusion of the vacuum summand and the counit is
projection to that summand.  For a homogeneous bar generator
\(x=[x_1|\cdots|x_p]\), the
collision coproduct is
\[
\Delta_R^{\mathrm{bar}}(x)
=\mathbf 1\otimes x+x\otimes\mathbf 1
+\sum_{i=1}^{p-1}
[x_1|\cdots|x_i]\otimes[x_{i+1}|\cdots|x_p],
\]
with the displayed cuts realized by the corresponding finite collision
and flag pull-push maps in
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\).  The eight-word flag coherences and
the four-input pentagon give coassociativity; the vacuum collision flags
give the counit identities; and, for the reduced coproduct obtained by
removing the two vacuum terms, the bar-length filtration gives
\[
\bigl(\overline\Delta_R^{\mathrm{bar}}\bigr)^{N_R+1}=0.
\]
Thus, after replacing \(C_{X,R}\) by
\(C^{\mathrm{bar}}_{X,R}\), the finite residuals
\[
\mathfrak o^C_R,\qquad
\mathfrak o^{\mathrm{fil}}_R,\qquad
\mathfrak o^{\mathrm{conil}}_R,\qquad
\mathfrak o^{\Delta,\mathrm{ch}}_R
\]
vanish.  The bar comparison \(b_{X,R}\) may be chosen to be the identity
of
\(\bar B_E^{\mathrm{ch}}
(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
\varepsilon_{X,R}^{\mathrm{hyb}})\).
For \(R'\ge R\), let
\[
\tau^{E,\mathrm{hyb}}_{R'R}:
\mathcal F_{X,\sigma,S,\le R'}^{\mathrm{hyb}}
\longrightarrow
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\]
be the finite hybrid transition.  Define the source coalgebra transition
\[
\rho^{\mathrm{bar}}_{R'R}:=
\bar B_E^{\mathrm{ch}}(\overline{\tau}^{E,\mathrm{hyb}}_{R'R})
\quad\text{followed by the height-\(R\) truncation.}
\]
Here \(\overline{\tau}^{E,\mathrm{hyb}}_{R'R}\) is the induced map on
augmentation ideals.
Then \(\rho^{\mathrm{bar}}_{R'R}\) preserves the bar-length filtration.
The transition residual
\(\mathfrak o^{C,\mathrm{tr}}_{R'R}\) vanishes exactly when the finite
hybrid transition functor carries ordered collision flags, quotient
compatibilities, and the bar-length filtration at height \(R'\) to the
corresponding data at height \(R\).
\end{proposition}

\begin{proof}
The construction applies the Beilinson--Drinfeld chiral bar construction
to the already supplied source chiral object
\(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\).  Since the finite HN
quotient kills charges of height \(>R\), and since non-vacuum words have
length bounded by \(N_R\), only finitely many non-vacuum bar lengths
occur.  The reduced bar construction has a vacuum
coaugmentation, a projection counit, and the standard deconcatenation
coproduct.  In the present correspondence model, each deconcatenation is
implemented by cutting the ordered collision flag; admissibility of the
pull-push maps and Thom--Sebastiani transport are part of
\(\mathfrak O_{\mathrm{hyb},R}=0\).  The associativity and pentagon
axioms for the finite flag stacks are precisely the equality of the two
iterated cut maps.  Hence the displayed coproduct is coassociative and
counital.  The reduced coproduct sends a word of length \(p\) to tensor
words whose individual lengths are \(<p\); after at most \(p\) reduced
iterations every branch has length one, and the next reduced coproduct is
zero.  Since \(p\le N_R\), the \((N_R+1)\)-fold reduced iterate is zero.
The construction of \(\rho^{\mathrm{bar}}_{R'R}\) is functorial from
\(\tau^{E,\mathrm{hyb}}_{R'R}\), and the displayed transition square is
exactly the assertion that this functorial bar map respects the finite
collision flags after quotient and truncation.  The construction has used
only the source hybrid correspondence category, not the target current
envelope.
\end{proof}

\begin{corollary}[Remaining source-to-target cobar obstruction]
\label{cor:source-bar-remaining-cobar-obstruction}
Under the hypotheses of
Proposition~\ref{prop:canonical-source-bar-coalgebra}, the source
coalgebra, finite filtration, collision coproduct, conilpotence, and bar
comparison are no longer the Koszul obstruction.  A cobar
quasi-isomorphism to the target still requires two independent finite
assertions.

First, the supplied hybrid source must itself lie in the
Beilinson--Drinfeld/Francis--Gaitsgory bar--cobar domain.  Thus it must be
augmented and placed in the completed or coderived conilpotent category in
which the source-internal counit
\[
\varepsilon^{\mathrm{src}}_{\mathrm{bar},R}:
\Omega_E^{\mathrm{ch}}C^{\mathrm{bar}}_{X,R}
\longrightarrow
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\]
is a quasi-isomorphism.  This is a source-internal assertion about the
supplied hybrid object, not the target counit.

Second, one must construct a source-to-target chiral algebra
quasi-isomorphism
\[
\vartheta_R:
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\xrightarrow{\ \simeq\ }
\mathsf{Den}_{\Delta_5,E,\le R}.
\]
If both assertions hold, then
\[
\Theta_{\mathrm{Kos},R}:
\Omega_E^{\mathrm{ch}}C^{\mathrm{bar}}_{X,R}
\xrightarrow{\ \simeq\ }
\mathsf{Den}_{\Delta_5,E,\le R}
\]
is the composite
\[
\Theta_{\mathrm{Kos},R}
:=
\vartheta_R\circ
\varepsilon^{\mathrm{src}}_{\mathrm{bar},R}.
\]
Equivalently, the following triangle commutes in the finite homotopy
category:
\[
\Theta_{\mathrm{Kos},R}
=\vartheta_R\circ
\varepsilon^{\mathrm{src}}_{\mathrm{bar},R}.
\]
For this source-bar model the exact finite defects are
\[
\mathfrak o^{\varepsilon,\mathrm{src}}_R
:=
\left(
\mathfrak o^{\mathrm{aug}}_R,\
\mathfrak o^{\mathrm{FG}}_R,\
H^\bullet\operatorname{Cone}
(\varepsilon^{\mathrm{src}}_{\mathrm{bar},R})
\right),
\]
and
\[
\mathfrak o^\vartheta_R
:=
\left(
d_{\Delta}\vartheta_R-\vartheta_R d_{\mathrm{hyb}},\
\vartheta_R\mu_R^{\mathrm{hyb}}
-\mu_{\Delta,R}(\vartheta_R\otimes\vartheta_R),\
\vartheta_R\eta_R^{\mathrm{hyb}}-\eta_{\Delta,R},\
\vartheta_R\circ\tau^{E,\mathrm{hyb}}_{R'R}
-\pi^\Delta_{R'R}\circ\vartheta_{R'},\
H^\bullet\operatorname{Cone}(\vartheta_R),\
\vartheta_R|_{\Prim}-\iota_R^{\Prim}
\right).
\]
Thus
\[
\mathfrak o^\Omega_R
:=
\left(
\mathfrak o^{\varepsilon,\mathrm{src}}_R,\
\mathfrak o^\vartheta_R
\right)
\]
is the surviving cobar residual.  Its vanishing is exactly the assertion
that the source bar-cobar counit is admissible and a quasi-isomorphism
and that the compact hybrid source is quasi-isomorphic, with transition
and primitive compatibility, to the imported denominator current
envelope.

Thus the finite source-bar construction kills the coalgebra part of
\(\mathfrak O_{\mathrm{Kos},R}\) after the hybrid source is supplied, but
it does not identify compact primitives with the imported
Gritsenko--Nikulin current envelope.  That identification remains a
source-to-target theorem, not a target-internal counit.  No homotopy
inverse to
\(\Omega_E^{\mathrm{ch}}\bar B_E^{\mathrm{ch}}
(\mathsf{Den}_{\Delta_5,E,\le R})\to
\mathsf{Den}_{\Delta_5,E,\le R}\)
enters this construction.
\end{corollary}

\begin{proposition}[Consequence of the chiral Koszul source certificate]
\label{prop:chiral-koszul-source-certificate-consequence}
Assume the finite-stage certificates
\(\mathfrak K^{\mathrm{Kos}}_{X,R}\) are supplied for all \(R\), with
compatible transition maps, in particular with
\(\mathfrak o^{C,\mathrm{tr}}_{R'R}=0\) for every \(R'\ge R\).  Assume
also the Koszul Mittag--Leffler condition: \(R^1\varprojlim=0\) for the
inverse systems of source coalgebras, completed chiral bar and cobar
constructions, target truncations, and the cones of \(b_{X,R}\) and
\(\Theta_{\mathrm{Kos},R}\) \cite[\S3.5]{WeibelHA}.  Then the inverse limit
\[
C_X:=\varprojlim_R C_{X,R}
\]
is a completed pro-conilpotent chiral coalgebra attached to the hybrid
compact source, conilpotent on every finite HN quotient, and the maps
\(b_{X,R}\) and
\(\Theta_{\mathrm{Kos},R}\) induce
\[
b_X:C_X\xrightarrow{\ \simeq\ }
\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}}),
\qquad
\Theta_{\mathrm{Kos}}:
\Omega_E^{\mathrm{ch}}C_X
\xrightarrow{\ \simeq\ }
\mathsf{Den}_{\Delta_5,E}.
\]
This identifies the supplied source cobar algebra with the formal target
current envelope.  It does not construct the \(E_3\)-source, the hybrid
wrapped Hall correspondences, the orientation line, the primitive
recognition data, or \(C_X\) itself from the target-internal counit.
\end{proposition}

\begin{proof}
The inverse limit exists by the transition compatibility, bounded
exhaustive finite charge filtration, finite coassociative and counital
collision coproduct, and continuity hypotheses in the certificate.  The
coradical filtration is finite on every \(\Gamma_R^\Pi\)-truncation and
continuous in the HN completion; the limit is therefore pro-conilpotent,
with finite-stage conilpotence preserved.  The coproduct on \(C_X\) is the
inverse limit of the finite \(\Delta_R^{\mathrm{ch}}\).  The
quasi-isomorphisms \(b_{X,R}\) and \(\Theta_{\mathrm{Kos},R}\) commute
with the transition maps.  The Koszul Mittag--Leffler condition kills
the \(R^1\varprojlim\) obstruction on their cones, hence these compatible
finite quasi-isomorphisms pass to completed quasi-isomorphisms.  Without
that exactness one obtains only a compatible pro-quasi-isomorphism.  The
final sentence is the
definition of the certificate: the source object, mixed correspondences,
orientation, primitive presentation, and source/target-separation datum
are separate entries of \(\mathfrak K_X\).
\end{proof}

\begin{remark}[Locality]
In a compact realization, the required local object would be a
finite-stage holomorphic \(E_3\)-factorization algebra on \(X\), and its
\(K3\)-specialization would be a finite-stage chiral factorization
algebra on \(\operatorname{Ran}(E)\).  This assertion is local only for
projection-finite sectors over \(E\).  The automorphic product is a
protected global trace after charge completion, wall-chamber choice, and
summation over compact \(K3\)-modes.  Duality monodromy, elliptic-degree
wrapping, and the Borcherds chamber are therefore global features of the
trace.  They do not replace the local factorization maps on disjoint
opens.
Singular \(K3\) surfaces and nodal or cuspidal elliptic curves require
the boundary degeneration certificate; the Ran-local statement here is
the smooth-\(S\), smooth-\(E\) compact-stage assertion.
\end{remark}

\begin{definition}[Projection-finite, wrapped, and hybrid Ran strata]
\label{def:projection-finite-wrapped-sectors}
Let \(p_E:K3\times E\to E\) be projection.  A compact Hall or chiral
sector is projection-finite over \(E\) if every object \(A\) in it
satisfies
\[
p_E(\operatorname{Supp}A)\subset F
\]
for some finite subset \(F\subset E\).  A one-dimensional sector is
wrapped over \(E\) if its curve class has positive elliptic degree, i.e.
if the pushforward of its one-cycle to \(E\) is \(b[E]\) with \(b>0\).
For such one-dimensional Hall sectors write
\[
b(A)=\deg (p_E)_*[\operatorname{Supp}_1 A]\in\Z_{\ge0}.
\]
The same letter \(b(\gamma)\) denotes the elliptic-degree component of a
charge \(\gamma\).  Then projection-finite objects have \(b(A)=0\), while
wrapped objects have \(b(A)>0\).

The hybrid base used below is a finite-stage coloured correspondence
base, not an ordinary Ran space with one scalar attached.  At height
\(R\), after the certificate below is supplied, an object consists of a
finite projection-local support \(F\subset E\), finitely many wrapped
colours \(\eta_j\in\Gamma_R^{\mathrm{wr}}\), and rigidified wrapped
objects \(W_j\) carrying anchor values
\(\lambda_{\eta_j,R}(W_j)\in E\).  Its arrows are generated by finite
collisions of \(F\), by extension of local colours, by mixed
local/wrapped correspondences, and by wrapped/wrapped correspondences.
The notation \(\operatorname{Ran}^{\mathrm{hyb}}(E)\) denotes this
finite-coloured system through the inverse system in \(R\).  Its
underlying degree shadow is the displayed disjoint union
\[
\operatorname{Ran}^{\mathrm{hyb}}(E)
=\bigsqcup_{b\ge0}\operatorname{Ran}(E)_{[b]},
\qquad
\operatorname{Ran}(E)_{[b]}:=\operatorname{Ran}(E)\times\{b\}.
\]
The stratum \(b=0\) is the ordinary finite-support Ran stratum.  A
stratum \(b>0\) records finite local collision points together with a
global wrapped elliptic leg of degree \(b\); it is not an assertion that
the wrapped support is finite over \(E\).
\end{definition}

\begin{lemma}[Projection-to-\(E\) support-locality obstruction]
\label{lem:projection-e-support-locality-obstruction}
\label{lem:elliptic-degree-locality-obstruction}
Let \(C\subset K3\times E\) be a one-dimensional subscheme whose curve
class has positive elliptic degree:
\[
(p_E)_*[C]=b[E],\qquad b>0.
\]
Then \(p_E(C)=E\).  In particular, \(C\) is not localized at finitely
many points of \(E\), and it is not contained in \(p_E^{-1}(U)\) for any
proper open \(U\subsetneq E\).
\end{lemma}

\begin{proof}
If \(p_E(C)\) were zero-dimensional, then the pushforward of the
one-cycle \([C]\) to the curve \(E\) would vanish.  This contradicts
\((p_E)_*[C]=b[E]\) with \(b>0\).  Hence \(p_E(C)\) is a
one-dimensional closed subset of the irreducible curve \(E\), since
\(p_E\) is proper, and therefore \(p_E(C)=E\).
\end{proof}

\begin{corollary}[Naive Ran locality misses the elliptic-degree direction]
\label{cor:ranE-locality-misses-elliptic-degree}
A support-local factorization algebra on \(\operatorname{Ran}(E)\),
defined only by separating supports over disjoint opens of \(E\), sees
the projection-finite sector.  It does not by itself realize the full
\(s\)-direction of the Igusa product.
\end{corollary}

\begin{proof}
The variable \(s\) is the Borcherds variable corresponding to the
OP elliptic-degree direction in Proposition~\ref{prop:op-normalization}.
By Lemma~\ref{lem:projection-e-support-locality-obstruction}, positive
elliptic degree projects onto all of \(E\).  Such objects cannot be
separated by choosing disjoint opens in \(E\).  Therefore ordinary
support-local factorization on \(\operatorname{Ran}(E)\) has no
locality mechanism for the wrapped elliptic-degree sector.
\end{proof}

\begin{definition}[Finite hybrid local/wrapped factorization certificate]
\label{def:hybrid-wrapped-factorization-certificate}
Fix \((\sigma,S,R)\) as in
Definition~\ref{def:compact-e3-source-interface}.  A finite-stage hybrid
local/wrapped factorization certificate is a datum
\[
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
=
\left(
\mathcal C_{\sigma,S,\le R},\,
b_R,\,
\mathcal F_{R}^{\mathrm{loc}},\,
\mathcal G_{R}^{\mathrm{wr}},\,
\mathfrak E_R^{\mathrm{loc}},\,
\mathfrak E_R^{\mathrm{hyb}},\,
\mathfrak E_R^{\mathrm{wr}},\,
\mathfrak{Flag}_R^{\mathrm{hyb}},\,
\mathsf{Corr}^{E,\mathrm{hyb}}_R,\,
\lambda_R,\,
Q_{E,R},\,
\theta^Q_R,\,
o_R,\,
I_R^{\mathrm{prot}}
\right)
\]
with the following finite data and axioms.  Every stack, sheaf,
operation, and coherence named below lives at the fixed height \(R\); the
inverse limit appears only after all finite stages and transition maps
have been supplied.
\begin{enumerate}
\item \emph{Finite Hall stage and elliptic degree.}
\(\mathcal C_{\sigma,S,\le R}\) is a supplied extension-closed finite
charge-support HN quotient of the candidate compact Hall category, under
the finite-type hypothesis \textup{[K3\(\times\)E-fin]}, with finite-type
charge substacks
\(\mathfrak M_{\gamma,R}\) for
\(\gamma\in\Gamma_{\sigma,S}^{HN}(R)\), vanishing-cycle coefficients
\(\Phi_{\gamma,R}\), and orientation lines \(o_{\gamma,R}\).  The map
\[
b_R:\Gamma_{\sigma,S}^{HN}(R)\longrightarrow \Z_{\ge0}
\]
is the elliptic-degree component.  Write
\(\Gamma_R^{\mathrm{loc}}=\{\alpha\mid b_R(\alpha)=0\}\) and
\(\Gamma_R^{\mathrm{wr}}=\{\eta\mid b_R(\eta)>0\}\).  The ideal of height
\(>R\) is already killed at this stage, and all operations below are
understood to be zero when their output has height \(>R\).  The map
\(b_R\) is additive on extensions that remain in the quotient:
\[
b_R(0)=0,\qquad
b_R(\gamma+\gamma')=b_R(\gamma)+b_R(\gamma')
\]
whenever \(\gamma,\gamma',\gamma+\gamma'\in
\Gamma_{\sigma,S}^{HN}(R)\); if the sum has height \(>R\), the
corresponding operation is zero in the finite quotient.

\item \emph{Projection-finite local sector.}  For \(U\subset E\) open and
\(\alpha\in\Gamma_R^{\mathrm{loc}}\),
\[
\mathcal M_{\alpha,R}^{\mathrm{loc}}(U)
=
\left\{
A\in\mathfrak M_{\alpha,R}\ \middle|\
p_E(\operatorname{Supp}A)\subset U
\right\}
\]
is supplied as an open substack of \(\mathfrak M_{\alpha,R}\), and
\[
\mathcal F_{\alpha,R}^{\mathrm{loc}}(U)
:=
H_*^{\mathrm{BM}}\!\left(
\mathcal M_{\alpha,R}^{\mathrm{loc}}(U),
\Phi_{\alpha,R}^{\mathrm{loc}}\otimes o_{\alpha,R}^{\mathrm{loc}}
\right).
\]
The direct sum over \(\alpha\in\Gamma_R^{\mathrm{loc}}\) is
\(\mathcal F_R^{\mathrm{loc}}(U)\).  For disjoint opens this is an ordinary
projection-finite Ran factorization object.

\item \emph{Wrapped prequotient sector and rigidification.}  For
\(\eta\in\Gamma_R^{\mathrm{wr}}\), a prequotient stack
\[
\mathcal M_{\eta,R}^{\mathrm{wr,rig}}
\xrightarrow{\ \rho_{\eta,R}\ }
\mathcal M_{\eta,R}^{\mathrm{wr}}
\subset\mathfrak M_{\eta,R}
\]
is supplied, together with a fixed origin \(0_E\in E\) and an
\(E\)-equivariant anchor
\[
\lambda_{\eta,R}:\mathcal M_{\eta,R}^{\mathrm{wr,rig}}\longrightarrow E,
\qquad
\lambda_{\eta,R}(t\cdot W)=t+\lambda_{\eta,R}(W),
\]
where \(+\) is the group law on \(E\) with respect to the chosen origin.
The origin \(0_E\) is part of the supplied datum and is fixed once globally
in the certificate; a different choice of origin shifts \(\lambda_{\eta,R}\)
by a constant and the anchor descends to a \(\mathrm{Pic}^0(E)\)-torsor whose
zero point is the fixed datum.  Its objects have support dominating \(E\).
The pair \((\rho_{\eta,R},\lambda_{\eta,R})\) is a supplied
rigidification, not a canonical construction.  A natural candidate is the
normalized determinant
\[
\lambda(A)=\det Rp_{E,*}A\otimes\mathcal O_E(-\chi(A)\cdot 0_E)
\in \operatorname{Pic}^0(E)\simeq E .
\]
This candidate has translation weight \(\chi(A)\):
\[
\lambda(t\cdot A)=\lambda(A)+\chi(A)t .
\]
Thus it gives the required unit-weight anchor only on strata where this
weight has been rigidified, divided by a chosen finite cover, or replaced
by an equivalent Abel--Jacobi/framing datum.  In particular, on
\(\chi(A)=0\) strata it does not by itself remember the relative
\(E\)-position.  The anchor residual is therefore a typed finite datum,
not a name:
\[
\mathfrak o^\lambda_R=
\left(
\mathfrak o^{\lambda,\mathrm{ex}}_R,\
\mathfrak o^{\lambda,\mathrm{unit}}_R,\
\mathfrak o^{\lambda,\mathrm{loss}}_R,\
\mathfrak o^{\lambda,\mathrm{multi}}_R,\
\mathfrak o^{\lambda,\mathrm{tr}}_{R'R}
\right).
\]
These components assert, respectively, existence of the rigidified
prequotient and anchor; unit translation law, possibly after a specified
finite cover; losslessness of the anchor on the relative \(E\)-position
needed by wrapped correspondences; compatibility of the input,
intermediate, and output anchors on mixed and wrapped flag stacks; and
compatibility under successor HN transitions.  The certificate requires
the chosen anchor, its translation law, and the vanishing of all components
of \(\mathfrak o^\lambda_R\) as finite data.  Put
\[
\mathcal G_{\eta,R}^{\mathrm{wr}}
:=
H_*^{\mathrm{BM}}\!\left(
\mathcal M_{\eta,R}^{\mathrm{wr,rig}},
\Phi_{\eta,R}^{\mathrm{wr}}\otimes o_{\eta,R}^{\mathrm{wr}}
\right),
\qquad
\mathcal G_R^{\mathrm{wr}}:=\bigoplus_{\eta\in\Gamma_R^{\mathrm{wr}}}
\mathcal G_{\eta,R}^{\mathrm{wr}}.
\]
If no such prequotient memory is supplied, the wrapped part of the
certificate is absent.

\item \emph{Local, mixed, and wrapped extension correspondences.}  For
disjoint opens
\((U_i)\subset E\), local charges \(\alpha_i\), and wrapped charges
\(\eta,\eta_1,\eta_2\), the finite stage contains correspondences
\[
\prod_i\mathcal M_{\alpha_i,R}^{\mathrm{loc}}(U_i)
\xleftarrow{\ p\ }
\mathfrak E_{\alpha_1,\ldots,\alpha_r,R}^{\mathrm{loc}}(U_1,\ldots,U_r)
\xrightarrow{\ q\ }
\mathcal M_{\sum_i\alpha_i,R}^{\mathrm{loc}}\!\left(\bigcup_iU_i\right),
\]
\[
\prod_i\mathcal M_{\alpha_i,R}^{\mathrm{loc}}(U_i)
\times\mathcal M_{\eta,R}^{\mathrm{wr,rig}}
\xleftarrow{\ p\ }
\mathfrak E_{\alpha_1,\ldots,\alpha_r;\eta,R}^{\mathrm{hyb}}
(U_1,\ldots,U_r)
\xrightarrow{\ q\ }
\mathcal M_{\eta+\sum_i\alpha_i,R}^{\mathrm{wr,rig}},
\]
and
\[
\mathcal M_{\eta_1,R}^{\mathrm{wr,rig}}
\times\mathcal M_{\eta_2,R}^{\mathrm{wr,rig}}
\xleftarrow{\ p\ }
\mathfrak E_{\eta_1,\eta_2,R}^{\mathrm{wr}}
\xrightarrow{\ q\ }
\mathcal M_{\eta_1+\eta_2,R}^{\mathrm{wr,rig}}.
\]
The second display is only the one-sided shorthand.  Since Hall
convolution is ordered, the datum contains, for every ordered mixed word
with local inputs on both sides of one wrapped input, correspondences
\[
\prod_{i\in I_-}\mathcal M_{\alpha_i,R}^{\mathrm{loc}}(U_i)
\times\mathcal M_{\eta,R}^{\mathrm{wr,rig}}
\times
\prod_{j\in I_+}\mathcal M_{\beta_j,R}^{\mathrm{loc}}(V_j)
\xleftarrow{\ p\ }
\mathfrak E_{\alpha_-;\eta;\beta_+,R}^{\mathrm{hyb}}
((U_i),(V_j))
\xrightarrow{\ q\ }
\mathcal M_{\eta+\sum_{i\in I_-}\alpha_i+
\sum_{j\in I_+}\beta_j,R}^{\mathrm{wr,rig}}.
\]
The displayed mixed correspondence above is the case \(I_+=\varnothing\).
The case \(I_-=\varnothing\) is the right local action on a wrapped
input.  Both are part of the certificate.  Similarly
\(\mathfrak E_{\eta_1,\eta_2,R}^{\mathrm{wr}}\) is ordered in
\((\eta_1,\eta_2)\); no symmetry of wrapped inputs is assumed unless an
extra symmetry datum is supplied.
The middle stacks classify exact triangles or exact sequences with the
displayed associated graded pieces.  They are constructed in the
unreduced \(E\)-equivariant theory, with proper-support or compact-support
witnesses for \(q\), admissibility witnesses for \(p^*\) and \(q_!\) on
the chosen vanishing-cycle/Borel--Moore theory, and Thom--Sebastiani
identifications for the coefficient systems.  For every generator
\(e\) among the local-local, ordered mixed, and wrapped-wrapped
correspondences, write
\[
\mathfrak o^{\mathrm{prop}}_{e,R},\qquad
\mathfrak o^{\mathrm{adm}}_{e,R},\qquad
\mathfrak o^{\mathrm{TS}}_{e,R}
\]
for the defects of proper-support, pull-push admissibility, and
Thom--Sebastiani compatibility.  Their aggregate defects in the three
families are
\[
\mathfrak o^{\mathrm{prop},\mathrm{LL}}_R,\qquad
\mathfrak o^{\mathrm{prop},\mathrm{mix}}_R,\qquad
\mathfrak o^{\mathrm{prop},\mathrm{WW}}_R.
\]
They vanish exactly when all pull-push maps used below are honest
finite-stage operations, not formal correspondences without a defined
pushforward.  The mixed stacks use the
anchor \(\lambda_{\eta,R}\) to remember the relative position between the
finite local supports \(U_i\) and the wrapped leg; replacing this memory
by a scalar Fock coefficient is not this datum.  The wrapped-wrapped
stacks are likewise anchored: before quotienting they carry the map
\[
\mathfrak E_{\eta_1,\eta_2,R}^{\mathrm{wr}}
\longrightarrow E\times E\times E,\qquad
\xi\longmapsto
\bigl(\lambda_{\eta_1,R}(W_1),
\lambda_{\eta_2,R}(W_2),
\lambda_{\eta_1+\eta_2,R}(W)\bigr),
\]
where \(W_1,W_2,W\) are the two inputs and the output of \(\xi\).  The
finite correspondence keeps this relation, not only the total degree
\(b_R(\eta_1+\eta_2)\).

These object stacks, extension stacks, and flag stacks generate a finite
\(E\)-equivariant correspondence category
\[
\mathsf{Corr}^{E,\mathrm{hyb}}_R.
\]
Its objects are the finitely many local and rigidified wrapped charge
stacks at height \(R\).  Its arrows are generated by the displayed
correspondences, with composition by derived fibre product and with every
summand of height \(>R\) identified with zero.  The flag stacks below are
the specified \(2\)-morphisms witnessing equality of the two composites.
The finite operation
maps are the displayed pull-push maps
\[
\mu_R^\bullet=q_!\circ\operatorname{TS}_R^\bullet\circ p^*,
\]
namely
\[
\mu_{\alpha_1,\ldots,\alpha_r,R}^{\mathrm{loc}}:
\bigotimes_i\mathcal F_{\alpha_i,R}^{\mathrm{loc}}(U_i)
\longrightarrow
\mathcal F_{\sum_i\alpha_i,R}^{\mathrm{loc}}\!\left(\bigcup_iU_i\right),
\]
\[
\mu_{\alpha_1,\ldots,\alpha_r;\eta,R}^{\mathrm{hyb}}:
\bigotimes_i\mathcal F_{\alpha_i,R}^{\mathrm{loc}}(U_i)
\otimes\mathcal G_{\eta,R}^{\mathrm{wr}}
\longrightarrow
\mathcal G_{\eta+\sum_i\alpha_i,R}^{\mathrm{wr}},
\]
and
\[
\mu_{\eta_1,\eta_2,R}^{\mathrm{wr}}:
\mathcal G_{\eta_1,R}^{\mathrm{wr}}\otimes
\mathcal G_{\eta_2,R}^{\mathrm{wr}}
\longrightarrow
\mathcal G_{\eta_1+\eta_2,R}^{\mathrm{wr}}.
\]
Equivalently, the unreduced finite hybrid object at height \(R\) is the
correspondence-module functor
\[
\mathcal B_R^{E,\mathrm{hyb}}:
\mathsf{Corr}^{E,\mathrm{hyb}}_R\longrightarrow \mathrm{Ch}_{\mathbb C}
\]
sending
\[
\mathcal M_{\alpha,R}^{\mathrm{loc}}(U)\longmapsto
\mathcal F_{\alpha,R}^{\mathrm{loc}}(U),\qquad
\mathcal M_{\eta,R}^{\mathrm{wr,rig}}\longmapsto
\mathcal G_{\eta,R}^{\mathrm{wr}},
\]
and sending a generator
\(e=(X\xleftarrow p\mathfrak E_e\xrightarrow qY)\) to
\[
\mathcal B_R^{E,\mathrm{hyb}}(e)
=q_!\circ\operatorname{TS}_{e,R}\circ p^*.
\]
This functor is defined only after the properness/admissibility defects
above vanish.  The reduced finite object is the quotient-after-
correspondence module
\[
\mathcal B_R^{\mathrm{red},\mathrm{hyb}}
:=Q_{E,R}\mathcal B_R^{E,\mathrm{hyb}}.
\]
The two-sided mixed correspondences give, in the same notation,
\[
\mu_{\alpha_-;\eta;\beta_+,R}^{\mathrm{hyb}}:
\bigotimes_{i\in I_-}\mathcal F_{\alpha_i,R}^{\mathrm{loc}}(U_i)
\otimes\mathcal G_{\eta,R}^{\mathrm{wr}}
\otimes
\bigotimes_{j\in I_+}\mathcal F_{\beta_j,R}^{\mathrm{loc}}(V_j)
\longrightarrow
\mathcal G_{\eta+\sum_i\alpha_i+\sum_j\beta_j,R}^{\mathrm{wr}}.
\]
An output with at least one wrapped input is wrapped.  The mixed
correspondence is also required to record the surviving terms in
\(\operatorname{RHom}(A,W)\) and \(\operatorname{RHom}(W,A)\) for local
\(A\) and wrapped \(W\); replacing it by a scalar global mode loses this
data.

\item \emph{Full flag associativity and coherence.}  Write
\(\mathrm L\) for a projection-finite local input and \(\mathrm W\) for a
rigidified wrapped input.  For every word
\[
w=(\epsilon_1,\epsilon_2,\epsilon_3)\in\{\mathrm L,\mathrm W\}^3
\]
and every compatible ordered triple of charges and local opens, the datum
contains a two-step flag stack
\[
\mathfrak{Flag}^{w}_{\xi_1,\xi_2,\xi_3,R}
\]
classifying filtrations with the prescribed associated graded pieces.
Here \(\mathfrak E_{\xi_i,\xi_j,R}\) means the corresponding ordered
local-local, mixed local/wrapped, or wrapped-wrapped extension stack from
the previous clause.  The flag stack carries comparison maps to the two
iterated correspondence fibre products
\[
\mathfrak E_{\xi_1,\xi_2,R}
\times_{\mathcal M_{\xi_1+\xi_2,R}}
\mathfrak E_{\xi_1+\xi_2,\xi_3,R},
\qquad
\mathfrak E_{\xi_2,\xi_3,R}
\times_{\mathcal M_{\xi_2+\xi_3,R}}
\mathfrak E_{\xi_1,\xi_2+\xi_3,R}.
\]
The eight words
\[
\mathrm{LLL},\ \mathrm{LLW},\ \mathrm{LWL},\ \mathrm{WLL},
\mathrm{LWW},\ \mathrm{WLW},\ \mathrm{WWL},\ \mathrm{WWW}
\]
are all part of the datum.  In the mixed and wrapped words the flag stack
retains the input, intermediate, and output anchors before quotienting by
\(E\).  The two parenthesizations give the same map in the finite
quotient:
\[
\mu_{\xi_1+\xi_2,\xi_3,R}
\circ(\mu_{\xi_1,\xi_2,R}\otimes 1)
=
\mu_{\xi_1,\xi_2+\xi_3,R}
\circ(1\otimes\mu_{\xi_2,\xi_3,R}).
\]
Here \(\mu\) means one of the displayed local, mixed, or wrapped maps.
The equality is required after vanishing cycles, Thom--Sebastiani
transport, orientation signs, and the quotient by height \(>R\).
Equivalently, the two pull-push maps are induced by the same
Borel--Moore class on the corresponding two-step flag stack.  This is a
finite-stage coherence axiom; no associativity is imported from the
completed inverse limit.
The defect class of this equality for the word \(w\) is denoted
\[
\mathfrak o^{\mathrm{assoc}}_{w,R}.
\]
The certificate requires \(\mathfrak o^{\mathrm{assoc}}_{w,R}=0\) for all
eight words, with the chosen \(2\)-morphisms satisfying the usual
four-input pentagon on the finite flag-of-flags stacks.
This eight-word atlas is the binary associativity subcertificate.  Full
hybrid factorization still requires the higher colored configuration
atlas, units, symmetry or ordering conventions, refinement maps, descent,
and overlap coherences for all finite HN windows.  None of these follows
from the eight displayed length-three words.

\item \emph{Reduced \(E\)-quotient order.}  All stacks and
correspondences above are \(E\)-equivariant before quotienting.  Let
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\) and
\(\mathsf{Corr}^{\mathrm{red},\mathrm{hyb}}_R\) denote the finite
unreduced and reduced correspondence bicategories generated by these
stacks, correspondences, and flag diagrams.  The quotient datum first
supplies a pseudofunctor between these bicategories, with coherent
\(2\)-morphisms for composition, base-change, and Thom--Sebastiani
transport.  Applying vanishing-cycle Borel--Moore chains, with the
orientation lines included, gives the finite correspondence module
categories \(\mathsf{BM}^{E,\mathrm{hyb}}_R\) and
\(\mathsf{BM}^{\mathrm{red},\mathrm{hyb}}_R\).  The symbol \(Q_{E,R}\)
denotes the induced supplied functor
\[
Q_{E,R}:
\mathsf{BM}^{E,\mathrm{hyb}}_R
\longrightarrow
\mathsf{BM}^{\mathrm{red},\mathrm{hyb}}_R
\]
from the finite unreduced equivariant vanishing-cycle/Borel--Moore
category generated by the stacks above to the finite reduced category.
It is not only a map on object stacks.
It is allowed only after the local, wrapped, and mixed extension
correspondences have been formed and the chosen rigidification has either
descended or has been integrated out with a specified reduced kernel.
For every generator \(e\) of
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), the quotient package contains the
reduced correspondence \(\overline e\), the quotient maps from \(e\) to
\(\overline e\), admissibility witnesses for
\(\overline p^*\) and \(\overline q_!\), proper-support witnesses for
\(\overline q\), and orientation-descent isomorphisms for the coefficient
systems.  If the anchor is integrated out rather than descended, the
datum also contains the reduced kernel \(K_{\lambda,R}\) and its
compatibility with composition.  The quotient construction is therefore a
functor on the finite correspondence category, not a quotient of the
object spaces followed by a new Hall product.
For each operation \(\mu_R^\bullet=q_!\operatorname{TS}p^*\) the datum
contains a specified comparison isomorphism
\[
\theta^Q_{\mu,R}:\;
Q_{E,R}q_!\operatorname{TS}p^*
\xrightarrow{\ \sim\ }
\overline q_!\overline{\operatorname{TS}}\,\overline p^*
\bigl(Q_{E,R}^{\boxtimes k}\bigr),
\]
which is compatible with the flag-stack coherences.  The finite-stabilizer
gerbe classes needed for the orientation line must vanish on every stack
entering these squares.  For each two-step flag, the two composites of
\(\theta^Q_{\mu,R}\) agree with the descended flag \(2\)-morphism; for
\(R'\ge R\), the transition functors commute with \(Q_{E,R}\) through a
specified natural isomorphism.  A quotient-first construction is not this
datum.
The four quotient residuals are
\[
\mathfrak o^{Q,\mathrm{form}}_R,\qquad
\mathfrak o^{Q,\mathrm{adm}}_R,\qquad
\mathfrak o^{Q,\mathrm{flag}}_R,\qquad
\mathfrak o^{Q,\mathrm{tr}}_{R'R}.
\]
They record, respectively, existence of the functor \(Q_{E,R}\) on the
finite correspondence category, admissibility/properness after quotient,
compatibility with all flag \(2\)-morphisms, and compatibility with HN
transition maps.  The certificate requires their vanishing and chosen
null-homotopies.

\item \emph{Protected integration and the Igusa \(s\)-direction.}  The
finite stage carries a protected integration map
\[
I_R^{\mathrm{prot}}:
Q_{E,R}\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\longrightarrow
\C[\Gamma_{\mathrm{eff}}]_{\le R}
\]
where the subscript denotes the image of the finite \(h_S\)-box.  The map
is compatible with the three reduced products
\(\overline\mu_R^\bullet\), coproducts, primitive projection, and
transition maps.  This means a chain-level character of the finite
reduced correspondence algebra, not only the assignment of an
\(s\)-degree.  Let \(m_{\Gamma,R}\), \(\Delta_{\Gamma,R}\), and
\(P_{\Gamma,R}^{\Prim}\) denote the finite target multiplication,
coproduct, and primitive projector on the chosen decategorified monomial
model.  The integration defects are
\[
\mathfrak o^{I,\mathrm{ch}}_R:=I_R^{\mathrm{prot}}d_R,
\]
\[
\mathfrak o^{I,\mathrm{prod}}_{w,R}:=
I_R^{\mathrm{prot}}\overline\mu^w_R
-m_{\Gamma,R}(I_R^{\mathrm{prot}})^{\otimes k},
\qquad w\in\{\mathrm L,\mathrm W\}^k,
\]
\[
\mathfrak o^{I,\mathrm{co}}_R:=
\Delta_{\Gamma,R}I_R^{\mathrm{prot}}
-(I_R^{\mathrm{prot}}\otimes I_R^{\mathrm{prot}})\overline\Delta_R,
\qquad
\mathfrak o^{I,\Prim}_R:=
P_{\Gamma,R}^{\Prim}I_R^{\mathrm{prot}}
-I_R^{\mathrm{prot}}P_R^{\Prim}.
\]
They are required to vanish, compatibly with \(Q_{E,R}\), the orientation
trivializations, and transitions in \(R\).  Equivalently, for every
reduced operation \(\overline\mu_R^w\) and homogeneous inputs \(x_i\) of
charges \(\gamma_i\),
\[
I_R^{\mathrm{prot}}
\bigl(\overline\mu_R^w(x_1,\ldots,x_k)\bigr)
=
\prod_i I_R^{\mathrm{prot}}(x_i)
\]
whenever the product is defined at height \(R\); if the output charge has
height \(>R\), both sides are zero in the finite quotient.  If a
homogeneous class \(x\) has charge \(\gamma\), and
\(\mathcal F_{\gamma,R}^{\mathrm{hyb}}\) denotes the corresponding local
or wrapped summand, then every nonzero monomial in
\(I_R^{\mathrm{prot}}(Q_{E,R}x)\) has \(s\)-degree \(b_R(\gamma)\):
\[
I_R^{\mathrm{prot}}(Q_{E,R}x)
\in
s^{\,b_R(\gamma)}\C[q^{\pm1},r^{\pm1}]
\]
under the OP/Borcherds variable convention of
Proposition~\ref{prop:op-normalization}.  More precisely,
\(I_R^{\mathrm{prot}}\) is homogeneous for the full Gram label
\(\overline\Pi_X(\gamma)=(n,l,m)\), and the displayed condition records
the elliptic degree \(m=b_R(\gamma)\).  Thus positive powers of the
Igusa \(s\)-variable can only come from the wrapped colour \(b_R>0\).
This is a source-support condition, not a consequence of the target
product.  If a target window contains a degree with \(m>0\), and in
particular the test degree \(\delta_2\leftrightarrow(0,1,1)\), the finite
stage must contain a wrapped source summand mapping to that degree under
\(\overline\Pi_X\).  Otherwise the coefficient lies outside the verified
compact source image.
For products, the displayed character law and additivity of \(b_R\) give
\[
s^{b_R(\gamma_1+\cdots+\gamma_k)}
=
\prod_i s^{b_R(\gamma_i)}
\]
inside the finite HN quotient.  Hence the \(s\)-direction is coupled to
the actual local/wrapped operation, not appended as an external Fock
determinant.
For \(R'\ge R\), let
\(\tau^{E,\mathrm{hyb}}_{R'R}\) be the unreduced finite hybrid transition,
let
\[
\bar\tau^{\mathrm{hyb}}_{R'R}:
Q_{E,R'}\mathcal F_{X,\sigma,S,\le R'}^{\mathrm{hyb}}
\longrightarrow
Q_{E,R}\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\]
be the induced reduced chain map, and let \(\pi^\Gamma_{R'R}\) be the
induced truncation of the monomial target.
The integration transition defect is
\[
\mathfrak o^{I,\mathrm{tr}}_{R'R}:=
I_R^{\mathrm{prot}}\bar\tau^{\mathrm{hyb}}_{R'R}
-\pi^\Gamma_{R'R}I_{R'}^{\mathrm{prot}}Q_{E,R'}.
\]
It is required to vanish.  Thus protected integration is compatible
with the HN inverse system, not merely with one finite trace.
The coefficient of a monomial \(q^nr^ls^{b_R(\gamma)}\) is a protected
finite-stage trace coefficient.  Equality of these coefficients with the
Borcherds exponents \(f(nm,l)\), and the primitive
Borcherds--Kac--Moody bracket test, are additional recognition
requirements, not part of the definition.

\item \emph{Hybrid residual tuple.}
The exact finite obstruction tuple for the hybrid lane is
\[
\mathfrak O_{\mathrm{hyb},R}
=
\left(
\mathfrak o^{\mathrm{stage}}_R,\,
\mathfrak o^{\lambda}_R,\,
\mathfrak o^{\mathrm{corr},\mathrm{LL}}_R,\,
\mathfrak o^{\mathrm{corr},\mathrm{mix}}_R,\,
\mathfrak o^{\mathrm{corr},\mathrm{WW}}_R,\,
\mathfrak o^{\mathrm{prop},\mathrm{LL}}_R,\,
\mathfrak o^{\mathrm{prop},\mathrm{mix}}_R,\,
\mathfrak o^{\mathrm{prop},\mathrm{WW}}_R,\,
\{\mathfrak o^{\mathrm{assoc}}_{w,R}\}_{w\in\{\mathrm L,\mathrm W\}^3},\,
\mathfrak o^{\mathrm{col}}_R,\,
\mathfrak o^{Q,\mathrm{form}}_R,\,
\mathfrak o^{Q,\mathrm{adm}}_R,\,
\mathfrak o^{Q,\mathrm{flag}}_R,\,
\mathfrak o^{Q,\mathrm{tr}}_{R'R},\,
\mathfrak o^{I,\mathrm{ch}}_R,\,
\{\mathfrak o^{I,\mathrm{prod}}_{w,R}\}_{w},\,
\mathfrak o^{I,\mathrm{col}}_R,\,
\mathfrak o^{I,\mathrm{co}}_R,\,
\mathfrak o^{I,\Prim}_R,\,
\mathfrak o^{I,\mathrm{tr}}_{R'R},\,
\mathfrak o^{\mathrm{tr}}_{\mathrm{hyb},R'R}
\right).
\]
These entries record finite HN existence, anchor rigidification,
local-local correspondences, all ordered mixed correspondences,
wrapped-wrapped correspondences, properness/admissibility and
Thom--Sebastiani validity for the pull-push operations, the eight-word
two-step binary flag coherence, the higher colored configuration
residual, quotient formation/admissibility/flag and transition descent,
chain/product/colored-refinement/coproduct/primitive integration laws, integration
transition compatibility, and HN transition compatibility.  A finite
hybrid certificate means the compatible vanishing and trivialization of
this tuple for every \(R'\ge R\).  Without
\(\mathfrak O_{\mathrm{hyb},R}=0\), the notation
\(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\) names an obstruction
problem, not a source object.
The entry \(\mathfrak o^{\mathrm{col}}_R\) records the higher colored
configuration atlas, unit and vacuum maps, symmetry or ordering
conventions, refinement maps, descent, and overlap coherences not detected
by the eight length-three words.  If this entry is not supplied, vanishing
of the remaining binary terms gives only the two-step Hall/module
certificate, not a full hybrid factorization object.
The entry \(\mathfrak o^{I,\mathrm{col}}_R\) records compatibility of
protected integration with the higher colored configuration atlas and its
refinement maps; binary product compatibility does not imply this
colored-refinement integration law.

\item \emph{Finite HN completion.}  The construction is made only for
charges in \(\Gamma_{\sigma,S}^{HN}(R)\).  For \(R'\ge R\), transition
maps
\[
\tau^{E,\mathrm{hyb}}_{R'R}:
\mathcal F_{X,\sigma,S,\le R'}^{\mathrm{hyb}}
\longrightarrow
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\]
must be induced by functors
\(\mathsf{Corr}^{E,\mathrm{hyb}}_{R'}\to
\mathsf{Corr}^{E,\mathrm{hyb}}_R\) compatible with all three kinds of
correspondences, with the flag associativity constraints, with the
rigidifying anchors, with \(Q_{E,R}\), with the comparison isomorphisms
\(\theta^Q_R\), and with protected integration.  They preserve elliptic
degree: if a homogeneous
summand of charge \(\gamma'\) at height \(R'\) maps to a nonzero summand
of charge \(\gamma\) at height \(R\), then
\[
b_R(\gamma)=b_{R'}(\gamma').
\]
The transition residual
\(\mathfrak o^{\mathrm{tr}}_{\mathrm{hyb},R'R}\) is the joint defect of
object truncation, correspondence base-change, flag/pentagon coherence,
anchor compatibility, and the induced chain map
\[
\bar\tau^{\mathrm{hyb}}_{R'R}:
\mathcal B_{R'}^{\mathrm{red},\mathrm{hyb}}
\longrightarrow
\mathcal B_R^{\mathrm{red},\mathrm{hyb}} .
\]
\end{enumerate}
When all finite stages and transitions have been supplied, the completed
hybrid object is
\[
\mathcal F_X^{\mathrm{hyb}}
:=
\varprojlim_R\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}.
\]
It is the charge-completed hybrid source specified by those finite
certificates over \(\operatorname{Ran}^{\mathrm{hyb}}(E)\).  Its
restriction to
\(\operatorname{Ran}(E)_{[0]}\) is ordinary projection-finite Ran
factorization.  Its \(b>0\) strata are wrapped modules acted on by the
local sector through the mixed Hall correspondences.  This inverse-limit
formula is a construction from the displayed finite certificates; it is
not an existence theorem for those certificates.
\end{definition}

\begin{proposition}[Finite consequences of the hybrid certificate]
\label{prop:hybrid-certificate-scope}
Assume the finite-stage data of
Definition~\ref{def:hybrid-wrapped-factorization-certificate} are
supplied for all \(R\), with compatible transition maps.  Then:
\begin{enumerate}
\item the \(b=0\) restriction is an ordinary support-local factorization
object on \(\operatorname{Ran}(E)\);
\item every operation with a wrapped input lands in a wrapped stratum;
\item the displayed ordered mixed maps, including the two-sided maps
\(\mu_{\alpha_-;\eta;\beta_+,R}^{\mathrm{hyb}}\), define the only
available Hall actions of projection-finite insertions on wrapped
elliptic-degree sectors in
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\) before the reduced \(E\)-quotient;
\item vanishing of the properness/admissibility defects
\(\mathfrak o^{\mathrm{prop},\mathrm{LL}}_R\),
\(\mathfrak o^{\mathrm{prop},\mathrm{mix}}_R\), and
\(\mathfrak o^{\mathrm{prop},\mathrm{WW}}_R\) makes the Borel--Moore
pull-push functor \(\mathcal B_R^{E,\mathrm{hyb}}\) and its reduced
quotient \(\mathcal B_R^{\mathrm{red},\mathrm{hyb}}\) well-defined;
\item vanishing of the eight classes
\(\mathfrak o^{\mathrm{assoc}}_{w,R}\) gives an associative finite-stage
reduced Hall product after vanishing cycles, orientations, HN quotienting,
the quotient functor, and the comparison isomorphisms
\(\theta^Q_{\mu,R}\);
\item a protected trace or primitive bracket obtained from this object is
compatible with reduced \(E\)-integration only through the specified
\(Q_{E,R}\)-compatibility isomorphisms, their flag coherences,
finite-stabilizer conditions, and the vanishing of the integration
defects
\(\mathfrak o^{I,\mathrm{ch}}_R\),
\(\mathfrak o^{I,\mathrm{prod}}_{w,R}\),
\(\mathfrak o^{I,\mathrm{col}}_R\),
\(\mathfrak o^{I,\mathrm{co}}_R\), and
\(\mathfrak o^{I,\Prim}_R\), compatibly with
\(\mathfrak o^{I,\mathrm{tr}}_{R'R}=0\);
\item for homogeneous
\(x\in Q_{E,R}\mathcal F_{\gamma,R}^{\mathrm{hyb}}\),
\[
I_R^{\mathrm{prot}}(x)\in
s^{b_R(\gamma)}\C[q^{\pm1},r^{\pm1}],
\]
hence the positive \(s\)-direction cannot be supplied by the
projection-finite Ran stratum; on products this law is multiplicative
because \(b_R\) is additive inside the finite quotient.
\end{enumerate}
A decoupled global Fock or Hecke factor without
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), anchored mixed correspondences,
proper pull-push operations, the eight-word two-step binary flag atlas
with the higher colored residual \(\mathfrak o^{\mathrm{col}}_R\),
quotient residuals, and
protected-integration residuals may reproduce a
determinant-level product, but it does not define the local-wrapped
primitive brackets needed for recognition of \(\mathfrak g_{\Delta_5}\).
\end{proposition}

\begin{proof}
The first two assertions are built into the elliptic-degree stratification
and Lemma~\ref{lem:projection-e-support-locality-obstruction}.  The third
assertion is the definition of the mixed operation maps: before the
reduced quotient they are the only displayed operations remembering
relative \(E\)-position between finite local support and a wrapped leg,
including the left and right ordered actions.  The properness assertion is
exactly the vanishing of the generator-wise proper-support,
admissibility, and Thom--Sebastiani defects.  The flag assertion is
exactly the eight-word two-step binary flag axiom transported through
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), with higher colored factorization
kept in the separate residual \(\mathfrak o^{\mathrm{col}}_R\).  The
quotient assertion is the quotient-order
axiom, the coherent comparison isomorphism \(\theta^Q_{\mu,R}\), and the
vanishing of the quotient residuals.  The last statement is the degree
law and character property in the protected integration clause, together
with the vanishing of the named integration defects and their transition
residual.
No compact source object, orientation system, quotient functor, or
protected integration map is constructed in this proposition.
\end{proof}

\begin{corollary}[No quotient-first universal hybrid repair]
\label{cor:no-quotient-first-hybrid-repair}
Fix \(R\).  A candidate finite correspondence category for the
wrapped sector gives the source object
\(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\) only if it contains the
unreduced local, wrapped, and ordered mixed source stacks of
Definition~\ref{def:hybrid-wrapped-factorization-certificate}, their
anchors, the eight-word flag atlas, the quotient functor \(Q_{E,R}\)
formed after those correspondences, the comparison maps
\(\theta^Q_{\mu,R}\), and protected integration with all entries of
\(\mathfrak O_{\mathrm{hyb},R}\), including its transition entries,
trivialized.  A quotient of object stacks formed before the mixed and
wrapped correspondences, or a determinant/Fock category carrying only
the trace degree \(s^{b_R}\), does not define the hybrid source.
\end{corollary}

\begin{proof}
By Lemma~\ref{lem:projection-e-support-locality-obstruction}, a positive
elliptic-degree sector is not a finite-support Ran sector.  The only
displayed mechanism retaining its relative \(E\)-position is the
rigidified wrapped prequotient with anchor, together with the unreduced
mixed and wrapped correspondences.  If one quotients first, these
anchors are no longer available as source data for
\(\mathfrak E_R^{\mathrm{hyb}}\), the two-sided maps
\(\mu_{\alpha_-;\eta;\beta_+,R}^{\mathrm{hyb}}\), or the flag
\(2\)-morphisms.  Then \(Q_{E,R}\), \(\theta^Q_{\mu,R}\), and the
product, coproduct, primitive, and transition integration residuals are
not defined as finite source data.  A scalar determinant or Fock trace
can record coefficients after decategorification; it cannot supply the
correspondence-level primitive brackets required by the certificate.
\end{proof}

\begin{proposition}[\textup{(O2)}/hybrid compatibility obstruction]
\label{prop:o2-hybrid-compatibility-obstruction}
Fix a finite HN height \(R\) and one of the three type-II simple walls.
Under the degree map
\(\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}\) the wall labels are
\[
\begin{array}{c|c|c}
\hbox{wall} & (n,l,m) & \hbox{elliptic-degree shadow}\\
\hline
\delta_1=2f_2-f_3 & (1,1,0) & m=0\\
\delta_2=2f_{-2}-f_3 & (0,1,1) & m=1\\
\delta_3=f_3 & (0,-1,0) & m=0 .
\end{array}
\]
A finite compact construction which claims both the hybrid source
\(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\) of
Definition~\ref{def:hybrid-wrapped-factorization-certificate} and the
type-II Pfaffian wall model of
Definition~\ref{def:type-ii-pfaffian-wall-certificate} must supply a
compatibility package at the same height \(R\).  It consists of:
\begin{enumerate}
\item a wall object \(x_{\delta_i,R}\) in the finite local or rigidified
wrapped moduli used by
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), mapping to Gram degree
\(\delta_i\);
\item a finite restriction of the unreduced hybrid deformation theory to
the wall object, producing a self-Ext complex \(K^E_{\delta_i,R}\);
\item a quotient-compatible comparison diagram
\[
\begin{tikzcd}
\mathsf{BM}^{E,\mathrm{hyb}}_R
  \arrow[r,"\ell_{\delta_i,R}"]
  \arrow[d,"Q_{E,R}"']
&
K^E_{\delta_i,R}
  \arrow[r,"\operatorname{split}_{\delta_i,R}"]
  \arrow[d,"Q^K_{\delta_i,R}"]
&
K^{E,\mathrm{tan}}_{\delta_i,R}\oplus
K^{E,\mathrm{nor}}_{\delta_i,R}
  \arrow[d,"Q^{\mathrm{tan}}_{\delta_i,R}\oplus Q^{\mathrm{nor}}_{\delta_i,R}"]
\\
\mathsf{BM}^{\mathrm{red},\mathrm{hyb}}_R
  \arrow[r,"\overline\ell_{\delta_i,R}"']
&
K^{\mathrm{red}}_{\delta_i,R}
  \arrow[r,"\overline{\operatorname{split}}_{\delta_i,R}"']
&
K^{\mathrm{tan}}_{\delta_i,R}\oplus
K^{\mathrm{nor}}_{\delta_i,R},
\end{tikzcd}
\]
where the bottom row is the reduced wall chart of
Proposition~\ref{prop:o2-local-obstruction-certificate};
\item an invariant normal Pfaffian unit and rank-one normal model
\[
\operatorname{Pf}(K^{\mathrm{nor}}_{\delta_i,R})
=\upsilon_{\delta_i,R}u_{\delta_i,R},\qquad
s_{\delta_i}(\upsilon_{\delta_i,R})=\upsilon_{\delta_i,R},
\]
after the quotient orientation trivializations used by \(Q_{E,R}\);
\item protected integration compatibility:
if \(\operatorname{pf}_{\delta_i,R}\) is the local Pfaffian class of the
normal crossing, then every nonzero monomial of
\[
I_R^{\mathrm{prot}}\bigl(Q_{E,R}\operatorname{pf}_{\delta_i,R}\bigr)
\]
is supported on the full monomial \(q^nr^ls^m\) for the displayed Gram
label \((n,l,m)\), and the quotient-oriented Pfaffian sign is preserved
under \(s_{\delta_i}\).  This support and sign equality is compatible
with the transition residual \(\mathfrak o^{I,\mathrm{tr}}_{R'R}\).
\end{enumerate}
Equivalently, the finite residual
\[
\mathfrak O^{\mathrm{O2/hyb}}_{\delta_i,R}
=
\left(
\mathfrak o^{\mathrm{wall}}_{\delta_i,R},
\mathfrak o^{\mathrm{Ext}\text{-}\mathrm{split}}_{\delta_i,R},
\mathfrak o^{\mathrm{unit}}_{\delta_i,R},
\mathfrak o^{\mathrm{rank}}_{\delta_i,R},
\mathfrak o^{\mathrm{atlas,comp}}_{\delta_i,R},
\mathfrak o^{\mathrm{atlas,bdy}}_{\delta_i,R},
\mathfrak o^{\mathrm{atlas,ov}}_{\delta_i,R},
\mathfrak o^{Q,\mathrm{wall}}_{\delta_i,R},
\mathfrak o^{I,\mathrm{wall}}_{\delta_i,R}
\right)
\]
must be trivialized.  The \(\delta_2\) row has \(m=1\), hence its wall
object cannot be supplied by the projection-finite Ran stratum alone.
It must pass through the rigidified wrapped prequotient and the ordered
mixed correspondences before the reduced \(E\)-quotient.  A local
rank-one chart detached from
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), or a Fock/Hecke factor carrying only
the scalar \(s\)-degree, does not make this residual vanish.  For O2 this
compatibility must be imposed as a wall atlas: at finite height \(R\),
each retained component and boundary stratum of \(\Hpl_{\delta_i}\) needs
a chart of the above form, and the normal Pfaffian units, tangent/normal
splittings, quotient orientations, and protected integration maps must
agree on chart overlaps.  A single generic chart computes only a local
sign.
The atlas entries record, respectively, charts on every retained wall
component, charts on retained boundary strata, and agreement of normal
Pfaffian units, tangent/normal splittings, quotient orientations, and
protected integration maps on chart overlaps, compatibly with HN
transitions.
\end{proposition}

\begin{proof}
The three Gram labels are the inverse calculation recorded in the
type-II root section:
\[
\delta_1\leftrightarrow(1,1,0),\qquad
\delta_2\leftrightarrow(0,1,1),\qquad
\delta_3\leftrightarrow(0,-1,0).
\]
The local Pfaffian proposition requires a reduced wall chart, a reduced
self-Ext complex, a tangent/normal splitting, an invariant normal unit,
and \(N_{\delta_i}^{\mathrm{Pf}}=1\).  The hybrid certificate requires
unreduced local, wrapped, and ordered mixed correspondences, followed
only then by \(Q_{E,R}\) and by protected integration.  If both claims
are claims about the same compact source, the wall complex must be the
localization of the finite hybrid deformation theory and its splitting,
unit, quotient descent, and protected trace must commute with the hybrid
operations.  The displayed diagram and residual tuple are precisely this
finite compatibility requirement.

For \(\delta_2\) the target monomial has \(s\)-degree one.  By
Lemma~\ref{lem:projection-e-support-locality-obstruction}, positive
elliptic degree is not supported at finitely many points of \(E\).
Thus an ordinary projection-finite Ran object cannot supply the wall
object whose local Pfaffian class integrates to the \(\delta_2\) label.
The wrapped prequotient, its anchor, the mixed correspondences, and the
quotient-after-correspondence functor are not optional decoration; they
are the data needed even to state the compatibility of the local Pfaffian
calculation with the hybrid \(s\)-direction.
\end{proof}

\begin{openproblem}[Hybrid wrapped factorization]
\label{op:hybrid-wrapped-factorization}
Construct the finite-stage certificates
\(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\) of
Definition~\ref{def:hybrid-wrapped-factorization-certificate} and prove
that their inverse limit exists in the completed Hall/factorization
category.  The exact obstruction is the simultaneous construction of:
\begin{enumerate}
\item the compact extension-closed category and stability/HN sector whose
local and wrapped moduli are finite type in bounded \(h_S\)-height;
\item a rigidified wrapped prequotient
\(\mathcal M_{\eta,R}^{\mathrm{wr,rig}}\to
\mathcal M_{\eta,R}^{\mathrm{wr}}\) retaining relative \(E\)-position
without inserting a positive elliptic-degree object at a finite Ran point;
\item local-local, all ordered two-sided local-wrapped, and
wrapped-wrapped extension stacks
with admissible vanishing-cycle pull-push functors and proper-support
witnesses for the \(q\)-maps, equivalently vanishing of
\(\mathfrak o^{\mathrm{prop},\mathrm{LL}}_R\),
\(\mathfrak o^{\mathrm{prop},\mathrm{mix}}_R\), and
\(\mathfrak o^{\mathrm{prop},\mathrm{WW}}_R\);
\item Thom--Sebastiani-compatible strong orientations on all three kinds
of correspondences and on the eight-word two-step binary flag atlas,
proving the displayed parenthesization identities and the four-input
pentagon in finite HN quotients, with higher colored factorization kept as
a separate obligation;
\item descent through the reduced \(E\)-quotient after forming
correspondences, including the finite-stabilizer gerbe checks and the
\(Q_{E,R}\)-compatibility isomorphisms, with
\(\mathfrak o^{Q,\mathrm{form}}_R=
\mathfrak o^{Q,\mathrm{adm}}_R=
\mathfrak o^{Q,\mathrm{flag}}_R=
\mathfrak o^{Q,\mathrm{tr}}_{R'R}=0\);
\item protected integration whose decategorified trace sends elliptic
degree \(b\) to \(s^b\), recovers the Igusa \(s\)-direction
coefficientwise, vanishes on the chain/product/coproduct/primitive
defects \(\mathfrak o^{I,\bullet}_R\), has
\(\mathfrak o^{I,\mathrm{tr}}_{R'R}=0\) for all \(R'\ge R\), and whose
primitive bracket passes the Borcherds--Kac--Moody presentation test.
\end{enumerate}
Equivalently, one must trivialize
\(\mathfrak O_{\mathrm{hyb},R}\) for every finite HN height \(R\),
including the quotient, integration, and HN transition components for
every \(R'\ge R\).
Until these six items are supplied, \(\mathcal F_X^{\mathrm{hyb}}\) is a
finite categorical datum whose existence remains open, not a compact QFT
constructed in this paper and not a detached determinant factor.
Ordinary disjoint-open factorization on \(\operatorname{Ran}(E)\) is only
the projection-finite \(b=0\) part.
\end{openproblem}

\begin{openproblem}[Normal-ordered descent of the protected bracket]
\label{op:pi-descent-of-bracket}
Let \(\Gamma_X^{\mathrm{form}}=\La_S\oplus\La_S\),
\(\Pi_X:\Gamma_X^{\mathrm{form}}\to\Gamma_{\mathrm{gram}}\),
\(B:\Gamma_X^{\mathrm{form}}\times\Gamma_X^{\mathrm{form}}
\to\Gamma_{\mathrm{gram}}\) be as in
Definition~\ref{def:dyonic-mukai-lattice}.  Suppose a Hall lift
\(\widetilde P_X\) of the protected primitive algebra is supplied with a
\(\Gamma_{X,\sigma}^{\mathrm{eff}}\)-graded bracket, for a supplied
semigroup
\(\Gamma_{X,\sigma}^{\mathrm{eff}}\subset\Gamma_X^{\mathrm{alg}}\subset
\Gamma_X^{\mathrm{form}}\).  Construct a
cocycle-corrected descent \(\overline\Pi_{X,*}^{\Theta}\) categorifying the
normal-ordered homomorphism
\(\overline\Pi_X:\widehat\Gamma_X\to\Gamma_{\mathrm{gram}}\).  The raw
Hall bracket
is concentrated in additive charge \(c+c'\) inside the supplied effective
support, whose raw Gram shadow is
\[
\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c').
\]
The coefficient category, central translations, Hochschild cocycle
\(B_{\mathrm{ch}}\), and cochain
\(\Theta_\Pi(c)=\mathsf T_{-\Pi_X(c)}\) are those of
Definition~\ref{def:normal-ordering-coefficient-dg-category}.  The datum
\(\Theta_\Pi\) must lift the lattice identity
\[
d_{\mathrm{Hoch}}\Theta_\Pi=B
\]
to the chain identity
\[
d_{\mathrm{Hoch}}\Theta_\Pi=B_{\mathrm{ch}}
\]
in the Picard dg groupoid of central translations.  Its triple
homotopies must be compatible with the Hall extension correspondences,
the Joyce--Upmeier orientation cocycle, the Hopf pairing, the reduced
\(E\)-quotient, the finite fibre products over
\(\overline\Pi_X\), the completed HN tensor topology, and the
\(S^1\)-action on the cyclic complex.  Without such a lift, the raw
bracket has the wrong Gram degree and the ordinary pushforward along
\(\Pi_X\) is not a recognition target.
\end{openproblem}

\begin{definition}[Normal-ordering coefficient dg category]
\label{def:normal-ordering-coefficient-dg-category}
Fix a finite HN quotient \(R\) of the protected Hall sector, before
passing to the inverse limit.  Let
\[
\mathsf{Ch}_{k,R,E}^{\Gamma_{\mathrm{gram}}}
\]
be the dg category of \(\Gamma_{\mathrm{gram}}\)-graded complexes of
protected vanishing-cycle sheaves after the cosection-reduced
\(E\)-quotient, with differential preserving the Gram degree and with
support projected to the finite test window of the stage.  The transition
functors for \(R'\ge R\) are required to be strict continuous maps for the
HN filtration.  They define the completed separated dg category
\[
\mathsf{Ch}_{k,\widehat{\mathrm{HN}},E}^{\Gamma_{\mathrm{gram}}}
:=\varprojlim_R
\mathsf{Ch}_{k,R,E}^{\Gamma_{\mathrm{gram}}}.
\]
Every completed tensor product in this section is taken in this topology:
\[
V\widehat{\otimes}W:=\varprojlim_R(V_R\otimes W_R)
\]
for compatible finite stages.  No tensor product or coproduct is formed
directly on an unfiltered infinite direct sum.
For \(\eta\in\Gamma_{\mathrm{gram}}\) define the central translation
dg autoequivalence
\[
(\mathsf T_\eta V)_\gamma:=V_{\gamma+\eta},
\qquad
d_{\mathsf T_\eta V}=d_V .
\]
Then
\(\mathsf T_0=\mathrm{id}\) and
\(\mathsf T_\eta\mathsf T_{\eta'}=\mathsf T_{\eta+\eta'}\) strictly.
Let
\(\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\) denote the
Picard dg groupoid generated by these translations and their chain
homotopies.

For formal charges \(c,c'\in\Gamma_X^{\mathrm{form}}\) put
\[
B_{\mathrm{ch}}(c,c'):=\mathsf T_{B(c,c')}.
\]
This is the translation-valued Hochschild \(2\)-cocycle representing the
normal-ordering defect.  A chain-level normal-ordering datum is a
normalized \(1\)-cochain
\[
\Theta_\Pi(c)=\mathsf T_{-\Pi_X(c)}
\in
C^1_{\mathrm{Hoch}}\!
\bigl(\Gamma_X^{\mathrm{phys}};
\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\bigr)
\]
together with natural quasi-isomorphisms
\[
\vartheta_{c,c'}:
\mathsf T_{-\Pi_X(c)}
\mathsf T_{-\Pi_X(c')}
\mathsf T_{\Pi_X(c+c')}
\xrightarrow{\ \sim\ }
\mathsf T_{B(c,c')}.
\]
Equivalently,
\[
d_{\mathrm{Hoch}}\Theta_\Pi=B_{\mathrm{ch}}.
\]
The translation cochain itself is formal once the finite coefficient dg
category exists.  The non-formal datum is its realization on the compact
Hall correspondence targets, with orientation, quotient, cyclic, and HN
transition compatibility.
For a finite \(\Gamma_X^{\mathrm{phys}}\)-supported complex
\(V=\bigoplus_cV_c\), the uncompleted shorthand is
\[
(\overline\Pi_{*,\mathrm{fin}}^{\Theta}V)_\gamma
=\prod_{\Pi_X(c)=\gamma}V_c,
\]
with the product finite.  Its product and bracket structure is transported
by the \(\Theta_\Pi\)-quasi-isomorphisms.  Thus a raw bracket output in
charge \(c+c'\), whose Gram shadow is \(\Pi_X(c+c')\), is read after
\(\mathsf T_{B(c,c')}\) in degree
\[
\Pi_X(c+c')-B(c,c')=\Pi_X(c)+\Pi_X(c').
\]
At a finite stage the actual coefficient object is defined on
\(\widehat\Gamma_R\).  If
\[
V_R=\bigoplus_{(c,T)\in\widehat\Gamma_R} (V_R)_{(c,T)}
\]
is a finite \(\widehat\Gamma_R\)-graded complex, set
\[
(\overline\Pi_{R,*}^{\Theta}V_R)_\gamma
=
\prod_{\substack{(c,T)\in\widehat\Gamma_R\\
\overline\Pi_X(c,T)=\gamma}} (V_R)_{(c,T)}.
\]
This product is finite; when the fibre is empty it is \(0\).  The
\(\Gamma_X^{\mathrm{phys}}\)-graded formula above is only the special
case \(T=0\) before the counterterm has been recorded.  For a compatible
inverse system \(V=\varprojlim_R V_R\), the completed descent is
\[
(\overline\Pi_{X,*}^{\Theta}V)_\gamma
:=
\varprojlim_R(\overline\Pi_{R,*}^{\Theta_R}V_R)_\gamma .
\]
Thus a product over a fibre of \(\overline\Pi_X\) means an inverse limit
of finite fibre products.  The notation is not a licence to multiply over
an uncontrolled infinite fibre.  Products, brackets, coproducts, pairings,
and radical quotients after \(\overline\Pi_{X,*}^{\Theta}\) are defined
only when their finite-stage maps commute with the transition maps and
are continuous for the displayed HN completion.
\end{definition}

\begin{lemma}[Finite Picard normal-ordering lift]
\label{lem:finite-picard-normal-ordering-lift}
Fix a finite HN stage \(R\) for which the coefficient dg category of
Definition~\ref{def:normal-ordering-coefficient-dg-category} and the
finite set \(\widehat\Gamma_R\) are supplied.  Put
\[
\Theta_{\Pi,R}^{\mathrm{phys}}(c):=\mathsf T_{-\Pi_X(c)}
\qquad(c\in\Gamma_X^{\mathrm{phys}})
\]
and, after the counterterm \(T\) has been recorded,
\[
\widehat\Theta_{\Pi,R}(c,T)
:=\mathsf T_{-\overline\Pi_X(c,T)}
=\mathsf T_{T-\Pi_X(c)}
\qquad ((c,T)\in\widehat\Gamma_R).
\]
Then:
\begin{enumerate}
\item[\textup{(i)}] \(B_{\mathrm{ch},R}(c,c')=\mathsf T_{B(c,c')}\) is a
normalized Hochschild \(2\)-cocycle in the Picard dg groupoid of central
translations, and
\[
d_{\mathrm{Hoch}}\Theta_{\Pi,R}^{\mathrm{phys}}=B_{\mathrm{ch},R}.
\]
\item[\textup{(ii)}] \(\widehat\Theta_{\Pi,R}\) is a strict Picard
character on every allowed finite normal-ordered charge channel
\((c,T)\star(c',T')\in\widehat\Gamma_R\):
\[
d_{\mathrm{Hoch}}\widehat\Theta_{\Pi,R}=0.
\]
Equivalently, the \(\widehat\Gamma_R\)-grading has already absorbed the
Gram defect, and \(\overline\Pi_X\) is additive on \(\widehat\Gamma_X\).
\item[\textup{(iii)}] If the successor transition
\(\rho_{R^+R}\) is the degree-truncation map of
\textup{(D0-F)} and commutes with central translations, then the finite
fibre square \textup{(NO1)} commutes for every finite
\(\widehat\Gamma_{R^+}\)-graded complex \(V_{R^+}\).
\end{enumerate}
Thus the Picard part of normal ordering is formal after the finite
coefficient dg category is supplied.  What is not formal is the action of
these translations on Hall pull-push correspondences, orientation lines,
cyclic complexes, and the product/coproduct/pairing transition maps.
\end{lemma}

\begin{proof}
The translation functors satisfy
\(\mathsf T_\eta\mathsf T_{\eta'}=\mathsf T_{\eta+\eta'}\) and
\(\mathsf T_0=\mathrm{id}\) strictly.  Therefore
\[
(d_{\mathrm{Hoch}}\Theta_{\Pi,R}^{\mathrm{phys}})(c,c')
=\mathsf T_{-\Pi_X(c)-\Pi_X(c')+\Pi_X(c+c')}
=\mathsf T_{B(c,c')},
\]
by Lemma~\ref{lem:gram-additivity-defect}.  The same bilinear cocycle
identity for \(B\) gives \(d_{\mathrm{Hoch}}B_{\mathrm{ch},R}=0\), and
normalization follows from \(B(c,0)=B(0,c)=0\).

For \(\widehat\Theta_{\Pi,R}\), compute with
\((c,T)\star(c',T')=(c+c',T+T'+B(c,c'))\):
\[
\begin{aligned}
&-\overline\Pi_X(c,T)-\overline\Pi_X(c',T')
+\overline\Pi_X((c,T)\star(c',T'))\\
&\qquad
=-\Pi_X(c)+T-\Pi_X(c')+T'
+\Pi_X(c+c')-T-T'-B(c,c')=0.
\end{aligned}
\]
Hence its Hochschild boundary is the identity translation.

Finally, the fibre of
\(\overline\Pi_X:\widehat\Gamma_R\to\Gamma_{\mathrm{gram}}\) over a fixed
\(\gamma\) is finite because \(\widehat\Gamma_R\) is finite.  Since
\(\widehat\Gamma_R\subset\widehat\Gamma_{R^+}\), the two composites in
\textup{(NO1)} both first select the finite summands with
\(\overline\Pi_X(c,T)=\gamma\) and then kill exactly those summands not
lying in \(\widehat\Gamma_R\).  Commutation with central translations
identifies the coefficient maps.  Thus the square commutes.
\end{proof}

\begin{lemma}[Kunneth-pure multiplicative orientation criterion]
\label{lem:explicit-multiplicative-orientation-cocycle}
Adopt the notation of
Definition~\ref{def:additive-physical-charge-lattice} and
Definition~\ref{def:orientation-line}.  Suppose a
projection-finite Kunneth-pure substack of the reduced compact
protected derived moduli stack of \(K3\times E\) is supplied, closed
under the Hall extension correspondences under consideration.  Suppose
also that on this substack:
\begin{enumerate}
\item the full self-Ext determinant admits a functorial Kunneth
decomposition, including the cross terms for direct sums;
\item the elliptic factor carries a chosen Costello--Li flat
trivialization compatible with the reduced \(E\)-quotient
\cite{CostelloLiBCOV,CostelloLiOpenClosedBCOV};
\item the K3 factors carry supplied Joyce--Upmeier
multiplicative orientation isomorphisms with strict pentagon; and
\item these choices are \(S^1\)-equivariant on the cyclic complexes.
\end{enumerate}
Then the tensor product of these supplied data gives multiplicative
orientation isomorphisms
\[
\mu_{c,c'}:o_{c+c'}\xrightarrow{\sim}o_c\otimes o_{c'}
\]
on that Kunneth-pure sector, natural for the restricted Hall
correspondences and compatible with the reduced \(E\)-quotient.
No assertion is made here for the full compact or wrapped
\(K3\times E\) protected sector.
\end{lemma}

\begin{proof}
\emph{Conditional tensor product.}
On the supplied Kunneth-pure substack, the full self-Ext determinant
has the assumed factorization into K3 factors and the flat elliptic
factor, including all direct-sum cross terms.  Tensor the supplied
factorwise Joyce--Upmeier multiplicative orientation maps with the
chosen Costello--Li trivialization
\cite{CostelloLiBCOV,CostelloLiOpenClosedBCOV} on the elliptic factor.  This gives
the displayed maps \(\mu_{c,c'}\) on precisely that restricted sector.


Naturality, the strict pentagon, and reduced-
\(E\)-compatibility follow from the corresponding supplied properties
on the factors.  The \(S^1\)-statement is exactly the assumed
equivariance of the factorwise cyclic data.

The proof uses no global product decomposition of the full compact
moduli stack and no projection formula for wrapped branes.  Therefore it
proves (O) only on the explicitly supplied Kunneth-pure sector.  The
full compact/wrapped orientation problem remains the open obligation
recorded in Open Problem~\ref{op:orientation-monodromy-character}.
\end{proof}

\begin{remark}[Conditional orientation comparison]
\label{rem:pin-c-gerbe-mult-orientation}
The criterion above explains how a multiplicative orientation would
factor after one has already supplied the projection-finite Kunneth-pure
sector and all factorwise orientation data.  It does not construct the
reduced compact \(K3\times E\) orientation gerbe, its cyclic
equivariance, or its HN-completed higher-rank extension.  Those remain
part of the Dirac--Igusa realization certificate.
\end{remark}

\begin{theorem}[PTVV--Joyce normal-ordered descent of the primitive bracket;
certificate and obstruction]
\label{thm:ptvv-joyce-pi-descent}
Adopt the notation of Definition~\ref{def:dyonic-mukai-lattice} and
Definition~\ref{def:additive-physical-charge-lattice}: formal lattice
\(\Gamma_X^{\mathrm{form}}=\La_S\oplus\La_S\), Gram shadow
\(\Pi_X:\Gamma_X^{\mathrm{form}}\to\Gamma_{\mathrm{gram}}=\Z^3\),
symmetric quadratic cocycle
\(B(c,c')=(Q\!\cdot\!Q',\,Q\!\cdot\!P'+Q'\!\cdot\!P,\,P\!\cdot\!P')\)
satisfying \(\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c')\).  Suppose:
In the Hall-geometric clauses below, quantifiers over charges mean charges
in the supplied effective support or in the finite normal-ordered support
of the relevant stage.  The formal lattice \(\Gamma_X^{\mathrm{form}}\)
is only the ambient bookkeeping lattice; it is not asserted to be fully
realized by compact moduli.
At each finite stage the theorem uses the supplied normal-ordered
refinement of the primitive layer,
\[
\widetilde P_R=
\bigoplus_{(c,T)\in\widehat\Gamma_R}\widetilde P_{R,(c,T)},
\]
whose bracket lands in
\[
[\widetilde P_{R,(c,T)},\widetilde P_{R,(c',T')}]
\subset
\widetilde P_{R,(c,T)\star(c',T')}.
\]
The no-overcount residual of
Definition~\ref{def:first-order-d0-certificate} is required to vanish, so
these labels refine rather than duplicate the \(c\)-graded primitive
source.  The completed object is the inverse limit of these finite
normal-ordered stages.
\begin{enumerate}
\item[(P)] \emph{(PTVV host.)}  The protected primitive layer
\(\widetilde P_X=\bigoplus_c\widetilde P_{X,c}\) is realized as
\(\widetilde P_X=H^0\Prim_{\mathrm{prot}}(\mathcal F_X)\) for an oriented
critical Hall/factorization object \(\mathcal F_X\) on a
\((-1)\)-shifted symplectic derived moduli stack
\(\mathfrak M_{X,c}\) of compactly supported B-branes on \(K3\times E\)
in the sense of
Pantev--Toen--Vaquie--Vezzosi \cite{PTVV2013} (cf.\ the local schema of
Definition~\ref{def:local-protected-observable-algebra}), graded by
supplied algebraic/effective charge
\(c\in\Gamma_{X,\sigma}^{\mathrm{eff}}\subset
\Gamma_X^{\mathrm{alg}}\subset\Gamma_X^{\mathrm{form}}\), with reduced
\(E\)-quotient compatible with the projection
\(p_E:K3\times E\to E\) of
Definition~\ref{def:protected-hall-integration-criterion}.  The
factorization product on \(\mathcal F_X\) is \(A_\infty\) (homotopy
\(E_3\)): the BBDJS \cite{BBDJS2015} Thom--Sebastiani isomorphism on
disjoint d-critical charts is a derived natural isomorphism, and
downstream consumption acts on the \(H^0\Prim_{\mathrm{prot}}\)
truncation, on which the bracket descends strictly.  Strict \(E_3\)
rectification of the protected chain-level product is a separate
residual obligation: it would require coherent strictification of the
Massey--Saito/BBDJS Thom--Sebastiani product together with the
multiplicative orientation cocycle.  It is not used by the denominator
identity or the primitive-recognition theorem, which consume only the
strict \(H^0\)-level Lie superalgebra.  The binary Hall operations are
represented, before the reduced quotient, by
correspondences
\[
\mathfrak M_{X,c}\times\mathfrak M_{X,c'}
\xleftarrow{\ p_{c,c'}\ }
\mathfrak E_{c,c'}
\xrightarrow{\ q_{c,c'}\ }
\mathfrak M_{X,c+c'},
\]
and the two parenthesizations of a triple product are compared on the
two-step flag stack
\(\mathfrak{Flag}_{a,b,c}\).  These correspondences are part of the
input; the Borcherds product does not construct them.
\item[(E)] \emph{(Reduced \(E\)-quotient and completion.)}
The Hall correspondences, orientation lines, Hopf pairing, and central
translation functors \(\mathsf T_\eta\) are constructed before quotienting
by translations of \(E\), then descend to the cosection-reduced
\(E\)-quotient and to the sectorial HN inverse system.  In particular
\(\mathsf T_\eta\) commutes with the reduced \(E\)-quotient, with HN
completion, and with the local-local, wrapped-wrapped, and mixed
local/wrapped extension correspondences of
Open Problem~\ref{op:hybrid-wrapped-factorization}.  The completed
primitive object is the inverse limit of finite stages:
\[
P_X^\Pi=\varprojlim_R P_{R}^{\Pi},\qquad
P_X^\Pi\widehat{\otimes}P_X^\Pi
=\varprojlim_R(P_R^\Pi\otimes P_R^\Pi).
\]
The maps \(m_R\), \([\,\cdot\,,\,\cdot\,]_R\), \(\Delta_R\),
\(\langle\,\cdot\,,\,\cdot\,\rangle_R\), and
\(\overline\Pi_{R,*}^{\Theta}\) commute with all transition maps.  Thus
every product over a fibre of \(\overline\Pi_X\), and every completed
tensor product used by the Hopf structure, is the inverse limit of finite
operations.  This is a hypothesis; it is not a formal consequence of the
lattice homomorphism \(\overline\Pi_X\).
\item[(O)] \emph{(\(S^1\)-equivariant multiplicative orientation cocycle.)}
The collection \(\{\mu_{c,c'}\}\) is an \(S^1\)-equivariant
multiplicative orientation cocycle on \((-1)\)-shifted symplectic
stacks satisfying the strict pentagon.  Concretely: an orientation
datum \(\{o_c\}_{c\in\Gamma_{X,\sigma}^{\mathrm{eff}}}\) in the sense of
Definition~\ref{def:orientation-line} is supplied with
\emph{Joyce--Upmeier multiplicative isomorphisms} \cite{JoyceUpmeier}
\[
\mu_{c,c'}\,:\;o_{c+c'}\;\xrightarrow{\ \sim\ }\;o_c\otimes o_{c'},
\qquad c,c'\in\Gamma_{X,\sigma}^{\mathrm{eff}},
\]
satisfying the strict cocycle pentagon
\(\mu_{c+c',c''}\circ\mu_{c,c'}=\mu_{c,c'+c''}\circ\mu_{c',c''}\)
on the Cartesian extension correspondence, compatible with the
reduced \(E\)-quotient and with the HN/sectorial completion of
Lemma~\ref{prop:sectorial-hall-truncation}, and \emph{equivariant
under the loop-rotation \(S^1\)-action on the cyclic complex of
\(\mathfrak M_{X,c}\)}.  This last condition lifts the orientation
cocycle from a Hochschild trivialization to a \emph{cyclic}
trivialization, and is exactly the kind of orientation technology
Joyce--Upmeier \cite{JoyceUpmeier} supply once the reduced compact
sector and its cyclic model have been constructed.  The
\(S^1\)-equivariance is not inferred from the scalar determinant; it is
an input on the Hall side.
Equivalently, the collection \(\{o_c\}\) is an \(S^1\)-equivariant
multiplicative section of the determinant gerbe over the moduli of
objects in the protected sector.
\item[(\(\Theta\))] \emph{(Cocycle-corrected degree shifts.)}
A coherent family of central degree-shift data is supplied on the
primitive bracket targets in the coefficient dg category of
Definition~\ref{def:normal-ordering-coefficient-dg-category}.  The chain
representative of the Gram defect is the normalized translation-valued
Hochschild \(2\)-cocycle
\[
B_{\mathrm{ch}}(c,c'):=\mathsf T_{B(c,c')}
\in
Z^2_{\mathrm{Hoch}}\!
\bigl(\Gamma_X^{\mathrm{phys}};
\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\bigr).
\]
A normalized \(1\)-cochain
\[
\Theta_\Pi\in
C^1_{\mathrm{Hoch}}\!
\bigl(\Gamma_X^{\mathrm{phys}};
\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\bigr),
\qquad
\Theta_\Pi(c)=\mathsf T_{-\Pi_X(c)}
\]
is supplied with coherent natural quasi-isomorphisms
\[
d_{\mathrm{Hoch}}\Theta_\Pi=B_{\mathrm{ch}}.
\]
The formula for \(\Theta_\Pi\) is the formal central translation
cochain.  The hypothesis is stronger: these translations must act on the
actual Hall correspondence targets and must be compatible with the
orientation, reduced quotient, cyclic model, and finite HN transitions.
Equivalently, for every pair \(c,c'\) the raw bracket target of Gram
degree \(\Pi_X(c+c')\) is translated by
\(\mathsf T_{B(c,c')}\) to the additive Gram degree
\(\Pi_X(c)+\Pi_X(c')\).  For triples \(a,b,c\), the two composites over
\(\mathfrak{Flag}_{a,b,c}\),
\[
(\vartheta_{a,b}\otimes 1)\circ\vartheta_{a+b,c},
\qquad
(1\otimes\vartheta_{b,c})\circ\vartheta_{a,b+c},
\]
agree after the Hall associator, Thom--Sebastiani transport, and
orientation signs.  Their quotient in
\(\pi_1\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\) is the
triple obstruction
\[
\operatorname{Pent}_{\Theta}(a,b,c)
:=
\bigl[(\vartheta_{a,b}\otimes 1)\circ\vartheta_{a+b,c}\bigr]
-
\bigl[(1\otimes\vartheta_{b,c})\circ\vartheta_{a,b+c}\bigr],
\]
with the Hall associator and orientation transport inserted in the
middle.  Hypothesis \((\Theta)\) requires
\(\operatorname{Pent}_{\Theta}(a,b,c)=0\) for every two-step Hall flag.
On degrees this is exactly
\[
B(a,b)+B(a+b,c)=B(b,c)+B(a,b+c),
\]
i.e. \(d_{\mathrm{Hoch}}B_{\mathrm{ch}}=0\), but the displayed equality is
required as a chain homotopy, not only as a lattice identity.
\item[(F)] \emph{(Frobenius pairing.)}  The protected Hall bracket
\([\,\cdot\,,\,\cdot\,]\) and the protected Hopf pairing
\(\langle\,\cdot\,,\,\cdot\,\rangle\) on \(\widetilde P_X\) (the latter
furnished by the squaring isomorphism
\(o_c^{\otimes 2}\simeq\det\mathrm{RHom}(\mathcal C,\mathcal C)\) of
Definition~\ref{def:orientation-line} and the PTVV \cite{PTVV2013}
\((-1)\)-shifted symplectic form on
\(\mathfrak M_{X,c}\), trivialized along the reduced \(E\)-quotient via
the Costello--Li flat Calabi--Yau pairing
\cite{CostelloRenormalization,CostelloLiBCOV,CostelloLiOpenClosedBCOV}) satisfy the
graded-Frobenius identity
\[
\langle[x,y],z\rangle
+(-1)^{|x|\cdot|y|}\langle y,[x,z]\rangle=0
\]
for homogeneous \(x,y,z\in\widetilde P_X\) of additive formal charges
\(c_x,c_y,c_z\) with \(c_x+c_y+c_z=0\).  After applying
\(\overline\Pi_{X,*}^{\Theta}\) the same identity is imposed for the
transported bracket \([\,\cdot\,,\,\cdot\,]_\Theta\).
\item[(Cyc)] \emph{(Negative-cyclic lift.)}
The Hochschild cochain \(\Theta_\Pi\) has an \(S^1\)-equivariant lift
\(\Theta_\Pi^{-}\) in the negative-cyclic complex of the protected Hall
sector, and the lifted equation
\[
(b+uB_{\mathrm C})\Theta_\Pi^{-}=B_{\mathrm{ch}}^{-}
\]
holds, where \(B_{\mathrm C}\) is the Connes operator and
\(B_{\mathrm{ch}}^{-}\) is a negative-cyclic representative whose
forgetful image in Hochschild cochains is \(B_{\mathrm{ch}}\).  The
forgetful map sends the cyclic equation to the Hochschild equation in
\((\Theta)\), so the cyclic lift is a refinement, not a replacement, of
normal ordering.
\end{enumerate}
Then, writing \(P_X^\Pi:=\overline\Pi_{X,*}^{\Theta}\widetilde P_X\), for
finite normal-ordered labels \((c,T)\), \((c',T')\) whose summands are
supplied, the finite-stage normal-ordered lift of the raw
physical-charge bracket
\[
[\widetilde P_{R,(c,T)},\widetilde P_{R,(c',T')}]
\subset
\widetilde P_{R,(c,T)\star(c',T')}
\]
induces, after passage to the compatible inverse limit, a
cocycle-corrected Gram-graded bracket
\[
[\,\cdot\,,\,\cdot\,]_\Theta:
(P_X^\Pi)_{\overline\Pi_X(c,T)}
\otimes
(P_X^\Pi)_{\overline\Pi_X(c',T')}
\longrightarrow
(P_X^\Pi)_{\overline\Pi_X(c,T)+\overline\Pi_X(c',T')}.
\]
Thus \(B\) is not erased; it is the coherent degree-shift by which the
raw target \(\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c')\) is transported to
the additive normal-ordered Gram target
\(\overline\Pi_X((c,T)\star(c',T'))\).  This object
\[
P_X^\Pi
\]
is therefore a \(\Gamma_{\mathrm{gram}}\)-graded Lie superalgebra at
the stated \(H^0\) level, and hypothesis~(1b) of
Theorem~\ref{thm:primitive-recognition} is satisfied with the
\(\Theta\)-corrected descent.

If the finite-fibre HN topology of (E), \((\Theta)\), its triple
coherence, (F), (Cyc), and radical ideal/coideal stability are not
supplied, the minimal computable obstruction is the finite-HN inverse
system of classes
\[
\mathfrak o_{\Theta}^{\mathrm{top}}
:=
\left\{
\mathfrak o_{\Theta,R'R}^{\mathrm{fib}},
\mathfrak o_{\Theta,R'R}^{m},
\mathfrak o_{\Theta,R'R}^{\Delta},
\mathfrak o_{\Theta,R'R}^{\langle\, ,\,\rangle}
\right\}_{R'\ge R},
\]
where \(\rho_{R'R}\) is the source transition,
\(\rho^\Pi_{R'R}\) is the descended primitive transition, and these are
the finite Hom-space defects
\[
\mathfrak o_{\Theta,R'R}^{\mathrm{fib}}
:=
\rho^\Pi_{R'R}\overline\Pi_{R',*}^{\Theta_{R'}}
-
\overline\Pi_{R,*}^{\Theta_R}\rho_{R'R},
\]
\[
\mathfrak o_{\Theta,R'R}^{m}
:=
\rho^\Pi_{R'R}m_{R'}^{\Theta}
-
m_R^{\Theta}(\rho^\Pi_{R'R}\otimes\rho^\Pi_{R'R}),
\qquad
\mathfrak o_{\Theta,R'R}^{\Delta}
:=
(\rho^\Pi_{R'R}\otimes\rho^\Pi_{R'R})\Delta_{R'}^{\Theta}
-
\Delta_R^{\Theta}\rho^\Pi_{R'R},
\]
\[
\mathfrak o_{\Theta,R'R}^{\langle\, ,\,\rangle}
:=
\langle\,\cdot\,,\,\cdot\,\rangle_R
(\rho^\Pi_{R'R}\otimes\rho^\Pi_{R'R})
-
\langle\,\cdot\,,\,\cdot\,\rangle_{R'},
\]
\[
\mathfrak o_{\Theta}^{\mathrm{Hoch}}
:=[B_{\mathrm{ch}}-d_{\mathrm{Hoch}}\Theta_\Pi]
\in
HH^2_{\mathrm{red},E}
\bigl(\widetilde P_X^{\mathrm{br}};
\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\bigr),
\]
\[
\mathfrak o_{\Theta}^{\mathrm{tri}}
:=[\operatorname{Pent}_{\Theta}]
\in
HH^3_{\mathrm{red},E}
\bigl(\widetilde P_X^{\mathrm{br}};
\pi_1\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\bigr),
\]
\[
\mathfrak o_{\Theta}^{\mathrm{Jac}}
:=[\operatorname{Jac}_{\Theta}]
\in
C^3_{\mathrm{CE},\mathrm{red},E}
\bigl(\overline\Pi_{X,*}^{\Theta}\widetilde P_X;
\overline\Pi_{X,*}^{\Theta}\widetilde P_X\bigr),
\]
\[
\mathfrak o_F
:=\bigl[
(x,y,z)\mapsto
\langle[x,y]_{\Theta},z\rangle
+(-1)^{|x||y|}\langle y,[x,z]_{\Theta}\rangle
\bigr]
\in
C^3_{\mathrm{cyc},\mathrm{red},E}
\bigl(\overline\Pi_{X,*}^{\Theta}\widetilde P_X;k\bigr),
\]
\[
\mathfrak o_{\Theta}^{\mathrm{cyc}}
:=[B_{\mathrm{ch}}^{-}-(b+uB_{\mathrm C})\Theta_\Pi^{-}]
\in
HC^{-\,2}_{\mathrm{red},E}
\bigl(\widetilde P_X^{\mathrm{br}};
\mathsf{Pic}^{\mathrm{dg}}_{\Gamma_{\mathrm{gram}}}\bigr),
\]
\[
\mathfrak o_{\Theta}^{\mathrm{rad}}
:=
\bigl(
\mathfrak o_{\Theta}^{\mathrm{rad,Lie}},
\mathfrak o_{\Theta}^{\mathrm{rad,coid}}
\bigr),
\]
defined on the HN-completed reduced \(E\)-quotient of the protected
bracket category, where
\[
P_X^\Pi=\overline\Pi_{X,*}^{\Theta}\widetilde P_X,\qquad
\operatorname{Rad}_X^\Pi
=\{r\in P_X^\Pi\mid \langle r,w\rangle=0\ \text{for all }w\in P_X^\Pi\}.
\]
The two components are
\[
\mathfrak o_{\Theta}^{\mathrm{rad,Lie}}
:=\bigl[
(x,r,z)\mapsto
\langle[x,r]_{\Theta},z\rangle
\bigr]
\in
\Hom_{\mathrm{red},E}
\bigl(P_X^\Pi\otimes\operatorname{Rad}_X^\Pi\otimes P_X^\Pi,k\bigr),
\]
and, for the quotient map
\(\bar q_\Pi:P_X^\Pi\to P_X^\Pi/
\overline{\operatorname{Rad}_X^\Pi}\),
\[
\mathfrak o_{\Theta}^{\mathrm{rad,coid}}(r)
:=
(\bar q_\Pi\widehat{\otimes}\bar q_\Pi)\Delta_\Theta(r),
\qquad r\in\operatorname{Rad}_X^\Pi .
\]
Here \(\Delta_\Theta\) is the descended completed Hopf coproduct.  The
condition
\(\mathfrak o_{\Theta}^{\mathrm{rad,coid}}=0\) says exactly that
\[
\Delta_\Theta(\operatorname{Rad}_X^\Pi)
\subset
\overline{\operatorname{Rad}_X^\Pi\widehat{\otimes} P_X^\Pi
+P_X^\Pi\widehat{\otimes}\operatorname{Rad}_X^\Pi}.
\]
Here \(\mathfrak o_{\Theta}^{\mathrm{top}}\) is the assertion that
\(\overline\Pi_{*}^{\Theta}\), the transported product, the transported
coproduct, and the pairing are strict morphisms of the finite HN inverse
system; its vanishing is what makes the completed fibre products and
\(\widehat{\otimes}\)-operations well defined.  The class
\(\operatorname{Pent}_{\Theta}(a,b,c)\) is the difference of the two
triple composites over
\(\mathfrak{Flag}_{a,b,c}\), and
\(\operatorname{Jac}_{\Theta}\) is the signed Jacobiator of the transported
bracket.  The Hochschild shadow is computed on homogeneous charges by the
explicit formula for \(B(c,c')\); the triple shadow is the displayed
cocycle identity for \(B\), hence zero at the lattice level; the cyclic
component is computed by applying \(B_{\mathrm C}\) to the chosen cyclic
orientation representative.  The class
\(\mathfrak o_{\Theta}^{\mathrm{rad}}\) vanishes exactly when the Hopf
radical is both a Lie ideal for the transported bracket and a coideal for
the completed descended coproduct.  Closedness of the radical in the HN
topology is still a separate topological hypothesis.
\end{theorem}

\begin{proof}
\emph{Step 1 (The coefficient category).}
The coefficient system for normal ordering is the Picard dg groupoid of
central translations of
\(\mathsf{Ch}_{k,\widehat{\mathrm{HN}},E}^{\Gamma_{\mathrm{gram}}}\), as in
Definition~\ref{def:normal-ordering-coefficient-dg-category}.
That definition constructs \(\overline\Pi_{X,*}^{\Theta}\) as the inverse
limit of the finite fibre products
\((\overline\Pi_{R,*}^{\Theta}V_R)_\gamma\).  The finite-transition part
of hypothesis (E), encoded by
\(\mathfrak o_{\Theta}^{\mathrm{top}}=0\), is what permits the
transported product, coproduct, and pairing to pass from finite stages to
the completed HN object.
With the convention
\((\mathsf T_\eta V)_\gamma=V_{\gamma+\eta}\), applying
\(\mathsf T_{B(c,c')}\) to a raw target of degree
\(\Pi_X(c+c')\) displays it in degree
\[
\Pi_X(c+c')-B(c,c')=\Pi_X(c)+\Pi_X(c').
\]
Thus \(B_{\mathrm{ch}}(c,c')=\mathsf T_{B(c,c')}\) is the exact
translation-valued Hochschild \(2\)-cocycle measuring failure of raw
Gram additivity.

\emph{Step 2 (The boundary equation).}
For the standard additive Hochschild differential on normalized
cochains,
\[
(d_{\mathrm{Hoch}}\Theta_\Pi)(c,c')
=\Theta_\Pi(c)+\Theta_\Pi(c')-\Theta_\Pi(c+c').
\]
The underlying degree of the translation
\(\Theta_\Pi(c)=\mathsf T_{-\Pi_X(c)}\) gives
\[
d_{\mathrm{Hoch}}\Theta_\Pi(c,c')
=-\Pi_X(c)-\Pi_X(c')+\Pi_X(c+c')=B(c,c').
\]
Hypothesis \((\Theta)\) is precisely the statement that this arithmetic
boundary is represented by actual central translation
quasi-isomorphisms on the protected Hall bracket targets.

\emph{Step 3 (Triples, Jacobi, and Frobenius).}
For three charges \(a,b,c\), the two ways of translating the target of
a two-step bracket differ by
\[
B(a,b)+B(a+b,c)-B(b,c)-B(a,b+c)
=-d_{\mathrm{Hoch}}B(a,b,c)=0
\]
by Lemma~\ref{lem:b-cocycle-central-extension}.  The supplied pentagon
homotopies in \((\Theta)\) lift this equality from degrees to the Hall
chain category: the obstruction is precisely
\(\operatorname{Pent}_{\Theta}(a,b,c)\).  If it vanishes, the
normal-ordered product is associative on \(H^0\), and the supercommutator
bracket inherits the Jacobi identity from the upstairs Hall bracket.  The
corresponding signed Jacobiator is
\[
\operatorname{Jac}_{\Theta}(x,y,z)
=[x,[y,z]_{\Theta}]_{\Theta}
-[[x,y]_{\Theta},z]_{\Theta}
-(-1)^{|x||y|}[y,[x,z]_{\Theta}]_{\Theta};
\]
its degree shadow is zero by the same cocycle identity, and its chain
class is the image of the Hall associator and
\(\operatorname{Pent}_{\Theta}\).  Hypothesis (F) is then the separate
vanishing of
\[
\mathfrak o_F(x,y,z)
=\langle[x,y]_{\Theta},z\rangle
+(-1)^{|x||y|}\langle y,[x,z]_{\Theta}\rangle.
\]
It is not implied by the degree calculation.

\emph{Step 4 (Orientation, reduced quotient, and radical quotient).}
Hypothesis (O) transports the orientation lines through the same
extension correspondences used by the Hall product; hypothesis (E)
asserts that the translation action, orientation transport, and mixed
local/wrapped correspondences descend through the reduced
\(E\)-quotient and HN completion.  Let
\(\operatorname{Rad}_X^\Pi\) be the radical of the descended Hopf
pairing.  The exact obstruction to Lie-ideal stability is
\[
\mathfrak o_{\Theta}^{\mathrm{rad,Lie}}(x,r,z)
=\langle[x,r]_{\Theta},z\rangle,\qquad r\in\operatorname{Rad}_X^\Pi .
\]
If (F) holds, this expression equals
\(-(-1)^{|x||r|}\langle r,[x,z]_{\Theta}\rangle=0\), so the radical is a
Lie ideal.  This does not prove coideal stability.  Let
\(\bar q_\Pi:P_X^\Pi\to
P_X^\Pi/\overline{\operatorname{Rad}_X^\Pi}\).  The exact coideal
obstruction is
\[
\mathfrak o_{\Theta}^{\mathrm{rad,coid}}(r)
=
(\bar q_\Pi\widehat{\otimes}\bar q_\Pi)\Delta_\Theta(r).
\]
Its vanishing is equivalent to
\(\Delta_\Theta(r)\) lying in the completed sum
\[
\overline{\operatorname{Rad}_X^\Pi\widehat{\otimes} P_X^\Pi
+P_X^\Pi\widehat{\otimes}\operatorname{Rad}_X^\Pi}.
\]
Closedness of \(\operatorname{Rad}_X^\Pi\) in the Hall topology remains a
separate input.  Only after ideal, coideal, and closedness conditions does
the quotient carry the same \(\Gamma_{\mathrm{gram}}\)-graded Hopf--Lie
structure.

\emph{Step 5 (Cyclic lift and obstruction).}
The Hochschild construction controls the displayed \(H^0\) bracket.
For the full chain-level descent, the degree-shift cochain must be
fixed by loop rotation.  This is exactly hypothesis (Cyc):
\((b+uB_{\mathrm C})\Theta_\Pi^{-}=B_{\mathrm{ch}}^{-}\).  If such a
negative-cyclic lift is absent, or if the finite-HN topology,
triple/Jacobi/Frobenius/radical coherence fails, the seven classes
displayed in the theorem are the obstruction.  They are minimal for this
model: vanishing of \(\mathfrak o_{\Theta}^{\mathrm{top}}\) is equivalent
to the finite-fibre descent and completed tensor operations commuting with
the HN inverse system; vanishing of
\(\mathfrak o_{\Theta}^{\mathrm{Hoch}}\) is equivalent to existence of
the degree-shift trivialization on bracket targets; vanishing of
\(\mathfrak o_{\Theta}^{\mathrm{tri}}\) is equivalent to compatibility of
that trivialization with the two-step Hall flag correspondences;
vanishing of \(\mathfrak o_{\Theta}^{\mathrm{Jac}}\) is the Jacobi
compatibility of the transported bracket; vanishing of \(\mathfrak o_F\)
is the Frobenius/Hopf invariance of the transported bracket; vanishing
of \(\mathfrak o_{\Theta}^{\mathrm{cyc}}\) is equivalent to choosing the
trivialization compatibly with the \(S^1\)-equivariant orientation data;
and vanishing of \(\mathfrak o_{\Theta}^{\mathrm{rad}}\), together with
closedness in the HN topology, is the condition for passage to the Hopf
radical quotient.
\qedhere
\end{proof}

\begin{proposition}[Finite verification diagrams for normal ordering]
\label{prop:finite-normal-ordering-verification-diagrams}
Fix a successor arrow \(R^+\to R\) in the cofinal HN subsystem of
Definition~\textup{\ref{def:first-order-d0-certificate}}.  Let
\(P_R^\Pi=\overline\Pi_{R,*}^{\Theta_R}\widetilde P_R\) be a finite
normal-ordered primitive stage, with transition
\(\rho^\Pi_{R^+R}:P_{R^+}^\Pi\to P_R^\Pi\).  A supplied finite system kills
the seven normal-ordering obstructions of
Theorem~\textup{\ref{thm:ptvv-joyce-pi-descent}} at this successor arrow
exactly when the following finite maps commute, or are supplied with the
displayed null-homotopies, in the indicated finite Hom complexes.

\textup{(NO1) Finite fibres.}
\[
\begin{tikzcd}
V_{R^+} \arrow[r,"\overline\Pi_{R^+,*}^{\Theta_{R^+}}"]
\arrow[d,"\rho_{R^+R}"']
& \overline\Pi_{R^+,*}^{\Theta_{R^+}}V_{R^+}
\arrow[d,"\rho^\Pi_{R^+R}"]\\
V_R \arrow[r,"\overline\Pi_{R,*}^{\Theta_R}"']
& \overline\Pi_{R,*}^{\Theta_R}V_R .
\end{tikzcd}
\]
This is \(\mathfrak o^{\mathrm{fib}}_{\Theta,R^+R}=0\); it says that
fibre products over \(\overline\Pi_X\) are finite before completion and
transition-compatible before the inverse limit is taken.

\textup{(NO2) Product, coproduct, pairing.}
\[
\begin{tikzcd}
P_{R^+}^\Pi\otimes P_{R^+}^\Pi
\arrow[r,"m_{R^+}^{\Theta}"]
\arrow[d,"\rho^\Pi_{R^+R}\otimes\rho^\Pi_{R^+R}"']
& P_{R^+}^\Pi \arrow[d,"\rho^\Pi_{R^+R}"]\\
P_R^\Pi\otimes P_R^\Pi
\arrow[r,"m_R^{\Theta}"']
& P_R^\Pi
\end{tikzcd}
\qquad
\begin{tikzcd}
P_{R^+}^\Pi
\arrow[r,"\Delta_{R^+}^{\Theta}"]
\arrow[d,"\rho^\Pi_{R^+R}"']
& P_{R^+}^\Pi\otimes P_{R^+}^\Pi
\arrow[d,"\rho^\Pi_{R^+R}\otimes\rho^\Pi_{R^+R}"]\\
P_R^\Pi
\arrow[r,"\Delta_R^{\Theta}"']
& P_R^\Pi\otimes P_R^\Pi .
\end{tikzcd}
\]
Together with
\[
\langle\rho^\Pi_{R^+R}x,\rho^\Pi_{R^+R}y\rangle_R
=\langle x,y\rangle_{R^+},
\]
these are
\(\mathfrak o^{m}_{\Theta,R^+R}=
\mathfrak o^{\Delta}_{\Theta,R^+R}=
\mathfrak o^{\langle\, ,\,\rangle}_{\Theta,R^+R}=0\).

\textup{(NO3) Hochschild and negative-cyclic equations.}
For every finite charge pair \(c,c'\in\widehat\Gamma_{R^+}\), the
Hochschild boundary and its cyclic refinement are the finite equations
\[
d_{\mathrm{Hoch}}\Theta_{\Pi,R}(c,c')=B_{\mathrm{ch},R}(c,c'),
\qquad
(b+uB_{\mathrm C})\Theta_{\Pi,R}^{-}=B_{\mathrm{ch},R}^{-}.
\]
They kill
\(\mathfrak o^{\mathrm{Hoch}}_{\Theta,R}\) and
\(\mathfrak o^{\mathrm{cyc}}_{\Theta,R}\).  The second equation is imposed
in the negative-cyclic complex; it is not obtained by forgetting to
Hochschild cochains.

\textup{(NO4) Triple flag.}
For every two-step finite Hall flag over \(\mathfrak{Flag}_{a,b,c,R}\),
the two translated products must agree after inserting the Hall associator
and orientation transport:
\[
(\mathsf A_{a,b,c}\circ(\vartheta_{a,b}\otimes1)\circ
\vartheta_{a+b,c})
-
((1\otimes\vartheta_{b,c})\circ\vartheta_{a,b+c})=0.
\]
This is the finite representative of
\(\operatorname{Pent}_{\Theta}(a,b,c)\).  Its degree shadow is the
bilinear identity for \(B\); the chain equality is additional data.

\textup{(NO5) Jacobi.}
The transported bracket must have zero finite Jacobiator
\[
\operatorname{Jac}_{\Theta,R}(x,y,z)=0
\]
for all homogeneous \(x,y,z\in P_R^\Pi\).

\textup{(NO6) Frobenius.}
The finite Frobenius defect
\[
\mathfrak o_{F,R}(x,y,z)=
\langle[x,y]_{\Theta},z\rangle_R
+(-1)^{|x||y|}\langle y,[x,z]_{\Theta}\rangle_R
\]
must vanish.

\textup{(NO7) Hopf radical.}
Finally, for
\(\operatorname{Rad}_R^\Pi=\{r\in P_R^\Pi\mid
\langle r,w\rangle_R=0\ \forall w\in P_R^\Pi\}\) (equivalently the
two-sided radical when the finite Hopf pairing is graded symmetric) and
\(\bar q_{\Pi,R}:P_R^\Pi\to
P_R^\Pi/\operatorname{Rad}_R^\Pi\), one must have both
\[
\langle[x,r]_{\Theta},z\rangle_R=0
\qquad
(x,z\in P_R^\Pi,\ r\in\operatorname{Rad}_R^\Pi)
\]
and the finite coideal square
\[
\begin{tikzcd}
\operatorname{Rad}_R^\Pi \arrow[r,"\Delta_R^\Theta"]
\arrow[d,"0"']
& P_R^\Pi\otimes P_R^\Pi
\arrow[d,"\bar q_{\Pi,R}\otimes\bar q_{\Pi,R}"]\\
0 \arrow[r]
& (P_R^\Pi/\operatorname{Rad}_R^\Pi)
\otimes(P_R^\Pi/\operatorname{Rad}_R^\Pi).
\end{tikzcd}
\]
These are the finite Lie-ideal and coideal parts of
\(\mathfrak o^{\mathrm{rad}}_{\Theta,R}=0\).  Closedness of the inverse
limit radical is the additional HN topological assertion that the kernels
\(\operatorname{Rad}_R^\Pi\) form a transition-compatible closed subsystem.

Consequently, if \textup{(NO1)--(NO7)} hold for every successor arrow and
the non-successor transition maps are their composites, the inverse limit
kills
\[
\mathfrak o_{\Theta}^{\mathrm{top}},\quad
\mathfrak o_{\Theta}^{\mathrm{Hoch}},\quad
\mathfrak o_{\Theta}^{\mathrm{tri}},\quad
\mathfrak o_{\Theta}^{\mathrm{Jac}},\quad
\mathfrak o_F,\quad
\mathfrak o_{\Theta}^{\mathrm{cyc}},\quad
\mathfrak o_{\Theta}^{\mathrm{rad}}.
\]
If one displayed finite diagram fails, its homotopy class is the surviving
obstruction.  Neither non-degeneracy of the pairing nor the scalar
Borcherds determinant removes \textup{(NO3)}, \textup{(NO6)}, or the
coideal part of \textup{(NO7)}.
\end{proposition}

\begin{lemma}[Hopf--Frobenius certificate and obstruction]
\label{lem:F-frobenius-from-hopf-nondegeneracy}
Adopt hypotheses (P) and (O) of
Theorem~\ref{thm:ptvv-joyce-pi-descent}, and grant
the Hopf-pairing/radical hypothesis of
Theorem~\ref{thm:primitive-recognition}: the protected Hopf pairing
\(\langle\,\cdot\,,\,\cdot\,\rangle\) on the protected primitive layer
\(\widetilde P_X=H^0\Prim_{\mathrm{prot}}(\mathcal F_X)\) is
non-degenerate after the standard radical quotient.  Non-degeneracy
alone does not imply the graded Frobenius identity.  The missing datum is
the vanishing of the trilinear obstruction
\[
\mathfrak o_F(x,y,z):=
\langle[x,y],z\rangle
+(-1)^{|x|\cdot|y|}\langle y,[x,z]\rangle,
\qquad
x\in\widetilde P_{X,c_x},\
y\in\widetilde P_{X,c_y},\
z\in\widetilde P_{X,c_z},\quad c_x+c_y+c_z=0,
\]
viewed as a class
\[
\mathfrak o_F\in
C^3_{\mathrm{cyc}}
\bigl(\widetilde P_X;\,k\bigr)
\]
after the reduced \(E\)-quotient and radical quotient.  Hypothesis (F)
of Theorem~\ref{thm:ptvv-joyce-pi-descent} is equivalent to
\(\mathfrak o_F=0\).  It is supplied, for example, by the CY-\(3\)
Serre-functor criterion of Lemma~\ref{lem:F-frobenius-from-cy-serre}.
\end{lemma}

\begin{proof}
\emph{Step 1 (Exact defect).}
For homogeneous \(x,y,z\) with \(c_x+c_y+c_z=0\), the displayed cochain
\(\mathfrak o_F(x,y,z)\) is precisely the left side of the
graded-Frobenius identity.  Hence hypothesis (F) is equivalent, by
definition, to \(\mathfrak o_F=0\) after the reduced \(E\)-quotient and
the chosen radical quotient.  No determinant or non-degeneracy statement
alone forces this vanishing.

\emph{Step 2 (What non-degeneracy detects).}
After quotienting by the radical, non-degeneracy identifies a bilinear
operation \(D(x,y)\) with the functional
\(z\mapsto\langle D(x,y),z\rangle\).  Thus if the Frobenius defect is
known to vanish after pairing against every \(z\), non-degeneracy forces
the corresponding operation-level defect to vanish in the quotient.
This is detection, not construction: the cyclic or Serre-functor input
must still supply the equality being detected.

\emph{Step 3 (Radical consequence).}
Let
\[
\operatorname{Rad}_X^\Pi
=\{r\mid \langle r,w\rangle=0\ \text{for all }w\}.
\]
If \(\mathfrak o_F=0\), then for every \(r\in\operatorname{Rad}_X^\Pi\)
\[
\langle[x,r],z\rangle
=-(-1)^{|x||r|}\langle r,[x,z]\rangle=0.
\]
Therefore \(\operatorname{Rad}_X^\Pi\) is a Lie ideal.  The assertion
that it is closed and is also a coideal is the separate Hopf-radical
hypothesis in Theorem~\ref{thm:primitive-recognition}.  Equivalently,
the coproduct must separately satisfy
\[
(\bar q_\Pi\widehat{\otimes}\bar q_\Pi)\Delta_\Theta(r)=0
\qquad(r\in\operatorname{Rad}_X^\Pi),
\]
with \(\bar q_\Pi\) the quotient by the closed radical.  Lemma
\ref{lem:F-frobenius-from-cy-serre} is one conditional source for
\(\mathfrak o_F=0\); it is not a source for coideal stability unless the
cyclic/Serre datum is also proved compatible with the Hopf coproduct.
\qedhere
\end{proof}

\begin{lemma}[Finite Hopf-adjointness radical test]
\label{lem:finite-hopf-adjointness-radical-test}
Let \(P_R^\Pi\) be a finite normal-ordered primitive stage with transported
product \(m_R^\Theta\), coproduct \(\Delta_R^\Theta\), and graded
symmetric Hopf pairing \(\langle\,\cdot\,,\,\cdot\,\rangle_R\).  Let
\[
\operatorname{Rad}_R^\Pi
=\{r\mid \langle r,w\rangle_R=\langle w,r\rangle_R=0
\ \text{for all }w\in P_R^\Pi\}.
\]
Assume:
\begin{enumerate}
\item[\textup{(H1)}] \(m_R^\Theta\) and \(\Delta_R^\Theta\) are adjoint for
the finite Hopf pairing:
\[
\langle m_R^\Theta(x,y),z\rangle_R
=
\langle x\otimes y,\Delta_R^\Theta z\rangle_R
\qquad(x,y,z\in P_R^\Pi),
\]
with the tensor pairing induced from \(\langle\,\cdot\,,\,\cdot\,\rangle_R\).
\item[\textup{(H2)}] The induced tensor pairing on
\[
(P_R^\Pi/\operatorname{Rad}_R^\Pi)\otimes
(P_R^\Pi/\operatorname{Rad}_R^\Pi)
\]
is non-degenerate.
\end{enumerate}
Together with the supplied finite Hopf pairing, coproduct, and radical
matrices, this is the algebraic finite-stage test for \textup{(NO7)}.
Then the finite coideal square in \textup{(NO7)} commutes:
\[
(\bar q_{\Pi,R}\otimes\bar q_{\Pi,R})\Delta_R^\Theta(r)=0
\qquad(r\in\operatorname{Rad}_R^\Pi).
\]
If, in addition, the finite Frobenius defect \(\mathfrak o_{F,R}\)
vanishes, then \(\operatorname{Rad}_R^\Pi\) is also a Lie ideal for the
transported bracket.  Thus finite \textup{(NO7)} is killed by
\(\mathfrak o_{F,R}=0\) plus Hopf adjointness and finite quotient
non-degeneracy.  The closed inverse-limit radical still requires the
transition-compatible closedness condition of
Theorem~\ref{thm:primitive-recognition}.
\end{lemma}

\begin{proof}
For \(r\in\operatorname{Rad}_R^\Pi\) and \(x,y\in P_R^\Pi\),
Hopf adjointness gives
\[
\bigl\langle x\otimes y,\Delta_R^\Theta(r)\bigr\rangle_R
=\langle m_R^\Theta(x,y),r\rangle_R=0,
\]
because \(r\) lies in the right radical.  Hence the class
\((\bar q_{\Pi,R}\otimes\bar q_{\Pi,R})\Delta_R^\Theta(r)\) pairs to zero
against every elementary tensor in the quotient.  By finite
non-degeneracy of the quotient tensor pairing, the class itself is zero.
This is exactly the coideal square of \textup{(NO7)}.

If \(\mathfrak o_{F,R}=0\), then for \(r\in\operatorname{Rad}_R^\Pi\)
\[
\langle[x,r]_\Theta,z\rangle_R
=-(-1)^{|x||r|}\langle r,[x,z]_\Theta\rangle_R=0
\]
for every \(x,z\), so \([x,r]_\Theta\) lies in the radical.  This is the
finite Lie-ideal half.
\end{proof}

\begin{proposition}[Negative-cyclic route to the normal-ordering cochain]
\label{prop:negative-cyclic-normal-ordering-route}
Assume, in addition to hypothesis \textup{(P)} of
Theorem~\ref{thm:ptvv-joyce-pi-descent}, that the protected Hall sector
has a cyclic model \(A_X^{\mathrm{prot}}\) with mixed complex
\((C_*(A_X^{\mathrm{prot}}),b,B_{\mathrm C})\), a cyclic class
\(\varpi_X\) representing the PTVV form, and a Connes-contraction
cochain \(\iota_{\varpi_X}\Pi_X\) satisfying
\[
(b+uB_{\mathrm C})(\iota_{\varpi_X}\Pi_X)=B_{\mathrm{ch}}^{-},
\]
where \(B_{\mathrm{ch}}^{-}\) is a negative-cyclic lift whose Hochschild
image is \(B_{\mathrm{ch}}\), and \(B_{\mathrm{ch}}\) maps to the
Gram-defect cocycle \(B\) under the Loday--Quillen--Tsygan comparison
\[
HC^2_{\mathrm{strict}}\longrightarrow HH^2
\]
\cite{LodayQuillen1984}, \cite{Tsygan1983},
\cite[\S2]{LodayCyclicHomology}.  If the induced two-step flag
homotopies have \(\operatorname{Pent}_{\Theta}=0\), then the cochain
\(\Theta_\Pi^{-}:=\iota_{\varpi_X}\Pi_X\) supplies the
negative-cyclic part of \textup{(Cyc)} and the Hochschild part of
hypothesis \((\Theta)\).  It supplies none of the Frobenius identity, the
finite-HN topology, or the Hopf-radical ideal/coideal condition.
\end{proposition}

\begin{proof}
After forgetting to Hochschild cochains, the displayed equation becomes
\(d_{\mathrm{Hoch}}\Theta_\Pi=B_{\mathrm{ch}}\), whose degree shadow is
\(B\), and the cocycle identity \(\delta B=0\) gives the degree shadow of
the triple pentagon.  The actual Hall flag coherence is still the
vanishing of \(\operatorname{Pent}_{\Theta}\).  This route is a second
construction of the \(\Theta\)-datum once the cyclic model and the
triple homotopies are available.  It is not a consequence of (P) alone.
It does not assert compatibility of fibre products over
\(\overline\Pi_X\) with the HN transitions, and it contains no information
about the completed coproduct on a radical element.
\qedhere
\end{proof}

\begin{remark}[Comparison of the two proofs]
\label{rem:cyclic-vs-orientation-step4}
\([B]=[B_{\mathrm{ch}}]\) under the Loday--Quillen--Tsygan comparison
\(HC^*_{\mathrm{strict}}\to HH^*\) of \cite{LodayQuillen1984},
\cite{Tsygan1983}, \cite[\S2]{LodayCyclicHomology}, with witnessing
cochains \(\Theta\) (PTVV--Joyce) and
\(\iota_{\varpi_X}\Pi_X\) (cyclic homology), whenever the cyclic model
and comparison cochain are supplied.
\end{remark}

\begin{remark}[Status of the descent criterion]
\label{rem:ptvv-joyce-pi-status}
Theorem~\ref{thm:ptvv-joyce-pi-descent} is a conditional descent
criterion.  Its inputs are the PTVV host (P), the reduced quotient and
HN completion (E), including finite-fibre compatibility of
\(\overline\Pi_{*}^{\Theta}\) and continuity of \(\widehat{\otimes}\), the
supplied \(S^1\)-equivariant multiplicative orientation cocycle (O), the
degree-shift cochain \(\Theta\), the Frobenius pairing (F), the
negative-cyclic lift (Cyc), and Hopf-radical stability.
Lemma~\ref{lem:explicit-multiplicative-orientation-cocycle}
constructs (O) only on a supplied projection-finite Kunneth-pure sector;
it does not construct the full compact or wrapped reduced
\(K3\times E\) protected sector.  Thus the remaining obligations are
geometric and chain-level: construct (P), (E), and (O) beyond the
Kunneth-pure sector including the HN/higher-rank extension, prove that
the supplied \(\Theta\) identifies the raw Gram defect \(B\) with
canonical degree shifts in the protected primitive bracket, kill
\(\mathfrak o_{\Theta}^{\mathrm{top}}\), \(\mathfrak o_F\), and prove
closed Hopf-radical coideal stability.  The
scalar Borcherds determinant and the denominator algebra do not discharge
these obligations.
\end{remark}

\begin{lemma}[Graded Frobenius identity from CY-3 Serre functor]
\label{lem:F-frobenius-from-cy-serre}
Suppose that the protected observable algebra
\(\mathcal A_X\) of
Definition~\ref{def:local-protected-observable-algebra}, after the
reduced \(E\)-quotient and the Costello--Li flat trivialization
\cite{CostelloRenormalization,CostelloLiBCOV,CostelloLiOpenClosedBCOV}
along the elliptic factor, is realized
as a Calabi--Yau \(A_\infty\)-category of dimension \(d=3\),
i.e.~it carries a Serre functor \(S\simeq[3]\) and a
non-degenerate cyclically invariant pairing
\[
\langle\,\cdot\,,\,\cdot\,\rangle_S
:\Hom_{\mathcal A_X}(X,Y)\otimes
\Hom_{\mathcal A_X}(Y,X[3])\longrightarrow k,
\]
in the sense of Kontsevich--Soibelman \cite{KSCoHA} (cyclic
\(A_\infty\)-structure) and PTVV
\cite{PTVV2013}/BBDJS \cite{BBDJS2015} (orientation data realising the
shift \([3]\) on the moduli of objects of \(\mathcal A_X\)).  Let
\(\widetilde P_X\subset H_*(\mathcal A_X)\) be the protected primitive
subspace, equipped with the Hall bracket \([\,\cdot\,,\,\cdot\,]\) and
the Hopf pairing \(\langle\,\cdot\,,\,\cdot\,\rangle\) of
Theorem~\ref{thm:primitive-recognition}.  Suppose, moreover, that at
every finite HN stage the primitive Hall bracket is represented by the
antisymmetrisation of the finite product \(m_{2,R}\), the cyclic trace
descends through the reduced \(E\)-quotient, and the trace, pairing, and
primitive projection commute with the transition maps.  Then the graded
Frobenius identity holds:
\[
\langle[x,y],z\rangle
+(-1)^{|x|\cdot|y|}\langle y,[x,z]\rangle=0,
\qquad x,y,z\in\widetilde P_X\ \mathrm{homogeneous},
\]
i.e.~hypothesis (F) of Theorem~\ref{thm:ptvv-joyce-pi-descent} is met.
\end{lemma}

\begin{proof}
\emph{Step 1 (Serre pairing and cyclic trace).}
A CY-\(d\) \(A_\infty\)-category \(\mathcal A_X\) is, by
\cite{KSCoHA} (\S~10), an \(A_\infty\)-category equipped with a
quasi-isomorphism \(S\xrightarrow{\sim}[d]\) of bimodules and a
non-degenerate cyclically symmetric pairing
\(\langle\,\cdot\,,\,\cdot\,\rangle_S\) on
\(\Hom_{\mathcal A_X}(-,-)\), of total degree \(-d\).  Equivalently,
there is a chain-level cyclic trace
\(\tr_S:\Hom_{\mathcal A_X}(X,X)\to k[-d]\) satisfying
\(\tr_S(f\circ g)=(-1)^{|f|\cdot|g|}\tr_S(g\circ f)\) for composable
homogeneous \(f,g\) (loc.~cit., Lemma~10.2.4).  PTVV
\cite{PTVV2013} produce the underlying \((-d)\)-shifted symplectic
form on \(\mathfrak M_{X,c}\); BBDJS \cite{BBDJS2015} extend the
orientation/d-critical datum that realises \(S\simeq[d]\) at chain
level on the perfect-complex moduli.  Costello--Li
\cite{CostelloRenormalization,CostelloLiBCOV,CostelloLiOpenClosedBCOV}
flat trivialization along the elliptic
factor reduces \(d=4\) to \(d=3\), so the discussion takes \(d=3\) and the
identification \(\langle x,y\rangle=\tr_S(x\cdot y)\), where
\(\cdot\) is the cup product on the protected primitive subspace.

\emph{Step 2 (Frobenius from cyclic invariance).}
Specialise to homogeneous primitives \(x,y,z\in\widetilde P_X\) and
expand the Hall bracket as the graded commutator
\([x,y]=x\cdot y-(-1)^{|x|\cdot|y|}y\cdot x\) (the bracket on
primitives in a connected graded Hopf algebra is the antisymmetrised
product, as part of the primitive Lie-superalgebra structure assumed in
Theorem~\ref{thm:primitive-recognition}).  Then
\begin{align*}
\langle[x,y],z\rangle
&=\tr_S\bigl((x\cdot y-(-1)^{|x|\cdot|y|}y\cdot x)\cdot z\bigr)\\
&=\tr_S(x\cdot y\cdot z)-(-1)^{|x|\cdot|y|}\tr_S(y\cdot x\cdot z).
\end{align*}
Cyclic invariance of \(\tr_S\) applied to the second term gives
\(\tr_S(y\cdot x\cdot z)=(-1)^{|y|\cdot(|x|+|z|)}\tr_S(x\cdot z\cdot y)\),
and applied to the first gives
\(\tr_S(x\cdot y\cdot z)=(-1)^{|x|\cdot(|y|+|z|)}\tr_S(y\cdot z\cdot x)\).
Substituting and re-collecting,
\[
\langle[x,y],z\rangle=
-(-1)^{|x|\cdot|y|}\tr_S\bigl(y\cdot(x\cdot z-(-1)^{|x|\cdot|z|}z\cdot x)\bigr)
=-(-1)^{|x|\cdot|y|}\langle y,[x,z]\rangle,
\]
which is (F).

\emph{Step 3 (Finite-stage chain-level lift).}
The cyclic trace \(\tr_S\) is a strict invariant on the
\(A_\infty\)-homotopy category by \cite{KSCoHA}, \S~10.2; on
\(d\)-critical thickenings it lifts to perfect-complex chain level by
\cite{BBDJS2015} (the cyclic structure on the vanishing-cycle dg
algebra) and PTVV \cite{PTVV2013} (the shifted symplectic form
descends to the cotangent complex of \(\mathfrak M_{X,c}\)).  By the
finite-stage hypotheses, this cyclic trace, the product, the pairing, and
the primitive projector all descend through the reduced \(E\)-quotient and
commute with HN transitions.  The identity of Step~2 therefore holds at
each finite \(R\) and passes to the completed protected primitive
subspace \(\widetilde P_X\).  A cyclic trace on an auxiliary model would
not prove the Frobenius identity for the Hall bracket unless these
finite-stage compatibilities were supplied.
\qedhere
\end{proof}

\begin{remark}
Lemma~\ref{lem:F-frobenius-from-cy-serre} derives (F) from the
CY-\(3\) Serre functor of \(\mathcal A_X\), parallel to the derivation
through the squaring isomorphism
\(o_c^{\otimes 2}\simeq\det\mathrm{RHom}(\mathcal C,\mathcal C)\) of
Definition~\ref{def:orientation-line} and the Hopf pairing of
Theorem~\ref{thm:primitive-recognition}.  Both derivations meet at
\(\langle\,\cdot\,,\,\cdot\,\rangle=\tr_S(\,\cdot\,\cdot\,\cdot\,)\), the
BBDJS \cite{BBDJS2015} cyclic upgrade of the PTVV
\cite{PTVV2013} \((-1)\)-shifted symplectic form, and produce the same
sign convention \((-1)^{|x|\cdot|y|}\) on the Gram degree
\(c_x+c_y+c_z=0\).  It proves only \(\mathfrak o_F=0\); it does not
prove \(\mathfrak o_{\Theta}^{\mathrm{top}}=0\), coideal stability of the
Hopf radical, a no-extra-relations theorem, or PBW compatibility.  It is
therefore one input to the full Dirac--Igusa realization certificate, not
a substitute for it.
\end{remark}

\begin{proposition}[Finite normal-ordering closure criterion]
\label{prop:finite-normal-ordering-closure-criterion}
Fix a successor arrow \(R^+\to R\).  Suppose a finite Hall--Dirac atlas
\(\mathfrak A_R\) and its successor transition are supplied through the
normal-ordering lane, and suppose the following finite data hold.
\begin{enumerate}
\item[\textup{(N1)}] The coefficient dg categories, central translations,
and degree-truncation transitions satisfy
Lemma~\ref{lem:finite-picard-normal-ordering-lift}.
\item[\textup{(N2)}] The Joyce--Kontsevich--Soibelman pull-push product,
coproduct, and finite Hopf pairing are strictly compatible with the
successor transition after \(\Theta_\Pi\)-transport.
\item[\textup{(N3)}] The \(S^1\)-equivariant lift
\(\Theta_{\Pi,R}^{-}\) satisfies
\[
(b+uB_{\mathrm C})\Theta_{\Pi,R}^{-}=B_{\mathrm{ch},R}^{-},
\]
and its Hochschild shadow is
\(d_{\mathrm{Hoch}}\Theta_{\Pi,R}=B_{\mathrm{ch},R}\).
\item[\textup{(N4)}] The two translated products over every finite
two-step Hall flag agree after inserting the Hall associator and
Joyce--Upmeier orientation transport.
\item[\textup{(N5)}] The transported bracket is the graded commutator of
the finite product on \(H^0\), so the Jacobiator is the image of the
associator and the \(\Theta\)-pentagon.
\item[\textup{(N6)}] The finite cyclic trace satisfies the CY-\(3\)
Serre-functor criterion of
Lemma~\ref{lem:F-frobenius-from-cy-serre}; equivalently
\(\mathfrak o_{F,R}=0\).
\item[\textup{(N7)}] The finite Hopf pairing is product-coproduct adjoint,
its quotient tensor pairing is non-degenerate, and the radical kernels
are preserved by the successor transition, as in
Lemma~\ref{lem:finite-hopf-adjointness-radical-test}.
\end{enumerate}
Then the finite normal-ordering diagrams \textup{(NO1)--(NO7)} of
Proposition~\ref{prop:finite-normal-ordering-verification-diagrams}
commute at the arrow \(R^+\to R\).  Hence the seven finite obstruction
classes
\[
\mathfrak o^{\mathrm{top}}_{\Theta,R^+R},\quad
\mathfrak o^{\mathrm{Hoch}}_{\Theta,R},\quad
\mathfrak o^{\mathrm{tri}}_{\Theta,R},\quad
\mathfrak o^{\mathrm{Jac}}_{\Theta,R},\quad
\mathfrak o_{F,R},\quad
\mathfrak o^{\mathrm{cyc}}_{\Theta,R},\quad
\mathfrak o^{\mathrm{rad}}_{\Theta,R}
\]
vanish at that finite stage.  Conversely, the first failed item among
\textup{(N1)--(N7)} is the corresponding obstruction component unless an
independent finite null-homotopy for the same \textup{(NO)} diagram is
supplied.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:finite-picard-normal-ordering-lift}, \textup{(N1)}
kills the finite fibre square \textup{(NO1)} and the Hochschild part of
\textup{(NO3)}.  Hypothesis \textup{(N2)} is exactly the product,
coproduct, and pairing square \textup{(NO2)}.  Hypothesis \textup{(N3)}
kills the negative-cyclic part of \textup{(NO3)}, as in
Proposition~\ref{prop:negative-cyclic-normal-ordering-route}.  Hypothesis
\textup{(N4)} is \textup{(NO4)}.  Under \textup{(N5)}, associativity and
\textup{(NO4)} imply the finite Jacobi identity, so \textup{(NO5)}
vanishes.  Hypothesis \textup{(N6)} is exactly \textup{(NO6)} by
Lemma~\ref{lem:F-frobenius-from-cy-serre}.  Finally,
Lemma~\ref{lem:finite-hopf-adjointness-radical-test} proves the coideal
part of \textup{(NO7)}, while \textup{(NO6)} proves the Lie-ideal part.
Transition preservation of the finite radical kernels is the finite
closedness condition needed before passing to the inverse limit.
\end{proof}

\begin{remark}[Unitarity]
This paper uses the protected index, the virtual determinant, and
the Borcherds denominator algebra.  A holomorphic \(E_3\)-factorization
algebra in cochains is part of the open Dirac--Igusa realization
certificate, not a positive Hilbert-space construction already in hand.  Negative
coefficients \(f(nm,l)\) record an odd excess in a protected supertrace
or in a \(K_0\)-representative; actual parity dimensions require an
additional Hilbert-space or denominator-algebra parity datum.  If the
untwisted compactification is unitary, the statement that survives the
twist is right-moving cohomology, protected integration, and the signed
index.  Reflection positivity is not a hypothesis of the Borcherds
denominator theorem.
\end{remark}

\begin{lemma}[Cyclotomic-spectrum construction of the multiplicative
orientation cocycle; alternative source for hypothesis (O) of
Theorem~\textup{\ref{thm:ptvv-joyce-pi-descent}}]
\label{lem:cyclotomic-multiplicative-orientation}
Let \(\mathcal F_X\) be the protected observable algebra of
Definition~\textup{\ref{def:local-protected-observable-algebra}},
graded by supplied algebraic/effective charge
\(c\in\Gamma_{X,\sigma}^{\mathrm{eff}}\subset
\Gamma_X^{\mathrm{alg}}\subset\Gamma_X^{\mathrm{form}}\), and let
\(\{o_c\}_{c\in\Gamma_{X,\sigma}^{\mathrm{eff}}}\) be the orientation lines of
Definition~\textup{\ref{def:orientation-line}}.  Suppose:
\begin{enumerate}
\item[\textup{(C1)}] \emph{(Cyclotomic host.)} Each charged sector
\(\mathcal F_{X,c}\) is realised as a connective cyclotomic spectrum
in the sense of Nikolaus--Scholze \cite{NikolausScholze}; the
\(p\)-typical cyclotomic structure map
\(\varphi_p:\mathcal F_{X,c}\to(\mathcal F_{X,c})^{tC_p}\) is the
Frobenius inherited from the chiral product on
\(\operatorname{Ran}(E)\).  Equivalently, the underlying spectrum
\(HH(\mathcal F_{X,c})\) carries the natural \(S^1\)-action by the
Connes operator \(B\) of Goodwillie \cite{Goodwillie1985}, with
genuine \(S^1\)-fixed points
\(HC^-(\mathcal F_{X,c}):=HH(\mathcal F_{X,c})^{hS^1}\).
\item[\textup{(C2)}] \emph{(Determinant track.)} The orientation line
\(o_c\) lifts to a unit
\(\widehat o_c\in\pi_0HC^-(\mathcal F_{X,c})\) representing the
graded determinant
\(\det\mathrm{RHom}(\mathcal C,\mathcal C)^{1/2}\) of
Definition~\textup{\ref{def:orientation-line}} in the \(S^1\)-equivariant
periodic Picard groupoid, in the sense of
Joyce--Upmeier \cite{JoyceUpmeier}.
\item[\textup{(C3)}] \emph{(Strict tensor compatibility.)} The
external product on \(\{\mathcal F_{X,c}\}\) is symmetric monoidal as
a map of cyclotomic spectra,
\(\mathcal F_{X,c}\boxtimes\mathcal F_{X,c'}\to\mathcal F_{X,c+c'}\),
intertwining \(\varphi_p\) on each side.
\end{enumerate}
Then there exists a multiplicative orientation cocycle
\[
\mu_{c,c'}\,:\;o_{c+c'}\;\xrightarrow{\ \sim\ }\;o_c\otimes o_{c'},
\qquad c,c'\in\Gamma_{X,\sigma}^{\mathrm{eff}},
\]
with the following properties:
\begin{enumerate}
\item[\textup{(i)}] (Strict pentagon.)
\(\mu_{c+c',c''}\circ\mu_{c,c'}=\mu_{c,c'+c''}\circ\mu_{c',c''}\) as
maps of \(HC^-\)-modules, with no higher coherence remainder.
\item[\textup{(ii)}] (\(S^1\)-equivariance.) Each \(\mu_{c,c'}\) is
an \(S^1\)-equivariant map of cyclotomic spectra; the Connes operator
\(B\) intertwines source and target.
\item[\textup{(iii)}] (PTVV compatibility.) The Tate construction
\((-)^{tC_p}\) carries \(\mu_{c,c'}\) to a comparison of Frobenius
twists \(\mathcal F_{X,c}^{(p)}\otimes\mathcal F_{X,c'}^{(p)}\to
\mathcal F_{X,c+c'}^{(p)}\) compatible with the PTVV \cite{PTVV2013}
\((-1)\)-shifted symplectic form on \(\mathfrak M_{X,c}\), in the
sense that \(\mu_{c,c'}\) restricts on the underlying graded
determinants to the symplectic-Lagrangian comparison map of
\cite{JoyceUpmeier}.
\end{enumerate}
In particular, hypothesis (O) of
Theorem~\textup{\ref{thm:ptvv-joyce-pi-descent}} is satisfied, and the
construction of \(\{\mu_{c,c'}\}\) is independent of the Costello--Li
flat Calabi--Yau pairing and of any K\"unneth decomposition of
\(\mathcal F_X\) along \(K3\times E\).
\end{lemma}

\begin{proof}
\emph{Step 1 (Construction of \(\mu_{c,c'}\) in \(HC^-\)).}  Apply the
\(S^1\)-fixed-points functor \((-)^{hS^1}\) to the symmetric monoidal
external product of (C3): the resulting map
\[
HC^-(\mathcal F_{X,c})\otimes HC^-(\mathcal F_{X,c'})
\;\longrightarrow\;
HC^-(\mathcal F_{X,c+c'})
\]
is a strict map of \(\mathbb E_\infty\)-algebras in cyclotomic spectra
by Nikolaus--Scholze \cite[Cor.~II.1.7, Thm.~II.6.9]{NikolausScholze},
since \((-)^{hS^1}\) is lax symmetric monoidal and the cyclotomic
Frobenius \(\varphi_p\) is itself symmetric monoidal.  Take
\(\widehat o_c\) and \(\widehat o_{c'}\) as in (C2); their product
under this map lifts the right-hand side of the desired isomorphism
\(o_c\otimes o_{c'}\), and divides the lift \(\widehat o_{c+c'}\) of
\(o_{c+c'}\) to define
\(\mu_{c,c'}:=\widehat o_{c+c'}\cdot
(\widehat o_c\boxtimes\widehat o_{c'})^{-1}\).  The Connes operator
\(B\) acts trivially on units of \(\pi_0\), so \(\mu_{c,c'}\) is
\(S^1\)-equivariant on the nose.

\emph{Step 2 (Strict pentagon from \(\mathbb E_\infty\)-associativity).}
The pentagon
\(\mu_{c+c',c''}\circ\mu_{c,c'}=\mu_{c,c'+c''}\circ\mu_{c',c''}\) is
the \(\pi_0\)-shadow of the strict associator of the
\(\mathbb E_\infty\)-algebra structure on \(\bigoplus_c HC^-(\mathcal F_{X,c})\)
in cyclotomic spectra.  Strictness follows because Nikolaus--Scholze
\cite[Thm.~I.1.13]{NikolausScholze} present the cyclotomic
\(\infty\)-category as a strict \(\mathbb E_\infty\)-monoidal limit
along the Frobenius diagram; the homotopy-coherent pentagon
collapses to an on-the-nose identity at the level of
\(\pi_0\)-units.  No higher coherence datum is required, because
\(\pi_0HC^-\) is a discrete commutative monoid and units satisfy strict
associativity in any commutative monoid.

\emph{Step 3 (\(S^1\)-equivariance built in).}  By construction
\(HC^-=HH^{hS^1}\) is the genuine \(S^1\)-fixed-points spectrum, so
every map produced by Step~1 is \(S^1\)-equivariant.  The Connes
operator \(B\) is the generator of the \(S^1\)-action on \(HH\)
\cite{Goodwillie1985}, and \(B\) acts as a derivation on \(HC^-\);
it kills \(\pi_0\)-units, hence kills \(\mu_{c,c'}\) as a higher
homotopy.

\emph{Step 4 (Tate-construction comparison with PTVV).}  Apply
\((-)^{tC_p}\) to the equation defining \(\mu_{c,c'}\).  The
Frobenius \(\varphi_p\) intertwines source and target by (C1) and (C3),
so \(\mu_{c,c'}^{tC_p}\) is the comparison of Frobenius twists
\(\mathcal F_{X,c}^{(p)}\otimes\mathcal F_{X,c'}^{(p)}\to
\mathcal F_{X,c+c'}^{(p)}\).  Restrict to the underlying graded
determinants: the symplectic structure on
\(\mathfrak M_{X,c}\) of PTVV \cite{PTVV2013} is the
\((-1)\)-shifted symplectic form whose square root is \(o_c\)
\textup{(Definition~\ref{def:orientation-line})}; under
\((-)^{tC_p}\) this form is sent to the Tate-Frobenius pairing on
\(\det\mathrm{RHom}(\mathcal C,\mathcal C)^{(p)}\), which by
Joyce--Upmeier \cite[multiplicative orientation
construction]{JoyceUpmeier} agrees with the
symplectic-Lagrangian comparison map.  Compatibility (iii) follows.

The data \(\{\mu_{c,c'}\}\) is a multiplicative
orientation cocycle satisfying (i)--(iii), so hypothesis (O) of
Theorem~\ref{thm:ptvv-joyce-pi-descent} holds.  The construction
factors through the cyclotomic-spectrum machinery of Nikolaus--Scholze
\cite{NikolausScholze} and the Connes-\(B\) calculus of
Goodwillie \cite{Goodwillie1985}; it does not invoke Costello--Li
chiral pairings, K\"unneth decompositions of \(\mathcal F_X\) along
\(K3\times E\), or any compactness datum beyond (C1)--(C3).  \qedhere
\end{proof}

\begin{remark}
Hypotheses (C1), (C2), (C3) are open for \(K3\times E\): (C1) asks
\(\mathcal F_{X,c}\) to carry a cyclotomic structure in the
Nikolaus--Scholze sense \cite{NikolausScholze}; (C2) asks orientation
lines to lift to \(\pi_0HC^-\) units, refining
Definition~\ref{def:orientation-line}; (C3) asks symmetric monoidality
of \(\{\mathcal F_{X,c}\}\) at the cyclotomic level.  The cocycle
\(\mu_{c,c'}\) is built from the Hochschild--cyclic machinery of
\(\mathcal F_X\) alone, supplying an alternative construction of
hypothesis (O) disjoint from the Costello--Li flat Calabi--Yau pairing
and from any K\"unneth decomposition.
\end{remark}

\begin{definition}[Sectorial Hall truncation]
\label{def:sectorial-hall-truncation}
Suppose an extension-closed compact Hall category graded by the additive
formal lattice \(\Gamma_X^{\mathrm{form}}\) of
Definition~\ref{def:additive-physical-charge-lattice}, with actual
charges in a supplied algebraic/effective support semigroup, together with
the Gram map \(\Pi_X\), a stability/HN/support datum
\(\sigma=(Z_\sigma,\mathcal P_\sigma)\), and semistable stacks
\(\mathfrak M_{\sigma,S,c}^{ss}\) for
\(c\in\Gamma_{X,\sigma}^{\mathrm{eff}}\subset
\Gamma_X^{\mathrm{alg}}\subset\Gamma_X^{\mathrm{form}}\).
Fix a strict
sector \(S\subset\C^\times\) of angular width \(<\pi\), with no active
semistable ray on its boundary.  Choose \(\vartheta\) so that
$$
h_S(c):=\Re(e^{-i\vartheta}Z_\sigma(c))>0
$$
on every nonzero semistable class with central charge in \(S\).
For \(R>0\), set
$$
F_{\sigma,S}(R)
=\{c\mid \mathfrak M_{\sigma,S,c}^{ss}\ne\varnothing,\
0<h_S(c)\le R\},
$$
and
$$
\Gamma_{\sigma,S}^{HN}(R)
=\left\{c_1+\cdots+c_k\ \middle|\
c_i\in F_{\sigma,S}(R),\
\sum_i h_S(c_i)\le R\right\}.
$$
If an oriented critical Hall object
\(\mathcal H_{\sigma,S}^{or}\) has been constructed, put
$$
\mathcal H_{\sigma,S}^{>R}
=\prod_{h_S(c)>R}\mathcal H_{\sigma,S,c}^{or},
\qquad
\mathsf F_R\mathcal H_{\sigma,S}^{or}
=\mathcal H_{\sigma,S}^{or}/\mathcal H_{\sigma,S}^{>R}.
$$
\end{definition}

\begin{lemma}[Conditional finite charge-support Hall quotient]
\label{prop:sectorial-hall-truncation}
A nonzero additive heart cannot have finite nonzero charge support in
\(\Gamma_X^{\mathrm{form}}\).  The pushed-forward active support
\(\Gamma_{\mathrm{act}}\subset\Gamma_{\mathrm{gram}}\) is not additive.
The finite charge-support Hall object is therefore not a finite
active-support heart.

Assume the support property, the
HN property, finite type of the
semistable stacks in bounded \(h_S\)-height, and the oriented critical
Hall correspondences.  Then \(F_{\sigma,S}(R)\) and
\(\Gamma_{\sigma,S}^{HN}(R)\) are finite,
\(\mathcal H_{\sigma,S}^{>R}\) is a two-sided Hall ideal, and
\(\mathsf F_R\mathcal H_{\sigma,S}^{or}\) is a finite charge-support
Hall quotient.
The compact sectorial Hall object is the completed inverse system
$$
\widehat{\mathcal H}_{\sigma,S}^{or}
=\varprojlim_R\mathsf F_R\mathcal H_{\sigma,S}^{or}.
$$
\end{lemma}

\begin{proof}
If a heart contains an object of nonzero charge \(c\), it contains
all finite direct sums of that object, hence all charges \(kc\).
Since \(\Gamma_X^{\mathrm{form}}\) is torsion-free, the charge support is
infinite.  Also \((0,-1,0)\in\Gamma_{\mathrm{act}}\), while
\((0,-2,0)\notin\Gamma_{\mathrm{act}}\), so active support is not
additive.

For semistable classes in \(S\), the strict-sector condition gives
\(h_S(c)\ge \kappa|Z_\sigma(c)|\) for some \(\kappa>0\).  The support
property and discreteness of the numerical lattice make
\(F_{\sigma,S}(R)\) finite.  The function \(h_S\) is positive and
additive on extensions in the sector; hence HN sums of total height
\(\le R\) form a finite set and the subspace of height \(>R\) is a
two-sided Hall ideal.  The inverse limit is the \(h_S\)-adic Hall
completion.  This supplies the charge-index finiteness part of the
finite Hall package; the full certificate also includes finite-type
d-critical substacks, finite-dimensional protected cohomology, and
proper/admissible pull-push geometry.
\end{proof}

\begin{definition}[First-order Dirac--Igusa \(D_0\)-certificate]
\label{def:first-order-d0-certificate}
Fix a stability/HN sector \((\sigma,S)\) as in
Definition~\textup{\ref{def:sectorial-hall-truncation}}.  The certificate
operates under two explicit standing hypotheses:
\begin{itemize}
\item[\textup{[K3$\times$E-fin]}] \emph{Finite-type semistable substacks
at bounded HN height.}  For every \(R>0\), the substack of
\(\sigma\)-semistable objects in \(\mathsf{D}^b(\mathrm{Coh}(K3\times E))\)
of HN height \(\le R\) and active charge in
\(F_{\sigma,S}(R)\) is of finite type over \(\mathbb C\).
K3-surface finite-wall and HN technology motivates this hypothesis; the
\(K3\times E\) threefold case is not in the cited literature and is taken
as part of the supplied datum.
\item[\textup{[ML]}] \emph{Mittag--Leffler descent for the HN inverse
system.}  The transition maps \(\rho_{R'R}\) of clauses (D0-F)--(D0-S) below
satisfy \(\lim^1=0\) on every finite \(\Gamma_R^{\mathrm{test}}\)-supported
piece.  Equivalently, the inverse system is uniformly surjective on each
finite charge slice; the completed Dirac--Igusa state is then a Lie object
in the strict sense rather than only a pro-Lie object.
\end{itemize}
The recognition theorem of
Theorem~\textup{\ref{thm:dirac-pfaffian-recognition-conditional}} reads as
a strict isomorphism only after both hypotheses are granted.  If [ML] fails,
the recognition statement weakens to a pro-comparison.

Write
\(\Gamma_R^{HN}:=\Gamma_{\sigma,S}^{HN}(R)\).  For
\(c\in\Gamma_R^{HN}\), put
\[
\mathcal T_R(c)=
\left\{
\sum_{1\le i<j\le k}B(c_i,c_j)\ \middle|\
c=c_1+\cdots+c_k,\ c_i\in F_{\sigma,S}(R),\
\sum_i h_S(c_i)\le R
\right\}.
\]
The empty decomposition is allowed for \(c=0\), giving \(T=0\).
The finite normal-ordered support at height \(R\) is
\[
\widehat\Gamma_R=
\{(c,T)\mid c\in\Gamma_R^{HN},\ T\in\mathcal T_R(c)\}
\subset\widehat\Gamma_X,
\qquad
\Gamma_R^\Pi:=\overline\Pi_X(\widehat\Gamma_R)
\subset\Gamma_{\mathrm{gram}}.
\]
The label \(T\) is not an extra brane charge and not a new moduli
factor.  It is finite normal-ordering coefficient data attached to an HN
word, equivalently a central-translation label for the coefficient
system.  The same underlying total charge \(c\) may appear with several
such labels before a no-overcount theorem is supplied.  Thus
\(\widehat\Gamma_R\) is finite coefficient-system data; functorial
descent of these labels through the finite Hall correspondences is part
of the \(D_0\)-certificate.
The coefficient label must also be lossless.  For a label \((c,T)\), let
\(\mathcal W_R(c,T)\) be the finite set of HN words whose normal-ordering
label is \((c,T)\), let \(\mathcal H^{or}_{R,w}\) denote the iterated
extension-correspondence object attached to \(w\), and let
\(\mathcal H^{or}_{R,(c,T)}\) be the summand labelled by \((c,T)\) when
the finite source kernel is supplied.  The no-overcount residual
\[
\mathfrak o^{\mathrm{no}}_{R,c,T}:=
\operatorname{Cone}\!\left(
\bigoplus_{w\in\mathcal W_R(c,T)}\mathcal H^{or}_{R,w}
\longrightarrow
\mathcal H^{or}_{R,(c,T)}
\right)
\]
is an object of the finite derived category of source coefficient
complexes.  Its acyclicity records that the normal-ordering labels
neither duplicate nor lose source summands.  It is finite-stage source
data, not a consequence of the lattice identity for \(\overline\Pi_X\).

For nonzero \(\gamma=(n,l,m)\in\Gamma_{\mathrm{gram}}\), set the finite
target exponent
\[
a_\Delta(\gamma)=
\begin{cases}
f(nm,l),&\gamma\in\Gamma_{\mathrm{eff}},\\
0,&\gamma\notin\Gamma_{\mathrm{eff}}.
\end{cases}
\]
Fix also a proper height
\[
h_\Delta:\Gamma_{\mathrm{gram}}\longrightarrow\Z_{\ge0},
\qquad
h_\Delta(n,l,m)=|n|+|l|+|m|
  \]
on the Gram-index lattice.  The \(D_0\) bookkeeping also fixes a
nondecreasing cofinal target-window schedule
\[
N_R^\Delta\in\Z_{\ge0},\qquad
R'\ge R\Rightarrow N_{R'}^\Delta\ge N_R^\Delta,\qquad
\sup_R N_R^\Delta=\infty .
\]
This schedule is finite-window bookkeeping, not a relation between HN
height and automorphic height.  To make each transition-obstruction
stage a finite datum, fix a cofinal discrete subsystem
\[
\mathcal R=\{R_0<R_1<R_2<\cdots\}\subset\mathbb R_{>0},
\qquad R_\nu\to\infty,
\]
and take all inverse limits below over \(\mathcal R\).  Cofinality does
not change the completed HN object or the target exhaustion; the
finite-type substack and proper-correspondence assertions are the
separate geometric entries of the same certificate.  For
\(R=R_\nu\) write \(R^+=R_{\nu+1}\).  Transition maps for non-successor
arrows are composites of the successor maps.  Thus the independent
transition obstruction at a stage is a finite obstruction, not an
infinite product of defects over all larger heights.  In what follows,
\(R\) denotes an element of this cofinal subsystem.

Define the finite target and test windows
\[
\Gamma_{\Delta,R}
:=\{\gamma\in\Gamma_{\mathrm{eff}}\setminus\{0\}\mid
h_\Delta(\gamma)\le N_R^\Delta\},
\qquad
\Gamma_R^{\mathrm{test}}
:=(\Gamma_R^\Pi\setminus\{0\})\cup\Gamma_{\Delta,R}.
\]
\[
\Gamma_R^{\Pi,+}:=\Gamma_R^\Pi\cap\Gamma_{\mathrm{eff}},
\qquad
\Gamma_R^{\mathrm{test},+}
:=(\Gamma_R^{\Pi,+}\setminus\{0\})\cup\Gamma_{\Delta,R}.
\]
The superscript \(+\) denotes the cusp-positive Pfaffian half; the full
Borcherds--Kac--Moody double also has the opposite root spaces and is
tested separately in the primitive-recognition theorem.
Write
\[
A_R:=\{\gamma\in\Gamma_R^{\mathrm{test},+}\mid a_\Delta(\gamma)\ne0\},
\qquad
Z_R:=\{\gamma\in\Gamma_R^{\mathrm{test},+}\mid a_\Delta(\gamma)=0\}.
\]
The inclusion \(A_R\subset\Gamma_R^{\Pi,+}\) is not built into the target
schedule; it is a finite source-coverage residual tested below.
The set \(\widehat\Gamma_R\), and hence
\(\Gamma_R^\Pi\), \(\Gamma_{\Delta,R}\), and
\(\Gamma_R^{\mathrm{test}}\), is finite by
Lemma~\ref{prop:sectorial-hall-truncation} and properness of
\(h_\Delta\).  Cofinality of \(N_R^\Delta\) makes the target windows
exhaust \(\Gamma_{\mathrm{eff}}\setminus\{0\}\).  For \(R'\ge R\) the
inclusions
\[
\widehat\Gamma_R\subset\widehat\Gamma_{R'},\qquad
\Gamma_R^\Pi\subset\Gamma_{R'}^\Pi,\qquad
\Gamma_{\Delta,R}\subset\Gamma_{\Delta,R'}
\]
hold.  A first-order Dirac--Igusa \(D_0\)-certificate for
\(X=K3\times E\) is the choice of the schedule \(N_R^\Delta\) above,
together with a compatible inverse system of finite-stage
state/observable packages
\[
D_{0,R}=
\bigl(\mathcal H^{or}_{R},\mathcal F_{R}^{D_0},K_R^\Pi,
P_R^\Pi,m_R,\Delta_R,[\,\cdot\,,\,\cdot\,]_R,I_R^{\mathrm{prot}},
\Theta_{\Pi,R},\Theta_{\Pi,R}^{-},\mathfrak D_{X,R},
\mathscr L_{\mathrm{Pf},R},\operatorname{pf}_{X,R},\iota_R^{obs}\bigr),
\qquad R\in\mathcal R,
\]
together with successor transition maps whose composites give every
non-successor arrow.  If the transition residuals below vanish and the
composite transition identities hold, the inverse limit is denoted
\[
D_0(X;\sigma,S)=
\bigl(\widehat{\mathcal H}^{or}_{\sigma,S},
\mathcal F_X^{D_0},K_X^\Pi,P_X^\Pi,\mathfrak D_X,
\Theta_\Pi,\Theta_\Pi^{-},\mathscr L_{\mathrm{Pf},X},
\operatorname{pf}_X,\iota_X^{obs}\bigr).
\]
The clauses are the following.
\begin{enumerate}
\item[\textup{(D0-F)}] \emph{Finite-stage maps and transitions.}
At height \(R\), all state, observable, primitive, Pfaffian, and
comparison data are defined on the finite support
\(\widehat\Gamma_R\) and its Gram image \(\Gamma_R^\Pi\).  The stage
carries Hall product, coproduct, primitive bracket, and protected
integration maps
\[
m_R,\qquad \Delta_R,\qquad [\,\cdot\,,\,\cdot\,]_R,\qquad
I_R^{\mathrm{prot}},
\]
and a charge-preserving observable comparison
\[
\iota_R^{obs}:\mathcal F_R^{D_0}\longrightarrow
\mathsf{Den}_{\Delta_5,E}.
\]
For the successor arrow \(R^+\to R\) there are transition maps
\[
\rho^H_{R^+R}:\mathcal H^{or}_{R^+}\to\mathcal H^{or}_{R},\qquad
\rho^F_{R^+R}:\mathcal F_{R^+}^{D_0}\to\mathcal F_R^{D_0},\qquad
\rho^K_{R^+R}:K_{R^+}^\Pi\to K_R^\Pi,\qquad
\rho^P_{R^+R}:P_{R^+}^\Pi\to P_R^\Pi,
\]
and compatible maps \(\rho^{\mathrm{Pf}}_{R^+R}\) on Pfaffian lines.  These
maps are degree-truncation maps: after projection to
\(\widehat\Gamma_R\), \(\Gamma_R^\Pi\), and
\(\Gamma_R^{\mathrm{test}}\), all summands of HN height \(>R\) are zero.
For a non-successor \(R'\ge R\), the map \(\rho_{R'R}\) is the composite
of the successor maps.  Let
\(\pi^{\Delta}_{R^+R}\) denote the finite target truncation on
\(\mathsf{Den}_{\Delta_5,E}\) and on
\(\C[\Gamma_{\Delta,R^+}]\to\C[\Gamma_{\Delta,R}]\).  The transition residual
\[
\mathfrak o^{\mathrm{tr}}_{R^+R}
\]
is the finite tuple of defect maps, in the corresponding finite Hom
spaces over \(\Gamma_R^{\mathrm{test}}\), asserting compatibility of
\(\rho_{R^+R}\) with
\[
m,\quad \Delta,\quad [\,\cdot\,,\,\cdot\,],\quad I^{\mathrm{prot}},
\quad \Theta_\Pi,\quad \Theta_\Pi^{-},\quad \mathfrak D,\quad \iota^{obs},
\quad \operatorname{pf}.
\]
For example it includes the defects
\[
\rho^F_{R^+R}m_{R^+}-m_R(\rho^F_{R^+R}\otimes\rho^F_{R^+R}),\qquad
\rho^P_{R^+R}[\,\cdot\,,\,\cdot\,]_{R^+}
-[\,\rho^P_{R^+R}(\cdot),\rho^P_{R^+R}(\cdot)\,]_R,
\]
\[
I_R^{\mathrm{prot}}\rho^F_{R^+R}
-\pi^\Delta_{R^+R}I_{R^+}^{\mathrm{prot}},\qquad
\iota_R^{obs}\rho^F_{R^+R}
-\pi^\Delta_{R^+R}\iota_{R^+}^{obs},\qquad
\rho^K_{R^+R}\mathfrak D_{X,R^+}
-\mathfrak D_{X,R}\rho^K_{R^+R},\qquad
\rho^{\mathrm{Pf}}_{R^+R}(\operatorname{pf}_{X,R^+})
-\operatorname{pf}_{X,R}.
\]
The certificate requires
\(\mathfrak o^{\mathrm{tr}}_{R^+R}=0\) for every successor arrow.  The
zero means a chosen finite equality or null-homotopy in the indicated Hom
complex.  Non-successor compatibility is then the corresponding composite
equality; if non-successor maps are recorded separately, the evident
cocycle identity for \(R''\ge R'\ge R\) is also part of the finite
transition datum.  These equalities are finite-stage data, not formal
consequences of the inverse-limit notation.

\item[\textup{(D0-S)}] \emph{State object; conditional datum, open
construction.}
A certificate supplies an oriented critical Hall/factorization inverse
system whose completed state side is
\[
\widehat{\mathcal H}^{or}_{\sigma,S}
=\varprojlim_R\mathsf F_R\mathcal H_{\sigma,S}^{or}
\]
formed first on the finite HN quotients of
Definition~\ref{def:sectorial-hall-truncation}.  Each finite quotient
carries finite-type semistable substacks, extension correspondences,
vanishing-cycle coefficients, orientation lines, Hall product and
coproduct maps, and protected integration.  All products, coproducts,
brackets, pairings, and comparison maps are defined on the finite
quotients and are continuous for the inverse limit.  This clause is a
conditional datum; Lemma~\ref{prop:sectorial-hall-truncation}
proves only the finite-first formal shape once the Hall object and the
HN/support hypotheses are supplied.

\item[\textup{(D0-Q)}] \emph{Reduced quotient and orientation obstruction
classes; conditional trivializations.}
Let \(\mathsf{St}_R\) be the finite stable-stratum index set in the
chosen finite-type atlas at height \(R\).  For every
\(\mathcal C\in\mathsf{St}_R\), with stable stratum
\(\mathfrak M^{\mathrm{st}}_{R,\mathcal C}\subset\mathcal H_R^{or}\), the
certificate includes the computed obstruction
tuple
\[
\mathfrak o^{or}_{R,\mathcal C}=
\left(
\alpha^{\mathrm{red}}_{R,\mathcal C},\
\alpha^{E,\mathrm{free}}_{R,\mathcal C},\
\{(\widetilde\beta^{E,N}_{R,\mathcal C},
\lambda^{E,N}_{R,\mathcal C})\}_{N\in\mathcal N_R(\mathcal C)}
\right),
\]
where
\[
\alpha^{\mathrm{red}}_{R,\mathcal C}
\in H^2(\mathfrak M^{\mathrm{red}}_{R,\mathcal C};\mathbb F_2),
\qquad
\alpha^{E,\mathrm{free}}_{R,\mathcal C}
\in H^2(BE;\mathbb F_2),
\]
and
\[
\widetilde\beta^{E,N}_{R,\mathcal C}
\in H^2_{E[N]}(\mathfrak M^{\mathrm{st}}_{R,\mathcal C};\mathbb F_2)
\]
is present for each finite stabilizer \(E[N]\) appearing at height \(R\).
Its point-stabilizer restriction is a class
\(\beta^{E,N}_{R,\mathcal C}\in H^2(BE[N];\mathbb F_2)\) only after the
mixed Borel terms, stabilizer action on stratum cohomology, and
spectral-sequence differentials have vanished.  After
\(\widetilde\beta^{E,N}_{R,\mathcal C}\) has been null-trivialized, the
certificate also records the finite linearization character
\[
\lambda^{E,N}_{R,\mathcal C}\in H^1(BE[N];\mathbb F_2)
\]
and requires the zero character.  The certificate supplies
null-trivializations of all degree-two classes and zero finite
degree-one characters, compatible with the transition maps.  These are
exactly the ordinary reduced gerbe, connected \(BE\)-linearization,
finite-stabilizer gerbe, and finite-stabilizer \(H^1\)-character
obstructions of Lemma~\ref{lem:E-equivariant-descent-obstruction}.  Their
vanishing gives the reduced quotient and orientation line needed for the
\(D_0\) Pfaffian.  Equivalently, (D0-Q) supplies the finite-stage
quotient-orientation character system of
Proposition~\ref{prop:finite-stage-quotient-orientation-character-system}
for the local, wrapped, mixed, and flag strata at height \(R\).  It does
not compute the Weyl monodromy character; that is the separate content of
(O1)\(^+\) and (O2) in
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}.

\item[\textup{(D0-C)}] \emph{Charge completion; proved lattice input.}
The finite quotients are graded by the normal-ordered charge extension
\[
\widehat\Gamma_X=\Gamma_X^{\mathrm{phys}}\oplus_B\Gamma_{\mathrm{gram}},
\qquad
(c,T)\star(c',T')=(c+c',T+T'+B(c,c')),
\]
and the observable Gram degree is
\[
\overline\Pi_X(c,T)=\Pi_X(c)-T.
\]
A semistable one-particle generator of charge \(c\) is placed in
\((c,0)\); composite HN words are labelled by the corresponding
\((c,T)\in\widehat\Gamma_R\).  Thus \(T=0\) is not asserted for every
normal-ordered composite.
The bracket of homogeneous states satisfies
\[
[\widetilde P_{X,(c,T)},\widetilde P_{X,(c',T')}]
\subset
\widetilde P_{X,(c,T)\star(c',T')}.
\]
At height \(R\) this statement is read inside \(\widehat\Gamma_R\), with
targets of height \(>R\) killed by the quotient.  The finite-support
assertion follows from Lemma~\ref{prop:sectorial-hall-truncation}; the
additivity of \(\overline\Pi_X\) follows from
Lemma~\ref{lem:b-cocycle-central-extension}; no chain-level Hall
strictification is claimed by this lattice statement.

\item[\textup{(D0-O)}] \emph{State/observable interface; imported target,
conditional source.}
A certificate supplies, at finite height \(R\), source observable shadows
\(\mathcal F_R^{D_0}\).  Their compatible inverse limit
\(\mathcal F_X^{D_0}\) is obtained from
\(\widehat{\mathcal H}^{or}_{\sigma,S}\) by the supplied
\(K3\)-to-\(E\) specialization and, in positive elliptic degree, by a
hybrid wrapped repair.  It is a source object.  The target observable
algebra is the target current envelope
\(\mathsf{Den}_{\Delta_5,E}\) of
Proposition~\ref{prop:formal-current-envelope}.  The interface is a
charge-preserving comparison morphism
\[
\iota_X^{obs}:\mathcal F_X^{D_0}\longrightarrow
\mathsf{Den}_{\Delta_5,E}
\]
whose constant-current primitive restriction is
\[
\iota_X^{\Prim}:
H^0\Prim_{\mathrm{prot}}
(\overline\Pi_{X,*}^{\Theta}\mathcal F_X^{D_0})
\longrightarrow
\mathfrak g_{\Delta_5}.
\]
The target side is imported from Gritsenko--Nikulin; the source and the
comparison morphism are conditional data.  The finite observable residual
\[
\mathfrak o^{obs}_R
\]
is the finite tuple of defects measuring whether \(\iota_R^{obs}\) is a
morphism for the finite product, coproduct, primitive bracket, protected
trace, and constant-current primitive comparison after projection to
\(\Gamma_R^{\mathrm{test}}\).  Here
\(m_{\Delta_5},\Delta_{\Delta_5},[\,\cdot\,,\,\cdot\,]_{\Delta_5}\), and
\(\operatorname{tr}_{\Delta_5}\) denote the corresponding finite target
operations induced from \(\mathsf{Den}_{\Delta_5,E}\).  Thus
\(\mathfrak o^{obs}_R\) includes
\[
\iota_R^{obs}m_R-m_{\Delta_5}(\iota_R^{obs}\otimes\iota_R^{obs}),
\qquad
\Delta_{\Delta_5}\iota_R^{obs}-(\iota_R^{obs}\otimes\iota_R^{obs})\Delta_R,
\]
\[
\iota_R^{\Prim}([x,y]_R)-[\iota_R^{\Prim}x,\iota_R^{\Prim}y]_{\Delta_5},
\qquad
I_R^{\mathrm{prot}}-\operatorname{tr}_{\Delta_5}\iota_R^{obs}.
\]
The certificate requires \(\mathfrak o^{obs}_R=0\).  This is a finite
comparison with the imported observable target.  It is not the
presentation-level primitive isomorphism, injectivity, surjectivity, or
no-extra-relations theorem; those belong to the full recognition
certificate.  No target truncation, target bar--cobar counit, or
homotopy inverse to \(\iota_R^{obs}\) is allowed to define
\(\mathcal F_R^{D_0}\).  The source object is supplied first, and the
arrow points source-to-target.

\item[\textup{(D0-N)}] \emph{Exact normal-ordered descent; conditional
finite-topology, Hochschild, triple, Jacobi, Frobenius, cyclic, and radical
trivializations.}
At finite height \(R\), the datum \(\Theta_{\Pi,R}\) is the central
translation cochain
\[
\Theta_{\Pi,R}(c)=\mathsf T_{-\Pi_X(c)}
\]
in the coefficient dg category of
Definition~\ref{def:normal-ordering-coefficient-dg-category}, and
\(\Theta_{\Pi,R}^{-}\) is its negative-cyclic lift.  For
\((c,T),(c',T')\in\widehat\Gamma_R\), it gives coherent degree-shift
quasi-isomorphisms
\[
\Theta_{(c,T),(c',T')}:
\Pi_X(c+c')-T-T'-B(c,c')
\longrightarrow
\bigl(\Pi_X(c)-T\bigr)+\bigl(\Pi_X(c')-T'\bigr)
\]
on primitive bracket targets.  Equivalently,
\(\Theta_\Pi\) categorifies the equality
\[
\overline\Pi_X((c,T)\star(c',T'))
=\overline\Pi_X(c,T)+\overline\Pi_X(c',T')
\]
and turns the upstairs physical Hall bracket into a
\(\Gamma_{\mathrm{gram}}\)-graded bracket after
\(\overline\Pi_{X,*}^{\Theta}\).  This is exactly the conditional input of
Theorem~\ref{thm:ptvv-joyce-pi-descent}; constructing
\(\Theta_\Pi\) on the reduced compact/wrapped sector is open.
The finite coefficient pieces are
\[
(\overline\Pi_{R,*}^{\Theta}V_R)_\gamma
=
\prod_{\substack{(c,T)\in\widehat\Gamma_R\\
\overline\Pi_X(c,T)=\gamma}}(V_R)_{(c,T)},
\]
and this product is finite.  For the successor arrow \(R^+\to R\), the
transition maps must
commute with these finite fibre products, with \(m_R^\Theta\), with
\(\Delta_R^\Theta\), and with the finite pairing.  The corresponding
transition defect is
\[
\mathfrak o^{\mathrm{top}}_{\Theta,R^+R}
=
\left(
\mathfrak o^{\mathrm{fib}}_{\Theta,R^+R},
\mathfrak o^{m}_{\Theta,R^+R},
\mathfrak o^{\Delta}_{\Theta,R^+R},
\mathfrak o^{\langle\, ,\,\rangle}_{\Theta,R^+R}
\right),
\]
with the components defined in
Theorem~\ref{thm:ptvv-joyce-pi-descent}.  Its vanishing is the finite
statement that the completed fibre products and
\(\widehat{\otimes}\)-operations exist as inverse limits.
Equivalently, with
\[
B_{\mathrm{ch},R}(c,c'):=\mathsf T_{B(c,c')},
\]
the certificate supplies trivializations
\[
d_{\mathrm{Hoch}}\Theta_{\Pi,R}=B_{\mathrm{ch},R},
\qquad
(b+uB_{\mathrm C})\Theta_{\Pi,R}^{-}=B_{\mathrm{ch},R}^{-},
\]
and the triple and Jacobi coherences of
Theorem~\ref{thm:ptvv-joyce-pi-descent}.  Thus the finite-stage
obstruction classes
\[
\mathfrak o^{\mathrm{top}}_{\Theta,R^+R},\qquad
\mathfrak o^{\mathrm{Hoch}}_{\Theta,R},\qquad
\mathfrak o^{\mathrm{tri}}_{\Theta,R},\qquad
\mathfrak o^{\mathrm{Jac}}_{\Theta,R},\qquad
\mathfrak o_{F,R},\qquad
\mathfrak o^{\mathrm{cyc}}_{\Theta,R},\qquad
\mathfrak o^{\mathrm{rad}}_{\Theta,R}
\]
vanish in the finite-topology, Hochschild, triple-coherence,
Chevalley--Eilenberg, cyclic-Frobenius, negative-cyclic, and Hopf-radical
ideal/coideal groups displayed there.  The radical class is read as the
ordered pair
\((\mathfrak o^{\mathrm{rad,Lie}}_{\Theta,R},
\mathfrak o^{\mathrm{rad,coid}}_{\Theta,R})\).  Equivalently, every
successor arrow must satisfy the finite tests
\textup{(NO1)--(NO7)} of
Proposition~\ref{prop:finite-normal-ordering-verification-diagrams}.
Proposition~\ref{prop:finite-normal-ordering-closure-criterion} records
the finite closure proved by the preceding finite tests: the
Picard/Hochschild and finite-fibre parts are formal after the coefficient
dg category and degree-truncation topology are supplied, while the cyclic
lift, two-step flag coherence, Frobenius trace, and Hopf-adjoint radical
tests remain source-side data.

\item[\textup{(D0-D)}] \emph{First-order object; conditional.}
There are perfect finite-stage \(\Gamma_R^\Pi\)-graded supercomplexes
\(K_R^\Pi\), compatible under \(\rho^K_{R^+R}\), with finite-dimensional
parity pieces.  At each finite stage there is a \(\Z/2\)-odd skew-adjoint
first-order operator/algebra
\[
\mathfrak D_{X,R}:K_R^\Pi\longrightarrow K_R^\Pi
\]
whose primitive symbol is the finite normal-ordered Hall bracket on
\(P_R^\Pi\).  The successor transition compatibility
\[
\rho^K_{R^+R}\mathfrak D_{X,R^+}
=\mathfrak D_{X,R}\rho^K_{R^+R}
\]
is one component of \(\mathfrak o^{\mathrm{tr}}_{R^+R}=0\).  The inverse
limits are
\[
K_X^\Pi=\varprojlim_R K_R^\Pi,\qquad
\mathfrak D_X=\varprojlim_R\mathfrak D_{X,R}.
\]
Their protected primitive cohomology is
\[
P_X^\Pi
=H^0\Prim_{\mathrm{prot}}
(\overline\Pi_{X,*}^{\Theta}\mathcal F_X^{D_0}),
\]
and the primitive symbol of \(\mathfrak D_X\) is the normal-ordered Hall
bracket.  The term
``first-order'' means the Pfaffian/primitive object before scalar
squaring; it does not assert an analytic Dirac operator on an already
constructed Hilbert space.

\item[\textup{(D0-Pf)}] \emph{Pfaffian line, finite support, and
normalization; conditional datum, imported automorphic target.}
For every \(R\) there is a Pfaffian line
\(\mathscr L_{\mathrm{Pf},R}\) attached to \(\mathfrak D_{X,R}\) and to the
finite reduced orientation line of the stage, with a finite squaring
isomorphism
\[
\mathscr L_{\mathrm{Pf},R}^{\otimes2}\simeq
\mathscr L_{\det,R}.
\]
The successor maps \(\rho^{\mathrm{Pf}}_{R^+R}\) commute with these square
isomorphisms, as part of
\(\mathfrak o^{\mathrm{tr}}_{R^+R}=0\), and identify the inverse limit
with a Pfaffian line
\[
\mathscr L_{\mathrm{Pf},X},\qquad
\mathscr L_{\mathrm{Pf},X}^{\otimes2}\simeq
\mathscr L_{\det,X},
\]
attached to \(\mathfrak D_X\) and the orientation line on the
state object, together with a normalized section
\(\operatorname{pf}_{X,R}\) at height \(R\) and
\(\operatorname{pf}_X=\varprojlim_R\operatorname{pf}_{X,R}\).  Let
\(x^\gamma=q^nr^ls^m\) for \(\gamma=(n,l,m)\).  Projected to the finite
monomial span of \(\Gamma_R^{\Pi,+}\), the Borcherds-cusp
product formula below is not a construction of the compact source.  It is
the finite determinant calculation after the primitive spaces, the
first-order block decomposition, and the Pfaffian line have been
supplied.  For \(\gamma\in\Gamma_R^{\Pi,+}\) write
\(P^{\Pi,+}_{R,\gamma}:=P^\Pi_{R,\gamma}\), and for
\(\gamma\notin\Gamma_R^{\Pi,+}\) set \(P^{\Pi,+}_{R,\gamma}=0\).  For a
homogeneous primitive mode in cusp-positive degree
\(\gamma\in\Gamma_R^{\Pi,+}\), the elementary two-term Pfaffian/Koszul
block is the skew block
\[
J_{\gamma}=
\begin{pmatrix}
0&1-x^\gamma\\
-(1-x^\gamma)&0
\end{pmatrix},
\]
acting on
\(P^{\Pi,+}_{R,\gamma}\oplus(P^{\Pi,+}_{R,\gamma})^\vee[1]\); its Pfaffian
contribution, with the supplied Pfaffian orientation convention, is
\((1-x^\gamma)^{\sdim P^{\Pi,+}_{R,\gamma}}\).  Equivalently, an even
basis vector contributes \((1-x^\gamma)\), an odd basis vector contributes
\((1-x^\gamma)^{-1}\), and the exponent is
\(\dim P^{\Pi,+}_{R,\gamma,\bar0}
-\dim P^{\Pi,+}_{R,\gamma,\bar1}\).  Thus the
expansion is
\[
\operatorname{pf}_{X,R}|_{\mathfrak c_\infty}
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{\substack{\gamma\in\Gamma_R^{\Pi,+}\\ \gamma\ne0}}
(1-x^\gamma)^{\sdim P^{\Pi,+}_{R,\gamma}}.
\]
The Pfaffian half is not the full BKM double: it records the
cusp-positive product factors.  Negative root representatives and the
Cartan/imaginary completion enter the Lie recognition statement after the
primitive bracket and pairing are supplied.  Write
\[
p^{\bar0}_{R,\gamma}:=\dim P^{\Pi,+}_{R,\gamma,\bar0},\qquad
p^{\bar1}_{R,\gamma}:=\dim P^{\Pi,+}_{R,\gamma,\bar1}.
\]
The finite-stage support, signed-parity, and leading-coefficient defects
\[
\mathfrak o^{\mathrm{supp}}_{R,\gamma}:=
\begin{cases}
P^{\Pi,+}_{R,\gamma},& a_\Delta(\gamma)=0,\\
0,&a_\Delta(\gamma)\ne0,
\end{cases}
\qquad
\mathfrak o^{\mathrm{par}}_{R,\gamma}
:=p^{\bar0}_{R,\gamma}-p^{\bar1}_{R,\gamma}
-a_\Delta(\gamma)\in\mathbb Z,
\]
\[
\mathfrak o^{\mathrm{lead}}_R:=\operatorname{lc}_{\mathfrak c_\infty}
(\operatorname{pf}_{X,R})-64\in\mathbb C
\]
are required to satisfy
\[
\mathfrak o^{\mathrm{supp}}_{R,\gamma}=
\mathfrak o^{\mathrm{par}}_{R,\gamma}=0
\quad(\gamma\in\Gamma_R^{\mathrm{test},+}),
\qquad
\mathfrak o^{\mathrm{lead}}_R=0 .
\]
The support residual is an actual super-vector-space residual, not only a
\(K_0\) class: its vanishing excludes invisible even--odd cancelling
primitive pieces in target-zero degrees.  The parity residual is a signed
superdimension residual; the Borcherds product fixes this integer, not a
canonical split of the nonzero multiplicity into even and odd compact
states.  For a fixed \(R\), these residuals decide only the supplied
finite test window.  The inclusion of active target degrees in the source
image is itself a residual condition, not a consequence of the automorphic
product.  Thus the target windows do not prove compact source coverage;
they test it inside the source-covered finite stages.  If the residuals
vanish compatibly for all \(R\), and the cofinal windows are
source-covered, the limit section has the prescribed
expansion
\[
\operatorname{pf}_X|_{\mathfrak c_\infty}
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{\gamma=(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{\sdim P^\Pi_{X,\gamma}},
\]
with
\[
\sdim P^\Pi_{X,(n,l,m)}=f(nm,l).
\]
No source-window theorem is asserted here.  The schedule
\(N_R^\Delta\) is an external finite target test; it becomes a source
coverage theorem only after the supplied finite Hall stages prove
\(A_R\subset\Gamma_R^{\Pi,+}\) compatibly in \(R\).
The equality of the resulting product with \(\Delta_5\) is imported from
the Borcherds--Gritsenko--Nikulin product.  The compact parity pieces
realizing these signed dimensions are conditional data, not a consequence
of the scalar OP square.  No source computation of the primitive
exponents is claimed here.  The equalities
\(\sdim P^\Pi_{X,(n,l,m)}=f(nm,l)\) are part of the supplied
\(D_0\)-certificate, tested against the imported Borcherds product.  A
source computation would derive these signed dimensions from the compact
Hall correspondences, orientation data, and protected integration before
comparison with the target denominator algebra.  A section-level statement
\(\operatorname{pf}_X=\Delta_5\) also requires a supplied isomorphism from
the Pfaffian line \(\mathscr L_{\mathrm{Pf},X}\) to the pullback of the
automorphic weight-five line, compatible with the cusp trivialization and
the squaring maps.  The finite product formula alone is only a recognition
test after such line-comparison data have been supplied.
\end{enumerate}
\end{definition}

\begin{remark}[Chamber dependence and wall-crossing]
\label{rem:chamber-conditional-wall-crossing}
The certificate is indexed by a Bridgeland-type supplied stability/HN sector
\((\sigma,S)\), in the K3-surface lineage of
\cite{BridgelandK3Stability,BayerMacriProjectivity}.  The lattice cocycle
\(B(c,c')\) is chamber-independent: it
records only Mukai pairings of fixed lattice vectors.  The compact
Hall/factorization side \(D_0(X;\sigma,S)\) is chamber-dependent: the
finite-type semistable substacks change under wall-crossing, and the
Kontsevich--Soibelman wall-crossing formula relates Hall counts in
adjacent chambers.

If the certificate
\(D_0(X;\sigma,S)\) is supplied in chamber \(\sigma\), then the
normal-ordered map \(\overline\Pi_X\) remains a homomorphism and the
recognition target is \(\mathfrak g_{\Delta_5}\) provided the chamber
identifications hold for the OP/DT scalar import of
Proposition~\textup{\ref{prop:op-normalization}}; that the chosen
\(\sigma\) lies in the OP/DT chamber, or that the wall-crossing transport
is compatible with \(\overline\Pi_X\), is a separate conjectural input.
The manuscript does not assert chamber-independence of the recognition
target; that is an open conjecture.
\end{remark}

\begin{proposition}[Finite Pfaffian window obstruction]
\label{prop:finite-pfaffian-window-obstruction}
Fix \(R\in\mathcal R\), and put
\[
A_R:=\{\gamma\in\Gamma_R^{\mathrm{test},+}\mid a_\Delta(\gamma)\ne0\},
\qquad
Z_R:=\{\gamma\in\Gamma_R^{\mathrm{test},+}\mid a_\Delta(\gamma)=0\}.
\]
For any supplied finite source package \(D_{0,R}\), vanishing of
\(\mathfrak o^{\mathrm{supp}}_{R,\gamma}\) and
\(\mathfrak o^{\mathrm{par}}_{R,\gamma}\) on
\(\Gamma_R^{\mathrm{test},+}\) is equivalent to the two finite conditions
\[
P^{\Pi,+}_{R,\gamma}=0\quad(\gamma\in Z_R),
\qquad
\gamma\in\Gamma_R^{\Pi,+},\quad
p^{\bar0}_{R,\gamma}-p^{\bar1}_{R,\gamma}=a_\Delta(\gamma)
\quad(\gamma\in A_R).
\]
In particular every active target degree in the cofinal window must
already occur in the source image:
\[
A_R\subset\Gamma_R^{\Pi,+} .
\]
The strongest object constructed from the automorphic input alone at
this stage is the finite \(K_0\)-Pfaffian shadow
\[
[\mathsf P_{\Delta,R}^{K_0}]
:=\sum_{\gamma\in\Gamma_R^{\mathrm{test},+}}
a_\Delta(\gamma)[\C_\gamma]
\in
K_0\!\left(\Gamma_R^{\mathrm{test},+}\text{-graded }
\mathrm{sVect}_{\mathrm{fd}}\right)
\]
and the finite formal section
\[
\operatorname{pf}^{K_0}_{\Delta,R}
:=
64q^{1/2}r^{1/2}s^{1/2}
\prod_{\gamma\in\Gamma_R^{\mathrm{test},+}}
(1-x^\gamma)^{a_\Delta(\gamma)} .
\]
This shadow is a target invariant.  It is not a compact Hall object, not
a Pfaffian line on the reduced quotient, and not a first-order operator.
For \(\gamma\in A_R\), the pair of compact parity dimensions is not
determined by the shadow: adding a finite vector space \(W_\gamma\) in
both parities replaces
\[
(P^\Pi_{R,\gamma,\bar0},P^\Pi_{R,\gamma,\bar1})
\quad\text{by}\quad
(P^\Pi_{R,\gamma,\bar0}\oplus W_\gamma,
 P^\Pi_{R,\gamma,\bar1}\oplus W_\gamma)
\]
and leaves the finite product, support test, signed-parity test, and
leading coefficient unchanged.  Thus compact parity pieces on the
cofinal target windows are extra source data.  They cannot be constructed
from \(\Delta_5\), from the denominator product, or from the OP scalar
square.
\end{proposition}

\begin{proof}
If \(\gamma\in Z_R\), the support residual is
\(\mathfrak o^{\mathrm{supp}}_{R,\gamma}=P^{\Pi,+}_{R,\gamma}\); its vanishing
is exactly the first displayed condition.  If \(\gamma\in A_R\) and
\(\gamma\notin\Gamma_R^{\Pi,+}\), the convention
\(P^{\Pi,+}_{R,\gamma}=0\) gives
\(\mathfrak o^{\mathrm{par}}_{R,\gamma}=-a_\Delta(\gamma)\ne0\).  Hence
vanishing forces \(\gamma\in\Gamma_R^{\Pi,+}\), and then the parity
residual is exactly
\[
p^{\bar0}_{R,\gamma}-p^{\bar1}_{R,\gamma}-a_\Delta(\gamma)=0.
\]
This proves the equivalence and the active-window coverage.

The finite formal section is obtained by applying the
superdeterminant formula to the \(K_0\)-class
\([\mathsf P_{\Delta,R}^{K_0}]\).  This construction takes place in the
Grothendieck group of finite graded super vector spaces.  It contains no
extension correspondences, no orientation line, and no skew-adjoint
finite operator.  Finally, the replacement by
\(W_\gamma\oplus\Pi W_\gamma\) has zero class in \(K_0\), so it does not
change \(p^{\bar0}_{R,\gamma}-p^{\bar1}_{R,\gamma}\) or any product
depending only on signed superdimension.  The actual parity pieces are
therefore invisible to the finite Pfaffian shadow.
\end{proof}

\begin{openproblem}[Source computation of the Igusa exponents]
\label{op:source-computation-igusa-exponents}
Derive the equalities
\[
\sdim P^{\Pi,+}_{R,\gamma}=a_\Delta(\gamma),
\qquad
\gamma\in\Gamma_R^{\mathrm{test},+},
\]
from the compact Hall correspondences, orientation data, quotient descent,
and protected integration at finite height \(R\), before comparison with
the imported Borcherds product.  The present certificate only tests a
supplied source object against the target exponents.
\end{openproblem}

\begin{definition}[Finite Hall source kernel and downstream normal-ordering
package]
\label{def:finite-hall-source-kernel}
Fix \(R\in\mathcal R\).  A finite Hall source kernel at height \(R\) is
first the following source-side geometric datum, before normal-ordering,
protected integration, or comparison with the Borcherds target:
\[
\mathfrak S^{\mathrm{geom}}_R=
\bigl(
\mathfrak M_{R,\widehat c},\Phi_{R,\widehat c},
\mathfrak E_{R,\widehat c,\widehat c'},
p_{R,\widehat c,\widehat c'},q_{R,\widehat c,\widehat c'},
o_{R,\widehat c},\mu^{or}_{R}
\bigr)_{\widehat c,\widehat c'\in\widehat\Gamma_R}.
\]
The finite source package used by the \(D_0\)-certificate is
\[
\mathfrak S_R=
\bigl(
\mathfrak S^{\mathrm{geom}}_R,
I_R^{\mathrm{prot}},
\Theta_{\Pi,R},\Theta_{\Pi,R}^{-}
\bigr).
\]
Only \(\mathfrak S^{\mathrm{geom}}_R\) is the common finite geometric
kernel.  The protected integration map and the normal-ordering cochains
are downstream finite data; they are part of the certificate, not
consequences of the geometric kernel alone.  The requirements are finite
and source-internal.
\begin{enumerate}
\item[\textup{(S0)}] The finite direct sum of protected cohomology groups
has a supplied unit, counit, multiplication, and coproduct, making it a
finite graded bialgebra object before primitives are taken.  The counit is
denoted \(\epsilon_R\), the coproduct \(\Delta_R\), and
\[
\Prim_R:=\ker\bigl(\Delta_R-(1\otimes\mathrm{id})
-(\mathrm{id}\otimes1)\bigr)\cap\ker(\epsilon_R)
\]
is the finite primitive subobject.
\item[\textup{(S1)}] Each
\(\mathfrak M_{R,\widehat c}\) is a finite-type d-critical stack with
compactly supported BBDJS vanishing-cycle complex
\(\Phi_{R,\widehat c}\), orientation line \(o_{R,\widehat c}\), and
finite-dimensional protected cohomology.
\item[\textup{(S2)}] For every product whose target charge remains in
\(\widehat\Gamma_R\), the extension correspondence
\[
\mathfrak M_{R,\widehat c}\times\mathfrak M_{R,\widehat c'}
\xleftarrow{\ p_{R,\widehat c,\widehat c'}\ }
\mathfrak E_{R,\widehat c,\widehat c'}
\xrightarrow{\ q_{R,\widehat c,\widehat c'}\ }
\mathfrak M_{R,\widehat c\star\widehat c'}
\]
is admissible for vanishing-cycle pull-push, proper on the protected
support used by \(I_R^{\mathrm{prot}}\), and equipped with the oriented
Thom--Sebastiani transport \(\mu_R^{or}\).  If
\(\widehat c\star\widehat c'\notin\widehat\Gamma_R\), the projected
correspondence is declared zero in the finite quotient.
\item[\textup{(S3)}] The two-step extension stacks carry the usual flag
associativity isomorphisms, and the coproduct correspondences are
admissible in the same Borel--Moore or compact-support formalism.
\item[\textup{(S3')}] The multiplication and coproduct satisfy the finite
bialgebra compatibility diagram after vanishing-cycle pull-push and
orientation transport.  Consequently the supercommutator of two primitives
is again primitive at this finite stage.
\item[\textup{(S4)}] The added normal-ordering cochains
\(\Theta_{\Pi,R}\), \(\Theta_{\Pi,R}^{-}\) act on the actual finite
correspondence targets, not merely on the lattice labels.
\end{enumerate}
For a successor arrow \(R^+\to R\), a transition-compatible family of
kernels also includes truncation morphisms on stacks, extension stacks,
coefficient complexes, orientations, and protected integration maps,
with non-successor maps defined as their composites.
\end{definition}

\begin{proposition}[Finite \(D_0\) Hall source package from a supplied kernel]
\label{prop:finite-d0-hall-source-construction}
A supplied finite Hall source kernel \(\mathfrak S_R\) determines the
finite state-side Hall object, its primitive bracket, and the justified
first-order differential shadow as follows.

First set
\[
\mathcal H^{or}_{R,\widehat c}
:=
\mathrm H_c^\bullet
(\mathfrak M_{R,\widehat c},
\Phi_{R,\widehat c}\otimes o_{R,\widehat c}),
\qquad
\mathcal H^{or}_{R}:=
\bigoplus_{\widehat c\in\widehat\Gamma_R}
\mathcal H^{or}_{R,\widehat c}.
\]
This is finite-dimensional because \(\widehat\Gamma_R\) is finite and
\textup{(S1)} imposes finite protected cohomology on each summand.  The
Hall product and coproduct are the finite pull-push maps
\[
m_{R,\widehat c,\widehat c'}
=
q_{R,\widehat c,\widehat c',!}\,
\operatorname{TS}^{or}_{R,\widehat c,\widehat c'}\,
p_{R,\widehat c,\widehat c'}^*,
\]
\[
\Delta_{R,\widehat c,\widehat c'}
=
p_{R,\widehat c,\widehat c',!}\,
(\operatorname{TS}^{or}_{R,\widehat c,\widehat c'})^{-1}\,
q_{R,\widehat c,\widehat c'}^*,
\]
with zero output when the target charge leaves \(\widehat\Gamma_R\).
The two-step flag isomorphisms in \textup{(S3)} give associativity and
coassociativity at this finite height; their failure is exactly the finite
flag component of the \(D_0\) residual.

Let \(P_R\subset\mathcal H_R^{or}\) be the primitive part for
\(\Delta_R\), and put
\[
P_R^\Pi:=\overline\Pi_{R,*}^{\Theta_R}P_R .
\]
The normal-ordering cochain in \textup{(S4)} transports the supercommutator
of \(m_R\) to a finite \(\Gamma_R^\Pi\)-graded bracket
\[
[\,\cdot\,,\,\cdot\,]_{\Theta,R}:
P^\Pi_{R,\gamma}\otimes P^\Pi_{R,\gamma'}
\longrightarrow P^\Pi_{R,\gamma+\gamma'} .
\]
If the finite Jacobi diagram \textup{(NO5)} holds, this is a finite Lie
superalgebra bracket.  Equivalently, it determines the Chevalley--Eilenberg
first-order differential
\[
d_{\mathrm{CE},R}:
C^\bullet_{\mathrm{CE}}(P_R^\Pi)
\longrightarrow
C^{\bullet+1}_{\mathrm{CE}}(P_R^\Pi),
\]
the unique degree-one derivation whose quadratic part is dual to
\([\,\cdot\,,\,\cdot\,]_{\Theta,R}\).  The identity
\(d_{\mathrm{CE},R}^2=0\) is exactly the finite Jacobi identity with the
Koszul signs.  This is the first-order differential justified by the
finite Hall source core.  It is not yet the protected Dirac operator
\(\mathfrak D_{X,R}\), and it carries no Pfaffian line, unless the extra
Dirac/Pfaffian data of
Proposition~\ref{prop:finite-d0-atlas-parity-obstruction} are supplied.

For a transition-compatible family \(\mathfrak S_{R^+}\to\mathfrak S_R\),
the specified truncation morphisms induce
\[
\rho^H_{R^+R}:\mathcal H^{or}_{R^+}\to\mathcal H^{or}_{R},\qquad
\rho^P_{R^+R}:P^\Pi_{R^+}\to P^\Pi_R .
\]
They are morphisms of finite Hall objects precisely when the product,
coproduct, pairing, integration, and normal-ordering squares
\textup{(NO1)--(NO7)} commute.  Thus the source kernel constructs the
finite Hall source and names the exact residuals obstructing its passage
to a \(D_{0,R}\)-stage.
\end{proposition}

\begin{proof}
The direct sum is finite by finiteness of \(\widehat\Gamma_R\) and the
finite-dimensionality imposed in \textup{(S1)}.  The BBDJS
Thom--Sebastiani isomorphism, transported through the orientation
isomorphisms, identifies the vanishing-cycle coefficients on the source
of the correspondence with the coefficient system on the target.  The
properness/admissibility in \textup{(S2)} therefore makes the displayed
pull-push maps defined.  The zero convention for charges outside
\(\widehat\Gamma_R\) is exactly the finite charge-support Hall quotient
convention.
The two-step flag isomorphisms in \textup{(S3)} identify the two
parenthesized pull-push composites, hence give associativity and the
dual coproduct coherence at height \(R\).  Clause \textup{(S0)} supplies
the finite unit, counit, multiplication, and coproduct, and defines
primitives as the displayed kernel.  Clause \textup{(S3')} supplies the
finite bialgebra compatibility diagram, so the supercommutator of two
primitives is again primitive.  The normal-ordering cochain acts on the
actual correspondence targets by \textup{(S4)}, so it transports the
bracket to the additive \(\Gamma_R^\Pi\)-degree.  Finally, the
Chevalley--Eilenberg differential is the standard derivation dual to a
Lie superalgebra bracket; its square is the Jacobiator with the Koszul
signs.  The transition assertion is the same pull-push naturality applied
to the supplied truncation morphisms.
\end{proof}

\begin{proposition}[Cofinal target-window \(K_0\) parity shadow]
\label{prop:cofinal-target-window-parity-model}
For every \(R\in\mathcal R\), the target exponents construct a canonical
minimal finite super-vector-space model on the test window:
\[
\mathsf P^{\min}_{\Delta,R,\gamma}:=
\begin{cases}
\C^{a_\Delta(\gamma)}\ \hbox{in parity }\overline0,
&a_\Delta(\gamma)>0,\\
\C^{-a_\Delta(\gamma)}\ \hbox{in parity }\overline1,
&a_\Delta(\gamma)<0,\\
0,&a_\Delta(\gamma)=0,
\end{cases}
\qquad
\gamma\in\Gamma_R^{\mathrm{test},+}.
\]
It satisfies
\[
[\mathsf P^{\min}_{\Delta,R}]
=
\sum_{\gamma\in\Gamma_R^{\mathrm{test},+}}
a_\Delta(\gamma)[\C_\gamma]
=[\mathsf P_{\Delta,R}^{K_0}]
\]
and gives the formal Pfaffian section
\(\operatorname{pf}^{K_0}_{\Delta,R}\) of
Proposition~\ref{prop:finite-pfaffian-window-obstruction}.

Let \(P_R^{\Pi,+}:=P_R^\Pi|_{\Gamma_R^{\Pi,+}}\) be the cusp-positive
primitive source half constructed from a finite Hall source kernel.  On
\(\Gamma_R^{\mathrm{test},+}\), vanishing of
\(\mathfrak o^{\mathrm{supp}}_{R,\gamma}\) and
\(\mathfrak o^{\mathrm{par}}_{R,\gamma}\) is equivalent to the
Grothendieck equality
\[
[P_R^{\Pi,+}|_{\Gamma_R^{\mathrm{test},+}}]
=
[\mathsf P^{\min}_{\Delta,R}]
\]
together with active-window source coverage
\[
\{\gamma\in\Gamma_R^{\mathrm{test},+}\mid a_\Delta(\gamma)\ne0\}
\subset\Gamma_R^{\Pi,+}
\]
and actual vanishing of source primitive spaces in all target-zero
degrees.  This equality upgrades to an isomorphism of graded super vector
spaces
\[
P^{\Pi,+}_{R,\gamma}\simeq
\mathsf P^{\min}_{\Delta,R,\gamma}
\qquad(\gamma\in\Gamma_R^{\mathrm{test},+})
\]
if and only if the no-hidden-cancellation condition
\[
\min\{\dim P^{\Pi,+}_{R,\gamma,\overline0},
\dim P^{\Pi,+}_{R,\gamma,\overline1}\}=0
\]
holds for every active \(\gamma\) in the test window.  Without that extra
source condition, one may add \(W_\gamma\oplus\Pi W_\gamma\) in any active
degree without changing the Pfaffian product, the signed parity residual,
or the leading coefficient.
\end{proposition}

\begin{proof}
The definition of \(\mathsf P^{\min}_{\Delta,R,\gamma}\) gives signed
dimension \(a_\Delta(\gamma)\) in every test degree and no vector space
when \(a_\Delta(\gamma)=0\).  Hence its Grothendieck class is the
displayed finite \(K_0\)-Pfaffian shadow.  The equivalence between
vanishing residuals, active-window source coverage, and the stated
\(K_0\)-equality is exactly
Proposition~\ref{prop:finite-pfaffian-window-obstruction}, with the
support residual remembering actual source spaces in target-zero degrees.
For an active \(\gamma\), two finite super vector spaces of signed
dimension \(a_\Delta(\gamma)\) are isomorphic to the minimal model
precisely when one parity has dimension zero.  Adding
\(W_\gamma\oplus\Pi W_\gamma\) changes neither signed dimension nor any
superdeterminant depending only on signed dimension.  This proves the
last assertion.
\end{proof}

\begin{proposition}[Finite Hall--Dirac atlas and parity-lift obstruction]
\label{prop:finite-d0-atlas-parity-obstruction}
Fix \(R\in\mathcal R\).  The finite Hall source core is constructed from
the source kernel of Definition~\ref{def:finite-hall-source-kernel} by
Proposition~\ref{prop:finite-d0-hall-source-construction}.  A genuine
construction of the full finite stage \(D_{0,R}\), including the Dirac
operator and Pfaffian line, is equivalent to supplying in addition a
finite Hall--Dirac atlas
\[
\mathfrak A_R=
\bigl(
\mathfrak M_{R,\widehat c},\mathfrak E_{R,\widehat c,\widehat c'},
\Phi_{R,\widehat c},o_{R,\widehat c},\mu^{or}_{R},
\mathcal F_R^{D_0},\Theta_{\Pi,R},\Theta_{\Pi,R}^{-},\iota_R^{obs},
K_R^\Pi,\mathfrak D_{X,R},
\mathscr L_{\mathrm{Pf},R},\ell_R
\bigr)
\]
with the following data.
\begin{enumerate}
\item[\textup{(A1)}] \emph{Finite extension-closed d-critical source.}
For each \(\widehat c=(c,T)\in\widehat\Gamma_R\) there is a finite-type
d-critical stack
\(\mathfrak M_{R,\widehat c}\) with compactly supported BBDJS
vanishing-cycle coefficient complex
\(\Phi_{R,\widehat c}\).  The finite union
\(\mathfrak M_R=\coprod_{\widehat c\in\widehat\Gamma_R}
\mathfrak M_{R,\widehat c}\) is closed under those extensions whose
charge remains in \(\widehat\Gamma_R\).  Thus for
\(\widehat c,\widehat c'\), with
\(\widehat c\star\widehat c'\in\widehat\Gamma_R\), there is a finite-type
extension correspondence
\[
\mathfrak M_{R,\widehat c}\times\mathfrak M_{R,\widehat c'}
\xleftarrow{\ p_{R,\widehat c,\widehat c'}\ }
\mathfrak E_{R,\widehat c,\widehat c'}
\xrightarrow{\ q_{R,\widehat c,\widehat c'}\ }
\mathfrak M_{R,\widehat c\star\widehat c'} ,
\]
and the correspondence is empty after projection to the quotient when the
target charge leaves \(\widehat\Gamma_R\).  The two-step extension stacks
for triples in \(\widehat\Gamma_R\) satisfy the usual flag associativity
isomorphisms.
\item[\textup{(A2)}] \emph{Orientation square and quotient
linearization.}
There are orientation lines
\[
o_{R,\widehat c}^{\otimes2}
\simeq
\det\mathrm{RHom}_{\mathrm{red}}
(\mathcal C_{\widehat c},\mathcal C_{\widehat c})
\]
on the finite strata, Thom--Sebastiani orientation isomorphisms
\(\mu^{or}_{R,\widehat c,\widehat c'}\) over the extension
correspondences, and zero quotient-linearization characters for every
finite stabilizer appearing in the reduced \(E\)-quotient.  Equivalently
the classes \(\mathfrak o^{or}_{R,\mathcal C}\) of \textup{(D0-Q)}
vanish with chosen finite trivializations.
\item[\textup{(A3)}] \emph{Finite Hall operations, normal ordering, and
protected integration.}
The maps \(p_{R,\widehat c,\widehat c'}\) and
\(q_{R,\widehat c,\widehat c'}\) are admissible for vanishing-cycle
pull-push and proper on the support used by the protected trace.  The
resulting Joyce--Kontsevich--Soibelman pull-push operations define
\[
m_R,\qquad \Delta_R,\qquad [\,\cdot\,,\,\cdot\,]_R,\qquad
I_R^{\mathrm{prot}},
\]
and the source observable shadow \(\mathcal F_R^{D_0}\), normal-ordering
cochains \(\Theta_{\Pi,R}\), \(\Theta_{\Pi,R}^{-}\), and comparison map
\(\iota_R^{obs}\) are defined source-first.  They satisfy the finite flag,
coproduct, trace, observable-comparison, Hochschild, and negative-cyclic
diagrams required in \textup{(D0-F)}, \textup{(D0-O)}, and
\textup{(D0-N)}.
\item[\textup{(A4)}] \emph{Finite first-order complex.}
There is a perfect \(\Gamma_R^\Pi\)-graded supercomplex \(K_R^\Pi\) and
an odd skew-adjoint first-order endomorphism
\[
\mathfrak D_{X,R}:K_R^\Pi\to K_R^\Pi
\]
whose primitive symbol on
\[
P_R^\Pi=H^0\Prim_{\mathrm{prot}}
(\overline\Pi_{R,*}^{\Theta}\mathcal F_R^{D_0})
\]
is the Hall bracket of \textup{(A3)}.
\item[\textup{(A5)}] \emph{Pfaffian square.}
On the reduced finite quotient
\(\mathfrak Q_R:=(\mathfrak M_R/E)^{\mathrm{red}}\) there is a determinant
line \(\mathscr L_{\det,R}\) attached to \(K_R^\Pi\), a square root
\[
\eta_R:\mathscr L_{\mathrm{Pf},R}^{\otimes2}
\xrightarrow{\ \sim\ }\mathscr L_{\det,R},
\]
and a finite section \(\operatorname{pf}_{X,R}\) whose leading coefficient
at the Borcherds cusp is \(64\).
\item[\textup{(A6)}] \emph{Parity lift on the positive Pfaffian test window.}
For every \(\gamma\in\Gamma_R^{\mathrm{test},+}\) there are actual compact
primitive super-vector spaces
\[
P^{\Pi,+}_{R,\gamma}
=P^{\Pi,+}_{R,\gamma,\bar0}\oplus P^{\Pi,+}_{R,\gamma,\bar1}
\]
with
\[
\ell_R(\gamma)=
\bigl(\dim P^{\Pi,+}_{R,\gamma,\bar0},
\dim P^{\Pi,+}_{R,\gamma,\bar1}\bigr),
\]
such that \(P^{\Pi,+}_{R,\gamma}=0\) for \(a_\Delta(\gamma)=0\), and
\[
\dim P^{\Pi,+}_{R,\gamma,\bar0}
-\dim P^{\Pi,+}_{R,\gamma,\bar1}
=a_\Delta(\gamma)
\]
for \(a_\Delta(\gamma)\ne0\).  This includes the active-window source
coverage \(A_R\subset\Gamma_R^{\Pi,+}\).
\item[\textup{(A7)}] \emph{Successor transition diagrams.}
For \(R^+\to R\) there are truncation maps on the stacks, extension
stacks, coefficient complexes, first-order complexes, and Pfaffian lines
such that
\[
\begin{tikzcd}
\mathfrak E_{R^+,\widehat c,\widehat c'}
 \arrow[r,"q_{R^+}"] \arrow[d,"\tau^E_{R^+R}"']
&
\mathfrak M_{R^+,\widehat c\star\widehat c'}
 \arrow[d,"\tau^M_{R^+R}"]
\\
\mathfrak E_{R,\widehat c,\widehat c'}
 \arrow[r,"q_R"']
&
\mathfrak M_{R,\widehat c\star\widehat c'}
\end{tikzcd}
\qquad
\begin{tikzcd}
\mathfrak E_{R^+,\widehat c,\widehat c'}
 \arrow[r,"p_{R^+}"] \arrow[d,"\tau^E_{R^+R}"']
&
\mathfrak M_{R^+,\widehat c}\times
\mathfrak M_{R^+,\widehat c'}
 \arrow[d,"\tau^M_{R^+R}\times\tau^M_{R^+R}"]
\\
\mathfrak E_{R,\widehat c,\widehat c'}
 \arrow[r,"p_R"']
&
\mathfrak M_{R,\widehat c}\times
\mathfrak M_{R,\widehat c'}
\end{tikzcd}
\]
commute after projection to the finite quotient, and the induced diagrams
for \(\rho^K_{R^+R}\mathfrak D_{X,R^+}\),
\(\rho^{\mathrm{Pf}}_{R^+R}\eta_{R^+}\), and
\(\rho^{\mathrm{Pf}}_{R^+R}(\operatorname{pf}_{X,R^+})\) commute.  The
finite tuple of failures of these diagrams is denoted
\(\mathfrak o^{\mathrm{atlas}}_{R^+R}\); it is one source-level
realization of the transition residual
\(\mathfrak o^{\mathrm{tr}}_{R^+R}\).
\end{enumerate}

If \(\mathfrak A_R\) is supplied and
\(\mathfrak o^{\mathrm{atlas}}_{R^+R}=0\), then the pull-push operations,
orientation square, first-order operator, Pfaffian line, and parity lift
construct the finite package \(D_{0,R}\) of
Definition~\ref{def:first-order-d0-certificate}.  Conversely, every
constructed \(D_{0,R}\) gives such finite atlas data after forgetting to
the finite support and reduced quotient.  Thus the missing object is not
the target determinant; it is the finite atlas \(\mathfrak A_R\) and its
successor-compatible trivializations.

Moreover the two remaining Pfaffian ambiguities are exact.  The
Pfaffian square-root choices for a fixed determinant line are empty unless
\([\mathscr L_{\det,R}]\) is divisible by \(2\) in
\(\operatorname{Pic}(\mathfrak Q_R)\); when nonempty, their isomorphism
classes form a torsor under \(\operatorname{Pic}(\mathfrak Q_R)[2]\), with
the \(H^1(\mathfrak Q_R;\mathbb F_2)\) local-system shadow used in the
finite-stabilizer orientation tests.  For an active degree
\(\gamma\in A_R\), the compact parity lifts form the affine monoid
\[
\mathscr P_R(\gamma)
=
\{(u,v)\in\Z_{\ge0}^2\mid u-v=a_\Delta(\gamma)\},
\qquad
(u,v)\mapsto(u+t,v+t).
\]
The finite \(K_0\)-Pfaffian shadow fixes only the difference \(u-v\).
The no-hidden-cancellation condition
\[
\min(u,v)=0
\]
would select the unique minimal lift
\[
(u,v)=
\begin{cases}
(a_\Delta(\gamma),0),&a_\Delta(\gamma)>0,\\
(0,-a_\Delta(\gamma)),&a_\Delta(\gamma)<0,
\end{cases}
\]
but this is an extra source axiom.  It is not implied by
\(\Delta_5\), by the denominator algebra, by the OP scalar square, or by
equality in \(K_0\).
\end{proposition}

\begin{proof}
Given \(\mathfrak A_R\), clauses \textup{(A1)}--\textup{(A3)} are exactly
the finite Joyce--Kontsevich--Soibelman Hall pull-push construction with
BBDJS vanishing-cycle coefficients and Joyce--Upmeier orientation
transport.  Finiteness of the index set makes all sums and products
finite, and the two-step flag isomorphisms are precisely the associativity
and coproduct-coherence diagrams.  Clause \textup{(A4)} gives
\textup{(D0-D)}.  Clause \textup{(A5)} gives the finite Pfaffian square
and the leading coefficient condition in \textup{(D0-Pf)}.  Clause
\textup{(A6)} is exactly the vanishing of the support and parity residuals
on \(\Gamma_R^{\mathrm{test},+}\), with active-window coverage as in
Proposition~\ref{prop:finite-pfaffian-window-obstruction}.  Clause
\textup{(A7)} gives the successor compatibility diagrams; their failure
is the displayed finite residual \(\mathfrak o^{\mathrm{atlas}}_{R^+R}\),
which maps into \(\mathfrak o^{\mathrm{tr}}_{R^+R}\).  Hence the data
assemble to \(D_{0,R}\).  The converse is tautological: a constructed
finite \(D_{0,R}\) already contains the finite source stacks,
correspondences, coefficient systems, operator, Pfaffian line, and parity
pieces named above, after restriction to its finite support.

The assertion about square roots is the elementary Picard-group
classification: a line \(L\) admits a square root iff its class lies in
\(2\operatorname{Pic}(\mathfrak Q_R)\); the set of square roots, when
nonempty, is acted on simply transitively by \(2\)-torsion line bundles.
Passing to \(\mathbb F_2\)-local systems gives the
\(H^1(\mathfrak Q_R;\mathbb F_2)\) shadow.  Finally
\(\mathscr P_R(\gamma)\) is the set of nonnegative integer solutions to
one linear equation \(u-v=a_\Delta(\gamma)\).  Adding \((t,t)\) preserves
the \(K_0\) class and all product exponents.  Therefore signed dimension
does not determine compact parity pieces unless the extra condition
\(\min(u,v)=0\) is supplied.
\end{proof}

\begin{theorem}[Finite \(D_0\)-certificate: proved, imported,
conditional, and open parts]
\label{thm:first-order-d0-certificate}
This first-order certificate separates finite objects obtained from
supplied kernels and atlases from the open existence of those kernels and
atlases.
\begin{enumerate}
\item[\textup{(lattice/finite bookkeeping, conditional on supplied HN support)}]
For every \(R\in\mathcal R\), the
normal-ordered support
\(\widehat\Gamma_R\), its image \(\Gamma_R^\Pi\), the target window
\(\Gamma_{\Delta,R}\), the ambient test window
\(\Gamma_R^{\mathrm{test}}\), and the positive Pfaffian test window
\(\Gamma_R^{\mathrm{test},+}\) of
Definition~\ref{def:first-order-d0-certificate} are finite; by
cofinality of the target-window schedule, the windows
\(\Gamma_{\Delta,R}\) exhaust
\(\Gamma_{\mathrm{eff}}\setminus\{0\}\).  The lattice charge completion
\(\widehat\Gamma_X\) and the normal-ordered homomorphism
\(\overline\Pi_X\) exist and are additive, by
Lemma~\ref{prop:sectorial-hall-truncation} and
Lemma~\ref{lem:b-cocycle-central-extension}.
The exhaustion statement is target-side only; it does not assert that
every target degree lies in the image of the supplied finite Hall support.
\item[\textup{(imported)}] The target observable algebra
\(\mathsf{Den}_{\Delta_5,E}\), its constant-current denominator algebra
\(\mathfrak g_{\Delta_5}\), and the product
\[
64q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}(1-q^nr^ls^m)^{f(nm,l)}
=\Delta_5
\]
are supplied by the Borcherds--Gritsenko--Nikulin theorem and
Proposition~\ref{prop:formal-current-envelope}.
\item[\textup{(finite source package from supplied kernel)}] If, at height \(R\), a
finite Hall source kernel \(\mathfrak S_R\) in the sense of
Definition~\ref{def:finite-hall-source-kernel} is supplied, then
Proposition~\ref{prop:finite-d0-hall-source-construction} determines the
finite state object \(\mathcal H_R^{or}\), the Hall product, coproduct,
primitive bracket, normal-ordered finite primitive algebra \(P_R^\Pi\),
successor transition maps, and the Chevalley--Eilenberg first-order
differential \(d_{\mathrm{CE},R}\) justified by the finite bracket.  This
is finite algebra obtained from supplied source data at height \(R\).  It
is not yet the protected
Dirac operator \(\mathfrak D_{X,R}\) and carries no Pfaffian line unless
the extra Dirac/Pfaffian atlas data are supplied.  Independently, the
cofinal target exponents construct the minimal finite target-window
parity model
\(\mathsf P^{\min}_{\Delta,R}\) of
Proposition~\ref{prop:cofinal-target-window-parity-model}; comparison
with actual compact source primitives is exactly the support/parity and
no-hidden-cancellation test recorded there.
\item[\textup{(finite residual)}] Once the finite Hall--Dirac atlas
\(\mathfrak A_R\) of
Proposition~\ref{prop:finite-d0-atlas-parity-obstruction} is supplied,
including the finite semistable stacks, extension correspondences,
vanishing-cycle pull-push maps, protected integration maps, source
comparison, first-order complex, Pfaffian square, and compact parity
lifts at height \(R\), the obstruction tuple recorded by the finite-stage
\(D_0\) certificate is the vanishing, with compatible trivializations, of
\[
\mathfrak O_{D_0,R}:=
\left(
\mathfrak o^{\mathrm{tr}}_{R^+R},\
\{\mathfrak o^{or}_{R,\mathcal C}\}_{\mathcal C\in\mathsf{St}_R},\
\mathfrak o^{obs}_R,\
\mathfrak o^{\mathrm{top}}_{\Theta,R^+R},\
\mathfrak o^{\mathrm{Hoch}}_{\Theta,R},\
\mathfrak o^{\mathrm{tri}}_{\Theta,R},\
\mathfrak o^{\mathrm{Jac}}_{\Theta,R},\
\mathfrak o_{F,R},\
\mathfrak o^{\mathrm{cyc}}_{\Theta,R},\
\mathfrak o^{\mathrm{rad}}_{\Theta,R},\
\{\mathfrak o^{\mathrm{no}}_{R,c,T}\}_{(c,T)\in\widehat\Gamma_R},\
\{\mathfrak o^{\mathrm{supp}}_{R,\gamma}\}_{\gamma\in
\Gamma_R^{\mathrm{test},+}},\
\{\mathfrak o^{\mathrm{par}}_{R,\gamma}\}_{\gamma\in
\Gamma_R^{\mathrm{test},+}},\
\mathfrak o^{\mathrm{lead}}_R
\right).
\]
These classes are typed in
Definition~\ref{def:first-order-d0-certificate}, the no-overcount label
paragraph following \(\widehat\Gamma_R\), and
Theorem~\ref{thm:ptvv-joyce-pi-descent}.  They are not determined by
\(\Delta_5\), by the denominator algebra, or by the OP scalar square.
Vanishing here means chosen null-trivializations in the displayed finite
obstruction groups or complexes, compatible with the successor transition
\(R^+\to R\) and hence with its composites; a numerical zero in a
Grothendieck group is not such a trivialization.
The Pfaffian part has the sharp finite consequence recorded in
Proposition~\ref{prop:finite-pfaffian-window-obstruction}: active target
degrees in \(\Gamma_R^{\mathrm{test},+}\) must lie in the source image, but
the compact parity dimensions themselves remain extra source data.
\item[\textup{(conditional)}] If a tuple satisfying
Definition~\ref{def:first-order-d0-certificate} is supplied, then it
supplies hypothesis \textup{(D0)} of
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}.  Its primitive
bracket is compatible with normal-ordered descent on the nose:
\[
[P^\Pi_{X,\gamma},P^\Pi_{X,\gamma'}]_{\Theta}
\subset P^\Pi_{X,\gamma+\gamma'},
\qquad \gamma,\gamma'\in\Gamma_{\mathrm{gram}},
\]
and its Pfaffian section has the formal cusp expansion
\[
\operatorname{pf}_X|_{\mathfrak c_\infty}
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{\gamma=(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)},
\]
which the imported Borcherds--Gritsenko--Nikulin theorem identifies with
the normalized \(\Delta_5\) product at \(\mathfrak c_\infty\).  This is
not a section-level equality in the automorphic line; that conclusion
requires the supplied Pfaffian-to-automorphic comparison
\(\iota_{\mathrm{aut}}\) of
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}.
\item[\textup{(usage certificate)}] Every use of \textup{(D0)} in
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional} factors through
one of the displayed clauses of
Definition~\ref{def:first-order-d0-certificate}: finite state and
transition data through \textup{(D0-F)}--\textup{(D0-S)}, reduced
orientation descent through \textup{(D0-Q)}, source/observable comparison
through \textup{(D0-O)}, normal-ordered grading through \textup{(D0-C)}
and \textup{(D0-N)}, the protected first-order complex through
\textup{(D0-D)}, and the Pfaffian target windows, support residuals,
signed parity exponents, and leading coefficient through
\textup{(D0-Pf)}.
\item[\textup{(open)}] The compact state-side construction of
\(\widehat{\mathcal H}^{or}_{\sigma,S}\), the finite Hall source kernels
\(\mathfrak S_R\), the finite Hall--Dirac atlases
\(\mathfrak A_R\), the finite-stage hybrid wrapped object
\(\mathcal F_R^{D_0}\), the obstruction trivializations
\(\mathfrak O_{D_0,R}=0\) and
\(\mathfrak o^{\mathrm{atlas}}_{R^+R}=0\), the compatible inverse system,
the Pfaffian line on the reduced compact quotient, and the compact parity
pieces
\(P^{\Pi,+}_{R,\gamma,\bar0}\), \(P^{\Pi,+}_{R,\gamma,\bar1}\) on
\(\Gamma_R^{\mathrm{test},+}\), including vanishing in target-zero degrees,
are not constructed in this paper.  The target \(K_0\)-shadow supplies
only the signed differences; it does not trivialize the Pfaffian
square-root torsor or select a compact parity lift.
\end{enumerate}
\end{theorem}

\begin{proof}
For fixed \(R\), the set \(F_{\sigma,S}(R)\) is finite by
Lemma~\ref{prop:sectorial-hall-truncation}.  Since \(h_S\) is positive on
active semistable charges, the length of a decomposition
\(c=c_1+\cdots+c_k\) with \(\sum_i h_S(c_i)\le R\) is bounded.  Hence only
finitely many sums \(\sum_{i<j}B(c_i,c_j)\) occur, so
\(\widehat\Gamma_R\) and \(\Gamma_R^\Pi\) are finite.
The function \(h_\Delta(n,l,m)=|n|+|l|+|m|\) is proper on the lattice
\(\Gamma_{\mathrm{gram}}\), so \(\Gamma_{\Delta,R}\) is finite.  Since
\(\sup_RN_R^\Delta=\infty\), the union over all \(R\) is
\(\Gamma_{\mathrm{eff}}\setminus\{0\}\).  Thus
\(\Gamma_R^{\mathrm{test}}\) is finite.  If \(R'\ge R\), then
\(F_{\sigma,S}(R)\subset F_{\sigma,S}(R')\) and every decomposition of
height \(\le R\) is also a decomposition of height \(\le R'\); this gives
the displayed inclusions of \(\widehat\Gamma_R\), \(\Gamma_R^\Pi\), and
\(\Gamma_{\Delta,R}\).
Lemma~\ref{lem:b-cocycle-central-extension} gives associativity of
\(\star\) and
\(\overline\Pi_X((c,T)\star(c',T'))=
\overline\Pi_X(c,T)+\overline\Pi_X(c',T')\).  The imported item is
Proposition~\ref{prop:bgn-identification} together with
Theorem~\ref{thm:denominator-algebra-identity} and
Proposition~\ref{prop:formal-current-envelope}.

Proposition~\ref{prop:finite-d0-hall-source-construction} is the finite
source package determined by the displayed source kernel: the Hall vector
spaces are compactly supported vanishing-cycle cohomologies, the product
and coproduct are the finite pull-push maps, the primitive bracket is the
normal-ordered supercommutator, and the first-order CE differential is
the standard derivation dual to that finite Lie bracket.
Proposition~\ref{prop:cofinal-target-window-parity-model} constructs the
minimal target-window parity model directly from the finite exponent
function \(a_\Delta\), and identifies the exact extra condition needed to
compare it with the compact source primitives.

The residual tuple \(\mathfrak O_{D_0,R}\) is a collection of already
typed obstructions.  The transition component records compatibility in
the finite inverse system.  The quotient-orientation component is the
criterion of Lemma~\ref{lem:E-equivariant-descent-obstruction}.  The
observable component records that the source/target comparison respects
the finite product, coproduct, bracket, trace, and primitive comparison.
The next seven are the finite-topology, Hochschild, triple, Jacobi,
Frobenius, negative-cyclic, and Hopf-radical ideal/coideal obstruction
classes of Theorem~\ref{thm:ptvv-joyce-pi-descent}; the final three state exactly
the finite target coverage, absence of invisible zero-target primitive
support, signed Pfaffian multiplicity, and cusp-leading normalization
required in the Pfaffian line.  Their vanishing is therefore necessary
for the finite stage to be a \(D_0\)-stage, and, once the finite stacks,
correspondences, first-order complex, comparison map, and Pfaffian line
have been supplied, is precisely the extra trivialization data demanded by
Definition~\ref{def:first-order-d0-certificate}.

Assume the \(D_0\)-certificate.  Clause \textup{(D0-F)} gives the finite
stages and transition maps.  Clause \textup{(D0-S)} gives the HN-completed
state object on which the Hall operations are defined.  Clause
\textup{(D0-Q)} supplies the reduced quotient and orientation line used in
the Pfaffian construction.  Clause \textup{(D0-C)} places operations in the
corrected charge extension.  Clause \textup{(D0-N)} supplies the
chain-level shift categorifying the additivity of
\(\overline\Pi_X\); hence the descended primitive bracket is
\(\Gamma_{\mathrm{gram}}\)-graded.  Clause \textup{(D0-O)} supplies the
source observable shadow and comparison map.  Clauses \textup{(D0-D)} and
\textup{(D0-Pf)} supply the first-order object and its Pfaffian line.  The
support, signed-superdimension, target-window exhaustion, and
leading-coefficient conditions in \textup{(D0-Pf)}, combined with the
imported Borcherds product, give the normalized
\(\Delta_5\) cusp expansion for \(\operatorname{pf}_X\).

It remains to check the stated usage certificate in
Theorem~\ref{thm:dirac-pfaffian-recognition-conditional}.  Step 1 uses
only the supplied first-order object, the normal-ordered primitive
multiplicities, and the leading Pfaffian normalization; these are
\textup{(D0-D)} and \textup{(D0-Pf)}.  Step 2 uses the imported
Borcherds--Gritsenko--Nikulin product, not a compact construction.  Step
3 uses the Pfaffian cusp normalization from \textup{(D0-Pf)} and the
imported Oberdieck--Pixton scalar normalization.  Step 5 uses only the
supplied chiral protected first-order theory and its decategorification,
supplied by \textup{(D0-F)}--\textup{(D0-Pf)}.  Step 4 is independent of \(D_0\)
except for the existence of the Pfaffian object; its signs come from
(O1), (O1)\(^+\), and (O2).  Thus the certificate implies every use of
\textup{(D0)} and no stronger compact existence claim is made.

The final item is a status statement: none of the source-side objects or
trivializations named there is constructed by the lattice calculation, by
the denominator algebra, or by the scalar OP square.
\end{proof}

\begin{definition}[Dirac--Igusa realization certificate]
\label{def:compact-igusa-realization-datum}
A compact realization of the Igusa square root is a
Dirac--Igusa realization certificate
$$
\mathfrak K_X=(L_X,H_X,O_X,D_X,R_X).
$$
Its first-order truncation is the \(D_0\)-certificate of
Definition~\ref{def:first-order-d0-certificate}.  The full certificate
adds the orientation-monodromy, chiral Koszul, and primitive-recognition
data needed to identify the compact state-side algebra with the
Gritsenko--Nikulin target.  It is not a consequence of the Borcherds
product, the scalar Oberdieck--Pixton square, the target current envelope,
the target bar--cobar counit, or the existence of orientation lines alone.
It is the list of data whose construction would turn the virtual
determinant \(\mathcal D_X=\Delta_5\) into a compact first-order protected
realization.  The five entries have the following meanings.
\begin{enumerate}
\item[\((L_X)\)] \emph{Local charge and \(E_3\) host.}
This entry consists of the formal dyonic Mukai lattice
\(\Gamma_X^{\mathrm{form}}\), the algebraic/effective Hall support inside
it, the Gram map
\(\Pi_X:\Gamma_X^{\mathrm{form}}\to\Gamma_{\mathrm{gram}}\), and the
cocycle \(B\) of
Definition~\ref{def:additive-physical-charge-lattice} and
Lemma~\ref{lem:gram-additivity-defect}.  The Hall category is graded by
the supplied algebraic/effective charge support, not by
\(\Gamma_{\mathrm{gram}}\) itself.
\((L_X)\) also includes the normal-ordered extension
\[
\widehat\Gamma_X=\Gamma_X^{\mathrm{form}}\oplus_B\Gamma_{\mathrm{gram}},
\qquad
\overline\Pi_X(c,T)=\Pi_X(c)-T,
\]
and the primitive saturated lifts of
Lemma~\ref{lem:primitive-lift-every-gram-triple}.  Finally, it includes
a supplied charge-completed holomorphic
\(E_3\)-factorization algebra, denoted \(\mathcal A^{E_3}_X\), on
\(X=K3\times E\), finite-first after the sectorial HN quotients of
Lemma~\ref{prop:sectorial-hall-truncation}.  A compact
holomorphic-Chern--Simons/BV construction, if it satisfies descent, the
quantum master equation, and anomaly cancellation in the completed charge
category, is a candidate source for this datum.  The datum also includes
a fixed \(E_3\)-formality point, a chain-level homotopy/framing datum
for the chosen operadic model, compact-support control, and continuity
of the \(E_3\) operations across
the finite HN inverse system.

\item[\((H_X)\)] \emph{Hybrid \(K3\)-to-\(E\) factorization shadow.}
This entry consists of a supplied finite-first
K3-to-\(E\) source interface in the sense of
Definition~\ref{def:compact-e3-source-interface}, a chain-level
specialization \(\mathrm{Sp}^{\mathrm{ch}}_{K3,E}\), and named comparison
maps \(\kappa_E\) (chiral-Koszul) and \(\pi_*^{\mathrm{ch}}\)
(proper-pushforward identification), with the triple zigzag
$$
\mathcal A^{E_3}_X
\xrightarrow{\ \mathrm{Sp}^{\mathrm{ch}}_{K3,E}\ }
\mathcal F_X^{(0)}
\xrightarrow{\ \kappa_E\ }
\mathcal F_X^{(1)}
\xrightarrow{\ \pi_*^{\mathrm{ch}}\ }
(p_E)_*\mathcal A^{E_3}_X
$$
of equivalences in the projection-finite sectors.  In the wrapped
elliptic-degree sectors, the required filling is the finite-HN inverse
system whose limit is the hybrid object
\(\mathcal F_X^{\mathrm{hyb}}\) of
Definition~\ref{def:hybrid-wrapped-factorization-certificate}.  Thus
\((H_X)\) includes the hybrid Ran base
\(\operatorname{Ran}^{\mathrm{hyb}}(E)\), projection-finite local
sectors \(\mathcal F_{\alpha,R}^{\mathrm{loc}}(U)\), rigidified wrapped
prequotient sectors \(\mathcal G_{\eta,R}^{\mathrm{wr}}\) with anchors
\(\lambda_{\eta,R}\), finite correspondence categories
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), and the three finite operation
families
\[
\mu_R^{\mathrm{loc}},\qquad
\mu_R^{\mathrm{hyb}},\qquad
\mu_R^{\mathrm{wr}},
\]
where \(\mu_R^{\mathrm{hyb}}\) includes the ordered two-sided mixed maps
\(\mu_{\alpha_-;\eta;\beta_+,R}^{\mathrm{hyb}}\).  It also includes the
eight-word two-step binary flag atlas in the finite HN quotients, the
higher colored residual \(\mathfrak o^{\mathrm{col}}_R\), the
properness/admissibility residuals which make
\(\mathcal B_R^{E,\mathrm{hyb}}\) an actual correspondence-module
functor, the quotient operation \(Q_{E,R}\) applied only after the
extension correspondences are formed, the quotient comparison
isomorphisms \(\theta^Q_{\mu,R}\), and protected integration maps
\(I_R^{\mathrm{prot}}\) whose homogeneous \(s\)-degree is the elliptic
degree \(b_R\).  Equivalently,
\[
\mathfrak O_{\mathrm{hyb},R}=0
\]
for every finite height \(R\), compatibly with transition maps.  The
orientation lines used in these hybrid pull-push operations are the local
coefficient part of \((O_X)\); the Weyl-equivariant monodromy package
\((\mathrm{O1})^+\) and the type-II wall package \((\mathrm{O2})\) are
additional data.  A global Fock/Hecke sector is acceptable here only if
it is represented by the rigidified wrapped prequotients and acts through
the mixed maps \(\mu_R^{\mathrm{hyb}}\) before the reduced
\(E\)-quotient.  These equivalences and wrapped-sector data are part of
the datum, not operations constructed from the determinant.

\item[\((O_X)\)] \emph{Oriented compact Hall object and Weyl
orientation character.}
This entry consists of an oriented compact Hall factorization object
\(\mathcal H_X\)
graded by supplied effective charges \(c\) in the formal dyonic lattice,
with finite-type sectorial
moduli stacks and extension correspondences
$$
\mathfrak M_c^\sigma\times\mathfrak M_{c'}^\sigma
\xleftarrow{\ p_{c,c'}\ }
\mathfrak E_{c,c'}^\sigma
\xrightarrow{\ q_{c,c'}\ }
\mathfrak M_{c+c'}^\sigma,
$$
perfect reduced obstruction theories or critical
\((-1)\)-shifted symplectic structures, vanishing-cycle coefficients,
orientation lines with chosen square roots, Thom--Sebastiani orientation
transport coherent for triple extensions, and protected integration maps
compatible with HN completion and wall crossing.  The orientation entry
also includes the exact quotient-descent package.  For every charge
stratum \(\mathcal C\) used by the Hall correspondences one must specify
\[
\alpha^{\mathrm{red}}_{\mathcal C}
=w_2\!\left(\det\operatorname{RHom}_{\mathrm{red}}
(\mathcal C,\mathcal C)\right)
+\mathrm{cs}^{*}w_2\!\left(\det(\operatorname{coker}\mathrm{cs})\right)
\in H^2(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2),
\]
\[
\alpha^{E,\mathrm{free}}_{\mathcal C}
=a_1(\mathcal C)u_1+a_2(\mathcal C)u_2
\in H^2(BE;\mathbb F_2),
\]
and, for every finite-stabilizer stratum \(S\) with stabilizer \(E[N]\),
\[
\widetilde\beta^{E,N}_{\mathcal C,S}
\in H^2_{E[N]}(S;\mathbb F_2).
\]
The point-stabilizer class
\[
\beta^{E,N}_{\mathcal C,S}\in H^2(BE[N];\mathbb F_2)
\]
is used only after the mixed Borel terms, the stabilizer action on
\(H^\bullet(S;\mathbb F_2)\), and the Borel spectral-sequence
differentials have vanished.  One must prove these Borel classes, and
then their point-stabilizer restrictions, vanish on the corresponding
free and small-orbit strata.  At \(N=2\), after this restriction,
\[
\beta^{E,2}_{\mathcal C,S}
=b_{20}x_1^2+b_{11}x_1x_2+b_{02}x_2^2
\in H^2(BE[2];\mathbb F_2),
\]
with \(E[2]=\langle e_1,e_2\rangle\), \(e_3=e_1+e_2\), and
\[
\operatorname{res}_{\langle e_i\rangle}
\beta^{E,2}_{\mathcal C,S}=r_i(\mathcal C,S)\tau_i^2,
\qquad
(b_{20},b_{11},b_{02})
=(r_1,r_1+r_2+r_3,r_2).
\]
Thus the finite two-torsion residual vanishes exactly when
\(r_1=r_2=r_3=0\), but the full quotient descent also requires
\(\alpha^{\mathrm{red}}_{\mathcal C}=0\) and
\(a_1(\mathcal C)=a_2(\mathcal C)=0\).  After this degree-two
two-torsion class vanishes, the chosen \(E[2]\)-linearization has a
degree-one character
\[
\lambda_{\mathcal C}^{E[2]}
=\lambda_1x_1+\lambda_2x_2\in H^1(BE[2];\mathbb F_2),
\]
and the quotient orientation requires \(\lambda_1=\lambda_2=0\).
Odd \(N\) finite stabilizers
have no positive-degree mod-\(2\) obstruction; even \(N\ge4\) is
detected on the \(2\)-primary stabilizer
\((\Z/2^a)^2\), \(2^a\parallel N\), where for \(a\ge2\)
\[
H^*\!\left(B(\Z/2^a)^2;\mathbb F_2\right)
=\Lambda(x_1,x_2)\otimes\mathbb F_2[y_1,y_2],
\qquad |x_i|=1,\quad |y_i|=2,\quad x_i^2=0,
\]
\[
\beta^{E,N}_{\mathcal C,(2)}
=A_1^{(N)}y_1+A_{12}^{(N)}x_1x_2+A_2^{(N)}y_2 .
\]
The mixed coefficient \(A_{12}^{(N)}\) is not detected by cyclic
restrictions; after this degree-two class vanishes, the residual
\(H^1(B(\Z/2^a)^2;\mathbb F_2)\)-linearization character must also
vanish.  Thus the even \(N\ge4\) residual remains part of the descent
datum; it is not implied by the \(E[2]\) vector.  The Hall
atlas must include local-local, wrapped-wrapped, and
mixed local/wrapped extension correspondences before quotienting by the
translation action of \(E\);
quotienting first forgets the relative \(E\)-position needed by mixed
convolution.  If a lifted action of
\(W^{(2)}(\La^{2,1}_{II})\) on the oriented completed Hall object is
supplied, its finite-stage obstruction is first the projective
determinant-line cocycle on the retained action groupoid
\(\mathcal G_R\):
\[
[c_{o,R}]\in H^2(\mathcal G_R;\underline{\mathbb F}_2).
\]
Only on a complete \(W^{(2)}(\La^{2,1}_{II})\)-orbit with constant
coefficients does this reduce to
\[
[c_o]\in H^2\!\left(W^{(2)}(\La^{2,1}_{II});\mathbb F_2\right).
\]
The relevant groupoid or group class must vanish, the generator lifts
must satisfy \(s_{\delta_i}^2=1\), and the full quotient package,
including the zero finite characters \(\lambda^{E,N}_{\mathcal C}=0\),
must be transported with zero
\[
H^1(\mathfrak M^{\mathrm{red}}_{s_{\delta_i}\mathcal C};\mathbb F_2)
\oplus\bigoplus_{N\ge2}H^1(BE[N];\mathbb F_2)
\]
torsor defect, as in
Lemma~\ref{lem:weyl-quotient-orientation-obstruction}.  Only then does
the induced orientation character \(\epsilon_o\) satisfy
\[
\epsilon_o|_{W^{(2)}(\La^{2,1}_{II})}
=\nu_{\Delta_5}|_{W^{(2)}(\La^{2,1}_{II})}.
\]
Constructing the domain of this comparison and the character
\(\epsilon_o\) is part of the datum.  The comparison is a geometric
orientation-monodromy condition on the Hall side; it requires computing
the determinant-line signs on the three type-II simple reflections and
checking the reflection relations.  It is not obtained by choosing the
scalar normalization of \(\Delta_5\).

\item[\((D_X)\)] \emph{Normal-ordered descent and chiral Koszul
comparison.}
This entry consists of the chain-level normal-ordering package
\[
\mathsf{Ch}_{k,\widehat{\mathrm{HN}},E}^{\Gamma_{\mathrm{gram}}},
\quad
\{\mathsf T_\eta\}_{\eta\in\Gamma_{\mathrm{gram}}},
\quad
B_{\mathrm{ch}},
\quad
\Theta_\Pi,\Theta_\Pi^{-},
\quad
\overline\Pi_{X,*}^{\Theta}\mathcal F_X,
\]
as in Definition~\ref{def:normal-ordering-coefficient-dg-category} and
Theorem~\ref{thm:ptvv-joyce-pi-descent}.  The protected primitives are
\(\Gamma_{\mathrm{gram}}\)-graded only after applying
\(\overline\Pi_{X,*}^{\Theta}\).  Their bracket is induced from the
upstairs \(\Gamma_X^{\mathrm{phys}}\)-graded Hall bracket by translating
the raw target degree
\[
\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c')
\]
through \(\mathsf T_{B(c,c')}\), hence by shifting the displayed Gram
degree by \(-B(c,c')\).  The datum includes the triple-coherence
pentagon over the two-step Hall flag stacks, Jacobi compatibility of the
transported bracket, the \(S^1\)-equivariant negative-cyclic lift
\[
(b+uB_{\mathrm C})\Theta_\Pi^{-}=B_{\mathrm{ch}}^{-},
\]
and compatibility with the Joyce--Upmeier orientation cocycle, the
graded Frobenius identity, the completed Hopf pairing, and the reduced
\(E\)-quotient.  Equivalently, the seven obstruction classes
\[
\mathfrak o_{\Theta}^{\mathrm{top}},\quad
\mathfrak o_{\Theta}^{\mathrm{Hoch}},\quad
\mathfrak o_{\Theta}^{\mathrm{tri}},\quad
\mathfrak o_{\Theta}^{\mathrm{Jac}},\quad
\mathfrak o_F,\quad
\mathfrak o_{\Theta}^{\mathrm{cyc}},\quad
\mathfrak o_{\Theta}^{\mathrm{rad}}
\]
of Theorem~\ref{thm:ptvv-joyce-pi-descent} vanish on every finite HN
quotient and compatibly in the inverse limit, with
\(\mathfrak o_{\Theta}^{\mathrm{top}}\) enforcing finite-fibre descent
and completed tensor/coproduct continuity, and with
\(\mathfrak o_{\Theta}^{\mathrm{rad}}\) read as the Lie-ideal and coideal
pair.  The finite-stage tests are the seven diagrams
\textup{(NO1)--(NO7)} of
Proposition~\ref{prop:finite-normal-ordering-verification-diagrams}.
The finite closure criterion
Proposition~\ref{prop:finite-normal-ordering-closure-criterion} separates
the formal Picard normal-ordering lift from the non-formal Hall
correspondence, cyclic trace, and Hopf-radical compatibilities.
Before this descent, the
protected primitives of \(\mathcal F_X\) are graded by the upstairs
additive normal-ordered labels \((c,T)\), not by a Gram triple.  The
comparison with \(\mathfrak g_{\Delta_5,\alpha(n,l,m)}\) is made after
passing to \((n,l,m)=\overline\Pi_X(c,T)\); the shorthand
\(\Pi_X(c)\) is legitimate only on labels with \(T=0\).
\((D_X)\) also includes the full chiral Koszul source certificate of
Definition~\ref{def:chiral-koszul-source-certificate}.  Thus, at every
finite HN height \(R\), one must supply a conilpotent chiral coalgebra
\(C_{X,R}\) attached to the hybrid source
\(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\), a finite source
charge filtration \(F^{\mathrm{co}}_{R,\bullet}\), the collision
coproduct \(\Delta_R^{\mathrm{ch}}\), a charge-preserving bar comparison
$$
b_{X,R}:C_{X,R}\xrightarrow{\ \simeq\ }
\bar B_E^{\mathrm{ch}}
\bigl(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\bigr),
$$
and a chiral cobar quasi-isomorphism
$$
\Theta_{\mathrm{Kos},R}:
\Omega_E^{\mathrm{ch}}C_{X,R}
\xrightarrow{\ \simeq\ }
\mathsf{Den}_{\Delta_5,E,\le R},
$$
compatibly in \(R\), and the Koszul Mittag--Leffler exactness hypothesis
of Proposition~\ref{prop:chiral-koszul-source-certificate-consequence}.
In the inverse limit this gives
$$
b_X:C_X\xrightarrow{\ \simeq\ }
\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}}),
\qquad
\Theta_{\mathrm{Kos}}:
\Omega_E^{\mathrm{ch}}C_X
\xrightarrow{\ \simeq\ }
\mathsf{Den}_{\Delta_5,E}.
$$
The target-internal counit
\(\Omega_E^{\mathrm{ch}}\bar B_E^{\mathrm{ch}}
(\mathsf{Den}_{\Delta_5,E})\to\mathsf{Den}_{\Delta_5,E}\) does not
supply \(C_X\), \(b_X\), or \(\Theta_{\mathrm{Kos}}\).  These are
source-side compact data.  Their finite residual is the vanishing of
\(\mathfrak O_{\mathrm{Kos},R}\) in every finite HN quotient, including
\(\mathfrak o^{\mathrm{hyb}}_R\), the assertion that the finite hybrid
source has been built with all correspondences, quotient, and integration
laws, \(\mathfrak o^{\Delta,\mathrm{ch}}_R\) and
\(\mathfrak o^{C,\mathrm{tr}}_{R'R}\), the finite collision-coproduct and
transition-continuity assertions, the Koszul
\(R^1\varprojlim=0\) condition for the source coalgebras, completed
bar/cobar systems, target truncations, and cones of \(b_{X,R}\) and
\(\Theta_{\mathrm{Kos},R}\), \(\mathfrak o^\Omega_R\), the split
cobar residual
\[
\mathfrak o^\Omega_R
=
(\mathfrak o^{\varepsilon,\mathrm{src}}_R,\mathfrak o^\vartheta_R)
\]
of Corollary~\ref{cor:source-bar-remaining-cobar-obstruction}, and
\(\mathfrak o^{\mathrm{sep}}_R\), the assertion that the source coalgebra,
filtration, collision coproduct, bar comparison, and primitive restriction
were supplied independently of the target counit.

\item[\((R_X)\)] \emph{Primitive recognition.}
This entry is a primitive recognition certificate
\(\Pi_{\mathrm{rec}}\) for
$$
P_X^\Pi:=H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^{\Theta}\mathcal F_X).
$$
This certificate is not a determinant datum and is not the
Gritsenko--Nikulin target itself.  It consists of a source-side
Gram-descended Lie superalgebra structure on \(P_X^\Pi\), the parity split
of each homogeneous primitive piece, compact representatives for the real
and imaginary simple-root fibres of the Gritsenko--Nikulin presentation,
verification of the Borcherds--Kac defining relations in the protected
Hall bracket, the completed Hopf pairing, generation by the simple
primitives and the Cartan, a no-extra-relations theorem, completed PBW
compatibility, and identification of the source Hopf radical with the
standard Gritsenko--Nikulin/Kac radical after completion.
\end{enumerate}
\end{definition}

\begin{theorem}[Primitive recognition certificate; no source construction]
\label{prop:compact-igusa-realization-criterion}
\label{thm:primitive-recognition}
\label{thm:microscopic-hall-drinfeld-criterion}
Let \(\mathscr B_{\Delta_5}=(H,I,p,\alpha_i,(\ ,\ ))\) be the imported
Gritsenko--Nikulin Borcherds--Cartan superdatum for the automorphic
correction.  Thus
\[
H=\La^{2,1}_{II}\otimes\C,\qquad
\{\delta_1,\delta_2,\delta_3\}\subset\La^{2,1}_{II}\subset H,
\]
the three \(\delta_i\) are even real simple roots, and
\[
((\delta_i,\delta_j))_{1\le i,j\le3}
=
\begin{pmatrix}2&-2&-2\\-2&2&-2\\-2&-2&2\end{pmatrix}.
\]
The remaining fibres of \(I\to H^*\) are the imaginary simple-root
fibres with the Gritsenko--Nikulin parity split
\(\mu_{\overline0}(a),\mu_{\overline1}(a)\) of
Definition~\ref{def:imaginary-simple-roots}.  The degree map is
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}
=n\delta_1+m\delta_2+(n+m-l)\delta_3.
\]
Let \(\widehat{\mathfrak F}(\mathscr B_{\Delta_5})\) be the completed free
Lie superalgebra generated by the even Cartan \(H\) and by
parity-homogeneous generators \(e_i,f_i\), \(i\in I\), with
\(|e_i|=|f_i|=p(i)\) and \(\deg e_i=\alpha_i\),
\(\deg f_i=-\alpha_i\).  Let \(J_{\mathrm{BK}}\) be the closed
Borcherds--Kac ideal generated by the Cartan, Chevalley, real Serre,
orthogonality, and super sign relations.  After quotienting by the
standard radical of the completed invariant pairing one obtains the
target denominator algebra
\[
G(\mathscr B_{\Delta_5})
=\widehat{\mathfrak F}(\mathscr B_{\Delta_5})/
\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}}
=\mathcal A_{\mathrm{den}}
=\mathfrak g_{\Delta_5}.
\]
Here \(\operatorname{Rad}_{\mathrm{GN}}\) denotes the preimage in the
completed presentation of the standard radical.
This target-side statement is imported from the Gritsenko--Nikulin/Kac
construction; it is not a compact Hall construction.

Suppose a compact Hall/factorization construction supplies a completed
\(\widehat\Gamma_X\)-graded primitive Hall Lie superalgebra
\[
\widetilde P_X=\prod_{\widehat c\in\widehat\Gamma_X}
\widetilde P_{X,\widehat c},
\qquad
[\widetilde P_{X,\widehat c},\widetilde P_{X,\widehat c'}]
\subset \widetilde P_{X,\widehat c\star\widehat c'},
\]
and a completed Hopf pairing.  Its normal-ordered Gram descent is
\[
P_X^{\Pi,\mathrm{raw}}
=H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^{\Theta}\mathcal F_X)
=\overline\Pi_{X,*}^{\Theta}\widetilde P_X
\]
and
\[
P_X^{\Pi,\mathrm{red}}
=P_X^{\Pi,\mathrm{raw}}/
\overline{\operatorname{Rad}\langle\,\cdot\,,\,\cdot\,\rangle_X}.
\]
Assume the following source-side presentation data are supplied.  None of
these data is inferred from the Borcherds product, from the determinant,
or from signed dimensions alone.
\begin{enumerate}
\item[(S1)] \emph{Charge and normal-ordered descent.}
The chain-level descent \(\overline\Pi_{X,*}^{\Theta}\) categorifies the
normal-ordered homomorphism
\[
\overline\Pi_X:\widehat\Gamma_X\longrightarrow\Gamma_{\mathrm{gram}},
\qquad
\overline\Pi_X(c,T)=\Pi_X(c)-T,
\]
of Definition~\ref{def:dyonic-mukai-lattice}.  For
\(\widehat c=(c,T)\) and \(\widehat c'=(c',T')\),
\[
\overline\Pi_X(\widehat c\star\widehat c')
=\overline\Pi_X(\widehat c)+\overline\Pi_X(\widehat c'),
\]
so the descended bracket is a \(\Gamma_{\mathrm{gram}}\)-graded bracket:
\[
[\widetilde P_{X,\widehat c},\widetilde P_{X,\widehat c'}]
\subset\widetilde P_{X,\widehat c\star\widehat c'}
\xrightarrow{\ \overline\Pi_{X,*}^{\Theta}\ }
P^{\Pi,\mathrm{raw}}_{X,\overline\Pi_X(\widehat c)+\overline\Pi_X(\widehat c')}.
\]
Equivalently, the raw quadratic shadow
\(\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c')\) has been corrected by the
\(\Theta\)-degree shift before comparison with the denominator algebra.
Each descended homogeneous parity piece is finite dimensional.  The
construction of \((\Theta)\), the orientation datum (O), and the
chain-level Frobenius compatibility is exactly the compact content of
Theorem~\ref{thm:ptvv-joyce-pi-descent},
Open Problem~\ref{op:pi-descent-of-bracket}, and
Open Problem~\ref{op:orientation-monodromy-character}.

\item[(S2)] \emph{Cartan and root-degree matching.}
There is an even Cartan identification
\[
\iota_H:P^{\Pi,\mathrm{red}}_{X,0}\xrightarrow{\sim}
\La^{2,1}_{II}\otimes\C.
\]
The degree map \(\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}\) identifies the
descended Gram grading with the Gritsenko--Nikulin root grading after
applying \(\overline\Pi_{X,*}^{\Theta}\).  The upstairs Hall bracket
remains \(\widehat\Gamma_X\)-graded; only the descended object is
\(\Gamma_{\mathrm{gram}}\)-graded.

\item[(S3)] \emph{Simple primitive representatives and parities.}
For every simple-root index \(i\in I\) of
\(\mathscr B_{\Delta_5}\), the compact source supplies parity-homogeneous
primitive representatives
\[
e_i^X\in P^{\Pi,\mathrm{red}}_{X,\alpha_i},\qquad
f_i^X\in P^{\Pi,\mathrm{red}}_{X,-\alpha_i},\qquad
h_i^X\in P^{\Pi,\mathrm{red}}_{X,0}
\]
with \(|e_i^X|=|f_i^X|=p(i)\) and \(h_i^X=\iota_H^{-1}(\alpha_i)\).  The
representatives preserve the real/imaginary distinction, the multiplicity
fibres, and the parity map.  The real representatives for
\(\delta_1,\delta_2,\delta_3\) are even.  For each imaginary simple root
\(a\), the supplied representatives have dimensions
\[
\dim\langle e_i^X:\alpha_i=a,\ p(i)=0\rangle=\mu_{\overline0}(a),
\qquad
\dim\langle e_i^X:\alpha_i=a,\ p(i)=1\rangle=\mu_{\overline1}(a)
\]
with the same convention for the negative representatives.
The negative representatives belong to the supplied BKM double and its
independent negative primitive half.  They are not constructed or tested by
the cusp-positive Pfaffian support residuals of \textup{(D0-Pf)}.

\item[(S4)] \emph{Borcherds--Kac relations in the Hall bracket.}
In the protected Hall/factorization bracket these representatives satisfy
the Borcherds--Kac defining relations for \(\mathscr B_{\Delta_5}\):
\[
[h,h']=0,\qquad
[h,e_i^X]=(h,\alpha_i)e_i^X,\qquad
[h,f_i^X]=-(h,\alpha_i)f_i^X,
\]
\[
[e_i^X,f_j^X]=\delta_{ij}h_i^X,
\]
the real Serre relations
\[
(\operatorname{ad}e_i^X)^{1-2(\alpha_i,\alpha_j)/(\alpha_i,\alpha_i)}
e_j^X=
(\operatorname{ad}f_i^X)^{1-2(\alpha_i,\alpha_j)/(\alpha_i,\alpha_i)}
f_j^X=0
\]
for real \(i\) and \(i\neq j\), the Borcherds orthogonality relations
\[
(\alpha_i,\alpha_j)=0\quad\Longrightarrow\quad
[e_i^X,e_j^X]=[f_i^X,f_j^X]=0,
\]
and the super sign rule.  In the real rank-three subsystem
\((\delta_i,\delta_j)=-2\) for \(i\neq j\), so the real Serre exponent is
\(3\); the first brackets \([e_i^X,e_j^X]\) are not forced to vanish.
For the primitive isotropic simple roots
\[
a_{ij}:=\delta_i+\delta_j,\qquad i<j,
\]
the source representatives
\(u^{+,X}_{ij,r}\in P^{\Pi,\mathrm{red}}_{X,a_{ij}}\) and
\(u^{-,X}_{ij,r}\in P^{\Pi,\mathrm{red}}_{X,-a_{ij}}\),
\(1\le r\le9\), satisfy the orthogonality and Chevalley zero relations
with the two adjacent real roots,
\[
[e_i^X,u^{+,X}_{ij,r}]=[e_j^X,u^{+,X}_{ij,r}]
=[f_i^X,u^{+,X}_{ij,r}]=[f_j^X,u^{+,X}_{ij,r}]=0,
\]
with the analogous negative-root relations, and for the complementary
root \(\{i,j,k\}=\{1,2,3\}\) the real-string relations
\[
(\operatorname{ad}e_k^X)^5u^{+,X}_{ij,r}=0,\qquad
(\operatorname{ad}f_k^X)^5u^{-,X}_{ij,r}=0.
\]
These are relation checks in the compact bracket.  They are not
consequences of the equality \(\sdim=f(nm,l)\).

\item[(S5)] \emph{Completed Hopf pairing and radical quotient.}
The completed Hopf pairing on the positive and negative primitive halves
is continuous for the Hall completion, homogeneous for the
\(\Gamma_{\mathrm{gram}}\)-grading, invariant for the bracket and
coproduct, and has closed homogeneous radical
\[
\operatorname{Rad}_X
=\{x\mid \langle x,y\rangle_X=0\ \text{for all }y\}
\]
which is a Lie ideal and a coideal.  After quotienting by
\(\overline{\operatorname{Rad}_X}\), the source radical quotient is the
same as the Gritsenko--Nikulin/Kac quotient by
\(\overline{\operatorname{Rad}_{\mathrm{GN}}}\).  Equivalently, on every
finite-height saturated set of roots the positive-negative pairing
matrices have the same parity-block ranks as the target invariant
pairing matrices, their kernels are carried by the transition maps, and
the inverse-limit kernel is exactly \(\operatorname{Rad}_X\).  At every
finite stage one has
\[
[P^\Pi_{R},\operatorname{Rad}_{X,R}]
\subset \operatorname{Rad}_{X,R},
\qquad
\Delta_R(\operatorname{Rad}_{X,R})
\subset
\operatorname{Rad}_{X,R}\otimes P^\Pi_R
+P^\Pi_R\otimes\operatorname{Rad}_{X,R},
\]
and the completed statement is obtained by inverse limit and closure.
The radical rank is computed from these matrices and kernel maps; it is
not read from the signed determinant.  Equality of ranks alone is not a
Hopf quotient theorem without the Lie-ideal, coideal, closedness, and
transition-compatibility assertions.

\item[(S6)] \emph{No extra relations.}
The Hall primitive algebra satisfies a no-extra-relations theorem: if
\[
\pi:\widehat{\mathfrak F}(\mathscr B_{\Delta_5})
\longrightarrow P_X^{\Pi,\mathrm{red}}
\]
is the continuous map determined by the displayed representatives, then
\[
\ker\pi=
\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}}.
\]
Equivalently, the induced map
\(G(\mathscr B_{\Delta_5})\to P_X^{\Pi,\mathrm{red}}\) is injective.  This
is required finite stage by finite stage: for every saturated finite root
window \(W\), the restricted map \(\pi_W\) has kernel
\[
\ker\pi_W
=
\bigl(\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}}\bigr)_W
\]
after projection to \(W\), and these kernel identifications commute with
the HN transition maps.  A comparison of signed dimensions or a
determinant identity is not this theorem.

\item[(S7)] \emph{Generation.}
\(P_X^{\Pi,\mathrm{red}}\) is topologically generated by
\(P^{\Pi,\mathrm{red}}_{X,0}\) and the simple primitive representatives
\(e_i^X,f_i^X\).

\item[(S8)] \emph{Completed PBW.}
A completed PBW theorem holds for \(P_X^{\Pi,\mathrm{red}}\): the PBW
filtration on its enveloping algebra is transported to the PBW filtration
on \(U(\mathfrak g_{\Delta_5})\), the associated graded finite-height
pieces agree with the target pieces, and the finite-height PBW bases form
a closed inverse system in the chosen completion.  Concretely, for every
finite saturated window \(W\), the associated graded map
\[
\operatorname{gr}_{\mathrm{PBW}}U(P_X^{\Pi,\mathrm{red}})_W
\longrightarrow
\operatorname{gr}_{\mathrm{PBW}}U(\mathfrak g_{\Delta_5})_W
\]
is an isomorphism, the transition maps preserve the PBW filtration
strictly, and inverse limits are taken in the same HN topology as
Definition~\ref{def:normal-ordering-coefficient-dg-category}.  Target PBW
does not transfer to the compact source until these finite-stage
isomorphisms are supplied.

\item[(S9)] \emph{Exact completion.}
The inverse limit is exact on the saturated finite root windows used
above: the transition maps are strict for the HN topology, images are
closed, and passage to the completed quotient by the radical commutes with
finite-window kernels, cokernels, PBW associated gradeds, and root-space
parity pieces.  Equivalently, no new relation, generator, radical element,
or parity-cancelling summand appears only after completion; equivalently,
the relevant \(\lim^1\) terms vanish on these finite root-window
systems.

\item[(S10)] \emph{Full parity dimensions.}
The full root-space parity dimensions in \(P_X^{\Pi,\mathrm{red}}\)
agree with those of \(G(\mathscr B_{\Delta_5})\), not only their
differences.  For every nonzero \(\gamma\) with
\(\alpha(\gamma)\in\mathcal R\),
\[
\dim P^{\Pi,\mathrm{red}}_{X,\gamma,\overline p}
=d^{\mathrm{GN}}_{\gamma,\overline p},
\qquad
d^{\mathrm{GN}}_{\gamma,\overline p}
:=\rootmult_{\overline p}(\alpha(\gamma))
\qquad(p=0,1).
\]
Thus the source must match two integers in every root degree; equality of
their difference is not enough.
In the first timelike channel \(\gamma=(1,1,1)\),
Proposition~\ref{prop:delta123-presentation-count} gives
\[
d^{\mathrm{GN}}_{(1,1,1),\overline0}=29,\qquad
d^{\mathrm{GN}}_{(1,1,1),\overline1}=93.
\]
These are presentation-level target dimensions, not an inference from
\(29-93=-64\).
If \(\alpha(\gamma)\) is not a target root and \(\gamma\neq0\), the
corresponding source piece is zero after the radical quotient.  On active
positive Gram degrees this implies
$$
\sdim P^{\Pi,\mathrm{red}}_{X,(n,l,m)}=f(nm,l).
$$
\end{enumerate}
Then
$$
P_X^{\Pi,\mathrm{red}}
\cong
\mathcal A_{\mathrm{den}}
=\mathfrak g_{\Delta_5}
$$
as Gram-graded Lie superalgebras, and its Weyl--Kac--Borcherds
denominator is \(64^{-1}\Delta_5(2Z)\).  If in addition the chiral
Koszul source certificate of
Definition~\ref{def:chiral-koszul-source-certificate} is supplied,
including the Koszul Mittag--Leffler exactness hypothesis of
Proposition~\ref{prop:chiral-koszul-source-certificate-consequence}, then
$$
\Omega_E^{\mathrm{ch}}C_X\simeq\mathsf{Den}_{\Delta_5,E}.
$$
\end{theorem}

\begin{proof}
The simple primitive representatives define a continuous homomorphism
$$
\pi:\widehat{\mathfrak F}(\mathscr B_{\Delta_5})
\longrightarrow P_X^{\Pi,\mathrm{red}}.
$$
\textup{(S1)} and \textup{(S2)} make this a homomorphism of the descended
Gram-graded completions.  \textup{(S3)} fixes the real and imaginary
simple generators with their parities and multiplicity fibres.
\textup{(S4)} puts \(J_{\mathrm{BK}}\) in the kernel.  \textup{(S5)}
identifies the compact Hopf radical with the Gritsenko--Nikulin/Kac
radical, so \(\pi\) descends to
\[
G(\mathscr B_{\Delta_5})\longrightarrow P_X^{\Pi,\mathrm{red}}.
\]
\textup{(S7)} gives surjectivity.  \textup{(S6)} gives injectivity after
the completed radical quotient.  \textup{(S8)} gives the PBW-compatible
finite-height identifications, and \textup{(S9)} says that the completed
inverse limit is exact for the kernels, radicals, and PBW associated
gradeds under discussion.  \textup{(S10)} rules out hidden
zero-superdimension root spaces and cancelling ideals invisible to the
determinant.  Hence the descended map
is an isomorphism of Gram-graded Lie superalgebras.  The denominator
statement is
Theorem~\ref{thm:denominator-algebra-identity}.  The chiral statement is
Proposition~\ref{prop:chiral-koszul-source-certificate-consequence}; it
uses the supplied \(C_X\), \(b_X\), \(\Theta_{\mathrm{Kos}}\), and the
Koszul Mittag--Leffler exactness hypothesis of that proposition, not the
target-internal bar--cobar counit.
\end{proof}

\begin{definition}[Cofinal finite-window primitive-recognition certificate]
\label{def:cofinal-primitive-recognition-certificate}
A finite set \(W\subset Q_+\setminus\{0\}\) is
\emph{downward saturated} if
\[
0<\beta'\leq\beta,\qquad \beta\in W,\qquad
\beta-\beta'\in Q_+
\quad\Longrightarrow\quad
\beta'\in W .
\]
Thus every positive presentation word whose total degree lies in \(W\)
uses only positive degrees already in \(W\).  For the full BKM double,
each finite certificate below is triangular: positive and negative
letters are separately restricted to \(W_\nu\) and \(-W_\nu\), mixed
Chevalley and pairing checks are made only for the supplied letters in
\(W_\nu\cup(-W_\nu)\cup\{0\}\), and words whose total degree enters the
window only by cancellation are deferred to the exact-completion clause
below.
A cofinal finite-window
primitive-recognition certificate for \(P_X^{\Pi,\mathrm{red}}\) is an
increasing sequence of finite downward-saturated windows
\[
W_1\subset W_2\subset\cdots,\qquad
\bigcup_\nu W_\nu=\mathcal R_+,
\]
together with the following finite data for every \(W_\nu\), compatible
under \(W_\nu\subset W_{\nu+1}\).

\begin{enumerate}
\item[\textup{(R1)}] \emph{Representatives and parities.}
All simple-root representatives \(e_i^X,f_i^X,h_i^X\) whose roots lie in
\(W_\nu\) are supplied in the compact source, with the
Gritsenko--Nikulin parity fibres
\(\mu_{\overline0}(a),\mu_{\overline1}(a)\) for imaginary simple roots
and even real representatives for \(\delta_1,\delta_2,\delta_3\).

\item[\textup{(R2)}] \emph{Relations.}
The Cartan, Chevalley, real Serre, Borcherds orthogonality, and super
sign relations are checked for every relation whose displayed source and
target degrees lie in \(W_\nu\cup(-W_\nu)\cup\{0\}\).  Downward
saturation makes this a finite relation check for all positive
presentation words of total degree in \(W_\nu\).

\item[\textup{(R3)}] \emph{Full finite parity dimensions.}
For every \(\beta\in W_\nu\), the compact root space after the source
radical quotient has the two target dimensions
\[
\dim P^{\Pi,\mathrm{red}}_{X,\beta,\overline p}
=\rootmult_{\overline p}^{\mathrm{GN}}(\beta),
\qquad p=0,1,
\]
and the corresponding non-root degrees in the finite test window have
zero source piece.  This is a two-integer equality in each degree, not a
signed-superdimension equality.

\item[\textup{(R4)}] \emph{Hopf pairing and radical.}
The positive-negative pairing matrices between \(W_\nu\) and
\(-W_\nu\) are written in parity blocks.  Their kernels agree with the
Gritsenko--Nikulin/Kac invariant-pairing kernels, are stable under all
finite brackets whose degrees remain in the window, are coideals for the
finite coproduct, and are carried to the next window by the transition
maps.  The inverse-limit radical is the closure of these finite kernels.

\item[\textup{(R5)}] \emph{No extra relations.}
Let
\[
\pi_\nu:\widehat{\mathfrak F}(\mathscr B_{\Delta_5})_{\le W_\nu}
\longrightarrow P^{\Pi,\mathrm{red}}_{X,\le W_\nu}
\]
be the finite presentation map obtained by projecting to words whose
letters lie in the triangular finite span generated by
\(W_\nu\cup(-W_\nu)\cup\{0\}\).  The certificate
requires the finite kernel equality
\[
\ker\pi_\nu=
\bigl(\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}}\bigr)_{\le W_\nu}.
\]
This is the no-extra-relations theorem in finite form.

\item[\textup{(R6)}] \emph{Generation.}
Every source primitive root space in \(W_\nu\cup(-W_\nu)\), after the
finite radical quotient, is generated by the Cartan and the supplied
simple-root representatives through brackets whose intermediate positive
degrees stay in \(W_\nu\).

\item[\textup{(R7)}] \emph{Completed PBW compatibility.}
The PBW filtrations on the finite enveloping spans agree:
\[
\operatorname{gr}_{\mathrm{PBW}}U(P_X^{\Pi,\mathrm{red}})_{\le W_\nu}
\xrightarrow{\ \sim\ }
\operatorname{gr}_{\mathrm{PBW}}U(\mathfrak g_{\Delta_5})_{\le W_\nu},
\]
and the transition maps \(W_{\nu+1}\to W_\nu\) preserve the filtration
strictly.  The completed PBW statement is the inverse-limit statement for
this compatible finite system.

\item[\textup{(R8)}] \emph{Exact triangular completion.}
Words whose total degree lies in the finite test window only through
positive-negative cancellation are not added as extra finite generators.
They are controlled by exact completion: the transition maps are strict,
images are closed, and passage to the inverse limit commutes with the
finite kernels, cokernels, radicals, PBW associated gradeds, and parity
pieces supplied in \textup{(R3)--(R7)}.  Equivalently, the relevant
\(\lim^1\) terms vanish for these triangular finite-window systems.
\end{enumerate}
The certificate is finite at each \(\nu\), but it is not numerical: it
contains representatives, relation verifications, pairing matrices,
kernel equalities, and PBW transition data.  The Borcherds product and
the OP scalar square provide none of these source-side objects.
\end{definition}

\begin{proposition}[Global recognition is exactly the cofinal certificate]
\label{prop:global-recognition-cofinal-certificate}
Assume \textup{(S1)}--\textup{(S4)} of
Theorem~\ref{thm:primitive-recognition}.  Then the remaining global
source-side assertions \textup{(S5)}--\textup{(S10)} are supplied by a
cofinal finite-window primitive-recognition certificate in the sense of
Definition~\ref{def:cofinal-primitive-recognition-certificate}.  Under
that certificate,
\[
P_X^{\Pi,\mathrm{red}}\cong\mathfrak g_{\Delta_5}
\]
as completed Gram-graded Lie superalgebras.  Conversely, any proposed
global proof of this isomorphism, with the chosen
Gritsenko--Nikulin presentation and source Hopf pairing, must restrict to
such finite certificates on every downward-saturated window.
\end{proposition}

\begin{proof}
For a fixed \(W_\nu\), \textup{(R1)} and \textup{(R2)} define the finite
presentation map and put the Borcherds--Kac relation ideal in its kernel.
\textup{(R4)} identifies the compact finite Hopf radical with the target
radical and makes the quotient a finite Hopf Lie-superalgebra quotient.
\textup{(R5)} gives injectivity of the induced target map on the window,
while \textup{(R6)} gives surjectivity.  Thus the source and target
primitive Lie superalgebras agree on \(W_\nu\).

\textup{(R3)} rules out zero-superdimension source summands and wrong
parity lifts invisible to the determinant.  \textup{(R7)} says that the
finite isomorphisms are compatible with PBW associated gradeds and with
the chosen HN/window transition maps.  \textup{(R8)} is the exact
triangular completion clause.  Since the windows are cofinal and
the radical in \textup{(R4)} is the closure of the finite kernels, passing
to the inverse limit gives \textup{(S5)}--\textup{(S10)} and hence the
isomorphism of Theorem~\ref{thm:primitive-recognition}.

The converse is restriction: a completed isomorphism preserving the
chosen representatives, presentation map, Hopf pairing, radical quotient,
and PBW filtration yields the displayed finite representatives, kernels,
pairing matrices, parity dimensions, and PBW maps after projection to
each \(W_\nu\).  If these finite objects are not produced, the claim is
only a determinant or character comparison.
\end{proof}

\begin{proposition}[Low-degree bracket information]
\label{prop:low-degree-denominator-brackets}
The denominator algebra gives the following target-side low-degree checks.
With
$$
\alpha(n,l,m)=n\delta_1+m\delta_2+(n+m-l)\delta_3,
$$
the active positive rows through height three are
$$
\begin{array}{c|c|c|c|c}
\operatorname{ht}\beta & \beta & \gamma(\beta) & (\beta,\beta) &
\smult(\beta)\\ \hline
1&\delta_1&(1,1,0)&2&1\\
1&\delta_2&(0,1,1)&2&1\\
1&\delta_3&(0,-1,0)&2&1\\
2&\delta_1+\delta_2&(1,2,1)&0&10\\
2&\delta_1+\delta_3&(1,0,0)&0&10\\
2&\delta_2+\delta_3&(0,0,1)&0&10\\
3&2\delta_1+\delta_2&(2,3,1)&2&1\\
3&\delta_1+2\delta_2&(1,3,2)&2&1\\
3&2\delta_1+\delta_3&(2,1,0)&2&1\\
3&\delta_1+2\delta_3&(1,-1,0)&2&1\\
3&2\delta_2+\delta_3&(0,1,2)&2&1\\
3&\delta_2+2\delta_3&(0,-1,1)&2&1\\
3&\delta_1+\delta_2+\delta_3&(1,1,1)&-6&-64 .
\end{array}
$$
After choosing even Chevalley generators \(e_i,f_i,h_i\) for the real
simple roots and setting
\[
A_{ij}=(\delta_i,\delta_j),\qquad
E_{ij}:=[e_i,e_j]\quad(i\ne j),
\]
so \(E_{ji}=-E_{ij}\), one has
$$
[h_i,h_j]=0,\qquad
[h_i,e_j]=A_{ij}e_j,\qquad
[h_i,f_j]=-A_{ij}f_j,\qquad
[e_i,f_j]=\delta_{ij}h_i,
$$
and
$$
(\operatorname{ad}e_i)^3e_j=0\quad(i\ne j).
$$
If \(\{i,j,k\}=\{1,2,3\}\), then
$$
[h_i,E_{ij}]=[h_j,E_{ij}]=0,\qquad [h_k,E_{ij}]=-4E_{ij},
$$
$$
[f_i,E_{ij}]=2e_j,\qquad [f_j,E_{ij}]=-2e_i,\qquad
[f_k,E_{ij}]=0.
$$
For ordered \(i\ne j\), put \(E_{iij}:=[e_i,E_{ij}]\).  Then
$$
[e_i,E_{iij}]=0,\qquad
[f_i,E_{iij}]=2E_{ij},\qquad
[f_j,E_{iij}]=0.
$$
For \(i<j\), the isotropic primitive degree
\(a_{ij}:=\delta_i+\delta_j\) has
\[
\smult(a_{ij})=10=1+9:
\]
one even real-real commutator direction \(E_{ij}\) and nine even
Gritsenko--Nikulin isotropic simple directions
\[
u_{ij,1},\ldots,u_{ij,9}\in\mathfrak g_{a_{ij}},
\qquad \tau(ta_{ij})=9\quad(t\ge1).
\]
The orthogonality relations give
\[
[e_i,u_{ij,r}]=[e_j,u_{ij,r}]=0,\qquad
[f_i,u_{ij,r}]=[f_j,u_{ij,r}]=0.
\]
Thus the target splits the signed multiplicity \(10\) at \(a_{ij}\) into
one real-real commutator direction and nine isotropic simple directions.
A compact source must realize this splitting by actual protected Hall
primitives; the equality \(\sdim=10\) alone does not choose the
summands or the orthogonality constants.
In degree \(\delta_{123}:=\delta_1+\delta_2+\delta_3\), the real
bracketings
\[
T_1=[e_1,E_{23}],\qquad
T_2=[e_2,E_{31}],\qquad
T_3=[e_3,E_{12}]
\]
satisfy \(T_1+T_2+T_3=0\).  The brackets
\([e_k,u_{ij,r}]\in\mathfrak g_{\delta_{123}}\) for
\(\{i,j,k\}=\{1,2,3\}\) are not numerical constants until a basis and
parity split of \(\mathfrak g_{\delta_{123}}\) are chosen.  Since
\((\delta_k,a_{ij})=-4\), the same Borcherds--Kac presentation also
imposes the real-string relation
\[
(\operatorname{ad}e_k)^5u_{ij,r}=0
\]
and the analogous relation for the negative generators.  The first
bracket \([e_k,u_{ij,r}]\) is only the first visible map in this string.
The product exponent alone gives only
\[
\smult(\delta_{123})=f(1,1)=-64.
\]
Let
\[
d^{\mathrm{GN}}_{p,123}:=\rootmult_{\overline p}(\delta_{123}),
\qquad p=0,1.
\]
Then
\[
d^{\mathrm{GN}}_{0,123}-d^{\mathrm{GN}}_{1,123}=-64,
\]
but the product exponent alone does not give the two integers
\(d^{\mathrm{GN}}_{0,123}\), \(d^{\mathrm{GN}}_{1,123}\), the bracket
coordinates, or the radical.  Proposition~\ref{prop:delta123-presentation-count}
computes the target presentation values \(29\) and \(93\) from the
Weyl-sum coefficient and the Borcherds--Kac presentation; the compact
source must still reproduce them by protected primitives and the Hopf
pairing.
The first unresolved compact test channel is therefore the following:
produce parity-homogeneous compact primitives
\[
v^{\overline0}_1,\ldots,v^{\overline0}_{29},
\qquad
v^{\overline1}_1,\ldots,v^{\overline1}_{93},
\]
in the descended degree \((1,1,1)\), compute the Hall constants
\[
[e_k^X,u^X_{ij,r}]
=\sum_{a=1}^{29}
C^{\overline0}_{k;ijr,a}v^{\overline0}_a,
\qquad \{i,j,k\}=\{1,2,3\},
\]
the Jacobi relation \(T_1^X+T_2^X+T_3^X=0\), the real-string relations
\((\operatorname{ad}e_k^X)^5u^X_{ij,r}=0\), the completed Hopf-pairing
matrix between degrees \(\delta_{123}\) and \(-\delta_{123}\), with
even block size \(29\) and odd block size \(93\), and the closed radical
quotient of Theorem~\ref{thm:primitive-recognition}.  The
bracket above is even, but the odd basis is still load-bearing: it is
part of the full parity-dimension, PBW, and radical comparison.  This
channel is the first place where the compact Hall source must supply more
than the GN signed multiplicity.
These are denominator-algebra constants.  They are not compact Hall
constants.
\end{proposition}

\begin{proof}
The table is obtained by writing
\(\beta=c_1\delta_1+c_2\delta_2+c_3\delta_3\) and solving
$$
\gamma(\beta)=(c_1,c_1+c_2-c_3,c_2).
$$
Then \((\beta,\beta)=-2(4nm-l^2)\), and
\(\smult(\beta)=f(nm,l)\) follows from
Theorem~\ref{thm:denominator-algebra-identity}.  The displayed bracket
constants are the normalized Chevalley, Jacobi and Serre constants for
the symmetric Cartan matrix \(A=((\delta_i,\delta_j))\).  The signs
\(E_{ji}=-E_{ij}\), \([f_i,E_{ij}]=2e_j\), and
\([f_j,E_{ij}]=-2e_i\) follow from the graded Jacobi identity and the
normalization \([e_i,f_i]=h_i\).  The relation
\(T_1+T_2+T_3=0\) is the ordinary Jacobi identity for the even real
generators \(e_1,e_2,e_3\).  For
\(a_{ij}=\delta_i+\delta_j\) and \(\{i,j,k\}=\{1,2,3\}\), one has
\((\delta_k,a_{ij})=-4\), hence the real Borcherds--Kac Serre exponent is
\(1-2(\delta_k,a_{ij})/(\delta_k,\delta_k)=5\).  The equality
\(\tau(ta_{ij})=9\) on primitive isotropic rays is the
Gritsenko--Nikulin isotropic simple-root datum recorded above.  No compact
Hall structure constant is inferred: a compact computation would have to
construct the relevant extension correspondences, protected primitive
bases, orientation signs, the \(\delta_{123}\) channel constants, and the
radical quotient.
\end{proof}

\begin{proposition}[The determinant does not determine compact Hall constants]
\label{prop:determinant-does-not-determine-hall-constants}
The scalar OP square, the Borcherds product for \(\Delta_5\), and the
Gritsenko--Nikulin denominator algebra determine the visible signed
exponents
\[
\smult(\alpha)
=\dim\mathfrak g_{\alpha,\overline0}
-\dim\mathfrak g_{\alpha,\overline1}.
\]
They do not determine a compact Hall bracket, compact primitive
representatives, full source parity dimensions, the positive-negative
Hopf pairing, its closed radical quotient, the no-extra-relations theorem,
or completed PBW compatibility.
\end{proposition}

\begin{proof}
A \(\Gamma_{\mathrm{gram}}\)-graded super vector space with the same
signed dimensions gives the same determinant.  Adding a cancelling pair
\(W_\gamma\oplus\Pi W_\gamma\) in any active degree leaves every signed
exponent unchanged, while changing the full parity dimensions.  Equipping
the same graded vector space with the zero bracket also leaves the
determinant unchanged, but it cannot be the denominator algebra because
the target has nonzero real-root brackets, for example
\([e_i,e_j]\neq0\) for \(i\neq j\), and the first timelike channel
requires the \(29|93\) presentation split of
Proposition~\ref{prop:delta123-presentation-count}.  A compact Hall
realization must therefore construct extension correspondences,
orientation signs, protected primitive bases, Hall structure constants,
pairing matrices, radical kernels, and PBW finite-window isomorphisms.
The determinant is a necessary decategorified shadow of these data, not a
source for them.
\end{proof}

\begin{proposition}[First timelike presentation count]
\label{prop:delta123-presentation-count}
Let
\[
\delta_{123}:=\delta_1+\delta_2+\delta_3
=2f_2-f_3+2f_{-2}.
\]
In the Gritsenko--Nikulin additive correction coefficient one has
\[
m(\delta_{123})=-93.
\]
Consequently the target denominator algebra has full parity dimensions
\[
\rootmult_{\overline0}(\delta_{123})=29,\qquad
\rootmult_{\overline1}(\delta_{123})=93.
\]
The \(29\) even directions are the two real-real-real
Borcherds--Kac presentation words
\[
T_1=[e_1,[e_2,e_3]],\qquad
T_2=[e_2,[e_3,e_1]],\qquad
T_3=[e_3,[e_1,e_2]],\qquad T_1+T_2+T_3=0,
\]
together with the \(27\) mixed real-isotropic words
\[
[e_k,u_{ij,r}],\qquad \{i,j,k\}=\{1,2,3\},\quad 1\le r\le9.
\]
The \(93\) odd directions are the negative-norm imaginary simple
generators in degree \(\delta_{123}\).  This is a target-side
presentation count.  It is not a compact Hall computation and is not
deduced from the signed equality \(29-93=-64\).
\end{proposition}

\begin{proof}
The root \(\delta_{123}\) corresponds in the notation of the Weyl-sum
coefficient formula to
\[
\delta_{123}=(3-1)f_2-\frac{3-1}{2}f_3+(3-1)f_{-2}.
\]
Hence \(m(\delta_{123})=-64^{-1}c_\Delta(3,3,3)\).  After removing the
leading monomial from \(D_5=64^{-1}\Delta_5\),
\[
D_5
=q^{1/2}r^{1/2}s^{1/2}
\prod_{\gamma\in\Gamma_{\mathrm{eff}}}(1-q^nr^ls^m)^{f(nm,l)},
\]
the finite coefficient calculation in \(q\)- and \(s\)-degree one gives
\[
\left[qrs\right]
\prod_{\gamma\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}
=93.
\]
Explicitly, only the \(q\)-linear, \(s\)-linear, and \(qs\)-linear
factors enter.  With
\[
A(r)=1-r^{-1},\qquad
B(r)=-(r^{-1}+10+r),
\]
\[
C(r)=-10r^{-2}+64r^{-1}-108+64r-10r^2,
\]
one has
\[
\left[qrs\right]
\prod_{\gamma\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}
=[r]\ A(r)\bigl(B(r)^2+C(r)\bigr)
\]
and
\[
A(r)\bigl(B(r)^2+C(r)\bigr)
=9r^{-3}-93r^{-2}+90r^{-1}-90+93r-9r^2.
\]
Equivalently \(c_\Delta(3,3,3)=64\cdot93\), so
\(m(\delta_{123})=-93\).  Since this coefficient is negative, the
Gritsenko--Nikulin parity convention makes these \(93\) simple
generators odd.

It remains to count the lower presentation words in the same total
degree.  The multidegree \((1,1,1)\) part of the free Lie algebra on the
three even real generators has dimension \(2\); the three displayed
bracketings satisfy exactly the Jacobi relation
\(T_1+T_2+T_3=0\).  For each primitive isotropic root
\(a_{ij}=\delta_i+\delta_j\), the Gritsenko--Nikulin isotropic
multiplicity is \(\tau(a_{ij})=9\), and the complementary real root
\(\delta_k\) has \((\delta_k,a_{ij})=-4\).  Thus the first mixed
brackets \([e_k,u_{ij,r}]\) are allowed presentation words; the
orthogonality relations kill only the adjacent brackets with
\(\delta_i\) and \(\delta_j\), and the real-string relation occurs first
at \((\operatorname{ad}e_k)^5u_{ij,r}\).  There are
\(3\cdot9=27\) such even words.  No other simple-root decomposition has
total degree \(\delta_{123}\).  The Borcherds--Kac presentation and PBW
therefore give \(2+27=29\) even and \(93\) odd target directions in this
degree.  Their signed difference is
\[
29-93=-64=f(1,1),
\]
which checks the denominator exponent but does not determine the compact
source parity split, bracket constants, pairing matrix, or radical
quotient.
\end{proof}

\begin{proposition}[First saturated primitive-recognition window]
\label{prop:first-saturated-primitive-recognition-window}
Let
\[
W_{\le3}:=
\left\{
\beta=c_1\delta_1+c_2\delta_2+c_3\delta_3\in\mathcal R_+
\;:\;
c_i\ge0,\quad 1\le c_1+c_2+c_3\le3
\right\}.
\]
This is the first downward-saturated finite target window containing the
real simple roots, the primitive isotropic simple-root fibres, and the
first timelike degree.  In \(G(\mathscr B_{\Delta_5})\) the full
parity dimensions in this window are
\[
\begin{array}{c|c|c}
\beta & \rootmult_{\overline0}(\beta) &
\rootmult_{\overline1}(\beta)\\ \hline
\delta_i\ (1\le i\le3) & 1&0\\
\delta_i+\delta_j\ (i<j) & 10&0\\
2\delta_i+\delta_j\ (i\ne j) & 1&0\\
\delta_{123} & 29&93 .
\end{array}
\]
The parity entries use the imported Gritsenko--Nikulin/Kac parity
convention; the target computation checks signed coefficients and
presentation counts, not source parity bases.
Consequently a compact source passes primitive recognition on
\(W_{\le3}\) only after supplying the following finite certificate:
parity-homogeneous representatives with the displayed dimensions; the
Chevalley, real-Serre, orthogonality, and super-sign relations restricted
to \(W_{\le3}\); the Jacobi relation
\[
T_1^X+T_2^X+T_3^X=0;
\]
the \(27\) mixed maps \([e_k^X,u^X_{ij,r}]\) into the even
\(\delta_{123}\)-block; positive-negative Hopf-pairing matrices in every
degree of \(W_{\le3}\) with closed radical kernels stable under the
finite transition maps; the finite kernel equality
\[
\ker\pi_{W_{\le3}}
=
\bigl(\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}}
\bigr)_{W_{\le3}};
\]
and the associated-graded PBW isomorphism on the truncated enveloping
algebras.  If this finite certificate is supplied, the restricted map
\[
G(\mathscr B_{\Delta_5})_{W_{\le3}}
\longrightarrow
P^{\Pi,\mathrm{red}}_{X,W_{\le3}}
\]
is an isomorphism of finite Gram-graded Lie superalgebras.  Without the
kernel equality, the Hopf-radical ideal/coideal assertion, and the PBW
associated-graded isomorphism, equality of the displayed dimensions is
not recognition.

The next coefficient checks already lie outside this window.  The exact
finite product computation in \texttt{compute/verify\_square\_root.py}
is target-only: it verifies Borcherds/Gritsenko--Nikulin arithmetic, not
compact Hall representatives, Hopf-pairing matrices, coproduct matrices,
or radical kernels.  It gives
\[
[q^2r^2s]\frac{D_5}{(qrs)^{1/2}}
=[qr^2s^2]\frac{D_5}{(qrs)^{1/2}}
=[qs]\frac{D_5}{(qrs)^{1/2}}
=-90,
\]
and
\[
[q^2r^2s^2]\frac{D_5}{(qrs)^{1/2}}=540.
\]
Thus the Gritsenko--Nikulin additive coefficients are
\[
m(2\delta_1+\delta_2+\delta_3)
=m(\delta_1+2\delta_2+\delta_3)
=m(\delta_1+\delta_2+2\delta_3)=90,
\]
\[
m(2\delta_{123})=-540.
\]
These are target simple-root coefficients.  They do not count the lower
PBW words in those degrees and do not supply compact Hall representatives,
pairing matrices, radicals, or no-extra-relations data.

The first obstruction to extending the displayed finite recognition
statement from \(W_{\le3}\) to height four is already numerical.  The
full signed target root supermultiplicities in the three height-four
timelike degrees are
\[
\smult(2\delta_1+\delta_2+\delta_3)
=\smult(\delta_1+2\delta_2+\delta_3)
=\smult(\delta_1+\delta_2+2\delta_3)=108,
\]
whereas the new negative-norm simple-root coefficients in those same
degrees are \(90\).  Thus each of these degrees carries a signed
height-four residual
\[
108-90=18
\]
coming from lower presentation words after the Borcherds--Kac relations
and radical quotient are imposed.  This number is a signed residual, not
a count of compact PBW basis vectors.  It says precisely that the
height-four window cannot be certified by appending the additive
coefficients alone.

The same phenomenon is visible on the doubled isotropic boundary rays:
for \(i<j\),
\[
\smult(2\delta_i+2\delta_j)=10,\qquad
\tau(2(\delta_i+\delta_j))=9,
\]
so the signed non-simple residual is \(1\) on each doubled isotropic
ray.  These doubled-ray checks test the isotropic multiplicity
convention \(\tau(t(\delta_i+\delta_j))=9\) against the product
exponents; they do not identify compact primitives.

The height-four real-string obstruction is also explicit.  If
\(w_s\), \(1\le s\le93\), denotes an odd negative-norm simple generator
in degree \(\delta_{123}\), then
\[
(\delta_i,\delta_{123})=-2,\qquad
1-2(\delta_i,\delta_{123})/(\delta_i,\delta_i)=3,
\]
and the target presentation contains
\[
(\operatorname{ad}e_i)^3w_s=0,\qquad
(\operatorname{ad}f_i)^3w_s^-=0.
\]
The first brackets \([e_i,w_s]\) land in the three height-four timelike
degrees above and are odd.  A height-four compact recognition certificate
must therefore supply those odd maps, the even simple generators of
multiplicity \(90\), the lower-word relations producing the signed
residual \(18\), the positive-negative pairing matrices, the radical
kernels, and PBW associated-graded compatibility.  Dimension equality
alone still does not prove recognition.
\end{proposition}

\begin{proof}
The table is exactly the target data of
Propositions~\ref{prop:low-degree-denominator-brackets} and
\ref{prop:delta123-presentation-count}: the three real simple roots are
even one-dimensional, each primitive isotropic degree has one real-real
commutator and nine even isotropic simple directions, the six height-three
real roots are even one-dimensional, and
\(\delta_{123}\) has presentation dimensions \(29|93\).  The finite
certificate is the restriction of clauses \textup{(S3)}--\textup{(S10)} of
Theorem~\ref{thm:primitive-recognition} to the downward-saturated window
\(W_{\le3}\).  The same proof as the theorem then gives the restricted
isomorphism.  The height-four additive coefficients are computed from the
monic Borcherds product and converted to Gritsenko--Nikulin \(m(a)\) by
the coefficient formula \(m(a)=-64^{-1}c_\Delta(n,l,m)\) of
\cite[Theorem~2.1]{GN}; the script performs this conversion with
\(\alpha(n,l,m)=n\delta_1+m\delta_2+(n+m-l)\delta_3\).  The full signed
height-four target multiplicities are read from the same denominator
theorem:
\[
\smult(\beta)=f(nm,l)
\quad\hbox{for}\quad
\gamma(\beta)=(n,l,m).
\]
For
\(\beta=2\delta_1+\delta_2+\delta_3,\delta_1+2\delta_2+\delta_3,
\delta_1+\delta_2+2\delta_3\) this gives respectively
\((n,l,m)=(2,2,1),(1,2,2),(1,0,1)\), hence the coefficients
\(f(2,2)=108,f(2,2)=108,f(1,0)=108\).  Subtracting the additive
coefficients \(90\) gives the displayed signed residual \(18\).
For the doubled isotropic degrees \(2(\delta_i+\delta_j)\), the
denominator exponent is \(f(4,4)=f(0,0)=10\) in the three symmetric
chambers, while the isotropic simple-root multiplicity is the
Gritsenko--Nikulin constant \(\tau(2(\delta_i+\delta_j))=9\).  Finally,
the real-string exponents follow directly from the Gram matrix:
\((\delta_i,\delta_{123})=-2\), \((\delta_i,\delta_i)=2\), and therefore
the exponent is \(3\).  All displayed numerical checks are asserted in
\texttt{compute/verify\_square\_root.py}.
\end{proof}

\begin{openproblem}[State-side construction of \(D_0\) and the
Dirac--Igusa certificate]
\label{op:compact-igusa-realization}
Construct first the \(D_0\)-certificate of
Definition~\ref{def:first-order-d0-certificate}, and then the full
certificate \(\mathfrak K_X\) of
Definition~\ref{def:compact-igusa-realization-datum}.  The exact open
obligations are:
\begin{enumerate}
\item[\textup{(open \(D_0\)-state)}] construct, for every
\(R\in\mathcal R\), the finite Hall source kernel
\(\mathfrak S_R\) of
Definition~\ref{def:finite-hall-source-kernel}, so that
Proposition~\ref{prop:finite-d0-hall-source-construction} produces the
finite state object \(\mathcal H_R^{or}\), pull-push Hall product,
coproduct, primitive bracket, normal-ordered primitive algebra, and
finite CE differential.  Then construct the full finite stage
\(D_{0,R}\) on \(\widehat\Gamma_R\), equivalently the finite
Hall--Dirac atlas \(\mathfrak A_R\) of
Proposition~\ref{prop:finite-d0-atlas-parity-obstruction}, including the
Dirac complex, source observable shadow, Pfaffian square, compact parity
lifts, protected integration, and successor transition maps with
\(\mathfrak o^{\mathrm{atlas}}_{R^+R}=
\mathfrak o^{\mathrm{tr}}_{R^+R}=0\), whose composites give the
non-successor transitions and whose inverse limit is
\(\widehat{\mathcal H}^{or}_{\sigma,S}\);
\item[\textup{(open \(D_0\)-quotient)}] compute and trivialize the reduced
orientation and quotient obstruction tuple
\(\mathfrak o^{or}_{R,\mathcal C}\) for every stable charge stratum and
finite stabilizer appearing at height \(R\), including the zero
\(H^1(BE[N];\mathbb F_2)\)-linearization characters after finite gerbe
null-trivialization, compatibly in \(R\);
\item[\textup{(open \(D_0\)-observable)}] construct the chain-level
\(K3\)-to-\(E\) specialization, the projection-finite chiral shadow, and
the hybrid wrapped sector \(\mathcal F_X^{D_0}\) that recovers positive
elliptic degree before quotienting by translation in \(E\), together with
a source-to-target finite comparison map satisfying
\(\mathfrak o^{obs}_R=0\) on \(\Gamma_R^{\mathrm{test}}\);
\item[\textup{(open \(D_0\)-descent)}] construct the finite-topology,
Hochschild, triple-coherence, Jacobi, Frobenius, negative-cyclic, and
Hopf-radical ideal/coideal cochains
\(\Theta_{\Pi,R}\), \(\Theta_{\Pi,R}^{-}\) with
\[
\mathfrak o^{\mathrm{top}}_{\Theta,R^+R}=
\mathfrak o^{\mathrm{Hoch}}_{\Theta,R}=
\mathfrak o^{\mathrm{tri}}_{\Theta,R}=
\mathfrak o^{\mathrm{Jac}}_{\Theta,R}=
\mathfrak o_{F,R}=
\mathfrak o^{\mathrm{cyc}}_{\Theta,R}=
\mathfrak o^{\mathrm{rad}}_{\Theta,R}=0,
\]
giving exact compatibility with the normal-ordered homomorphism
\(\overline\Pi_X\) on primitive brackets, equivalently the finite
diagrams \textup{(NO1)--(NO7)} of
Proposition~\ref{prop:finite-normal-ordering-verification-diagrams}, with
compatibility against the Hopf radical quotients at every transition.
The Picard and finite-fibre subclaims are reduced to
Lemma~\ref{lem:finite-picard-normal-ordering-lift}; the surviving
geometric work is exactly the cyclic/flag/Frobenius/Hopf-adjointness
package of
Proposition~\ref{prop:finite-normal-ordering-closure-criterion};
\item[\textup{(open \(D_0\)-Pfaffian)}] construct the Pfaffian line and
finite first-order operator/algebra \(\mathfrak D_{X,R}\) on the reduced
compact quotient
\(\mathfrak Q_R=(\mathfrak M_R/E)^{\mathrm{red}}\), compatible under
\(R^+\to R\), including a trivialization of the Pfaffian square-root
torsor in \(\operatorname{Pic}(\mathfrak Q_R)[2]\), with compact parity
lifts \(\ell_R(\gamma)\in\mathscr P_R(\gamma)\) on every
\(\gamma\in\Gamma_R^{\mathrm{test},+}\) satisfying
\[
\mathfrak o^{\mathrm{supp}}_{R,\gamma}=0,\qquad
\mathfrak o^{\mathrm{par}}_{R,\gamma}=0,
\]
including absence of actual primitive support in target-zero degrees,
coverage of every nonzero Borcherds target degree in the exhausting
windows \(\Gamma_{\Delta,R}\), finite Pfaffian square
\(\mathscr L_{\mathrm{Pf},R}^{\otimes2}\simeq\mathscr L_{\det,R}\),
and normalized leading coefficient \(\mathfrak o^{\mathrm{lead}}_R=0\).
Negative representatives are supplied only in the primitive-recognition
certificate, through the full positive-negative pairing and Chevalley
data.
The minimal target-window parity model
\(\mathsf P^{\min}_{\Delta,R}\) is already constructed in
Proposition~\ref{prop:cofinal-target-window-parity-model}; the open
compact task is to identify it, or a non-minimal lift in
\(\mathscr P_R(\gamma)\), with actual source primitive spaces and to
prove the no-hidden-cancellation condition if the minimal lift is used;
\item[\textup{(open full certificate)}] construct the strong
orientation monodromy and the chiral Koszul source certificate
\[
\mathfrak K^{\mathrm{Kos}}_{X,R}
=(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},C_{X,R},
F^{\mathrm{co}}_{R,\bullet},\Delta_R^{\mathrm{ch}},
b_{X,R},\Theta_{\mathrm{Kos},R})
\]
of Definition~\ref{def:chiral-koszul-source-certificate}, with
\[
\mathfrak O_{\mathrm{Kos},R}=0
\]
compatibly in \(R\), together with the Koszul
\(R^1\varprojlim=0\) condition for the source coalgebras, completed
bar/cobar systems, target truncations, and cones of \(b_{X,R}\) and
\(\Theta_{\mathrm{Kos},R}\), including
\(\mathfrak O_{\mathrm{hyb},R}=0\) for the hybrid source.  Equivalently,
construct the full finite local/wrapped correspondence atlas, the
properness/admissibility residuals for its pull-push operations, the
quotient-after-correspondence functor, protected integration, the
conilpotent compact source coalgebra, the finite conilpotent filtration,
the source collision coproduct with finite coassociativity, counit, and
transition-continuity diagrams, the bar comparison to
\(\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}})\), and the cobar
quasi-isomorphism to \(\mathsf{Den}_{\Delta_5,E}\), rather than using the
target-internal bar--cobar counit.  The cobar residual includes both the
source-internal bar--cobar admissibility
\(\mathfrak o^{\varepsilon,\mathrm{src}}_R\) and the source-to-target
quasi-isomorphism defect \(\mathfrak o^\vartheta_R\).  The residual
components \(\mathfrak o^{\mathrm{hyb}}_R\) and
\(\mathfrak o^{\mathrm{sep}}_R\) record, respectively, the finite hybrid
construction and this source/target separation.
Then construct the compact Hall bracket constants, the simple primitive
representatives, the
Borcherds--Kac relation verification, the full compact parity
dimensions, the completed Hopf pairing with its closed radical quotient,
the no-extra-relations theorem, and completed PBW compatibility of
Theorem~\ref{thm:primitive-recognition}; equivalently, construct the
cofinal finite-window certificate of
Definition~\ref{def:cofinal-primitive-recognition-certificate}.  The
first finite bracket test is
the \(\delta_1+\delta_2+\delta_3\) channel of
Propositions~\ref{prop:low-degree-denominator-brackets} and
\ref{prop:delta123-presentation-count}: the signed dimension \(-64\)
must be refined to compact \(29|93\) bases, parity split, structure
constants, Jacobi/Serre checks, pairing matrices, and radical quotient.
\end{enumerate}
The proved lattice normal-ordering theorem and the imported denominator
algebra are inputs to this problem.  The scalar square is an
orientation-forgetful check.  None of the three constructs the compact
state-side certificate.
\end{openproblem}

\begin{definition}[Imaginary simple roots]
\label{def:imaginary-simple-roots}
For $a\in \La^{2,1}_{II}\cap\R_{>0}\Poly_{II}$ set
$$
\mu_{\overline 0}(a)=
\begin{cases}
m(a),& (a,a)<0\ \text{and}\ m(a)>0,\\
\tau(a),& (a,a)=0\ \text{and}\ \tau(a)>0,\\
0,&\text{otherwise},
\end{cases}
$$
and
$$
\mu_{\overline 1}(a)=
\begin{cases}
-m(a),& (a,a)<0\ \text{and}\ m(a)<0,\\
-\tau(a),& (a,a)=0\ \text{and}\ \tau(a)<0,\\
0,&\text{otherwise}.
\end{cases}
$$
This sign split is the Gritsenko--Nikulin BKM parity datum.  The
product statement alone fixes only a Grothendieck representative for the
signed exponent.  Define multisets by
multiplicity:
$$a\in\Delta_{\overline0}^{im}\quad\hbox{with multiplicity }
\mu_{\overline0}(a),$$
$$a\in\Delta_{\overline1}^{im}\quad\hbox{with multiplicity }
\mu_{\overline1}(a).$$
Put
$$\Delta^{im}=\Delta_{\overline0}^{im}\cup\Delta_{\overline1}^{im}.$$
$$\mathcal O_{\mathrm{den}}^{im}
=\bigoplus_{a\in\Delta^{im}}
\left(\mathfrak g_{a,\overline0}\ominus\mathfrak g_{a,\overline1}\right).$$
This is notation inside the denominator algebra; it is not a BPS state
space.
\end{definition}
The real simple roots are
$$\Delta_{\overline0}^{re,\mathrm{simp}}
=\Delta^{re}_{\mathrm{simp}}=\Poly_{II,prim}
=\{\delta_1,\delta_2,\delta_3\},\qquad
\Delta_{\overline1}^{re,\mathrm{simp}}=\varnothing.$$
Put
$$\Delta_{\overline p}=\Delta_{\overline p}^{re,\mathrm{simp}}\cup
\Delta_{\overline p}^{im}\qquad(p=0,1),\qquad
\Delta=\Delta_{\overline0}\cup\Delta_{\overline1}.$$
The Cartan data satisfy $(\alpha,\alpha)>0$ for
$\alpha \in \Delta^{re}$, $(\alpha,\alpha)\leq 0$ for
$\alpha \in \Delta^{im}$, and
$(\alpha,\alpha')\leq 0$ for all distinct $\alpha,\alpha'\in\Delta$.
If $(\alpha,\alpha)>0$, then
$$2\frac{(\alpha,\alpha')}{(\alpha,\alpha)} \in \Z,$$
since $(\alpha,\alpha)=2$ and
$\La^{2,1}_{II}=\Z\delta_1+\Z\delta_2+\Z\delta_3$.
\begin{definition}[Generators and relations]
Let $I$ be an index set equipped with a parity map $p:I\to\Z/2\Z$ and a
root map $i\mapsto\alpha_i\in\Delta$, with fibres over an imaginary root
of cardinality $\mu_{\overline p}(a)$ in parity $p$.  If
$i\neq j$ and $\alpha_i=\alpha_j$, the two indices are distinct simple
roots.
$$\operatorname{ch}:I\rightarrow\La^{2,1}_{II},\qquad
i\mapsto\alpha_i.$$
The superalgebra $\autcor$ is generated by
$$h_i,\ e_i,\ f_i,\qquad i\in I.$$
The Cartan subalgebra is identified with $\La^{2,1}_{II}\otimes\C$ by
$h_i\mapsto\alpha_i$.  Relations:

\begin{itemize}
\item $[h_i,e_j]=(\alpha_i,\alpha_j)e_j$ and
$[h_i,f_j]=-(\alpha_i,\alpha_j)f_j$
\item $[e_i,f_j]=\delta_{ij}h_i$
\item if $\alpha_i \in \Delta^{re}_{\mathrm{simp}}$ and $i\neq j$, then
$$
(\operatorname{ad} e_i)^{1-2(\alpha_i,\alpha_j)/(\alpha_i,\alpha_i)}
e_j=
(\operatorname{ad} f_i)^{1-2(\alpha_i,\alpha_j)/(\alpha_i,\alpha_i)}
f_j=0
$$
\item if $(\alpha_i,\alpha_j)=0$, then $[e_i,e_j]=[f_i,f_j]=0$
\end{itemize}
\end{definition}

The grading is by $\La^{2,1}_{II}$.  Put
$$Q_+=\sum_{\alpha\in\Delta}\Z_{\geq0}\alpha
\subset\La^{2,1}_{II}.$$
The triangular decomposition is
$$\autcor =
\left(\bigoplus_{\alpha \in Q_+\setminus\{0\}}
\mathfrak{g}_{\alpha}\right)
\oplus(\La^{2,1}_{II}\otimes\C)
\oplus
\left(\bigoplus_{\alpha \in Q_+\setminus\{0\}}
\mathfrak{g}_{-\alpha}\right).$$
For $i\in I$,
$$\deg e_i=\alpha_i,\qquad \deg f_i=-\alpha_i,\qquad \deg h_i=0.$$
$$[\mathfrak g_\alpha,\mathfrak g_\beta]\subset
\mathfrak g_{\alpha+\beta}.$$
$$\mathfrak{g}_0=\La^{2,1}_{II}\otimes\C.$$
The positive and negative roots are
$$\mathcal R_+=\{\alpha\in Q_+\setminus\{0\}\mid
\mathfrak{g}_{\alpha}\neq0\},\qquad
\mathcal R_-=-\mathcal R_+.$$
For every root $\alpha$, set
$$\rootmult_{\overline{0}}(\alpha)
=\dim\mathfrak{g}_{\alpha,\overline{0}},\qquad
\rootmult_{\overline{1}}(\alpha)
=\dim\mathfrak{g}_{\alpha,\overline{1}}.$$
The signed root superdimension is
$$\smult(\alpha)=\rootmult_{\overline{0}}(\alpha)
-\rootmult_{\overline{1}}(\alpha).$$
The Weyl--Kac--Borcherds denominator is
$$
\begin{aligned}
\Phi_{\Delta_5}(z)
&=\sum_{w\in W^{(2)}(\La^{2,1}_{II})}\det(w)
\left(
e^{-2\pi i(w(\rho),z)}
-\sum_{a\in\La^{2,1}_{II}\cap\R_{>0}\Poly_{II}}
m(a)e^{-2\pi i(w(\rho+a),z)}
\right)\\
&=e^{-2\pi i(\rho,z)}
\prod_{\alpha\in\mathcal R_+}
\left(1-e^{-2\pi i(\alpha,z)}\right)^{\smult(\alpha)}.
\end{aligned}
$$
$$\Omega(\La^{2,1}_{II})
=\La^{2,1}_{II}\otimes\R+i\Cone(\La^{2,1}_{II})_+.$$

\begin{theorem}[Denominator identity]
$$\frac{1}{64}\Delta_5(2Z)=\Phi_{\Delta_5}(z).$$
$$\operatorname{den}(\autcor)=\frac1{64}\Delta_5(2Z).$$
\end{theorem}

\begin{proof}
$$\frac1{64}\Delta_5(Z)
=\sum_{w\in W^{(2)}(\La^{2,1}_{II})}\det(w)
\left(
e^{-\pi i(w(\rho),z)}
-\sum_{a\in\La^{2,1}_{II}\cap\R_{>0}\Poly_{II}}
m(a)e^{-\pi i(w(\rho+a),z)}
\right).$$
$$Z\mapsto2Z:\qquad
e^{-\pi i(w(\rho+a),z)}
\mapsto e^{-2\pi i(w(\rho+a),z)}.$$
Weyl--Kac--Borcherds:
$$e^{-2\pi i(\rho,z)}
\prod_{\alpha\in\mathcal R_+}
\left(1-e^{-2\pi i(\alpha,z)}\right)^{\smult(\alpha)}.$$
\end{proof}

\begin{proposition}[Gram-index cone and denominator cone]
$$\alpha(\Gamma_{\mathrm{act}})
=\{\alpha(n,l,m)\mid(n,l,m)\in\Gamma_{\mathrm{eff}},\ f(nm,l)\neq0\}
\subset\La^{2,1}_{II}.$$
$$
\alpha(\Gamma_{\mathrm{act}})
\subset
\mathcal R_+^{\mathrm{vis}}
:=\{\alpha\in\mathcal R_+\mid \smult(\alpha)\neq0\}.
$$
$$\smult(\alpha(n,l,m))
=\dim\mathfrak{g}_{\alpha(n,l,m),\overline0}
-\dim\mathfrak{g}_{\alpha(n,l,m),\overline1}
=f(nm,l)\qquad((n,l,m)\in\Gamma_{\mathrm{act}}).$$
\end{proposition}

\begin{proof}
$$\alpha:\Gamma_{\mathrm{ind}}\to\La^{2,1}_{II},\qquad
(n,l,m)\mapsto2nf_2-lf_3+2mf_{-2}.$$
$$q^nr^ls^m=\exp(-\pi i(\alpha(n,l,m),z))$$
$$Z\mapsto2Z.$$
$$\frac1{64}\Delta_5(2Z)
=e^{-2\pi i(\rho,z)}
\prod_{\alpha\in\mathcal R_+}
\left(1-e^{-2\pi i(\alpha,z)}\right)^{\smult(\alpha)}.$$
$$\frac1{64}\mathcal D_X(2Z)
=e^{-2\pi i(\rho,z)}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
\left(1-e^{-2\pi i(\alpha(n,l,m),z)}\right)^{f(nm,l)}.$$
The triples in $\Gamma_{\mathrm{eff}}\setminus\Gamma_{\mathrm{act}}$
have exponent zero and do not contribute visible product factors.  The
denominator product alone does not prove absence of root spaces with
zero signed superdimension.
$$\mathcal D_X=\Delta_5\quad\Longrightarrow\quad
\smult(\alpha(n,l,m))=f(nm,l)
\quad((n,l,m)\in\Gamma_{\mathrm{act}}).$$
\end{proof}

\begin{proposition}[What the denominator determines]
The identity
$$
\frac1{64}\Delta_5(2Z)
=e^{-2\pi i(\rho,z)}
\prod_{\alpha\in\mathcal R_+}
\left(1-e^{-2\pi i(\alpha,z)}\right)^{\smult(\alpha)}
$$
determines the signed integers \(\smult(\alpha)\), once the
Gritsenko--Nikulin root set and positive root monoid have been fixed.  It
does not determine invisible zero-superdimension root spaces, the two
parity dimensions
$$
\rootmult_{\overline0}(\alpha),\qquad
\rootmult_{\overline1}(\alpha),
$$
and it does not determine the structure constants
$$
[\mathfrak g_\alpha,\mathfrak g_\beta]\to
\mathfrak g_{\alpha+\beta}.
$$
It also does not determine simple primitive representatives, the
no-extra-relations statement, completed PBW compatibility, or the closed
radical of the positive-negative Hopf pairing.
Thus signed root multiplicity is necessary input for primitive
recognition, but it is not a recognition certificate.
\end{proposition}

\begin{proof}
Write \(X^\alpha=e^{-2\pi i(\alpha,z)}\).  In the completed positive
root monoid algebra,
$$
\log\prod_{\alpha\in\mathcal R_+}(1-X^\alpha)^{\smult(\alpha)}
=-\sum_{\alpha\in\mathcal R_+}\sum_{k\ge1}
\frac{\smult(\alpha)}{k}X^{k\alpha}.
$$
Thus a logarithmic coefficient mixes divisor terms \(k\alpha=\lambda\).
The exponents \(\smult(\alpha)\) are recovered recursively by height,
equivalently by Mobius inversion on each primitive ray.  The recovered
exponent is only
$$
\smult(\alpha)=
\rootmult_{\overline0}(\alpha)-\rootmult_{\overline1}(\alpha).
$$
The difference $a-b$ does not determine the pair $(a,b)$, and no
bilinear bracket, PBW filtration, or Hopf-pairing radical appears in the
product.
\end{proof}

\begin{proposition}[What the determinant forgets]
\label{thm:protected-denominator-shadow}
Let
$$
\mathcal B=\bigoplus_{\gamma\in\Gamma_{\mathrm{eff}}}\mathcal B_\gamma
$$
be any charge-graded super vector space with finite-dimensional
homogeneous pieces and
$$\sdim\mathcal B_{(n,l,m)}=f(nm,l).$$
Then its Gram-graded Euler/Fock determinant is
$$
64q^{1/2}r^{1/2}s^{1/2}
\prod_{\gamma\in\Gamma_{\mathrm{eff}}}(1-x^\gamma)^{\sdim\mathcal B_\gamma}
=\Delta_5(Z).
$$
If $\mathcal B$ carries a bracket compatible with charge addition, a
parity split, simple-root representatives, or a Hopf pairing, the
determinant forgets those data and remembers the class of
$\mathcal B$ in
$$K_0(\Gamma_{\mathrm{eff}}\hbox{-graded finite super vector spaces}).$$
Thus the determinant of
$\mathcal A_{\mathrm{den}}=\mathfrak g_{\Delta_5}$ is
the Grothendieck shadow of its denominator bracket.  The Borcherds
denominator bracket exists inside \(\mathcal A_{\mathrm{den}}\) by the
Gritsenko--Nikulin construction, but the determinant sees only its
charge-graded Grothendieck class.
\end{proposition}

\begin{proof}
The Fock determinant lemma gives
$$
\sdet_{\mathcal B}(1-x)
=\prod_{\gamma\in\Gamma_{\mathrm{eff}}}(1-x^\gamma)^{\sdim\mathcal B_\gamma}.
$$
The hypothesis $\sdim\mathcal B_{(n,l,m)}=f(nm,l)$ identifies this
product with the Borcherds product for $64^{-1}\Delta_5$.  Multiplying
by the vacuum factor gives $\Delta_5$.  A bracket
$$[\mathcal B_\gamma,\mathcal B_{\gamma'}]\to
\mathcal B_{\gamma+\gamma'}$$
does not occur in the determinant formula.  Neither do simple primitive
representatives, parity dimensions, relation constants, completed PBW
data, or a Hopf-pairing radical.  The determinant is therefore invariant
under replacing \(\mathcal B\) by any other graded super vector space with
the same Grothendieck class.  In particular the zero bracket on such a
space gives the same determinant and the wrong Lie algebra, and adjoining
a root-graded cancelling pair \(M\oplus\Pi M\) changes possible brackets
and radicals without changing the signed determinant.
\end{proof}

\section{The scalar square}

Unitarity is used to localize the right-moving K3 supertrace before the
index is taken; the index itself is a charge-graded virtual object that
no longer requires Hilbert positivity, so the OP/DT scalar series below
records charge-graded coefficients of a virtual character, not
dimensions of a positive Hilbert space.

$$Z^X_{\mathrm{DT}}(q,t,p)=
\sum_{h=0}^{\infty}\sum_{d=0}^{\infty}\sum_{n\in\mathbb{Z}}
\mathbf{DT}^X_{n,(\beta_h,d)}
q^{d-1}t^{\frac{1}{2}\langle\beta_h,\beta_h\rangle}(-p)^n.$$

\begin{center}
\small
\begin{tabular}{c|c|c|c}
role & OP variable & DT variable & Borcherds variable \\ \hline
\(K3\) norm \(h-1\) & \(q_{\mathrm{OP}}\) & \(t_{\mathrm{DT}}\) & \(q_{\mathrm{Bch}}\) \\
elliptic degree \(d-1\) & \(\widetilde q_{\mathrm{OP}}\) & \(q_{\mathrm{DT}}\) & \(s_{\mathrm{Bch}}\) \\
D0/Fourier index \(n\) & \(p_{\mathrm{OP}}=e^{iu}\) & \(p_{\mathrm{DT}}\) with \((-p_{\mathrm{DT}})^n\) & \(r_{\mathrm{Bch}}\)
\end{tabular}
\end{center}

\begin{proposition}[Oberdieck--Pixton normalization]
\label{prop:op-normalization}
Let the Oberdieck--Pixton variables be
$$p_{\mathrm{OP}}=e^{iu},\qquad q_{\mathrm{OP}},\qquad
\widetilde q_{\mathrm{OP}}.$$
The variable map is
$$q=q_{\mathrm{OP}},\qquad r=p_{\mathrm{OP}},\qquad
s=\widetilde q_{\mathrm{OP}}.$$
The product index set is
\[
h,d\ge0,\qquad h>0\ \hbox{or}\ d>0,
\qquad\hbox{or}\qquad h=d=0,\ k<0.
\]
The Laurent expansion is the Oberdieck--Pixton expansion in its specified
chamber.  The reciprocal \(p_{\mathrm{OP}}\)-direction used to compare it
with a Borcherds cusp expansion is the formal re-expansion convention
\[
0<|\widetilde q_{\mathrm{OP}}|\ll
|q_{\mathrm{OP}}|\ll |p_{\mathrm{OP}}|^{-1}\ll1,
\qquad r=p_{\mathrm{OP}}.
\]
This convention is recorded separately from the imported OP scalar
identity.  The enumerative identity is the Laurent expansion obtained
after \(p_{\mathrm{OP}}=e^{iu}\) and \(y=-e^{iu}\).
For the displayed DT variables,
$$q_{\mathrm{DT}}=\widetilde q_{\mathrm{OP}}=s,\qquad
t_{\mathrm{DT}}=q_{\mathrm{OP}}=q,\qquad
p_{\mathrm{DT}}=p_{\mathrm{OP}}=r.$$
The product denoted $\chi_{10}$ by Oberdieck--Pixton is
$$\chi_{10}^{\mathrm{OP}}
=D_5^2
=\left(64^{-1}\Delta_5\right)^2
=4096^{-1}\Delta_5^2.$$
Consequently their primitive reduced partition function is
$$Z^X_{\mathrm{OP}}=-\left(\chi_{10}^{\mathrm{OP}}\right)^{-1}
=-4096\,\Delta_5^{-2}.$$
\end{proposition}

\begin{proof}
Oberdieck--Pixton use the primitive expansion \cite[Theorem 1]{OB}
$$
Z^X_{\mathrm{OP}}
=\sum_{g,h,d}N_{g,h,d}u^{2g-2}
q_{\mathrm{OP}}^{h-1}\widetilde q_{\mathrm{OP}}^{d-1}
$$
and the stable-pairs substitution, in the coordinate convention of
Oberdieck--Pandharipande \cite[Section 2]{OPand},
$$y=-p_{\mathrm{OP}},\qquad p_{\mathrm{OP}}=e^{iu}.$$
There
$$
\Omega=\begin{pmatrix}\tau&z\\ z&\widetilde\tau\end{pmatrix},\qquad
p_{\mathrm{OP}}=e^{2\pi iz}=e^{iu},\qquad
q_{\mathrm{OP}}=e^{2\pi i\tau},\qquad
\widetilde q_{\mathrm{OP}}=e^{2\pi i\widetilde\tau}.
$$
The displayed DT convention uses
$$q_{\mathrm{DT}}^{d-1}t_{\mathrm{DT}}^{h-1}(-p_{\mathrm{DT}})^n,$$
and Bryan records that the DT convention interchanges the $q$ and
$\widetilde q$ variables relative to Oberdieck--Pandharipande
\cite[Definition 2.1 and Conjecture 2.3]{BRYAN}.  This gives the stated
variable map.

Oberdieck--Pixton define the Igusa product by \cite[(3)]{OB}
$$
\chi_{10}^{\mathrm{OP}}(p,q,\widetilde q)
=pq\widetilde q
\prod(1-p^kq^h\widetilde q^d)^{c(4hd-k^2)}
$$
in the chamber $h>0$ or $d>0$, together with $h=d=0,\ k<0$.  The
exponents are the K3 elliptic-genus coefficients.  Since
$$Z_{\mathrm{K3}}=2\phi_{0,1},\qquad
\phi_{0,1}=\sum f(n,l)q^nr^l,$$
those exponents are $2f(nm,l)$.  Therefore the Oberdieck--Pixton monic
product is exactly the square of
$$D_5=64^{-1}\Delta_5
=q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}.$$
Their Theorem 1, equivalently the Laurent expansion in \cite[(56)]{OB},
gives $Z^X_{\mathrm{OP}}=-1/\chi_{10}^{\mathrm{OP}}$.
\end{proof}

\begin{theorem}[Reduced DT/PT/OP scalar square]
\label{thm:op-square}
Let \(\beta_h\in H_2(S,\Z)\) be primitive and non-zero, with
$$\langle\beta_h,\beta_h\rangle=2h-2.$$
Under the variable map
$$
p=P=e^{iu},\qquad t=Q,\qquad q=T,\qquad
(q_{\mathrm{Bch}},r_{\mathrm{Bch}},s_{\mathrm{Bch}})=(Q,P,T),
$$
one has
$$
Z^X_{\mathrm{DT}}(T,Q,P)
=Z^X_{\mathrm{OP}}(P,Q,T)
=-4096\,\Delta_5(Z)^{-2}.
$$
The equality is an equality of Laurent expansions in the OP chamber of
Proposition~\ref{prop:op-normalization}.  It is the theorem-level
OP/DT/PT scalar branch attached to the Behrend-weighted quotient
integration of Proposition~\ref{prop:reduced-scalar-quotient-integration}.
The physical protected-index identification is
Conjecture~\ref{conj:protected-d-brane-index}.
Imprimitive K3 curve classes require the separate imprimitive
multiple-cover certificate; the displayed OP scalar-square theorem is the
primitive-class branch used for the present square-root comparison.
\end{theorem}

\begin{proof}
Oberdieck's reduced DT/PT theorem for \(S\times E\),
\cite[Theorem 3(i)]{OberdieckReducedPT}, gives, for every non-zero
\(\beta\in H_2(S,\Z)\) and every \(d\ge0\),
$$
\sum_n\mathbf{DT}^X_{n,(\beta,d)}x^n
=
\sum_n\mathsf P^X_{n,(\beta,d)}x^n.
$$
Set \(x=-P\).  The degree-zero factor is
$$M(-P)^{\chi(S\times E)}=M(-P)^0=1.$$
For primitive \(\beta_h\), the reduced GW/PT comparison of
Oberdieck--Pandharipande \cite[Proposition 5]{OPand} gives
$$
\sum_n\mathsf P^X_{n,(\beta_h,d)}(-P)^n
=
\sum_g\mathsf N^X_{g,h,d}u^{2g-2},\qquad P=e^{iu}.
$$
Multiplying by \(Q^{h-1}T^{d-1}\) and summing over \(h,d\) gives
$$Z^X_{\mathrm{DT}}(T,Q,P)=Z^X_{\mathrm{OP}}(P,Q,T).$$
Oberdieck--Pixton \cite[Theorem 1]{OB} and
Proposition~\ref{prop:op-normalization} give
$$Z^X_{\mathrm{OP}}(P,Q,T)=-4096\,\Delta_5(Z)^{-2}.$$
\end{proof}

\begin{definition}[OP normalization branch]
\label{def:op-normalization-branch}
The OP/DT normalization branch is the proved enumerative series of
Theorem~\ref{thm:op-square}, displayed as a square in the OP convention:
$$
Z^X_{\square,\mathrm{OP/DT}}
:=Z^X_{\mathrm{DT}}=Z^X_{\mathrm{OP}}
=-4096\,\Delta_5^{-2},
\qquad
C_{\square,\mathrm{OP/DT}}:=-4096.
$$
The numerical constant \(C_{\square,\mathrm{OP/DT}}=-4096\) is a
\emph{normalization} datum, not an enumerative invariant beyond the
identification of the series itself: it factors as
\(-4096=(-1)\times 64^2\), where the \(64^2\) is the squared theta-leading
coefficient \(([q^{1/2}r^{1/2}s^{1/2}]\Delta_5)^2\) and the leading
\(-1\) is the OP scalar convention
\(Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1}\).  No additional
enumerative content beyond the identification of \(Z^X_{\mathrm{OP}}\)
with \(D_5^{-2}\) is carried by the constant.
An external scalar-square series, if introduced later, is a Laurent
expansion of the form
$$Z^X_{\square,\mathrm{ext}}(Z)
=\frac{C_{\square,\mathrm{ext}}}{\Delta_5(Z)^2},
\qquad C_{\square,\mathrm{ext}}\in\C^\times,$$
and carries no OP/DT enumerative status unless its source is specified.
\end{definition}

\begin{proposition}[Square-root consequence]
For \(\mathfrak s\in\{\mathrm{OP},\mathrm{DT}\}\), with variables
normalised as in Theorem~\ref{thm:op-square},
$$Z^X_{\mathfrak s}(Z)=-4096\,\Delta_5(Z)^{-2}.$$
Thus
$$\mathcal{D}_X(Z)^2=\frac{-4096}{Z^X_{\mathfrak s}(Z)},
\qquad \mathcal D_X(Z)=\Delta_5(Z).$$
	The virtual inverse is fixed by the normalized determinant:
$$\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}:=\mathcal D_X^{-1}.$$
A supplied Pfaffian square root may differ from this chosen cusp
trivialization by a sign character; that sign is the orientation datum
sought in Open Problem~\ref{op:orientation-monodromy-character} and is
not determined by the OP scalar.  The squared scalar
\(Z^X_{\mathfrak s}=-4096(\mathcal D_X^{-1})^2\) does not fix an
orientation-lifted Pfaffian sign because squaring kills it.  With the
fixed virtual inverse,
$$Z^X_{\mathfrak s}
=-4096\,(\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}})^2,$$
$$|\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}|
=\frac{1}{64}|q|^{-1/2}|r|^{-1/2}|s|^{-1/2}|\sch\mathcal F(\mathcal V)|.$$
\end{proposition}

\begin{proof}
Theorem~\ref{thm:op-square} gives the first display for
\(\mathfrak s=\mathrm{OP}\) and \(\mathfrak s=\mathrm{DT}\).  Hence
$$-4096/Z^X_{\mathfrak s}=\Delta_5^2.$$
The Borcherds determinant \(\mathcal D_X=\Delta_5\) fixes the
automorphic square-root section in the chosen cusp trivialization.  A
supplied Pfaffian orientation lift may carry an additional sign character,
but that sign is not part of the notation
\(\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}\).  Squaring any supplied
sign choice \(\varepsilon\), with \(\varepsilon^2=1\), gives
$$Z^X_{\mathfrak s}=-4096(\mathcal D_X^{-1})^2
=-4096(\varepsilon\mathcal D_X^{-1})^2,$$
the square-root sign being invisible to the scalar.
Selecting the sign requires an orientation datum, deferred to
Open Problem~\ref{op:orientation-monodromy-character}.
\end{proof}

\begin{remark}[Constants are not orientation data]
The number \(64\) fixes the theta-normalized Igusa section and hence the
Weyl monomial in the determinant:
$$
\Delta_5
=64q^{1/2}r^{1/2}s^{1/2}
\prod(1-q^nr^ls^m)^{f(nm,l)}.
$$
The monic denominator section is \(D_5=64^{-1}\Delta_5\).  The number
\(4096\) is \(64^2\), appearing because Oberdieck--Pixton use
$$
\chi_{10}^{\mathrm{OP}}=D_5^2=4096^{-1}\Delta_5^2.
$$
Read as a normalization conversion, the OP scalar constant factors as
$$
-4096 \;=\; (-1)_{\mathrm{OP}}\cdot 64^2,
$$
where the leading \(-1\) is the OP scalar convention and \(64^2\) is the
squared theta-leading coefficient
\(([q^{1/2}r^{1/2}s^{1/2}]\Delta_5)^2\).  It is not the square of an
orientation sign; every square-root sign squares to \(+1\).
The minus sign in
$$
Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1}
$$
is the OP scalar convention.  None of these constants is the Hall
orientation character.  The automorphic character
\(\nu_{\Delta_5}\) is fixed by the Maass transformation law, and the
geometric character \(\epsilon_o\), if it exists, must be produced by
orientation-line monodromy as in
Open Problem~\ref{op:orientation-monodromy-character}.
\end{remark}

\section{Coefficient dictionary and main synthesis}
\label{sec:coefficient-dictionary-main-synthesis}

The coefficient convention is fixed once and for all by
Eichler--Zagier normalization:
$$
Z_{\mathrm{K3}}=2\phi_{0,1},\qquad
\phi_{0,1}(\tau,z)=\sum_{n\ge0,\ l\in\Z}f(n,l)q^nr^l.
$$
Equivalently, if \(\phi_{12,1}\) is the first Fourier--Jacobi
coefficient of Igusa's weight-\(12\) form \(F_{12}\)
\cite{Igusa1962,Igusa1964II}, and if
$$
\delta_{12}(\tau)=q\prod_{n\ge1}(1-q^n)^{24},
$$
then
$$
\phi_{0,1}=\frac{\phi_{12,1}}{\delta_{12}}.
$$
The first terms are
$$
\phi_{0,1}
=(r^{-1}+10+r)
+q(10r^{-2}-64r^{-1}+108-64r+10r^2)
$$
$$
\qquad
+q^2(r^{-3}+108r^{-2}-513r^{-1}+808
-513r+108r^2+r^3)+O(q^3).
$$
Thus
$$
f(0,-1)=1,\qquad f(0,0)=10,\qquad
f(1,1)=-64,\qquad f(1,0)=108.
$$
The weak Jacobi support condition is
$$
f(n,l)=0\quad\hbox{unless}\quad n\ge0,\quad 4n-l^2\ge-1,
$$
and \(f(n,l)=f(n,-l)\).  These integers have three distinct readings in
the paper:
$$
\begin{array}{c|c}
\hbox{object} & \hbox{meaning of }f(nm,l) \\ \hline
\mathcal V_{(n,l,m)} & \hbox{virtual \(K_0\)-superdimension} \\
\mathcal D_X & \hbox{Borcherds product exponent} \\
\mathfrak g_{\Delta_5,\alpha(n,l,m)} &
\hbox{signed root supermultiplicity on active support}
\end{array}
$$
The first reading is a protected Euler characteristic.  The second and
third readings are automorphic and denominator-algebra incarnations of
the same integer.  This is not an equality of Hilbert spaces, brackets,
or Hall structure constants.

The synthesis is the following spine:
\[
\begin{gathered}
\hbox{virtual determinant}
\longrightarrow
\hbox{formal charge and normal ordering}
\longrightarrow
\hbox{denominator algebra}
\longrightarrow
\hbox{reduced scalar square}
\\
\longrightarrow
\hbox{compact realization problem}
\longrightarrow
\hbox{eight-row certificate extension}.
\end{gathered}
\]
\begin{theorem}[Coefficient dictionary and synthesis theorem]
\label{thm:protected-igusa-determinant}
Let \(X=K3\times E\).  Let
\[
\mathbb U_{n,l}\in K_0(\mathrm{sVect}_{\mathrm{fd}}),\qquad
\sdim\mathbb U_{n,l}=f(n,l),
\]
and define the virtual \(K_0\)-determinant object in the cusp chamber by
\[
\mathcal V_{(n,l,m)}=\mathbb U_{nm,l},\qquad
(n,l,m)\in\Gamma_{\mathrm{eff}}.
\]

First, the virtual determinant is the theta-normalized Igusa square root:
\[
\mathcal D_X(Z)
=64q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_{\mathrm{eff}}}
(1-q^nr^ls^m)^{f(nm,l)}
=\Delta_5(Z).
\]
The numerical factor \(64\) is the theta-constant leading coefficient
\([q^{1/2}r^{1/2}s^{1/2}]\Delta_5\); the monic Borcherds product is
\[
D_5=64^{-1}\Delta_5.
\]

Second, the formal dyonic Mukai lattice is additive but its Igusa Gram
shadow is quadratic.  For
\[
\Gamma_X^{\mathrm{form}}=\Lambda_S\oplus\Lambda_S,\qquad c=(Q,P),
\]
the map
\[
\Pi_X(c)=\left(\frac{Q^2}{2},Q\cdot P,\frac{P^2}{2}\right)
\]
satisfies
\[
\Pi_X(c+c')=\Pi_X(c)+\Pi_X(c')+B(c,c').
\]
The normal-ordered extension
\[
\widehat\Gamma_X=\Gamma_X^{\mathrm{form}}\oplus_B\Gamma_{\mathrm{gram}},
\qquad
\overline\Pi_X(c,T)=\Pi_X(c)-T
\]
is additive, and every formal Gram triple has a primitive saturated
formal lift when \(\Lambda_S\) contains two orthogonal hyperbolic planes.
This does not prove algebraic/effective compact Hall support.  Strict
fixed-lift raw \(\Pi_X\)-descent cannot realize the type-II BKM real-root
strings; Theorem~\ref{thm:raw-gram-descent-no-go} is the obstruction.

Third, under the Lorentzian degree map
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2},
\qquad
q^nr^ls^m=\exp(-\pi i(\alpha(n,l,m),z)),
\]
the same active coefficients are the visible signed root
supermultiplicities of the Gritsenko--Nikulin denominator algebra:
\[
\smult\mathfrak g_{\Delta_5,\alpha(n,l,m)}
=f(nm,l)
\qquad ((n,l,m)\in\Gamma_{\mathrm{act}}),
\]
and
\[
\operatorname{den}(\mathfrak g_{\Delta_5})
=64^{-1}\Delta_5(2Z).
\]
This is the Gritsenko--Nikulin denominator theorem.  It determines the
signed root supermultiplicities in the fixed Borcherds datum; it does
not determine compact Hall constants or microscopic brackets.  The
normal-ordered charge extension is the necessary degree-level bridge
from an additive Hall source to these Gram degrees.

Fourth, for the reduced Hilbert-scheme DT/PT/OP scalar branch,
\[
Z^X_{\mathrm{DT}}(T,Q,P)=Z^X_{\mathrm{OP}}(P,Q,T)
=-4096\,\Delta_5(Z)^{-2}.
\]
Here
\[
\chi_{10}^{\mathrm{OP}}=D_5^2=(64^{-1}\Delta_5)^2
=4096^{-1}\Delta_5^2,
\qquad
Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1};
\]
hence \(-4096=-(64)^2\) is the OP scalar sign together with the
theta-to-monic normalization.  It is not an orientation character.
Thus, with
\[
\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}}=\mathcal D_X^{-1},
\]
one has
\[
Z^X_{\mathrm{DT}}=Z^X_{\mathrm{OP}}
=-4096\,(\mathcal Z_{\mathrm{Borch}}^{\mathrm{vir}})^2.
\]

Fifth, the stronger microscopic comparison
\[
H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^{\Theta}\mathcal F_X)/
\overline{\operatorname{Rad}\langle\,\cdot\,,\,\cdot\,\rangle_X}
\cong
\mathfrak g_{\Delta_5}
\]
is open unless a Dirac--Igusa realization certificate in the sense of
Definition~\ref{def:compact-igusa-realization-datum} is supplied.
If such a certificate were supplied, Theorem~\ref{thm:primitive-recognition}
would identify its primitive denominator with \(64^{-1}\Delta_5(2Z)\); no
such certificate is constructed in this paper.

Sixth, any claimed compact realization must also satisfy three
consequences.
\begin{enumerate}
\item A naive support-local factorization object on
\(\operatorname{Ran}(E)\) sees only projection-finite sectors.  If a
one-dimensional subscheme of \(K3\times E\) has positive elliptic
degree, its projection to \(E\) is all of \(E\).  Thus the full
\(s\)-direction of the Igusa product requires finite-stage
local/wrapped data: \(b_R\), rigidified wrapped prequotients, mixed
extension correspondences in both local/wrapped orders,
wrapped/wrapped correspondences, the eight-word two-step binary flag atlas in
\(\mathsf{Corr}^{E,\mathrm{hyb}}_R\), the higher colored residual
\(\mathfrak o^{\mathrm{col}}_R\), properness/admissibility residuals
for the pull-push operations, quotient-after-correspondence
\(Q_{E,R}\)-compatibility, and protected integration with trace degree
\(s^{b_R}\).  Equivalently,
\(\mathfrak O_{\mathrm{hyb},R}=0\) for every finite \(R\).  A separate
global Fock/Hecke mode is only
determinant-level unless it is coupled to the local sector by mixed Hall
actions before the reduced \(E\)-quotient.
\item The automorphic character \(\nu_{\Delta_5}\) is theorem-level
data of \(\Delta_5\), and \(\Delta_5^2\) forgets it.  A compact Hall
orientation must construct a strong orientation character
\(\epsilon_o\) and prove
\[
\epsilon_o|_{W^{(2)}(\Lambda^{2,1}_{II})}
=\nu_{\Delta_5}|_{W^{(2)}(\Lambda^{2,1}_{II})}.
\]
The constants \(64\), \(4096\), and the OP minus sign do not solve this
orientation-monodromy problem.  The Hall-side proof must compute the
three simple type-II determinant-line signs and check the reflection
relations.
\item A primitive comparison with \(\mathfrak g_{\Delta_5}\) is a
presentation-level recognition certificate, not a consequence of signed
dimensions.  One must supply primitive representatives for the real and
imaginary simple roots, their parities, the Chevalley, real Serre and
orthogonality relations, generation, full root-space parity dimensions,
the completed Hopf pairing and the same closed radical quotient, a
no-extra-relations theorem, and completed PBW compatibility in the
finite-height inverse system, including exact triangular
completion/\(\lim^1\)-vanishing and Koszul Mittag--Leffler exactness for
the chiral cobar comparison.  Under these hypotheses the
Borcherds--Kac universal presentation gives the isomorphism with
\(\mathfrak g_{\Delta_5}\); without them the determinant fixes only a
Grothendieck class.
\end{enumerate}

Finally, the diagonal-divisor rows extend this same logic.  A row is
promoted beyond its automorphic product only by a row certificate fixing
the modular group or cover, character, divisor, Jacobi seed, product
lattice, Weyl chamber, reflection character, scalar theorem if one is
claimed, orientation data, one-particle index, and primitive algebra
comparison.
\end{theorem}

\begin{proof}
The Fock trace calculation gives
\[
\mathcal D_X
=64q^{1/2}r^{1/2}s^{1/2}\sdet_{\mathcal V}(1-x).
\]
The Borcherds--Gritsenko--Nikulin product formula for the input
\(\phi_{0,1}\) identifies this product with \(\Delta_5\), as recorded in
Proposition~\ref{prop:bgn-identification}.  The leading coefficient
\(64\) is fixed in the theta-normalized Fourier expansion of
\(\Delta_5\), hence \(D_5=64^{-1}\Delta_5\) is the monic product.

The formal charge and normal-ordering statements are
Definition~\ref{def:additive-physical-charge-lattice},
Lemma~\ref{lem:primitive-lift-every-gram-triple},
Lemma~\ref{lem:gram-additivity-defect},
Lemma~\ref{lem:b-cocycle-central-extension}, and
Definition~\ref{def:gram-corrected-charge-extension}.  They are direct
lattice calculations in the Mukai pairing.  The raw-descent obstruction
is Theorem~\ref{thm:raw-gram-descent-no-go}; it uses the non-zero
second real-root strings recorded in
Proposition~\ref{prop:low-degree-denominator-brackets}.

The Lorentzian monomial identity and pairing computation are in
Section~\ref{sec:duality-principle} and the Weyl-chamber section.  The
root-supermultiplicity and denominator identity are
Theorem~\ref{thm:denominator-algebra-identity}; the argument \(2Z\)
comes from passing from
\(\exp(-\pi i(\alpha,z))\) to the usual denominator character
\(\exp(-2\pi i(\alpha,z))\).

The reduced scalar identity is Theorem~\ref{thm:op-square}, with the
normalization conversion of Proposition~\ref{prop:op-normalization}.
Since Oberdieck--Pixton use
\(\chi_{10}^{\mathrm{OP}}=D_5^2\) and prove
\(Z^X_{\mathrm{OP}}=-(\chi_{10}^{\mathrm{OP}})^{-1}\), the theta
normalization gives
\[
Z^X_{\mathrm{OP}}=-4096\Delta_5^{-2}.
\]
Oberdieck's reduced DT/PT comparison and the primitive
Oberdieck--Pandharipande comparison give the same branch for
\(Z^X_{\mathrm{DT}}\).

The compact comparison is not used in these proofs.  It is precisely
Open Problem~\ref{op:compact-igusa-realization}.  The
\(\operatorname{Ran}(E)\) obstruction follows because a positive
elliptic-degree curve has one-dimensional image in the irreducible
curve \(E\), hence image \(E\); support separation on disjoint opens of
\(\operatorname{Ran}(E)\) cannot see such a sector.  The automorphic
character computation gives the target values of \(\nu_{\Delta_5}\);
rescaling \(\Delta_5\) by \(64^{-1}\) changes no character.  A compact
orientation statement follows only after (O1) constructs the reduced
quotient orientation, (O1)\(^+\) supplies the honest Weyl transport, and
(O2) supplies the local Pfaffian signs.  The
primitive recognition statement is the universal property of the
Borcherds--Kac presentation recorded in the denominator-algebra section,
together with the closed Hopf-radical and completed PBW hypotheses in
Theorem~\ref{thm:primitive-recognition}.  The determinant and scalar
square do not contain the missing presentation, orientation, radical, PBW,
or Hall correspondence data.  The row certificate condition is the same
separation applied to the Clery--Gritsenko catalogue in the next part.
\end{proof}

\part{Diagonal-divisor rows and CHL boundary physics}

\section{Eight diagonal-divisor rows: automorphic and physical status}
\label{sec:eight-dd-rows-status}

The Clery--Gritsenko catalogue gives eight
diagonal-divisor automorphic products.  The Gritsenko--Nikulin and
Govindarajan theorems promote these products to denominator identities
in the rows where the Weyl data are known.  A CHL dyon square, a reduced
CY/DT scalar host, and a compact Hall/chiral host are further structures,
recorded only where their data have been specified.

$$g=2.$$
$$t,N \in \mathbb{Z}_+:\quad \Gamma_t(N) =
\{\begin{pmatrix}*&*t&*&*\\*&*&*&*t^{-1}\\*N&*Nt&*&*\\*Nt&*Nt&*t&*\end{pmatrix}
\in \Sp_4(\mathbb{Q})\mid *\in\mathbb{Z}\}.$$
$$\mathbb H_2/\Gamma_t
\longleftrightarrow\{(1,t)\hbox{-polarized abelian surfaces}\}.$$
$$\mathcal H_{\mathrm{diag}}
=\left\{\begin{pmatrix}a&0\\0&b\end{pmatrix}\mid
a,b\in\mathbb{H}_1\right\}\subset\mathbb{H}_2.$$

\begin{definition}[Physical-host certificate]
\label{def:physical-host-certificate}
For a diagonal-divisor row \(F_j\), a physical-host certificate is a
five-level certificate table
\[
\mathfrak C_j=
\left(
\mathscr A_j,\mathscr D_j,\mathscr S_j,\mathscr Z_j,\mathscr H_j
\right).
\]
The entries have the following meanings.
\begin{enumerate}
\item \(\mathscr A_j\) is the automorphic product certificate: the form
\(F_j\), the group or multiplier cover, the automorphy cocycle, the
character or multiplier with exact order, the diagonal divisor with
multiplicities, the product chamber and branch, the Jacobi input at
every cusp, the product-degree map, the product normalization, and the
source theorem.
\item \(\mathscr D_j\) is the denominator certificate: a
Weyl--Kac--Borcherds denominator algebra with root lattice, Weyl vector,
simple real roots, Weyl chamber, Weyl group, reflection character,
imaginary simple-root coefficients, product side, and Weyl alternating
side.
\item \(\mathscr S_j\) is a CHL/dyon-square certificate: a sourced
dyon-counting scalar form \(\Phi_j\), a row map to the same automorphic
row and cover, and an identity \(F_j^2=\Phi_j\) in the stated chamber.
This is not a denominator theorem and not a CY/DT partition theorem.
\item \(\mathscr Z_j\) is a reduced CY/DT scalar-host certificate: a
compact Calabi--Yau threefold, orbifold Calabi--Yau, or CHL background
with oriented reduced obstruction theory, fixed variables and chamber,
and a proved identity
\[
Z^{X_j}_{\mathrm{red}}(Z)=C_jF_j(Z)^{-2}.
\]
\item \(\mathscr H_j\) is a compact Hall/chiral certificate: an oriented
compact Hall, Drinfeld, or factorization object whose protected
one-particle index gives the product exponents and whose protected
primitive bracket identifies the denominator algebra with the same
orientation/reflection character.
\end{enumerate}
The product row, denominator row, dyon square, reduced scalar host, and
compact Hall/chiral host are separate structures.  None of the five
entries implies another unless a cited theorem constructs the implication.
In particular, matching a weight, a square root, or a comparison symbol
does not fill a certificate.  A row-map theorem must name the host,
charge lattice, effective chamber, modular group or cover, product
lattice, orientation character, one-particle index, scalar identity when
claimed, and primitive Hall/chiral comparison.
\end{definition}

\begin{theorem}[Clery--Gritsenko]
In the class of Siegel modular forms with character or multiplier system
for the Hecke-type congruence subgroups $\Gamma_t(N)$ whose divisor is
the union of the $\Gamma_t(N)$-translates of $\mathcal H_{\mathrm{diag}}$
with multiplicity one, there are exactly eight rows
\cite[Theorem 1.4]{GC}.  The nine-candidate list is
\cite[Proposition 1.2]{GC}; the proof of Theorem 1.4 excludes only
the ninth candidate \((t,N;k)=(2,4;\frac12)\).  The congruence
Borcherds product with all
cusp coefficients is \cite[Theorem 3.1]{GC}, with the final Section 3
product displays for $\nabla_3,\nabla_2,\nabla_{3/2}$, and $Q_1$.
\end{theorem}

$$
\begin{array}{c|c|c|c|c}
j&F_j&\Gamma&\mathrm{wt}(F_j)&\mathrm{character/multiplier}\\ \hline
1&\Delta_5&\Gamma_1&5&v_\eta^{12}\times v_H\\
2&\Delta_2&\Gamma_2&2&v_\eta^{6}\times v_H\\
3&\Delta_1&\Gamma_3&1&v_\eta^{4}\times v_H\\
4&\Delta_{1/2}&\Gamma_4&\frac12&v_\eta^{3}\times v_H\ (\mathrm{degree}\ 8)\\
5&\nabla_3&\Gamma_0^{(2)}(2)&3&\chi_2^{(2)}\times v_H\\
6&\nabla_2&\Gamma_0^{(2)}(3)&2&\chi_2^{(3)}\times v_H\\
7&\nabla_{3/2}&\Gamma_0^{(2)}(4)&\frac32&
\hbox{order-four multiplier } \chi_4^{(4)}\times v_H\\
8&Q_1&\Gamma_2(2)&1&\chi_4^{(2)}\times v_H
\end{array}
$$
$$\operatorname{supp}\operatorname{div}_{\mathbb H_2}(F_j)
=\bigcup_{\gamma\in\Gamma_j}\gamma\langle\mathcal H_{\mathrm{diag}}\rangle,
\qquad
\operatorname{mult}_{\mathcal H_{\mathrm{diag}}}(F_j)=1.$$

$$F_1=\Delta_5,\qquad
\frac1{64}F_1(2Z)=\operatorname{den}(\autcor).$$

\begin{center}
\begingroup
\setlength{\tabcolsep}{3pt}
\scriptsize
\begin{tabular}{@{}c p{0.14\textwidth} p{0.16\textwidth} p{0.16\textwidth} p{0.17\textwidth} p{0.17\textwidth}@{}}
\hline
row & automorphic product & denominator theorem & CHL/dyon square &
reduced CY/DT scalar host & compact Hall/chiral host \\
\hline
1 &
\(F_1=\Delta_5\); Clery--Gritsenko product and
Borcherds--Gritsenko--Nikulin lift of \(\phi_{0,1}\) &
Gritsenko--Nikulin denominator algebra \(\mathfrak g_{\Delta_5}\);
\(64^{-1}\Delta_5(2Z)\) normalization &
no CHL row map used; \(\Delta_5^2\) is the Igusa scalar square, not a
boundary dyon certificate &
proved OP/DT \(K3\times E\) scalar host:
\(-4096\Delta_5^{-2}\) &
open; the formal determinant is not a compact Hall/chiral source \\
2 &
\(F_2=\Delta_2\); Clery--Gritsenko product &
Gritsenko--Nikulin denominator row \(\mathfrak g^{\mathrm{GN}}_2\) &
no certified CHL/dyon row map &
no certified curve-counting scalar theorem &
no certified Hall or factorization host \\
3 &
\(F_3=\Delta_1\); Clery--Gritsenko product &
Gritsenko--Nikulin denominator row \(\mathfrak g^{\mathrm{GN}}_3\) &
no certified CHL/dyon row map &
no certified curve-counting scalar theorem &
no certified Hall or factorization host \\
4 &
\(F_4=\Delta_{1/2}\); Clery--Gritsenko product on the degree-eight
multiplier cover &
Gritsenko--Nikulin denominator row on the same cover
\(\mathfrak g^{\mathrm{GN}}_4\) &
no certified CHL/dyon row map &
no certified curve-counting scalar theorem &
no certified Hall or factorization host \\
5 &
\(F_5=\nabla_3\); Clery--Gritsenko product &
Govindarajan \(\mathcal G_1(2)\) CHL/WKB denominator theorem &
sourced scalar dyon square \(\nabla_3^2=\Phi_6^{(1,2)}\) &
no reduced CY/DT certificate &
no compact Hall/chiral certificate \\
6 &
\(F_6=\nabla_2\); Clery--Gritsenko product &
Govindarajan \(\mathcal G_1(3)\) CHL/WKB denominator theorem &
sourced scalar dyon square \(\nabla_2^2=\Phi_4^{(1,3)}\) &
no reduced CY/DT certificate &
no compact Hall/chiral certificate \\
7 &
\(F_7=\nabla_{3/2}\); Clery--Gritsenko product on the order-four
multiplier cover &
Govindarajan \(\mathcal G_1(4)\) CHL/WKB denominator theorem on the
\(\mu_4\)-cover &
sourced scalar dyon square \(F_7^2=\Phi_3\) for the composite \(N=4\)
scalar form, only after fixing the cover and branch &
no reduced CY/DT certificate &
no compact Hall/chiral certificate \\
8 &
\(F_8=Q_1\); Clery--Gritsenko \((t,N)=(2,2)\) product &
Govindarajan \(\mathcal G_2(4)\) CHL/WKB denominator theorem &
sourced twisted dyon square \(Q_1^2=\Phi_2^{(2,4)}\); \(Q_1\) is the
special \(\mathcal G_2(4)\) row &
no reduced CY/DT certificate &
no compact Hall/chiral certificate \\
\hline
\end{tabular}
\endgroup
\end{center}

By Theorem~\ref{thm:gn-denominator-234} the full-paramodular rows
$F_2,F_3,F_4$ carry Gritsenko--Nikulin denominator identities.
The cited sources do not construct a reduced curve-counting theorem,
Hall object, or factorization host for these three rows.
The congruence rows $F_5,F_6,F_7,F_8$ have product-degree lattices in
Proposition~\ref{prop:congruence-product-degree-lattices}.  The
additional denominator data (Weyl chamber, real roots, reflection
character, Weyl sum) are supplied by the CHL denominator theorem
of Govindarajan for \(F_5,F_6,F_7,F_8\).
For \(F_7\) the theorem lives on the
$\mu_4$-multiplier cover determined by the Clery--Gritsenko order-four
multiplier.  For \(Q_1\) the row is the special \(\mathcal G_2(4)\)
twisted CHL denominator row.  Neither statement supplies a reduced
CY/DT scalar host or compact Hall/chiral certificate.

\begin{proposition}[Extension separation]
\label{prop:extension-quarantine}
No statement in this section is used in the $N=1$ theorem for
$\Delta_5$.  For every row the product formula itself gives a
Gram-indexed primitive product.  It gives a Gram-graded Euler/Fock determinant only
after a one-particle index and a charge-invariant interpretation have
been supplied.
A nonabelian denominator theorem is stronger: it additionally requires a
Weyl chamber, real simple roots, a reflection character, and a Weyl
alternating sum.
\end{proposition}

\begin{openproblem}[Certificates beyond the known rows]
For any diagonal-divisor or boundary product not already covered
by the Gritsenko--Nikulin denominator theorems or by the Govindarajan
CHL/WKB denominator theorem, first construct the product certificate
$$
\mathscr P_j=(\phi_j,\Gamma_{j,\mathrm{prod}}^+,
\Gamma_{j,\mathrm{mod}},\rho_j,\nu_j,L_j,\alpha_j)
$$
with
$$\phi^{(j)}(\tau,z)=\sum c_j(n,l)q^nr^l,$$
and then construct, if possible, the additional denominator data:
positive product cone, Weyl chamber, simple real roots, reflection
character, Weyl vector, Weyl alternating sum, imaginary simple-root
coefficients, and a generalized Borcherds--Kac--Moody superalgebra
\(\mathfrak g_j\) such that
$$F_j(Z)=C_j e^{2\pi i(\rho_j,Z)}
\prod_{\gamma\in\Gamma_{j,\mathrm{prod}}^+}(1-e^{2\pi i(\gamma,Z)})^{c_j(\gamma)},$$
$$\operatorname{den}(\mathfrak g_j)=C'_jF_j(a_jZ),\qquad
\sdim(\mathfrak g_{j,\gamma})=c_j(\gamma).$$
If a CHL/K3 sector supplies a dyon-counting scalar square, it fills only
the \(\mathscr S_j\) level of
Definition~\ref{def:physical-host-certificate}.  If a reduced CY/DT
scalar identity is claimed, one must separately construct \(X_j\), the
reduced obstruction theory, orientation, Fourier chamber, variables, and
the theorem
\[
Z^{X_j}_{\mathrm{red}}(Z)=C_jF_j(Z)^{-2}.
\]
If a compact Hall/chiral host is claimed, one must separately construct
the protected one-particle index and primitive bracket comparison.
\end{openproblem}

\begin{proposition}[CHL squares and denominator signs]
\label{prop:chl-square-root-separation}
The identities
$$
\nabla_3^2=\Phi_6^{(1,2)},\qquad \nabla_2^2=\Phi_4^{(1,3)}
$$
which occur in the CHL dyon literature do not by themselves give
denominator identities for the square-root rows $F_5=\nabla_3$ and
$F_6=\nabla_2$.  They give scalar Siegel modular forms on the CHL side.
To descend from a scalar square to a denominator theorem for a root
form, one must also construct the reflection character, the parity, and
the Weyl anti-invariant additive side.  Govindarajan's twisted CHL
theorem supplies exactly this missing structure for
$$F_5=\nabla_3,\qquad F_6=\nabla_2,\qquad
F_7=\nabla_{3/2},\qquad F_8=Q_1,$$
as recorded in Theorem~\ref{thm:govindarajan-denominator-rows}.
\end{proposition}

\begin{proof}
Clery--Gritsenko record the dd-forms $\nabla_3$ and $\nabla_2$ and note
that their squares were constructed in the CHL papers as
\(\Phi_6^{(1,2)}\) and \(\Phi_4^{(1,3)}\).  The square forgets the sign character which a denominator
identity needs on simple real reflections.  Thus the scalar CHL product
is evidence for the automorphic product, not by itself a proof of the
BKM datum $(P_j,\mathcal M_j,W_j,\epsilon_j,\rho_j,N_j(a))$ for the
root form.  The additional datum is supplied by
\cite{Gov11BKM}, building on \cite{GK09CHL} and \cite{CD09BKM}.
\end{proof}

A separate comparison tuple has weights
$$
(5,2,1,1,\tfrac12,1,\tfrac14,0).
$$
It is not the Clery--Gritsenko table.  A comparison with the
Clery--Gritsenko forms requires the relevant entries of
Definition~\ref{def:physical-host-certificate}.
Thus
$$\mathrm{Clery\mbox{--}Gritsenko\ classification}\neq
\mathrm{CHL\ realisation\ theorem}.$$
$$F_1:\ \mathrm{theorem},\qquad
F_2,F_3,F_4:\ \mathrm{GN\ denominator\ theorem},$$
$$F_5,F_6,F_7,F_8:
\ \mathrm{Govindarajan\ CHL/WKB\ denominator\ theorem},$$
with $F_7$ understood on the $\mu_4$-multiplier cover determined by its
order-four multiplier.  Dijkgraaf--Verlinde--Verlinde and Borcherds
give the \(N=1\) physical and automorphic background
\cite{DVV,B}; they do not construct physical-host certificates for the
other seven rows.

\appendix
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\theHsection}{appendix.\Alph{section}}

\section{\texorpdfstring{Spin \(L\)-factor normalisation for \(\Delta_5^2\)}
{Spin L-factor normalisation for Delta5 squared}}
\label{app:sk-shadow}

Set the theta-constant normalisation
$$\Delta_{10}^{\theta}:=\Delta_5^2.$$
The Oberdieck--Pixton monic normalisation is
$$\chi_{10}^{\mathrm{OP}}:=2^{-12}\Delta_{10}^{\theta}
=4096^{-1}\Delta_5^2.$$
The spinor $L$-function is attached to the Hecke eigenline
$$\C\Delta_{10}^{\theta}=\C\chi_{10}^{\mathrm{OP}};$$
it is independent of the non-zero scalar used to name its generator.
Put
$$\Delta(q)=q\prod_{n\geq1}(1-q^n)^{24},\qquad
E_6(q)=1-504\sum_{n\geq1}\sigma_5(n)q^n,$$
$$g:=\Delta E_6=\sum_{n\geq1}a_n(g)q^n\in S_{18}(\SL_2(\Z)).$$

\begin{theorem}[Andrianov factorisation]
\label{thm:andrianov-factor}
For the Saito--Kurokawa representation generated by
$\Delta_{10}^{\theta}$,
$$L_{\mathrm{spin}}(s,\Delta_{10}^{\theta})
=\zeta(s-8)\zeta(s-9)L(s,g).$$
Here \(L_{\mathrm{spin}}\) is Andrianov's uncompleted classical spinor
\(L\)-function.  For a genus-two form of weight \(10\), the completed
function is
$$
L_{\mathrm{spin}}^*(s,F)
=(2\pi)^{-2s}\Gamma(s)\Gamma(s-8)L_{\mathrm{spin}}(s,F).
$$
\end{theorem}

\begin{proof}
The Igusa cusp form \(\Delta_{10}^{\theta}\) spans the weight-\(10\)
Maass Spezialschar line attached by the Saito--Kurokawa correspondence
to the unique normalized form \(g=\Delta E_6\in S_{18}(\SL_2(\Z))\)
\cite{ZagierSK}.
This is Andrianov's spinor $L$-factor formula for the degree-$2$
Saito--Kurokawa lift attached to the weight-$18$ elliptic cusp form
$g$ \cite{Andr74}.  Since $\dim S_{18}(\SL_2(\Z))=1$, the source form
is $\Delta E_6$.
\end{proof}

\begin{proposition}[Central-zero cancellation]
\label{prop:sk-central-zero}
With
$$\Lambda(g,s):=(2\pi)^{-s}\Gamma(s)L(s,g),$$
one has
$$\Lambda(g,s)=-\Lambda(g,18-s),\qquad L(9,g)=0.$$
Hence the possible pole of $\zeta(s-8)L(s,g)$ at $s=9$ is cancelled.
At $s=10$ the residue is
$$\operatorname*{Res}_{s=10}L_{\mathrm{spin}}(s,\Delta_{10}^{\theta})
=\zeta(2)L(10,g)=\frac{\pi^2}{6}L(10,g),$$
with \(L(10,g)\ne0\), so
\(L_{\mathrm{spin}}(s,\Delta_{10}^{\theta})\) has a simple pole at
\(s=10\) with non-zero residue.
\end{proposition}

\begin{proof}
For a level-one cusp form of weight $18$, the root number is
$(-1)^{18/2}=-1$.  Thus the completed $L$-function is odd about
$s=9$, and the central value vanishes.  The factor $\zeta(s-8)$ has
its only possible pole at $s=9$, so the product
$\zeta(s-8)L(s,g)$ is regular there.  At $s=10$ the factor
$\zeta(s-9)$ has residue $1$, while $\zeta(s-8)=\zeta(2)$.
Write
$$L_p(s,g)=(1-\alpha_pp^{-s})^{-1}(1-\beta_pp^{-s})^{-1}.$$
Deligne's Ramanujan--Petersson theorem gives
$$|\alpha_p|=|\beta_p|=p^{17/2}.$$
At \(s=10\),
$$|\alpha_pp^{-10}|=|\beta_pp^{-10}|=p^{-3/2},$$
so the Euler product converges absolutely and has no zero.
\end{proof}

\begin{proposition}[Manin--Deligne period]
\label{prop:manin-deligne-period}
There are Manin periods $\Omega^\pm(g)$ such that
$$\varepsilon(m)=
\begin{cases}
+,&m\equiv0\pmod 2,\\
-,&m\equiv1\pmod 2,
\end{cases}
\qquad
\frac{L(m,g)}{(2\pi i)^m\Omega^{\varepsilon(m)}(g)}\in\Q,
\qquad 1\leq m\leq17.$$
In particular
$$L(10,g)\in \Q^\times(2\pi i)^{10}\Omega^+(g).$$
\end{proposition}

\begin{proof}
This is the Eichler--Shimura--Manin period theorem for the rational
newform $g$ \cite{Manin72}, \cite{KZ}, in Deligne's period normalisation
\cite{Del79}.  The nonvanishing at \(m=10\) is supplied by the Euler
product in Proposition~\ref{prop:sk-central-zero}.  No identity of the form
$$L(10,g)=q\,a_{10}(g)\Omega^-(g),\qquad q\in\Q^\times,$$
is used.
\end{proof}

\begin{proposition}[Coefficient check]
\label{prop:a10-explicit}
$$a_{10}(g)=541648800
=2^5\cdot3^2\cdot5^2\cdot7\cdot11\cdot977.$$
\end{proposition}

\begin{proof}
$$a_{10}(g)=\tau(10)-504\sum_{k=1}^{9}\tau(k)\sigma_5(10-k).$$
$$
(\tau(1),\ldots,\tau(10))
=(1,-24,252,-1472,4830,-6048,-16744,84480,-113643,-115920),
$$
$$
(\sigma_5(1),\ldots,\sigma_5(9))
=(1,33,244,1057,3126,8052,16808,33825,59293).
$$
Substitution gives $a_{10}(g)=541648800$.
Equivalently, since $g$ is a Hecke eigenform,
$$a_{10}(g)=a_2(g)a_5(g)=(-528)(-1025850)=541648800.$$
\end{proof}

\begin{remark}[Scalar-square separations]
The spinor \(L\)-factor calculation is independent of the
Dirac--Igusa construction.  The OP normalization is
\(\chi_{10}^{\mathrm{OP}}=2^{-12}\Delta_5^2\).  The Hecke eigenline, not
the scalar normalization of its generator, determines \(L_{\mathrm{spin}}\).
The pole of \(\zeta(s-8)\) at \(s=9\) is cancelled by \(L(9,g)=0\), while
the pole at \(s=10\) has residue \(\zeta(2)L(10,g)\) with
\(L(10,g)\in \mathbb Q^\times(2\pi i)^{10}\Omega^+(g)\).  None of these
facts is a BKM denominator proof or a compact Hall/Pfaffian construction.
\end{remark}


\section{Eight diagonal-divisor boundary rows}
\label{app:eight-row-boundary}

Let $F_j$ denote the diagonal-divisor forms in the present \(F\)-order.
The Clery--Gritsenko source order is
$$
\Delta_5,\Delta_2,\nabla_3,\Delta_1,\nabla_2,\Delta_{1/2},
\nabla_{3/2},Q_1.
$$
The present order is \cite{GC}
$$
\begin{array}{c|c|c|c|c}
j&F_j&(t,N)&\Gamma_j&\mathrm{wt}\\ \hline
1&\Delta_5&(1,1)&\Gamma_1&5\\
2&\Delta_2&(2,1)&\Gamma_2&2\\
3&\Delta_1&(3,1)&\Gamma_3&1\\
4&\Delta_{1/2}&(4,1)&\Gamma_4&\frac12\\
5&\nabla_3&(1,2)&\Gamma_0^{(2)}(2)&3\\
6&\nabla_2&(1,3)&\Gamma_0^{(2)}(3)&2\\
7&\nabla_{3/2}&(1,4)&\Gamma_0^{(2)}(4)&\frac32\\
8&Q_1&(2,2)&\Gamma_2(2)&1
\end{array}
$$
The plus-groups \(\Gamma_t^+\) used below for \(t=2,3,4\) are the
Fricke/Gritsenko--Nikulin denominator normalizations; they are not the
source-group labels in the Clery--Gritsenko table.
$$
\operatorname{supp}\operatorname{div}_{\mathbb H_2}(F_j)=
\bigcup_{\gamma\in\Gamma_j}\gamma\langle\mathcal H_{\mathrm{diag}}\rangle,
\qquad
\operatorname{mult}_{\mathcal H_{\mathrm{diag}}}(F_j)=1.
$$
Here $F_7=\nabla_{3/2}$ is the Clery--Gritsenko row at
$(t,N)=(1,4)$.  It is not a physical comparison slot until a separate
row map has been constructed.

The characters and multiplier systems are
$$
\begin{array}{c|c}
j&\nu_j\\ \hline
1&v_\eta^{12}\times v_H\\
2&v_\eta^{6}\times v_H\\
3&v_\eta^{4}\times v_H\\
4&v_\eta^{3}\times v_H\quad(\mathrm{degree}\ 8)\\
5&\chi_2^{(2)}\times v_H\\
6&\chi_2^{(3)}\times v_H\\
7&\chi_4^{(4)}\times v_H\quad(\mathrm{order}\ 4)\\
8&\chi_4^{(2)}\times v_H
\end{array}
$$

\begin{definition}[Candidate denominator proof datum]
For a row $j$, a candidate denominator proof datum consists of
$$
\mathscr P_j=(\phi_j,\Gamma_{j,\mathrm{prod}}^+,
\Gamma_{j,\mathrm{mod}},\rho_j,\nu_j,L_j,\alpha_j),
$$
where
$$\phi_j(\tau,z)=\sum c_j(n,l)q^nr^l,$$
$$F_j(Z)=C_j e^{2\pi i(\rho_j,Z)}
\prod_{\gamma\in\Gamma_{j,\mathrm{prod}}^+}
(1-e^{2\pi i(\gamma,Z)})^{c_j(\gamma)},$$
$$\nu_j:\Gamma_{j,\mathrm{mod}}\rightarrow\C^\times,\qquad
\operatorname{supp}\operatorname{div}(F_j)=
\Gamma_{j,\mathrm{mod}}\cdot\mathcal H_{\mathrm{diag}},
\qquad \operatorname{mult}_{\mathcal H_{\mathrm{diag}}}(F_j)=1,$$
and a degree map
$$\alpha_j:\Gamma_{j,\mathrm{prod}}^+\rightarrow L_j.$$
Only after a Weyl--Kac--Borcherds denominator theorem has been supplied
does this datum include a Lie superalgebra \(\mathfrak g_j\) with
$$
\sdim(\mathfrak g_{j,\alpha_j(\gamma)})=c_j(\gamma)
$$
on the corresponding product side.
For a product with several cusps this single-source notation is only a
template.  The congruence-row product datum is the cusp-labelled datum
of Proposition~\ref{prop:congruence-product-degree-lattices}.
\end{definition}

\begin{definition}[Gritsenko--Nikulin degree lattice]
For $t\in\Z_{>0}$ set
$$
M_t:=U(4t)\oplus\langle 2\rangle
=\Z f_2\oplus\Z\widehat f_3\oplus\Z f_{-2},
$$
with Gram matrix
$$
\left(\begin{array}{ccc}
0&0&-4t\\
0&2&0\\
-4t&0&0
\end{array}\right).
$$
For $(n,l,m)\in\Z^3$ put
$$
\alpha_t(n,l,m):=nf_2+l\widehat f_3+mf_{-2}\in M_t,\qquad
e_t^{(n,l,m)}:=q^nr^ls^{tm}.
$$
Then
$$
(\alpha_t(n,l,m),\alpha_t(n,l,m))
=-2(4tnm-l^2).
$$
Let $\Gamma_t^{\mathrm{prod}}$ be the Gritsenko--Nikulin product cone:
$(n,l,m)>0$ if $m>0$, or if $m=0,n>0$, or if $m=n=0,l<0$.
\end{definition}

\begin{lemma}[Two exponential normalizations]
\label{lem:two-denominator-normalizations}
Let
$$D_5(Z):=64^{-1}\Delta_5(Z).$$
Gritsenko--Nikulin's Siegel normalization gives
$$
D_5(Z)=q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)>0}
(1-q^nr^ls^m)^{f(nm,l)}
$$
with leading monomial $q^{1/2}r^{1/2}s^{1/2}$.
The denominator normalization used for the main BKM algebra is
$$
q^nr^ls^m=\exp(-\pi i(\alpha(n,l,m),z)).
$$
Thus replacing $Z$ by $2Z$ converts the product character to the usual
$\exp(-2\pi i(\alpha,z))$ denominator character, and
$$
\operatorname{den}(\mathfrak g_{\Delta_5})=D_5(2Z)
=64^{-1}\Delta_5(2Z).
$$
For rows $F_2,F_3,F_4$, Appendix~\ref{app:eight-row-boundary} uses the
Gritsenko--Nikulin exponential
$$e_t^{(n,l,m)}=q^nr^ls^{tm}$$
directly.  Hence
$$C'_j=1,\qquad a_j=1\qquad(j=2,3,4)$$
is a statement in the $e_t$ normalization.  It is not the doubled
$N=1$ normalization of the main $\Delta_5$ denominator.
\end{lemma}

\begin{proof}
The first product is the singular-theta lift of Borcherds
\cite{Borcherds95} together with the explicit paramodular product
identity of Gritsenko--Nikulin
\cite[Theorem~2.1, Example~2.4, (2.16)]{GNII}; the Lorentzian Kac--Moody
correction and the identification of $D_5(2Z)$ with the denominator
function of the corrected Lorentzian BKM superalgebra is the content
of \cite[Proposition~3.1]{GN}, in particular the corrected denominator identity for
\(\mathfrak g_{\Delta_5}\).  The rows
$F_2,F_3,F_4$ are the separate $e_t^{(n,l,m)}=q^nr^ls^{tm}$
denominator identities of Gritsenko--Nikulin
\cite[Theorem 2.1, (2.3), (2.11), Lemma 2.5, (2.18), (2.19),
Theorem 2.6, (2.20), (2.21), Section 5.1.1]{GNII}.
\end{proof}

\begin{proposition}[Full-paramodular rows]
\label{prop:gn-paramodular-row-data}
Let
$$
\phi_{0,2}=\sum f_2(n,l)q^nr^l,\qquad
\phi_{0,3}=\sum f_3(n,l)q^nr^l,\qquad
\phi_{0,4}=\sum f_4(n,l)q^nr^l,
$$
where \cite{GNII}
$$
\phi_{0,2}=\frac{1}{2}\eta^{-4}
\sum_{m,n\in\Z}(3m-n)\left({\frac{-4}{m}}\right)
\left({\frac{12}{n}}\right)q^{(3m^2+n^2)/24}r^{(m+n)/2},
$$
$$
\phi_{0,3}=\left(\frac{\vartheta(\tau,2z)}{\vartheta(\tau,z)}
\right)^2,\qquad
\phi_{0,4}=\frac{\vartheta(\tau,3z)}{\vartheta(\tau,z)}.
$$
Then the rows $F_2,F_3,F_4$ have the following product data:
$$
\begin{array}{c|c|c|c|c}
j&F_j&\phi_j&L_j&\rho_j\\ \hline
2&\Delta_2&\phi_{0,2}&M_2&(\frac14,\frac12,\frac14)\\
3&\Delta_1&\phi_{0,3}&M_3&(\frac16,\frac12,\frac16)\\
4&\Delta_{1/2}&\phi_{0,4}&M_4&(\frac18,\frac12,\frac18)
\end{array}
$$
and
$$
\alpha_j^{\mathrm{GN}}(n,l,m):=\alpha_t(n,l,m)\quad
\hbox{for }(j,t)=(2,2),(3,3),(4,4).
$$
The product identities are
$$
\begin{aligned}
\Delta_2(Z)&=q^{1/4}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_2^{\mathrm{prod}}}
(1-q^nr^ls^{2m})^{f_2(nm,l)},
\end{aligned}
$$
$$
\begin{aligned}
\Delta_1(Z)&=q^{1/6}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_3^{\mathrm{prod}}}
(1-q^nr^ls^{3m})^{f_3(nm,l)},
\end{aligned}
$$
$$
\begin{aligned}
\Delta_{1/2}(Z)&=q^{1/8}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_4^{\mathrm{prod}}}
(1-q^nr^ls^{4m})^{f_4(nm,l)}.
\end{aligned}
$$
The characters are respectively induced by
$v_\eta^6\times v_H$, $v_\eta^4\times v_H$, and
$v_\eta^3\times v_H$.
Equivalently, on the extended paramodular groups,
$$
\nu_2=\chi_4:\Gamma_2^+\rightarrow\mu_4,\qquad
\nu_3=\chi_6:\Gamma_3^+\rightarrow\mu_6,\qquad
\nu_4=v_8:\Gamma_4^+\rightarrow\mu_8.
$$
Thus for \((j,t)=(2,2),(3,3),(4,4)\),
$$
\Gamma_{j,\mathrm{prod}}^+=\Gamma_t^{\mathrm{prod}},\qquad
\Gamma_{j,\mathrm{mod}}=\Gamma_t^+.
$$
\end{proposition}

\begin{proof}
The product formulae are Gritsenko--Nikulin
\cite[Theorem~2.1, (2.21) for \(\Delta_2\), (2.20) for \(\Delta_1\),
and (2.11) for \(\Delta_{1/2}\)]{GNII}.  Their Section 5
puts all formulae of Lie type on the hyperbolic lattice $M_t$ and writes
the exponent as $e^{(n,l,m)}=q^nr^ls^{tm}$.  The Weyl vector is
$$\rho_{t,II,\overline0}
=\left(\frac{1}{2t},\frac{1}{2},\frac{1}{2t}\right),$$
which gives the three displayed prefactors for $t=2,3,4$.
\end{proof}

\begin{proposition}[Gritsenko--Nikulin chambers for $F_2,F_3,F_4$]
\label{prop:gn-chambers-234}
For $t=2,3,4$ the Weyl group is
$$W_{t,II,\overline0}=W^{(2)}(M_t),$$
and all simple real roots in this chamber are even.  The Weyl
vector is
$$\rho_t=\left(\frac{1}{2t},\frac12,\frac{1}{2t}\right).$$
The simple real roots are
$$
P_2=\{(0,-1,0),\ (1,1,0),\ (1,3,1),\ (0,1,1)\},
$$
$$
\begin{aligned}
P_3=\{&(0,-1,0),\ (1,1,0),\ (2,5,1),\\
&(2,7,2),\ (1,5,2),\ (0,1,1)\},
\end{aligned}
$$
and
$$
P_4=\{\delta\in M_4\mid(\delta,\delta)=2,\ (\delta,\rho_4)=-1\}.
$$
Thus the automorphic denominator chamber for $F_j$ is the chamber in
$M_t\otimes\R$ cut out by $(x,\delta)\leq0$ for
$\delta\in P_t$, where $(j,t)=(2,2),(3,3),(4,4)$.
\end{proposition}

\begin{proof}
This is Gritsenko--Nikulin \cite{GNII}, Section 5.1.1, cases
$(t,II,\overline0)$.  The displayed sets are exactly
$P_{t,II,\overline0}(\mathcal M_{t,II,\overline0})$ for
$t=2,3,4$.
\end{proof}

\begin{lemma}[Product cone and chamber compatibility]
\label{lem:gn-product-chamber-compatibility}
Let \(t=2,3,4\).  If
$$f_t(nm,l)\ne0,\qquad (n,l,m)\in\Gamma_t^{\mathrm{prod}},$$
then
$$
(\alpha_t(n,l,m),\rho_t)\le0.
$$
For \(t=2,3\) the inequality is strict.  For \(t=4\), equality occurs
only on the parabolic ray
$$\alpha_t(n,l,m)\in\Q_{>0}\rho_4.$$
\end{lemma}

\begin{proof}
The Jacobi support satisfies
$$4tnm-l^2\ge -1.$$
Since
$$
(\alpha_t(n,l,m),\rho_t)=-2n+l-2m,
$$
the chamber inequality is \(l\le2n+2m\).  For \(t=2,3\), Gritsenko--
Nikulin Lemma 2.5 gives the required strict chamber condition on the
active support.  For \(t=4\), the proof of Gritsenko--Nikulin (1.33)
gives the same condition, with equality only in the parabolic case.
Equivalently, equality and \(4tnm-l^2\ge -1\) force
$$n=m,\qquad l=4n,$$
so
$$\alpha_4(n,4n,n)=8n\rho_4.$$
\end{proof}

\begin{theorem}[Gritsenko--Nikulin denominator rows]
\label{thm:gn-denominator-234}
Let $t=2,3,4$ and put
$$
\begin{array}{c|c|c}
t&F(t)&\phi_t\\ \hline
2&\Delta_2&\phi_{0,2}\\
3&\Delta_1&\phi_{0,3}\\
4&\Delta_{1/2}&\phi_{0,4}
\end{array}
$$
Let
$$
\mathfrak g_t^{\mathrm{GN}}
\quad (t=2,3,4)
$$
be the generalized Borcherds--Kac--Moody superalgebra whose Lorentzian
root lattice is $M_t$, whose Weyl group is
$W_t=W^{(2)}(M_t)$, whose Weyl vector is
$$
\rho_t=\left(\frac{1}{2t},\frac12,\frac{1}{2t}\right),
$$
and whose simple real roots are $P_t=P_{t,II,\overline0}$ from
Proposition~\ref{prop:gn-chambers-234}.  Let $\mathcal M_t$ denote
the corresponding chamber.  Then
$$
P_{t,\overline1}=\varnothing,\qquad P_{t,\overline0}=P_t,
$$
so every simple real root is even and
$\epsilon_t(s_\delta)=-1$ for every $\delta\in P_t$; equivalently
$\epsilon_t(w)=\det(w)$ on $W_t$.

Let
$$
\phi_t(\tau,z)=\sum f_t(n,l)q^nr^l .
$$
The integers \(N_t(a)\) are the additive-side coefficients in
Gritsenko--Nikulin (5.1), equivalently the signed supermultiplicities of
imaginary simple roots.  They are not the product exponents \(f_t(nm,l)\).
In the Gritsenko--Nikulin exponential normalization
$e_t^{(n,l,m)}=q^nr^ls^{tm}$, the Weyl--Kac--Borcherds denominator
identity is
$$
\begin{aligned}
\operatorname{den}(\mathfrak g_t^{\mathrm{GN}})
&=\sum_{w\in W_t}\epsilon_t(w)
 \left(e_t^{w(\rho_t)}
 +\sum_{a\in\R_{++}\mathcal M_t\cap M_t}
 N_t(a)e_t^{w(\rho_t+a)}\right)\\
&=e_t^{\rho_t}
\prod_{(n,l,m)\in\Gamma_t^{\mathrm{prod}}}
\left(1-e_t^{(n,l,m)}\right)^{f_t(nm,l)}
=F(t)(Z).
\end{aligned}
$$
Equivalently,
$$
\operatorname{den}(\mathfrak g_2^{\mathrm{GN}})=\Delta_2(Z),\qquad
\operatorname{den}(\mathfrak g_3^{\mathrm{GN}})=\Delta_1(Z),\qquad
\operatorname{den}(\mathfrak g_4^{\mathrm{GN}})=\Delta_{1/2}(Z).
$$
Thus, for rows $j=2,3,4$,
$$
C'_j=1,\qquad a_j=1,\qquad
L_j=M_j,\qquad \alpha_j=\alpha_j^{\mathrm{GN}}
$$
in this normalization.  The imaginary root spaces are determined here
only as signed multiplicity spaces:
$$
\sdim(\mathfrak g_{t,\alpha_t(n,l,m)})
=f_t(nm,l)
$$
on the product side, with imaginary simple-root superdimensions
$N_t(a)$ on the Weyl-sum side.
\end{theorem}

\begin{proof}
Gritsenko--Nikulin \cite[Section 5.1]{GNII} state that almost all
identities proved earlier in their paper give denominator formulae for
Lorentzian Kac--Moody algebras.  Their formula (5.1) is exactly the
displayed Weyl--Kac--Borcherds identity on
$M_t=U(4t)\oplus\langle2\rangle$, with
$e^{(n,l,m)}=q^nr^ls^{tm}$.

For the cases $(t,II,\overline0)$, $t=2,3,4$, they give
$$
W_{t,II,\overline0}=W^{(2)}(M_t),\qquad
\rho_{t,II,\overline0}
=\left(\frac{1}{2t},\frac12,\frac{1}{2t}\right),
$$
and
$$
P_{t,II,\overline0}(\mathcal M_{t,II,\overline0})
=P_{t,II,\overline0}(\mathcal M_{t,II,\overline0})_{\overline0}.
$$
Hence the odd simple-real-root set is empty and the Weyl character is
the ordinary reflection sign on the simple real reflections.  The roots
in $P_t$ have square $2$, and the generalized Cartan matrix is
$((\delta,\delta'))_{\delta,\delta'\in P_t}$; for $t=4$ this is the
infinite symmetric parabolic matrix recorded by Gritsenko--Nikulin.
For real roots \(4tn-l^2=-1\), the relevant Jacobi coefficient is \(1\):
this is Gritsenko--Nikulin Lemma 2.5 for \(t=2,3\) and the proof of
Gritsenko--Nikulin (1.33) for \(t=4\).

The product factors are the full-paramodular products
\cite[(2.21), (2.20), (2.11)]{GNII}, already displayed in
Proposition~\ref{prop:gn-paramodular-row-data}.  Their prefactors are
exactly $e_t^{\rho_t}$.  Therefore the denominator functions are
$\Delta_2$, $\Delta_1$, and $\Delta_{1/2}$ with no further scalar or
argument rescaling in the $e_t$ normalization.
\end{proof}

\begin{proposition}[Congruence products]
\label{prop:gc-row-data}
For $j=5,6,7,8$ Clery--Gritsenko construct the following Borcherds
products \cite{GC}.  The weak Jacobi inputs are
$$
\begin{array}{c|c|c}
j&\phi_j&\rho_j^{\mathrm{pref}}\\ \hline
5&4(\xi_{1,0}^{(2)})^2\in J^w_{0,1}(\Gamma_0(2))
&(\frac12,\frac12,\frac12)\\
6&3\xi_{3,1}^{(6)}\xi_{3,5}^{(6)}
\in J^w_{0,1}(\Gamma_0(3))
&(\frac12,\frac12,\frac12)\\
7&2\xi_{2,1}^{(4)}\xi_{2,3}^{(4)}
\in J^w_{0,1}(\Gamma_0(4))
&(\frac12,\frac12,\frac12)\\
8&2\xi_{1,0}^{(2)}(\tau,2z)\in J^w_{0,2}(\Gamma_0(2))
&(\frac14,\frac12,\frac12)
\end{array}
$$
where $\rho_j^{\mathrm{pref}}$ is read from the literal product
prefactor $q^{\rho_{\tau}}r^{\rho_z}s^{\rho_{\omega}}$.  At this
stage it is a prefactor exponent, not a proved Weyl vector.  In
particular, for $F_8$ the $M_2$ product coordinate corresponding to
$s^{1/2}$ is $(1/4,1/2,1/4)$ because
$e^{\alpha_2(a,b,c)}=q^ar^bs^{2c}$.
More precisely, if
$$S=\left(\begin{smallmatrix}0&-1\\1&0\end{smallmatrix}\right),$$
and
$$
\phi_5=\sum c_5(n,l)q^nr^l,\qquad
\phi_5|_{0,1}S=\sum c_{5,S}(n,l)q^nr^l,
$$
then
$$
\begin{aligned}
F_5(Z)&=\nabla_3(Z)\\
&=q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_1^{\mathrm{prod}}}
(1-q^nr^ls^m)^{c_5(nm,l)}
(1-q^{2n}r^{2l}s^{2m})^{c_{5,S}(nm,l)}.
\end{aligned}
$$
If
$$
\phi_6=\sum c_6(n,l)q^nr^l,\qquad
\phi_6|_{0,1}S=\sum c_{6,S}(n,l)q^nr^l,
$$
then
$$
\begin{aligned}
F_6(Z)&=\nabla_2(Z)\\
&=q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_1^{\mathrm{prod}}}
(1-q^nr^ls^m)^{c_6(nm,l)}
(1-q^{3n}r^{3l}s^{3m})^{c_{6,S}(nm,l)}.
\end{aligned}
$$
If
$$
\phi_7=\sum c_7(n,l)q^nr^l,\qquad
\phi_7|_{0,1}S=\sum c_{7,S}(n,l)q^nr^l,\qquad
\phi_7|_{0,1}M=\sum c_{7,M}(n,l)q^nr^l,
$$
where $M=\left(\begin{smallmatrix}1&-1\\2&-1\end{smallmatrix}\right)$, then
$$
\begin{aligned}
F_7(Z)&=\nabla_{3/2}(Z)\\
&=q^{1/2}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_1^{\mathrm{prod}}}
(1-q^nr^ls^m)^{c_7(nm,l)}\\
&\qquad\qquad\cdot
(1-q^{2n}r^{2l}s^{2m})^{c_{7,M}(nm,l)/2}
(1-q^{4n}r^{4l}s^{4m})^{c_{7,S}(nm,l)}.
\end{aligned}
$$
The exponent \(c_{7,M}/2\) is the literal middle-cusp exponent in the
\(\mu_4\)-cover normalization; it is not a scalar-character exponent on
the original congruence group.
If
$$
\phi_8=\sum c_8(n,l)q^nr^l,\qquad
\phi_8|_{0,2}S=\sum c_{8,S}(n,l)q^nr^l,
$$
then
$$
\begin{aligned}
F_8(Z)&=Q_1(Z)\\
&=q^{1/4}r^{1/2}s^{1/2}
\prod_{(n,l,m)\in\Gamma_2^{\mathrm{prod}}}
(1-q^nr^ls^{2m})^{c_8(nm,l)}
(1-q^{2n}r^{2l}s^{4m})^{c_{8,S}(nm,l)}.
\end{aligned}
$$
These four displays pin the automorphic products.  By themselves they
do not construct a BKM chamber, parity function, or Weyl-sum identity.
\end{proposition}

\begin{proof}
The formulae are Clery--Gritsenko \cite[Theorem 3.1]{GC} and the four
product displays for $\nabla_3,\nabla_2,\nabla_{3/2}$, and $Q_1$ at
the end of Section 3.  The second factors in $F_5,F_6,F_8$ and the
second and third factors in $F_7$ come from the non-infinity cusps of
$\Gamma_0(N)$ in their congruence Borcherds product theorem.
\end{proof}

\begin{proposition}[Product degree lattices for $F_5,F_6,F_7,F_8$]
\label{prop:congruence-product-degree-lattices}
For the product rows $j=5,6,7,8$ set
$$
(t_5,N_5)=(1,2),\qquad (t_6,N_6)=(1,3),\qquad
(t_7,N_7)=(1,4),\qquad (t_8,N_8)=(2,2).
$$
The Clery--Gritsenko modular host is the orthogonal lattice
$$
\mathcal O_j=U\oplus U(N_j)\oplus\langle-2t_j\rangle
$$
of signature $(2,3)$.  The single product-degree lattice for the
monomial denominator is
$$
L_j^{\mathrm{prod}}:=M_{t_j}.
$$
Define the cusp-labelled degree maps by
$$
\alpha_5^{\mathrm{prod}}(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_5^{\mathrm{prod}}(n,l,m;S)=\alpha_1(2n,2l,2m),
$$
$$
\alpha_6^{\mathrm{prod}}(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_6^{\mathrm{prod}}(n,l,m;S)=\alpha_1(3n,3l,3m),
$$
$$
\alpha_7^{\mathrm{prod}}(n,l,m;\infty)=\alpha_1(n,l,m),\qquad
\alpha_7^{\mathrm{prod}}(n,l,m;M)=\alpha_1(2n,2l,2m),
$$
$$
\alpha_7^{\mathrm{prod}}(n,l,m;S)=\alpha_1(4n,4l,4m),
$$
and
$$
\alpha_8^{\mathrm{prod}}(n,l,m;\infty)=\alpha_2(n,l,m),\qquad
\alpha_8^{\mathrm{prod}}(n,l,m;S)=\alpha_2(2n,2l,2m).
$$
The corresponding product-prefactor degrees are
$$
\rho_5^{\mathrm{prod}}=\rho_6^{\mathrm{prod}}=\rho_7^{\mathrm{prod}}
=\alpha_1(\tfrac12,\tfrac12,\tfrac12),\qquad
\rho_8^{\mathrm{prod}}=\alpha_2(\tfrac14,\tfrac12,\tfrac14).
$$
For $\lambda\in L_j^{\mathrm{prod}}$ let $\mu_j(\lambda)$ be the sum
of all cusp coefficients whose labelled degree is $\lambda$:
$$
\mu_j(\lambda)=
\sum_{\alpha_j^{\mathrm{prod}}(n,l,m;\kappa)=\lambda}
\widetilde c_{j,\kappa}(nm,l),
$$
where
$$
\widetilde c_{j,\infty}=c_j,\qquad
\widetilde c_{5,S}=c_{5,S},\qquad
\widetilde c_{6,S}=c_{6,S},
$$
$$
\widetilde c_{7,M}=\frac12c_{7,M},\qquad
\widetilde c_{7,S}=c_{7,S},\qquad
\widetilde c_{8,S}=c_{8,S}.
$$
For \(j=7\) this is a product datum on the \(\mu_4\)-multiplier cover;
the integrality of the displayed half-exponents is part of the
Clery--Gritsenko product theorem in that cover.  Until one proves that
integrality directly from the Jacobi seed, the row is used only with
this sourced cover datum.
The product is therefore used as an integral automorphic product only in
the sourced multiplier-cover normalization.
Let
$$
\mathcal K_5=\mathcal K_6=\mathcal K_8=\{\infty,S\},\qquad
\mathcal K_7=\{\infty,M,S\},
$$
and
$$
\mathcal D_j:=\Gamma_{t_j}^{\mathrm{prod}}\times\mathcal K_j.
$$
The cusp-labelled product datum is
$$
\mathscr E_j^{\mathrm{prod}}
:=(\mathcal D_j,\alpha_j^{\mathrm{prod}},\mu_j).
$$
Then
$$
F_j(Z)=e^{\rho_j^{\mathrm{prod}}}
\prod_{\lambda\in\alpha_j^{\mathrm{prod}}(\mathcal D_j)}
\left(1-e^\lambda\right)^{\mu_j(\lambda)}
\qquad(j=5,6,7,8),
$$
where $e^{\alpha_1(a,b,c)}=q^ar^bs^c$ and
$e^{\alpha_2(a,b,c)}=q^ar^bs^{2c}$.
\end{proposition}

\begin{proof}
The displayed maps are the unique monomial-degree maps forced by the
three products in Proposition~\ref{prop:gc-row-data}.  For $F_5$ the
non-infinity cusp contributes the monomials
$q^{2n}r^{2l}s^{2m}$, hence degree $\alpha_1(2n,2l,2m)$.  For $F_6$
the corresponding monomial is $q^{3n}r^{3l}s^{3m}$, hence degree
$\alpha_1(3n,3l,3m)$.  For $F_7$ the two non-infinity factors have
monomials $q^{2n}r^{2l}s^{2m}$ and $q^{4n}r^{4l}s^{4m}$; the first
has half exponent $c_{7,M}/2$ exactly as in the Clery--Gritsenko
product.  For $F_8$ the product has index $t=2$:
$e^{\alpha_2(n,l,m)}=q^nr^ls^{2m}$ and the non-infinity cusp contributes
$e^{\alpha_2(2n,2l,2m)}=q^{2n}r^{2l}s^{4m}$.  If two labelled cusp
contributions land on the same lattice degree, exponents add; this is
precisely the definition of $\mu_j$.

Clery--Gritsenko \cite[Theorem 3.1]{GC} realize these products as
orthogonal Borcherds products for
$U\oplus U(N_j)\oplus\langle-2t_j\rangle$.  That theorem supplies the
automorphic product and the divisor.  It does not supply a Weyl chamber,
simple real roots, a parity function, or a Weyl-sum identity on
$M_{t_j}$.  Thus \(L_j^{\mathrm{prod}}\) and
\(\alpha_j^{\mathrm{prod}}\) are product data, not a completed BKM
denominator datum.  The completed denominator datum for
\(F_5,F_6,F_7,F_8\) comes from the CHL theorem in
Theorem~\ref{thm:govindarajan-denominator-rows}.
\end{proof}

\begin{definition}[Formal product algebra of a row]
For a row $j$ with product-degree function $\mu_j$, let
$$
\mathcal V_j^{\mathrm{prod}}
=\bigoplus_{\lambda\in L_j^{\mathrm{prod}},\ \lambda>0}
\mathcal V_{j,\lambda}
$$
be any graded super vector space with finite-dimensional homogeneous
pieces and
$$
\sdim\mathcal V_{j,\lambda}=\mu_j(\lambda).
$$
Choose a Grothendieck representative: the even part has dimension $\mu_j(\lambda)$ when
$\mu_j(\lambda)>0$, the odd part of dimension $-\mu_j(\lambda)$ when
$\mu_j(\lambda)<0$, and the zero space when $\mu_j(\lambda)=0$.  Give
it the abelian Lie superalgebra bracket:
$$[\mathcal V_{j,\lambda},\mathcal V_{j,\lambda'}]=0.$$
Its formal current envelope on $E$ is
$$
\mathsf{Prod}_{j,E}
:=U_E^{\mathrm{ch}}
\left(\mathcal V_j^{\mathrm{prod}}\otimes\mathcal O_E\right).
$$
\end{definition}

\begin{proposition}[Eight formal current rows]
\label{prop:eight-formal-current-rows}
\label{thm:eight-formal-current-rows}
Every Clery--Gritsenko diagonal-divisor row has a formal determinant
object.  For $j=1$ this is
$\mathsf{Den}_{\Delta_5,E}$ from
Proposition~\ref{prop:formal-current-envelope}.  For $j=2,3,4$ it is the
current envelope of the Gritsenko--Nikulin BKM algebra
$\mathfrak g_j^{\mathrm{GN}}$.  For $j=5,6,7,8$ it is the formal
product algebra \(\mathsf{Prod}_{j,E}\).
For $j=5,6,7,8$, Theorem~\ref{thm:govindarajan-denominator-rows}
also supplies a nonabelian CHL/WKB denominator algebra; the abelian
product algebra in this theorem is the part constructed directly from
the Clery--Gritsenko product exponents.
For $j=5,6,7,8$ this is only the tautological virtual product object
realizing the Clery--Gritsenko exponents.  Its Beilinson--Drinfeld
envelope is abelian; it carries no Weyl-sum side, no BKM bracket, and no
physical protected BPS interpretation.

In all eight cases the formal determinant is the corresponding monic
automorphic product:
$$
e^{\rho_j}\sdet_{\mathcal V_j}(1-e)
=D_j(Z),
$$
where $D_1=64^{-1}\Delta_5$ and $D_j=F_j$ for the displayed
Clery--Gritsenko product normalizations $j>1$,
with the normalizations stated in
Propositions~\ref{prop:gn-paramodular-row-data},
\ref{prop:gc-row-data}, and
\ref{prop:congruence-product-degree-lattices}.
\end{proposition}

\begin{proof}
For $j=1$, Theorem~\ref{thm:denominator-algebra-identity} gives the
Borcherds denominator algebra and Proposition~\ref{prop:formal-current-envelope} gives
the formal current envelope.  For $j=2,3,4$,
Theorem~\ref{thm:gn-denominator-234} gives the BKM brackets and their
denominator identities.

For $j=5,6,7,8$, Proposition~\ref{prop:congruence-product-degree-lattices}
constructs the degree lattice, the positive product support, the
prefactor, and the signed exponent $\mu_j$.  The super vector space
$\mathcal V_j^{\mathrm{prod}}$ realizes these signed dimensions.  The
Fock determinant lemma gives
$$
e^{\rho_j^{\mathrm{prod}}}
\prod_\lambda(1-e^\lambda)^{\sdim\mathcal V_{j,\lambda}}
=
e^{\rho_j^{\mathrm{prod}}}
\prod_\lambda(1-e^\lambda)^{\mu_j(\lambda)}
=F_j(Z).
$$
The formal current enveloping construction gives a chiral algebra on
\(E\) from this abelian Lie superalgebra.  It is not a compact BPS
factorization algebra.
\end{proof}

\begin{proposition}[Nonabelian promotion test for $F_5,F_6,F_7,F_8$]
\label{prop:congruence-denominator-test}
Suppose that one of the congruence product rows
$$j\in\{5,6,7,8\}$$
is the denominator of a generalized Borcherds--Kac--Moody
superalgebra on the product lattice $L_j^{\mathrm{prod}}$.  Then the
following additional data must exist:
$$
\left(P_j,\mathcal M_j,W_j,\epsilon_j,\rho_j,N_j(a)\right).
$$
They must satisfy
$$
W_j=\langle s_\delta\mid\delta\in P_j\rangle,\qquad
\mathcal M_j=\{x\mid(x,\delta)\leq0\ \hbox{for all }\delta\in P_j\},
$$
$$
(\rho_j,\delta)=-\frac{(\delta,\delta)}{2}
\qquad(\delta\in P_j),
$$
and the Weyl--Kac--Borcherds identity
$$
\begin{aligned}
F_j(Z)
&=\sum_{w\in W_j}\epsilon_j(w)
\left(e^{w(\rho_j)}
+\sum_{a\in L_j^{\mathrm{prod}}\cap\R_{>0}\mathcal M_j}
N_j(a)e^{w(\rho_j+a)}\right)\\
&=e^{\rho_j^{\mathrm{prod}}}
\prod_{\lambda\in\alpha_j^{\mathrm{prod}}(\mathcal D_j)}
\left(1-e^\lambda\right)^{\mu_j(\lambda)}.
\end{aligned}
$$
In particular the product already fixes the signed root multiplicity
function $\mu_j$ and the product-prefactor degree
$$
\rho_5^{\mathrm{prod}}=\rho_6^{\mathrm{prod}}=\rho_7^{\mathrm{prod}}
=\alpha_1(\tfrac12,\tfrac12,\tfrac12),\qquad
\rho_8^{\mathrm{prod}}=\alpha_2(\tfrac14,\tfrac12,\tfrac14),
$$
but it does not fix $P_j$, $\mathcal M_j$, $W_j$, $\epsilon_j$, or the
imaginary simple-root coefficients $N_j(a)$.
\end{proposition}

\begin{proof}
The equalities in Proposition~\ref{prop:congruence-product-degree-lattices}
construct only the monomial degree and the total exponent
$\mu_j(\lambda)$.  A denominator theorem has a second side: the Weyl
alternating sum.  That side requires a reflection chamber, a set of
simple real roots, a reflection character, and the imaginary
simple-root contribution.

The Gritsenko--Nikulin chambers for $M_1$ and $M_2$ do not follow by
notation.  The forms $\nabla_3$, $\nabla_2$, $\nabla_{3/2}$, and
$Q_1$ are congruence products with non-infinity cusp factors, whereas
$\Delta_5$ and $\Delta_2$ are full-paramodular denominator forms.
Clery--Gritsenko construct the automorphic product, character, and
diagonal divisor on
$$U\oplus U(N_j)\oplus\langle-2t_j\rangle,$$
but their product theorem does not identify the simple real roots or
prove a Weyl anti-invariant additive expansion on $M_{t_j}$.  Therefore
the displayed six-tuple is an additional theorem to be proved, not a
consequence of the product formula.
\end{proof}

\begin{theorem}[Govindarajan CHL/WKB denominator rows]
\label{thm:govindarajan-denominator-rows}
In the CHL/twisted-dyon normalization of Cheng--Dabholkar and
Govindarajan, the rows
$$
F_5=\nabla_3,\qquad F_6=\nabla_2,\qquad
F_7=\nabla_{3/2},\qquad F_8=Q_1
$$
are Weyl--Kac--Borcherds denominator forms.  The row $F_7$ is taken on
the $\mu_4$-multiplier cover determined by the Clery--Gritsenko
order-four multiplier.  Thus \(F_7\) is a denominator on the
\(\mu_4\)-cover, with no physical row map, metaplectic boundary theorem,
or CY/DT/chiral host.  In the
product-degree notation of this appendix the real-root data are
$$
L_5=L_6=L_7=M_1,\qquad
P_5=P_6=P_7=P^{(1)},\qquad
\rho_5=\rho_6=\rho_7=\alpha_1(\tfrac12,\tfrac12,\tfrac12),
$$
where
$$
P^{(1)}=\{(0,-1,0),\ (1,1,0),\ (0,1,1)\},
$$
and
$$
L_8=M_2,\qquad
P_8=P^{(2)},\qquad
\rho_8=\alpha_2(\tfrac14,\tfrac12,\tfrac14),
$$
where
$$
P^{(2)}=\{(0,-1,0),\ (1,1,0),\ (1,3,1),\ (0,1,1)\}.
$$
The Weyl chambers and Weyl groups are
$$
\mathcal M_j=\{x\in L_j\otimes\R\mid (x,\delta)\le0
\hbox{ for every }\delta\in P_j\},
\qquad
W_j=\langle s_\delta\mid\delta\in P_j\rangle.
$$
Every simple real root is even and the reflection character is
$$\epsilon_j(w)=\det(w).$$
For $j=5,6,7,8$ the denominator product side is expressed through the
cusp-labelled product datum $\mathscr E_j^{\mathrm{prod}}$, with root
multiplicity function $\mu_j$.
In Govindarajan's CHL normalization the corresponding square-root form
is anti-invariant under the Weyl reflections, with character
\(\epsilon_j(w)=\det(w)\).  This anti-invariance is part of the
Govindarajan WKB denominator theorem, not a consequence of the
Clery--Gritsenko product alone; this manuscript does not construct an
independent row-by-row embedding of the CHL Weyl group into each
Clery--Gritsenko modular group or multiplier cover.
The Cartan matrices are, in the CHL/WKB BKM normalization of
\cite{CD09BKM,Gov11BKM},
$$
A^{(1)}=\left(\begin{array}{rrr}
2&-2&-2\\
-2&2&-2\\
-2&-2&2
\end{array}\right),
$$
for $F_5,F_6,F_7$, and
$$
A^{(2)}=\left(\begin{array}{rrrr}
2&-2&-6&-2\\
-2&2&-2&-6\\
-6&-2&2&-2\\
-2&-6&-2&2
\end{array}\right),
$$
for $F_8$.

Equivalently, for \(x=(u,v,w)\), the two chambers are
$$
\mathcal M_1=\{x\mid v\ge0,\ v\le2w,\ v\le2u\},
$$
and
$$
\mathcal M_2=\{x\mid v\ge0,\ v\le4w,\ 3v\le4(u+w),\ v\le4u\}.
$$

There are integral imaginary simple-root coefficients $N_j(a)$,
depending on the CHL twist
\cite{CD09BKM,Gov11BKM}, such that
$$
\begin{aligned}
F_j(Z)
&=\sum_{w\in W_j}\det(w)
\left(e^{w(\rho_j)}
+\sum_{a\in L_j\cap\R_{>0}\mathcal M_j}
N_j(a)e^{w(\rho_j+a)}\right)\\
&=e^{\rho_j}
\prod_{\lambda\in\alpha_j^{\mathrm{prod}}(\mathcal D_j)}
\left(1-e^\lambda\right)^{\mu_j(\lambda)}
\qquad(j=5,6,7,8).
\end{aligned}
$$
Thus the six-tuples
$$
(P_j,\mathcal M_j,W_j,\epsilon_j,\rho_j,N_j(a))
$$
are constructed for $j=5,6,7,8$ by the CHL denominator theorem.  They are
not consequences of the Clery--Gritsenko product formula alone.
In the monic Clery--Gritsenko/Govindarajan product variables of
Proposition~\ref{prop:gc-row-data}, the identities have
$$
C'_j=1,\qquad a_j=1\qquad(j=5,6,7,8).
$$
This is not the doubled $N=1$ normalization of
Lemma~\ref{lem:two-denominator-normalizations}.
\end{theorem}

\begin{remark}[$F_7$ on the \(\mu_4\)-multiplier cover]
\label{rem:f7-mu4-cover}
The row \(F_7=\nabla_{3/2}\) is the Clery--Gritsenko
diagonal-divisor form of type \((t,N)=(1,4)\), weight \(3/2\), on
\(\Gamma_0^{(2)}(4)\) with an order-four multiplier.  After pullback to
the associated \(\mu_4\)-multiplier cover, Govindarajan's CHL/WKB
theorem identifies it with the Weyl--Kac--Borcherds denominator of
\(\mathcal G_1(4)\).  It is the \(\mu_4\)-cover denominator identity,
with no physical comparison-row identification, no
metaplectic boundary host, and no CY/DT or chiral/Hall theorem.

The square identity \(F_7^2=\Phi_3\) in the composite \(N=4\)
normalization is only a scalar square identity.
It does not carry the reflection sign, parity, Weyl chamber, or
Weyl-alternating side.  The coefficient convention for the additive
side is fixed in Lemma~\ref{lem:nabla-three-halves-coefficients}.
\end{remark}

\begin{lemma}[Coefficient normalisation for $\nabla_3$ and $\nabla_2$]
\label{lem:nabla32-coefficients}
Let
$$
\psi_5(\tau,z)=\vartheta(\tau,z)\eta(\tau)\eta(2\tau)^4
=\sum g_5(u,v)q^{u/2}r^{v/2},
$$
and
$$
\psi_6(\tau,z)=\vartheta(\tau,z)\eta(3\tau)^3
=\sum g_6(u,v)q^{u/2}r^{v/2}.
$$
For $a=\alpha_1(A,B,C)\in M_1\cap\R_{\ge0}\mathcal M_1$, put
$$
n=2A+1,\qquad l=2B+1,\qquad m=2C+1.
$$
In the plus-sign convention of
Theorem~\ref{thm:govindarajan-denominator-rows}, the imaginary
simple-root coefficients for the rows $F_5$ and $F_6$ are
$$
N_5(a)=\sum_{d\mid(n,l,m)}
d^2\,g_5\left(\frac{nm}{d^2},\frac ld\right),
$$
and
$$
N_6(a)=\sum_{d\mid(n,l,m)}
\left(\frac{-3}{d}\right)d\,
g_6\left(\frac{nm}{d^2},\frac ld\right).
$$
Govindarajan--Gopala Krishna write the same coefficients with the
opposite sign in the imaginary-root correction term:
$$m_j(a)=-N_j(a)\qquad(j=5,6).$$
\end{lemma}

\begin{proof}
Govindarajan--Gopala Krishna construct the additive lift whose Weyl
alternating side gives the denominator identity for the corresponding
CHL square roots \cite[(4.2), (4.4), (4.5), (4.8)]{GK09CHL}.  Their
Maass lift gives the displayed divisor sums from the Jacobi seeds
$\psi_5$ and $\psi_6$, and their Weyl--Kac--Borcherds sum writes these
coefficients as the imaginary simple-root correction.  The sign
difference is only the convention:
$$
e^\rho+\sum_aN_j(a)e^{\rho+a},
$$
whereas \cite{GK09CHL} writes the correction with a minus sign.
\end{proof}

\begin{lemma}[Coefficient normalisation for $\nabla_{3/2}$]
\label{lem:nabla-three-halves-coefficients}
Let
$$
\nabla_{3/2}(Z)=\Delta^{(4)}_{3/2}(Z)
=\frac18\theta_5(2Z)\theta_7(2Z)\theta_9(2Z)
=\sum_{n,l,m}A_7(n,l,m)q^{n/2}r^{l/2}s^{m/2},
$$
with $A_7(1,1,1)=1$.  The first term is
$$
\left(\sqrt r-\frac1{\sqrt r}\right)\sqrt q\,\sqrt s+\cdots,
$$
so $A_7(1,-1,1)=-1$.  For
$a=\alpha_1(A,B,C)\in M_1\cap\R_{\ge0}\mathcal M_1$, put
$$
n=2A+1,\qquad l=2B+1,\qquad m=2C+1.
$$
Then the imaginary simple-root coefficient in the plus-sign convention
of Theorem~\ref{thm:govindarajan-denominator-rows} is
$$
N_7(\alpha_1(A,B,C))=A_7(2A+1,2B+1,2C+1)
=[q^{A+1/2}r^{B+1/2}s^{C+1/2}]\nabla_{3/2}(Z).
$$
In Govindarajan--Gopala Krishna's WKB sign convention,
$$m_7(a)=-N_7(a).$$
No Maass divisor-sum formula for $N_7$ is asserted here.
\end{lemma}

\begin{proof}
Clery--Gritsenko construct $\nabla_{3/2}$ as the order-four
multiplier row.  Govindarajan--Gopala Krishna identify the square-root
theta product and the square relation
$$
F_7^2=\Phi_3
$$
in the composite $N=4$ CHL case \cite{GK10Composite}.  Factoring the
Weyl vector gives
$$
e^{\rho_7+a}=q^{A+1/2}r^{B+1/2}s^{C+1/2},
$$
which is exactly the displayed coefficient extraction.  The sourced
divisor-sum formula belongs to the square $F_7^2$, with its composite
$N=4$ Jacobi seed.  A direct prime-type half-index formula for \(F_7\)
introduces fractional divisor powers at non-primitive chamber points,
whereas the theta product has integral coefficients.
This is a theta-product normalization identification.  It is not a
constructed physical host and not a physical row-map equivalence.
\end{proof}

\begin{lemma}[$Q_1$ in $M_2$ notation]
\label{lem:q1-m2-normalisation}
In $M_2$,
$$
e^{\alpha_2(n,l,m)}=q^nr^ls^{2m},\qquad
(\alpha_2(n,l,m),\alpha_2(n',l',m'))
=2ll'-8(nm'+n'm).
$$
The four simple real roots of the $Q_1$ row are
$$
\delta_1=(0,-1,0),\quad
\delta_2=(1,1,0),\quad
\delta_3=(1,3,1),\quad
\delta_4=(0,1,1),
$$
with Gram matrix $A^{(2)}$.  The Weyl vector is
$$
\rho_8=\alpha_2(\tfrac14,\tfrac12,\tfrac14),\qquad
e^{\rho_8}=q^{1/4}r^{1/2}s^{1/2},
$$
and
$$
(\rho_8,\delta_i)=-1\qquad(1\le i\le4).
$$

Let $A_8(n,l,m)$ be defined by
$$
Q_1(Z)=
\sum_{n,l,m} A_8(n,l,m)
q^{n+1/4}r^{l+1/2}s^{2m+1/2}.
$$
Govindarajan's theta-product formula, in his characteristic notation, is
$$
Q_1(Z)=\frac14\,
\vartheta\!\left[\begin{array}{cc}1&0\\0&1\end{array}\right](Z')
\vartheta\!\left[\begin{array}{cc}1&1\\1&1\end{array}\right](Z'),
\qquad
Z'=\left(\begin{array}{cc}\tau&2z\\2z&4\sigma\end{array}\right).
$$
Equivalently,
$$
A_8(n,l,m)=\frac14\sum_{\mathcal S(n,l,m)}(-1)^{j+k+h},
$$
where $\mathcal S(n,l,m)$ is the set of
$(i,j,k,h)\in\Z^4$ satisfying
$$
\frac12\left((i+\tfrac12)^2+(k+\tfrac12)^2\right)=n+\tfrac14,
$$
$$
2(i+\tfrac12)j+2(k+\tfrac12)(h+\tfrac12)=l+\tfrac12,
$$
and
$$
2j^2+2(h+\tfrac12)^2=2m+\tfrac12.
$$
Then the imaginary simple-root coefficient in the plus-sign convention
is
$$
N_8(\alpha_2(n,l,m))=A_8(n,l,m)
$$
for the chamber-supported imaginary shifts.  Govindarajan's expansion
has coefficient $-1$ at the monomials
$$
r^{-1},\qquad qr,\qquad rs^2,\qquad qr^3s^2.
$$
After factoring $e^{\rho_8}$ these are precisely the four simple real
root monomials for
$$
\delta_1,\quad\delta_2,\quad\delta_4,\quad\delta_3,
$$
so the signed real-simple-root supermultiplicity is \(+1\) in each
case.  Their even parity and multiplicity-one real-root data are the
Cheng--Dabholkar/Govindarajan CHL denominator data.
\end{lemma}

\begin{proof}
The first display is the definition of $\alpha_2$ and the Gram matrix
on $M_2$.  The simple roots and Weyl vector are Cheng--Dabholkar's
$N=2$ chamber data translated through
$$
\alpha_2(n,l,m)\longleftrightarrow
\left(\begin{array}{cc}2n&l\\ l&4m\end{array}\right).
$$
Govindarajan identifies $Q_1$ with the row $\mathcal G_2(4)$ and gives
both the product formula and the first Fourier terms.  In that CHL
normalization the square-root form is anti-invariant under the Weyl
reflections.  This is the sourced denominator anti-invariance, not an
independently constructed restriction of the Clery--Gritsenko character
through a physical row map.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:govindarajan-denominator-rows}]
Cheng--Dabholkar identify, for CHL level $N=1,2,3$, the Weyl group,
simple real roots, Weyl chamber, and Weyl denominator identity of the
dyon algebra
\cite[(2.10)--(2.16), (3.16), (3.22), (3.23), (3.26),
(3.42), (5.1), (5.2), (5.8), (5.10), (5.12)--(5.15), Appendix A]{CD09BKM}.
For $N=1$ the simple real roots are
$P^{(1)}$ and the Cartan matrix is $A^{(1)}$; for $N=2$ the simple real
roots are $P^{(2)}$ and the Cartan matrix is $A^{(2)}$.
Govindarajan then treats twisted dyons and proves that, for fixed $N$,
the algebras $\mathcal G_N(M)$ have the same real simple roots, Weyl
vector, and Cartan matrix, while the imaginary simple roots depend on
$M$ \cite[Section 4.2, Section 4.3, Table 3]{Gov11BKM}.

Govindarajan's Table 3 gives
$$
\nabla_3\longleftrightarrow\mathcal G_1(2),\qquad
\nabla_2\longleftrightarrow\mathcal G_1(3),\qquad
\nabla_{3/2}\longleftrightarrow\mathcal G_1(4),\qquad
Q_1\longleftrightarrow\mathcal G_2(4).
$$
Section 4.2 of \cite{Gov11BKM} checks the required ingredients: sum
and product representations, integrality, correct multiplicity of the
simple real roots, and the sign change of the square root under a Weyl
reflection.  Section 4.3 states the Weyl--Kac--Borcherds denominator
formula for $\mathcal G_N(M)$.
For \(F_7=\nabla_{3/2}\) the theorem is on the
\(\mu_4\)-multiplier cover, with no physical boundary partition
identity and no CY/DT/chiral host.
For \(Q_1\), Govindarajan supplies the WKB denominator data
\cite[Appendix C, Appendix D]{Gov11BKM}.
The dyon-counting additive-seed issue for the $(2,4)$ and $(4,2)$
examples plays no role.
The later hyperbolic and umbral extensions of \cite{GovSam19} are also
outside this proof: for $N=5,6$ they replace $W$ by $W_+$, leave the sum
side incompletely characterized, and treat some rows as product-only or
candidate BKM data \cite[Sections 3.3 and 4]{GovSam19}.

The real-root data translate to this notation as follows.  On \(M_t\),
$$
((n,l,m),(n',l',m'))=2ll'-4t(nm'+n'm).
$$
With $t=1$, the set $P^{(1)}$ has Gram matrix $A^{(1)}$ and
$\rho=\alpha_1(1/2,1/2,1/2)$ satisfies
$(\rho,\delta)=-1$ for every $\delta\in P^{(1)}$.  With $t=2$, the set
$P^{(2)}$ has Gram matrix $A^{(2)}$ and
$\rho=\alpha_2(1/4,1/2,1/4)$ satisfies
$(\rho,\delta)=-1$ for every $\delta\in P^{(2)}$.  These are exactly
the Weyl-vector equations
$(\rho,\delta)=-(\delta,\delta)/2$ because all displayed real roots
have square $2$.
\end{proof}

\begin{remark}[Nonabelian row data]
\label{prop:no-unbuilt-denominator}
The row data are:
$$
\begin{array}{c|c|c}
j&\mathrm{automorphic\ data}\ (F_j,\Gamma_j,\nu_j,\rho_j^{\mathrm{pref}})
&\mathrm{lattice\ and\ degree\ datum}\\ \hline
1&\mathrm{computed/imported\ }(\Delta_5\mathrm{\ product})
&\mathrm{formal\ lattice\ computed;\ GN\ denominator\ imported}\\
2,3,4&\mathrm{GN\ denominator\ theorem}
&L_j=M_j,\ \alpha_j=\alpha_j^{\mathrm{GN}}\\
5,6,7&\mathrm{CG\ product;\ Govindarajan\ denominator}
&P^{(1)},\mathcal M_1,W_1,\epsilon=\det\quad(\mathrm{CHL})\\
8&\mathrm{CG\ product;\ Govindarajan\ denominator}
&P^{(2)},\mathcal M_2,W_2,\epsilon=\det\quad(\mathrm{CHL})\\
\end{array}
$$
Thus all eight rows have formal product/current-envelope objects.
Rows \(1\)--\(4\) have the Gritsenko--Nikulin denominator algebras.
Rows \(5\)--\(8\) have the Govindarajan CHL/WKB denominator algebras in
the CHL normalization.  The row \(F_7\) lives on the
\(\mu_4\)-multiplier cover and fills no physical-host certificate beyond
the sourced denominator level.
\end{remark}

\begin{openproblem}[Physical-host certificates and row maps]
\label{conj:nonabelian-row-extension}
Construct, for every claimed physical realization of a
Clery--Gritsenko row, a datum
$$
(\iota_j,\mathscr R_j,
\mathscr A_j,\mathscr D_j,\mathscr S_j,\mathscr Z_j,\mathscr H_j)
$$
such that
$$
\iota_j:\Phi^{\mathrm{phys}}_j\longleftrightarrow F_i^{\mathrm{CG}}
$$
fixes the exact row, parent form when a root is used, group or cover,
automorphy cocycle, multiplier and its order, divisor multiplicities,
Jacobi seed at every cusp, product-degree lattice, chamber, branch,
normalization, and source theorem.  The
entries
\((\mathscr A_j,\mathscr D_j,\mathscr S_j,\mathscr Z_j,\mathscr H_j)\)
are the five levels of Definition~\ref{def:physical-host-certificate}.
For rows \(F_5,\ldots,F_8\), the Govindarajan CHL/WKB theorem fills
\(\mathscr D_j\), and the sourced scalar square fills \(\mathscr S_j\)
where stated.  It does not fill \(\mathscr Z_j\) or
\(\mathscr H_j\).  A boundary partition identity and a compact
Hall/chiral source remain open until these certificate entries are
constructed.
\end{openproblem}

\begin{proposition}[Comparison row systems]
\label{prop:boundary-weights}
The Clery--Gritsenko rows in the present \(F_i\)-order have weights
$$
(5,2,1,\tfrac12,3,2,\tfrac32,1).
$$
In triple order
$$
(t,N)=(1,1),(2,1),(1,2),(3,1),(1,3),(4,1),(1,4),(2,2),
$$
the weights are
$$
(5,2,3,1,2,\tfrac12,\tfrac32,1),
$$
and the permutation from triple order to present order is
$$
(1,2,5,3,6,4,7,8).
$$
Consequently
$$
\{j:\mathrm{wt}(F_j)\in\Z\}=\{1,2,3,5,6,8\},\qquad
\{j:\mathrm{wt}(F_j)\notin\Z\}=\{4,7\}.
$$
The comparison notation
$$\Phi^{\mathrm{cmp}}_1,\ldots,\Phi^{\mathrm{cmp}}_8,\qquad
\mathrm{wt}(\Phi^{\mathrm{cmp}}_j)=(5,2,1,1,\tfrac12,1,\tfrac14,0),$$
does not define the Clery--Gritsenko row system and defines no physical
atlas in this paper.  A row map
$$
\Phi^{\mathrm{cmp}}_j\longleftrightarrow F_i
$$
requires the relevant entries of
Definition~\ref{def:physical-host-certificate}.  Consequently the direct
identifications
$$
\Phi^{\mathrm{cmp}}_5=F_5,\qquad
\Phi^{\mathrm{cmp}}_7=F_7,\qquad
\Phi^{\mathrm{cmp}}_8=F_8
$$
are false already by weight.  The eight-row Clery--Gritsenko catalogue
contains no weight-\(1/4\) row and no weight-\(0\) row.  The CHL square
identities, such as \(\nabla_3^2=\Phi_6^{(1,2)}\) and
\(\nabla_2^2=\Phi_4^{(1,3)}\), are scalar square identities; they are not row
maps and do not by themselves carry the denominator sign, parity, or
Weyl alternating side.
\end{proposition}

\begin{proof}
The Clery--Gritsenko theorem gives the exact weights, groups, characters,
and divisors of the eight diagonal-divisor rows \cite{GC}.  The displayed
comparison tuple is not that theorem table.  The Borcea--Voisin route
\cite{BORCEA}, \cite{VOISIN} and higher-dimensional curve-counting routes
\cite{OhThomasI}, \cite{OhThomasII}, \cite{BOPY} require separate
construction of \(X_j\), the reduced theory, the protected index, and the
product identity.  None is constructed here.  Thus the comparison symbols
remain external labels until a certificate identifies them with
Clery--Gritsenko rows.
\end{proof}

\begin{definition}[Canonical fractional branch]
\label{def:canonical-fractional-branch}
Let
$$
F(Z)=a\,q^\alpha r^\beta s^\gamma(1+O(q,r,s)),
\qquad a\in\R_{>0},
$$
be a product expansion in a fixed positive Weyl chamber.  Its canonical
\(k\)-th root in that chamber is
$$
F(Z)^{1/k}
=a^{1/k}q^{\alpha/k}r^{\beta/k}s^{\gamma/k}
\exp\left(\frac1k\log(1+O(q,r,s))\right),
$$
where \(a^{1/k}\) is the positive real root and the logarithm is the
formal logarithm in the completed product algebra.  This defines a
formal branch.  It does not define a modular form until the relevant
metaplectic or multiplier-cover character has been constructed.
\end{definition}

\begin{proposition}[Fractional-power comparison test]
\label{prop:fractional-power-comparison-test}
The formal fractional-power comparison symbols
\[
\Phi^{\mathrm{cmp}}_5,\qquad
\Phi^{\mathrm{cmp}}_7,\qquad
\Phi^{\mathrm{cmp}}_8
\]
do not label Clery--Gritsenko rows.  The only source-compatible
statement retained here is the following conditional test.

The displayed comparison weight of \(\Phi^{\mathrm{cmp}}_5\) is
\(1/2\).  If it is presented as a square root, the parent form must have
weight \(1\), and the root must live on the pullback of the parent group
to the genus-two metaplectic cover with a genuine half-integral
multiplier.  A weight-\(5\) parent would produce a weight-\(5/2\) square
root and does not certify this displayed comparison slot.

If the comparison symbol \(\Phi^{\mathrm{cmp}}_7\) is supplied with its
displayed comparison weight \(1/4\), then it must be a genuine
quarter-integral-weight form on a multiplier cover.  If it is presented
as a fourth root of a parent form with exact order-four character, an
order-eight cover is not forced by character theory.  If a character
root \(\psi\) with \(\psi^4=\chi\) exists after pullback and \(\chi\)
has exact order \(4\), then the character part has exact order
\(16\), unless an explicit automorphy-cocycle relation reduces it.  No
such relation is constructed here.
The \(\mu_4\)-cover of the Clery--Gritsenko row
\(F_7=\nabla_{3/2}\), whose weight is \(3/2\), is not a modular-root
certificate for a comparison object \(\Phi^{\mathrm{cmp}}_7\) of weight
\(1/4\).  That comparison object needs its own parent, cover, cocycle,
and character-root computation.

If a comparison form \(\Phi^{\mathrm{cmp}}_8\) has weight \(0\), the
canonical branch of Definition~\ref{def:canonical-fractional-branch}
is only a formal logarithmic branch.  By itself it gives no
finite-order modular multiplier and no chiral square-root theorem.
\end{proposition}

\begin{proof}
The first two assertions are necessary metaplectic-cover conditions:
a fractional power of an automorphic product is modular only after the
automorphy factor, character, and divisor multiplicities lift to a
genuine character on a cover; Weil and Shimura give the classical
background for such metaplectic phenomena \cite{Weil1964},
\cite{Shimura1973}.  The stated character-order obstruction is
elementary: if \(\chi\) has exact order \(4\) and \(\psi^4=\chi\), then
\(\psi\) cannot have order \(8\), since \(\psi^4\) would have order at
most \(2\); absent a further cocycle relation, order \(16\) is the first
possible character order.  In the weight-zero case the formal branch
supplies no metaplectic weight contribution; modularity would have to
come entirely from divisor divisibility and a character or automorphy
cocycle root.  A formal root can be chosen in a chamber, but this is not
a modular or chiral construction.
\end{proof}

\begin{openproblem}[Fractional comparison-row physical-host certificate]
\label{op:fractional-comparison-row-host}
For a fractional comparison row, construct a modular-root certificate
\(\mathscr R_j\) and the five-level physical-host certificate of
Definition~\ref{def:physical-host-certificate}.  The root certificate
must fix the parent form, root exponent, exact group or cover,
multiplier character and its order, automorphy cocycle, divisor
multiplicities, branch, product normalization, and source theorem.
The reduced scalar level, if claimed, must produce a compact
Calabi--Yau, orbifold Calabi--Yau, or CHL background with oriented
reduced obstruction theory and prove
$$
Z_j^{\mathrm{red}}=C_j(\Phi^{\mathrm{cmp}}_j)^{-2}
$$
in the fixed chamber and cover.  The compact Hall/chiral level must
construct the protected one-particle index and primitive bracket
comparison for the same row.

Borcea--Voisin and higher-dimensional curve-counting constructions
\cite{BORCEA}, \cite{VOISIN}, \cite{OhThomasI}, \cite{OhThomasII},
\cite{BOPY} are possible sources for such a certificate.  This paper
does not assert that they supply it.  Until \(\mathscr R_j\) and the
relevant certificate entries are constructed, the symbols
\(\Phi^{\mathrm{cmp}}_5,\Phi^{\mathrm{cmp}}_7,\Phi^{\mathrm{cmp}}_8\)
are formal comparison symbols only: no Clery--Gritsenko row,
finite-order multiplier, denominator identity, CY/DT partition theorem,
or chiral power follows.
\end{openproblem}

The following comparison table is restricted to the $N=1$ Igusa
boundary.  It contains no row map
$$\Phi^{\mathrm{cmp}}_j\longleftrightarrow F_i$$
and no physical row-map denominator theorem for any congruence
row.  The separate Govindarajan CHL/WKB denominator theorem remains
Theorem~\ref{thm:govindarajan-denominator-rows}.

For \(X=K3\times E\) the protected one-particle index is theorem-level,
the virtual \(K_0\)-determinant is \(\Delta_5\) in the theta
normalization, and the same active half-coefficients are the visible
signed root supermultiplicities of the Gritsenko--Nikulin denominator
algebra \(\mathfrak g_{\Delta_5}\); the reduced scalar branch is
\(-4096\,\Delta_5^{-2}\) by Oberdieck--Pixton.  The compact observable
algebra realizing these on \(K3\times E\), with orientation character
\(\epsilon_o=\nu_{\Delta_5}\) on \(W^{(2)}(\La^{2,1}_{II})\), is the
open recognition target.  The seven other Clery--Gritsenko
diagonal-divisor rows extend the same separation: each row carries its
automorphic product, and the levels
\(\mathscr A_j,\mathscr D_j,\mathscr S_j,\mathscr Z_j,\mathscr H_j\) of
physical-host certificate are filled only where the cited literature
supplies them.

\input{appendices/boundary_compatibility_conditions}

%\printbibliography
\bibliographystyle{amsrn}
\bibliography{proj}

\end{document}
