\subsection{The hybrid factorization carrier $\operatorname{Ran}^{\mathrm{hyb}}(E)$}
\label{subsec:hybrid-ran-carrier}

The first entry of the Dirac--Igusa pro-object is the carrier on which
chiral operations live.  An ordinary Beilinson--Drinfeld factorization
algebra on $\operatorname{Ran}(E)$ \cite[\S3.1]{BD} sees only a finite
multiset of points of $E$ and the operations attached to their
collisions; this is the projection-finite stratum.  The Igusa product
\(\Delta_5\) carries a Borcherds variable $s$ whose positive powers
record positive elliptic-degree wrapping, and a one-dimensional
subscheme of \(K3\times E\) of positive elliptic degree projects
\emph{onto} \(E\).  Locality on $\operatorname{Ran}(E)$ alone has no
mechanism for it.

\begin{lemma}[Projection-to-$E$ support-locality obstruction;
\textit{proved}]
\label{lem:wrapped-projection-obstruction}
Let $C\subset K3\times E$ be a one-dimensional subscheme whose curve
class has positive elliptic degree, $(p_E)_*[C]=b[E]$ with $b>0$.  Then
$p_E(C)=E$.  In particular $C$ is not localized at finitely many points
of $E$, and is not contained in $p_E^{-1}(U)$ for any proper open
$U\subsetneq E$.
\end{lemma}

\begin{proof}
If $p_E(C)$ were zero-dimensional, the pushforward of $[C]$ to $E$
would vanish, contradicting $(p_E)_*[C]=b[E]$ with $b>0$.  Properness
of $p_E$ makes $p_E(C)$ closed, and the irreducibility of $E$ forces
$p_E(C)=E$.
\end{proof}

The hybrid carrier replaces the Ran space by a two-stratum object that
records, simultaneously, finite local supports and wrapped elliptic
legs.  At every finite Harder--Narasimhan height $R$ the datum is a
finite-coloured correspondence base, not a Ran space with a scalar
attached.

\begin{definition}[Hybrid Ran base]
\label{def:hybrid-ran-base}
Let $p_E:K3\times E\to E$ be projection.  A compact Hall or chiral
sector is \emph{projection-finite over $E$} if every object $A$ in it
satisfies $p_E(\operatorname{Supp}A)\subset F$ for some finite subset
$F\subset E$.  A one-dimensional sector is \emph{wrapped over $E$} if
its curve class has positive elliptic degree, in which case write
\[
b(A)=\deg(p_E)_*[\operatorname{Supp}_1A]\in\Z_{\ge0}.
\]
At finite height $R$, a point of the hybrid base
$\operatorname{Ran}^{\mathrm{hyb}}(E)_{\le R}$ consists of a finite
projection-local support $F\subset E$, finitely many wrapped colours
$\eta_j\in\Gamma_R^{\mathrm{wr}}$, and rigidified wrapped objects
$W_j$ carrying anchor values $\lambda_{\eta_j,R}(W_j)\in E$.  Its
arrows are generated by collisions of $F$, by extensions of local
colours, by mixed local/wrapped correspondences, and by
wrapped/wrapped correspondences.  The underlying degree shadow is
\[
\operatorname{Ran}^{\mathrm{hyb}}(E)
=\bigsqcup_{b\ge0}\operatorname{Ran}(E)_{[b]},
\qquad
\operatorname{Ran}(E)_{[b]}:=\operatorname{Ran}(E)\times\{b\}.
\]
The stratum $b=0$ is the ordinary Beilinson--Drinfeld
finite-support Ran stratum on $E$
\cite[\S3.4]{BD}.  A stratum
$b>0$ records finite local collision points together with a global
wrapped elliptic leg of degree $b$; it does \emph{not} assert that the
wrapped support is finite over $E$.
\end{definition}

\begin{corollary}[Naive Ran locality misses the elliptic-degree
direction; \textit{proved}]
\label{cor:naive-ranE-misses-s}
A support-local factorization algebra on $\operatorname{Ran}(E)$,
defined only by separating supports over disjoint opens of $E$,
sees the projection-finite sector.  It does not realize the full
$s$-direction of the Igusa product.
\end{corollary}

\begin{proof}
The Borcherds variable $s$ corresponds to the
Oberdieck--Pandharipande/Donaldson--Thomas elliptic-degree direction
\cite{OberdieckReducedPT}.  By Lemma~\ref{lem:wrapped-projection-obstruction},
positive elliptic-degree objects project onto all of $E$.  Such
objects cannot be separated by disjoint opens.  Therefore ordinary
Ran-locality has no locality mechanism for the wrapped sector.
\end{proof}

\subsubsection*{Finite hybrid local/wrapped factorization datum}

The full carrier at finite stage is the following datum (licensing
type~$\delta$: supplied finite chain data, with named obstruction
classes that must be trivialized).

\begin{definition}[Finite hybrid local/wrapped factorization datum]
\label{def:hybrid-wrapped-factorization-datum}
Fix a Bridgeland-style stability sector $(\sigma,S)$ in the K3-surface
lineage \cite{BridgelandK3Stability,BayerMacriProjectivity} and a
finite HN height $R$.  A finite-stage hybrid datum is
\[
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
=\bigl(
\mathcal C_{\sigma,S,\le R},\,
b_R^{\mathrm{geom}},\,
\mathcal F_R^{\mathrm{loc}},\,
\mathcal G_R^{\mathrm{wr}},\,
\mathfrak E_R^{\mathrm{loc}},\,
\mathfrak E_R^{\mathrm{hyb}},\,
\mathfrak E_R^{\mathrm{wr}},\,
\mathfrak{Flag}_R^{\mathrm{hyb}},\,
\mathsf{Corr}^{E,\mathrm{hyb}}_R,\,
\lambda_R,\,
Q_{E,R},\,
\theta^Q_R,\,
o_R,\,
I_R^{\mathrm{prot}}\bigr)
\]
with the seven clauses below.  Every stack, sheaf, operation, and
coherence lives at the fixed height $R$; the inverse limit appears
only after all finite stages and transition maps have been supplied.

\begin{enumerate}
\item \emph{Finite Hall stage and elliptic degree.}
$\mathcal C_{\sigma,S,\le R}$ is a supplied extension-closed
charge-support HN quotient of the candidate compact Hall category
under the finite-type hypothesis $\textup{[K3$\times$E-fin]}$,
with finite-type substacks
$\mathfrak M_{\gamma,R}$ for
$\gamma\in\Gamma_{\sigma,S}^{\mathrm{HN}}(R)$,
vanishing-cycle coefficients $\Phi_{\gamma,R}$, and orientation lines
$o_{\gamma,R}$.  The geometric elliptic-degree component
\[
b_R^{\mathrm{geom}}:\Gamma_{\sigma,S}^{\mathrm{HN}}(R)\longrightarrow\Z_{\ge0}
\]
splits the finite charge support into local and wrapped pieces:
$\Gamma_R^{\mathrm{loc}}=\{b_R^{\mathrm{geom}}=0\}$,
$\Gamma_R^{\mathrm{wr}}=\{b_R^{\mathrm{geom}}>0\}$.  The map is
additive on retained extensions; outputs of height $>R$ are zero.

\item \emph{Projection-finite local sector through closed
configurations.}  For a finite set $I$, set
\[
Z_I=\bigcup_{i\in I}\{(e,(e_j)_j)\in E\times E^I\mid e=e_i\}.
\]
For $\alpha\in\Gamma_R^{\mathrm{loc}}$ the stage supplies a
closed-configuration incidence stack
\[
\mathfrak M_{\alpha,R,I}^{\mathrm{loc,cl}}
=\{(A,\mathbf e)\in\mathfrak M_{\alpha,R}\times E^I\mid
p_E(\operatorname{Supp}A)\subset Z_I(\mathbf e)\}
\]
compatible with diagonals $E^J\to E^I$, symmetric-group descent, and
the d-critical/vanishing-cycle structure.  Open-support locality is
recovered as a limit
\[
\mathcal M_{\alpha,R}^{\mathrm{loc}}(U)
\simeq\operatorname*{colim}_{I}
\bigl(\mathfrak M_{\alpha,R,I}^{\mathrm{loc,cl}}\times_{E^I}U^I\bigr),
\]
and the configuration map $\pi_{\alpha,R,I}$ produces
\[
\mathscr H_{\alpha,R,I}^{\mathrm{loc}}
=(\pi_{\alpha,R,I})_!(\Phi_{\alpha,R,I}^{\mathrm{loc}}\otimes
o_{\alpha,R,I}^{\mathrm{loc}}).
\]
For an open $U\subset E$,
\[
\mathcal F_{\alpha,R}^{\mathrm{loc}}(U)
=\bigoplus_{I/S_I}R\Gamma_c\!\left(U^I,
j_{U,I}^{!}\mathscr H_{\alpha,R,I}^{\mathrm{loc}}\right),
\]
and $\mathcal F_R^{\mathrm{loc}}(U)$ is the direct sum over
$\Gamma_R^{\mathrm{loc}}$.  Locality is $!$-restriction on closed
configuration spaces; the open-support Borel--Moore formula is a
theorem to be derived from this atlas, not the primary datum.

\item \emph{Wrapped prequotient sector and rigidification.}  For
$\eta\in\Gamma_R^{\mathrm{wr}}$, a prequotient stack
\[
\mathcal M_{\eta,R}^{\mathrm{wr,rig}}
\xrightarrow{\rho_{\eta,R}}
\mathcal M_{\eta,R}^{\mathrm{wr}}\subset\mathfrak M_{\eta,R}
\]
is supplied with a fixed origin $0_E\in E$ and an $E$-equivariant
anchor $\lambda_{\eta,R}:\mathcal M_{\eta,R}^{\mathrm{wr,rig}}\to E$
satisfying $\lambda_{\eta,R}(t\cdot W)=t+\lambda_{\eta,R}(W)$.  A
natural candidate anchor is the normalized determinant of pushforward
$\det Rp_{E,*}A\otimes\mathcal O_E(-\chi(A)\cdot 0_E)\in
\operatorname{Pic}^0(E)\simeq E$, with translation weight $\chi(A)$;
on $\chi(A)=0$ strata it does not by itself remember the relative
$E$-position, and rank-one wrapped pairs of identical determinant and
charge can have distinct wrapped self-Ext dimensions
($\dim\operatorname{Ext}^1_E$ on $\mathcal O_E^{\oplus2}$ is $4$,
on $L\oplus L^{-1}$ with $L^2\ne\mathcal O_E$ is $2$).  The anchor
residual is therefore a typed finite datum
\[
\mathfrak o^\lambda_R=\bigl(
\mathfrak o^{\lambda,\mathrm{ex}}_R,\
\mathfrak o^{\lambda,\mathrm{unit}}_R,\
\mathfrak o^{\lambda,\mathrm{loss}}_R,\
\mathfrak o^{\lambda,\mathrm{multi}}_R,\
\mathfrak o^{\lambda,\mathrm{tr}}_{R'R}\bigr).
\]
With the anchor in place, set
\[
\mathcal G_{\eta,R}^{\mathrm{wr}}
=H_*^{\mathrm{BM}}\!\left(
\mathcal M_{\eta,R}^{\mathrm{wr,rig}},
\Phi_{\eta,R}^{\mathrm{wr}}\otimes o_{\eta,R}^{\mathrm{wr}}\right),
\qquad
\mathcal G_R^{\mathrm{wr}}=\bigoplus_{\eta}\mathcal G_{\eta,R}^{\mathrm{wr}}.
\]

\item \emph{Local, mixed, and wrapped extension correspondences.}  For
disjoint opens $(U_i)\subset E$, local charges $\alpha_i$, and wrapped
charges $\eta,\eta_1,\eta_2$, the finite stage contains the
correspondence stacks
\[
\mathfrak E_{\alpha_1,\ldots,\alpha_r,R}^{\mathrm{loc}}(U_1,\ldots,U_r),
\quad
\mathfrak E_{\alpha_1,\ldots,\alpha_r;\eta,R}^{\mathrm{hyb}},
\quad
\mathfrak E_{\eta_1,\eta_2,R}^{\mathrm{wr}},
\]
together with the ordered \emph{two-sided} mixed stacks
\[
\mathfrak E_{\alpha_-;\eta;\beta_+,R}^{\mathrm{hyb}}((U_i),(V_j))
\]
classifying ordered insertions of finite local supports on both sides
of one wrapped input.  The defects of closed-configuration finite-type
properness, pull-push admissibility, and Thom--Sebastiani transport
are recorded by
\[
\mathfrak o^{\mathrm{prop},\mathrm{LL}}_R,\
\mathfrak o^{\mathrm{prop},\mathrm{mix}}_R,\
\mathfrak o^{\mathrm{prop},\mathrm{WW}}_R,
\]
and aggregate residuals
$\mathfrak o^{\mathrm{conf}}_R$,
$\mathfrak o^{\mathrm{conf{-}prop}}_R$,
$\mathfrak o^{\mathrm{adm}}_R$,
$\mathfrak o^{\mathrm{TS}}_R$.  Mixed and wrapped stacks remember
input--output anchors before quotienting,
\[
\mathfrak E_{\eta_1,\eta_2,R}^{\mathrm{wr}}
\to E\times E\times E,
\qquad
\xi\mapsto(\lambda_{\eta_1,R}(W_1),
\lambda_{\eta_2,R}(W_2),
\lambda_{\eta_1+\eta_2,R}(W));
\]
replacing this memory by a scalar Fock or Hecke factor is not the
hybrid datum.  These stacks generate a finite $E$-equivariant
correspondence category $\mathsf{Corr}^{E,\mathrm{hyb}}_R$ with
operation maps $\mu_R^\bullet=q_!\circ\operatorname{TS}_R\circ p^*$.

\item \emph{Eight-word two-step binary flag atlas.}  Write
$\mathrm L$ for a projection-finite local input and $\mathrm W$ for a
rigidified wrapped input.  For every word
$w=(\epsilon_1,\epsilon_2,\epsilon_3)\in\{\mathrm L,\mathrm W\}^3$ and
every compatible ordered triple $(\xi_1,\xi_2,\xi_3)$ of charges and
local opens, the datum supplies a two-step flag stack
$\mathfrak{Flag}^{w}_{\xi_1,\xi_2,\xi_3,R}$ classifying filtrations
with the prescribed associated graded pieces, with comparison maps to
the iterated correspondence fibre products.  The eight words
\[
\mathrm{LLL},\ \mathrm{LLW},\ \mathrm{LWL},\ \mathrm{WLL},\
\mathrm{LWW},\ \mathrm{WLW},\ \mathrm{WWL},\ \mathrm{WWW}
\]
are all part of the datum; in mixed and wrapped words the flag stack
retains input/intermediate/output anchors before $E$-quotient.  The
two parenthesizations give the same map in the finite quotient,
\[
\mu_{\xi_1+\xi_2,\xi_3,R}\circ(\mu_{\xi_1,\xi_2,R}\otimes 1)
=\mu_{\xi_1,\xi_2+\xi_3,R}\circ(1\otimes\mu_{\xi_2,\xi_3,R}),
\]
with defect classes $\mathfrak o^{\mathrm{assoc}}_{w,R}$ required to
vanish for all eight words; the chosen $2$-morphisms must satisfy the
four-input pentagon on the four-step flag-of-flags stacks.  The
higher-coloured residual $\mathfrak o^{\mathrm{col}}_R$ records the
remaining colored configuration data, units, symmetry conventions,
refinement maps, descent, and overlap coherences for all finite HN
windows.  The eight-word atlas gives only binary associativity; full
hybrid factorization requires the higher-coloured residual to vanish
in addition.

\item \emph{Quotient-after-correspondence functor and reduced
$E$-quotient.}  All stacks and correspondences above are
$E$-equivariant before quotienting.  The quotient datum supplies a
pseudofunctor
\[
\mathsf{Corr}^{E,\mathrm{hyb}}_R\longrightarrow
\mathsf{Corr}^{\mathrm{red},\mathrm{hyb}}_R
\]
with coherent $2$-morphisms for composition, base-change, and
Thom--Sebastiani transport; applying vanishing-cycle Borel--Moore
chains gives the finite correspondence module categories
$\mathsf{BM}^{E,\mathrm{hyb}}_R$ and
$\mathsf{BM}^{\mathrm{red},\mathrm{hyb}}_R$, and the induced functor
$Q_{E,R}$ between them.  For each operation
$\mu_R^\bullet=q_!\operatorname{TS}p^*$ the datum carries a comparison
isomorphism
\[
\theta^Q_{\mu,R}:Q_{E,R}\,q_!\operatorname{TS}p^*
\xrightarrow{\sim}
\overline q_!\overline{\operatorname{TS}}\,\overline p^*
(Q_{E,R}^{\boxtimes k}),
\]
compatible with the flag-stack coherences.  The four quotient
residuals
$\mathfrak o^{Q,\mathrm{form}}_R,
\mathfrak o^{Q,\mathrm{adm}}_R,
\mathfrak o^{Q,\mathrm{flag}}_R,
\mathfrak o^{Q,\mathrm{tr}}_{R'R}$
must vanish.  A quotient-first construction (object-stack quotient
followed by a new Hall product) is \emph{not} this datum.

\item \emph{Protected integration with Gram-trace degree.}
The finite stage carries a protected integration map
\[
I_R^{\mathrm{prot}}:Q_{E,R}\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\longrightarrow\C[\Gamma_{\mathrm{eff}}]_{\le R}
\]
compatible with reduced product, coproduct, primitive projection, and
HN transition.  For homogeneous $x$ of charge $\gamma$ with full Gram
label $\overline\Pi_X(\gamma)=(n,l,m)$,
\[
I_R^{\mathrm{prot}}(Q_{E,R}x)\in
s^{m_R(\gamma)}\C[q^{\pm1},r^{\pm1}],
\qquad
m_R(\gamma)=m,
\]
in the OP/Borcherds variables of
Proposition~\ref{conv:op-chamber}.  The Gram trace $m_R$ is
additive under $\overline\Pi_X$, so
$s^{m_R(\gamma_1+\cdots+\gamma_k)}=\prod_i s^{m_R(\gamma_i)}$ inside
the finite quotient: the $s$-direction is coupled to the actual
local/wrapped operation, not appended as an external Fock determinant.
The integration defects
\[
\mathfrak o^{I,\mathrm{ch}}_R,\
\{\mathfrak o^{I,\mathrm{prod}}_{w,R}\}_w,\
\mathfrak o^{I,\mathrm{co}}_R,\
\mathfrak o^{I,\Prim}_R,\
\mathfrak o^{I,\mathrm{tr}}_{R'R}
\]
record chain compatibility, multiplicativity on each word, comultiplicativity, primitive
compatibility, and HN transition.
\end{enumerate}

The aggregate finite obstruction tuple of the hybrid lane is
\[
\mathfrak O_{\mathrm{hyb},R}
=(\mathfrak o^{\mathrm{stage}}_R,
\mathfrak o^{\lambda}_R,
\mathfrak o^{\mathrm{corr},\mathrm{LL}}_R,
\mathfrak o^{\mathrm{corr},\mathrm{mix}}_R,
\mathfrak o^{\mathrm{corr},\mathrm{WW}}_R,
\mathfrak o^{\mathrm{conf}}_R,
\{\mathfrak o^{\mathrm{assoc}}_{w,R}\}_w,
\mathfrak o^{\mathrm{col}}_R,
\mathfrak o^{Q,\bullet}_R,
\mathfrak o^{I,\bullet}_R,
\mathfrak o^{\mathrm{tr}}_{\mathrm{hyb},R'R}).
\]
\end{definition}

\begin{proposition}[Finite consequences of the hybrid datum;
\textit{conditional on
$\mathfrak O_{\mathrm{hyb},R}=0$}]
\label{prop:hybrid-datum-scope}
Assume the data of
Definition~\ref{def:hybrid-wrapped-factorization-datum} are supplied
for all $R$ with compatible transition maps, and
$\mathfrak O_{\mathrm{hyb},R}=0$.  Then:
\begin{enumerate}
\item the $b=0$ restriction is an ordinary support-local factorization
algebra on $\operatorname{Ran}(E)$ in the sense of Beilinson--Drinfeld
\cite[\S3.4]{BD}, equivalently a Costello--Gwilliam factorization
algebra over the smooth real curve $E_{\mathrm{top}}$
\cite[Vol.~II~\S10]{CostelloGwilliam2};
\item every operation with a wrapped input lands in a wrapped
stratum;
\item the ordered mixed maps, including the two-sided
$\mu_{\alpha_-;\eta;\beta_+,R}^{\mathrm{hyb}}$, are the only Hall
actions of projection-finite insertions on wrapped sectors in
$\mathsf{Corr}^{E,\mathrm{hyb}}_R$ before reduced $E$-quotient;
\item the eight-word atlas plus pentagon coherence yield an
associative finite-stage reduced Hall product after vanishing cycles,
orientations, HN quotienting, the quotient functor, and the
$\theta^Q_{\mu,R}$;
\item for homogeneous $x$ of charge $\gamma$,
$I_R^{\mathrm{prot}}(Q_{E,R}x)\in s^{m_R(\gamma)}\C[q^{\pm1},r^{\pm1}]$,
hence the positive $s$-direction cannot be supplied by the
projection-finite stratum alone.
\end{enumerate}
\end{proposition}

\begin{proof}
Items (i) and (ii) are built into the elliptic-degree stratification
and Lemma~\ref{lem:wrapped-projection-obstruction}.  Item (iii) is the
definition of the mixed operations: before reduced $E$-quotient they
are the only displayed operations remembering relative $E$-position
between finite local supports and a wrapped leg.  Items (iv) and (v)
are the eight-word coherence and the protected integration clause.
\end{proof}

\begin{corollary}[No quotient-first universal hybrid repair;
\textit{proved}]
\label{cor:no-quotient-first-hybrid-repair}
A candidate finite correspondence category for the wrapped sector
gives the source object $\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}$
only if it contains the unreduced local, wrapped, and ordered mixed
source stacks of
Definition~\ref{def:hybrid-wrapped-factorization-datum}, their
anchors, the eight-word flag atlas, the quotient functor $Q_{E,R}$
formed after those correspondences, the comparison maps
$\theta^Q_{\mu,R}$, and protected integration with
$\mathfrak O_{\mathrm{hyb},R}=0$.  A quotient of object stacks formed
\emph{before} the mixed and wrapped correspondences, or a
determinant/Fock category carrying only the trace degree
$s^{m_R}$, does not define the hybrid source.
\end{corollary}

\begin{proof}
By Lemma~\ref{lem:wrapped-projection-obstruction}, a positive
elliptic-degree sector is not a finite-support Ran sector; only the
rigidified wrapped prequotient with anchor, together with the
unreduced mixed and wrapped correspondences, retains the relative
$E$-position used by the source data.  A quotient-first construction
loses these anchors.
\end{proof}

\subsubsection*{Cross-repo anchor}

The hybrid carrier is the K3$\times E$-specialization of the
two-stage construction $\textup{CY}_d\textup{-Cat}\to E_d$-$\textup{HolFA}(X)\to
\textup{ChirAlg}(C)$ supplied by the Vol III Calabi--Yau quantum-groups
constellation: the projection-finite local stratum is the
$E_3$-holomorphic factorization algebra restricted to the smooth
elliptic factor, and the wrapped stratum is the chain-level
$K3$-fusion datum that the local stratum cannot see.  Beilinson and
Drinfeld's Ran construction \cite[\S3.4--\S3.5]{BD} provides the
$b=0$ part; the $b>0$ part is the obligation that this manuscript
isolates and the parallel chiral-bar-cobar volume tracks under the
name Hall--Borcherds residual.  The eight-word two-step binary flag
atlas $w\in\{\mathrm L,\mathrm W\}^3$ is the smallest closed coherence
calculus that detects the local/wrapped split through binary
associativity; it is independent of the higher-coloured residual
$\mathfrak o^{\mathrm{col}}_R$ which closes higher symmetric arities,
units, and overlaps.

\subsubsection*{Status under (D0)}

Probes A005, A011, A026, A037, A042 record finite-stage components of
$\mathfrak o^{\mathrm{stage}}_R$ and $\mathfrak o^{\lambda}_R$.
Discharge of the wrapped-leg construction and the eight-word atlas at
finite height is open; the $b=0$ stratum is the classical
projection-finite Ran sector of \cite{BD}.
The hybrid carrier is therefore the projection-finite Ran stratum
unconditionally, and the wrapped stratum conditionally on the named
finite obstruction tuple $\mathfrak O_{\mathrm{hyb},R}$.

Chiral operations on $\mathrm{Ran}^{\mathrm{hyb}}(E)$ require an
orientation line on the cosection-reduced d-critical heart.  On
$K3\times E$ this orientation descends through the reduced
$E$-quotient; on rank-$2$ $E$-strata it is the Klein-four
trivialization of the relative determinant.  Entry $(\mathrm L 2)$,
constructed in \S\ref{subsec:cosection-twisted-orientation}, is this
orientation.
