\subsection{Cosection-twisted reduced d-critical orientation}
\label{subsec:cosection-twisted-orientation}

The d-critical structure of the compact Hall sector on $K3\times E$ is
the second entry of the pro-object.  It supplies a vanishing-cycle
coefficient system, a Joyce--Upmeier--type orientation line, and a
quotient-descent package for the reduced $E$-quotient.  These are the
finite-stage operands of the Hall product.  Before any Pfaffian wall
or Weyl transport can be discussed, the orientation line must descend
through the cosection-reduced moduli.

The compact Hall heart is built from a Bridgeland-type stability
sector $(\sigma,S)$ on $D^b(\operatorname{Coh}(K3\times E))$ in the K3
lineage of \cite{BridgelandK3Stability,BayerMacriProjectivity}.  The
PTVV $(-1)$-shifted symplectic structures
\cite{PTVV2013} restrict to the finite-type stacks selected by the HN
quotient and give Joyce d-critical structures
\cite{BBDJS2015} after classical truncation.  The K3 fibre
direction supplies a semiregularity cosection
$\operatorname{CS}_{\mathcal C}$, surjective on reduced strata, whose
filtered Hall additivity on extension stacks
\[
q^*\operatorname{CS}_C
=p_1^*\operatorname{CS}_A+p_2^*\operatorname{CS}_B
\]
is the input to Kiem--Li cosection localization
\cite{JoyceSong,JoyceUpmeier}.

\subsubsection*{The reduced determinant complex}

For an object $\mathcal C$ in the chosen finite stage, write
\[
K^{\mathrm{red}}_{\mathcal C}
=\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C),
\]
the cosection-reduced self-Ext complex.  The reduced orientation line
is supplied with a chosen square root,
\[
o_{\mathcal C}\in\operatorname{Pic}(\mathfrak M^{\mathrm{or}}_X),
\qquad
o_{\mathcal C}^{\otimes 2}\simeq\det K^{\mathrm{red}}_{\mathcal C},
\]
in the sense of \cite{JoyceUpmeier}, and is multiplicative under the
reduced extension correspondences:
$o_{\mathcal C\oplus\mathcal C'}\simeq
o_{\mathcal C}\otimes o_{\mathcal C'}$ compatibly with the Hall
additivity above.  This is the data on which Thom--Sebastiani
transport is supplied for the vanishing-cycle coefficient sheaves.

\subsubsection*{(O1) Strong reduced orientation through the
quotient-orientation tower}

The compact Hall product on $X=K3\times E$ is built only after the
reduced $E$-quotient.  The orientation line must descend through this
quotient, and descent is detected by a tower of mod-$2$
Borel-equivariant gerbes.  For a charge stratum $\mathcal C$:

\begin{enumerate}
\item the reduced gerbe class
\[
\alpha^{\mathrm{red}}_{\mathcal C}
=w_2(\det K^{\mathrm{red}}_{\mathcal C})
+\mathrm{cs}^{*}w_2(\det\operatorname{coker}\mathrm{cs})
\in H^2(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2);
\]
\item the free $E$-class
\[
\alpha^{E,\mathrm{free}}_{\mathcal C}
=a_1(\mathcal C)u_1+a_2(\mathcal C)u_2
\in H^2(BE;\mathbb F_2);
\]
\item for each finite-stabilizer stratum $S$ with stabilizer
$H\subset E_{\mathrm{tors}}$, the equivariant class
$\widetilde\beta^{H}_{\mathcal C,S}\in H^2_H(S;\mathbb F_2)$, whose
point-stabilizer restriction $\beta^H_{\mathcal C,S}\in H^2(BH;\mathbb F_2)$
is read only after the mixed Borel terms, the stabilizer action on
$H^\bullet(S;\mathbb F_2)$, and the spectral-sequence differentials
have vanished.
\end{enumerate}

\begin{definition}[(O1) Strong multiplicative reduced orientation]
\label{def:O1-strong-reduced-orientation}
The (O1) datum at finite HN height $R$ consists of:
the reduced orientation line $o_{\mathcal C}$ with chosen square root;
its multiplicativity under reduced extension correspondences with
chosen Thom--Sebastiani transport;
null-trivializations of $\alpha^{\mathrm{red}}_{\mathcal C}$,
$\alpha^{E,\mathrm{free}}_{\mathcal C}$,
$\widetilde\beta^{H}_{\mathcal C,S}$ and
$\beta^{H}_{\mathcal C,S}$ on every charge stratum
used by the Hall correspondences;
and a choice of zero $H^1(BH;\mathbb F_2)$-linearization character
$\lambda^{H}_{\mathcal C,S}=0$ for each finite stabilizer.

The full-level specialization at $H=E[2]$ is the Klein-four condition
\[
\beta^{E,2}_{\mathcal C,S}
=b_{20}x_1^2+b_{11}x_1x_2+b_{02}x_2^2,
\quad
(b_{20},b_{11},b_{02})=(r_1,r_1+r_2+r_3,r_2),
\]
\[
\operatorname{res}_{\langle e_i\rangle}\beta^{E,2}_{\mathcal C,S}
=r_i\tau_i^2,
\]
with vanishing $r_1=r_2=r_3=0$ on every retained two-torsion
stratum.  For full-level $H=E[N]$ with $2^a\parallel N$, $a\ge2$, the
two-primary residual takes value in
$H^2(B(\Z/2^a)^2;\mathbb F_2)=\mathbb F_2\langle y_1,x_1x_2,y_2\rangle$
and contains the mixed coefficient $A_{12}^{(N)}$ \emph{not} detected
by cyclic restrictions.
\end{definition}

(O1) is therefore not a single Picard-line assertion: it is the
ordinary square root, the null-trivialization of the reduced and
equivariant degree-two gerbes, and the choice of zero degree-one
linearization characters for the actual finite stabilizers.  At
finite HN height this is the cocycle system of
\cite{JoyceUpmeier} restricted to $K3\times E$.

\subsubsection*{(O1)$^+$ Weyl-equivariant transport along
$W^{(2)}(\Lambda_{II}^{2,1})$}

The orientation gerbe descends through the reduced $E$-quotient, but
the Igusa structure also requires it to be compatible with the Weyl
group of the BKM target.  For each of the three type-II simple
reflections $s_{\delta_i}$ ($i=1,2,3$), the $K3\times E$ side carries
a wall transport
\[
\tau_i:o_{\mathcal C}\longrightarrow s_{\delta_i}^{*}o_{\mathcal C}.
\]
The word \emph{coherent} is load-bearing.  At finite height, the
first object is the finite partial action groupoid $\mathcal G_R$
whose objects are retained oriented quotient strata and whose arrows
are the retained type-II wall transports; a choice of
determinant-line lifts gives a $2$-cocycle
$c_{o,R}\in Z^2(\mathcal G_R;\underline{\mathbb F}_2)$.  Only on a
complete $W^{(2)}(\Lambda_{II}^{2,1})$-orbit with constant
coefficients does this reduce to the group cohomology class
\[
[c_o]\in H^2\bigl(W^{(2)}(\Lambda_{II}^{2,1});\mathbb F_2\bigr).
\]

\begin{definition}[(O1)$^+$ Weyl-equivariant determinant-line
transport]
\label{def:O1-plus-weyl-transport}
The (O1)$^+$ datum is the supplied set of lifts $\{\tau_i\}$
satisfying $[c_o]=0$ with chosen $1$-cochain killing $c_o$, the
normalization $\tau_i^2=1$, and the transport of the
quotient-orientation package
\[
\mathfrak q_{\mathcal C}=\bigl(\alpha^{\mathrm{red}}_{\mathcal C},
\alpha^{E,\mathrm{free}}_{\mathcal C},
\{(\beta^H_{\mathcal C},\lambda^H_{\mathcal C})\}_{H\in
\mathcal H(\mathcal C)}\bigr)
\]
along $\tau_i$ between charge strata over Weyl-related Gram degrees.
The torsor defect of this transport is
\[
\omega_{i,\mathcal C}\in
H^1(\mathfrak M^{\mathrm{red}}_{s_{\delta_i}\mathcal C};\mathbb F_2)
\oplus
\bigoplus_{H\in\mathcal H(\mathcal C)}H^1(BH;\mathbb F_2),
\]
required to vanish.  The Coxeter presentation of
$W^{(2)}(\Lambda_{II}^{2,1})$ then promotes these lifts to an honest
action on the oriented Pfaffian line over the wall-complement of the
reduced compact Hall sector.
\end{definition}

(O1)$^+$ is a determinant-line monodromy datum.  No scalar formula
enters; the transports must move the entire null-trivialization
package, not only the underlying line.  The (O1)$^+$ ledger comprises
$[c_o]=0$, the chosen cochain, the unitarity $\tau_i^2=1$, and the
torsor vanishing $\omega_{i,\mathcal C}=0$ on every retained orbit.

\subsubsection*{Cosection localization and the cosection-reduced
heart}

The K3 semiregularity cosection $\operatorname{CS}_{\mathcal C}$
selects a reduced obstruction theory; the corresponding Behrend
constructible function $\nu^{\mathrm{red}}$ produces the reduced
vanishing-cycle complex $\Phi^{\mathrm{red}}$ used in the Hall
product \cite{BEHREND,JoyceSong}.  The filtered Hall additivity
$q^*\operatorname{CS}_C=p_1^*\operatorname{CS}_A+p_2^*\operatorname{CS}_B$
on extension stacks is the cosection-localization compatibility
required by the Hall correspondence; the Joyce--Upmeier
orientation lines are required to be Thom--Sebastiani-coherent on
the resulting two-step and four-input flag stacks.

\begin{proposition}[Finite d-critical Hall product;
\textit{conditional on the (O1) and atlas data}]
\label{prop:finite-dcritical-hall-product}
Fix $R$ and closed-configuration substacks
$\mathfrak M_{c,R,I}^{\mathrm{loc,cl}}$ in a noetherian abelian Hall
heart, and assume:
\begin{enumerate}
\item finite-type quasi-smooth derived Artin enhancements of the
selected object, extension, and two-step flag stacks, with perfect
obstruction theories;
\item finite residual inertia after scalar, $E$-translation, and
wrapped rigidifications;
\item finite-type extension and flag stacks with admissible $p^*$
and $q_!$;
\item PTVV $(-1)$-shifted symplectic structures restricting to these
substacks, classical truncations carrying Joyce d-critical
structures \cite{PTVV2013,BBDJS2015};
\item surjective K3 semiregularity cosections with filtered Hall
additivity;
\item Joyce--Upmeier orientation lines and orientation transports
\cite{JoyceUpmeier} with all finite-stabilizer characters
trivialized;
\item Thom--Sebastiani transport for the reduced vanishing-cycle
sheaves satisfying two-step flag pentagons and higher coloured
configuration coherences.
\end{enumerate}
Then the finite reduced local-local product
\[
m_R^{\mathrm{red}}=q_!\circ\operatorname{TS}^{\mathrm{red}}_R\circ p^*
\]
is an honest morphism on
$H_c^{\bullet}(\mathfrak M_{c,R,I}^{\mathrm{loc,cl}},
\Phi_{c,R,I}^{\mathrm{red}}\otimes o_{c,R,I}^{\mathrm{red}})$
and is associative on the finite stage.
\end{proposition}

The first obstruction to removing these hypotheses is finite inertia:
proper finite-type correspondences do not by themselves eliminate
residual $\mathbb G_m$, direct-sum, or parabolic automorphisms, and a
residual $\mathbb G_m$ already contributes
$H^\bullet(B\mathbb G_m)=\C[u]$ to protected cohomology.  The phrase
\emph{finite stage} here means finite charge support, finite-type
stacks, and finite-dimensional protected cohomology after the stated
quotients and admissibility hypotheses; it does not mean that the
Hall correspondence morphisms are themselves finite morphisms.

\subsubsection*{Quotient-after-correspondence ordering}

The $E$-quotient is taken \emph{after} the extension correspondences,
not before.  A pseudofunctor
$\mathsf{Corr}^{E,\mathrm{hyb}}_R\to
\mathsf{Corr}^{\mathrm{red},\mathrm{hyb}}_R$ supplies the descent;
applying the vanishing-cycle Borel--Moore functor with orientation
lines included gives $Q_{E,R}$ between the corresponding finite
correspondence module categories.  For each operation
$\mu_R^\bullet=q_!\operatorname{TS}p^*$ a chosen comparison
isomorphism
\[
\theta^Q_{\mu,R}:Q_{E,R}\,q_!\operatorname{TS}p^*
\xrightarrow{\sim}
\overline q_!\overline{\operatorname{TS}}\,\overline p^*
(Q_{E,R}^{\boxtimes k})
\]
is part of the datum.  Its compatibility with the eight-word flag
$2$-morphisms and HN transitions is the (O1) descent calculus.  A
quotient-first construction (object-stack quotient followed by a new
Hall product) is not the same datum.

\subsubsection*{Status of the obstruction tuple}

The orientation lane carries the residual
\[
\mathfrak O_{\mathrm{or},R}
=\bigl(
\mathfrak o^{\mathrm{red}}_{\mathcal C},
\mathfrak o^{E,\mathrm{free}}_{\mathcal C},
\{\mathfrak o^{H}_{\mathcal C,S}\}_{H,S},
\{\mathfrak o^{\lambda^H}_{\mathcal C,S}\}_{H,S},
[c_o]_R,\,\xi_{c_o,R},\,
\{\mathfrak o^{\tau,2}_{i,R}\}_i,\,
\{\omega_{i,\mathcal C,R}\}_i\bigr)
\]
required to vanish at every finite HN height, with chosen
null-trivializations.  Probes A074, A076, A082 audit the (O1) tower;
probes A047, A049, A089 audit (O1)$^+$.  Discharge of (O1) under
$K3\times E$-specific finite-stabilizer hypotheses is open in
generality; the K3-fibrewise framework of
\cite{JoyceSong,JoyceUpmeier} reduces (O1) on the projection-finite
stratum to the finite-stabilizer linearization choice and the mixed
Borel computation, and the wrapped stratum is the open piece tracked
by the Hall--Borcherds residual in the parallel Vol II constellation.

\subsubsection*{Cross-repo anchor}

Vol III's Calabi--Yau quantum-groups stratification observes that
$K3\times E$ admits no global non-commutative crepant resolution, so
the orientation lane cannot be supplied by a global NCCR-induced
heart; the cosection-twisted reduced d-critical structure is forced
on the chosen Bridgeland heart instead.  The displayed Borel
calculation at $E[2]$ is the smallest finite stabilizer detected by
the cosection-reduced determinant; even $N\ge4$ stabilizers carry the
mixed coefficient $A_{12}^{(N)}$, which the displayed cyclic
restrictions miss, and which (O1) requires to be null-trivialized as
part of the full degree-two gerbe.

The orientation $o_R$ trivializes the Joyce--Upmeier obstruction to
a compatible Hall product on the cosection-twisted heart.  Once
$o_R$ is in place, the Hall product, the collision coproduct, and
the protected primitive extraction are unambiguous.  Entry
$(\mathrm L 3)$ is the Hall apparatus of
\S\ref{subsec:hall-correspondences}.
