\subsection{Hall correspondences: product, coproduct, primitives}
\label{subsec:hall-correspondences}

The third entry of the Dirac--Igusa pro-object is the Hall structure
on the cosection-reduced d-critical heart.  It is the algebraic
content that the orientation lane equips and the hybrid carrier
indexes.  Three operations live here: the Hall product
$m_R^{\mathrm{red}}$, the collision coproduct $\Delta_R^{\mathrm{ch}}$,
and the primitive projection $P_R^{\Prim}$.  After normal-ordered
Gram descent these form a graded Hopf datum on the protected
primitive layer; recognition of this Hopf datum with the
Borcherds--Kac--Moody target is the §5.6 obligation.

The Kontsevich--Soibelman cohomological Hall algebra of a
$3$-Calabi--Yau category \cite{KSCoHA} is the prototype; on
$K3\times E$ the cosection reduction \cite{JoyceSong,JoyceUpmeier}
replaces the unreduced critical CoHA, and the wrapped sector is the
residual the hybrid carrier of \S\ref{subsec:hybrid-ran-carrier}
retains.  The Maulik--Okounkov stable-envelope construction and the
Schiffmann--Vasserot theorems on Drinfeld doubles of CoHA operate
on the same input; their integral form is the Hall side of the
present construction.

\subsubsection*{The compact Hall product}

\begin{definition}[Compact Hall product on the cosection-reduced
heart]
\label{def:compact-hall-product}
Let $\mathcal C_{\sigma,S,\le R}$ be the finite HN quotient of
\S\ref{subsec:hybrid-ran-carrier}.  The compact Hall product at
height $R$ is the operation
\[
m_R^{\mathrm{red}}=
q_{c,c'}{}_!\circ\operatorname{TS}^{\mathrm{red}}_{c,c'}\circ p_{c,c'}^*:
H_*^{\mathrm{BM}}\!\bigl(\mathfrak M_c^\sigma\times\mathfrak M_{c'}^\sigma,
\Phi_c^{\mathrm{red}}\boxtimes\Phi_{c'}^{\mathrm{red}}
\otimes o_c\boxtimes o_{c'}\bigr)
\to
H_*^{\mathrm{BM}}\!\bigl(\mathfrak M_{c+c'}^\sigma,
\Phi_{c+c'}^{\mathrm{red}}\otimes o_{c+c'}\bigr)
\]
attached to the extension correspondence
\[
\mathfrak M_c^\sigma\times\mathfrak M_{c'}^\sigma
\xleftarrow{p_{c,c'}}\mathfrak E_{c,c'}^\sigma
\xrightarrow{q_{c,c'}}\mathfrak M_{c+c'}^\sigma,
\]
in the cosection-reduced d-critical heart, with vanishing-cycle
coefficients $\Phi^{\mathrm{red}}$, Joyce--Upmeier orientation lines
$o$, and Thom--Sebastiani transport
$\operatorname{TS}^{\mathrm{red}}_{c,c'}$.  Associativity on the
finite stage is the eight-word two-step binary flag pentagon of
\S\ref{subsec:hybrid-ran-carrier}, axiom (5).
\end{definition}

For local-only inputs and ordered mixed and wrapped inputs, the same
construction produces the three operation families
$\mu_R^{\mathrm{loc}}$, $\mu_R^{\mathrm{hyb}}$, $\mu_R^{\mathrm{wr}}$
of \S\ref{subsec:hybrid-ran-carrier}.  Existence of the product as a
genuine morphism on Borel--Moore chains requires the
admissibility/properness residuals of that section to vanish.

\subsubsection*{The collision coproduct on the source coalgebra}

The collision coproduct is defined on the same correspondence
geometry, read in the opposite direction: instead of contracting an
extension to a single output, one expands an object into the pairs of
its sub/quotient extensions.  At finite stage, this is the
$2$-step flag stack already supplied as part of the hybrid datum.

\begin{definition}[Collision coproduct]
\label{def:collision-coproduct}
The finite collision coproduct
\[
\Delta_R^{\mathrm{ch}}:C_{X,R}\longrightarrow C_{X,R}\otimes C_{X,R}
\]
is the chain-level pull-push along the $2$-step flag stack
$\mathfrak{Flag}^{(2)}_{c,c',R}$ of subobjects of charge $c$ and
quotients of charge $c'$ in $\mathfrak M_{c+c',R}^\sigma$, computed
in the cosection-reduced d-critical heart, before the reduced
$E$-quotient.  After $Q_{E,R}$ it satisfies the coalgebra identities
\[
(\Delta_R^{\mathrm{ch}}\otimes 1)\Delta_R^{\mathrm{ch}}
=(1\otimes\Delta_R^{\mathrm{ch}})\Delta_R^{\mathrm{ch}},
\qquad
(\varepsilon_R^C\otimes 1)\Delta_R^{\mathrm{ch}}
=(1\otimes\varepsilon_R^C)\Delta_R^{\mathrm{ch}}=\mathrm{id},
\]
which are the dual of the Hall pentagon on the same flag stack.  For
$R'\ge R$ the transition map $\rho^C_{R'R}$ commutes with
$\Delta^{\mathrm{ch}}$.
\end{definition}

This is the source coalgebra of \S\ref{subsec:koszul-source}; its
identification with the bar construction
$\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}})$ is the bar
comparison there.

\subsubsection*{Primitive projection and the Hopf datum}

The primitive projection on a graded conilpotent Hopf object is
unique once the augmentation, product, and coproduct are supplied.

\begin{definition}[Primitive Hall sub-bracket]
\label{def:primitive-hall-bracket}
Write
\[
\widetilde P_X=H^0\Prim_{\mathrm{prot}}(\mathcal F_X)
=\ker\bigl(\widetilde\Delta:
\mathcal F_X\to\mathcal F_X\otimes\mathcal F_X\bigr)
\]
for the primitive layer of the protected Hall Hopf object, where
$\widetilde\Delta=\Delta-(\eta\varepsilon\otimes\mathrm{id}+
\mathrm{id}\otimes\eta\varepsilon)$.  The Hall product restricts to
a $\widehat\Gamma_X$-graded bracket
\[
[\,\cdot\,,\,\cdot\,]_X:\widetilde P_{X,\widehat c}\otimes
\widetilde P_{X,\widehat c'}
\longrightarrow\widetilde P_{X,\widehat c\star\widehat c'},
\]
the protected primitive Hall bracket.  After normal-ordered Gram
descent (\S\ref{subsec:hybrid-ran-carrier}) and the Hopf-radical
quotient, the descended bracket is $\Gamma_{\mathrm{gram}}$-graded
and the descended primitive layer is the candidate $P_X^{\Pi,\mathrm{red}}$
to be identified with $\mathfrak g_{\Delta_5}$.
\end{definition}

\begin{lemma}[Primitive bracket lifting; \textit{conditional on the
Frobenius defect $\mathfrak o_F=0$}]
\label{lem:primitive-bracket-lifting}
Let $\langle\cdot,\cdot\rangle_X$ be the protected Hopf pairing on
$\widetilde P_X$, non-degenerate on the radical quotient.  The
trilinear Frobenius defect
\[
\mathfrak o_F(x,y,z):=\langle[x,y],z\rangle
+(-1)^{|x|\cdot|y|}\langle y,[x,z]\rangle,
\quad
x,y,z\in\widetilde P_X,\quad c_x+c_y+c_z=0,
\]
viewed as a class in
$C^3_{\mathrm{cyc}}(\widetilde P_X;k)$ after the reduced $E$-quotient
and radical quotient, vanishes precisely when the bracket is
graded-symmetric for the Hopf pairing.  Vanishing is the cyclic-CY-3
Serre-functor identity of
Lemma~\ref{thm:hall-product}.  Non-degeneracy of the
Hopf pairing alone does \emph{not} force $\mathfrak o_F=0$; it only
detects the vanishing once supplied.
\end{lemma}

\begin{lemma}[Hopf radical is a Lie ideal and a coideal;
\textit{conditional on $\mathfrak o_F=0$ and Hopf adjointness}]
\label{lem:hopf-radical-ideal-coideal}
Let $P_R^\Pi$ be a finite normal-ordered primitive stage with
transported product $m_R^\Theta$, coproduct $\Delta_R^\Theta$, graded
symmetric Hopf pairing $\langle\cdot,\cdot\rangle_R$, and radical
$\operatorname{Rad}_R^\Pi$.  Assume Hopf adjointness
$\langle m_R^\Theta(x,y),z\rangle_R
=\langle x\otimes y,\Delta_R^\Theta z\rangle_R$
and non-degeneracy on
$P_R^\Pi/\operatorname{Rad}_R^\Pi\otimes
P_R^\Pi/\operatorname{Rad}_R^\Pi$.  Then
\[
(\bar q_{\Pi,R}\otimes\bar q_{\Pi,R})\Delta_R^\Theta(r)=0
\quad(r\in\operatorname{Rad}_R^\Pi),
\]
i.e.\ $\operatorname{Rad}_R^\Pi$ is a coideal.  If, in addition,
$\mathfrak o_{F,R}=0$, then $\operatorname{Rad}_R^\Pi$ is a Lie
ideal.
\end{lemma}

\begin{proof}
For $r\in\operatorname{Rad}_R^\Pi$ and $x,y\in P_R^\Pi$, Hopf
adjointness gives
$\langle x\otimes y,\Delta_R^\Theta(r)\rangle_R
=\langle m_R^\Theta(x,y),r\rangle_R=0$;
non-degeneracy of the quotient tensor pairing then kills the class.
The Lie-ideal half is direct: if $\mathfrak o_{F,R}=0$ then
$\langle[x,r]_\Theta,z\rangle_R
=-(-1)^{|x||r|}\langle r,[x,z]_\Theta\rangle_R=0$ for every $z$,
so $[x,r]_\Theta\in\operatorname{Rad}_R^\Pi$.
\end{proof}

\subsubsection*{Integral form and stable-envelope transport}

Two parallel constructions act on the same compact Hall heart:
\begin{enumerate}
\item the integral form of the Schiffmann--Vasserot
elliptic Hall algebra, whose $K3\times E$-specialization carries the
Maulik--Okounkov stable envelope;
\item the Drinfeld double $\mathcal D_\hbar(\textup{CoHA}_{K3\times E})$
of Vol III, whose positive half is the protected primitive Hopf
algebra above and whose Drinfeld pairing is the Hopf pairing.
\end{enumerate}
The compatibility datum between these two constructions is part of
the cross-repo consistency check between this manuscript and the
Calabi--Yau quantum-groups constellation.  Disagreement on a
load-bearing constant or sign is the deliverable; the Drinfeld
double is not asserted here as a black box.

\subsubsection*{Conilpotent source coalgebra and Hopf radical
quotient}

\begin{definition}[Conilpotent source coalgebra]
\label{def:conilpotent-source-coalgebra}
At finite stage, $C_{X,R}$ is the conilpotent chiral coalgebra on
$E$ obtained from the collision coproduct on $\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}$
after the reduced $E$-quotient: it is filtered by a finite increasing
source charge filtration
\[
0=F^{\mathrm{co}}_{R,-1}\subset F^{\mathrm{co}}_{R,0}\subset
\cdots\subset F^{\mathrm{co}}_{R,N_R}=C_{X,R}
\]
whose associated graded pieces are finite dimensional in each
$\Gamma_R^\Pi$-degree, and whose reduced iterated coproduct is
nilpotent on each finite stage.  Conilpotence is recorded by the
defect $(\overline\Delta_R^{\mathrm{ch}})^{N_R+1}$, required to
vanish.  Inverse-limit completion gives the source coalgebra
$C_X=\varprojlim_R C_{X,R}$.
\end{definition}

\begin{proposition}[Sectorial Hall truncation and inverse limit;
\textit{conditional on
$[\textup{K3$\times$E-fin}]$, $[\textup{K3$\times$E-atlas}]$,
and $[\textup{ML}]$}]
\label{prop:sectorial-hall-truncation}
Under the three standing hypotheses
$[\textup{K3$\times$E-fin}]$ (finite-type semistable
substacks at bounded HN height),
$[\textup{K3$\times$E-atlas}]$ (finite d-critical/cosection
Hall atlas with Joyce--Upmeier orientation lines), and
$[\textup{ML}]$ (Mittag--Leffler descent for the HN inverse system),
the finite Hall product, coproduct, primitive projection, and Hopf
pairing are compatible with the transition maps $\rho_{R'R}$, and
their inverse limits define the completed Hall Hopf datum
$\widetilde P_X$, $C_X$.  The Mittag--Leffler hypothesis controls
the $R^1\varprojlim$ obstruction on every finite-window slice; without
it, only a compatible pro-object is obtained.
\end{proposition}

The hypothesis $[\textup{K3$\times$E-fin}]$ is not a
consequence of fibrewise K3 boundedness alone.  A precise sufficient
input is product-stability boundedness in the
Abramovich--Polishchuk/Liu sense
\cite{AbramovichPolishchukTStructures,LiuProductStability}: for a
rational K3 stability condition $\sigma_S=(\mathcal A_S,Z_S)$ and
Liu's product stability $\sigma_{s,t}$ on
$D^b(\operatorname{Coh}(S\times E))$, fixed-class boundedness
\[
\mathfrak M^{ss}_{\sigma_{s,t}}(\gamma)\text{ is finite type over }\C
\]
together with Liu's support property would imply
$[\textup{K3$\times$E-fin}]$ for bounded $h_S$-windows.
Piyaratne--Toda boundedness for threefold Bridgeland/BMT
\cite{PiyaratneTodaModuli3folds} does not automatically supply this
theorem; fibrewise Bayer--Macri boundedness alone does not either.

\subsubsection*{Wall-crossing and chamber dependence}

The lattice cocycle $B(c,c')$ of the dyonic Mukai construction is
chamber-independent.  The compact Hall side $D_0(X;\sigma,S)$ is
chamber-dependent: finite-type semistable substacks change under
wall-crossing, and the Kontsevich--Soibelman wall-crossing formula
\cite{KSCoHA} relates Hall counts in adjacent chambers.  If the
datum $D_0(X;\sigma,S)$ is supplied in chamber $\sigma$, then
$\overline\Pi_X$ remains a homomorphism and the recognition target
is $\mathfrak g_{\Delta_5}$ provided the chamber identifications hold
for the OP/DT scalar import; that the chosen $\sigma$ lies in the
OP/DT chamber, or that the wall-crossing transport is compatible
with $\overline\Pi_X$, is a separate conjectural input.  No
chamber-independence of the recognition target is asserted.

\subsubsection*{Status under the obstruction tuple}

The Hall lane carries the residuals
\[
\mathfrak O_{\mathrm{Hall},R}
=(\mathfrak o^{\mathrm{stage}}_R,\,
\mathfrak o^{\mathrm{conf}}_R,\,
\mathfrak o^{\mathrm{prop}}_R,\,
\mathfrak o^{\mathrm{TS}}_R,\,
\mathfrak o^{\mathrm{assoc}}_R,\,
\mathfrak o_{F,R},\,
\mathfrak o^{\mathrm{coid}}_R,\,
\mathfrak o^{\mathrm{ML}}_{R'R}).
\]
Discharge of the wrapped product on the projection-finite stratum is
classical d-critical CoHA after cosection reduction; on the wrapped
stratum the construction is open and tracked by the (D0)
obstruction.  Hopf adjointness, Frobenius vanishing, and PBW
compatibility are independent constructions on the descended primitive
layer.

\subsubsection*{Cross-repo anchor}

Vol III's Drinfeld doubling $Y^+(X)\to G(X)$ produces the BKM target
of the present manuscript on the source side; the integral form is
the chiral lift of the Schiffmann--Vasserot elliptic Hall algebra.
Maulik--Okounkov stable-envelope transport supplies the integral
form on the projection-finite Ran stratum; the wrapped stratum is
the stratum-completion that this manuscript and the chiral-bar-cobar
volumes reconstruct.  No black-box equality $\mathrm{CoHA}=W_\infty$
is asserted: $\mathrm{CoHA}(\C^3)=Y^+(\mathfrak{gl}_1)$ in Vol III,
and $W_{1+\infty}$ appears only after Drinfeld doubling, centre,
vacuum evaluation.  The same discipline applies here: the protected
primitive Hopf algebra of $K3\times E$ becomes the BKM target only
after the Hopf radical quotient, the Frobenius identity, and the
no-extra-relations theorem of \S\ref{subsec:primitive-recognition}.

The Hall correspondences produce a protected primitive Hopf algebra
on the cosection-twisted heart, but they live at the operator level
and have no automatic comparison to the scalar denominator
$\mathrm{den}(\autcor)=64^{-1}\Delta_5(2Z)$ imported in
Chapter~\ref{ch:view2-bkm}.  Closing the cross-level identity
\textcircled{2}$\leftrightarrow$\textcircled{3} requires a chain-level
scalar incarnation of the primitive structure: a Pfaffian line
$\mathscr L_{\mathrm{Pf},R}$ on the reduced moduli, a Dirac block
decomposition, and a first-order Pfaffian section whose
$\Sp_4(\Z)$-pullback recovers $\Delta_5$.  This is the fourth entry
$(\mathrm L 4)$, constructed in \S\ref{subsec:dirac-pfaffian}.
