\subsection{Koszul source coalgebra and chiral MC twisting}
\label{subsec:koszul-source}

The fifth entry of the Dirac--Igusa pro-object is the Koszul lane:
the source coalgebra $C_X$, the bar comparison $b_X$, and the cobar
quasi-isomorphism $\Theta_{\mathrm{Kos}}$ to the imported current
envelope $\mathsf{Den}_{\Delta_5,E}$.  Source--target separation is
load-bearing.  The target counit
\[
\varepsilon_{\Delta,R}:
\Omega_E^{\mathrm{ch}}\bar B_E^{\mathrm{ch}}
(\mathsf{Den}_{\Delta_5,E,\le R})
\longrightarrow
\mathsf{Den}_{\Delta_5,E,\le R}
\]
is internal to the imported denominator current envelope and produces
no source data.  The compact Koszul comparison
$\Omega_E^{\mathrm{ch}}C_X\simeq\mathsf{Den}_{\Delta_5,E}$ is a
source-to-target theorem on the supplied hybrid source, conditional
on the named obstructions.

The Beilinson cut applies in its purest form on this lane.  $\bar
B^{\mathrm{ch}}$ is MC twisting / coupling coalgebra; it is not the
bulk.  The bulk is $\mathsf{Den}_{\Delta_5,E}$ itself, the chiral
shadow of the BKM denominator algebra; the source coalgebra $C_X$ is
the supplied compact Hall data after collision coproduct, conilpotent
filtration, and bar-length truncation, and the cobar map is the
comparison.

\subsubsection*{Source--target separation}

\begin{lemma}[Source--target separation for the Koszul lane;
\textit{proved}]
\label{lem:source-target-koszul-separation}
Fix a finite height $R$.  The target counit
$\varepsilon_{\Delta,R}$ above is a morphism internal to the imported
current envelope.  A source Koszul datum is different data: it must
first construct
\[
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},\qquad
C_{X,R},\qquad F^{\mathrm{co}}_{R,\bullet},\qquad
\Delta_R^{\mathrm{ch}}
\]
from the finite hybrid correspondence category
$\mathsf{Corr}^{E,\mathrm{hyb}}_R$, its quotient functor $Q_{E,R}$,
orientations, the eight-word two-step binary flag atlas, and the
separate higher coloured configuration residual; only then may it
compare
\[
b_{X,R}:C_{X,R}\simeq
\bar B_E^{\mathrm{ch}}\bigl(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
\varepsilon_{X,R}^{\mathrm{hyb}}\bigr),
\quad
\Theta_{\mathrm{Kos},R}:\Omega_E^{\mathrm{ch}}C_{X,R}\simeq
\mathsf{Den}_{\Delta_5,E,\le R}.
\]
Setting $C_{X,R}=\bar B_E^{\mathrm{ch}}(\mathsf{Den}_{\Delta_5,E,\le R})$,
or choosing a homotopy inverse to $\varepsilon_{\Delta,R}$, does not
produce a source datum.
\end{lemma}

\begin{proof}
The domain of $\varepsilon_{\Delta,R}$ contains only target
augmentation, target charge filtration, and target chiral
operations; it does not contain rigidified wrapped prequotients,
anchors, mixed local/wrapped correspondences,
quotient-after-correspondence functor, orientation transport,
protected integration, or primitive representatives.  These are the
data from which the source coalgebra and collision coproduct are
required to be built.
\end{proof}

\subsubsection*{Chiral Koszul source datum}

\begin{definition}[Chiral Koszul source datum]
\label{def:chiral-koszul-source-datum}
Fix $(\sigma,S,R)$ and the Gram image $\Gamma_R^\Pi$.  A finite-stage
chiral Koszul source datum is
\[
\mathfrak K^{\mathrm{Kos}}_{X,R}
=\bigl(
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
C_{X,R},
F^{\mathrm{co}}_{R,\bullet},
\Delta_R^{\mathrm{ch}},
b_{X,R},
\Theta_{\mathrm{Kos},R}\bigr)
\]
with the following clauses; every entry is source-side finite data
except for the terminal comparison with the imported target.
\begin{enumerate}
\item \emph{Source chiral object.}  $\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}$
is the finite hybrid object of \S\ref{subsec:hybrid-ran-carrier},
with $\mathfrak O_{\mathrm{hyb},R}=0$.
\item \emph{Conilpotent chiral coalgebra.}  $C_{X,R}$ is a coaugmented
conilpotent chiral coalgebra on $E$, filtered by a finite increasing
source charge filtration $F^{\mathrm{co}}_{R,\bullet}$; reduced iterated
coproduct nilpotent on each finite stage.
\item \emph{Collision coproduct.}  $\Delta_R^{\mathrm{ch}}$ is the
collision coproduct from the finite Hall correspondences (local-local,
ordered local-wrapped, wrapped-wrapped, and eight-word flag stacks),
defined before $Q_{E,R}$; after quotient it satisfies coassociativity
and counitality.  Transition maps $\rho^C_{R'R}$ commute with
$\Delta^{\mathrm{ch}}$.
\item \emph{Bar comparison.}  $b_{X,R}:C_{X,R}\simeq
\bar B_E^{\mathrm{ch}}(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
\varepsilon_{X,R}^{\mathrm{hyb}})$
is a charge-preserving quasi-isomorphism of conilpotent chiral
coalgebras compatible with primitive projection, the completed Hopf
pairing, the reduced $E$-quotient, and the normal-ordered descent
$\overline\Pi_{X,*}^\Theta$.
\item \emph{Cobar comparison with the target envelope.}
$\Theta_{\mathrm{Kos},R}:\Omega_E^{\mathrm{ch}}C_{X,R}\simeq
\mathsf{Den}_{\Delta_5,E,\le R}$
is a charge-preserving quasi-isomorphism of augmented chiral
algebras.  Restricted to constant-current primitives after the
Hopf-radical quotient it gives the primitive recognition morphism
\[
\iota_R^{\Prim}:H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^\Theta
\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}})
\longrightarrow\mathfrak g_{\Delta_5,\le R}.
\]
\end{enumerate}
The exact finite Koszul obstruction tuple is
\[
\mathfrak O_{\mathrm{Kos},R}
=(\mathfrak o^C_R,\mathfrak o^{\mathrm{fil}}_R,
\mathfrak o^{\mathrm{conil}}_R,
\mathfrak o^{\Delta,\mathrm{ch}}_R,
\{\mathfrak o^{C,\mathrm{tr}}_{R'R}\}_{R'\ge R},
\mathfrak o^b_R,\mathfrak o^\Omega_R,
\mathfrak o^{\mathrm{hyb}}_R,
\mathfrak o^\Pi_R,
\mathfrak o^{\mathrm{sep}}_R,
\mathfrak o^{\Prim}_R).
\]
\end{definition}

\subsubsection*{Canonical finite source-bar coalgebra}

For a hybrid source with bounded-length augmentation ideal, a
canonical model exists.

\begin{proposition}[Canonical finite source-bar coalgebra;
\textit{conditional on $\mathfrak O_{\mathrm{hyb},R}=0$ and bounded
length}]
\label{prop:canonical-source-bar-coalgebra}
Suppose $\mathfrak O_{\mathrm{hyb},R}=0$ and there is an integer $N_R$
such that every nonzero ordered word of non-vacuum hybrid inputs of
total HN height $\le R$ has length at most $N_R$, with HN height
positive on every non-vacuum colour surviving in the reduced bar
construction.  Suppose an augmentation
$\varepsilon_{X,R}^{\mathrm{hyb}}:\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}\to k\mathbf 1$
is supplied.  Then the canonical source-bar coalgebra
\[
C^{\mathrm{bar}}_{X,R}
=\bar B_E^{\mathrm{ch}}\bigl(\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}},
\varepsilon_{X,R}^{\mathrm{hyb}}\bigr)
=k\mathbf 1\oplus\bigoplus_{1\le p\le N_R}
\bar B^{\mathrm{ch},p}_E(\overline{\mathcal F}_{X,R}),
\]
filtered by bar-length, with deconcatenation collision coproduct
\[
\Delta_R^{\mathrm{bar}}([x_1|\cdots|x_p])=
\mathbf 1\otimes[x_1|\cdots|x_p]
+[x_1|\cdots|x_p]\otimes\mathbf 1
+\sum_{i=1}^{p-1}[x_1|\cdots|x_i]\otimes[x_{i+1}|\cdots|x_p],
\]
realizes a chiral Koszul source datum with
$\mathfrak o^C_R=\mathfrak o^{\mathrm{fil}}_R=
\mathfrak o^{\mathrm{conil}}_R=\mathfrak o^{\Delta,\mathrm{ch}}_R=0$
and $b_{X,R}=\mathrm{id}$.
\end{proposition}

\begin{proof}
Apply the Beilinson--Drinfeld chiral bar construction
\cite[\S3.7]{BD} to the supplied hybrid object.  Since the finite HN
quotient kills charges of height $>R$ and non-vacuum words have
length $\le N_R$, only finitely many bar lengths occur.  The
deconcatenation coproduct on each ordered word is realized by
cutting the corresponding ordered collision flag in
$\mathsf{Corr}^{E,\mathrm{hyb}}_R$; admissibility of pull-push and
Thom--Sebastiani transport are part of $\mathfrak O_{\mathrm{hyb},R}=0$.
The eight-word flag pentagon and four-input pentagon are
coassociativity; vacuum collision flags are counitality.  After at
most $p\le N_R$ reduced iterations, every branch has length one and
the next reduced coproduct is zero, so $(\overline\Delta_R^{\mathrm{bar}})^{N_R+1}=0$.
\end{proof}

\subsubsection*{Remaining cobar obstruction}

The bar coalgebra is supplied; the cobar map is not.  Two
independent residuals remain.

\begin{corollary}[Remaining source-to-target cobar obstruction;
\textit{proved}]
\label{cor:source-bar-remaining-cobar-obstruction}
Under the hypotheses of
Proposition~\ref{prop:canonical-source-bar-coalgebra}, a cobar
quasi-isomorphism $\Theta_{\mathrm{Kos},R}$ requires:
\begin{enumerate}
\item \emph{Source-internal bar-cobar counit.}  The supplied hybrid
source must lie in the Beilinson--Drinfeld/Francis--Gaitsgory
bar-cobar domain \cite[Theorem~6.2.2]{FrancisGaitsgoryCKD}, with the
source-internal counit
\[
\varepsilon^{\mathrm{src}}_{\mathrm{bar},R}:
\Omega_E^{\mathrm{ch}}C^{\mathrm{bar}}_{X,R}
\longrightarrow\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\]
a quasi-isomorphism in the chosen completed/coderived conilpotent
category.  Defects:
$\mathfrak o^{\varepsilon,\mathrm{src}}_R=
(\mathfrak o^{\mathrm{aug}}_R,\mathfrak o^{\mathrm{FG}}_R,
H^\bullet\operatorname{Cone}\varepsilon^{\mathrm{src}}_{\mathrm{bar},R})$.
\item \emph{Source-to-target chiral algebra quasi-isomorphism.}
$\vartheta_R:\mathcal F_{X,\sigma,S,\le R}^{\mathrm{hyb}}
\xrightarrow{\simeq}\mathsf{Den}_{\Delta_5,E,\le R}$
preserving differential, product, unit, transition maps, and
primitive restriction.  Defects:
\[
\mathfrak o^\vartheta_R=\bigl(d_{\Delta}\vartheta_R-\vartheta_R d_{\mathrm{hyb}},
\vartheta_R\mu_R^{\mathrm{hyb}}-\mu_{\Delta,R}(\vartheta_R\otimes\vartheta_R),
\vartheta_R\eta_R^{\mathrm{hyb}}-\eta_{\Delta,R},
\vartheta_R\circ\tau^{E,\mathrm{hyb}}_{R'R}-\pi^\Delta_{R'R}\circ\vartheta_{R'},
H^\bullet\operatorname{Cone}\vartheta_R,
\vartheta_R|_{\Prim}-\iota_R^{\Prim}\bigr).
\]
\end{enumerate}
Then $\Theta_{\mathrm{Kos},R}=\vartheta_R\circ
\varepsilon^{\mathrm{src}}_{\mathrm{bar},R}$, and the surviving cobar
residual is $\mathfrak o^\Omega_R=(\mathfrak o^{\varepsilon,\mathrm{src}}_R,
\mathfrak o^\vartheta_R)$.  No homotopy inverse to the target counit
$\varepsilon_{\Delta,R}$ enters this construction.
\end{corollary}

\subsubsection*{Class M completion and chiral Koszulness}

The bar/cobar comparison takes place in the completed ambient
category.  Class~M holds in the completed ambient: analytic
HS-sewing, coderived BV $=$ bar, weight-completed, pro-, $J$-adic.
On chain-level ordinary complexes, the chiral bar/cobar pair is the
comparison input, not the closed Koszulness theorem; chiral
Koszulness in the homotopy setting is a separate theorem of
Francis--Gaitsgory \cite{FrancisGaitsgoryCKD}.

\subsubsection*{Koszul Mittag--Leffler exactness}

The completed bar/cobar inverse system is controlled by a
finite-slice Mittag--Leffler condition on every relevant tower.

\begin{proposition}[Consequence of the chiral Koszul source datum;
\textit{conditional on Koszul Mittag--Leffler}]
\label{prop:chiral-koszul-source-datum-consequence}
Assume $\mathfrak K^{\mathrm{Kos}}_{X,R}$ is supplied for all $R$ with
compatible transition maps and
$\mathfrak o^{C,\mathrm{tr}}_{R'R}=0$, and that the Koszul
Mittag--Leffler condition holds: $R^1\varprojlim=0$ for the inverse
systems of source coalgebras, completed chiral bar/cobar
constructions, target truncations, and the cones of $b_{X,R}$ and
$\Theta_{\mathrm{Kos},R}$ \cite[\S3.5]{WeibelHA}.  Then
$C_X=\varprojlim_R C_{X,R}$ is a completed pro-conilpotent chiral
coalgebra attached to the hybrid compact source, conilpotent on
every finite HN quotient, and the maps $b_{X,R}$ and
$\Theta_{\mathrm{Kos},R}$ induce
\[
b_X:C_X\xrightarrow{\simeq}
\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}}),
\qquad
\Theta_{\mathrm{Kos}}:\Omega_E^{\mathrm{ch}}C_X
\xrightarrow{\simeq}\mathsf{Den}_{\Delta_5,E}.
\]
This identifies the supplied source cobar algebra with the formal
target current envelope; it does not construct the $E_3$-source, the
hybrid wrapped Hall correspondences, the orientation line, the
primitive recognition data, or $C_X$ itself from the target-internal
counit.
\end{proposition}

\begin{proof}
Inverse-limit existence follows from transition compatibility, the
bounded exhaustive finite charge filtration, finite coassociative and
counital collision coproduct, and continuity hypotheses.  The
coradical filtration is finite on every $\Gamma_R^\Pi$-truncation;
the Koszul Mittag--Leffler hypothesis kills $R^1\varprojlim$ on the
cones of $b_{X,R}$ and $\Theta_{\mathrm{Kos},R}$, giving completed
quasi-isomorphisms.  Without that exactness one obtains only a
compatible pro-quasi-isomorphism.
\end{proof}

\subsubsection*{Chiral MC twisting / coupling coalgebra}

Bar is twisting; bar is not bulk.  The reduced bar coalgebra
$\bar B_E^{\mathrm{ch}}(\mathcal F_X^{\mathrm{hyb}})$ is the
Maurer--Cartan coupling coalgebra of the supplied hybrid chiral
algebra: its primitive elements are the chain-level inputs of MC
twisting in the Beilinson--Drinfeld/Francis--Gaitsgory framework,
and its grouplike completion records the homotopy-coherent twisting
data.  The bulk of the present manuscript is the imported denominator
algebra $\mathsf{Den}_{\Delta_5,E}$, equivalently the chiral
$Z^{\mathrm{der}}_{\mathrm{ch}}$ centre of the relevant
boundary algebra in the parallel chiral-bar-cobar volumes; the
Koszul comparison maps $C_X$, an instance of MC coupling, into the
target chiral algebra by the cobar construction.

\subsubsection*{Status under the obstruction tuple}

The Koszul lane carries the residuals
\[
\mathfrak O_{\mathrm{Kos},R}\quad\text{and}\quad
\mathfrak o^{\mathrm{ML},\mathrm{Kos}}_{R'R}.
\]
With $\mathfrak O_{\mathrm{hyb},R}=0$ and the canonical source-bar
construction, the coalgebra defects vanish; only the cobar residual
$\mathfrak o^\Omega_R=(\mathfrak o^{\varepsilon,\mathrm{src}}_R,
\mathfrak o^\vartheta_R)$ remains.  Discharge of the source-internal
counit and the source-to-target chiral algebra quasi-isomorphism
operates in the completed Beilinson--Drinfeld/Francis--Gaitsgory
bar-cobar domain; the Koszul Mittag--Leffler hypothesis controls the
inverse-system passage.

\subsubsection*{Cross-repo anchor}

The source--target separation is the $K3\times E$-side instance of
the Vol II Beilinson cut: bar is twisting, bar is not bulk; the
boundary algebra is $A=\mathcal F_X^{\mathrm{hyb}}$ at finite stage,
and the bulk is $Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ which receives
the cobar of the bar coalgebra after MC coupling.  Vol I master
patterns prohibit the identification of the chiral bar with the bulk
chiral algebra and require the Koszul comparison to be a separate
theorem in the homotopy setting; the same firewall is enforced
above.  The compact Koszul comparison and the chiral
Koszulness theorem are not identical; the present construction lives
on the comparison side, with chiral Koszulness in the
Francis--Gaitsgory sense as the abstract input.

$\Theta_{\mathrm{Kos},R}$ identifies the cobar of the source
coalgebra with the imported current envelope of $\autcor$.
Recognition closes the cross-level identity: it identifies the
source-side protected primitive $P_X^{\Pi,\mathrm{red}}$, extracted
from $C_X$ via the Hopf radical quotient, the Frobenius identity,
and the no-extra-relations criterion, with the Borcherds--Kac--Moody
algebra $\mathfrak g_{\Delta_5}$.  Entry $(\mathrm L 6)$ is this
recognition apparatus, in \S\ref{subsec:primitive-recognition}.
