\subsection{Primitive recognition apparatus}
\label{subsec:primitive-recognition}

The sixth entry of the Dirac--Igusa pro-object is the primitive
recognition theorem: an isomorphism of Gram-graded Lie superalgebras
\[
P_X^{\Pi,\mathrm{red}}\cong\mathfrak g_{\Delta_5}
\]
between the cosection-twisted reduced Hall primitive layer of
$K3\times E$ and the imported Borcherds--Kac--Moody denominator
algebra.  Signed superdimensions alone do not suffice for this
theorem.  The Borcherds product fixes
$\sdim P^{\Pi,\mathrm{red}}_{X,\gamma}=f(nm,l)$ for $\gamma=(n,l,m)$;
this is one integer in each degree.  A source--target identification
fixes two integers in every degree (the parity dimensions), the
relation ideal, the radical equality, the no-extra-relations theorem,
the completed PBW filtration, and the Hopf-radical coideal stability.

The counterexample-against-determinant route is the zero-bracket graded
super vector space with the same signed dimensions: identical
denominator, no Lie structure, no Hopf datum.  Recognition therefore
requires representatives, relations, pairings, kernels, and PBW data,
not numerics.

\subsubsection*{Borcherds--Cartan target datum}

The target side imports the Borcherds--Kac superdatum
$\mathscr B_{\Delta_5}=(H,I,p,\alpha_i,(\,,\,))$ of
Gritsenko--Nikulin \cite{GN,GNPartI,GNII} after the
\cite{KAC:1,BorcherdsGKM88} presentation conventions.  The Cartan is
$H=\Lambda_{II}^{2,1}\otimes\C$, the three real simple roots
$\delta_1,\delta_2,\delta_3$ form a hyperbolic triangle with Gram
matrix
\[
((\delta_i,\delta_j))_{i,j}=
\begin{pmatrix}2&-2&-2\\-2&2&-2\\-2&-2&2\end{pmatrix},
\]
and the imaginary fibres of $I\to H^*$ carry the
Gritsenko--Nikulin parity split
$\mu_{\overline 0}(a),\mu_{\overline 1}(a)$ for imaginary simple
roots.  The degree map is
\[
\alpha(n,l,m)=2nf_2-lf_3+2mf_{-2}
=n\delta_1+m\delta_2+(n+m-l)\delta_3,
\]
with $\widehat{\mathfrak F}(\mathscr B_{\Delta_5})$ the completed
free Lie superalgebra on the parity-homogeneous generators
$e_i,f_i$, $i\in I$, and $J_{\mathrm{BK}}$ the closed
Borcherds--Kac ideal generated by Cartan, Chevalley, real Serre,
orthogonality, and super sign relations.  The target denominator
algebra is
\[
G(\mathscr B_{\Delta_5})
=\widehat{\mathfrak F}(\mathscr B_{\Delta_5})/
\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}}
=\mathcal A_{\mathrm{den}}
=\mathfrak g_{\Delta_5}.
\]

\subsubsection*{Source-side data}

\begin{theorem}[Primitive recognition from finite source
representatives; \textit{conditional on (S1)--(S10)}]
\label{thm:primitive-recognition}
Let a compact Hall/factorization construction give a completed
$\widehat\Gamma_X$-graded primitive Hall Lie superalgebra
$\widetilde P_X$ and a completed Hopf pairing.  Its normal-ordered
Gram descent
\[
P_X^{\Pi,\mathrm{desc}}
=H^0\Prim_{\mathrm{prot}}(\overline\Pi_{X,*}^\Theta\mathcal F_X)
=\overline\Pi_{X,*}^\Theta\widetilde P_X,
\quad
P_X^{\Pi,\mathrm{red}}
=P_X^{\Pi,\mathrm{desc}}/\overline{\operatorname{Rad}\langle\,,\,\rangle_X}.
\]
Suppose the following ten source-side data are constructed.

\begin{enumerate}
\item[\textup{(S1)}] \emph{Charge and normal-ordered descent.}  The
chain-level descent $\overline\Pi_{X,*}^\Theta$ categorifies the
homomorphism $\overline\Pi_X(c,T)=\Pi_X(c)-T$, so that the descended
bracket is $\Gamma_{\mathrm{gram}}$-graded.  Each descended homogeneous
parity piece is finite dimensional.

\item[\textup{(S2)}] \emph{Cartan and root-degree matching.}  An even
Cartan identification $\iota_H:P^{\Pi,\mathrm{red}}_{X,0}
\xrightarrow{\sim}\Lambda_{II}^{2,1}\otimes\C$ aligning the descended
Gram grading with the GN root grading via $\alpha(n,l,m)$.

\item[\textup{(S3)}] \emph{Simple primitive representatives and
parities.}  For every simple-root index $i\in I$, parity-homogeneous
representatives $e_i^X,f_i^X,h_i^X$ in
$P^{\Pi,\mathrm{red}}_{X,\pm\alpha_i}$ and
$P^{\Pi,\mathrm{red}}_{X,0}$, with $|e_i^X|=|f_i^X|=p(i)$,
$h_i^X=\iota_H^{-1}(\alpha_i)$, and the GN multiplicity fibres
$\mu_{\overline 0}(a),\mu_{\overline 1}(a)$ for imaginary simple
roots.  Real representatives for $\delta_1,\delta_2,\delta_3$ are even.

\item[\textup{(S4)}] \emph{Borcherds--Kac relations in the Hall
bracket.}  In the protected Hall/factorization bracket the
representatives satisfy:
\[
[h,h']=0,\quad [h,e_i^X]=(h,\alpha_i)e_i^X,\quad
[h,f_i^X]=-(h,\alpha_i)f_i^X,\quad
[e_i^X,f_j^X]=\delta_{ij}h_i^X,
\]
the real Serre relations
\[
(\operatorname{ad}e_i^X)^{1-2(\alpha_i,\alpha_j)/(\alpha_i,\alpha_i)}
e_j^X=0,
\quad
(\operatorname{ad}f_i^X)^{1-2(\alpha_i,\alpha_j)/(\alpha_i,\alpha_i)}
f_j^X=0\qquad(\text{real }i,\ i\ne j),
\]
the Borcherds orthogonality relations
$(\alpha_i,\alpha_j)=0\Rightarrow[e_i^X,e_j^X]=[f_i^X,f_j^X]=0$, and
the super sign rule.  In the rank-three real subsystem, the Serre
exponent is $3$ ($(\delta_i,\delta_j)=-2$); first brackets
$[e_i^X,e_j^X]$ are not forced to vanish.  For the primitive isotropic
roots $a_{ij}=\delta_i+\delta_j$ ($i<j$), the source supplies
$u^{\pm,X}_{ij,r}\in P^{\Pi,\mathrm{red}}_{X,\pm a_{ij}}$,
$1\le r\le 9$, satisfying orthogonality and Chevalley zero with
adjacent real roots, with real-string relations
$(\operatorname{ad}e_k^X)^5 u^{+,X}_{ij,r}=0$ for the complementary
$\{i,j,k\}=\{1,2,3\}$.

\item[\textup{(S5)}] \emph{Completed Hopf pairing and radical
quotient.}  Continuous, homogeneous, invariant for bracket and
coproduct, with closed homogeneous radical
$\operatorname{Rad}_X=\{x\mid\langle x,y\rangle_X=0\ \forall y\}$ a Lie
ideal and coideal.  After quotienting by
$\overline{\operatorname{Rad}_X}$, the source radical quotient is
identified with the GN/Kac quotient
$\overline{\operatorname{Rad}_{\mathrm{GN}}}$.  At every finite stage
the Lie-ideal and coideal stability hold and the inverse-limit kernel
is exactly $\operatorname{Rad}_X$.

\item[\textup{(S6)}] \emph{No extra relations.}  If
$\pi:\widehat{\mathfrak F}(\mathscr B_{\Delta_5})\to
P_X^{\Pi,\mathrm{red}}$ is the continuous map determined by the
representatives,
$\ker\pi=\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}}$.
Equivalently, $G(\mathscr B_{\Delta_5})\to P_X^{\Pi,\mathrm{red}}$ is
injective.  This is checked finite stage by finite stage on saturated
windows, with kernel identifications commuting with HN transitions.

\item[\textup{(S7)}] \emph{Generation.}  $P_X^{\Pi,\mathrm{red}}$ is
topologically generated by $P^{\Pi,\mathrm{red}}_{X,0}$ and the simple
primitive representatives.

\item[\textup{(S8)}] \emph{Completed PBW.}  PBW filtration
compatibility:
\[
\operatorname{gr}_{\mathrm{PBW}}U(P_X^{\Pi,\mathrm{red}})_W
\xrightarrow{\sim}
\operatorname{gr}_{\mathrm{PBW}}U(\mathfrak g_{\Delta_5})_W
\]
on every saturated finite window $W$, with strict transition maps
and inverse limit in the HN topology of
\S\ref{subsec:hall-correspondences}.

\item[\textup{(S9)}] \emph{Exact completion.}  Inverse limit exact on
the saturated finite root windows: transition maps strict, images
closed, and passage to the completed radical quotient commuting with
finite-window kernels, cokernels, PBW associated gradeds, and parity
pieces.  Equivalently, no new relation, generator, radical element,
or parity-cancelling summand appears only after completion.

\item[\textup{(S10)}] \emph{Full parity dimensions.}  For every
nonzero $\gamma$ with $\alpha(\gamma)\in\mathcal R$,
\[
\dim P^{\Pi,\mathrm{red}}_{X,\gamma,\overline p}
=\rootmult_{\overline p}(\alpha(\gamma)),\qquad p=0,1.
\]
On the first timelike channel $\gamma=(1,1,1)$,
\[
d^{\mathrm{GN}}_{(1,1,1),\overline 0}=29,\qquad
d^{\mathrm{GN}}_{(1,1,1),\overline 1}=93.
\]
These are presentation-level target dimensions, not an inference
from $29-93=-64$.
\end{enumerate}
Then $P_X^{\Pi,\mathrm{red}}\cong\mathfrak g_{\Delta_5}$ as
Gram-graded Lie superalgebras, with denominator
$64^{-1}\Delta_5(2Z)$.  If in addition the chiral Koszul source datum
of \S\ref{subsec:koszul-source} is constructed (including Koszul
Mittag--Leffler exactness), then $\Omega_E^{\mathrm{ch}}C_X\simeq
\mathsf{Den}_{\Delta_5,E}$.
\end{theorem}

\begin{proof}
The simple primitive representatives define a continuous homomorphism
$\pi:\widehat{\mathfrak F}(\mathscr B_{\Delta_5})\to
P_X^{\Pi,\mathrm{red}}$.  (S1) and (S2) make $\pi$ a homomorphism of
the descended Gram-graded completions.  (S3) fixes the real and
imaginary simple generators with their parities and multiplicity
fibres.  (S4) puts $J_{\mathrm{BK}}$ in the kernel.  (S5) identifies
the compact Hopf radical with the GN/Kac radical, so $\pi$ descends
to $G(\mathscr B_{\Delta_5})\to P_X^{\Pi,\mathrm{red}}$.  (S7) gives
surjectivity; (S6) gives injectivity after the completed radical
quotient.  (S8) gives PBW-compatible finite-height identifications;
(S9) gives exactness in the inverse limit; (S10) rules out hidden
zero-superdimension root spaces and cancelling ideals invisible to
the determinant.  The chiral statement uses $C_X$, $b_X$,
$\Theta_{\mathrm{Kos}}$, and the Koszul Mittag--Leffler exactness of
\S\ref{subsec:koszul-source}.
\end{proof}

\subsubsection*{Cofinal finite-window primitive recognition}

The Borcherds product fixes signed target superdimensions; the
Gritsenko--Nikulin/Kac presentation fixes full target parity
dimensions only in the degrees where the presentation has been
computed.  A compact $K3\times E$ source is identified with the
denominator algebra only by source representatives, pairings,
radicals, relation ideals, PBW, and exact transition maps.

The imported target on the first window $W_{\le 3}$ has parity table
\[
\delta_i:1|0,\quad
a_{ij}:10|0,\quad
2\delta_i+\delta_j:1|0,\quad
\delta_{123}:29|93,
\]
so $29-93=-64=f(1,1)$.  These are target data; they do not construct
compact source primitives, source pairings, radical kernels, or
source bracket constants.

\begin{definition}[Cofinal finite-window primitive-recognition datum]
\label{def:cofinal-primitive-recognition-datum}
A finite set $W\subset Q_+\setminus\{0\}$ is \emph{downward
saturated} if $0<\beta'\le\beta$, $\beta\in W$, $\beta-\beta'\in Q_+$
imply $\beta'\in W$.  A cofinal finite-window primitive-recognition
datum for $P_X^{\Pi,\mathrm{red}}$ is an increasing sequence of
finite downward-saturated windows $W_1\subset W_2\subset\cdots$ with
$\bigcup_\nu W_\nu=\mathcal R_+$, together with the following finite
data on every $W_\nu$, compatible under $W_\nu\subset W_{\nu+1}$.

\begin{enumerate}
\item[(R0)] \emph{Compact source labels.}  Every source basis vector
in $W_\nu\cup(-W_\nu)\cup\{0\}$ satisfies the compact source
admissibility condition.  Target labels from
$G(\mathscr B_{\Delta_5})$ appear only in target rows or as
codomains of comparison maps.
\item[(R1)] \emph{Representatives and parities.}  Simple-root
representatives $e_i^X,f_i^X,h_i^X$ whose roots lie in $W_\nu$ are
supplied with the GN parity fibres for imaginary simple roots and
even real representatives for $\delta_1,\delta_2,\delta_3$.
\item[(R2)] \emph{Relations.}  Cartan, Chevalley, real Serre,
orthogonality, and super sign relations checked for every relation
whose displayed source and target degrees lie in
$W_\nu\cup(-W_\nu)\cup\{0\}$.
\item[(R3)] \emph{Full finite parity dimensions.}  For every
$\beta\in W_\nu$,
$\dim P^{\Pi,\mathrm{red}}_{X,\beta,\overline p}
=\rootmult_{\overline p}^{\mathrm{GN}}(\beta)$ ($p=0,1$), with zero
on non-root degrees.  Two-integer equality, not signed-superdimension.
\item[(R4)] \emph{Hopf pairing and radical.}  Positive-negative
pairing matrices written in parity blocks; kernels agree with GN/Kac
invariant-pairing kernels; stable under finite brackets in the
window; coideal for finite coproduct; carried to the next window by
transitions; inverse-limit radical the closure of finite kernels.
\item[(R5)] \emph{No extra relations.}  Finite kernel equality
$\ker\pi_\nu=
(\overline{J_{\mathrm{BK}}+\operatorname{Rad}_{\mathrm{GN}}})_{\le W_\nu}$.
\item[(R6)] \emph{Generation.}  Source primitive root spaces in
$W_\nu\cup(-W_\nu)$ generated by Cartan and supplied simple
representatives through brackets whose intermediate positive degrees
stay in $W_\nu$.
\item[(R7)] \emph{Completed PBW compatibility.}  Strict PBW
filtration preservation under transitions, inverse-limit PBW
compatibility.
\item[(R8)] \emph{Exact triangular completion.}  Words whose total
degree lies in the finite test window only through positive-negative
cancellation are not added as extra finite generators; transition
maps strict, images closed, $\lim^1$ vanishing on the triangular
finite-window systems.
\end{enumerate}
The datum is finite at each $\nu$, but not numerical: it contains
representatives, relation verifications, pairing matrices, kernel
equalities, and PBW transition data.  The Borcherds product and the
OP scalar square provide none of these source-side objects.
\end{definition}

\begin{proposition}[Global recognition is exactly the cofinal datum;
\textit{proved}]
\label{prop:global-recognition-cofinal-datum}
Assume (S1)--(S4) of Theorem~\ref{thm:primitive-recognition}.  Then
the remaining global source-side assertions (S5)--(S10) are supplied
by a cofinal finite-window primitive-recognition datum
$\{W_\nu,(\textup{R0})\text{--}(\textup{R8})\}$ in the sense of
Definition~\ref{def:cofinal-primitive-recognition-datum}, and
conversely.
\end{proposition}

\begin{proof}
The two sides record the same data: each $W_\nu$ is a saturated
finite window in (S5)--(S9), and (R3) is exactly the
two-integer parity equality of (S10) on $W_\nu$.  The Hopf pairing
matrices, kernel equalities, PBW filtrations, no-extra-relations
ledger, and transition strictness are word-for-word the cofinal
contents of (S5)--(S9), and the cusp-positive arithmetic side of
$f(nm,l)$ is recovered from the parity equalities (R3) on the active
target degrees.  Conversely, given (R0)--(R8) on a cofinal system,
inverse limit exactness (R8) gives the global statements
(S5)--(S9), and (R3) on a cofinal exhaustion gives (S10).
\end{proof}

\subsubsection*{Recognition criterion at the window $W_{\le 3}$}

For a finite window $W$ with $S_W=W\cup(-W)\cup\{0\}$, a compact
source datum consists of compact-source bases
$b^X_{R,\gamma_\beta,\overline p,a}$, parity pieces, product,
coproduct, bracket, pairing, radical, and quotient matrices
$M,D,B,G,K,Q$, comparison maps $A_{\beta,\overline p}$, relation
identities, the no-extra kernel equality, PBW associated gradeds,
and strict Mittag--Leffler transition maps.  The target labels
$e_i,E_{ij},u_{ij,r},T_i,M_{ij,r},w_s$ occur only in target blocks
or as codomain coordinates of $A_{\beta,\overline p}$.

The window $W_{\le 3}$ is the first arithmetic window, not the
first relation-closed window.  A relation-closed test must include
real-Serre terminal rows, doubled isotropic rows, $\delta_{123}$-real
strings, odd--odd $\delta_{123}$ rows, and complementary
height-seven strings, or pass to the downward-saturated closure.

\subsubsection*{What signed dimensions miss}

\begin{lemma}[Signed dimensions are not recognition;
\textit{proved}]
\label{lem:signed-dimensions-miss}
Let $V_\bullet$ be a $\widehat\Gamma_X$-graded super vector space
with zero bracket and zero coproduct, with the same signed
superdimensions $\sdim V_\gamma=f(nm,l)$ as
$P_X^{\Pi,\mathrm{red}}$.  Then $V_\bullet$ has the same Borcherds
denominator $64^{-1}\Delta_5(2Z)$ as $\mathfrak g_{\Delta_5}$ but is
not isomorphic to it as a Lie superalgebra.
\end{lemma}

\begin{proof}
The denominator depends only on signed superdimensions; the bracket
data, no-extra-relations theorem, Hopf-radical coideal stability, and
PBW filtration are independent.  $V_\bullet$ has trivial bracket and
trivial Hopf radical; the BKM relations $J_{\mathrm{BK}}$ are not in
the kernel of any nonzero map to $V_\bullet$ for non-Cartan letters.
\end{proof}

This lemma is the counterexample that prohibits the determinant route
to recognition.  It is also the structural reason eight clauses
(S1)--(S10) collapse to one: signed dimensions are necessary and
not sufficient, and the seven extra clauses are exactly the missing
data.

\subsubsection*{Status under the obstruction tuple}

The recognition lane carries the residuals
\[
\mathfrak O_{\mathrm{Rec},\nu}=
\bigl(
\mathfrak o^{(\textup{R1})}_\nu,
\ldots,
\mathfrak o^{(\textup{R8})}_\nu,
\mathfrak o^{\mathrm{tr}}_{\nu+1,\nu}
\bigr),
\]
required to vanish on every cofinal window.  The first arithmetic
window $W_{\le 3}$ is achievable from the GN target side; the first
relation-closed window includes the real-Serre terminal rows and the
$\delta_{123}$ odd--odd rows.  Probes A047, A049, A089 record
finite-stage components of the (R0)--(R8) ledger; A074, A076, A082
audit the source-radical/Hopf-coideal stability under (O1).
Discharge of the source-internal recognition theorem at any one
window beyond $W_{\le 3}$ is open and tracked by the cross-volume
Master Critique.

\subsubsection*{Cross-repo anchor}

The recognition theorem is the source side of the Vol III Drinfeld
double construction and the target side of the Borcherds 1992 GKM
\cite{B}/\cite{Borcherds95} program; Gritsenko--Nikulin
\cite{GN,GNPartI,GNII} and Kac \cite{KAC:1} supply the target
denominator algebra and parity table.  The slogan
$\mathrm{CoHA}(\C^3)=W_{1+\infty}$ is forbidden: the present
recognition is at the level of the protected primitive Hall
algebra, before Drinfeld doubling, and it identifies that algebra
with $\mathfrak g_{\Delta_5}$, not with the centred or
vacuum-evaluated double.

Entries $(\mathrm L 1)$--$(\mathrm L 6)$ name the constructed
objects; the explicit finite-stage calculus assembling them is the
eight algorithms A1--A8, each with typed input, output, and named
local obstruction.  Entry $(\mathrm L 7)$ is this calculus, in
\S\ref{subsec:eight-build-algorithms}.
