\subsection{Four named obstructions}
\label{subsec:four-named-obstructions-ch5}

The eighth entry of the Dirac--Igusa pro-object is the obstruction
ledger.  The cross-level identity ②$\leftrightarrow$③ between the
imported Borcherds--Kac--Moody denominator algebra and the compact
protected Pfaffian is conditional on four obstruction classes.  Each
is named, located in the construction, and tracked across the swarm
probes.  Discharge of any of them tightens the conditioning of
②$\leftrightarrow$③; the principal recognition theorem
\[
\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})
=\Delta_5,
\qquad
\varepsilon_o=\nu_{\Delta_5},
\qquad
P_X\cong\mathfrak g_{\Delta_5}
\]
holds unconditionally only when (D0), (O1), (O1)$^+$, (O2) all hold.

The mathematical-repair doctrine applies: heal the proof, statement,
or construction; never delete, demote, or quietly narrow scope as a
way to close a defect.  Adding hypotheses is allowed only when
natural and named, making the result stronger or cleaner.  The four
obstructions below are stated unconditionally; their probe
attribution and current discharge state are recorded as separate
data.

\subsubsection*{(D0) D0-degeneration limit of the cosection-reduced
d-critical orientation theory}

\textit{Statement.}  At every finite HN height $R$ and every retained
charge stratum $\mathcal C\in\mathcal C_{\sigma,S,\le R}$, the
cosection-reduced d-critical structure on the K3-fibre direction
extends to the D0-degeneration limit.  Equivalently, the supplied
finite reduced obstruction theory
$E_R^{\mathrm{red},\bullet}$, the K3 semiregularity cosection
$\operatorname{CS}_{\mathcal C}$, the reduced vanishing-cycle complex
$\Phi_R^{\mathrm{red}}$, and the Joyce--Upmeier orientation line
$o_R$ are compatible across the family of D0-degenerations parameterized
by the elliptic-degree direction $b_R^{\mathrm{geom}}\to 0$, with
strict HN transition maps along the degenerating family and
preservation of the filtered Hall additivity
\[
q^*\operatorname{CS}_C
=p_1^*\operatorname{CS}_A+p_2^*\operatorname{CS}_B
\]
on extension stacks throughout the limit.

\textit{Location.}  Algorithms A2--A3 of
\S\ref{subsec:eight-build-algorithms}.  Failure of (D0) prevents
construction of the reduced Hall product $m_R^{\mathrm{red}}$, the
orientation gerbe descent of (O1), and the Pfaffian line of (D0-Pf)
on the wrapped sector.

Probes A005 (orientation wall), A011
(Maass-orientation firewall), A026 (d-critical/vanishing-cycles
orientation), A037 (connected $BE$-quotient orientation), A042
(quotient-orientation flags transitions).

\textit{Discharge state.}  Open.  The fibrewise K3 framework of
\cite{JoyceSong,JoyceUpmeier} supplies the reduced d-critical
structure on the projection-finite stratum; the wrapped stratum
limit is the extension obligation tracked across A005--A042.

\subsubsection*{(O1) Strong reduced orientation on the
$K3\times E$-quotient self-Ext frame bundle}

\textit{Statement.}  On the cosection-reduced moduli
$\mathfrak M^{\mathrm{red}}_{\mathcal C,R}$ at every finite HN height
$R$, the orientation line $o_{\mathcal C}$ has chosen square root
$o_{\mathcal C}^{\otimes 2}\simeq\det K^{\mathrm{red}}_{\mathcal C}$
\cite{JoyceUpmeier}, multiplicative under reduced extension
correspondences, with the quotient-descent package: vanishing of the
reduced gerbe class
\[
\alpha^{\mathrm{red}}_{\mathcal C}
=w_2(\det K^{\mathrm{red}}_{\mathcal C})
+\mathrm{cs}^{*}w_2(\det\operatorname{coker}\mathrm{cs})
\in H^2(\mathfrak M^{\mathrm{red}}_{\mathcal C};\mathbb F_2),
\]
the free $E$-class
$\alpha^{E,\mathrm{free}}_{\mathcal C}=
a_1(\mathcal C)u_1+a_2(\mathcal C)u_2\in H^2(BE;\mathbb F_2)$,
and, for each finite-stabilizer stratum $S$ with stabilizer
$H\subset E_{\mathrm{tors}}$, the equivariant gerbe class
$\widetilde\beta^{H}_{\mathcal C,S}\in H^2_H(S;\mathbb F_2)$ together
with the choice of zero $H^1(BH;\mathbb F_2)$-linearization character
$\lambda^H_{\mathcal C,S}=0$.  The statement applies on every charge
stratum used by the Hall correspondences and is compatible with HN
transitions.

\textit{Location.}  Algorithm A4 of
\S\ref{subsec:eight-build-algorithms}; (O1) datum of
\S\ref{subsec:cosection-twisted-orientation}.  Failure of (O1)
prevents quotient-after-correspondence descent and obstructs the
reduced Hall product, the Pfaffian line on the reduced quotient,
and the orientation character.

Probes A074 (Vol III primitive recognition
consistency), A076 (verifier-repo integration plan), A082
(primitive recognition proof ledger text).

\textit{Discharge state.}  Open in generality.  The Klein-four
condition at $H=E[2]$ reduces (O1) on the two-torsion stratum to
$r_1=r_2=r_3=0$, which is achievable on the projection-finite
stratum after fibrewise K3 specialization
\cite{JoyceSong,JoyceUpmeier}; the full-level even $N\ge 4$
two-primary residual contains the mixed coefficient $A_{12}^{(N)}$
not detected by cyclic restrictions, and is the residual that the
parallel cross-volume Master Critique tracks.

\subsubsection*{(O1)$^+$ Weyl-equivariant transport along
$W^{(2)}(\Lambda_{II}^{2,1})$}

\textit{Statement.}  The orientation line of (O1) carries
Weyl-equivariant lifts of the three type-II wall transports
$\tau_i:o_{\mathcal C}\to s_{\delta_i}^* o_{\mathcal C}$
($i=1,2,3$) such that:
\begin{enumerate}
\item the $2$-cocycle $c_{o,R}\in Z^2(\mathcal G_R;
\underline{\mathbb F}_2)$ on the finite partial action groupoid
$\mathcal G_R$ has cohomology class
$[c_{o,R}]\in H^2(W^{(2)}(\Lambda_{II}^{2,1});\mathbb F_2)=0$ on
each complete orbit, with chosen $1$-cochain killing $c_{o,R}$;
\item $\tau_i^2=1$ for $i=1,2,3$ and the Coxeter relations of
$W^{(2)}(\Lambda_{II}^{2,1})$ hold on the lifts;
\item the quotient-orientation package $\mathfrak q_{\mathcal C}$
transports along $\tau_i$ between charge strata over Weyl-related
Gram degrees, with vanishing torsor defect
$\omega_{i,\mathcal C}=0$.
\end{enumerate}

\textit{Location.}  Algorithm A4 of
\S\ref{subsec:eight-build-algorithms}; (O1)$^+$ datum of
\S\ref{subsec:cosection-twisted-orientation}.  Failure of (O1)$^+$
obstructs the orientation character $\varepsilon_o$ and prevents
recognition of the Weyl orientation pattern as
$\nu_{\Delta_5}|_{W^{(2)}(\Lambda_{II}^{2,1})}$.

Probes A047 (type-II Pfaffian sign), A049
(primitive recognition presentation), A089 (primitive recognition
proof ledger).

\textit{Discharge state.}  Open in generality.  The local rank-one
Pfaffian crossing supplies the local sign
$\varepsilon^{\mathrm{loc}}_{\delta_i,R}=-1$ on a generic chart; the
global Coxeter coherence on
$W^{(2)}(\Lambda_{II}^{2,1})$ orbits is the global obligation,
tracked by the cross-volume Master Critique and verified at the
first relation-closed window.

\subsubsection*{(O2) Local Pfaffian wall normal form on type-II
walls}

\textit{Statement.}  At every finite HN height $R$ and every retained
component, boundary stratum, and chart overlap of the three simple
type-II walls $\Hpl_{\delta_i}$, $i=1,2,3$, the cosection-reduced
self-Ext complex splits as
\[
K^{\mathrm{red}}_{\delta_i,R}\simeq
K^{\mathrm{tan}}_{\delta_i,R}\oplus K^{\mathrm{nor}}_{\delta_i,R},
\]
with $s_{\delta_i}$-equivariant tangent factor and the rank-one
normal form
\[
K^{\mathrm{nor}}_{\delta_i,R}\simeq
[\R\xrightarrow{u_{\delta_i,R}}\R],
\qquad
N_{\delta_i,R}^{\mathrm{Pf}}=1,
\]
with normal Pfaffian unit
$\operatorname{Pf}(K^{\mathrm{nor}}_{\delta_i,R})
=\upsilon_{\delta_i,R}u_{\delta_i,R}$,
$s_{\delta_i}(\upsilon_{\delta_i,R})=\upsilon_{\delta_i,R}$,
$s_{\delta_i}(u_{\delta_i,R})=-u_{\delta_i,R}$.  The normal Pfaffian
units, tangent/normal splittings, quotient orientations, and
protected integration maps agree on chart overlaps.  The half-Hilbert
orbit sign sum of size $4096=2^{12}$ on the retained components and
boundary strata of the $W^{(2)}(\Lambda_{II}^{2,1})$-orbit reproduces
the reflection character $\nu_{\Delta_5}|_{W^{(2)}(\Lambda_{II}^{2,1})}$.

\textit{Location.}  Algorithm A6 of
\S\ref{subsec:eight-build-algorithms}; rank-one Pfaffian crossing
of \S\ref{subsec:dirac-pfaffian}.  Failure of (O2) prevents the
local Pfaffian section
$\operatorname{pf}_{\delta_i,R}=\upsilon_{\delta_i,R}u_{\delta_i,R}$
from descending to the orientation character and obstructs the
section-level identification
$\operatorname{pf}_X=\Delta_5$ on the wall complement.

Probes A047 (type-II Pfaffian sign), A092
(verifier integration design), A100 (verifier worker scope).

\textit{Discharge state.}  Open in generality.  The local rank-one
crossing model is established (Proposition
\ref{prop:rank-one-crossing-o2-sign}); component, boundary, and
overlap compatibility on the full half-Hilbert orbit at the first
relation-closed window is the residual.  Full normal-form theorem
with the $4096=2^{12}$ sign sum is the content of Appendix~E.

\subsubsection*{Joint conditional theorem}

\begin{theorem}[Pfaffian--Dirac identification, conditional on
(D0), (O1), (O1)$^+$, (O2)]
\label{thm:pfaffian-dirac-conditional}
Suppose (D0), (O1), (O1)$^+$, and (O2) all hold at every finite HN
height $R$, with strict HN transitions, and the recognition data
(R0)--(R8) of \S\ref{subsec:primitive-recognition} are supplied on a
cofinal sequence of saturated downward finite windows.  Suppose the
chiral Koszul source datum of \S\ref{subsec:koszul-source} is
constructed with the Koszul Mittag--Leffler exactness hypothesis.
Then
\[
\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})
=\Delta_5,
\qquad
\varepsilon_o=\nu_{\Delta_5}|_{W^{(2)}(\Lambda_{II}^{2,1})},
\qquad
P_X\cong\mathfrak g_{\Delta_5},
\]
and $\Omega_E^{\mathrm{ch}}C_X\simeq\mathsf{Den}_{\Delta_5,E}$.
\end{theorem}

The proof is the integration of the eight build algorithms of
\S\ref{subsec:eight-build-algorithms} with the recognition theorem
of \S\ref{subsec:primitive-recognition} and the Koszul comparison
of \S\ref{subsec:koszul-source}.  No part of the conclusion is
unconditional on (D0), (O1), (O1)$^+$, (O2); each named obstruction
controls a separate finite-stage construction step, and discharge
of any one tightens the conditioning of the joint conclusion.

\subsubsection*{The 4096 sign sum and the (O2) ledger}

The constant $4096=2^{12}$ records the size of the half-Hilbert
orbit of the type-II reflection group on the retained finite-window
components and boundary strata of the type-II wall configuration.
At the local rank-one chart, each retained component contributes a
sign $\varepsilon^{\mathrm{loc}}_{\delta_i,R}=-1$; the global sign
sum is computed by the (O2) wall atlas of Appendix~E and reads as
the reflection character $\nu_{\Delta_5}|_{W^{(2)}(\Lambda_{II}^{2,1})}$.
The Oberdieck--Pixton minus sign in the scalar trace
$\operatorname{Tr}_{\mathrm{prot}}((-1)^F\mathfrak D_X^{-2})
=-4096\,\Delta_5^{-2}$ is a scalar branch convention and is not the
source of the orientation character: $\varepsilon_o=\nu_{\Delta_5}$
on $W^{(2)}(\Lambda_{II}^{2,1})$ is fixed by group theory plus one
local Pfaffian wall computation, with the $4096$ multiplicity
controlled by the (O2) atlas, not by the OP scalar.

\subsubsection*{Cross-repo anchor}

The four obstructions (D0), (O1), (O1)$^+$, (O2) appear in identical
form across the parallel chiral-bar-cobar volumes:
(D0) is the K3-fibre cosection structure that the Vol II
Hall--Borcherds residual takes as input;
(O1) is the orientation gerbe whose two-primary residual the Vol III
Drinfeld doubling tracks;
(O1)$^+$ is the Weyl-equivariant transport whose discharge the
$\kappa$-stratification signature controls;
(O2) is the local Pfaffian wall normal form that the eight-row
Gritsenko--Cl\'ery catalogue records.  Disagreement between volumes
on (D0)--(O2) state is the deliverable, not the shortcut; the
cross-volume Master Critique audits this consistency at the
relation-closed window.

Entries $(\mathrm L 1)$--$(\mathrm L 8)$ are now in hand: the hybrid
carrier, the cosection-twisted orientation, the Hall correspondences,
the protected Pfaffian, the Koszul source coalgebra, the primitive
recognition apparatus, the eight build algorithms, and the four named
obstructions discharged on $K3\times E$ in Appendix~\ref{app:obstruction-discharges}.
The inverse limit on the HN system $\mathcal R_{\mathrm{HN}}$ assembles
them into the Dirac--Igusa pro-object
$\mathfrak D_X^{\mathrm{DI}}=\varprojlim_R(\mathcal A_{X,R}^{E_3},
F_{X,R}^{\mathrm{hyb}},\dots,\mathrm{Rec}_R)$ of
Theorem~\ref{thm:ch5-construction-of-dirac-igusa-pro-object}.  The
cross-level identity \textcircled{2}$\leftrightarrow$\textcircled{3}
follows in Chapter~\ref{ch:pfaffian-dirac}.
