% =====================================================================
% Chapter 2 — K3 x E setup, Mukai dictionary, lattice polarization,
% normal-ordered Gram cocycle, and hybrid Ran^{hyb}(E) factorization
% carrier. Structural reconstitution of the source TeX (current main.tex
% lines 371--548 and 4401--5185), surgical edits absorbed: K3xE threefold
% throughout, n = chi(O_Y) directly; Bott-element framing of B(c,c)=
% 2 Pi_X(c) excised; the three Delta_5 names tagged on first use; the
% E-descent lemma split into connected and finite-stabilizer branches;
% the linearization lemma stated as a criterion, not as vanishing.
% =====================================================================

\chapter{K3$\times$E setup, Mukai dictionary, lattice polarization,
normal-ordered Gram cocycle, hybrid $\operatorname{Ran}^{\mathrm{hyb}}(E)$ carrier}
\label{ch:k3xe-setup}

The arithmetic source produces three named scalars at level five.  Each
is the Igusa cusp form $\Phi_{10}^{1/2}$ on a different categorical
chain.  The automorphic chain produces the section
\[
\mathcal{D}_X = \Delta_5
\in M_5\!\bigl(\Sp_4(\Z),\,\nu_{\Delta_5}\bigr)
\qquad\text{(View \textcircled{1}; proved \cite{Borcherds95,GN}).}
\]
The Borcherds--Kac--Moody (BKM) chain produces the denominator
\[
\operatorname{den}(\mathfrak g_{\Delta_5}) = 64^{-1}\,\Delta_5(2Z)
\qquad\text{(View \textcircled{2}; proved \cite{GN}).}
\]
The compact Pfaffian chain produces, granted the four-obstruction
discharge of
Theorem~\ref{thm:G-four-obstruction-discharge} of
Appendix~\ref{app:obstruction-discharges}, the protected Pfaffian
\[
\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}}) = \Delta_5
\qquad\text{(View \textcircled{3}; proved on $K3\times E$ at the chiral-shadow level).}
\]
The handle ``$\Delta_5$'' with no superscript is reserved for working
formulas; manuscript prose names which of $\mathcal D_X$,
$\operatorname{den}(\mathfrak g_{\Delta_5})$, or
$\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})$ is meant.
The cross-level identity \textcircled{2}$\leftrightarrow$\textcircled{3}
is unconditional at the chiral-shadow level on \(K3\times E\),
granted the discharges of
$(\mathrm{D0})$, $(\mathrm{O1})$, $(\mathrm{O1}^+)$, $(\mathrm{O2})$
in Theorems~\ref{thm:G-D0}, \ref{thm:G-O1}, \ref{thm:G-O1-plus},
\ref{thm:G-O2-orbit-transport}.

\paragraph{The Mukai--Gram dictionary as the chapter's organizing principle.}
The chapter is structured around the Mukai--Gram dictionary on
\(K3\times E\): the Mukai lattice
\(\widetilde H(S,\Z)\) of \(S\) (rank \(24\), signature \((4,20)\),
\cite{Mukai1984}) is the K3-side data, the K\"unneth tensor with
\(H^*(E,\Z)\) supplies the threefold lattice
\(\widetilde H(X,\Z)\) of rank \(48\) and signature \((24,24)\), and
the Gram-index lattice
\(\Gamma_{\mathrm{gram}}=\Z^3\) is the polarisation under which the
Borcherds product variables \((q,r,s)\) of
View~\textcircled{2} live.  The dictionary maps:
\[
 \widetilde H(X,\Z)\;\xrightarrow{\;\Pi_X\;}\;\Gamma_{\mathrm{gram}}=\Z^3
 \;\hookrightarrow\;\La^{2,1}_{II}\;\hookrightarrow\;\La^{3,2},
\]
the rightmost arrow the embedding into the type-IV singular-theta-lift
ambient of Chapter~\ref{ch:singular-theta-lift}.  Each step is a
named lattice with a named pairing; the chapter develops them in
turn.  Detailed lattice computations are in
Appendix~\ref{appendix:mukai-gram-dictionary}; this chapter supplies
the dictionary as the organising axis of \(K3\times E\) data.

The chapter assembles the geometric and lattice data feeding all three.
The compact target is fixed at $X = S \times E$ with $S$ a smooth complex
projective K3 surface and $E$ a smooth elliptic curve over $\C$; this is
a Calabi--Yau threefold ($\dim_\C X = 3$, $K_X \cong \mathcal{O}_X$;
proved/$\alpha$, \cite{Mukai1984,Mukai1987}), so $n = \chi(\mathcal O_Y)$
appears directly.  The $(\kappa_{\mathrm{cat}},
\kappa_{\mathrm{ch}}^{\mathrm{Hodge}}, \kappa_{\mathrm{ch}}^{\mathrm{Heis}},
\kappa_{\mathrm{BKM}}, \kappa_{\mathrm{fiber}}) = (0, 0, 3, 5, 24)$ tuple
of \cite{CYQGVolIII} (the K3$\times$E row of the
Gritsenko--Cl\'ery catalogue) is the categorical-dimensional anchor; every
use of $\kappa$ in this manuscript carries one of these five subscripts.

The four-step build is geometric, then arithmetic.  First, the formal
dyonic charge lattice $\Gamma_X^{\mathrm{form}} = \Lambda_S \oplus
\Lambda_S$ on the Mukai sector and the algebraic/effective Hall support
$\Gamma_{X,\sigma}^{\mathrm{eff}} \subset \Gamma_X^{\mathrm{alg}} \subset
\Gamma_X^{\mathrm{form}}$ inside it.  Second, the quadratic Gram map
$\Pi_X : \Gamma_X^{\mathrm{form}} \to \Gamma_{\mathrm{gram}} = \Z^3$ and
its symmetric bilinear polarization $B = -\delta\Pi_X$.  Third, the
normal-ordered extension
$\widehat\Gamma_X = \Gamma_X^{\mathrm{form}} \oplus_B \Gamma_{\mathrm{gram}}$
and the additive map $\overline\Pi_X(c, T) = \Pi_X(c) - T$, with the
fixed-lift raw-pushforward obstruction theorem fixing the necessity of
that extension.  Fourth, the hybrid factorization carrier
$\operatorname{Ran}^{\mathrm{hyb}}(E) = \operatorname{Ran}(E)_{b=0}
\sqcup \operatorname{Ran}^{\mathrm{wr}}(E)_{b>0}$, with the projection-
locality obstruction fixing the necessity of the wrapped stratum.

% =====================================================================
\section{Smooth K3$\times$E threefold and Mukai lattice}
\label{sec:k3xe-mukai-lattice}
% =====================================================================

% -------------------------------------------------------------------
\subsection{The compact target}
\label{subsec:k3xe-compact-target}
% -------------------------------------------------------------------

\begin{definition}[K3$\times$E threefold; primitive geometric datum]
\label{def:k3xe-threefold}
A \emph{K3$\times$E threefold} is a triple $(X, S, E)$ in which $S$ is a
smooth complex projective K3 surface (so $K_S \cong \mathcal{O}_S$,
$h^{1,0}(S) = 0$, $h^{2,0}(S) = 1$; \cite{Mukai1984}),
$E$ is a smooth elliptic curve over $\C$ with marked origin
$0_E \in E$, and
\[
X := S \times E.
\]
The canonical bundle is trivial, $K_X \cong p_S^*K_S \otimes p_E^*K_E
\cong \mathcal O_X$, and Hodge invariants are
\[
\dim_\C X = 3,\qquad
\chi_{\mathrm{top}}(X) = \chi_{\mathrm{top}}(S)\cdot\chi_{\mathrm{top}}(E)
= 24 \cdot 0 = 0,\qquad
\chi(\mathcal O_X) = \chi(\mathcal O_S)\cdot\chi(\mathcal O_E) = 2\cdot 0 = 0.
\]
The threefold $X$ is a Calabi--Yau threefold (proved/$\alpha$).
\end{definition}

\begin{remark}[Distinguishing $\chi_{\mathrm{top}}(K3) = 24$ and
$\chi(\mathcal O_S) = 2$]
\label{rem:two-K3-Eulers}
The integer $24 = \chi_{\mathrm{top}}(K3)$ enters the Borcherds
exponent $f(0, 0)/2 = 5$ via $f(0, 0) = 2(\chi_{\mathrm{top}}(K3))/24
\cdot \dim_\C\!\bigl(\widetilde H(K3,\C)/(\R\!\cdot\!1 \oplus
\R\!\cdot\!\omega_K)\bigr) = 10$, equivalently $\phi_{0, 1}(\tau, 0) =
24\,\eta(\tau)^{-2}\theta_1\theta_2\theta_3\theta_4 = 12\!+\cdots$ at
$z = 1/2$ (computed/$\beta$, \cite{EZ:1}).  The integer
$\chi(\mathcal O_S) = 2$ enters the categorical Calabi--Yau dimension and
the holomorphic part of the Mukai pairing.  The two integers do not
collapse: the $\kappa$-tuple of \cite{CYQGVolIII}
records $\kappa_{\mathrm{fiber}} = 24 = \chi_{\mathrm{top}}(K3)$, not
$2 = \chi(\mathcal O_S)$, and the universal Borcherds identity
$\kappa_{\mathrm{BKM}}(\Phi_N) = c_N(0)/2$ at $\Phi_1 = \Delta_5$ gives
$c_1(0) = 10$ and $\kappa_{\mathrm{BKM}} = 5$, while
$\kappa_{\mathrm{ch}}^{\mathrm{Heis}} + \chi(\mathcal O_E) = 3 + 0 = 3$:
the additive collapse $\kappa_{\mathrm{BKM}} = \kappa_{\mathrm{ch}}^{\mathrm{Heis}}
+ \chi(\mathcal O_{\mathrm{fiber}})$ disagrees with the universal
identity at $N = 1$ (proved/$\alpha$, \cite{CYQGVolIII}
counterexample).  The level $\kappa_{\mathrm{BKM}} = 5$ is the cusp-form
weight; the manuscript writes the protected scalar shadow at level
$n = \chi(\mathcal O_Y)$, with the threefold $Y$ specialized to the
K3$\times$E fibre over the closed cobordism.  The K3$\times$E target
is a Calabi--Yau threefold; the manuscript reads $X$ as a threefold
throughout.
\end{remark}

% -------------------------------------------------------------------
\subsection{Mukai lattice on the K3 factor}
\label{subsec:k3-mukai-lattice}
% -------------------------------------------------------------------

\begin{definition}[Mukai lattice and Mukai pairing]
\label{def:mukai-lattice}
Let $S$ be a smooth complex K3 surface.  The \emph{Mukai lattice} is the
total even cohomology
\[
\Lambda_S
:= \widetilde H(S, \Z)
= H^0(S, \Z) \oplus H^2(S, \Z) \oplus H^4(S, \Z),
\]
identified with the K-theoretic charge lattice
$K_0(D^b(\mathrm{Coh}\,S))_{\mathrm{tor.\,free}}$ via the Mukai vector
\[
v(\mathcal F)
:= \mathrm{ch}(\mathcal F)\sqrt{\mathrm{Td}(S)}
= \bigl(r(\mathcal F),\,c_1(\mathcal F),\,r(\mathcal F) + \mathrm{ch}_2(\mathcal F)\bigr),
\]
where $r$ is the rank, $c_1$ is the first Chern class, and the half-shift
$r$ in the four-form term comes from $\mathrm{Td}(S) = 1 + 2[\mathrm{pt}]$
(proved/$\beta$, \cite{Mukai1984,Mukai1987}).  The \emph{Mukai pairing}
is
\[
\bigl\langle (r, c, s),\,(r', c', s')\bigr\rangle_{\mathrm{Muk}}
:= c\cdot c' - r s' - r' s,
\]
where $c\cdot c' \in \Z$ is the cup product on $H^2(S, \Z)$.  It is even,
unimodular, of signature $(4, 20)$, and rank $24$:
\[
\Lambda_S \cong II_{4, 20}
\cong U^{\oplus 4} \oplus E_8(-1)^{\oplus 2},
\]
where $U$ denotes the rank-two hyperbolic plane $U \cong \mathbb Z e
\oplus \mathbb Z f$ with $e^2 = f^2 = 0$, $e\cdot f = 1$, and $E_8(-1)$
denotes the negative-definite $E_8$ root lattice (proved/$\beta$,
\cite{Mukai1987,NIKULIN}).
\end{definition}

\begin{remark}[Sign convention]
\label{rem:mukai-sign-convention}
The signature $(4, 20)$ uses the convention that $H^0\oplus H^4$
contributes a hyperbolic plane $U$ via $(1, 0, 0)$ and $(0, 0, 1)$ and
that $H^2(S, \Z) \cong II_{3, 19} \cong U^{\oplus 3} \oplus
E_8(-1)^{\oplus 2}$, which has positive part of dimension $3$.  Together,
$\Lambda_S = U \oplus II_{3, 19} \cong U^{\oplus 4} \oplus
E_8(-1)^{\oplus 2}$ with positive part of dimension $4$ (proved/$\beta$,
\cite{Mukai1987}).  The signature is $(4, 20)$, not $(20, 4)$: the
positive direction is the smaller side.  Throughout the manuscript a
reflection $r_v$ across $v\in\Lambda_S$ acts by $r_v(x) = x - 2(x, v)v/(v,
v)$, taking the $\R$-linear extension when $(v, v)\ne 0$, without
implicit sign reversal.
\end{remark}

% -------------------------------------------------------------------
\subsection{K\"unneth and the formal even Mukai sector on $X = S \times E$}
\label{subsec:kunneth-formal-mukai}
% -------------------------------------------------------------------

\begin{definition}[Formal even Mukai sector on $X = S \times E$]
\label{def:formal-even-mukai-sector}
Pick a basepoint $0_E \in E$ and the standard generators
$1_E \in H^0(E, \Z)$ and $\omega_E \in H^2(E, \Z)$ with $\int_E \omega_E
= 1$.  Every even cohomology class on $X = S \times E$ decomposes as
\[
v_X = P \otimes 1_E + Q \otimes \omega_E,\qquad
P, Q \in \Lambda_S
\]
(proved/$\beta$, K\"unneth on simply connected $\widetilde H$ tensor
$E$-cohomology).  The pair $(Q, P)\in\Lambda_S\oplus\Lambda_S$ is the
\emph{formal even charge}.  The component $P\otimes 1_E$ is invariant
under translation along $E$, while $Q\otimes\omega_E$ records the
$E$-degree.

The \emph{formal full-Mukai dyonic lattice} is the additive abelian
group
\[
\Gamma_X^{\mathrm{form}} := \Lambda_S \oplus \Lambda_S,\qquad
c = (Q, P),
\]
with electric component $Q$ and magnetic component $P$.  In this
chapter the legacy notation $\Gamma_X^{\mathrm{phys}}$ is retained as a
mnemonic only and equals $\Gamma_X^{\mathrm{form}}$:
\[
\Gamma_X^{\mathrm{phys}} := \Gamma_X^{\mathrm{form}}.
\]
This is not the full four-dimensional $\mathcal N = 4$ electric--magnetic
charge lattice and not compact Hall support.  It is the D6--D2--D0/OP
even branch on which the Mukai Gram map is tested before imposing
algebraicity, effectivity, stability, or non-emptiness of compact Hall
moduli.
\end{definition}

\begin{definition}[Algebraic/effective Hall support]
\label{def:algebraic-effective-hall-support}
Fix a polarised K3 surface $(S, H)$, a chosen Mukai vector lattice
$\Lambda_{S, \mathrm{alg}} \subset \Lambda_S$ (the image of the
algebraic K-class lattice generated by sheaves whose Mukai vector lies in
$H^0\oplus\mathrm{NS}(S)\oplus H^4$), and a stability condition $\sigma$
on $D^b(\mathrm{Coh}\,S\times E)$ (Bridgeland-stable; folklore/$\beta$,
\cite{KSCoHA}).  Set
\[
\Gamma_X^{\mathrm{alg}}
:= \Lambda_{S,\mathrm{alg}}\oplus\Lambda_{S,\mathrm{alg}},\qquad
\Gamma_{X, \sigma}^{\mathrm{eff}}
\subset \Gamma_X^{\mathrm{alg}}
\subset \Gamma_X^{\mathrm{form}},
\]
where the \emph{$\sigma$-effective semigroup}
$\Gamma_{X, \sigma}^{\mathrm{eff}}$ is the additive sub-semigroup of
charges supported by $\sigma$-semistable objects of nonzero Mukai vector.
Membership in $\Gamma_{X, \sigma}^{\mathrm{eff}}$ is not implied by
membership in $\Gamma_X^{\mathrm{alg}}$ or by formal lattice arithmetic
(folklore/$\beta$).
\end{definition}

\begin{remark}[Three-tier inclusion]
\label{rem:three-tier-inclusion}
The hierarchy $\Gamma_{X, \sigma}^{\mathrm{eff}}
\subset \Gamma_X^{\mathrm{alg}}
\subset \Gamma_X^{\mathrm{form}}$
distinguishes three discipline registers.  $\Gamma_X^{\mathrm{form}}$ is
the formal additive group on which $\Pi_X$ is defined and the
polarization identity $B = -\delta\Pi_X$ holds.  $\Gamma_X^{\mathrm{alg}}$
is the K-theoretic algebraic sublattice; the rank-one extension closure
of $\Gamma_X^{\mathrm{alg}}$ inside $\Gamma_X^{\mathrm{form}}$ records the
Mukai-effective branch (computed/$\beta$,
\cite{Mukai1987,KSCoHA}).  $\Gamma_{X, \sigma}^{\mathrm{eff}}$ is the
$\sigma$-stable Hall support; it depends on $\sigma$ and is not
fibre-functorial in the K3 type.  The sectorial Hall truncation of
\S\ref{sec:k3xe-hybrid-ran-carrier} works at the second level after
imposing finite Harder--Narasimhan height bounds.
\end{remark}

\begin{lemma}[Two orthogonal hyperbolic planes inside $\Lambda_S$]
\label{lem:two-hyperbolic-planes}
The Mukai lattice contains two orthogonal hyperbolic planes:
\[
U \oplus U \hookrightarrow \Lambda_S,\qquad
U_1 = \Z e_1 \oplus \Z f_1,\quad U_2 = \Z e_2 \oplus \Z f_2,
\]
with $e_i^2 = f_i^2 = 0$, $e_i\cdot f_i = 1$, and $U_1\perp U_2$ inside
the Mukai pairing (proved/$\alpha$, \cite{NIKULIN}).
\end{lemma}

\begin{proof}
Direct from $\Lambda_S \cong U^{\oplus 4} \oplus E_8(-1)^{\oplus 2}$.
\end{proof}

% =====================================================================
\section{Quadratic Gram map and lattice polarization}
\label{sec:gram-map-polarization}
% =====================================================================

% -------------------------------------------------------------------
\subsection{Igusa variables and the Gram-index lattice}
\label{subsec:igusa-variables-gram-index}
% -------------------------------------------------------------------

For a Siegel period
\[
Z = \begin{pmatrix} z_1 & z_2 \\ z_2 & z_3 \end{pmatrix}
\in \mathcal H_2,\qquad
q = e^{2\pi i z_1},\quad r = e^{2\pi i z_2},\quad s = e^{2\pi i z_3},
\]
and
\[
T(n, l, m) = \begin{pmatrix} n & l/2 \\ l/2 & m \end{pmatrix},\qquad
n, l, m \in \Z,
\]
the trace pairing
\[
\bigl(T(n, l, m), Z\bigr)_{\mathrm{tr}}
:= \mathrm{tr}\bigl(T(n, l, m)\,Z\bigr)
= n z_1 + l z_2 + m z_3
\]
gives the Borcherds monomial $x^{(n, l, m)} = q^n r^l s^m$.

\begin{definition}[Gram-index lattice and effective semigroup]
\label{def:gram-index-lattice}
The \emph{Gram-index lattice} is
\[
\Gamma_{\mathrm{gram}} := \Z^3,\qquad
\gamma = (n, l, m).
\]
The \emph{cusp-positive semigroup} at the standard cusp $\mathfrak
c_\infty$ with chamber convention $0 < |s| \ll |q| \ll |r|^{-1} \ll 1$
is
\[
\Gamma_{\mathrm{eff}}
= \{(n, l, m) : m > 0,\ n \ge 0,\ l \in \Z\}
\cup \{(n, l, 0) : n > 0,\ l \in \Z\}
\cup \{(0, l, 0) : l < 0\}.
\]
The \emph{Jacobi-active sublocus}
$\Gamma_{\mathrm{act}} \subset \Gamma_{\mathrm{eff}}$ is the locus of
nonvanishing $f(nm, l)$ in the weak Jacobi form $\phi_{0, 1}$
(computed/$\beta$, \cite{EZ:1}).
\end{definition}

\begin{proposition}[Gram matrix convention for protected charges]
\label{prop:gram-matrix-convention}
For a formal even charge $c = (Q, P) \in \Gamma_X^{\mathrm{form}}$ in
the unimodular lattice $\Lambda_S$, set
\[
n = \frac{(Q, Q)}{2},\qquad
l = (Q, P),\qquad
m = \frac{(P, P)}{2}.
\]
Then $n, l, m \in \Z$ (since $\Lambda_S$ is even unimodular,
proved/$\gamma$),
\[
\begin{pmatrix} (Q, Q) & (Q, P) \\ (P, Q) & (P, P) \end{pmatrix}
= 2\,T(n, l, m),\qquad
\det\bigl(2 T(n, l, m)\bigr) = 4 n m - l^2,
\]
and $x^{(n, l, m)} = q^n r^l s^m$ is the Fourier character of
$\bigl(T(n, l, m), Z\bigr)_{\mathrm{tr}}$.
\end{proposition}

\begin{proof}
The Mukai pairing is integer-valued and even on $\Lambda_S\oplus\Lambda_S$
by Definition~\ref{def:mukai-lattice}.  The matrix identity is the
direct expansion
\[
\begin{pmatrix} (Q, Q) & (Q, P) \\ (P, Q) & (P, P) \end{pmatrix}
= \begin{pmatrix} 2 n & l \\ l & 2 m \end{pmatrix}
= 2\,T(n, l, m).
\]
The determinant follows.  The Fourier character is
$\exp(2\pi i\,\mathrm{tr}(T Z)) = q^n r^l s^m$.
\end{proof}

% -------------------------------------------------------------------
\subsection{The Gram map and its bilinear cocycle}
\label{subsec:gram-map-bilinear-cocycle}
% -------------------------------------------------------------------

\begin{definition}[Quadratic Gram map and bilinear cocycle]
\label{def:gram-map-cocycle}
The \emph{Gram map} is the quadratic projection
\[
\Pi_X : \Gamma_X^{\mathrm{form}} \longrightarrow \Gamma_{\mathrm{gram}},
\qquad
\Pi_X(Q, P)
= \left(\frac{(Q, Q)}{2},\,(Q, P),\,\frac{(P, P)}{2}\right).
\]
The \emph{symmetric bilinear cocycle} $B$ associated to $\Pi_X$ is
\[
B : \Gamma_X^{\mathrm{form}} \times \Gamma_X^{\mathrm{form}}
\longrightarrow \Gamma_{\mathrm{gram}},\qquad
B\bigl((Q, P), (Q', P')\bigr)
= \bigl((Q, Q'),\,(Q, P') + (Q', P),\,(P, P')\bigr).
\]
\end{definition}

\begin{lemma}[Gram additivity defect]
\label{lem:gram-additivity-defect}
For $c, c' \in \Gamma_X^{\mathrm{form}}$,
\[
\Pi_X(c + c') = \Pi_X(c) + \Pi_X(c') + B(c, c').
\]
The defect $B$ is symmetric, $\Z$-bilinear, integer-valued, and
satisfies polarization: $B(c, c) = 2\,\Pi_X(c)$.  As an ordinary
additive cochain identity,
\[
B = -\delta\Pi_X,\qquad
(\delta q)(c, c') = q(c) + q(c') - q(c + c').
\]
(proved/$\gamma$.)
\end{lemma}

\begin{proof}
Write $c = (Q, P)$, $c' = (Q', P')$; then
\[
\frac{(Q + Q')^2}{2}
= \frac{Q^2}{2} + \frac{Q'^2}{2} + Q\cdot Q',
\]
\[
(Q + Q')\cdot(P + P')
= Q\cdot P + Q'\cdot P' + Q\cdot P' + Q'\cdot P,
\]
\[
\frac{(P + P')^2}{2}
= \frac{P^2}{2} + \frac{P'^2}{2} + P\cdot P'.
\]
The three cross terms are the three components of $B(c, c')$.
Symmetry, bilinearity, and integrality follow from the corresponding
properties of the Mukai pairing.  Polarization is the case $c' = c$.
The cochain identity rewrites the additivity defect.
\end{proof}

\begin{lemma}[Bilinear cocycle identity]
\label{lem:b-cocycle-identity}
$B$ is normalized, $B(c, 0) = B(0, c) = 0$, and the additive coboundary
\[
(\delta B)(a, b, c) := B(b, c) - B(a + b, c) + B(a, b + c) - B(a, b)
\]
vanishes identically on $\Gamma_X^{\mathrm{form}}$ (proved/$\gamma$).
\end{lemma}

\begin{proof}
By bilinearity in each slot,
\[
B(a + b, c) = B(a, c) + B(b, c),\qquad
B(a, b + c) = B(a, b) + B(a, c).
\]
Substituting,
\[
(\delta B)(a, b, c)
= B(b, c) - B(a, c) - B(b, c) + B(a, b) + B(a, c) - B(a, b) = 0.
\]
The polarization identity $B(c, c) = 2\,\Pi_X(c)$ is the only place where
$B$ takes a non-vanishing value on the diagonal; this is structural,
not a Bott-element framing.
\end{proof}

\begin{remark}[Polarization, not Bott element]
\label{rem:polarization-not-bott}
The identity $B(c, c) = 2\,\Pi_X(c)$ is the polarization identity for
the symmetric bilinear $B$ associated to the quadratic $\Pi_X$.  It is
forced by the homogeneous-of-degree-two structure of the Gram map.  No
external Bott-element framing or characteristic-class coincidence is
involved.  The full structural content is that $\Pi_X$ is a homogeneous
quadratic on the additive group $\Gamma_X^{\mathrm{form}}$ valued in
$\Gamma_{\mathrm{gram}}$, with associated symmetric bilinear $B$ given by
the Mukai pairing of components on each direction.
\end{remark}

% -------------------------------------------------------------------
\subsection{Formal lift of every Gram triple}
\label{subsec:formal-gram-triple-lift}
% -------------------------------------------------------------------

\begin{lemma}[Formal primitive torsion-one lift of every Gram triple]
\label{lem:primitive-lift-every-gram-triple}
Suppose $\Lambda_S$ contains two orthogonal hyperbolic planes $U_1\oplus
U_2$ with bases $(e_1, f_1, e_2, f_2)$ as in
Lemma~\ref{lem:two-hyperbolic-planes}.  Then every Gram triple
$(n, l, m) \in \Z^3$ admits a primitive saturated formal full-Mukai lift
$c = (Q, P) \in \Gamma_X^{\mathrm{form}}$ with $\Pi_X(Q, P) = (n, l, m)$.
One may take
\[
Q = e_1 + n f_1,\qquad
P = l f_1 + e_2 + m f_2.
\]
For this lift, the wedge torsion invariant
\[
I(Q, P)
:= \gcd\!\bigl\{\text{coordinates of }Q\wedge P\text{ in a }\Z\text{-basis of }
{\textstyle\bigwedge^2\Lambda_S}\bigr\}
\]
equals $1$.
(proved/$\beta$.)
\end{lemma}

\begin{proof}
The hyperbolic-plane pairings give
\[
Q^2 = 2 n,\qquad P^2 = 2 m,\qquad Q\cdot P = l,
\]
hence $\Pi_X(Q, P) = (n, l, m)$.  The submodule $\Z Q + \Z P \subset
\Lambda_S$ contains the unimodular minor
$\det\!\begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix} = 1$ in the rows
indexed by $e_1, e_2$ of the coefficient matrix in
$(e_1, f_1, e_2, f_2)$, so the lift is primitive saturated.
The wedge expansion
\[
Q\wedge P
= l\,e_1\wedge f_1 + e_1\wedge e_2 + m\,e_1\wedge f_2
+ n\,f_1\wedge e_2 + nm\,f_1\wedge f_2
\]
contains the basis element $e_1\wedge e_2$ with coefficient $1$, so the
gcd is $1$ and $I(Q, P) = 1$.
\end{proof}

\begin{remark}[Pointwise existence is not Hall support]
\label{rem:pointwise-not-hall-support}
Lemma~\ref{lem:primitive-lift-every-gram-triple} produces a formal
charge plane realizing every prescribed Igusa degree.  It does not prove
algebraicity of $(Q, P)$, effectivity, non-empty compact Hall moduli,
duality-orbit descent, source-index descent, or any chain-level Hall
strictification.  The compact Hall obstruction is functorial
compatibility of pointwise existence with Hall addition and the
primitive bracket; only the latter is the working content of
Chapter~\ref{chap:dirac-igusa-pro-object}.
\end{remark}

% =====================================================================
\section{Normal-ordered Gram extension}
\label{sec:normal-ordered-extension}
% =====================================================================

% -------------------------------------------------------------------
\subsection{Central extension and the additive normal-ordered Gram
homomorphism}
\label{subsec:central-extension-additive-gram}
% -------------------------------------------------------------------

\begin{definition}[Normal-ordered extension and Gram homomorphism]
\label{def:normal-ordered-extension}
Set
\[
\widehat\Gamma_X
:= \Gamma_X^{\mathrm{form}}\oplus\Gamma_{\mathrm{gram}},
\]
with operation
\[
(c, T)\star(c', T')
:= \bigl(c + c',\,T + T' + B(c, c')\bigr).
\]
Define the \emph{normal-ordered Gram map}
\[
\overline\Pi_X : \widehat\Gamma_X \longrightarrow \Gamma_{\mathrm{gram}},
\qquad
\overline\Pi_X(c, T) = \Pi_X(c) - T.
\]
The \emph{raw placement} and the \emph{split section} are
\[
i_0 : \Gamma_X^{\mathrm{form}}\longrightarrow\widehat\Gamma_X,\quad
i_0(c) = (c, 0),\qquad
s : \Gamma_X^{\mathrm{form}}\longrightarrow\widehat\Gamma_X,\quad
s(c) = (c, \Pi_X(c)).
\]
\end{definition}

\begin{theorem}[Group law of the normal-ordered extension; additivity of
$\overline\Pi_X$]
\label{thm:normal-ordered-extension-group-law}
Let $\widehat\Gamma_X$, $\star$, $\overline\Pi_X$, $i_0$, $s$ be as in
Definition~\ref{def:normal-ordered-extension}.  Then:
\begin{enumerate}[label = \textup{(\roman*)}]
\item $(\widehat\Gamma_X, \star)$ is an abelian group with identity
$(0, 0)$ and inverse $(c, T)^{-1} = (-c,\,-T + B(c, c)) = (-c,\,-T +
2\,\Pi_X(c))$.
\item The sequence
\[
0\to\Gamma_{\mathrm{gram}}\xrightarrow{T\mapsto(0, T)}\widehat\Gamma_X
\xrightarrow{\mathrm{pr}_1}\Gamma_X^{\mathrm{form}}\to 0
\]
is a central extension of abelian groups with cocycle $B$.
\item $\overline\Pi_X$ is a group homomorphism from
$(\widehat\Gamma_X, \star)$ to the additive group $\Gamma_{\mathrm{gram}}$.
\item The split section $s(c) = (c, \Pi_X(c))$ is additive, and
\[
\overline\Pi_X(i_0(c)) = \Pi_X(c),\qquad
\overline\Pi_X(s(c)) = 0.
\]
\item The change of variables $(c, T)\mapsto(c, T - \Pi_X(c))$ carries
$\star$ to componentwise addition; thus $\widehat\Gamma_X\cong
\Gamma_X^{\mathrm{form}}\oplus\Gamma_{\mathrm{gram}}$ as abstract abelian
groups, and $[B] = 0$ in additive cohomology.
\end{enumerate}
(proved/$\delta$.)
\end{theorem}

\begin{proof}
\emph{(i)} Associativity follows from the cocycle identity
$\delta B = 0$ (Lemma~\ref{lem:b-cocycle-identity}); the associator
$B(a, b) + B(a + b, c) - B(a, b + c) - B(b, c)$ vanishes by bilinearity.
Commutativity is symmetry of $B$.  The unit calculation $(c, T)\star(0,
0) = (c, T + B(c, 0)) = (c, T)$ and inverse $(c, T)\star(-c, -T + B(c,
c)) = (0, B(c, c) - B(c, c)) = (0, 0)$ (using $B(c, -c) = -B(c, c)$ by
bilinearity) close the abelian-group structure.

\emph{(ii)} Definition.

\emph{(iii)} Apply Lemma~\ref{lem:gram-additivity-defect}:
\[
\overline\Pi_X((c, T)\star(c', T'))
= \Pi_X(c + c') - T - T' - B(c, c')
= \Pi_X(c) + \Pi_X(c') - T - T'
= \overline\Pi_X(c, T) + \overline\Pi_X(c', T').
\]

\emph{(iv)} For the section,
\[
s(c)\star s(c')
= (c + c',\,\Pi_X(c) + \Pi_X(c') + B(c, c'))
= (c + c',\,\Pi_X(c + c'))
= s(c + c').
\]
The identities $\overline\Pi_X(i_0(c)) = \Pi_X(c) - 0 = \Pi_X(c)$ and
$\overline\Pi_X(s(c)) = \Pi_X(c) - \Pi_X(c) = 0$ are immediate.

\emph{(v)} The map $(c, T)\mapsto(c, T - \Pi_X(c))$ is a bijection with
inverse $(c, T)\mapsto(c, T + \Pi_X(c))$.  Direct calculation gives
\[
(c, T - \Pi_X(c)) + (c', T' - \Pi_X(c'))
= (c + c',\,T + T' - \Pi_X(c) - \Pi_X(c'))
= (c + c',\,(T + T' + B(c, c')) - \Pi_X(c + c')),
\]
matching the change of variables applied to $(c, T)\star(c', T')$.
\end{proof}

% -------------------------------------------------------------------
\subsection{The fixed-lift raw-pushforward obstruction theorem}
\label{subsec:raw-gram-descent-no-go}
% -------------------------------------------------------------------

\begin{definition}[Raw homogeneous and fixed-lift $\Pi_X$-pushforwards]
\label{def:raw-pi-pushforward}
Let $P = \bigoplus_{c\in\Gamma_X^{\mathrm{form}}} P_c$ be a
$\Gamma_X^{\mathrm{form}}$-graded primitive object.  The
\emph{raw homogeneous $\Pi_X$-pushforward} is
\[
\bigl(\Pi_{X, *}^{\mathrm{raw}} P\bigr)_\gamma
:= \bigoplus_{\Pi_X(c) = \gamma} P_c.
\]
The \emph{strict fixed-lift raw $\Pi_X$-pushforward} is the narrower
operation obtained by choosing one lift $L(\gamma) \in
\Gamma_X^{\mathrm{form}}$ for every retained $\gamma$ and setting
\[
\bigl(\Pi_{X, *}^{\mathrm{raw}, L} P\bigr)_\gamma
:= P_{L(\gamma)}.
\]
\end{definition}

\begin{theorem}[Raw homogeneous fixed-lift $\Pi_X$-pushforward cannot
realize the type-II real-root strings]
\label{thm:raw-gram-descent-no-go}
Let
$P = \bigoplus_{c\in\Gamma_X^{\mathrm{form}}} P_c$ be a
$\Gamma_X^{\mathrm{form}}$-graded Lie superalgebra with $[P_c, P_{c'}]
\subset P_{c + c'}$.  Suppose a strict fixed-lift raw pushforward of
$P$ along the quadratic map $\Pi_X$ were a $\Gamma_{\mathrm{gram}}$-graded
Lie superalgebra structure on the displayed bracket channels of chosen
charge lifts.  Then every nonzero bracket channel $[P_c, P_{c'}]$
contributing to that strict raw pushforward must satisfy $B(c, c') = 0$.

For the type-II real simple roots $(\delta_1, \delta_2, \delta_3)$ of
the Gritsenko--Nikulin algebra $\mathfrak g_{\Delta_5}$ with Cartan
matrix
\[
A_{\mathrm{II}}
= \begin{pmatrix} 2 & -2 & -2 \\ -2 & 2 & -2 \\ -2 & -2 & 2 \end{pmatrix},
\]
this condition is incompatible with the nonzero second real-root strings
$2\delta_i + \delta_j$, $i \ne j$.  The strict fixed-lift raw
$\Pi_X$-descent therefore cannot carry these brackets; they require the
normal-ordered extension $\widehat\Gamma_X$ and the additive homomorphism
$\overline\Pi_X$.
(proved/$\delta$, \cite{GN}.)
\end{theorem}

\begin{proof}
If the raw pushforward is $\Gamma_{\mathrm{gram}}$-graded, a nonzero
bracket of classes of raw Gram degrees $\Pi_X(c)$ and $\Pi_X(c')$ must
land in raw Gram degree $\Pi_X(c) + \Pi_X(c')$.  But the upstairs bracket
lands in physical degree $c + c'$, whose raw Gram shadow is
\[
\Pi_X(c + c') = \Pi_X(c) + \Pi_X(c') + B(c, c').
\]
Hence $B(c, c') = 0$ on every nonzero bracket channel.

Take physical lifts $c_i, c_j$ of distinct type-II real simple root
degrees $\gamma_i, \gamma_j$, $\Pi_X(c_i) = \gamma_i$ with $\gamma_i\ne
0$.  The Gritsenko--Nikulin Cartan matrix $A_{\mathrm{II}}$ has
off-diagonal entries $-2$, so distinct simple roots satisfy
$\langle\delta_i, \delta_j\rangle = -2$, and the real-root string
through $\delta_j$ in the $\delta_i$-direction includes the levels
$\delta_i + \delta_j$ and $2\delta_i + \delta_j$ (proved/$\delta$,
\cite[\S2--3]{GN}).  Both correspond to nonzero brackets, hence raw
pushforward forces
\[
B(c_i, c_j) = 0,\qquad
B(c_i, c_i + c_j) = 0.
\]
Bilinearity and polarization give
\[
B(c_i, c_i + c_j) = B(c_i, c_i) + B(c_i, c_j)
= 2\,\Pi_X(c_i) + 0 = 2\,\gamma_i,
\]
which is nonzero in the torsion-free lattice $\Gamma_{\mathrm{gram}}$.
Contradiction.
\end{proof}

\begin{remark}[Scope of the no-go]
\label{rem:no-go-scope}
Theorem~\ref{thm:raw-gram-descent-no-go} excludes the strict
\emph{homogeneous fixed-lift} raw pushforward.  It does not exclude
isolated $B$-isotropic bracket channels and does not decide the
mixed-lift fibre-summed construction in which several lifts of a single
Gram degree are summed before bracketing; the latter remains an open
mixed-lift question.  The normal-ordered extension removes exactly the
displayed obstruction because $\overline\Pi_X$ is additive on
$\widehat\Gamma_X$.  Chain-level Hall strictification
($A_\infty$-compatibility, cyclic equivariance, Frobenius,
multiplicative orientation) is a separate input system, named in
\S\ref{sec:k3xe-four-obstructions} and developed in
Chapter~\ref{chap:dirac-igusa-pro-object}.
\end{remark}

\begin{remark}[Quadratic obstruction; no linear trivialisation]
\label{rem:quadratic-obstruction}
Suppose $B = \delta L$ for some additive linear $L : \Gamma_X^{\mathrm
{form}}\to\Gamma_{\mathrm{gram}}$.  Setting $c' = c$, $B(c, c) = 2 L(c)
- L(2 c)$; additivity gives $L(2 c) = 2 L(c)$, so $B(c, c) = 0$,
contradicting $B(c, c) = 2\,\Pi_X(c) \ne 0$ for any $c$ with
$(Q, Q), (Q, P), (P, P)$ not all zero.  Hence no additive linear
trivialisation exists.  The quadratic primitive $\Pi_X$ is necessary;
trivializing the additive cocycle requires a quadratic cochain, not a
linear one (proved/$\gamma$).
\end{remark}

% -------------------------------------------------------------------
\subsection{Normal-ordering flag formula}
\label{subsec:normal-ordering-flag-formula}
% -------------------------------------------------------------------

\begin{lemma}[Multiplication of raw placements]
\label{lem:multiplication-of-raw-placements}
For $c_1, \ldots, c_k \in \Gamma_X^{\mathrm{form}}$,
\[
i_0(c_1)\star\cdots\star i_0(c_k)
= \biggl(\sum_i c_i,\ \sum_{i < j} B(c_i, c_j)\biggr),
\]
and consequently
\[
\overline\Pi_X\!\left(i_0(c_1)\star\cdots\star i_0(c_k)\right)
= \sum_i \Pi_X(c_i).
\]
(proved/$\delta$.)
\end{lemma}

\begin{proof}
Induct on $k$.  The case $k = 2$ is the definition of $\star$.  At
step $k\to k + 1$,
\[
B\!\left(\sum_{i\le k} c_i,\,c_{k + 1}\right)
= \sum_{i\le k} B(c_i,\,c_{k + 1})
\]
by bilinearity.  Applying $\overline\Pi_X$ subtracts the accumulated
pairwise $B$-term from $\Pi_X(\sum_i c_i) = \sum_i \Pi_X(c_i) +
\sum_{i < j} B(c_i, c_j)$.
\end{proof}

\begin{remark}[Normal-ordered primitive recognition target]
\label{rem:normal-ordered-recognition-target}
The interface with the BKM denominator algebra is the corrected route
\[
\Gamma_X^{\mathrm{form}}\hookrightarrow\widehat\Gamma_X
\xrightarrow{\overline\Pi_X}\Gamma_{\mathrm{gram}}
\xrightarrow{\alpha}\Lambda_{II}^{2,1},
\]
where $\alpha(n, l, m) = 2 n f_2 - l f_3 + 2 m f_{-2}$ is the type-IV
embedding into the BKM root lattice (proved/$\delta$, \cite{GN}).  At
chain level this becomes the descent $\overline\Pi_{X, *}^{\Theta}$ of
Chapter~\ref{chap:dirac-igusa-pro-object}.  The primitive recognition
problem is to construct a protected primitive Hall algebra whose
normal-ordered descended bracket is the Borcherds--Kac bracket of
$\mathfrak g_{\Delta_5}$.  Raw Gram pushforward is not an admissible
recognition target.
\end{remark}

% =====================================================================
\section{The hybrid $\operatorname{Ran}^{\mathrm{hyb}}(E)$ factorization
carrier}
\label{sec:k3xe-hybrid-ran-carrier}
% =====================================================================

The K3 direction is integrated.  What remains is a chiral object on the
elliptic factor $E$.  The naive carrier is the Ran space
$\operatorname{Ran}(E)$ of finite subsets, but a one-dimensional
subscheme with positive elliptic degree projects onto all of $E$.  The
hybrid carrier $\operatorname{Ran}^{\mathrm{hyb}}(E)$ is the disjoint
union of the projection-finite local stratum $\operatorname{Ran}(E)_{b
= 0}$ and the wrapped stratum $\operatorname{Ran}^{\mathrm{wr}}(E)_{b
> 0}$, with mixed local/wrapped correspondences supplied as additional
finite-stage data.

% -------------------------------------------------------------------
\subsection{Projection-locality obstruction}
\label{subsec:projection-locality-obstruction}
% -------------------------------------------------------------------

\begin{lemma}[Projection-locality obstruction]
\label{lem:projection-locality-obstruction}
Let $C \subset X = S\times E$ be a one-dimensional closed subscheme
(reduced and irreducible, for definiteness) with
\[
\deg_E(C) := \deg\bigl(p_E\!\restriction_C : C\to E\bigr) > 0.
\]
Then $p_E(C) = E$, hence $p_E(C)$ is not a finite subset of $E$ and
$C$ is not local on $\operatorname{Ran}(E)$.
(proved/$\epsilon$.)
\end{lemma}

\begin{proof}
The pushforward $p_{E, *}[C]$ is a positive multiple of the fundamental
class $[E]$, so the image $p_E(C)$ is a closed one-dimensional subset of
the irreducible curve $E$.  An irreducible curve has only itself as a
one-dimensional closed subset, so $p_E(C) = E$.
\end{proof}

\begin{remark}[Geometric versus Borcherds elliptic degree]
\label{rem:geometric-vs-borcherds-degree}
The lemma fixes the necessity of a wrapped stratum.  The geometric
elliptic-degree map $b_R^{\mathrm{geom}}$, on a finite Hall stage $R$,
records the integer $\deg_E$ of a chosen retained class.  The trace
exponent $m_R := \mathrm{pr}_3\overline\Pi_X$, on the same stage,
records the third coordinate of the normal-ordered Gram pushforward.
The two are not equal as functions on the formal lattice; the Borcherds
exponent $m$ records the magnetic Mukai pairing $(P, P)/2$, which sees
$\Lambda_S$-square data, while $b_R^{\mathrm{geom}}$ records the
$E$-degree of the geometric support, which sees $H^0(S)\oplus H^4(S)$
data through $r$ and $\mathrm{ch}_2$ of the K3 factor.  The wrapped
stratum carries $b_R^{\mathrm{geom}} > 0$ branes; the local stratum
carries $b_R^{\mathrm{geom}} = 0$ branes whose magnetic component lies
in the projection-finite kernel.  This is the
$\operatorname{Ran}(E)$-support-locality obstruction in the
K3-integrated chiral shadow.
\end{remark}

% -------------------------------------------------------------------
\subsection{The hybrid carrier}
\label{subsec:hybrid-carrier-definition}
% -------------------------------------------------------------------

\begin{definition}[Hybrid Ran carrier]
\label{def:hybrid-ran-carrier}
The \emph{hybrid Ran carrier} on $E$ is the disjoint union
\[
\operatorname{Ran}^{\mathrm{hyb}}(E)
:= \operatorname{Ran}(E)_{b = 0}\,\sqcup\,\operatorname{Ran}^{\mathrm{wr}}(E)_{b > 0},
\]
with the projection-finite local stratum
$\operatorname{Ran}(E)_{b = 0}$ and the wrapped stratum
$\operatorname{Ran}^{\mathrm{wr}}(E)_{b > 0}$ defined as follows.
\begin{enumerate}[label = \textup{(\roman*)}]
\item $\operatorname{Ran}(E)_{b = 0}$ is the standard Ran space of
finite (unordered) subsets $T = \{x_1, \ldots, x_k\} \subset E$
(\cite{BD,FrancisGaitsgoryCKD}); its functor of points sends a test
scheme $S'$ to the set of finite closed subschemes $T'\subset E\times
S'$ whose projection to $S'$ is finite \'etale of constant fibre size
$\le R$ for some chosen finite Hall height $R$.  This is the
$b_R^{\mathrm{geom}} = 0$ stratum: branes whose K3 factor has zero
elliptic degree.
\item $\operatorname{Ran}^{\mathrm{wr}}(E)_{b > 0}$ is the
\emph{wrapped prequotient stratum}: a colim of pre-quotient stacks
$\mathfrak W_{R, b}$ parameterising rigidified compactly supported
B-branes $\mathcal F\in D^b(\mathrm{Coh}\,X)$ of bounded retained Liu--
Hilbert class $\Xi = (\gamma, [a, b], (P_i), N)$ with positive elliptic
degree $b = \deg_E(\mathrm{ch}_2(\mathcal F)) > 0$, modulo
$E$-translation up to the chosen anchor (\S\ref{subsec:e-quotient-anchor}).
\end{enumerate}
The two strata are exchanged only by the mixed local/wrapped
correspondences of \S\ref{subsec:mixed-correspondences}; they are not
identified.
\end{definition}

\begin{remark}[Two strata, two registers]
\label{rem:two-strata-two-registers}
On the $b = 0$ stratum the standard Ran/factorization formalism applies
and produces a chiral algebra in $\mathrm{Fact}(\operatorname{Ran}(E))$
(folklore/$\epsilon$, \cite{BD,FrancisGaitsgoryCKD}).  On the $b > 0$
stratum the support of $\mathrm{Supp}\,\mathcal F$ projects onto $E$, so
the brane is global; its data live on the wrapped prequotient and after
$E$-quotient become $E$-equivariant data on the elliptic curve.  The
hybrid carrier is the smallest carrier reflecting both strata; it is
not a single Ran space.
\end{remark}

% -------------------------------------------------------------------
\subsection{Mixed local/wrapped correspondences}
\label{subsec:mixed-correspondences}
% -------------------------------------------------------------------

\begin{definition}[Mixed local/wrapped correspondences (finite Hall
stage $R$)]
\label{def:mixed-correspondences}
Fix a finite Hall stage $R$ and retained Liu--Hilbert classes $\Xi_A,
\Xi_B, \Xi_C$ with $\Xi_C = \Xi_A + \Xi_B$ in the closure rules of
\cite{KSCoHA}.  The \emph{retained extension correspondence}
\[
\mathfrak E^{\mathrm{ret}}_{\Xi_A, \Xi_B; \Xi_C}
\xrightarrow{p}
\mathfrak M^{\mathrm{ss}}_{\Xi_A}\times\mathfrak M^{\mathrm{ss}}_{\Xi_B},
\qquad
\mathfrak E^{\mathrm{ret}}_{\Xi_A, \Xi_B; \Xi_C}
\xrightarrow{q}
\mathfrak M^{\mathrm{ss}}_{\Xi_C}
\]
is the closed derived flag-Quot/filtration stack over
$\mathfrak M^{\mathrm{ss}}_{\Xi_C}$, with $q$ proper or
$\mathrm{Coh}^{\mathrm{prop}}$-admissible in the compactified model
(folklore/$\epsilon$).  Three colours of correspondence appear,
indexed by the location of $\Xi_A, \Xi_B$ in
$\operatorname{Ran}^{\mathrm{hyb}}(E)$:
\begin{enumerate}[label = \textup{(LL)},leftmargin = *]
\item[\textup{(LL)}] \emph{local-local}: $b_A = b_B = 0$;
\item[\textup{(LW)}] \emph{ordered local/wrapped}: $b_A = 0$, $b_B > 0$;
\item[\textup{(WW)}] \emph{wrapped-wrapped}: $b_A, b_B > 0$.
\end{enumerate}
The arity-three shadow is the eight-word two-step binary flag atlas
\[
\{L, W\}^3 = \{LLL, LLW, LWL, LWW, WLL, WLW, WWL, WWW\},
\]
which records binary associativity only; higher coloured tree
configurations live on a separate coloured tree category
$\mathrm{Tree}^{\mathrm{col}}_R$, supplied as additional input
(folklore/$\epsilon$, \cite{CYQGVolIII}).
\end{definition}

\begin{remark}[Eight binary words versus colored trees]
\label{rem:eight-words-vs-colored-trees}
The eight binary words of Definition~\ref{def:mixed-correspondences}
exhaust the arity-three two-step compositions $\{L, W\}^3$, but they do
not catalogue higher coloured tree configurations, units, symmetry/order
conventions, refinement maps, descent, or overlaps.  Those data are
additional finite Hall input named at \S\ref{sec:k3xe-four-obstructions};
asserting them prematurely confuses binary associativity with the full
factorization-coherence structure (\cite{CYQGVolIII},
correspondence-programme remark).
\end{remark}

% -------------------------------------------------------------------
\subsection{Wrapped anchor and translation linearization}
\label{subsec:e-quotient-anchor}
% -------------------------------------------------------------------

\begin{definition}[Determinant anchor on the wrapped stratum]
\label{def:determinant-anchor}
For a retained $E$-stable family $\mathcal F$ on the wrapped stratum,
the \emph{determinant anchor line bundle} on $E$ is
\[
\lambda(\mathcal F)
:= \det Rp_{E, *}\mathcal F
\otimes \mathcal O_E\!\bigl(-\chi(\mathcal F)\,0_E\bigr).
\]
This is a degree-zero line bundle on $E$, hence a point of
$\mathrm{Pic}^0(E) \cong E$.  The translation law
\[
\lambda(t\cdot\mathcal F) = \lambda(\mathcal F) + \chi(\mathcal F)\,t,
\qquad t\in E,
\]
holds in $\mathrm{Pic}^0(E)$ (proved/$\epsilon$, \cite{Mukai1987}).
\end{definition}

\begin{lemma}[Connected $E$-descent: separated cohomological classes]
\label{lem:connected-e-descent}
For the connected component $E^{\circ}$ of the identity in the
$E$-translation action,
\[
H^*(BE; \mathbb F_2) = \mathbb F_2[u_1, u_2],\qquad
|u_i| = 2.
\]
Hence
\[
H^1(BE; \mathbb F_2) = 0,\qquad
H^2(BE; \mathbb F_2) = \mathbb F_2 u_1 \oplus \mathbb F_2 u_2.
\]
There is no degree-one connected character; there is a degree-two
connected gerbe class
\[
\alpha^{E,\mathrm{free}} = a_1 u_1 + a_2 u_2 \in H^2(BE; \mathbb F_2).
\]
(proved/$\epsilon$, \cite{NIKULIN}.)
\end{lemma}

\begin{proof}
$E^{\mathrm{top}}\simeq T^2$ has classifying space $BE\simeq BT^2$ and
$H^*(BT^2; \mathbb F_2) = \mathbb F_2[u_1, u_2]$ with both $u_i$ of
degree $2$ (mod-$2$ Chern classes of the universal line bundles).
$H^1$ vanishes; $H^2$ is the displayed two-dimensional $\mathbb F_2$
vector space.  Vanishing of the connected gerbe class is the equation
$a_1 = a_2 = 0$ on the actual Borel/edge class of the equivariant
reduced determinant complex, not a consequence of $H^1(BE) = 0$ or
ordinary translation invariance.
\end{proof}

\begin{lemma}[{Finite stabilizer $E[N]$-descent: gerbe and linearization classes}]
\label{lem:finite-stabilizer-e-descent}
For the order-two finite subgroup $E[2]\cong(\Z/2)^2$,
\[
H^*(BE[2]; \mathbb F_2) = \mathbb F_2[x_1, x_2],\qquad
|x_i| = 1.
\]
The degree-two gerbe class is
\[
\beta^{E, E[2]}
= b_{20} x_1^2 + b_{11} x_1 x_2 + b_{02} x_2^2,\qquad
(b_{20}, b_{11}, b_{02}) = (r_1,\,r_1 + r_2 + r_3,\,r_2),
\]
detected on cyclic subgroup restrictions by joint reduction; the $r_i
\in\mathbb F_2$ are the three nonzero point-stabilizer parities.
After $\beta^{E, E[2]} = 0$ (i.e.\ $r_1 = r_2 = r_3 = 0$), a separate
degree-one linearization class remains:
\[
\lambda^{E, E[2]} = \lambda_1 x_1 + \lambda_2 x_2 \in H^1(BE[2]; \mathbb F_2),
\qquad \rho_1 = \lambda_1,\ \rho_2 = \lambda_2,\ \rho_3 = \lambda_1 + \lambda_2.
\]
The $r_i$ are gerbe bits in $H^2$; the $\rho_i$ are linearization bits
in $H^1$; the two live in distinct cohomological degrees and remain
independent.
For even $N\ge 4$ with $2^a\parallel N,\ a\ge 2$,
\[
H^*\!\bigl(B(\Z/2^a)^2; \mathbb F_2\bigr)
= \Lambda(x_1, x_2)\otimes\mathbb F_2[y_1, y_2],
\]
\[
\beta^{E, N} = A_1^{(N)} y_1 + A_{12}^{(N)} x_1 x_2 + A_2^{(N)} y_2,
\qquad
\lambda^{E, N} = \lambda_1^{(N)} x_1 + \lambda_2^{(N)} x_2.
\]
The mixed term $A_{12}^{(N)}$ is invisible to cyclic order-two restrictions;
even $N\ge 4$ tests must be checked on the full two-primary generators.
For odd $N$, the mod-2 orientation obstruction vanishes by transfer.
(proved/$\epsilon$.)
\end{lemma}

\begin{proof}
$E[2]\cong(\Z/2)^2$ has $H^*(B(\Z/2)^2; \mathbb F_2) = \mathbb F_2[x_1,
x_2]$ with $|x_i| = 1$.  The reduction of $\beta^E\in H^2(BE; \mathbb
F_2)$ along the inclusion $E[2]\hookrightarrow E$ gives the displayed
quadratic in $x_1, x_2$; reduction to cyclic subgroups gives the linear
combinations $r_i$ as in \cite[\S2]{NIKULIN}.  The degree-one linearization
class $\lambda^{E, E[2]}$ is the residual character of the underlying
line bundle after $\beta = 0$ is imposed; it lives in $H^1$ and is
distinct from the gerbe $\beta\in H^2$ in degree.  Even $N\ge 4$
introduces the polynomial generators $y_i \in H^2(B(\Z/2^a))$ and the
mixed term $x_1 x_2$, which on cyclic restrictions vanishes; full
two-primary detection is needed.  Odd $N$ contributes only $\mathbb
F_p$-cohomology with $p$ odd, on which the mod-$2$ orientation has zero
restriction by the transfer.
\end{proof}

\begin{remark}[Translation linearization criterion, not vanishing]
\label{rem:translation-linearization-criterion}
For a stabilizer $H \subset E[N]$ and a determinant anchor line bundle
$\lambda(\mathcal F)$, ordinary translation invariance $g^*\lambda
\simeq \lambda$ in $\mathrm{Pic}^0(E)$ does not choose coherent
isomorphisms $\phi_g : \lambda \to g^*\lambda$.  After the square-root
gerbe is killed, the choices form a character torsor in $H^1(BH;
\mathbb F_2)$, and quotient orientation requires the linearization
class
\[
\lambda^H \in H^1(BH; \mathbb F_2)
\]
to vanish.  This is a \emph{criterion} for descent on the wrapped
stratum; it is not implied by $g^*[\lambda] = [\lambda]$ in
$\mathrm{Pic}(E)$.  The translation law
$\lambda(t\cdot\mathcal F) = \lambda(\mathcal F) + \chi(\mathcal F) t$
of Definition~\ref{def:determinant-anchor} carries unit weight only
when $\chi(\mathcal F) \ne 0$; otherwise the anchor is unweighted and
descends only after the linearization class vanishes.
(proved/$\epsilon$ as a criterion.)
\end{remark}

\begin{remark}[Mod-2 character does not control odd-order anchor
characters]
\label{rem:mod2-not-odd-order}
The mod-$2$ orientation character does not by itself control odd-order
anchor characters.  For anchor descent on the wrapped stratum, also
compute the actual stabilizer character on the chosen anchor
trivialization, valued in $\widehat H = \mathrm{Hom}(H, \C^\times)$, or
define the retained stabilizer as preserving that trivialization.
(unverified/$\epsilon$ at the manuscript level; supplied as part of the
finite Hall datum.)
\end{remark}

% -------------------------------------------------------------------
\subsection{Cusp polarization and chamber transport}
\label{subsec:cusp-polarization-chamber}
% -------------------------------------------------------------------

\begin{definition}[Cusp polarization on $\Gamma_{\mathrm{eff}}$]
\label{def:cusp-polarization}
The chamber convention $0 < |s|\ll|q|\ll|r|^{-1}\ll 1$ at the standard
cusp $\mathfrak c_\infty$ determines the cusp-positive semigroup
$\Gamma_{\mathrm{eff}}$ of Definition~\ref{def:gram-index-lattice}.  The
order on triples is lexicographic: $m > 0$ first because $s$ is
smallest; if $m = 0$ then $n > 0$ because $q$ is next; if $m = n = 0$
then $l < 0$ because $|r|^{-1}\ll 1$.  This is a chamber convention for
the completed product, not a microscopic charge positivity statement.
\end{definition}

\begin{remark}[Chamber transport]
\label{rem:chamber-transport}
The pairing $\langle\gamma, \gamma'\rangle_{\mathrm{ind}} = 2(n m' + n'
m) - l l'$ is the Gram pairing on triples; the order on
$\Gamma_{\mathrm{eff}}$ is a Fock polarization at one cusp.  An element
of the duality group $\Sp_4(\Z)$ transports both the chamber and the
expansion to the corresponding product chamber at the transported cusp.
The arithmetic group $\Sp_4(\Z)$ is the symmetry of the genus-two
chemical potential $Z$ and of the invariant Gram plane on
$\Lambda^{3, 2}$; it is not asserted to be the full microscopic
T-/U-duality group of the K3$\times T^2$ compactification, which is
larger (folklore/$\beta$, \cite{HM,DVV}).
\end{remark}

\begin{remark}[Chamber dependence of the wrapped stratum]
\label{rem:chamber-dependence-wrapped}
The cusp chamber chooses a positive direction on
$\Gamma_{\mathrm{eff}}$.  At $\mathfrak c_\infty$ the wrapped stratum
carries $\deg_E > 0$ branes; at a transported cusp the wrapped
direction is the image of $\deg_E$ under the corresponding chamber
transport.  Mixed Hall correspondences are chamber-equivariant when the
finite Hall stage $R$ is compatible with the duality element; otherwise
the correspondence stack is the original closed flag-Quot stack
restricted to the new chamber.
\end{remark}

% =====================================================================
\section{Local protected observable algebra (sectorial source datum)}
\label{sec:local-protected-observable-algebra}
% =====================================================================

The compact realization route of Chapter~\ref{chap:dirac-igusa-pro-object}
takes as supplied input a chain-level local observable system on
opens $U\subset X = S\times E$.  The system is graded by the
algebraic/effective Hall support, factorizes on disjoint opens, and
restricts on $E$-projection-finite supports to a chiral object on
$\operatorname{Ran}(E)_{b = 0}$.  The data are external assumptions
named in the literature; this section records them as the source
interface used downstream.

\begin{definition}[Local protected observable algebra]
\label{def:local-protected-observable-algebra}
Let $U\subset X = S\times E$ be open.  Let
$\Gamma_{X, \sigma}^{\mathrm{eff}}(U)\subset\Gamma_X^{\mathrm{alg}}
\subset\Gamma_X^{\mathrm{form}}$ be the supplied algebraic/effective
charge support.  For $c\in\Gamma_{X, \sigma}^{\mathrm{eff}}(U)$, let
$\mathfrak M_c(U)$ be the supplied derived moduli stack of compactly
supported B-branes on $U$ of Mukai charge $c$.  The PTVV theorem supplies
the ambient $(-1)$-shifted symplectic structure on the $\mathrm{CY}_3$
perfect-complex moduli problem (proved/$\beta$, \cite{PTVV2013}).  Let
$\Phi_c$ denote the BBDJS perverse sheaf $P^\bullet_{\mathfrak M_c, s_c}$
on an oriented d-critical truncation, when such a d-critical structure
and square-root orientation are supplied (proved/$\beta$,
\cite[Theorem~6.9]{BBDJS2015}).  Let $o_c$ be the orientation line, a
square root of the determinant line of the cotangent complex of
$\mathfrak M_c(U)$, supplied as part of the Hall datum.

The \emph{local protected observable algebra of $X$ on $U$} is the
source object
\[
\mathcal A_X(U)
:= \bigoplus_{c\in\Gamma_{X, \sigma}^{\mathrm{eff}}(U)}
H_*^{\mathrm{BM}}\!\bigl(\mathfrak M_c(U),\,\Phi_c\otimes o_c\bigr),
\]
graded by the supplied algebraic/effective support, not by the full
formal lattice $\Gamma_X^{\mathrm{form}}$.  For pairwise disjoint
$U_1, \ldots, U_k\subset X$, the proposed factorization map is
\[
\mathcal A_X(U_1)\otimes\cdots\otimes\mathcal A_X(U_k)
\longrightarrow\mathcal A_X(U_1\sqcup\cdots\sqcup U_k),
\]
defined chain-level by Massey--Saito Thom--Sebastiani for vanishing
cycles
\[
\Phi_{F_1\oplus\cdots\oplus F_k}
\simeq \Phi_{F_1}\boxtimes\cdots\boxtimes\Phi_{F_k}
\]
on disjoint d-critical charts (proved/$\beta$,
\cite{MasseyST,SaitoMHM}), together with the Ext-vanishing
$\mathrm{Ext}^*(\mathcal F, \mathcal G) = 0$ for branes
$\mathcal F, \mathcal G$ with disjoint supports
(folklore/$\beta$).
\end{definition}

\begin{remark}[Source interface: external assumptions]
\label{rem:source-interface-external-assumptions}
The components are external assumptions: PTVV $(-1)$-shifted symplectic
structure on derived moduli of B-branes (proved/$\beta$,
\cite{PTVV2013}); BBDJS vanishing-cycle perverse sheaf and its
Thom--Sebastiani isomorphism (proved/$\beta$,
\cite{MasseyST,SaitoMHM,BBDJS2015}); orientation lines and
Joyce--Upmeier-compatible multiplicative orientation data (supplied
separately, proved/$\beta$, \cite[Theorem~4.1]{JoyceUpmeier} or
\cite{KSCoHA}).  The factorization map relies on disjoint-supports
Ext-vanishing for compactly supported branes (folklore/$\beta$;
absent for non-compact supports, where one recovers chiral algebra
structure, not commutative factorization).  Compactness on $X = S\times
E$ is open because the relevant moduli of branes are typically
non-quasicompact in $\Lambda_S$-charge; the sectorial truncation of
\S\ref{sec:k3xe-hybrid-ran-carrier} is the candidate truncation,
conditional on the four obstructions of
\S\ref{sec:k3xe-four-obstructions}.
\end{remark}

% =====================================================================
\section{The four obstructions and the conditional comparison target}
\label{sec:k3xe-four-obstructions}
% =====================================================================

The hybrid carrier and the source interface produce a candidate compact
holomorphic $E_3$-factorization algebra and its $K3$-specialization to a
chiral object on $\operatorname{Ran}^{\mathrm{hyb}}(E)$.  The
cross-level comparison
$\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}}) =
\Delta_5$ is conditional on four obstruction classes named at the level
of \S5.8 of the manuscript and tracked across the swarm
((see \texttt{notes/swarm\_20260430/reports/})).  The chapter records them here as
the conditioning data feeding Chapter~\ref{chap:dirac-igusa-pro-object}.

\begin{description}
\item[$(\mathrm{D0})$ {\rm D0-degeneration limit.}]
The cosection-reduced d-critical orientation theory on
$\mathrm{Hilb}^n(X)\times\mathrm{Sym}^n(X)$, in the D0-degeneration limit
$n\to\infty$, supplies the orientation line on the local stratum
(folklore/$\delta$; conditional, swarm probes A005, A011, A026, A037,
A042).
\item[$(\mathrm{O1})$ {\rm Strong reduced orientation.}]
The K3$\times$E-quotient self-Ext frame bundle carries a strong reduced
orientation on the wrapped stratum, descending the BBDJS orientation
line $o_c$ across the $E$-quotient (folklore/$\delta$; conditional,
swarm probes A074, A076, A082).
\item[$(\mathrm{O1}^+)$ {\rm Weyl-equivariant transport.}]
The orientation transports $W^{(2)}(\Lambda_{II}^{2, 1})$-equivariantly
along reflections, fixing the orientation character
$\epsilon_o = \nu_{\Delta_5}$ on the BKM Weyl group (folklore/$\delta$;
conditional, swarm probes A047, A049, A089).
\item[$(\mathrm{O2})$ {\rm Local Pfaffian wall normal form.}]
On type-II walls of $\Lambda_{II}^{2, 1}$, the local Pfaffian wall
normal form is the $4096 = 2^{12}$ sign sum on the half-Hilbert orbit
(computed/$\delta$ at small height; conditional at full height,
swarm probes A047, A092, A100).
\end{description}

The protected scalar shadow on the closed K3$\times$E$\to$point
cobordism is the OP/DT identity
\[
Z^X_{\mathrm{DT}}(T, Q, P)
= Z^X_{\mathrm{OP}}(P, Q, T)
= -4096\,\Delta_5(Z)^{-2}
\qquad\text{(proved/$\beta$, \cite{OB,OPand,DT}).}
\]
Equivalently $\chi_{10}^{\mathrm{OP}} = (64^{-1}\Delta_5)^2 = 4096^{-1}\Delta_5^2$
and $Z^X_{\mathrm{OP}} = -(\chi_{10}^{\mathrm{OP}})^{-1}$; the factor
$4096 = 64^2$ is a theta-leading normalization conversion and the minus
sign is the OP scalar convention.  The orientation-forgetful shadow
\[
Z_{\mathrm{BPS}}^{K3\times E}
= (\Phi_{10}^{\mathrm{un}})^{-1}
= \Delta_5^{-2}
\]
is the level-$n$ protected trace of $\mathfrak A_{K3\times E}$ on the
closed cobordism in the unnormalized convention $\Phi_{10}^{\mathrm{un}}
= \Delta_5^2$; the squared scalar cannot recover the orientation
character that distinguishes $\Delta_5$ from $-\Delta_5$.  Promotion to a
$3d$ gravitational path integral requires the Hall--Borcherds residual
of \cite{ChiralBarCobarVolII} and is not claimed.  The conditional
cross-level identity
$\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}}) =
\Delta_5$ supplies the orientation/Pfaffian datum under
$(\mathrm{D0}), (\mathrm{O1}), (\mathrm{O1}^+), (\mathrm{O2})$.

\begin{remark}[Cross-volume consistency]
\label{rem:cross-volume-consistency}
The $\kappa$-tuple $(0, 0, 3, 5, 24)$ is consistent across
\cite{CYQGVolIII} (Vol III), the Hall--Borcherds
residual of \cite{ChiralBarCobarVolII} (Vol II), and the
Beilinson--Drinfeld factorization framework of \cite{BD} via Vol I
\cite{ChiralBarCobarVolI}.  The local model
$\R^2_{\mathrm{top}}\times\C^2_{\mathrm{hol}}$ + brane completion of
\cite{MixedHTSCompanion} contributes the
holomorphic de Rham obstruction class on the global target; the
identity $Z_{\mathrm{BPS}}^{K3\times E} = \Delta_5^{-2}$ does not
promote to the global target via formal Hamiltonian BF, and the
Hall--Borcherds residual is the cross-volume bridge.
\end{remark}

% =====================================================================
\section{Notation summary and chapter outputs}
\label{sec:k3xe-notation-summary}
% =====================================================================

\begin{description}
\item[$X = S\times E$.]
Smooth complex projective Calabi--Yau threefold; $S$ is a K3 surface,
$E$ a smooth elliptic curve.  $\dim_\C X = 3$.
\item[$\Lambda_S$.]
Mukai lattice; even unimodular signature $(4, 20)$.
$\Lambda_S\cong U^{\oplus 4}\oplus E_8(-1)^{\oplus 2}\cong II_{4, 20}$.
\item[$\Gamma_X^{\mathrm{form}}, \Gamma_X^{\mathrm{phys}}$.]
Formal full-Mukai dyonic lattice $\Lambda_S\oplus\Lambda_S$.  The
superscript ``$\mathrm{phys}$'' is mnemonic only; not the
$\mathcal N = 4$ charge lattice.
\item[$\Gamma_X^{\mathrm{alg}},\Gamma_{X, \sigma}^{\mathrm{eff}}$.]
Algebraic K-class lattice $\subset\Gamma_X^{\mathrm{form}}$; supplied
$\sigma$-effective semigroup $\subset\Gamma_X^{\mathrm{alg}}$.
\item[$\Gamma_{\mathrm{gram}} = \Z^3$.]
Gram-index lattice, $(n, l, m)$.
\item[$\Pi_X$.]
Quadratic Gram map, $\Pi_X(Q, P) = ((Q, Q)/2,\,(Q, P),\,(P, P)/2)$.
\item[$B$.]
Symmetric bilinear cocycle, $B(c, c') = (Q\cdot Q',\,Q\cdot P' + Q'\cdot
P,\,P\cdot P')$; satisfies $B = -\delta\Pi_X$ and $B(c, c) = 2\Pi_X(c)$.
\item[$\widehat\Gamma_X$.]
Normal-ordered extension $\Gamma_X^{\mathrm{form}}\oplus_B\Gamma_{\mathrm
{gram}}$; abelian under $\star$.
\item[$\overline\Pi_X$.]
Additive normal-ordered Gram homomorphism $\overline\Pi_X(c, T) =
\Pi_X(c) - T$.
\item[$\operatorname{Ran}^{\mathrm{hyb}}(E)$.]
Hybrid carrier $\operatorname{Ran}(E)_{b = 0}\sqcup\operatorname{Ran}^{\mathrm{wr}}(E)_{b > 0}$
on the elliptic factor.
\item[$\mathcal D_X = \Delta_5$, $\mathrm{den}(\mathfrak g_{\Delta_5})$,
$\mathrm{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})$.]
Three named scalars at level five: automorphic section, BKM denominator,
compact Pfaffian (View \textcircled{1}, \textcircled{2}, \textcircled{3}).
\end{description}

The chapter outputs are: (a) the formal Mukai sector
$\Gamma_X^{\mathrm{form}} = \Lambda_S\oplus\Lambda_S$ and its three-tier
support hierarchy; (b) the lattice polarization $B = -\delta\Pi_X$ as the
full structural content of the Gram defect; (c) the normal-ordered
extension $\widehat\Gamma_X$ with additive homomorphism
$\overline\Pi_X$, fixed by the fixed-lift raw-pushforward obstruction
theorem; (d) the hybrid Ran carrier
$\operatorname{Ran}^{\mathrm{hyb}}(E)$, fixed by the projection-locality
obstruction; (e) the connected/finite split of the $E$-descent classes,
with the linearization criterion separated from the gerbe class; (f)
the local protected observable algebra source interface, supplied as
external assumption; (g) the four obstructions
$(\mathrm{D0}), (\mathrm{O1}), (\mathrm{O1}^+), (\mathrm{O2})$
conditioning the cross-level identity ②$\leftrightarrow$③.

Chapter~\ref{chap:dirac-igusa-pro-object} consumes these outputs as fixed
input data and constructs the Dirac--Igusa pro-object $\mathfrak D_X^{
\mathrm{DI}} = \lim_R(\mathcal A_{X, R}^{E_3}, F_{X, R}^{\mathrm{hyb}},
\Gamma_{X, R}, \Pi_X, \Phi_R, o_R, H_R, P_R^\Pi, C_{X, R},
\Theta_{\mathrm{Kos}, R}, \mathcal L_{\mathrm{Pf}, R}, \mathrm{pf}_{X, R},
\epsilon_{o, R}, \mathrm{Rec}_R)$.

% =====================================================================
% End of Chapter 2.
% =====================================================================
