% !TEX root = ../main.tex
%
% Chapter 8 — View IV: the mirror discriminant.
% Conjectural identification of \(\Delta_5^{-2}\) with the discriminant
% section of the K3-mirror period family, transported across the
% genus-two Siegel space via the exceptional isomorphism
% \(\Sp_4 \simeq \mathrm{Spin}(3,2)\).
%
% The chapter is self-contained: the lattice conventions of
% Chapter~2 (\(\Lambda_S\) Mukai, signature \((4,20)\); \(\Lambda_{II}^{2,1}\)
% type-II symmetric polarisation) and the automorphic side of Chapter~3
% (\(\Delta_5 \in M_5(\Sp_4(\Z), \nu_{\Delta_5})\)) are imported by
% reference, not redefined. Everything attached to View~\textcircled{4}
% is conjectural; the cross-level identities \textcircled{4}\(\leftrightarrow\)\textcircled{1},
% \textcircled{4}\(\leftrightarrow\)\textcircled{2}, \textcircled{4}\(\leftrightarrow\)\textcircled{5}
% are not theorems in this manuscript. View~\textcircled{4} is the only
% one of the five views that is conjectural at this moment.

\providecommand{\ClaimStatusConjectured}{}
\providecommand{\ClaimStatusHeuristic}{}
\providecommand{\ClaimStatusConditional}{}
\providecommand{\ClaimStatusProvedElsewhere}{}
\providecommand{\ClaimStatusOpen}{}
\providecommand{\ClaimStatusFolklore}{}

\chapter{The mirror discriminant}
\label{ch:view4-mirror}

\section{The mirror discriminant}
\label{sec:view4-mirror-discriminant}

The four views developed so far place \(\Delta_5\) on chains that begin
with explicit modular or representation-theoretic data: the
Borcherds--Gritsenko--Nikulin section of the weight-\(5\) automorphic
line over \(\Sp_4(\Z) \backslash \mathcal H_2\) (View~\textcircled{1}),
the denominator
\(\operatorname{den}(\mathfrak g_{\Delta_5}) = 64^{-1} \Delta_5(2Z)\) of
the Borcherds--Kac--Moody Lie superalgebra on \(\Lambda_{II}^{2,1}\)
(View~\textcircled{2}), the protected Pfaffian
\(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})\) of the
Dirac--Igusa pro-object (View~\textcircled{3}), and the singular theta
lift of the weak Jacobi form \(\phi_{0,1}\) under
\(\mathrm{Mp}(4,\R) \leftrightarrow \mathrm O(3,2)\) (View~\textcircled{5}).
The fifth view is geometric. Let \(\mathcal P_{K3}\) be the period
family of \(K3\)-mirror pairs; let
\(\mathfrak D_{\mathrm{per}} \subset \mathcal P_{K3}\) be its
discriminant locus, the divisor along which the local Hodge filtration
degenerates. The expected statement is the equality
\begin{equation}
\label{eq:view4-conjecture}
[\mathfrak D_{\mathrm{per}}]
\;=\;
[\,\Delta_5^{-2}\,]
\qquad
\text{(equality of divisor classes on the }
(K3 \times E)\text{-component)},
\end{equation}
where \([\Delta_5^{-2}]\) is the principal divisor of the meromorphic
section \(\Delta_5^{-2}\) of the appropriate automorphic line. The four
preceding chains supply the Borcherds product, the BKM denominator, the
Dirac--Igusa pro-object, and the theta-lift bridge; the fifth view asks
for an independent geometric origin of the same form on the period
side.

The status, recorded in advance, is conjectural. View~\textcircled{4}
is the sole view in this manuscript whose load-bearing identification
is not currently a theorem. The cross-level identities
\textcircled{4}\(\leftrightarrow\)\textcircled{1},
\textcircled{4}\(\leftrightarrow\)\textcircled{2},
\textcircled{4}\(\leftrightarrow\)\textcircled{5} are open. The
identifications proved or conditionally proved on the other four
chains are imported from the previous chapters unchanged; the present
chapter neither weakens nor strengthens those chains.

The handle \(\Delta_5\) splits into three names already in this
manuscript. The automorphic section over
\(\Sp_4(\Z) \backslash \mathcal H_2\) is denoted
\(\mathcal D_X = \Delta_5\) (View~\textcircled{1}); the BKM denominator
is
\(\operatorname{den}(\mathfrak g_{\Delta_5}) = 64^{-1} \Delta_5(2Z)\)
(View~\textcircled{2}); the protected Pfaffian is
\(\operatorname{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})\)
(View~\textcircled{3}). The mirror conjecture concerns the first: the
divisor identification~\eqref{eq:view4-conjecture} is a statement about
\(\mathcal D_X\) as an automorphic section, transported to the period
side.

\subsection{The K3 mirror-period family}
\label{subsec:k3-mirror-period}

The lattice-polarised K3 mirror is fixed by Dolgachev~\cite{DolgachevMirrorLP}
and tracked, throughout, through the Mukai lattice. Let
\[
\Lambda_{K3}
\;=\;
3U \oplus 2 E_8(-1),
\qquad
\widetilde \Lambda_{K3}
\;=\;
U \oplus \Lambda_{K3}
\;\simeq\;
4U \oplus 2 E_8(-1),
\]
the K3 lattice of signature \((3,19)\) and the Mukai lattice of
signature \((4,20)\) (Mukai~\cite{Mukai1984,Mukai1987}). A
\emph{lattice polarisation} of a complex K3 surface \(S\) is a
primitive embedding \(\iota \colon M \hookrightarrow \Pic(S)\) of an
even hyperbolic lattice \(M\), of signature \((1, t)\), such that
\(M^\perp \subset \Lambda_{K3}\) admits a primitive embedding of the
hyperbolic plane \(U\); the pair \((S, \iota)\) is then
\emph{Nikulin-admissible}, in the convention of
Gritsenko--Nikulin~\cite{GNII}\,\S\,3 and the rank-3 sublattice
constructions of Borcherds~\cite{Borcherds95}\,\S\,15. Here \(t\)
denotes the rank of \(M^{\!\perp}\) inside \(\Lambda_{K3}\) minus one,
and \((1,t)\) is signature in the convention
\(\mathrm{sign}(M) = (\#\text{positive}, \#\text{negative})\).

The associated period domain
\[
\Omega_M
\;=\;
\bigl\{
[\omega] \in \P\!\bigl(M^\perp \otimes \C\bigr)
\;:\;
\langle \omega, \omega \rangle = 0,
\;
\langle \omega, \bar\omega\rangle > 0
\bigr\}^+
\]
is the type-IV symmetric domain of signature \((2, 19 - t)\), with
arithmetic group \(\Gamma_M = \mathrm O^+(M^\perp)\) acting properly
discontinuously. The \emph{Dolgachev mirror lattice} is the
sub-lattice
\[
\check M
\;=\;
M^\perp \cap (U)^\perp
\;\subset\;
\Lambda_{K3},
\qquad
M^\perp
\;=\;
U \oplus \check M,
\]
so that \(\check M\) carries signature \((1, 19 - t)\) and is
hyperbolic. The mirror K3 surface \(S^\vee\) is the lattice-polarised
K3 with \(\Pic(S^\vee) \simeq \check M\); the Dolgachev map
\((S, \iota) \mapsto (S^\vee, \check\iota)\) descends to an involution
on the moduli stack \(\Omega_M / \Gamma_M\) and on its mirror
\(\Omega_{\check M} / \Gamma_{\check M}\); this is the
Dolgachev--Nikulin involution, recorded as
\(\iota_{\mathrm{DN}}\) in the cross-volume \(d=2\) Vol~III chapter on
derived categories~\cite[Prop.~6.4]{CYQGVolIII}.

The Aspinwall--Morrison form of the same construction~\cite{AspinwallMorrisonStringy}
realizes \(\Omega_M\) as the moduli space of lattice-polarised K3 sigma
models with B-field, and identifies the mirror involution as the
exchange of large-volume and large-complex-structure limits along the
two distinguished cusps of \(\Omega_M / \Gamma_M\). Aspinwall--Morrison
and Dolgachev produce the same lattice; the difference is in
presentation, not in object. The Mukai-lattice form
\[
\widetilde M = U \oplus M,
\qquad
\widetilde M^\perp = U \oplus M^\perp = 2 U \oplus \check M,
\qquad
\widetilde M^\perp \subset \widetilde \Lambda_{K3},
\]
is the convention adopted in the cross-volume Vol~III statement
\cite[Prop.~6.4 + Thm.~6.7]{CYQGVolIII}. The Dolgachev--Nikulin
involution acts as \(-\mathrm{id}\) on \(\widetilde M\) and
\(+\mathrm{id}\) on \(\widetilde M^\perp\), preserving the full
signature \((4, 20)\).

\paragraph{The rank-three case.} The polarisation relevant to View~\textcircled{4}
is
\[
M
\;=\;
U \oplus \langle -2 \rangle,
\qquad
\mathrm{rank}(M) = 3,
\qquad
\mathrm{sign}(M) = (1, 2),
\]
with Dolgachev mirror lattice
\[
\check M
\;=\;
\bigl(M^\perp \cap U^\perp\bigr)_{\Lambda_{K3}}
\;\simeq\;
U \oplus E_7(-1) \oplus E_8(-1),
\]
of rank \(17\) and signature \((1, 16)\) inside \(\Lambda_{K3}\); the
convention is
\(\mathrm{sign} = (\#\text{positive}, \#\text{negative})\) on the
bilinear form of the lattice. The decomposition follows from the
embedding \(\langle -2 \rangle \hookrightarrow E_8(-1)\) on a single
root, after which the orthogonal complement of the root inside
\(E_8(-1)\) is \(E_7(-1)\). Inside the Mukai lattice the augmented
sub-lattice is
\[
\widetilde M
\;=\;
U \oplus M
\;=\;
2 U \oplus \langle -2 \rangle,
\qquad
\mathrm{rank}(\widetilde M) = 5,
\qquad
\mathrm{sign}(\widetilde M) = (2, 3).
\]
Under the manuscript's convention (the exterior-square model of
\(\Sp_4 \simeq \mathrm{Spin}(3,2)\) at \S\,\ref{ssec:exceptional-iso})
the same lattice is written
\(\Lambda^{3,2} = U \oplus U \oplus \langle 2 \rangle\), with the
hyperbolic-plane summand
\(\HypPlan = \begin{pmatrix} 0 & -1 \\ -1 & 0 \end{pmatrix}\) carrying
signature \((1, 1)\) and the rank-1 summand carrying form value \(+2\)
on a generator. The two writings are the same lattice expressed in
opposite sign conventions on the bilinear form: the manuscript's
\((p, q) = (3, 2)\) is signature ``three positive, two negative''
when read with the manuscript's quadratic form, while the
Dolgachev convention writes the same signature ``two positive, three
negative'' on the form with reversed sign. The
\((+2)\)-vectors of the manuscript are the \((-2)\)-vectors of the
Dolgachev convention; the Heegner divisors and the period domain
are independent of the sign choice.

The period domain attached to \(\widetilde M = \Lambda^{3,2}\) is the
type-IV symmetric domain
\[
\Omega_{\widetilde M}
\;=\;
\bigl\{
[Z] \in \P\!\bigl(\widetilde M \otimes \C\bigr)
\;:\;
(Z, Z) = 0,\;
(Z, \bar Z) > 0
\bigr\}^+,
\qquad
\dim_{\C} \Omega_{\widetilde M} = 3,
\]
with arithmetic group
\(\Gamma_{\widetilde M} = \mathrm O^+(\widetilde M)
\simeq \mathrm O^+(\Lambda^{3,2})\) acting properly discontinuously,
where the component is fixed by the manuscript's positive cone
\(\mathcal C(\Lambda^{2,1})_+\) (\S\,\ref{ssec:exceptional-iso}). The
exceptional isogeny
\[
\PSp_4(\R)
\;\simeq\;
\SO(3, 2)_+,
\qquad
\Sp_4(\Z) / \{\pm 1\}
\;\simeq\;
\SO_+(\Lambda^{3,2}),
\]
imported as View~\textcircled{5} (the Sp(4) \(\simeq\) Spin(3,2)
bridge), gives the identification
\begin{equation}
\label{eq:view4-period-bridge}
\Omega_{\widetilde M} \big/ \Gamma_{\widetilde M}
\;\;\simeq\;\;
\mathcal H_2 \big/ \Sp_4(\Z).
\end{equation}
The form
\(\Delta_5 \in M_5(\Sp_4(\Z), \nu_{\Delta_5})\) of
View~\textcircled{1}, viewed as a section on the right-hand side of
\eqref{eq:view4-period-bridge}, is the Borcherds lift of the weak Jacobi
form \(\phi_{0,1}\) under the data
\((\widetilde M, \phi_{0,1})\) on the left-hand side
(Borcherds~\cite[Thm.~13.3]{B} applied to signature
\((2, 3)\); Gritsenko--Nikulin~\cite[Thm.~1.1]{GNII} for the
identification with the additive Gritsenko lift; the rank-3 row of
the Vol~III lattice-polarised \(\mathfrak g_L\) catalogue at
\(L = U \oplus \langle -2 \rangle\)).

The K3-side period domain on the rank-3 polarisation is a different,
larger object:
\[
\Omega_M
\;=\;
\bigl\{
[\omega] \in \P\!\bigl(M^\perp \otimes \C\bigr)
\;:\;
\langle \omega, \omega \rangle = 0,\;
\langle \omega, \bar\omega \rangle > 0
\bigr\}^+,
\qquad
\dim_{\C} \Omega_M = 17,
\]
where \(M^\perp \subset \Lambda_{K3}\) has signature \((2, 17)\) and
parametrises the \emph{transcendental} Hodge filtration of a
lattice-polarised K3 surface. The Borcherds lift used in
View~\textcircled{4} is on \(\Omega_{\widetilde M}\), not on
\(\Omega_M\): the difference is the absorption of the elliptic
factor \(\Lambda_E = U\) into \(\widetilde M = U \oplus M\), which is
the K\"unneth identification on \(K3 \times E\) recorded below in
\S\,\ref{subsec:k3xe-period-family}. The two period spaces are not
interchangeable: \(\Omega_{\widetilde M}\) of dimension \(3\) is the
genus-two Siegel space and supports \(\Delta_5\) directly via the
exceptional isogeny, while \(\Omega_M\) of dimension \(17\) is the
K3-only period space, on which the rank-\(3\) lattice-polarised lift
of \(\phi_{0,1}\) lands only after the additional Mukai-\(U\)
augmentation.

\subsection{The K3 \texorpdfstring{$\times$}{x} E period family}
\label{subsec:k3xe-period-family}

The threefold \(K3 \times E\) acquires its Hodge structure through the
K\"unneth decomposition. The Mukai lattice
\(\Lambda_S = H^*(S, \Z)\) of signature \((4, 20)\) carries the Mukai
pairing
\(\langle (r, c, s), (r', c', s') \rangle_{\mathrm{Muk}} = c \cdot c' - r s' - r' s\)
(Definition~\ref{def:mukai-lattice}); the elliptic factor
contributes \(\Lambda_E = H^*(E, \Z) = U\) with the standard hyperbolic
form. The total integral cohomology is
\[
H^*(K3 \times E, \Z)
\;=\;
\Lambda_S \otimes \Lambda_E
\;=\;
\Lambda_S \otimes U,
\]
a lattice of rank \(48\); the relevant Hodge filtration is controlled,
on each weight, by the K3 polarisation \(M\) and the \(\tau\)-modulus
of \(E\). The component of the period stack parametrising
\((K3 \times E)\)-pairs \((S, E_\tau)\) with \(S\) lattice-polarised
by \(M = U \oplus \langle -2 \rangle\) is, on the rank-3
Mukai-invariant stratum,
\begin{equation}
\label{eq:view4-k3e-moduli}
\mathcal P_{K3 \times E}
\;\;:=\;\;
\Omega_{\widetilde M} \big/ \Gamma_{\widetilde M}
\;\;\overset{\eqref{eq:view4-period-bridge}}{\simeq}\;\;
\mathcal H_2 \big/ \Sp_4(\Z),
\end{equation}
where the augmented lattice \(\widetilde M = U \oplus M\) absorbs the
elliptic Mukai-\(U\) summand into the K3-side Mukai-\(U\) summand.
The K\"unneth identification
\(\Lambda_E = U \subset \widetilde M\) is the Hodge-theoretic content
of the absorption: the elliptic period \(\tau \in \mathbb H_1\) is
absorbed into the type-IV variable \(z_1 \in \Omega_{\widetilde M}\)
under the manuscript's coordinatisation in
\S\,\ref{ssec:exceptional-iso}. Equation~\eqref{eq:view4-k3e-moduli}
is the period-side input on which View~\textcircled{4} is stated. It
is a theorem of Gritsenko--Nikulin~\cite[Thm.~1.1, Thm.~1.2]{GNII} (the
existence and identification of the lattice-polarised lift) and
Borcherds~\cite[\S\,15]{Borcherds95} (the period-domain
Borcherds-product convergence on signature \((2, 3)\)); it is not a
new statement.

The K3-only period domain \(\Omega_M\) of dimension \(17\) does not
enter \eqref{eq:view4-k3e-moduli}: its role is to parametrise the
transcendental Hodge filtration of \(S\) alone, before tensoring with
\(\Lambda_E = U\). The \((K3 \times E)\)-component is on
\(\Omega_{\widetilde M}\), of dimension \(3\). The relation
\(\widetilde M = U \oplus M\) is the bridge between the two
period spaces.

\subsection{The discriminant locus}
\label{subsec:view4-discriminant}

The period family \(\mathcal P_{K3 \times E}\) carries a natural
divisor: the locus along which the rank-3 lattice-polarised K3
surface acquires a nodal degeneration in the polarisation lattice
\(M\). On the type-IV symmetric domain \(\Omega_{\widetilde M}\),
the Heegner divisors are
\[
\mathfrak H_{(\delta)}
\;=\;
\bigl\{
[Z] \in \Omega_{\widetilde M}
\;:\;
(Z, \delta) = 0
\bigr\},
\qquad
\delta \in \widetilde M,
\;\;
(\delta, \delta) = 2,
\]
indexed by primitive square-\(2\) vectors of the manuscript's
form on \(\widetilde M = \Lambda^{3,2}\)
(equivalently, square-\((-2)\) vectors of the Dolgachev form on the
K3 side after the sign flip recorded above). On the corresponding
geometric component the K3 fibre acquires a nodal rational curve
in the class \(\delta\): the Hodge filtration on
\(H^2(S, \Z) \otimes H^*(E, \Z)\) degenerates along this divisor as
the elliptic factor passes through a Mukai-isomorphic point. The
\emph{period-family discriminant} is
\begin{equation}
\label{eq:view4-discriminant-divisor}
\mathfrak D_{\mathrm{per}}
\;\;=\;\;
\bigcup_{\substack{\delta \in \widetilde M \\ (\delta, \delta) = 2}}
\mathfrak H_{(\delta)} \big/ \Gamma_{\widetilde M}
\;\;\subset\;\;
\Omega_{\widetilde M} / \Gamma_{\widetilde M}.
\end{equation}
The \(\Gamma_{\widetilde M}\)-orbit structure on primitive square-\(2\)
vectors of \(\widetilde M\) breaks into type-I and type-II classes
(\(\delta \cdot \widetilde M = \Z\) versus \(\delta \cdot \widetilde M = 2\Z\),
the dichotomy already imported as the type-II versus type-I
distinction at the \(W^{(2)}(\Lambda_{II}^{2,1})\)-orbit level in
the manuscript's preceding chapters); the union in
\eqref{eq:view4-discriminant-divisor} runs over the type-II orbit,
which is the orbit relevant to the \(\Sp_4(\Z)\)-image of the
exceptional isogeny. The image in the quotient is one irreducible
Heegner-type divisor
(Bruinier--Funke~\cite[\S\,2]{BruinierFunkeHeegner} for the general
lattice-Heegner formulation in signature \((2, 3)\); the index-1 case
is implicit in Borcherds~\cite[Thm.~10.1]{B}). The same divisor,
transported across the bridge~\eqref{eq:view4-period-bridge}, is the
\emph{Humbert surface}
\[
\mathcal H_2^{(\mathrm{Hum})}
\;\;=\;\;
\bigl\{
[Z] \in \mathcal H_2 \big/ \Sp_4(\Z)
\;:\;
Z = \begin{pmatrix} \tau_1 & 0 \\ 0 & \tau_2 \end{pmatrix} \;\text{up to } \Sp_4(\Z)
\bigr\},
\]
the diagonal locus on which the principally polarised abelian surface
\(\C^2 / (\Z^2 + Z \Z^2)\) decomposes as a product of two elliptic
curves; the corresponding K3-side degeneration is exactly the nodal
rational curve. The match
\(\mathfrak D_{\mathrm{per}} \leftrightarrow \mathcal H_2^{(\mathrm{Hum})}\)
is fixed by the bridge~\eqref{eq:view4-period-bridge}.

The form \(\Delta_5\) of View~\textcircled{1} vanishes precisely along
this divisor: \(\Delta_5 \in M_5(\Sp_4(\Z), \nu_{\Delta_5})\) has a
simple zero on \(\mathcal H_2^{(\mathrm{Hum})}\)
\cite[Thm.~3.1]{GNPartI}\cite[\S\,3]{GNII}, with multiplier
\(\nu_{\Delta_5}\) accounting for the half-integral shift. Concretely,
the Borcherds product expansion of View~\textcircled{1} gives
\[
\Delta_5(Z)
\;=\;
64\, q^{1/2} r^{1/2} s^{1/2}
\prod_{(n, l, m) \in \Gamma_{\mathrm{eff}}}
(1 - q^n r^l s^m)^{f(nm, l)},
\]
and the zero locus is exactly \(\mathcal H_2^{(\mathrm{Hum})}\),
counted with multiplicity \(1\). Hence
\begin{equation}
\label{eq:view4-divisor-of-Delta5}
[\,\Delta_5^{\,-1}\,]
\;\;=\;\;
[\,\mathcal H_2^{(\mathrm{Hum})}\,]
\;\;=\;\;
[\,\mathfrak D_{\mathrm{per}}\,]
\quad \text{(divisor classes on } \mathcal H_2 / \Sp_4(\Z)).
\end{equation}
This identity is a theorem in the cited references; it is recorded
here as the input to the conjecture.

\subsection{The conjecture}
\label{subsec:view4-conjecture}

The discriminant of a period family carries multiplicities, not
just a support. For the K3-mirror period family on the rank-3
Mukai-invariant component, the relevant multiplicity is fixed by
the Hodge structure on \(H^2(S, \Z) \oplus H^*(E, \Z)\): a nodal K3
acquires a vanishing cycle of dimension \(2\), and the local
universal Hodge filtration degenerates with multiplicity \(2\)
along \(\mathfrak D_{\mathrm{per}}\) when the discriminant is
read as the divisor of a section of the period-bundle determinant
(Saito's mixed-Hodge-module formalism for the Hodge filtration on
the local Milnor fibre, \cite{SaitoMHM}; Bryan--Pandharipande
\cite[\S\,3]{BRYAN} for the genus-two BPS calculation that supplies
the same multiplicity at the level of generating functions).

\begin{conjecture}[The mirror discriminant identity]
\label{conj:mirror-discriminant}
\ClaimStatusConjectured
On the \((K3 \times E)\)-component of the K3-mirror period family,
parametrised by \eqref{eq:view4-k3e-moduli}, the meromorphic section
\[
\Delta_5^{\,-2}
\;\in\;
\Gamma\!\left(
\mathcal H_2 / \Sp_4(\Z),
\;\;
\mathcal L^{-10}_{\,\mathrm{aut}}
\right)
\]
of the inverse \(10\)th tensor power of the automorphic line bundle
\(\mathcal L_{\mathrm{aut}}\) coincides, as a meromorphic section of
the period-bundle determinant on \(\mathcal P_{K3 \times E}\), with the
discriminant of the K3-mirror period family. Equivalently, the polar
divisor of \(\Delta_5^{-2}\) is twice the period-family discriminant
\(\mathfrak D_{\mathrm{per}}\), and the comparison map
\[
\mathcal L^{-10}_{\,\mathrm{aut}}
\;\;\xrightarrow{\;\;\sim\;\;}\;\;
\bigl(\det \mathcal H^2_{\mathrm{tr}}\bigr)^{\,*}
\]
on the open complement \(\mathcal P_{K3 \times E}^{\circ}
= \mathcal P_{K3 \times E} \setminus \mathfrak D_{\mathrm{per}}\)
extends to a global identification of the inverse-period-determinant
section with \(\Delta_5^{-2}\).
\end{conjecture}

The conjecture is, at the level of divisor classes,
\begin{equation}
\label{eq:view4-divisor-equation}
[\,\Delta_5^{\,-2}\,]
\;\;=\;\;
2\,[\,\mathfrak D_{\mathrm{per}}\,]
\;\;=\;\;
2\,[\,\mathcal H_2^{(\mathrm{Hum})}\,];
\end{equation}
the identity~\eqref{eq:view4-divisor-of-Delta5} fixes the right-hand
side, and the conjectural content is the matching of multiplicities
and the trivialisation of the comparison line bundle.

\paragraph{Evidence.}
The genus-two Bryan--Pandharipande generating function for
disconnected genus-two BPS states on \(K3 \times E\) gives
\(Z^{K3 \times E}_{\mathrm{BPS}} = \Delta_5^{-2}\) in the cusp
chamber~\cite[Conj.~1]{BRYAN}; this identity has been proved by
Oberdieck--Pixton~\cite[Thm.~1]{OB} and is the input to
View~\textcircled{1} on the curve-counting side. Two facts converge:
the coefficient of \(\Delta_5^{-2}\) at a degenerate stable map is
controlled, by the Maulik--Toda Gopakumar--Vafa formalism
\cite{MaulikTodaGV}, by the local Milnor monodromy on the period
filtration; and the local Hodge-filtration multiplicity at a nodal K3
fibre is \(2\) (Saito~\cite{SaitoMHM}). Both of these are theorems,
not conjectures. What is conjectural is the global trivialisation: the
comparison line bundle
\(\mathcal L^{-10}_{\,\mathrm{aut}} \otimes (\det \mathcal H^2_{\mathrm{tr}})\)
admits no obstruction, and the identification of the two sides extends
across the discriminant divisor.

A separate piece of evidence is the precedent set by
Gritsenko--Nikulin~\cite[Thm.~4.1]{GNII}: at rank \(4\), with
polarisation \(L = U \oplus U\), the analogous Borcherds product is
the Igusa cusp form \(\Phi_{12}\) on the type-IV symmetric domain of
signature \((2, 4)\); Gritsenko--Nikulin proved that
\(\Phi_{12}\) is the quasi-pull-back of the discriminant section of
the universal lattice-polarised Hodge bundle on \(\Omega_L / \Gamma_L\).
Conjecture~\ref{conj:mirror-discriminant} is the rank-3 analogue of
the same identification, evaluated at the lattice
\(M = U \oplus \langle -2 \rangle\).

\paragraph{Status.}
\ClaimStatusConjectured\ The identification claim of
Conjecture~\ref{conj:mirror-discriminant} is conjectured. The
existence of the comparison line bundle is folklore; the divisor
identity~\eqref{eq:view4-divisor-of-Delta5} is a theorem; the
multiplicity-2 statement on the K3 side is a theorem; the global
extension across the discriminant divisor is the conjectural content.

\paragraph{What this conjecture supplies.}
If proved, View~\textcircled{4} embeds the present programme inside
mirror symmetry on \(K3 \times E\) at the level of period-side
discriminants. The identification supplies a new derivation of
\(\Delta_5\) that does not pass through the Borcherds product
(View~\textcircled{1}), the BKM denominator (View~\textcircled{2}),
the Pfaffian of the Dirac--Igusa pro-object (View~\textcircled{3}),
or the singular theta lift (View~\textcircled{5}). It is a fifth
chain. The fact that the same form arises on five chains is the
content of the pentadic thesis of the manuscript; the fifth chain,
conjectural now, completes the picture.

The opposite implication is also of interest. A proof of
Conjecture~\ref{conj:mirror-discriminant} would identify
\(\Delta_5^{-2}\) with the universal determinant section of the
\((K3 \times E)\)-mirror period family; combined with the Bryan--Oberdieck--Pixton
theorem~\cite[Thm.~1]{OB} that
\(Z^{K3 \times E}_{\mathrm{BPS}} = \Delta_5^{-2}\), this would give a
new proof of the genus-two BPS partition-function identity through
the period side, complementing the curve-counting derivation.

\subsection{What the conjecture does not assert}
\label{subsec:view4-not-asserted}

The Beilinson cut (\(\mathrm{CLAUDE.md}\)\,\S\,III) is in force.
The conjectural identification is on the period side: it concerns
the section \(\Delta_5^{-2}\) of an automorphic line bundle and the
discriminant divisor of the K3-mirror period family. It is not a
claim about the protected operator-level package
\(\mathfrak D_X^{\mathrm{DI}}\) of View~\textcircled{3}; that package
is constructed and proved, under the four named obstructions
\((\mathrm{D0})\), \((\mathrm{O1})\), \((\mathrm{O1}^+)\),
\((\mathrm{O2})\), in the
View~\textcircled{2}\(\leftrightarrow\)\textcircled{3} chapters
preceding this one. View~\textcircled{4} does not enter the operator
chain.

The level-\(n\) scalar partition function
\(Z^{K3 \times E}_{\mathrm{BPS}} = \Delta_5^{-2}\) is, on the present
programme, the orientation-forgetful trace of the Pfaffian package;
its promotion to a \(3d\) gravitational path integral requires the
Hall--Borcherds residual (Vol~II, \cite{ChiralBarCobarVolII}). The
mirror conjecture above says nothing about the gravitational lift; it
addresses only the geometric origin of the section
\(\Delta_5^{-2}\) on the K3-mirror period family.

The Borcherds--Kac--Moody denominator
\(\operatorname{den}(\mathfrak g_{\Delta_5}) = 64^{-1} \Delta_5(2 Z)\)
is on the algebraic side; it is a theorem of
Gritsenko--Nikulin~\cite[\S\,3, Thm.~3.1]{GNII}. The mirror
conjecture is on the period side and does not enter the algebraic
chain.

\subsection{Lattice-convention check}
\label{subsec:view4-lattice-check}

The lattice convention adopted above is the Dolgachev convention
\(\Lambda_{K3} = 3 U \oplus 2 E_8(-1)\), \(M = U \oplus \langle -2 \rangle\),
mirror lattice
\(\check M \simeq U \oplus E_7(-1) \oplus E_8(-1)\) (rank \(17\),
signature \((1,16)\)). Aspinwall--Morrison's original mirror-pair
construction~\cite{AspinwallMorrisonStringy} adopts the same lattice up
to the choice of which hyperbolic plane in \(\Lambda_{K3}\) is split
off; the two conventions agree on the K3 mirror lattice. The
Mukai-lattice form
\(\widetilde M = U \oplus M = 2U \oplus \langle -2\rangle\)
of rank 5 and signature \((2, 3)\) is the convention adopted in
cross-volume Vol~III~\cite[Prop.~6.4]{CYQGVolIII}; it is the convention
relevant to the period-domain bridge~\eqref{eq:view4-period-bridge}.
The lattice \(\widetilde M\) is identified with the manuscript's
\(\Lambda^{3,2}\) of \S\,\ref{ssec:exceptional-iso} by the sign-flip
on the rank-\(1\) summand recorded in \S\,\ref{subsec:k3-mirror-period}.
Disagreement on the lattice convention surfaces, in cross-volume work,
only as a sign convention on the Mukai pairing; it does not affect the
discriminant divisor.

The K3 vs.\ \((K3 \times E)\) period-space matching
\eqref{eq:view4-k3e-moduli} works because \emph{the Mukai \(U\)-summand
of} \(\widetilde M\) \emph{is the elliptic factor on the
\((K3 \times E)\)-side after K\"unneth absorption}, not because the
K3-mirror period family and the \((K3 \times E)\)-mirror period family
are abstractly equal. Disagreement on this point would surface as
a discrepancy between the \(\Sp_4\)-side and the
\(\mathrm O^+(2,3)\)-side; the
isomorphism~\eqref{eq:view4-period-bridge} is
exactly the Sp(4) \(\simeq\) Spin(3,2) bridge of
View~\textcircled{5}, and the absorption of \(\Lambda_E = U\) into
the Mukai \(U\)-summand of \(\widetilde M\) is the Hodge-theoretic
content of the K\"unneth product.

The phrase ``discriminant of WHAT'' is sharpened by the
multiplicity. There are two natural divisors on the period side:
the support divisor \(\mathfrak D_{\mathrm{per}}\) of the
period-family degeneration, and the principal divisor of the
section of \((\det \mathcal H^2_{\mathrm{tr}})^*\) realizing the
period-bundle determinant. The conjecture concerns the second:
\(\Delta_5^{-2}\) is conjectured to be that section, with polar
divisor twice the support divisor of
\(\mathfrak D_{\mathrm{per}}\). The factor of 2 is forced by the
local multiplicity of the Hodge filtration at a nodal K3 and is
matched, on the automorphic side, by the square of \(\Delta_5\); a
mismatch at the level of multiplicity would falsify the conjecture
by a factor that the Borcherds product does not allow.

The relation to the Borcherds--Gritsenko--Nikulin precedent at
rank \(4\) is the cleanest comparison. At
\(L = U \oplus U\) the analogous lift is \(\Phi_{12}\) on the type-IV
symmetric domain of signature \((2, 4)\), and Gritsenko--Nikulin
\cite[Thm.~4.1]{GNII} prove that \(\Phi_{12}\) is the quasi-pull-back
of the discriminant section of the universal lattice-polarised Hodge
bundle. The rank-3 analogue
\(L = U \oplus \langle -2 \rangle\) is
Conjecture~\ref{conj:mirror-discriminant}; the only piece missing
is the global comparison-line trivialisation. The
\(\Phi_{12}\) precedent is evidence; it is not a proof, since the
quasi-pull-back map at rank \(3\) is governed by a different Heegner
divisor structure.

\subsection{Open obligations}
\label{subsec:view4-open}

\begin{enumerate}
\item[\textnormal{(M1)}]
\ClaimStatusOpen\ \emph{Trivialisation of the comparison line.} The
comparison line bundle
\(\mathcal L^{-10}_{\,\mathrm{aut}} \otimes (\det \mathcal H^2_{\mathrm{tr}})\)
on \(\mathcal P_{K3 \times E}^{\circ}\) carries no first Chern class
that is not absorbed by the automorphic-character data of
\(\nu_{\Delta_5}^{-2}\). Sub-conjecture: this comparison line is
trivial. Implication: under (M1), the
identity~\eqref{eq:view4-divisor-equation} promotes from a divisor
identity to an equality of sections.

\item[\textnormal{(M2)}]
\ClaimStatusOpen\ \emph{Multiplicity at the cusp.}
Conjecture~\ref{conj:mirror-discriminant} concerns the polar divisor
of \(\Delta_5^{-2}\) on the open part \(\mathcal P_{K3 \times E}^{\circ}\);
the boundary behaviour at the rank-2 cusp of \(\mathcal H_2 / \Sp_4(\Z)\)
is governed by the singular weight \(c_1(0) / 2 = 5\)
(\cite[\S\,15]{Borcherds95}). Sub-conjecture: the boundary
multiplicity matches the singular weight on the period side.

\item[\textnormal{(M3)}]
\ClaimStatusOpen\ \emph{The mirror involution \(\iota_{\mathrm{DN}}\)
on the section.} The Dolgachev--Nikulin involution on
\(\widetilde\Lambda_{K3}\) acts as \(-\mathrm{id}\) on
\(\widetilde M = 2U \oplus \langle -2\rangle\) (signature \((2,3)\))
and as \(+\mathrm{id}\) on \(\widetilde M^\perp\) (signature
\((2, 17)\)); both halves carry the same positive-part rank \(2\),
which is the structural source of the symmetry. Sub-conjecture:
\(\iota_{\mathrm{DN}}^*(\Delta_5) = \Delta_5\) up to the multiplier
\(\nu_{\Delta_5}\), and the discriminant identity is
\(\iota_{\mathrm{DN}}\)-invariant.

\item[\textnormal{(M4)}]
\ClaimStatusOpen\ \emph{Cross-volume consistency at rank \(\geq 5\).}
The Vol~III rank-\(\geq 5\) lattice-polarised \(\mathfrak g_L\)
family~\cite{CYQGVolIIIWave3} is the conjectural extension of
Conjecture~\ref{conj:mirror-discriminant} to higher Picard rank.
At rank \(\geq 5\) the discriminant identity is conditional on the
Gritsenko--Cl\'ery 2018 admissibility conjecture
(Conj.~5.1 of \cite{GC}); the rank-\(3\) statement is the corresponding
conditional statement for the K3-Mukai-invariant lattice and is the
only one of the rank ladder relevant to this manuscript.
\end{enumerate}

The four open obligations \((\mathrm M 1)\)--\((\mathrm M 4)\) are
distinct from the four obstruction classes \((\mathrm{D0})\),
\((\mathrm{O1})\), \((\mathrm{O1}^+)\), \((\mathrm{O2})\) of
View~\textcircled{3}; the latter govern the operator-level chain
and are the conditioning for \textcircled{2}\(\leftrightarrow\)\textcircled{3},
while the former govern the period-side chain and are the
conditioning for \textcircled{4}\(\leftrightarrow\)\textcircled{1}.
The two sets do not interact: a discharge of \((\mathrm M 1)\) does
not advance the operator package, and a discharge of \((\mathrm{D0})\)
does not advance the period-side conjecture.

\subsection{Cross-repository consistency}
\label{subsec:view4-cross-repo}

The lattice convention
\(M = U \oplus \langle -2 \rangle\),
\(\check M \simeq U \oplus E_7(-1) \oplus E_8(-1)\),
\(\widetilde M = U \oplus M\) of
\S\,\ref{subsec:k3-mirror-period} is the convention of
Vol~III~\cite[\S\,6.4 + Prop.~6.4 + Thm.~6.7]{CYQGVolIII}; on the
\((K3 \times E)\)-component the Vol~III \(\kappa\)-tuple
\(\bigl(\kappa_{\mathrm{cat}}, \kappa_{\mathrm{ch}}^{\mathrm{Hodge}},
\kappa_{\mathrm{ch}}^{\mathrm{Heis}}, \kappa_{\mathrm{BKM}}, \kappa_{\mathrm{fiber}}\bigr)
= (0, 0, 3, 5, 24)\) is recorded with each entry sourced from a
distinct construction. The mirror discriminant of
Conjecture~\ref{conj:mirror-discriminant} is on the
\(\kappa_{\mathrm{BKM}} = 5\) row of the \(\kappa\)-tuple; the
period-side input is the discriminant divisor on the
lattice-polarised period stratum of the Vol~III chart
classification (Vol~III~\cite[\S\,V]{CYQGVolIII}: the
``lattice-polarised period domain'' equivariance stratum). The
\((K3 \times E)\)-fiber rank \(\kappa_{\mathrm{fiber}} = 24\) is the
Mukai-lattice rank of \(\widetilde \Lambda_{K3}\) and enters the
present chapter only as the rank of the Heisenberg algebra of the
Mukai lattice, not as a discriminant invariant.

The mixed-holomorphic-topological-strings companion volume
\cite{MixedHTSCompanion} records that the modular line bundle on
\(\overline{\mathcal A}_g\) at level \(g = 2\) is
\(\Omega_{\mathrm{central}}\), and that
\(\Phi_{10} = \chi_{10} = \Delta_5^{\,2}\) is the level-\(2\)
section. The conjecture above is consistent with that statement:
the polar divisor of \(\Delta_5^{-2} = \Phi_{10}^{-1}\) on
\(\overline{\mathcal A}_2\) is twice the divisor of \(\Delta_5\),
and the mirror discriminant identification is precisely the
geometric origin of that section.

The Vol~II Hall--Borcherds residual is silent on
View~\textcircled{4}: the period-side discriminant identification
is independent of the gravitational-lift bridge, and the
conjecture above does not require the residual to be discharged.
A discharge of the Hall--Borcherds residual on the
\((K3 \times E)\)-component would not by itself prove
Conjecture~\ref{conj:mirror-discriminant}; conversely, a proof
of Conjecture~\ref{conj:mirror-discriminant} would not
automatically discharge the Hall--Borcherds residual.

\medskip

The fifth view stands open. The four other views form a single
quadrilateral of theorems and conditional theorems; the fifth
view is the missing diagonal. Its discharge is the next
geometric problem in the programme.

% Bibliographic anchors used by this chapter that are not yet entered
% into proj.bib (queued for the integration owner; cross-volume
% citations are nonfatal because main.tex's \bibliography{proj} is
% the sole bibliography source):
%   AspinwallMorrisonStringy  (Aspinwall--Morrison, 1994/97)
%   DolgachevMirrorLP         (Dolgachev, J. Math. Sci. 81, 1996)
%   BruinierFunkeHeegner      (Bruinier--Funke, Crelle 594, 2006)
%   CYQGVolIII                (cross-repo: ~/calabi-yau-quantum-groups)
%   CYQGVolIIIWave3           (cross-repo: ~/calabi-yau-quantum-groups
%                              C13 lattice-polarised K3 ledger)
%   ChiralBarCobarVolII       (cross-repo: ~/chiral-bar-cobar-vol2)
%   MixedHTSCompanion         (cross-repo:
%                              ~/mixed-holomorphic-topological-strings)
%
% These keys are used inline above with the standard \cite{} macro;
% under \bibliography{proj} they will surface as undefined-citation
% warnings until the integration owner imports the entries (or
% replaces with substitute citations to GN, OB, BRYAN, MaulikTodaGV,
% SaitoMHM, BORCEA, VOISIN, Borcherds95, B already in proj.bib).
