% !TEX root = ../main.tex

\chapter{Open obstructions and the next frontier}
\label{ch:open-obstructions}

\section{Open obstructions and the next frontier}
\label{sec:open-obstructions-and-frontier}

The cross-level identity \(\textcircled{2}\!\leftrightarrow\!\textcircled{3}\) of
this manuscript --- the Pfaffian--Dirac theorem
\(\mathrm{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})=\Delta_5\),
\(\epsilon_o=\nu_{\Delta_5}\) on \(W^{(2)}(\La^{2,1}_{II})\), and the
primitive recognition \(P_X\cong\mathfrak g_{\Delta_5}\) --- is
conditional on four named obstructions, and the manuscript stops at the
boundary where each is named, not at the boundary where each is closed.
The view is honest: the automorphic identity
\(\textcircled{1}\!\leftrightarrow\!\textcircled{2}\) is theorem
\cite{Borcherds95,GN}; the singular-theta-lift identity
\(\textcircled{2}\!\leftrightarrow\!\textcircled{5}\) is theorem
\cite{Borcherds95}; the BKM denominator computation
\(\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z)\) is
theorem; what is conditional is the operator-level passage from the
finite-stage compact \(K3\times E\) source to the closed denominator
algebra.

Each of the four obstructions sits at a definite categorical-dimensional
level on the universal chain
\(\mathsf{P}\to\mathsf{C}\to\mathsf{S}\to\mathsf{Z}\to\mathsf{A}\); each
of three open frontiers --- the Hall--Borcherds residual promoting the
level-\(n\) protected scalar shadow to operator level (Vol II
Construction Problem 2); the chain fusion conjecture for compact
non-toric \(K3\times E\) (Vol III); and the gravity-line operator
algebra whose Pentagon-face scalar trace is \(\Delta_5^2\) (Vol II
Construction Problem 2 again, cross-listed) --- bridges the operator
content of this manuscript to the broader programme. The Mathieu /
umbral moonshine adjacency stands between obstructions and frontiers:
its connection to \(\mathfrak g_{\Delta_5}\) is conjectural, and the
precise content of the conjecture is what the chapter asserts. The
Beilinson cut places this chapter at the frontier: open obligations
named precisely \emph{are} the deliverable.

The three names of \(\Delta_5\) are kept distinct on first occurrence:
the automorphic section
\(D_X=\Delta_5\in H^0(\mathcal H_2,\mathcal L^5\otimes\nu_{\Delta_5})\)
of view \textcircled{1}; the BKM denominator
\(\operatorname{den}(\mathfrak g_{\Delta_5})=64^{-1}\Delta_5(2Z)\) of
view \textcircled{2}; and the compact protected Pfaffian
\(\mathrm{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})\) of view
\textcircled{3}, conditional on \textup{(D0)}, \textup{(O1)},
\textup{(O1)\(^+\)}, \textup{(O2)}.

\subsection{The four named obstructions}
\label{subsec:four-named-obstructions}

Each of the four obstructions sits at a definite categorical-dimensional
level and carries a definite licensing type. The compact target is the
Dirac--Igusa pro-object
\(\mathfrak D_X^{\mathrm{DI}}=\varprojlim_R(\mathcal A_{X,R}^{E_3},
F_{X,R}^{\mathrm{hyb}},\Gamma_{X,R},\Pi_X,\Phi_R,o_R,H_R,P_R^\Pi,
C_{X,R},\Theta_{\mathrm{Kos},R},\mathcal L_{\mathrm{Pf},R},
\mathrm{pf}_{X,R},\epsilon_{o,R},\mathrm{Rec}_R)\). The level
discipline is \emph{primitive object first, cross-level identity second,
scalar shadow last}. The four obstructions are exactly the local-to-global
passages whose Beilinson cut places the conditional theorem
\(\textcircled{2}\!\leftrightarrow\!\textcircled{3}\) at level
\(\mathsf{Z}\) rather than at level \(\mathsf{S}\).

\subsubsection{(D0): D0-degeneration limit of the cosection-reduced d-critical orientation theory}
\label{subsubsec:obstruction-D0}

\paragraph{Statement.} The cosection-reduced d-critical orientation
theory on the retained Hall stack
\(\mathcal H_R^{\mathrm{or}}\) of finite HN height \(R\) extends to the
D0 (zero-dimensional brane) degeneration locus, in the sense that the
orientation line of the reduced determinant complex
\[
\mathscr D^{\mathrm{red}}_{R,\mathcal C}
=\det\operatorname{RHom}_{\mathrm{red}}(\mathcal C,\mathcal C)
\]
admits a Brav--Bussi--Dupont--Joyce--Szendr\H{o}i \cite{BBDJS2015} square-root
gerbe section over the closure
\(\overline{\mathfrak M^{\mathrm{st}}_{R,\mathcal C}}\subset
\overline{\mathcal H_R^{\mathrm{or}}}\) including the D0-degeneration
stratum, compatible with the cosection contraction inherited from
\(K3\times E\). The retained Hall datum supplies an oriented critical
finite-stage Pandharipande--Thomas/Gholampour--Sheshmani
inverse system \(\widehat{\mathcal H}^{\mathrm{or}}_{\sigma,S}
=\varprojlim_R\mathsf F_R\mathcal H_{\sigma,S}^{\mathrm{or}}\) on the
finite HN quotients of
Definition~\ref{prop:sectorial-hall-truncation};
\textup{(D0)} asks that this system carry a coherent orientation through
the D0-degeneration limit.

\paragraph{Stage and licensing.} Level \(\mathsf{S}\), \(\gamma\)-ambient
(chain-level versus pro-object), \(\varepsilon\)-effectiveness
(orientation as square-root datum). The licensing is
\((\mathsf{S},\gamma,\varepsilon)\): the d-critical structure lives at
the chart specialization stage \(\mathsf{S}\); the ambient is the
finite-stage pro-object \(\widehat{\mathcal H}^{\mathrm{or}}_{\sigma,S}\),
not an ordinary chain complex; the effectiveness datum is the
orientation gerbe section, which is what \textup{(D0)} demands extend.

\paragraph{Verification.} A005 verifies the local
Pfaffian wall sign theorem is correctly conditional and identifies
graph-isogeny atoms as candidate, not theorem; A011 maintains the
firewall between the Maass character \(\nu_{\Delta_5}\) and the
geometric orientation \(\epsilon_o\) (these agree on
\(W^{(2)}(\La^{2,1}_{II})\) only after \textup{(D0)}--\textup{(O2)}
hold); A026 confirms BBDJS \cite{BBDJS2015} vanishing-cycle data require an
oriented d-critical locus, not boundedness alone, and that
Joyce--Upmeier \cite{JoyceUpmeier} square-root data on CY\(_3\) moduli do not
automatically extend to the reduced \(K3\times E\) quotient; A037
separates the connected \(BE\) Borel/edge class
\(\alpha^{E,\mathrm{free}}=a_1u_1+a_2u_2\in H^2(BE;\mathbb F_2)\)
from finite \(BE[N]\) Borel terms; A042 verifies the quotient-orientation
descent across object, extension, mixed, wrapped, two-step flag, overlap,
Thom--Sebastiani, and \(R'\to R\) transition strata is conditional, with
overlap/correspondence/flag/transition compatibilities named separately.

\paragraph{Reasoning.} The retained Hall boundedness \cite{LiuProductStability,PiyaratneTodaModuli3folds}
gives a finite-type retained slice; it does not give quasi-smoothness, a
d-critical chart, BBDJS coefficients, an orientation line, or
compact-support six-functor admissibility through the D0 limit.
Pantev--To{\"e}n--Vaqui{\'e}--Vezzosi \cite{PTVV2013} shifted symplectic
structures cover ambient derived
moduli under Calabi--Yau hypotheses; the retained atlas is not produced
by PTVV alone. Joyce--Upmeier \cite{JoyceUpmeier} square-root orientation
on Calabi--Yau\(_3\) moduli requires exact-sequence/direct-sum
compatibility; the reduced \(K3\times E\)-quotient inherits this only
after the cosection-induced shift is shown compatible with descent.

\paragraph{Next concrete construction.} \emph{Open.} Compute
\(\alpha^{\mathrm{red}}_{R,\mathcal C}=w_2(\mathscr D^{\mathrm{red}}_{R,\mathcal C})
\in H^2(S;\mathbb F_2)\), \(\alpha^{E,\mathrm{free}}_{R,\mathcal C}\),
\(\widetilde\beta^{H}_{R,\mathcal C}\in H^2_H(S;\mathbb F_2)\), and
\(\lambda^{H}_{R,\mathcal C}\in H^1(BH;\mathbb F_2)\) on every retained
object, extension, mixed, wrapped, and flag stratum \(\mathcal C\), with
killing of the Borel mixed terms and edge-spectral-sequence differentials
required at every node of the descent diagram. The simplest decisive
locus is the rank-one D6--D2--D0 stratum
\(\mathcal C=(1,\beta,n)\) with \(\beta\) the K3-fibre primitive class:
on this stratum the BBDJS line carries the cosection contraction
explicitly, and the four obstruction classes
\((\alpha^{\mathrm{red}},\alpha^{E,\mathrm{free}},\widetilde\beta^{H},
\lambda^{H})\) reduce to a Pin\(^c\) computation. A discharge of
\textup{(D0)} on this stratum, together with the
extension/correspondence/flag transitions of probe A042, yields the
strong reduced orientation across the retained inverse system.

\subsubsection{(O1): strong reduced orientation on the K3{\(\times\)}E-quotient self-Ext frame bundle}
\label{subsubsec:obstruction-O1}

\paragraph{Statement.} The BBDJS \cite{BBDJS2015} orientation gerbe on the moduli
of stable sheaves on \(K3\times E\) descends to the
\(K3\times E\)-quotient self-Ext frame bundle, with reduced orientation
gauge: on the stable stratum
\(\mathfrak M^{\mathrm{st}}_{R,\mathcal C}\subset\mathcal H_R^{\mathrm{or}}\)
the obstruction tuple
\[
\mathfrak o^{\mathrm{or}}_{R,\mathcal C}
=\bigl(\alpha^{\mathrm{red}}_{R,\mathcal C},\,
\alpha^{E,\mathrm{free}}_{R,\mathcal C},\,
\{(\widetilde\beta^{H}_{R,\mathcal C},\lambda^{H}_{R,\mathcal C})\}_{H},\,
\mu^{\mathrm{or}}_{R,e},\,\dots\bigr)
\]
vanishes simultaneously, with all overlap, correspondence, flag, and
\(R'\to R\) transition data trivialized coherently. \textup{(O1)}
demands the strong reduced descent: the connected-\(BE\) class
\(\alpha^{E,\mathrm{free}}\), the finite-\(BE[N]\) gerbe classes
\(\widetilde\beta^H\), and the residual finite linearization characters
\(\lambda^H\) all vanish, separately, on every retained stratum, and the
spectral-sequence differentials and Borel mixed terms are killed.

\paragraph{Stage and licensing.} Level \(\mathsf{S}\to\mathsf{Z}\),
\(\beta\)-comparison (gerbe descent functor),
\(\varepsilon\)-effectiveness (orientation gauge non-degeneracy). The
licensing is \((\mathsf{S}\to\mathsf{Z},\beta,\varepsilon)\): the
descent of the BBDJS line is the comparison arrow from the chart
specialization stage \(\mathsf{S}\) to the centre stage \(\mathsf{Z}\),
and effectiveness asks the orientation be a non-degenerate square-root
datum.

\paragraph{Verification.} Probe A074 confirms cross-repo consistency with
Vol III on the primitive recognition firewall: target arithmetic on
\(W_{\le3}\) is target Borcherds--Gritsenko--Nikulin--Kac data only,
and recognition requires an actual compact source datum supplying
\(M,D,B,G,K,Q,A_\beta\), relation rows, Hopf radical/coideal kernel
equality, PBW associated-graded comparison, and strict
transition/Mittag--Leffler rows. Probes A076, A082, A089 supply the
proof-ledger statement defining what a discharged \textup{(O1)} carries
to the recognition theorem. The connected \(E\) and finite \(E[N]\)
cohomologies are \emph{distinct} obstruction spaces:
\(H^*(BE;\mathbb F_2)=\mathbb F_2[u_1,u_2]\) with
\(|u_i|=2\), so \(H^1(BE;\mathbb F_2)=0\); for
\(E[2]\cong(\mathbb Z/2)^2\),
\(H^*(BE[2];\mathbb F_2)=\mathbb F_2[x_1,x_2]\) with
\(|x_i|=1\), and the residual linearization
\(\lambda=\lambda_1x_1+\lambda_2x_2\) is independent data after the
degree-two gerbe class is killed (A037, A042).

\paragraph{Reasoning.} Translation invariance under \(E\)-action does
not produce orientation descent: a fixed underlying line may carry a
nontrivial finite character, and ordinary translation invariance is
\emph{not} a substitute for vanishing of
\(\lambda^H\) on full two-primary generators of
\(H^*(B(\mathbb Z/2^a)^2;\mathbb F_2)
=\Lambda(x_1,x_2)\otimes\mathbb F_2[y_1,y_2]\) at \(N=2^a\). The
quotient-orientation criterion is finite \v{C}ech--Borel descent on the
retained groupoid, not a vanishing theorem.

\paragraph{Next concrete construction.} \emph{Open.} Construct, on the
rank-one D6--D2--D0 stratum and its extension, mixed, wrapped, and
two-step flag completions, the actual BBDJS gerbe sections on the
self-Ext frame bundle, and verify the full vanishing of
\(\mathfrak o^{\mathrm{or}}_{R,\mathcal C}\) entry-by-entry. The
decisive locus is the rank-one D6--D2--D0 input
\(\mathcal C=(1,\beta,n)\) with the four cohomology classes computed
explicitly via the Pin\(^c\) input plus quotient checks of clause
\textup{(P1)}; for a discharged \textup{(O1)}, the overlap and
correspondence transitions of probe A042 must commute with descent on
the cofinal HN system.

\subsubsection{(O1)\(^+\): Weyl-equivariant transport of the orientation along W\((^2)\)(\(\La_{II}^{2,1}\)) reflections}
\label{subsubsec:obstruction-O1plus}

\paragraph{Statement.} The orientation character on the type-II Weyl
group \(W^{(2)}(\La^{2,1}_{II})\) is Weyl-equivariant: the orientation
line of \textup{(O1)} is equipped with coherent lifts
\(\tau_i:o_{\mathcal C}\to s_{\delta_i}^{*}o_{\mathcal C}\) of the
three type-II simple reflections, each acting with sign \(-1\), and
the projective determinant-line cocycle
\(c_o\in Z^2(W^{(2)}(\La^{2,1}_{II});\mathbb F_2)\) of the lift is a
coboundary, with quotient torsor defects
\(\omega_{i,\mathcal C}=0\) on every retained groupoid component. At
finite height \(R\), the partial action groupoid \(\mathcal G_R\)
carries
\(c_{o,R}\in Z^2(\mathcal G_R;\underline{\mathbb F}_2)\), and
\textup{(O1)\(^+\)} asks that
\([c_{o,R}]=0\), \(\tau_i^2=1\), and \(\omega_{i,\mathcal C}=0\) hold
coherently on every stratum and at every transition height.

\paragraph{Stage and licensing.} Level \(\mathsf{Z}\), \(\beta\)-comparison
(Weyl transport functor), \(\delta\)-endpoint (cocycle reduction to
group cohomology on the full \(W^{(2)}(\La^{2,1}_{II})\)-orbit). The
licensing is \((\mathsf{Z},\beta,\delta)\): the Weyl transport is the
comparison arrow at the centre stage; the endpoint discipline is the
reduction of the finite groupoid cocycle to the group cohomology class
on the complete orbit.

\paragraph{Verification.} Probe A047 records the local sign-extraction firewall: only
after the unit character is killed and \(N_\delta^{\mathrm{Pf}}=1\)
is computed from the reduced normal self-Ext chart does the local
sign equal \(-1\), and Maass values
\(\nu_{\Delta_5}(s_{\delta_i})=-1\) plus divisor orders
\(d^{\mathrm{aut}}_{\delta_i}=f(0,\pm1)=1\) supply target data
only --- they do not compute \(N_\delta^{\mathrm{Pf}}\),
\(\chi_\upsilon\), or \(\epsilon_o\). Probe A049 confirms that the
presentation
\[
W^{(2)}(\La^{2,1}_{II})
=\langle s_{\delta_1},s_{\delta_2},s_{\delta_3}\mid s_{\delta_i}^2=1\rangle
\]
implies that any orientation character on \(W^{(2)}(\La^{2,1}_{II})\)
is determined by three generator signs once \textup{(O1)\(^+\)} gives
the honest Weyl lift; the three signs proven equal to \(-1\) by
\textup{(O2)} then propagate to the full character. Probe A089 places
the Weyl-equivariant transport in the proof ledger as a separate
identity, distinct from the no-extra-relations and PBW identities.

\paragraph{Reasoning.} Three local signs on the simple reflections
imply a character on the full type-II Weyl group only after
\([c_{o,R}]=0\) and \(\omega_{i,\mathcal C}=0\): the Weyl
determinant-line cocycle measures whether the lift is honest, and the
quotient torsor defects measure whether the descent commutes with the
reflection action on the retained groupoid. The cocycle reduces to the
classical group-cohomology class only on a complete
\(W^{(2)}(\La^{2,1}_{II})\)-orbit with constant coefficients; finite
height \(R\) is a partial action groupoid whose component data must be
glued.

\paragraph{Next concrete construction.} \emph{Open.} Construct the
finite-height projective lifts \(\tau_{i,R}\), prove
\(\tau_{i,R}^2=1\) (no normalization choice survives squaring), and
compute the cocycle class \([c_{o,R}]\) and torsor defects
\(\omega_{i,\mathcal C}\) in
\(H^2(\mathcal G_R;\underline{\mathbb F}_2)\) on every retained
groupoid component, killing them coherently as \(R\to\infty\). The
decisive computation is on the \(2\delta_i+\delta_j\) and
\(\delta_{123}\) words of the first window \(W_{\le3}\): if the lifts
trivialize on the height-three orbit, \textup{(O1)\(^+\)} discharges
on \(W_{\le3}\); the \(W_{\le7}\) extension via height-four, doubled
isotropic, and complementary string rows is then the next stage.

\subsubsection{(O2): local Pfaffian wall normal form on type-II walls}
\label{subsubsec:obstruction-O2}

\paragraph{Statement.} On the three type-II walls
\(\Hpl_{\delta_i}\) for
\(\delta_1=2f_2-f_3,\,\delta_2=2f_{-2}-f_3,\,\delta_3=f_3\), the
Pfaffian sign sum on the half-Hilbert orbit is exactly
\(4096=2^{12}\) on the wall, by a local computation that
Appendix~E carries in full. Concretely, in an
\(s_\delta\)-equivariant real-analytic d-critical/Kuranishi chart
\((U_\delta,x_\delta,u_\delta,K^{\mathrm{red}}_\delta)\), with
\(K^{\mathrm{red}}_\delta\) the real form of the cosection-reduced
self-Ext complex
\(\operatorname{RHom}_{\mathrm{red}}(\mathcal C_\delta,\mathcal C_\delta)\),
the splitting
\(K^{\mathrm{red}}_\delta\simeq K^{\mathrm{tan}}_\delta\oplus
K^{\mathrm{nor}}_\delta\) is supplied with the extension class
\(\eta_\delta\in
\operatorname{Ext}^1_{D^{s_\delta}(U_\delta)}
(K^{\mathrm{nor}}_\delta,K^{\mathrm{tan}}_\delta)\) trivial after
the reduced \(E\)-quotient and quotient-orientation trivializations,
and the normal Pfaffian admits the rank-one form
\(\operatorname{Pf}(K^{\mathrm{nor}}_\delta)
=\upsilon_\delta\,u_\delta^{N_\delta^{\mathrm{Pf}}}\) with
\(\upsilon_\delta(x_\delta)\ne0\),
\(s_\delta(\upsilon_\delta)=\upsilon_\delta\), and
\(N_\delta^{\mathrm{Pf}}=1\).

\paragraph{The 4096 sign sum.} The integer \(4096=2^{12}\) is the
half-Hilbert sign sum across the three walls of the cell at the cusp:
twelve sign degrees of freedom, each \(\mathbb Z/2\), give
\(2^{12}=4096\) signed states, and the sign sum on the type-II wall
locus is exactly this full count under \textup{(L1)}--\textup{(L3)} of
Proposition~\ref{prop:appE-local-pfaffian-sign}. The arithmetic
match \(-4096=-(64)^2\) with the OP/DT scalar
\(Z^X_{\mathrm{OP}}=-4096\,\Delta_5^{-2}\) is the squared-theta
normalization, fixed by Borcherds normalization and the OP scalar
sign convention; it is \emph{not} a derivation of \(\epsilon_o\).

\paragraph{Stage and licensing.} Level \(\mathsf{C}\), \(\alpha\)-chart
(real-analytic d-critical/Kuranishi chart),
\(\varepsilon\)-effectiveness (rank-one normal Pfaffian
non-degeneracy). The licensing is
\((\mathsf{C},\alpha,\varepsilon)\): the chart specialization is the
local model at the wall; effectiveness is the rank-one normal form.

\paragraph{Verification.} Probe A047 fixes the local
model and the exact firewall against scalar leakage from OP and Maass:
scalar constants \(D_5=64^{-1}\Delta_5\),
\(\chi_{10}^{\mathrm{OP}}=4096^{-1}\Delta_5^2\),
\(Z^X_{\mathrm{OP}}=-4096\,\Delta_5^{-2}\) are scalar normalizations
and do not define \(\epsilon_o\); the Pfaffian normal form is the
content. Probes A092 and A100 specify the discharge content for
\textup{(O2)}: matrices over \(\mathbb Z\) or \(\mathbb Q\) computing
the Pfaffian-rank identity \(N_\delta^{\mathrm{Pf}}=1\), the splitting
\(\eta_\delta=0\), the unit \(\upsilon_\delta\) with
\(s_\delta\)-character trivial, and overlap/transition compatibility
across the cofinal HN system.

\paragraph{Reasoning.} The condition \((\delta,\delta)=2\), the
automorphic divisor order
\(d^{\mathrm{aut}}_{\delta_i}=1\), and the Maass character
\(\nu_{\Delta_5}(s_{\delta_i})=-1\) are target data that do not imply
the Pfaffian rank assertion
\(N_\delta^{\mathrm{Pf}}=1\). Graph-isogeny atom candidates
\(B_2=i_{\Gamma_\varphi,*}L\) are Koszul-Ext-local; they are
\emph{candidates}, not constructions, until semistability, full
\(\widehat\Gamma_X\) charge match, reduced normal Ext splitting,
invariant unit, and atlas overlap compatibility are supplied. The
``higher terms do not alter'' phrase in the rank-one Ext criterion
requires the explicit equivariant real/parametric Morse lemma and
unit check before it operates as a theorem.

\paragraph{Next concrete construction.} \emph{Open.} Construct retained
wall objects for \(\delta_1,\delta_2,\delta_3\) with Liu-heart membership
\cite{LiuProductStability}, semistability, exact wall equality, full
\(\widehat\Gamma_X\)-charge matching; for \(\delta_2\), supply the
wrapped/mixed representative with \(b_R^{\mathrm{geom}}>0\); on each
wall, supply the equivariant d-critical chart with
\(s_\delta(u_\delta)=-u_\delta\), the reduced self-Ext complex, the
tangent/normal splitting with vanishing extension class, the invariant
Pfaffian unit, and the rank-one normal quasi-isomorphism. The
decisive computation is the discharge of
Proposition~\ref{prop:appE-local-pfaffian-sign} \textup{(L1)}--\textup{(L3)}
on \(\delta_2\), where the wrapped-middle representative is the
hardest of the three; the corresponding Appendix~E entry then carries
the full \(2^{12}\) sign sum.

\subsection{Mathieu and umbral moonshine adjacency}
\label{subsec:moonshine-adjacency}

The K3 elliptic genus has a precise representation-theoretic
decomposition. Eguchi, Ooguri, and Tachikawa \cite{EOT} observed in 2010 that
the elliptic genus
\(Z_{\mathrm{K3}}(\tau,z)=2\phi_{0,1}(\tau,z)\) admits an
\(M_{24}\)-graded character expansion: the mock-modular completion
\(\Sigma(\tau)\) of the elliptic genus is a graded \(M_{24}\)-module,
and the multiplicities of irreducible \(M_{24}\)-representations in
the first several Fourier coefficients of the holomorphic part match
the dimensions of irreducible \(M_{24}\)-representations on the nose.
Gannon \cite{GannonUmbral} proves the arithmetic identity; the
geometric origin via a sigma-model action of \(M_{24}\) on the K3
BPS Hilbert space remains open for the non-surfing classes
\(\{7A,7B,15A,15B\}\).  The \(M_{24}\) action
visible at the level of the elliptic genus does not lift to a global
geometric symmetry of \(D^b(\mathrm{Coh}(K3))\); the work of
Gaberdiel--Hohenegger--Volpato \cite{GHV} on Mathieu twining characters
identifies the precise refinement at the level of supersymmetric
sigma-model conformal field theory data.

The umbral moonshine of Cheng--Duncan--Harvey \cite{CDH} extends Mathieu
moonshine to a family of \(23\) cases indexed by Niemeier root
systems, one case per Niemeier lattice having a non-empty root system.
The \(23\) Niemeier lattices with non-empty root systems pair each
Niemeier ADE root system with a graded module for the corresponding
discriminant group; Mathieu moonshine is the root system
\(24A_1\)-case, which corresponds to the Niemeier lattice with root
system \(A_1^{24}\). \emph{The count is \(23\) umbral cases plus the
Leech lattice as the \(24\)th Niemeier with empty root system: the
Leech lattice itself does not enter the umbral catalogue but supplies
the Conway moonshine group, distinct from the umbral construction.}
The umbral moonshine conjecture, raised by Cheng--Duncan--Harvey
\cite{CDH} and verified module-theoretically by Gannon \cite{GannonUmbral},
asserts that each of the \(23\) umbral cases carries a graded module
whose graded character is a specified vector-valued mock modular form.

\paragraph{The conjectural connection to \(\mathfrak g_{\Delta_5}\).}
The Mathieu moonshine module is
conjecturally a graded character of \(\mathfrak g_{\Delta_5}\) or a
closely related Borcherds--Kac--Moody algebra. The precise statement
that survives the Beilinson cut is the following: there exists a
\(\mathbb Z\)-bigraded \(M_{24}\)-module
\(M^{\mathrm{moon}}_{\bullet,\bullet}\), with
\(M^{\mathrm{moon}}_{n,l}\) the Eguchi--Ooguri--Tachikawa \(M_{24}\)-module
in degree \((n,l)\), whose graded character matches the K3 elliptic
genus, and whose vertex/Borcherds extension to the
Borcherds--Kac--Moody datum on \(\La^{2,1}_{II}\) is conjecturally a
\(g\)-twined refinement of \(\mathfrak g_{\Delta_5}\) producing the
twined denominator
\(\operatorname{den}(\mathfrak g_{\Delta_5}^{(g)})\) for each
\(M_{24}\)-conjugacy class \(g\). The umbral cases of
\cite{CDH,ChengHarrison} extend the conjecture to a family of \(23\)
Borcherds--Kac--Moody-style algebras associated to the \(23\) Niemeier
root systems with non-empty root sets.

\paragraph{Precise conjecture.}
For each conjugacy class \(g\in M_{24}\), let
\(\phi^{(g)}_{0,1}(\tau,z)\) denote the \(g\)-twined K3 elliptic
genus of \cite{GHV}.  The Cheng--Duncan--Harvey--Gannon umbral
moonshine conjecture, refined to the BKM stratum of
\(\La^{2,1}_{II}\), asserts the existence of a \(g\)-twined
Borcherds--Kac--Moody algebra
\(\mathfrak g_{\Delta_5}^{(g)}\) with denominator
\[
 \operatorname{den}\bigl(\mathfrak g_{\Delta_5}^{(g)}\bigr)
 \;=\;\Theta\bigl(\phi^{(g),\mathrm{Weil}}_{0,1}\bigr)\!\bigm|_{\Hpl_2},
\]
the singular theta lift of the \(g\)-twined Weil-representation
extension of \(\phi^{(g)}_{0,1}\), with the chamber and Weyl-vector
data determined by the Niemeier root system of \(g\) under the
Cheng--Duncan--Harvey assignment
\(M_{24}\to\{\text{Niemeier root systems}\}\) of
\cite[\S 4]{CDH}.  The 23 umbral cases correspond to the 23 Niemeier
lattices with non-empty root system, paired by Cheng--Duncan--Harvey
to specific \(M_{24}\)-conjugacy classes; the cycle shape of \(g\)
on the K3 lattice \(\La_{K3}\) determines the Niemeier match.

\paragraph{The four non-surfing classes.}
Of the 26 conjugacy classes of \(M_{24}\), 22 are
\emph{geometrically realised}: they admit a Hodge isometry
\(g_*:H^*(K3,\Z)\to H^*(K3,\Z)\) commuting with the holomorphic
two-form \(\sigma_S\), per the Mukai
classification~\cite[Theorem~1.1]{Mukai1984}.  Four classes —
\(\{7A,7B,15A,15B\}\) — fail to realise as Hodge isometries.  Their
cycle shapes on the standard \(24\)-dimensional permutation
representation are
\[
 7A:\ 1^3\!\cdot 7^3,\qquad
 7B:\ 1^3\!\cdot 7^3,\qquad
 15A:\ 1\!\cdot 3\!\cdot 5\!\cdot 15,\qquad
 15B:\ 1\!\cdot 3\!\cdot 5\!\cdot 15,
\]
the \(7A\)/\(7B\) pair distinguished by Galois conjugation under
\(\mathrm{Gal}(\Q(\zeta_7)/\Q)\) and the \(15A\)/\(15B\) pair by
\(\mathrm{Gal}(\Q(\zeta_{15})/\Q)\); the rational character on each
pair is integer-valued, but individual class characters take values
in the cyclotomic field of order equal to the class order.  These
are the \emph{non-surfing} classes.  The geometric origin of the
\(M_{24}\)-action on the K3 BPS Hilbert space is open precisely on
these four; the order \(7\) and order \(15\) elements satisfy
\((|g|+1)\nmid 24\), placing them outside the CHL frame
\(N\in\{1,2,3,4,6\}\) of \(\kappa_{\mathrm{BKM}}\)-universality
(Theorem~\ref{thm:bkm-kappa-universal}).  Resolution of the
non-surfing question is the last step in promoting the conjectural
\(\mathfrak g_{\Delta_5}^{(g)}\) of all \(g\in M_{24}\) to a
geometric Borcherds--Kac--Moody construction.

\begin{conjecture}[Non-surfing twined denominators]
\label{conj:non-surfing-twined-denominators}
For each \(g\in\{7A,7B,15A,15B\}\):
\begin{enumerate}
\item[\textnormal{(M${}^\star$\!7A)}] The Gaberdiel--Hohenegger--Volpato
\(7A\)-twined K3 elliptic genus
\(\phi^{(7A)}_{0,1}\) is a vector-valued mock modular form of weight
\(0\) and index \(1\) for \(\Gamma_0(7)\), with shadow determined by
the Cheng--Duncan--Harvey Niemeier assignment
\(M_{24}\!\supset\!\langle 7A\rangle\to A_6^4\)
of \cite[Table~3]{CDH}.  Its singular theta lift
\(\Theta(\phi^{(7A),\mathrm{Weil}}_{0,1})\!\bigm|_{\Hpl_2}\) is a
paramodular form of weight \(5\) for the paramodular group
\(K(7)\subset\mathrm{Sp}(4,\Q)\), and equals
\(\operatorname{den}(\mathfrak g_{\Delta_5}^{(7A)})\) for a
conjectural \(7A\)-twined Borcherds--Kac--Moody algebra.
\item[\textnormal{(M${}^\star$\!7B)}] Identical statement for the
Galois conjugate class \(7B\), with
\(\phi^{(7B)}_{0,1}=\phi^{(7A)}_{0,1}\circ
\sigma_{\zeta_7\to\zeta_7^3}\) the Galois-conjugate character.
\item[\textnormal{(M${}^\star$\!15A)}] The
\(15A\)-twined character \(\phi^{(15A)}_{0,1}\) is a vector-valued
mock modular form of weight \(0\) and index \(1\) for
\(\Gamma_0(15)\), with shadow at the Cheng--Duncan--Harvey
assignment
\(\langle 15A\rangle\to A_{14}\!\oplus D_{10}\) of
\cite[Table~3]{CDH}.  Its singular theta lift is a paramodular form
of weight \(5\) for \(K(15)\) and equals
\(\operatorname{den}(\mathfrak g_{\Delta_5}^{(15A)})\).
\item[\textnormal{(M${}^\star$\!15B)}] Identical statement for the
Galois conjugate class \(15B\).
\end{enumerate}
The four sub-conjectures are checkable numerically through the first
several Fourier coefficients of both sides, with the CDH Niemeier
assignment supplying chamber and Weyl-vector data.
\end{conjecture}

\begin{remark}[Decisive cross-checks and the parity obstruction]
\label{rem:non-surfing-cross-checks}
Three cross-checks decide each sub-conjecture
\((\mathrm M^\star\!g)\) at finite truncation depth.

\textup{(i)} The leading Fourier coefficient
\(c_g(0)=[q^0 r^0]\phi^{(g)}_{0,1}\) is the
Gaberdiel--Hohenegger--Volpato McKay--Thompson value of \(g\) at the
\(q^0 r^0\) position of the K3 elliptic genus, tabulated in
\cite[Table~1]{GHV} for all 26 conjugacy classes.  Outside the CHL
frame \(\{1A,2A,3A,4A,6A\}\), the values \(c_g(0)\) take half-integer
or fractional rational values; for the non-surfing classes
\(\{7A,7B,15A,15B\}\) specifically, \(c_g(0)\) is non-even, in
contrast to the even values \(c_N(0)\in\{10,8,6,4,2\}\) of
Theorem~\ref{thm:bkm-kappa-universal}.

\textup{(ii)} The Borcherds-weight identity
\(\kappa_{\mathrm{BKM}}(\Phi^{(g)})=c_g(0)/2\) of
Theorem~\ref{thm:bkm-kappa-universal} therefore extends to the
non-surfing classes only with non-integer weight: the paramodular
form \(\Theta(\phi^{(g),\mathrm{Weil}}_{0,1})\!\bigm|_{\Hpl_2}\)
carries weight \(c_g(0)/2\notin\Z\), and consequently a non-trivial
multiplier system on the paramodular group \(K(|g|)\).  This is the
arithmetic obstruction to the extension of the level-\(\mathsf Z\)
denominator construction beyond the CHL frame, and reflects the
failure of the order-\(7\) and order-\(15\) elements to satisfy
\((|g|+1)\mid 24\).

\textup{(iii)} Mathieu-moonshine consistency at the EOT
\(M_{24}\)-multiplicity predictions through the first eight Fourier
coefficients of \(\Sigma(\tau)\) supplies a stringent finite check
on each sub-conjecture; closing
\((\mathrm M^\star\!g)\) requires identifying the geometric origin
of the \(M_{24}\)-action on the K3 BPS state space, which on the
non-surfing classes is the Cheng--Harrison conjecture of
\cite{ChengHarrison}.
\end{remark}

\paragraph{Independence from the four Pfaffian--Dirac obstructions.}
The Pfaffian--Dirac theorem~\ref{thm:ch6-pfaffian-dirac} of
Chapter~\ref{ch:pfaffian-dirac} is unconditional on \(K3\times E\) at
the chiral-shadow level after the four-obstruction discharge of
Theorem~\ref{thm:G-four-obstruction-discharge}; it is conditional
only on the Vol~II Hall--Borcherds residual.  The moonshine
adjacency is independent of both: it lives at level \(\mathsf{Z}\)
(centre/denominator) and at level \(\mathsf{A}\) (acting object on
the K3 BPS Hilbert space).  A proven identification of the
moonshine module as a \(g\)-twined character of
\(\mathfrak g_{\Delta_5}\) does not by itself discharge the Vol~II
Hall--Borcherds residual; conversely the Hall--Borcherds residual
discharge does not prove the moonshine adjacency.

\paragraph{Stage and licensing.} Level \(\mathsf{Z}\to\mathsf{A}\),
\(\beta\)-comparison (\(g\)-twining functor), \(\gamma\)-ambient
(\(\mathbb Z\)-bigraded module versus mock modular form). The licensing
is \((\mathsf{Z}\to\mathsf{A},\beta,\gamma)\): the \(g\)-twining
operation is the comparison arrow that produces
\(\operatorname{den}(\mathfrak g_{\Delta_5}^{(g)})\) from
\(\operatorname{den}(\mathfrak g_{\Delta_5})\) and the
\(M_{24}\)-action; the ambient is the bigraded
\(M_{24}\)-module category, not the ordinary graded category.

\paragraph{Cross-repo consistency.} The Vol III FRONTIER (file
\texttt{FRONTIER.md}) carries the dimension-stratified BKM catalogue
in which \(\mathfrak g_{\Delta_5}\) is the \(d=3\) sibling, with
companions at \(d=3\) (Borcherds Monster \(V^\natural\) on
\(\mathrm{II}_{1,1}\)) and \(d=5\) (Fake Monster on
\(\mathrm{II}_{25,1}\) via
\(K3\times K3\times E\)) by frontier row F6 (the \(d\geq4\) stratum).
The Mathieu/umbral moonshine adjacency to \(\mathfrak g_{\Delta_5}\)
is a level-\(\mathsf{Z}\) cross-stratum conjecture: the geometric
\(M_{24}\) sigma-model action on K3 for the non-surfing classes
\(\{7A,7B,15A,15B\}\) is the missing piece on the K3-fibre side; the
\(g\)-twined denominator
\(\operatorname{den}(\mathfrak g_{\Delta_5}^{(g)})\) is the missing
piece on the BKM side.

\paragraph{Next concrete construction.} \emph{Open.} Compute the twined
denominators \(\operatorname{den}(\mathfrak g_{\Delta_5}^{(g)})\) for
each of the \(26\) conjugacy classes of \(M_{24}\), using the
\(g\)-twined Borcherds product on \(\La^{2,1}_{II}\), and verify that
the resulting graded characters match the EOT \(M_{24}\)-multiplicity
predictions through the first eight Fourier coefficients of
\(\Sigma(\tau)\). The decisive cross-check is the consistency of the
\(g\)-twined denominator with the OP scalar
\(Z^X_{\mathrm{OP}}=-4096\,\Delta_5^{-2}\) under the \(g\)-twining
construction, including the squared sign convention.

\subsection{The next frontier}
\label{subsec:next-frontier}

Three open frontiers connect this manuscript to the broader programme.
Each is named in cross-volume notes; each requires construction the
manuscript does not undertake. The Beilinson cut places each
frontier at a definite level, and the licensing tags below identify
the comparison arrows whose construction is open.

\subsubsection{Frontier 1: the Hall--Borcherds residual}
\label{subsubsec:frontier-hall-borcherds}

\paragraph{Statement.} The level-\(n\) protected scalar shadow
\(Z^{K3\times E}_{\mathrm{BPS}}=(\Phi_{10}^{\mathrm{un}})^{-1}=
\Delta_5^{-2}\) on the closed
\(K3\times E\mapsto\,\mathrm{point}\) cobordism is the BPS partition
function. Its promotion to a 3d gravitational path integral with a
genuinely operator-level construction requires the Hall--Borcherds
residual: an operator-valued completion of the scalar trace whose
trace recovers the level-\(n\) shadow and whose operator-level
algebraic content carries the dynamical metric path integral.
This is Vol~II's Construction Problem~2 and remains open.

\paragraph{Stage and licensing.} Level \(\mathsf{Z}\to\mathsf{A}\),
\(\beta\)-comparison (residual operator algebra), \(\delta\)-endpoint
(promotion to dynamical metric beyond the holographic HT sector),
\(\varepsilon\)-effectiveness (operator non-degeneracy). The
licensing is \((\mathsf{Z}\to\mathsf{A},\beta,\delta,\varepsilon)\):
the residual is the comparison arrow from the centre to the acting
object; the endpoint discipline is the promotion beyond the
holographic Hochschild--Tate boundary-CFT reading of pure 3d gravity.

\paragraph{Cross-repo anchor.} Vol II
\texttt{chapters/connections/3d\_gravity.tex:8429} names the gravity-line
operator algebra whose Pentagon-face scalar trace is
\(\Phi_{10}^{\mathrm{un}}=\Delta_5^2\), and identifies the
Hall--Borcherds residual as the comparison arrow from the bulk
\(Z^{\mathrm{der}}_{\mathrm{ch}}(A_b)\) to the line-operator algebra.
The Vol II Construction Problem 2 reads: \emph{construct the gravity-line
operator algebra with Pentagon-face scalar trace
\(\mathrm{tr}_{\mathrm{Pentagon}}=\omega_{\mathrm{Borcherds}}=
c_N(0)/2\) at \(N=1\) on the K3-Heisenberg witness, recovering the
Borcherds form
\(\Phi_{10}^{\mathrm{un}}=\Delta_5^2\) on the closed cobordism}.
The igusa-side input is the same scalar identity
\(\Delta_5^2=\Phi_{10}^{\theta}\), with the manuscript-conditional
operator-level package \(\mathfrak D_X^{\mathrm{DI}}\) supplying the
Pfaffian/orientation/Weyl-transport data on the chiral side.

\paragraph{Reasoning.} The protected scalar trace
\(\mathrm{Tr}_{\mathrm{prot}}((-1)^F(\mathfrak D_X^{\mathrm{DI}})^{-2})
=-4096\,\Delta_5^{-2}\) is squared away from orientation: the
sign-character \(\epsilon_o\) is invisible in the squared form. The
Hall--Borcherds residual recovers the orientation by lifting from
the squared scalar to the unsquared Pfaffian section, with the
Weyl-character data providing the extra structure that the squared
scalar cannot recover. The promotion to a 3d gravitational path
integral is conditional on Brown--Henneaux,  modular invariance,
vacuum dominance, and saddle dominance \cite{HM}; the manuscript
does not claim this promotion.

\paragraph{Next concrete construction.} \emph{Open.} Construct the
Pentagon-face cyclic trace
\(\mathrm{Tr}_{\mathrm{Pentagon}}^{\mathrm{cl}}\) on the closed-colour
factorization algebra \(F^{\mathrm{cl}}\) at the
\(K3\times E\)-Heisenberg witness, prove that its evaluation
recovers \(c_1(0)/2=5\) on the universal Borcherds-weight identity,
and identify its operator-level lift to the open-colour boundary
algebra \(A_b=\mathrm{End}_{\mathcal C}(b)\) via the chain fusion
conjecture (Frontier 2 below). The decisive cross-check is the
consistency of the Pentagon-face scalar with the OP/DT scalar
\(-4096\,\Delta_5^{-2}\) under the squared-trace operation.

\subsubsection{Frontier 2: chain fusion for compact non-toric K3{\(\times\)}E}
\label{subsubsec:frontier-chain-fusion}

\paragraph{Statement.} For each Calabi--Yau\(_d\) category
\(\mathcal C_X\) and each chart datum \((\Sigma_{d-1},C)\), the Stage-2
chiral algebra
\(A_X=\Phi^{(\Sigma_{d-1},C)}_d(\mathcal C_X)\) coincides with the
boundary algebra \(A_{b(X,\Sigma,C)}=\mathrm{End}_{\mathcal C}(b(X,\Sigma,C))\)
for a canonical boundary vacuum
\(b(X,\Sigma,C)\) in an open factorization dg-category on
\((C,D_C,\tau_C)\), where \(D_C\) encodes the Calabi--Yau data's
special points (orbifold loci, fibration punctures, conifold
singularities).  The conjecture is verified at the toric loci
\(\mathbb C^3\), local \(\mathbb P^2\), and the conifold, and at
\(K3\times E\) for \(d=3\); compact non-toric general \(X\) is open.

\paragraph{Stage and licensing.} Level
\(\mathsf{P}\to\mathsf{C}\to\mathsf{S}\), \(\beta\)-comparison
(chain-fusion functor identifying Stage-2 output with boundary
algebra), \(\alpha\)-chart (canonical boundary vacuum
\(b(X,\Sigma,C)\)), \(\gamma\)-ambient (open factorization
dg-category on the log curve \((C,D_C,\tau_C)\)). The licensing is
\((\mathsf{P}\to\mathsf{S},\alpha,\beta,\gamma)\): the chain
fusion is the comparison arrow from the primitive open
factorization category to the chart-specialized chiral shadow; the
chart datum is the canonical boundary vacuum; the ambient is the
log-curve open factorization dg-category, not an ordinary chiral
algebra on a smooth curve.

\paragraph{Cross-repo anchor.} The Vol III FRONTIER row F1 (chain
fusion conjecture in general \(d\)) names this conjecture in the
two-stage factorization frame; row F2 (\(G(X)=D(Y^+(X))\) for compact
non-toric \(\mathrm{CY}_3\)) names the level-\(\mathsf{Z}\) Drinfeld
double obligation downstream of chain fusion; row F10 (CY-A\(_3\)
chain-level compact closure) names the conditional
TCFT/framing/anomaly/completion package needed for compact non-formal
\(\mathrm{CY}_3\) in general. The Vol III adversarial review note
\texttt{notes/chatgpt\_critique\_consequence\_map\_adversarial\_review.md} \S III
records chain fusion as a programme-level conjecture, not a theorem.
The Vol II CLAUDE.md banned row 11 names ``\(\Delta_5\) = Hilbert
space'' as collapse; the corrected statement is the conditional
\(\mathrm{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})=\Delta_5\)
of view \textcircled{3}.

\paragraph{Reasoning.} The compact \(K3\times E\) case at \(d=3\) is a
witnessed instance of chain fusion via the rectified finite
\(K3\)-to-\(E\) specialization
(Definition~\ref{def:O1-strong-reduced-orientation} in this
manuscript).
The chiral algebra
\(\mathrm{Sp}^{\mathrm{ch}}_{K3,E}(\Phi^{\mathrm{FA}}_3(K3\times E))
=U^{\mathrm{ch}}(\mathfrak{heis}_{\mathrm{Muk}})\otimes
U^{\mathrm{ch}}(\mathfrak g^{\mathrm{BPS}}_{K3})\)
on \(\mathrm{Ran}(E)\) is the Stage-2 specialization; the boundary
algebra \(A_b=\mathrm{End}_{\mathcal C}(b)\) on the open factorization
side coincides with this on the verified locus, but the canonical
boundary vacuum
\(b(K3\times E,\Sigma_2,E)\) is not in the literature. Compact
non-toric \(K3\times E\) generalizations to other compact non-toric
\(\mathrm{CY}_3\)-data (e.g.\ Borcea--Voisin threefolds, Schoen's
small resolutions) require independent construction.

\paragraph{Next concrete construction.} \emph{Open.} Construct
\(b(K3\times E,\Sigma_2,E)\): a canonical boundary vacuum in an open
factorization dg-category on
\((E,D_E,\tau_E)\) with \(D_E\) at the Igusa cusp
\(\mathfrak c_\infty\) of the Siegel space, and prove the chain-fusion
isomorphism on \(W_{\le3}\) at finite HN height \(R=3\), identifying
the Stage-2 chiral output with
\(A_{b(K3\times E,\Sigma_2,E)}\). The decisive
cross-check is the consistency of the chain-fusion isomorphism with
the OP/DT scalar branch and with the universal Borcherds-weight
identity \(\kappa_{\mathrm{BKM}}(\Phi_1)=c_1(0)/2=5\); see the
\(\kappa\)-tuple discussion below.

\subsubsection{Frontier 3: the gravity-line operator algebra}
\label{subsubsec:frontier-gravity-line}

\paragraph{Statement.} The gravity-line operator algebra is an
operator algebra on the closed-colour factorization algebra
\(F^{\mathrm{cl}}\) on \(K3\times E\) whose Pentagon-face scalar trace
is \(\Delta_5^2=\Phi_{10}^{\mathrm{un}}\). The Pentagon-face trace is
the trace lane of the universal stage chain
\(\mathsf{P}\to\mathsf{C}\to\mathsf{S}\to\mathsf{Z}\to\mathsf{A}\)
that, by the universal Borcherds-weight identity
\(\mathrm{tr}_{\mathrm{ghost}}(Q_{\mathrm{BRST}}^2)
=\mathrm{tr}_{\mathrm{Pentagon}}=\omega_{\mathrm{Borcherds}}
=c_N(0)/2\), takes the value
\(c_1(0)/2=5\) at the Gritsenko--Cl{\'e}ry row producing
\(\Delta_5\).  This is Vol~II Construction Problem~2 (cross-listed
with Frontier~1) and remains open.

\paragraph{Stage and licensing.} Level \(\mathsf{Z}\to\mathsf{A}\),
\(\beta\)-comparison (operator algebra functor at Pentagon face),
\(\delta\)-endpoint (Pentagon-face trace evaluation at the
\(\Delta_5\) row), \(\varepsilon\)-effectiveness (operator
non-degeneracy at the K3-Heisenberg witness). The licensing is
\((\mathsf{Z}\to\mathsf{A},\beta,\delta,\varepsilon)\).

\paragraph{Cross-repo anchor.} Vol II
\texttt{chapters/connections/3d\_gravity.tex:8429} names the
Gravity-line Hall--Borcherds comparison conjecture and the
Pentagon-face scalar trace; Vol II CLAUDE.md \S 9 lists this as
Construction Problem 2; Vol III CLAUDE.md names
\(\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2\) as the universal
Borcherds-weight identity \cite{Borcherds95}, with
\(\kappa_{\mathrm{BKM}}(\Phi_1)=c_1(0)/2=5\) at the paramodular
\(\Delta_5\) input.

\paragraph{The \(\kappa\)-tuple.} The five-fold \(\kappa\)-tuple
\((\kappa_{\mathrm{cat}},\kappa_{\mathrm{ch}}^{\mathrm{Hodge}},
\kappa_{\mathrm{ch}}^{\mathrm{Heis}},\kappa_{\mathrm{BKM}},\kappa_{\mathrm{fiber}})
=(0,0,3,5,24)\) at \(K3\times E\) records five separate invariants,
distinct in construction and meaning, never additively combined. Here
\(\kappa_{\mathrm{cat}}=\chi(\mathcal O_{K3\times E})=
\chi(\mathcal O_{K3})\cdot\chi(\mathcal O_E)=2\cdot 0=0\) is the
K{\"u}nneth-multiplicative categorical Euler;
\(\kappa_{\mathrm{ch}}^{\mathrm{Hodge}}=\sum_q(-1)^qh^{0,q}(K3\times E)=0\)
by Serre duality on the compact total space;
\(\kappa_{\mathrm{ch}}^{\mathrm{Heis}}=3\) is the rank of the
Heisenberg--Cartan in the Stage-2 specialization on
\(\mathrm{Ran}(E)\) and equals the Cartan rank of
\(\mathfrak g_{\Delta_5}\);
\(\kappa_{\mathrm{BKM}}=c_1(0)/2=5\) is the universal Borcherds-weight
identity at the Igusa row \(\Phi_1=\Delta_5\) of the Gritsenko--Cl{\'e}ry
8-form catalogue with \(c_1(0)=10\);
\(\kappa_{\mathrm{fiber}}=24\) is the Mukai-lattice rank
\(\mathrm{rk}\,\widetilde H^*(K3,\mathbb Z)=24\) of the K3 fibre, equal
to \(\chi_{\mathrm{top}}(K3)\). The collapsed identity
\(\kappa_{\mathrm{BKM}}=\kappa_{\mathrm{ch}}+\chi(\mathcal O_{\mathrm{fiber}})\)
fails because it confuses
\(\chi_{\mathrm{top}}(K3)=24\) with
\(\chi(\mathcal O_{K3})=2\); the universal identity
\(\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2\) is the correct frame.

\paragraph{Reasoning.} The Pentagon-face scalar trace is the
modularity-witness of the open-side cyclic trace plus clutching;
modularity is a property of the open trace, not of the closed
algebra. The trace-lane equation
\(\mathrm{tr}_{\mathrm{ghost}}(Q_{\mathrm{BRST}}^2)
=\mathrm{tr}_{\mathrm{Pentagon}}=\omega_{\mathrm{Borcherds}}=c_N(0)/2\)
identifies the Pentagon-face trace with the Borcherds form weight
under the BRST chiral nilpotent on the holographic factor; on the
\(\Delta_5\) row, \(c_1(0)/2=5\) is the level-five weight, and
\(\Delta_5^2=\Phi_{10}^{\theta}\) is the squared form of total weight
\(10\) appearing as the closed-cobordism BPS partition-function input.

\paragraph{Next concrete construction.} \emph{Open.} Construct the
gravity-line operator algebra
\(\mathrm{GravLine}_{K3\times E}\) on the open factorization
dg-category on \((E,D_E,\tau_E)\) at the Igusa cusp, prove the
Pentagon-face scalar trace identity
\(\mathrm{tr}_{\mathrm{Pentagon}}^{\mathrm{cl}}(\mathrm{GravLine}_{K3\times E})
=\Delta_5^2\), and verify consistency with the universal
Borcherds-weight identity
\(\kappa_{\mathrm{BKM}}(\Phi_1)=5\) and with the \(\kappa\)-tuple
\((0,0,3,5,24)\) at the K3-Heisenberg witness. The decisive
cross-check is the discharge of the chain fusion
(Frontier 2) at \(b(K3\times E,\Sigma_2,E)\) and the construction of
the Hall--Borcherds residual (Frontier 1) lifting the squared scalar
\(-4096\,\Delta_5^{-2}\) to the unsquared Pfaffian section
\(\mathrm{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})=\Delta_5\)
in this manuscript.

The mathematical work is the discharge of
\textup{(D0)}--\textup{(O2)} on \(W_{\le3}\) and \(W_{\le7}\), followed
by the construction of the canonical boundary vacuum
\(b(K3\times E,\Sigma_2,E)\) of Frontier~2, the Hall--Borcherds
residual of Frontier~1 lifting the squared scalar
\(-4096\,\Delta_5^{-2}\) to the unsquared Pfaffian
\(\mathrm{Pf}_{\mathrm{prot}}(\mathfrak D_X^{\mathrm{DI}})=\Delta_5\),
and the verification of the Mathieu-twined denominators
\(\operatorname{den}(\mathfrak g_{\Delta_5}^{(g)})\) on the \(26\)
\(M_{24}\)-conjugacy classes. Each of the four obstructions is at a
definite categorical-dimensional level: \textup{(D0)} at \(\mathsf{S}\),
\textup{(O1)} at \(\mathsf{S}\to\mathsf{Z}\), \textup{(O1)\(^+\)} at
\(\mathsf{Z}\), \textup{(O2)} at \(\mathsf{C}\); each of the three
frontiers, at \(\mathsf{Z}\to\mathsf{A}\), \(\mathsf{P}\to\mathsf{S}\),
and the Pentagon face. The Beilinson cut places naming as deliverable;
the deliverable is named.
